### 2018-05-15 challenges.tex
First version

\section{Challenges and Open Problems}
\label{sec:challenges}

...

\subsection{Single- vs. multi-domain}
...

\subsection{Simple Usage, Simple Parameters}
Proposal of a data generator (not necessarily for graph data) has to face an important schism. On the one hand, there is the aim to provide the user with as many parameters as possible in order to enable one to generate any kind of data. This approach seems to be reasonable, but it encounters the fact that users are usually unwilling to use complex benchmarking tools. This observation can be seen, for example, in the case of XML benchmarks -- even though there exist robust and complex data generators (such as ToXGene~\cite{conf/webdb/BarbosaMKL02}, which supports specification of structural aspects, value distributions, references etc.), the most popular benchmarking tool is XMark~\cite{Schmidt:2002:XBX:1287369.1287455} which models a single use case and enables to specify just the size of the data. Hence, the other extreme is to provide a simple data generator which does not require any complex settings and thus the benchmarking process is extremely simple and fast.

Considering the complex structure of graph data and the variety of applications having highly specific types of graphs, the latter solution is difficult to implement. A reasonable compromise can thus be seen in a data generator which is provided with sample graph data and is capable of automatic analysis of their structural and value specifics in order to gain the complex parameters.

\subsection{Evolving Graph Data}
As user requirements as well as environments change, most of the existing applications naturally evolve over time, at least to some extent. This evolution usually influences the structure of the data and consequently all the related parts of the application (i.e., storage strategies, operations, indices etc.). The respective data generator should hence be able to simulate such a growth and/or change in structure.

In some graph applications, such as, e.g., social networks, the evolution of the data is a significant aspect, especially in the activity graphs, that has been studied extensively~\cite{doreian1997evolution,Kumar:2006:SEO:1150402.1150476,Hellmann2014583,wang2013,Kossinets88,Viswanath:2009:EUI:1592665.1592675}.  A related problem is \emph{data versioning} and respective ability to query across multiple versions of data or in general its analysis. Considering graph data this problem is also common, for example  in the area of Linked Data~\cite{DBLP:conf/semweb/Papakonstantinou16,DBLP:conf/esws/MeimarisP16,fernandez2015towards,fernandez2015bear}.

As shown in papers~\cite{Leskovec:2005:RMT:2101235.2101254,Leskovec:2005:GOT:1081870.1081893}, evolving graphs have further specific features. For example, some graphs grow over time according to a \emph{densification power law} which means that real graphs tend to sprout many more edges than nodes, and thus are densifying as they grow. Also the effective diameter of graphs tends to shrink or stabilize as the graph grows with time.

%\paragraph{} Following the same recursion idea, paper~\cite{Leskovec:2005:RMT:2101235.2101254} uses Kronecker multiplication to generate self-similar graphs. The network starts with an initial graph G1 that contains $N_1$ nodes and $E_1$ edges. Using matrix recursion, larger successive graphs $G_2, G_3, ... G_n$ are generated. The $k$-th graph $G_k$ contains $N_k = N^k_1$ nodes. Many graphs often densify over time, exhibiting a growth in the number of edges that is superlinear to the number of nodes. Kronecker multiplication produces graphs with a fixed diameter and a densification power law degree distribution with exponent $k = log(E_1)/log(N_1)$. The graph generation process introduces a staircase effect in the nodes' degrees, and each community consists of smaller nested communities that are formed through expansion and recursion.

\subsection{Multi-model Data}
With the dawn of Big Data and especially its Variety aspect there have emerged also new types of database management systems. One of the most interesting ones are so-called \emph{multi-model databases} which enable to store and especially query across structurally different data. There exist various types of multi-model systems combining  distinct subsets of Big Data structures; hence, there naturally exists systems which combine graph data with other data models. For example, OrientDB\footnote{\url{http://orientdb.com/orientdb/}} which was implemented on the basis of an object DBMS currently supports graph, document, key/value, and object models.

Such type of DBMSs also needs a specific benchmark/data generator which enables to test new features and analyze efficiency of operations. However, since the multi-model systems are in the context of Big Data rather new, there exist only a few benchmarks targeting multi-model DBMSs (such as Bigframe~\cite{journals/pvldb/KunjirKB14} or UniBench~\cite{conf/cidr/lu17}) with limited capabilities.

\input{generators_community_detection}

### 2018-05-15 classification.tex
First version

\section{Classification of Graph Data Generators}
\label{sec:classification}

The graph data generators can be classified according to distinct criteria. For example, paper~\cite{DBLP:conf/sdm/ChakrabartiZF04} introduces two categories:

\begin{itemize}
  \item \emph{Degree-based generators}: Given a degree distribution (typically following a power law), these generators (e.g., Barabasi-Albert model~\cite{Barabasi99emergenceScaling}) try to find a graph that matches it, but without giving any insights about the graph or trying to match other criteria (like, e.g., small diameter, eigenvalues etc.).
  \item \emph{Procedural generators}: These generators (e.g., R-MAT~\cite{DBLP:conf/sdm/ChakrabartiZF04}) try to find simple mechanisms to generate graphs that match a property of the real graphs and, typically, the power law degree distribution.
\end{itemize}

Paper~\cite{Chakrabarti:2006:GML:1132952.1132954} introduces five categories of graph models (examples are further described below):
\begin{itemize}
  \item \emph{Random graph models} (e.g., Erd\"{o}s-R\'{e}nyi~\cite{Erdos:1960}) generated by a random process,
  \item \emph{Preferential attachment models} (e.g., Barabasi-Albert model) which try to model the power law from the preferential attachment viewpoint,
  \item \emph{Optimization-based models} (e.g., HOT model~\cite{PhysRevLett.84.2529}) resulting from the idea that power laws can result from resource optimizations and tolerance to risks,
  \item \emph{Tensor-based models} (e.g., R-MAT) targeting a trade-off between low number of model parameters and efficiency, and
  \item \emph{Internet-specific models} corresponding to hybrids using ideas from the other categories in order to suit the specific features of the graphs.
\end{itemize}

\paragraph{Erd\"{o}s-R\'{e}nyi} One of the first and still very popular approaches with lots of variations and modifications is the random graph model proposed in~\cite{Erdos:1960}. Given a positive integer $n$ and a probability value $0 \leq p \leq 1$, the graph $G(n,p)$ is an undirected graph on $n$ vertices whose edges are chosen s.t. for all pairs of vertices $u,v$ there is an edge $(u,v)$ with probability $p$.

\paragraph{Barabasi-Albert} The Barabasi-Albert (BA) model~\cite{Barabasi99emergenceScaling} proposes that structure emerges in network topologies as the result of two processes -- growth and preferential attachment. The BA model starts with a small set of nodes and grows the network as nodes and edges are added over time. Preferential attachment is based on the idea that the probability of connecting to a node is proportional to the current degree of that node (i.e., ``the rich get richer'').

\paragraph{HOT} The highly optimized tolerance (HOT)~\cite{PhysRevLett.84.2529} model is introduced  using a ``forest fire'' example as follows: Suppose we have a forest which is prone to forest fires. Each portion of the forest has a different chance of starting the fire. We wish to minimize the damage by assigning (a limited amount of) resources such as firebreaks at different positions in the forest. More precisely, we have $n$ possible events, each with an associated probability $p_i, 1 \le i \le n$. Each event can lead to some loss $l_i$, which is a function of the resources $r_i$ allocated for that event $(l_i = f (r_i))$, whose total number is limited ($\sum_i r_i \le R$ for some given $R$). The aim is to minimize the expected cost $\sum_i p_i l_i$. The authors show that resource placement is related to the probability distribution $p_i$ by a power law and the probability of events which cause a loss greater than some value $k$ is related to $k$ by a power law too.

\paragraph{R-MAT} The R-MAT (Recursive MATrix)~\cite{DBLP:conf/sdm/ChakrabartiZF04} model can be used to create graphs with community structure, power law degree distributions, and a small diameter. It generates weighted, directed and bipartite graphs. Graph generation is modeled with a matrix recursion procedure in which the adjacency matrix (empty at the beginning) is recursively subdivided into four equal-sized partitions and edges are distributed across the partitions with unequal probabilities.
\\

...

%~\cite{Gray:1992:BHD:530588}

Ideas to describe:

\begin{itemize}
  \item Domain-specific - predefined schema and domain knowledge - vs. application-specific~\cite{Tay2011}
  \item Use-case driven
  \item Query-centric vs. workload-driven~\cite{gMark}
  \item Language-specific (the document and query design is specifically laid out to test common language constructs, operator constellations, and data access patterns)~\cite{Schmidt2010}
  \item Application benchmarks attempt to predict the behaviour of a system on
certain classes of application by testing an example (or select examples) of that
class.
  \item Analytical benchmarks attempt to determine the presence or absence of cer-
tain performance related features, e.g., the presence of a query optimiser.
\end{itemize}

...

In Figure~\ref{fig:classification} ...

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{classification.png}
\caption{Classification of graph data generators}
\label{fig:classification}
\end{figure}

### 2018-05-15 comparison.tex
First version

\section{Comparative Study}
\label{sec:comparison}

In Tables~\ref{tab:comparisonCharacteristicsA},~\ref{tab:comparisonCharacteristicsB}   we overview the key characteristics of the data generators clustered according to the respective applications. In particular, we show:

\begin{itemize}
\item Characteristics of the domain - its \textit{type} (fixed, specified using a schema, or extracted from input data) and the particular \textit{target} domain, or, in case of a generic tool, the chosen sample domain,
\item Characteristics of \textit{read}/\textit{update} operations (if provided), i.e., whether the set of operations is fixed/generated, if it involves operation mixes (i.e., sets/sequences of operations), or if templates of operations are supported.
\item Key configuration options:  
  \begin{itemize}
    \item whether the generator deals only with structure, or also with \textit{properties} of the graph,
    \item supported types of \textit{distributions} used for generating of the data,
    \item \textit{output format} of the produced graph,
    \item  whether the generator is \textit{distributed} and thus enables more efficient data generation.
  \end{itemize}
\end{itemize}

\begin{sidewaystable}
\scriptsize 
\centering
\tbl{Key characteristics of the generators (part A)} {
\begin{tabular}{| c | p{2.2cm} | l |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
 \hline               
           &   & \multicolumn{2}{c}{\textbf{Domain}}
               & \multicolumn{2}{|c|}{\textbf{Operations}}             
               & \multicolumn{4}{c|}{\textbf{Configuration}}
               \\ \hline                
           &  \textbf{Generator}
               & \textbf{Type}
               & \textbf{Target / sample}               
               & \textbf{Read}
               & \textbf{Update}               
               & \textbf{\rot{Properties}}
               & \textbf{Distributions}
			   & \textbf{Output format}
               & \textbf{\rot{Distributed\ }}
               \\ \hline                
\hline   % general graphs (Angela)
\multirow{5}{*}{\rot{\textbf{General}}}
  & graph500  & fixed & & Y & N & Y & power-law & &  Y  \\
\cline{2-10}
   & R-MAt & fixed & & Y & N & Y & power-law & &  N  \\
\cline{2-10}
  & Watts-Strogatz~\cite{watts1998collective} & fixed & & Y & N & Y &  & &  N  \\
\cline{2-10}
  & Preferential Attachment~\cite{barabasi1999emergence} & fixed & & Y & N & Y &  & &  N  \\
\cline{2-10}
  & & & & & & & &  &   \\
\hline
\hline  % graph databases (Angela)
\multirow{4}{*}{\rot{\textbf{DBs}}}
 & XGDBench & fixed  & social network  & fixed & Y & Y & power-law &  MAG &  Y  \\
 \cline{2-10}
& graphGen & pattern-driven (Cypher schema) & user-defined  & -- & -- & Y & -- &  property graphs & N   \\
 \cline{2-10}
 & gMark & schema-driven (internal schema) &  user-defined  & generated &  N  & Y & uniform, normal, zipfian &  N-triples & N    \\
\hline
\hline % Semantic web (Irena)
\multirow{18}{*}{\rot{\textbf{Semantic web}}}
 & LUBM & fixed & university  & fixed & N & Y & random (LCG) &  RDF & N   \\  
\cline{2-10}
 & LBBM & extracted & Lehigh University BibTeX  & N & N & Y & Monte Carlo &  RDF & N   \\  
\cline{2-10}
 & UOBM & fixed & university  & fixed & N & Y & random &  RDF & N   \\  
\cline{2-10}
 & IIMB & fixed & movies  & N & N & Y & random &  RDF & N   \\  
\cline{2-10}
 & BSBM & fixed & e-commerce  & fixed & N & Y & mostly normal &  RDF, relational & N   \\ 
\cline{2-10}
 & SP$^2$Bench & fixed & DBLP  & fixed & N & Y & based on DBLP  & RDF & N   \\ 
\cline{2-10}
 & \cite{Duan:2011:AOC:1989323.1989340} & extracted & -- & N & Y &N & -- &  RDF & N    \\ 
\cline{2-10}
 & DBPSB & extracted & DBpedia &  templates & N & Y & random &  RDF & N   \\  
\cline{2-10}
 & LODIB & fixed & e-commerce &  N & N & Y & 44 types &  RDF & N   \\ 
\cline{2-10}
 & SIB & fixed & social network &  mixes & mix & Y & from real-world data &  RDF & N   \\ 
\cline{2-10}
 & Geographica & fixed & OpenStreetMap  & fixed + templates  & N & Y & -- &  RDF & N   \\ 
\cline{2-10}
 & WatDiv & schema-driven & user-defined  & templates & N & Y & uniform, normal, Zipfian &  RDF & N   \\  
\cline{2-10}
 & RBench & extracted & DBLP, Yago  & templates & N & Y & from real-world data &  RDF & N  \\  
\cline{2-10}
 & LDBC SPB & fixed & media  & mixes & N & Y & power law, skewed values, value correlation &  RDF & N  \\  
\cline{2-10}
 & LinkGen & & & & & & & & \\
\hline
\end{tabular} }
\label{tab:comparisonCharacteristicsA}
\end{sidewaystable}

\begin{sidewaystable}
\scriptsize 
\centering
\tbl{Key characteristics of the generators (part B)} {
\begin{tabular}{| c | p{2.2cm}| l |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
 \hline               
           &   & \multicolumn{2}{c}{\textbf{Domain}}
               & \multicolumn{2}{|c|}{\textbf{Operations}}             
               & \multicolumn{4}{c|}{\textbf{Configuration}}
               \\ \hline                
           &  \textbf{Generator}
               & \textbf{Type}
               & \textbf{Target / sample}               
               & \textbf{Read}
               & \textbf{Update}               
               & \textbf{\rot{Properties}}
               & \textbf{Distributions}
			   & \textbf{Output format}
               & \textbf{\rot{Distributed\ }}
               \\ \hline                
\hline
\hline % social networks (Arnau)
\multirow{9}{*}{\rot{\textbf{Social networks}}}
& LDBC SNB  & Y & Y &   generated &  & Y & Facebook-like &  CSV, RDF & Y     \\
\cline{2-10}
& S3G2 & Y & Y  & N &  & Y & Facebook-like  &  CSV, RDF & Y   \\
\cline{2-10}
& SNG  & Y & Y &   N &  & Y & power-law & ? &  ?   \\
\cline{2-10}
& Forest Fire  & N & Y   & N &  & N & power-law &  ? & N   \\
\cline{2-10}
& Darwini  & N & N &   N &  & N & user-defined &  ? & Y   \\
\cline{2-10}
& BTER  & N & N &   N &  & N & user-defined &  ? & Y  \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\hline
\hline   % graph analytics (Sherif)
\multirow{5}{*}{\rot{\textbf{Analytics}}}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & &  &   \\
\hline
\hline   % streaming (Sherif)
\multirow{5}{*}{\rot{\textbf{Streaming}}}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & &  &   \\
\hline
\end{tabular} }
\label{tab:comparisonCharacteristicsB}
\end{sidewaystable}

In Table~\ref{tab:comparisonReferences} we provide an overview of works which use the respective generator for evaluation of the proposed method or comparative study of a selected set methods. \QUE{CSUR has strict page limit 35 pages. I'm afraid that this will extend the list of references extremely.}

\begin{table}
\scriptsize
\centering
\tbl{Exploitation of the generators}{
\begin{tabular}{| l | p{11.5cm} | }
 \hline          \textbf{Generator}
               & \textbf{Cited in}
               \\ \hline
\hline  % general graphs
  & \\  
\hline
  & \\  
\hline
\hline % graph databases
  & \\  
\hline
  & \\  
\hline
\hline % Linked Data
 LUBM & \\  
\hline
 LBBM & \\  
\hline
 UOBM & \\  
\hline
 IIMB & \\  
\hline
 BSBM & \\  
\hline
 SP$^2$Bench & \\  
\hline
 DBPSB & \\  
\hline
 LODIB & \\  
\hline
 SIB & \\  
\hline
 Geographica & \\  
\hline
 WatDiv & \\  
\hline
 RBench & \\  
\hline
 LDBC SPB & \\  
\hline
\hline  % social networks
  & \\  
\hline
  & \\  
\hline
\end{tabular} }
\label{tab:comparisonReferences}
\end{table}

### 2018-05-15 comparison2.tex
First version

\section{Comparison}
\label{sec:comparison}

First, in Fig.~\ref{fig:timeline1} we provide a timeline which depicts when the particular data generator was introduced.

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{timeline1.png}
\caption{Timeline}
\label{fig:timeline1}
\end{figure}

Next, in Tables~\ref{tab:comparison_gen_text} to~\ref{tab:comparison_sn_yesno} we compare the functionalities of the generators. We focus on ....

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}[h]
\footnotesize
\centering
\tbl{Comparison of graph data generators -- general graphs}{
\begin{tabular}{| p{1.9cm} | p{1.2cm} | p{1.5cm} | p{1.3cm} | p{1.5cm} | p{1.5cm} |p{1.5cm} |}
 \hline
               & Graph
               & Parameters
               & Algorithm
               & Output format
               & Operations
               & Problem domain
               \\ \hline \hline
%   &  & & & &   &         \\ \hline
 GraphGen~\cite{GraphGen}   & labelled, undirected, connected & number of graphs, average size of graphs, average density, ... & \NO & list of graphs, their nodes and edges & frequent subgraph mining, query processing  &  \NO       \\ \hline
 HPC Scalable Graph Analysis Benchmark \cite{HPCgraph}  & weighted, directed & number of vertices, number of edges, and maximum weight of an edge & R-MAT & tuples $\langle$ start vertex, end vertex, weight $\rangle$ & classification of large vertex sets, graph extraction with BFS, and graph analysis with betweenness centrality & \NO         \\ \hline
 Graph 500 Benchmark \cite{Graph500} & weighted, undirected & scale, edge factor & R-MAT & tuples $\langle$ start vertex, end vertex, weight $\rangle$ & BFS  & \NO        \\ \hline
\end{tabular} }
\label{tab:comparison_gen_text}
\end{table}

\begin{table}[h]
\footnotesize
\centering
\tbl{Comparison of graph data generators -- Linked Data}{
\begin{tabular}{| p{1.9cm} | p{1.2cm} | p{3cm} | p{1.3cm} | p{3cm} | p{1.5cm} |}
 \hline
               & Graph
               & Parameters
               & Output format
               & Queries
               & Problem domain
               \\ \hline \hline
 LUBM \cite{Guo2005158} & RDF & seed for random number generation, number of universities, starting index of universities & RDF &  14 & storing, querying \\ \hline
 LBBM \cite{Wang2005} & RDF &  number of triples & RDF &  12 & storing, querying \\ \hline
 UOBM \cite{Ma:2006:TCO:2094613.2094629} & RDF & number of universities, probability of generating of various additional links & RDF & 15 & storing, querying  \\ \hline
 IIMB \cite{Ferrara08OM} & RDF & required transformations & RDF & \NO & instance matching \\ \hline
 BSBM \cite{Bizer09theberlin} & RDF & number of products & RDF, relational  & 12 & storing, querying          \\ \hline
 SP$^2$Bench \cite{Schmidt2010} & RDF & triple count / year up to which data is
generated & RDF & 12  &  storing, querying        \\ \hline
 \cite{Duan:2011:AOC:1989323.1989340} & RDF & size, coherence & RDF & \NO    &  storing, querying     \\ \hline
 DBPSB \cite{Morsey2011}     & RDF    & scale factor     & RDF    & 25 derived templates  & storing, querying\\ \hline
 LODIB \cite{DBLP:conf/www/RiveroSBR12} & RDF & number of product instances & RDF & \NO           & translation systems \\ \hline
 SIB \cite{sib} & RDF & number of users & RDF &  3 query mixes    & storing, querying \\ \hline
 Geographica \cite{DBLP:conf/semweb/GarbisKK13} & RDF & size & RDF & 29 + 11 queries + 2 query templates  & geospatial RDF stores    \\ \hline
 WatDiv \cite{Aluc:2014:DST:2717213.2717229}     &  RDF   &  WatDiv schema, scale factor, value distributions, number of query templates, their restrictions  &  RDF   &  user-specified number of query templates and respective query instances & storing, querying \\ \hline
 RBench \cite{Qiao:2015:RAR:2723372.2746479}     &   RDF  &  size + degree scaling factor   & RDF    & 5 types of queries generated for the synthetic data  & storing, querying  \\ \hline
 LDBC SPB \cite{spb}     & RDF   & size     & RDF   & 2 query mixes   & storing, querying \\ \hline
\end{tabular} }
\label{tab:comparison_ld_text}
\end{table}

\begin{table}[h]
\footnotesize
\centering
\tbl{Comparison of graph data generators -- graph databases}{
\begin{tabular}{| p{1.9cm} | p{1.2cm} | p{3cm} | p{1.3cm} | p{3cm} | p{1.5cm} |}
 \hline
               & Graph
               & Parameters
               & Output format
               & Queries
               & Problem domain
               \\ \hline \hline
gMark~\cite{gMark}   & any & graph and query workload configuration & various (e.g., N-triples + SQL, SPARQL, Datalog, openCypher) & synthetically generated  & querying, graph analytics, schema validation         \\ \hline
XGDBench~\cite{Dayarathna:2014:GDB:2676904.2676939}  & any & number of vertices and attributes per vertex, a threshold for random initialization of attributes, an edge affinity threshold, an affinity matrix & DistArray of X10 & 7 workloads & storing, graph operations \\ \hline
\end{tabular} }
\label{tab:comparison_gdb_text}
\end{table}

\begin{table}[h]
\footnotesize
\centering
\tbl{Comparison of graph data generators -- social networks}{
\begin{tabular}{| p{1.9cm} | p{1.2cm} | p{3cm} | p{1.3cm} | p{3cm} | p{1.5cm} |}
 \hline
               & Graph
               & Parameters
               & Output format
               & Queries
               & Problem domain
               \\ \hline \hline
 LFR~\cite{PhysRevE.78.046110}      & social network    & number of nodes, power-law exponents, mixing parameter  & n/a   & \NO    &  community detection    \\ \hline
 \cite{Barrett:2009:GAL:1995456.1995598} & social network & data sets, activity templates & n/a & \NO & analysis        \\ \hline
 \cite{Yao2011}   & linkage graph & burning probability, symmetry probability & n/a & \NO  & degree correlation analysis         \\ \hline
 LinkBench \cite{Armstrong:2013:LDB:2463676.2465296} & social network & number of nodes & MySQL compliant &  10 graph operations  & storing, data access       \\ \hline
 S3G2 \cite{Pham2013} & social network (RDF) & data schema, dictionaries, property value correlations, correlation dimensions  & RDF & \NO & storing, analysis         \\ \hline
 \cite{Sukthankar-SocialInfo2014} & social network & network to be cloned, homophily, link density & n/a & \NO & benchmarking, debugging, simulation   \\ \hline
 LDBC SNB \cite{Erling:2015:LSN:2723372.2742786}     &  social network (RDF)   &  the amount of persons    &  RDF (CSV, Ntriple)   & 3 workloads  &  storing, querying \\ \hline
\end{tabular} }
\label{tab:comparison_sn_text}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}[h]
\footnotesize
\centering
\tbl{Comparison of graph data generators -- general graphs (yes/no features)}{
\begin{tabular}{| l | l | l | l | l | l | l | l | }
 \hline
               & \rot{Domain-specific}
               & \rot{Language-specific}
               & \rot{Use-case driven}
               &  \rot{Considering true Big Data}
               \\ \hline \hline
% &  &  &  &            \\ \hline
 GraphGen \cite{GraphGen}  & \NO & \NO & \NO & \OK           \\ \hline
 HPC Scalable Graph Analysis Benchmark\cite{HPCgraph}  & \NO & \NO & \NO & \OK           \\ \hline
 Graph 500 Benchmark \cite{Graph500}     & \NO    &  \NO    & \NO    & \OK    \\ \hline
\end{tabular} }
\label{tab:comparison_gen_yesno}
\end{table}

\begin{table}[h]
\footnotesize
\centering
\tbl{Comparison of graph data generators -- Linked Data (yes/no features)}{
\begin{tabular}{| l | l | l | l | l | l | l | l | }
 \hline
               & \rot{Domain-specific}
               & \rot{Language-specific}
               & \rot{Use-case driven}
               &  \rot{Considering true Big Data}
               \\ \hline \hline
 LUBM \cite{Guo2005158}     & \OK    &  \NO    &  \OK   & \NO     \\ \hline
 LBBM \cite{Wang2005}     & \NO    &  \NO    &   \NO  &  \NO    \\ \hline
 UOBM \cite{Ma:2006:TCO:2094613.2094629}     &  \OK    &  \NO    &  \OK    & \NO     \\ \hline
 IIMB \cite{Ferrara08OM} & \OK & \NO & \OK &  \NO          \\ \hline
 BSBM \cite{Bizer09theberlin}     &  \OK   &  \NO    & \OK    &  \NO    \\ \hline
 SP$^2$Bench \cite{Schmidt2010}     & \OK    &  \OK    & \NO    &  \NO    \\ \hline
 \cite{Duan:2011:AOC:1989323.1989340}     & \NO & \NO  &  \NO   &  \NO    \\ \hline
 DBPSB \cite{Morsey2011}     & \OK    &  \NO    &  \OK   &  \NO    \\ \hline
 LODIB \cite{DBLP:conf/www/RiveroSBR12} & \OK & \NO & \OK &   \NO         \\ \hline
 SIB \cite{sib} & \OK & \OK & \OK &  \NO          \\ \hline
 Geographica \cite{DBLP:conf/semweb/GarbisKK13} & \OK & \OK & \OK & \NO           \\ \hline
 WatDiv \cite{Aluc:2014:DST:2717213.2717229}     &  \OK   & \OK     &  \NO   &   \NO   \\ \hline
 RBench \cite{Qiao:2015:RAR:2723372.2746479}     &  \NO   & \NO     & \NO    & \NO     \\ \hline
 LDBC SPB \cite{spb}     & \OK    & \NO     & \OK    &  \NO    \\ \hline
\end{tabular} }
\label{tab:comparison_ld_yesno}
\end{table}

\begin{table}[h]
\footnotesize
\centering
\tbl{Comparison of graph data generators -- graph databases (yes/no features)}{
\begin{tabular}{| l | l | l | l | l | l | l | l | }
 \hline
               & \rot{Domain-specific}
               & \rot{Language-specific}
               & \rot{Use-case driven}
               &  \rot{Considering true Big Data}
               \\ \hline \hline
Graph 500 Benchmark~\cite{Graph500}     & \NO    &  \NO    & \NO    & \NO     \\ \hline
XGDBench~\cite{Dayarathna:2014:GDB:2676904.2676939}      & \NO    & \NO     &  \NO   & \OK     \\ \hline
%      &     &      &     &      \\ \hline
\end{tabular} }
\label{tab:comparison_gdb_yesno}
\end{table}

\begin{table}[h]
\footnotesize
\centering
\tbl{Comparison of graph data generators -- social networks (yes/no features)}{
\begin{tabular}{| l | l | l | l | l | l | l | l | }
 \hline
               & \rot{Domain-specific}
               & \rot{Language-specific}
               & \rot{Use-case driven}
               & \rot{Considering true Big Data}
               & \rot{Statistical/Agent-based}
               \\ \hline \hline
LFR~\cite{PhysRevE.78.046110}      & \NO    &  \NO    & \NO    & \NO  & S   \\ \hline
 \cite{Barrett:2009:GAL:1995456.1995598} & \NO    &  \NO    & \NO    & \NO  & A   \\ \hline
 \cite{Yao2011}   & \NO  & \NO & \NO  & \NO  & S        \\ \hline
 LinkBench \cite{Armstrong:2013:LDB:2463676.2465296} & \OK & \NO & \OK & \OK & S          \\ \hline
  S3G2 \cite{Pham2013} & \NO & \NO & \NO & \OK & S       \\ \hline
%  \cite{Bernstein:2013:SAS:2499604.2499609} & \NO & \NO & \NO & \OK & A       \\ \hline
 \cite{Sukthankar-SocialInfo2014} & \NO    &  \NO    & \NO    & \NO & S    \\ \hline
 LDBC-SNB \cite{Erling:2015:LSN:2723372.2742786}     &   \OK    & \NO     & \OK    & \OK  & S  \\ \hline
%      &     &      &     &      \\ \hline

\end{tabular} }
\label{tab:comparison_sn_yesno}
\end{table}

As we can see ...

### 2018-05-15 conclusion.tex
First version

\section{Conclusion}
\label{sec:conclusion}

...

### 2018-05-15 data_sets.tex
First version

\subsection{Graph Data Sets}

Before we focus on graph data generators, we briefly overview graph data sets devoted to benchmarking of various types of graph algorithms. \cite{Knuth:1993:SGP:164984} denotes such a  database of graphs (or graph library or graph archive) and related computer programs as a \emph{graphbase}. In general, there exist several types of testing graph data sets~\cite{Bachmaier2012}:

\begin{itemize}
  \item A real-world data set which represents a graph, such as the Internet Movie Database (IMDb)\footnote{\url{http://www.imdb.com/}} or various data sets available in the Stanford Large Network Dataset Collection~\cite{snapnets},
  \item A general graphbase, such as the Open Graph Archive~\cite{Bachmaier2012}, the Stanford GraphBase~\cite{Knuth:1993:SGP:164984}, or the GraphArchive~\cite{GraphArchive},
  \item A dataset dedicated to specific experimental goals, such as graph partitioning and graph clustering~\cite{10dimacs}, shortest paths~\cite{9dimacs}, or graph coloring~\cite{coloring}, and
  \item A dataset devoted to matrices, such as the SuiteSparse Matrix Collection~\cite{SuiteSparse} or  the Matrix Market~\cite{MatrixMarket}.
\end{itemize}

...

### 2018-05-15 generators.tex
First version

\section{Graph Data Generators}
\label{sec:generators}

...

\input{data_sets}

\input{generators_general}

\input{generators_LinkedData}

\input{generators_GraphDatabases}

\input{generators_SocialNetworks}

\input{generators_analytics}

\input{generators_streaming}

% \subsection{Specific Types of Graphs}
% ...

% % Note: not in timeline or tables
% \paragraph{Heterogeneous Graphs} The Heterogeneous Graph Data Benchmark (GDB-H)~\cite{Gupta:2012:GLH:2741795.2741808} aims at \emph{heterogenous graph} data model, a mixed model graph structure that combines several existing generation techniques into a single benchmark. The idea is demonstrated using a drug discovery scenario whose schema involves 11 entity categories (e.g., genes, proteins, diseases, ...) and 3000 binary relationships (e.g., instanceOf, subclassOf, ...). The data is structured as a combination of $N$ overlapping named graphs $G_1, ... G_N$, where the overlap is accomplished by node sharing. A subset of the named graphs $G_1, ... G_k$ are hierarchical, i.e., they are structured as trees or DAGs. The remaining $N-k$ graphs are multigraphs which differ in terms of their network connectivity properties (some component graphs obey the power-law more strictly, some graphs have a larger skew in the distribution of edge labels, some graphs  are denser, some graphs may optionally have additional constraints regarding subgraph patterns). The user can specify the number of component graphs (8 to 100), the number of nodes (100,000 to 100,000,000), the number of node types (3 to 11), and the number of distinct edge labels (30 - 3000), and optionally also type ratios (the fraction of the component graphs having hierarchical, power-law, community or motif structure), node distribution (i.e. the relative size of graph components), edge density, overlapping etc.

% For the purpose of generating the heterogeneous graphs having heterogeneous, i.e. hierarchical, power-law, community-structured or purely random, structure the authors combine several existing approaches corresponding to the particular structural type~\cite{PhysRevLett.102.128701,doi:10.1080/10586458.2001.10504428}.

% \subsection{Object-Oriented and XML Databases (?)}

% see~\cite{Dominguez-Sal:2010:DDG:1946050.1946053}

### 2018-05-15 generators_GraphDatabases.tex
First version

\subsection{Graph Databases}
\label{sec:generators_GraphDatabases}

Currently there exists a number  of papers which compare the efficiency of graph databases with regards to distinct use cases, such as  the community detection problem~\cite{Beis2015}, social tagging systems~\cite{Giatsoglou2011}, graph traversal~\cite{Ciglan:2012:BTO:2374486.2375242}, graph pattern matching~\cite{Pobiedina2014}, data provenance~\cite{Vicknair:2010:CGD:1900008.1900067}, or even several distinct use cases~\cite{Grossniklaus2013Towar-24253}. However, the number of graph data generators and benchmarks designed particularly for graph databases is relatively small. Either a general graph generator is used for benchmarking graph databases, such as, e.g., the HPC Scalable Graph Analysis Benchmark~\cite{Dominguez-Sal:2010:SGD:1927585.1927590}. Or the graph DBMS benchmarking tools are designed in a more general scope. Hence it is questionable whether a benchmark specific for graph databases if necessary.

Paper~\cite{Dominguez-Sal:2010:DDG:1946050.1946053} discusses this question and related topics. On the basis of a review of applications of graph databases (namely social network analysis, proteomics or genetic interactions, recommendation systems, and travel planning and routing), the authors analyze and discuss the characteristics of the graphs that appear in such applications and how they could influence benchmarking, different types of operations used in these applications and the characteristics of the evaluation setup of the benchmark.

In the following paragraphs we overview graph data generators and benchmarks primarily targeting graph DBMSs.

\paragraph{XGDBench} XGDBench~\cite{Dayarathna:2014:GDB:2676904.2676939} is an extensible graph database benchmarking platform for cloud computing systems. Its intent is to automate
the process of graph database benchmarking in the cloud focusing on a graph database application for social networking services.

It extends the Yahoo! Cloud Multiplicative Attribute (MAG) Graph Serving Benchmark (YCSB)~\cite{Cooper:2010:BCS:1807128.1807152} and is composed of a workload generator client and a package of standard workloads that cover interesting parts of the performance space. 
The workload generator of YCSB supports definition of new workload types. XGDBench involves basic operations read / insert / update / delete an attribute, loading of the list of neighbors and BFS traversal. Using them 7 workloads are created, such as update heavy, read mostly, short range scan, traverse heavy etc.

The data model of XGDBench is a simplified version of the Multiplicative Attribute Graph (MAG)~\cite{Kim2010} model, a synthetic graph model for attribute graphs which models the interactions between the network structure and the node attributes. 
The generated graphs are thus in MAG format, with power-law degree distribution thus closely simulating real-world social networks.
The simplified MAG algorithm accepts the number of vertices of the generated graph, the number of attributes per vertex, a threshold value for random initialization of attributes, an edge affinity threshold value that determines whether there is an edge between two vertices, and an affinity matrix. It has been proven that MAG generates graphs with both analytically tractable and statistically interesting properties. A multi-threaded version of the graph generator that generates large graphs on multi-core systems faster was implemented.

\paragraph{GraphGen}  GraphAware GraphGen~\cite{GraphGen} is a graph generation engine based on Cypher, Neo4j's\footnote{\url{https://neo4j.com/}} query language.  It creates nodes and relationships based on a schema definition expressed in Cypher, and it can also generate property values on both 
nodes and edges. As such, GraphGen is a precursor of property graphs generators. The resulting graph can be exported to several formats (namely GraphJson and CypherQueries) or loaded directly to a DBMS. However, it is probably not maintained anymore.

\paragraph{gMark}  gMark~\cite{gMark} is a schema-driven, domain- and query language-independent graph instance and query workload generator.  It leverages a schema definition,
called a \emph{graph configuration}, which includes the enumeration of predicates (i.e., edge labels) and node types (i.e., node labels) occurring in the data, along with their properties in generated instances (occurrence constraints, degree distribution, etc.). \emph{Query workload configuration}  describes parameters of the queries to be generated (e.g., number of queries, arity, shape, selectivity etc.). The authors prove that given a graph configuration $G$, deciding whether there exists a graph satisfying $G$ is NP-complete. And, that given a query workload configuration $Q$, deciding
whether there exists a query workload satisfying $Q$ is NP-complete. Hence, gMark follows a heuristic strategy in the generation -- it attempts to achieve the exact values of the parameters and it may decide to relax some of them in order to obtain linear running time. gMark generates graphs under the form of N-triples and query workloads in four concrete syntaxes, including Cypher, SPARQL, SQL and LogicQL.

### 2018-05-15 generators_LinkedData.tex
First version

\subsection{Semantic Web}
\label{sec:generators_LinkedData}
With the dawn of the concept of Linked Data there have naturally emerged also respective benchmarks involving both real-world data sets and synthetic data sets with real-world characteristics. The used data sets correspond to RDF representation of relational-like data~\cite{Guo2005158,Bizer09theberlin}, social network-like data~\cite{Schmidt2010}, or specific and significantly more complex data structures such as biological data~\cite{Wu2014}. In the following overview we focus on benchmarking systems involving a kind of data generator or data modifier. Other types of systems or particular results can be found, e.g., at~\cite{RdfStoreBenchmarking}.

Considering the Big Data world, the Linked Data in general definitely belong to this group since we assume that the Linked (Open) Data Sets form a common Linked Open Data cloud\footnote{\url{http://lod-cloud.net/}}. On the other hand, the particular data sets can be relatively small.

\paragraph{LUBM} The use-case driven Lehigh University Benchmark (LUBM)~\cite{Guo2005158} considers the university domain. The ontology defines 43 classes and 32 properties, including 25 object properties and 7 datatype properties. The LUBM benchmark also provides 14 test queries. The authors focus on \emph{extensional} queries, i.e., queries about the instance data over ontologies, as an opposite to \emph{intentional} queries (i.e., queries about classes and properties). The Univ-Bench Artificial  (UBA) data generator features random and repeatable data generation (exploting classical linear congruential generator, LCG, of numbers). In particular, data generated by the tool are exactly repeatable with respect to universities (assigning them zero-based indexes, i.e., the first university is named University0 and so on).  The generator allows a user to specify the seed for random number generation, the number of universities, and the starting index of the universities.

An extension of LUBM, the Lehigh BibTeX Benchmark (LBBM)~\cite{Wang2005}, enables generating synthetic data for different ontologies. The generation is divided into two phases: (1) the property-discovering phase, and (2) the data generation phase. The authors present a probabilistic model that, given representative data of some domain, can capture the properties of the data and generate synthetic data that has similar properties. A Monte Carlo algorithm is used to generate synthetic data. The approach is demonstrated on the Lehigh University BibTeX ontology which consists of 28 classes and 80 properties. 12 test queries were designed for  the benchmark data.

Another extension of LUBM, the University Ontology Benchmark (UOBM)~\cite{Ma:2006:TCO:2094613.2094629}, focuses on two aspects: (1) usage of all constructs of OWL Lite and OWL DL~\cite{owl} and (2) lack of necessary links between the generated data which thus form isolated graphs. In the former case the original ontology is replaced by the two types of extended versions from which the user can choose. In the latter case cross-university and cross-department links are added to create a more complex graph.

\paragraph{IIMB} Contrary to the previous work, paper~\cite{Ferrara08OM} proposes the ISLab Instance Matching Benchmark (IIMB) for the problem of instance matching defined as follows: Given two instances $i_1$ and $i_2$, belonging to the same ontology or to different ontologies, instance matching is defined as a function $Im(i_1, i_2) \rightarrow \{0, 1\}$,  where $1$ denotes the fact that $i_1$ and $i_2$ are referred to the same real-world object and $0$ denotes the fact that $i_1$ and $i_2$ are referred to different objects. It targets the domain of movie data which contains 15 named classes, 5 object properties and 13 datatype properties. The data are extracted from IMDb\footnote{\url{http://www.imdb.com/}}.

The data generator corresponds to a data modifier which simulates differences between the data. In particular it involves data value differences (such as typographical errors or usage of different standard formats, e.g., for names), structural heterogeneity (represented by different levels of depth for properties representation, different aggregation criteria for properties representation, or missing values specification) and logical heterogeneity (such as instantiation on different subclasses of the same superclass or instantiation on disjoint classes).

\paragraph{BSBM} The Berlin SPARQL Benchmark (BSBM)~\cite{Bizer09theberlin}, also use-case driven, involves an e-commerce domain, where types Product, Offer and Vendor are used to model the relationships between products and the vendors offering them, while types Person and Review are used to model the relationship between users and product reviews these users write.
The benchmark also comes with 12 queries and 2 query mixes (sequences of the 12 queries) emulating the search and navigation pattern of a consumer looking for a product. The data generator supports creation of arbitrarily large datasets using the number of products $n$ as scale factor which further influences also other characteristics of the data, such as, e.g., the depth of type hierarchy of products (defined as $d = round(log_{10}(n))/2 + 1$), branching factor ($bfr = 2 \times round(log_{10}(n))$), the number of product features (having $lowerBound = 35 \times i / (d \times (d+1)/2 ? 1)$ and $upperBound = 75 \times i / (d \times (d+1)/2 ? 1)$) etc.

BSBM can output two representations -- an RDF representation and a purely relational representation. Thus BSBM also defines an SQL~\cite{sql} representation of the queries. This allows comparison of SPARQL~\cite{sparql} results with the performance of traditional RDBMSs.

\paragraph{SP$^2$Bench} The SP$^2$Bench is a language-specific benchmark~\cite{Schmidt2010} which uses the DBLP~\cite{dblp} as a domain for the dataset. %, so the types involve Person, Inproceedings, Article etc.
The generated documents mirror key characteristics and distributions found in the original DBLP database. The data mimics natural correlations between entities, such as power law distributions (found in the citation system or the distribution of publications among authors) and limited growth curves (e.g., the increasing number of venues and publications over time). All random functions of the generator base on a fixed seed which makes data generation deterministic. SP$^2$Bench is accompanied by 12 queries covering different operator constellations, RDF access paths, typical RDF constructs etc.

%\paragraph{JustBench} ~\cite{Bail:2010:JFO:1940281.1940285} ...

\paragraph{Data Coherence}  A comparison of 4 RDF benchmarks (namely TPC-H~\cite{TPC-H} data expressed in RDF, LUBM, BSBM, and SP$^2$Bench) and 6 real-wold data sets (such as, e.g.,  DBpedia~\cite{Bizer:2009:DCP:1640541.1640848}, the Barton Libraries Dataset~\cite{barton-benchmark}
WordNet~\cite{Miller:1995:WLD:219717.219748} etc.) is provided in paper~\cite{Duan:2011:AOC:1989323.1989340}. The authors focus mainly on \emph{structuredness} (\emph{coherence}) of each benchmark dataset claiming that a primitive metric (e.g., the number of triples or the average in/outdegree) quantifies only some specific aspect of each dataset. The level of structuredness of a dataset $D$ with respect to a type $T$ is determined by how well the instance data in $D$ conforms to type $T$. The type system is extracted from the data set looking for triples whose property is \texttt{http://www.w3.org/1999/02/22-rdf-syntax-ns\#type} and extracting type $T$ from their object. Properties of $T$ are determined as the union of all the properties that the instances of type $T$ have. The structuredness is then expressed as a weighted sum of share of set properties of each type, whereas higher weights are assigned to types with more instances.

The authors show that structuredness of the chosen benchmarks is fixed, whereas real-world RDF datasets lie in currently untested parts of the spectrum. As a consequence, they introduce a new benchmark that accepts as input any dataset along with a desired level of structuredness and size (smaller than the size of the original data), and uses the input dataset as a seed to produce a subset of the original data with the indicated size and structuredness. In addition they show that structuredness and size mutually influence each other.

\paragraph{DBPSB} DBpedia SPARQL Benchmark (DBPSB)~\cite{Morsey2011,Morsey:2012:UBR:2900929.2901031} proposed at the University of Leipzig is based on queries that were issued by humans and applications
against existing RDF data. In addition, the authors argue that benchmarks like LUBM, BSBM, or SP$^2$Bench resemble relational database benchmarks involving relational data structures with few and homogeneously structured classes, whereas RDF knowledge bases are increasingly heterogeneous (e.g., DBpedia version 3.6, for example, contains 289,016 classes of which 275 classes belong
to the DBpedia ontology) and various datatypes and object references of different types are
used in property values. Hence, they propose a generic SPARQL benchmark creation methodology based on: a flexible data generation mimicking an input data source, query-log mining, clustering, and SPARQL feature analysis.

The proposed dataset creation process starts with an input dataset. Datasets of multiple size of the original data are created by duplicating all triples and changing their namespaces.  For generating smaller datasets, an appropriate fraction of all triples is selected randomly or by sampling across classes in the dataset. The goal of the query analysis and clustering is to detect prototypical queries on the basis of their frequent usage and similarity. The methodology is applied on the DBpedia SPARQL endpoint and a set of 25 SPARQL query templates is derived, which cover most commonly used SPARQL features and are used to generate the actual benchmark queries by parametrization.

\paragraph{LODIB} The Linked Open Data Integration Benchmark (LODIB)~\cite{DBLP:conf/www/RiveroSBR12} aims to reflect the real-world heterogeneities that exist on the Web of Data in order to enable testing of Linked Data translation systems. It provides a catalogue of 15 data translation patterns (e.g., rename class, remove language tag etc.), each of which is a common data translation problem in the context of Linked Data. The benchmark provides a data generator that produces three different synthetic data sets that need to be translated
by the system under test into a single target vocabulary. They  reflect the pattern distribution in analyzed 84 data translation examples from the LOD Cloud. The data sets reflect the same e-commerce scenario used for BSBM.

\paragraph{SIB} The authors of the Social Network Intelligence BenchMark (SIB)~\cite{sib} claim that current benchmarks are limited in representing the real RDF datasets and are mostly relational-like. Hence, they propose a benchmark for challenging query processing over real graphs. It simulates an RDF backend of a social network site, in which users and their interactions form an social graph of social activities such as writing posts, posting comments, creating/managing groups, etc. The distribution of generated data on each relation conforms to the data distribution analyzed over real-world social networks. Association rules are included in order to convey the real-world data correlation into synthetic data. The  generated data is linked with the RDF datasets from DBpedia. The benchmark specification contains 3 query mixes -- interactive, update, and analysis -- expressed in SPARQL 1.1 Working Draft.

\paragraph{Geographica} The authors of benchmark Geographica~\cite{DBLP:conf/semweb/GarbisKK13} target the area of geospatial data and respective SPARQL extensions GeoSPARQL and stSPARQL. The benchmark involves (1) a real-world workload based on publicly available linked data sets covering a range of geometry types (e.g., points, lines, polygons) and (2) a synthetic workload. In the former case they further distinguish (1) a micro benchmark that tests primitive spatial functions (involving 29 queries) and (2) macro benchmark that tests the performance of RDF stores in typical application scenarios like reverse geocoding or map search and browsing (consisting of 11 queries). In the latter case of a synthetic workload the generator produces synthetic datasets of various sizes that corresponds to an ontology based on OpenStreetMap (i.e., states in a country, land ownership, roads and  points of interest) and instantiates query templates. The spatial extent of the land ownership dataset constitutes a uniform grid of $n \times n$ hexagons, whereas the size of each dataset is given relatively to $n$. The synthetic workload generator produces SPARQL queries corresponding to spatial selection and spatial joins by instantiating 2 query templates.

\paragraph{WatDiv} The Waterloo SPARQL Diversity Test Suite (WatDiv)~\cite{Aluc:2014:DST:2717213.2717229} developed at the University of Waterloo provides stress testing tools to address the observation that existing SPARQL benchmarks are not suitable for testing systems for diverse queries and varied workloads. The authors introduce two classes of query features -- structural and data-driven -- and perform an in-depth analysis on existing SPARQL benchmarks (LUBM, BSBM, SP$^2$Bench, and DBPSB) using the two classes of query features. The structural features involve triple pattern count, join vertex count, join vertex degree, and join vertex count. The data-driven features involve result cardinality and several types of selectivity. The analysis of the four benchmarks reveals that they are not sufficiently diverse to test the strengths and weaknesses of different physical design choices employed by RDF systems.

The proposed solution, WatDiv, involves (1) a data generator which generates scalable datasets according to WatDiv schema, (2) a query template generator which traverses the WatDiv schema and generates a diverse set of query templates, (3) a query generator which instantiates the templates with actual RDF terms from the dataset, and (4) a feature extractor which computes the structural and data-driven features of the generated data and workload. For the study in the paper the authors generated 12,500 test queries from 125 query templates.

\paragraph{RBench} RBench~\cite{Qiao:2015:RAR:2723372.2746479} is an application-specific benchmark which takes any RDF dataset as a template, and generates a set of synthetic datasets with similar characteristic, the required size scaling factor $s$ and the (node) degree scaling factor $d$. A generated benchmark dataset is considered similar to the given dataset if their values for the dataset evaluation metrics and query evaluation times for different techniques are similar. Three evaluation metrics -- dataset coherence (i.e., a measure how uniformly predicates are distributed among the same type/class), relationship specialty (i.e., the number of occurrences of the same predicate associated with each resource), and literal diversity -- are utilized for this purpose. A query generation process is proposed to generate 5 types of queries (node queries, edge queries, star queries, path queries, and subgraph queries) for any generated data.

The benchmark project FEASIBLE~\cite{Saleem2015} is also an application-specific benchmark; however, contrary to RBench, it is able to generate benchmarks from a set of queries (in particular from query logs) by selecting prototypical queries of a user-defined
size from the input set of queries.

\paragraph{LDBC}  The Linked Data Benchmark Council\footnote{\url{http://ldbcouncil.org/industry/organization/origins}} (LDBC)~\cite{Angles:2014:LDB:2627692.2627697} is a result of a (closed) EU project that brought together a community of academic researchers and industry, whose main objective was the development of open source, yet industrial grade, benchmarks for graph and RDF databases. The following three benchmarks were developed and are currently maintained.

The Semantic Publishing Benchmark (SPB)~\cite{spb} is inspired by the Media/Publishing industry (namely BBC\footnote{\url{http://www.bbc.com/}}). The application scenario considers a media or a publishing organization that deals with large volume of streaming content, namely news, articles or  ``media assets''. This content is enriched with metadata that describes it and links it to reference knowledge -- taxonomies and databases that include relevant concepts, entities and factual information. The SPB data generator produces scalable in size synthetic large data. Synthetic data consists of a large number of annotations of media assets that refer entities found in reference datasets. The data generator models three types of relations in produced synthetic data: (1) clustering of data, (2) correlations of entities, and (3) random tagging of entities. Two workloads are provided: (1) basic, involving an interactive query-mix, querying the relations between entities in reference data, and (2) advanced,  consisting of interactive and analytical query-mixes.

The Social Network Benchmark (SNB) models a social network akin to Facebook (see Section~\ref{sec:generators_socialnetworks}).

Graphalytics~\cite{Iosup:2016:LGB:3007263.3007270} is an industrial-grade benchmark for graph analysis platforms. It involves 6 real-world datasets and 2 synthetic datasets generated by LDBC SNB (see Section~\ref{}) and Graph500 (see Section~\ref{}). The benchmark involves 6 algorithms: breadth-first search, PageRank, weakly connected components, community detection using label propagation, local clustering coefficient, and single-source shortest paths.

LinkGen~\cite{10.1007/978-3-319-46547-0_12}

### 2018-05-15 generators_SocialNetworks.tex
First version

\subsection{Social Networks}
\label{sec:generators_socialnetworks}

On-line social networks, like Facebook, Twitter, or LinkedIn, have become a phenomenon used by billions of people every day and thus providing extremely useful information for various domains. However, an analysis of such type of graph has to cope with two problems: (1) availability of the data and (2) privacy of the data. Hence, data generators which provide realistic synthetic social network graphs are in great demand.

Analyses of social networks identify their various specific features~\cite{Chakrabarti:2006:GML:1132952.1132954}. For example, the social graph has high \emph{clustering coefficient}, i.e. the degree of transitivity of a graph. Or, its diameter, i.e. the minimum number of hops in which some fraction (e.g., 90\%) of all connected pairs of nodes can reach each other, is usually low due to weak ties joining faraway cliques. Another important aspect of social networks is the community effect. A detailed study of structure of communities in 70 real-world networks is provided, e.g., in paper~\cite{Leskovec:2008:SPC:1367497.1367591}. Authors of paper~\cite{Prat-Perez:2014:CSS:2621934.2621942} analyze the structure of communities (clustering coefficient, triangle participation ratio, bridges, diameter, conductance and size) in both real graphs and output by existing graph generators LFR~\cite{PhysRevE.78.046110} and the LDBC-SNB~\cite{Erling:2015:LSN:2723372.2742786}. %They discover that communities found among different graphs follow quite similar distributions and that communities in a single graph have diverse nature, and are difficult to fit with a single model.

Network generators can be categorized into statistical and agent-based. \emph{Statistical approaches}~\cite{PhysRevE.78.046110,Yao2011,Armstrong:2013:LDB:2463676.2465296,Pham2013,Sukthankar-SocialInfo2014,Erling:2015:LSN:2723372.2742786,Nettleton2016} focus on reproducing aspects of the network statistics. In \emph{agent-based approaches}~\cite{Barrett:2009:GAL:1995456.1995598,Bernstein:2013:SAS:2499604.2499609}  the networks are constructed by directly simulating the agents' social choices.

\paragraph{LFR} Lancichinetti, Fortnato and Radicchi (hence LFR)~\cite{PhysRevE.78.046110} develop a class of benchmark graphs whose nodes participate in internal community structures. The benchmark models directed and weighted real-world networks (e.g., social networks) containing overlapping communities of different sizes. The algorithm assumes that both the degree and the community size distributions are power laws. Each node shares a fraction $(1 - \mu)$ of its links with the other nodes of its community and a fraction $\mu$ with the other nodes of the network, where $\mu$ is called \emph{mixing parameter}. The sizes of the communities are taken from a power law distribution such that the sum of all sizes equals the number of nodes of the graph. The generation process starts with an empty graph and incrementally fills in the adjacency matrix by obeying the described constraints.

\paragraph{Realistic Social Network} Paper~\cite{Barrett:2009:GAL:1995456.1995598} focuses on construction of realistic social networks using a combination of public and private data sets and large-scale agent based techniques. The process works as follows: Step 1 creates a synthetic population by integrating databases from commercial and public sources. In Step 2, a set of activity templates are determined. Each synthetic individual is assigned a 24-hour activity sequence including geo-locations for each activity.

To demonstrate the approach, the authors develop a synthetic population for the United States that models every individual in the population. The synthetic population is a set of geographically located people and households. Household structure and demographics are derived from U.S. Census data. The activity templates are  based on several thousand responses to an activity or time-use survey. Demographic information for each person and location, a minute-by-minute schedule of each person's activities, and the locations where these activities take place is generated by a combination of simulation and data fusion techniques. This information is captured by a dynamic social contact network.

Similar agent-based strategies can be found, e.g., in papers~\cite{Bernstein:2013:SAS:2499604.2499609}.

\paragraph{Linkage vs. Activity Graphs} Paper~\cite{Yao2011} distinguishes two types of social network graphs -- the \emph{linkage graph}, where nodes stand for the people in the social network and edges are their friendship links, and the \emph{activity graph}, where nodes also stand for the people but edges stand for their interactions. On the basis of analysis of Flickr\footnote{\url{https://www.flickr.com/}} social links and Epinions\footnote{\url{http://www.epinions.com/}} network of user interactions, the authors discover that they both exhibit power-law degree distribution, high clustering coefficient (community structure), and small diameter; also regarding the dynamic properties they both follow densification law and relatively stable clustering coefficient over time. However, the authors do not observe diameter shrinking in Epinions? activity graph and there is a difference in degree correlation (how frequently nodes with similar degrees connect to each other). Namely linkage graphs have positive degree correlation whereas activity graphs show neutral degree correlation.

With regards to the findings, the proposed generator focusses on linkage graphs with positive degree correlation. For this purpose it extends the ``forest fire'' spreading process algorithm~\cite{Leskovec:2005:GOT:1081870.1081893} with link symmetry. It has two parameters -- the \emph{burning probability} $P_b$ which is in charge of the burning process, and the \emph{symmetry probability} $P_s$ which indicates backward linking from old nodes to new ones. $P_b$ controls a BFS-based forward burning process. The fire burns increasingly fiercely with $P_b$ approaching 1. Meanwhile, $P_s$ adds fuel to the fire as it brings more links. It gives chances for big nodes
to connect back to big nodes.

\paragraph{LinkBench} The LinkBench benchmark~\cite{Armstrong:2013:LDB:2463676.2465296} aims to predict the performance of a database when used for persistent storage of Facebook?s production data. The benchmark considers true Big Data and related problems with sharding, replication etc. The social graph at Facebook comprises objects (nodes with IDs, version, timestamp and data) and associations (directed edges, pairs of node IDs, with visibility, timestamp and data). The size of the target graph is the number of nodes. Graph edges are generated concurrently with graph nodes during bulk loading. The node ID space is divided into chunks based on the ID of the source node which  are processed in parallel. The edges of the graph are generated in accordance with the results of analysis of real-world Facebook data (such as outdegree distribution). A workload corresponding to 10 graph operations (such as insert object, count the number of associations etc.) and their respective characteristics over the real-world data is generated for the synthetic data.

\paragraph{S3G2} The Scalable Structure-correlated Social Graph Generator (S3G2)~\cite{Pham2013} is a general framework which  generates a directed labeled graph, where the nodes are objects with property values, and their structure is determined by the class a node belongs to. S3G2 does not aim at generating near real-world data, but at generating synthetic graphs which a correlated structure. It causes that the probability to choose a certain property value (from a pre-defined dictionary), or the probability to connect two nodes with an edge are influenced by existing data values. For example, it is possible to have a correlated degree distribution, from which the degree of each node is generated, correlated with properties of node. Hence the generator can ensure that, e.g., people with many friends in a social network will typically post more pictures than people with few friends, i.e., the amount of friend nodes influences the amount of posted comment and picture nodes.

The data generation process starts with generating a number of nodes with property values generated according to specified property value correlations and then adding respective edges according to specified correlation dimensions. It has multiple phases, each focusing on one correlation dimension. Each pass along one correlation dimension is a Map phase in which data is generated, followed by a Reduce phase that sorts the data along the correlation dimension in the next pass. A heuristic observation that ``the probability that two nodes are connected is typically skewed with respect to some similarity between the nodes'' enables to focus only on sliding window of most probable candidates.

The core idea of the framework is demonstrated using an example of a social network (consisting of persons and social activities).  The dictionaries for property values are inspired by DBpedia and provided with 20 property value correlations. The edges are generated according to 3 correlation dimensions.

\paragraph{Cloning of Social Networks} Paper~\cite{Sukthankar-SocialInfo2014} introduces a synthetic network generator designed for cloning social network statistics of an existing dataset. The network starts with a small number of nodes, and new nodes are added until the network reaches the required number. It has two basic parameters: homophily and link density. A high \emph{homophily} value indicates that links are more likely to be formed between nodes with the same label; these labels can be viewed as being equivalent to community membership.

Attribute Synthetic Generator (ASG) is a network generator for reproducing the node feature distribution of standard networks and rewiring the network to preferentially connect nodes that exhibit a high feature similarity. The network is initialized with a group of three nodes, and new nodes and links are added to the network based on link density, homophily, and feature similarity. As new nodes are created, their labels are assigned based on the prior label distribution. After the network has reached the same number of nodes as the original social media dataset, each node initially receives a random attribute assignment. Then a stochastic optimization
process is used to move the initial assignments closer to the target distribution extracted from social media dataset using the Particle Swarm Optimization algorithm. The tuned attributes are then used to add additional links to the network based on the feature similarity parameter -- a source node is selected randomly and connected to the most similar node.

Multi-Link Generator (MLG) further  uses link co-occurrence statistics from the original dataset to create a multiplex network. MLG uses the same network growth process as ASG.. Based on the link density parameter, either a new node is generated with a label based on the label distribution of the target dataset or a new link is created between two existing nodes.

\paragraph{LDBC SNB} The Social Network Benchmark (SNB)~\cite{Erling:2015:LSN:2723372.2742786} provided by LDBC consists of three distinct benchmarks on a common dataset corresponding to three different workloads. SNB models a social network akin to Facebook. The dataset consists of persons and a friendship network that connects them; whereas the majority of the data is in the messages that these persons post in discussion trees on their forums. The three query workloads involve: (1) SNB-Interactive (i.e., complex read-only queries, that touch a significant amount of data), (2) SNB-BI (which accesses a large percentage of all entities in the dataset and groups these in various dimensions), and (3) SNB-Algorithms (i.e., graph analysis algorithms, including PageRank, Community Detection, Clustering and Breadth First Search). The graph generator realizes power laws, uses skewed value distributions, and introduces plausible correlations between property values and graph structures. It is implemented on top of Hadoop to provide scalability.

The generated data have become a part if several graph benchmarks, such as GraphBIG~\cite{Nai:2015:GUG:2807591.2807626}.

\paragraph{Towards More Realistic Data} The authors of paper~\cite{Nettleton2016} claim that the main body of existing work lies in topology generation which approximate the characteristics of a real social network (such as a small graph diameter, small average path length, skew degree distribution, and community structures), however without data. Hence, they implement a general stochastic modeling system which allows the users to populate a graph topology with data. The approach has three steps: (1) topology generation (using R-MAT) plus community identification using the Louvain method~\cite{1742-5468-2008-10-P10008} or usage of a real-world topology from SNAP\footnote{\url{https://snap.stanford.edu/data/}}, (2) data definition (following distribution profiles, attribute value definitions, using a parameterizable set of data propagation rules and affinities), and (3) data population.

### 2018-05-15 generators_analytics.tex
First version

\subsection{Graph Analytics}
\label{sec:generators_analytics}

...

### 2018-05-15 generators_community_detection.tex
First version

\subsection{Graphs Generators for Benchmarking Community Detection Algorithms}
\label{sec:generators_community_detection}

Community detection is one of the many graph analytics algorithms typically used on domains such as social networks or bioinformatics. Communities are groups of vertices that are highly connected among them, while being scarcely connected to the rest of the graph. Such communities emerge from the fact that real graphs are not random, but follow realworld dynamics that make similar entities to have a larger probability to be connected. As a consequence, detected communities are used used to reval vertices with similar characteristics, for instance to discover functionally equivalent proteins in protein-protein interaction networks, or persons with similar interests in social networks.

Such applications have made community detection a hot topic during the last fifteen years with tens of developed algorithms and detection strategies. In order to compare the quality of the different proposed techniques, one needs graphs with reference communities, that is,. communities which known beforehand. Since it is very difficult to have large real graphs with reference communities --mainly because these would require a manual labeling--, graphs for benchmarking community detection algorithms typically generated synthetically.

The first attempts to compare community detection algorithms using synthetic graphs proposed the use of random graphs composed by several Erd\"{o}s-R\'{e}nyi~\cite{Erdos:1960} subgraphs, connected more internally than externally~\cite{danon2005comparing}. Each of these subgraphs has the same size and the same internal/external density of edges. However, such graphs miss the realism observed in real graphs, where communities are of different sizes and densities.

Thus, Lancichinetti, Fortunato and Radicchi (hence LFR)~\cite{PhysRevE.78.046110} propose a class of benchmark graphs for community detection where communities are of different sizes and densities. The generator generates communities of different sizes following a power-law distribution whose parameters can be configured. The degree of the nodes is also sampled from a power-law distribution. Additionally, the generator introduces the concept of the ``mixing factor'', which specifies the fraction of its links connecting nodes belonging to different communities. Such parameter allows to tune the degree of modularity of the generated graph, thus testing the robustness of hte algorithms under different conditions. The generation process starts with an empty graph and incrementally fills in the adjacency matrix by obeying the described constraints.

Lancichinetti, Fortunato and Radicchi \cite{PhysRevE.80.016118} extended LFR to support the notion of directed graphs and overlapping communities. Overlapping communities extend the notion of communities by allowing the sharing of vertices, thus a vertex can belong to more than one community. This extended generator allows controlling the same parameters of the previous version, but also the amount of overlap of the generated communities.

Besides synthetic graph generators, Yang and Leskovec~\cite{yang2015defining} proposed hte use of real graphs with explicit group annotations (e.g. forums in a social network, categories of products, etc.) to infer what they call ``meta-communities'', and use them to evaluate overlapping community detection algorithms. However, a recent study from Hric, Darst and Fortunato~\cite{hric2014community} reveal a loose correspondence between  communities --the authors refer to them as structural communities-- and meta-communities.  This result reveals that those algorithms working for structural communities do not work well for finding meta-communities and viceversa, suggesting significantly different underlying characteristics between the two types of communities, which are yet to be indentified.

In this regard and to the best of our knowledge, there does not exist a set of generators to generate graphs with meta-communities for community detection algorithm benchmarking. The closest one is the LDBC-SNB data generator~\cite{Erling:2015:LSN:2723372.2742786} thanks to the generation of groups of users in the social network. Even though the generation process does not specifically enforce the generation of groups (meta-communities) for benchmarking community detection algorithms, the study from Prat-Pe\'rez and Dominguez-Sal reveals that these groups are more similar to the real meta-communities than those structural communities generated by the LFR benchmark~\cite{Prat-Perez:2014:CSS:2621934.2621942}.

The differences observed between structural and meta-communities reveal the need of more accurate community defeinitions thight more specifically to the domain or use case. Current community detection algorithms and graph generators for community detection are stuck to the traditional (and vague) definition of community, assuming that there exists a single algorithm that would fit all the use cases. Thus, future work requires the study of domain-specific community characteristics that can be used to generate graphs with a community structure that accurately resemble that of specific use cases, and thus revealing which are the best algorithms for each particular scenario.revealing which are the best algorithms for each particular scenario.

### 2018-05-15 generators_general.tex
First version

\subsection{General Graphs}
\label{sec:generators_general}

First of all we will focus on papers dealing with generation of general graph data not aiming at particular application domain. Currently, there exists a number of tools which involve a kind of general graph data generator, such as gtools from projects nauty and Traces~\cite{gtools} or the Stanford GraphBase~\cite{GraphBase}. We will, however, focus on primarily generating/benchmarking projects targeting Big Data world.

\paragraph{GraphGen} For the purpose of testing the scalability of an indexing technique called FG-index~\cite{Cheng:2007:FTV:1247480.1247574} on size of the database of graphs, their average size and average density, the authors have also implemented a synthetic generator called GraphGen~\cite{GraphGen}. It is based on the IBM synthetic data generation code for associations and sequential patterns\footnote{From 1996, no longer available at \url{http://www.almaden.ibm.com/cs/projects/iis/hdb/Projects/data mining/mining.shtml}.}. GraphGen creates a collection of labeled, undirected and connected graphs aiming at performance evaluation of frequent subgraph mining algorithms and graph query processing algorithms. The result is represented as a list of graphs, each consisting of a list of nodes and a list of edges.

\paragraph{HPC Scalable Graph Analysis Benchmark} The HPC Scalable Graph Analysis Benchmark~\cite{HPCgraph,Bader:2005:DIH:2099301.2099360} represents an application with multiple analysis techniques that access a single data structure representing a weighted, directed graph. The benchmark is composed of four separated operations (graph construction, classification of large vertex sets, graph extraction with BFS, and graph analysis with betweenness centrality) on a graph that follows a power-law distribution.

The graph generator constructs a list of edge tuples containing vertex identifiers (with the edge direction from the first one to the second one) and weights that represent data assigned to the edges of the multigraph in the form of positive integers with a uniform random distribution. The generator has the following parameters: number of vertices, number of edges, and maximum weight of an edge. The algorithm of the generator is based on R-MAT. Since the authors aim to avoid data locality, in the final step the vertex numbers are randomly permuted, and then edge tuples randomly shuffled.

A related project from the same authors developed for the 9th DIMACS Shortest Paths Challenge is GTgraph~\cite{GTgraph}. It involves three types of graphs: input graph instances used in the DARPA HPCS SSCA\#2 graph theory benchmark (version 1.0), Erd\"{o}s-R\'{e}nyi random graphs, and small-world graphs based on the R-MAT model.

\paragraph{Graph 500 Benchmark} The Graph 500 Benchmark~\cite{Graph500} includes a scalable data generator which produces weighted, undirected graph as a list of edge tuples containing the label of start vertex and end vertex together with a weight that represents data assigned to the edge. The space of vertex  labels is the set of integers beginning with 0. The input values required to describe the graph are (1) scale, i.e., the logarithm base two of the number of vertices, and (2) edge factor, i.e., the ratio of the graph's edge count to its vertex count (i.e., half the average degree of a vertex in the graph). The graph generator is a Kronecker generator similar to R-MAT. The data must not exhibit any locality, so in the final step the vertex labels and order of edges are randomly shuffled.

The covered operations currently involve BFS; however, the authors intend to involve also two more types -- optimization (single source shortest path) and edge-oriented (maximal independent set) -- and five graph-related business areas cybersecurity, medical informatics, data enrichment, social networks, and symbolic networks.

%\paragraph{gtools} Projects nauty and Traces~\cite{gtools} are programs for computing automorphism groups of graphs and digraphs~\cite{McKay201494}; they can also produce a canonical label. In the respective package there is also suite of programs called gtools which involve generators for non-isomorphic graphs, bipartite graphs, digraphs, and multigraphs.

### 2018-05-15 generators_streaming.tex
First version

\subsection{Graph Data Streaming}
\label{sec:generators_streaming}

...

### 2018-05-15 introduction.tex
First version

\section{Introduction}
\label{sec:intro}

In recent years the term Big Data has become a phenomenon that breaks down borders of many technologies and approaches that have so far been acknowledged as mature and robust for any conceivable application. Gartner Inc.\footnote{\url{http://www.gartner.com/}} describes Big Data as ``\emph{high \textbf{v}olume, high \textbf{v}elocity, and/or high \textbf{v}ariety information assets that require new forms of processing to enable enhanced decision making, insight discovery and process optimization}''.

...

\TODO{there are two types of graph big data sets - large graphs and large sets of small graphs; we focus on the former one}

\paragraph*{Contributions} In this survey we will focus on graph data generators in the context of Big Data and related applications of graph algorithms. The key contributions are as follows:

\begin{itemize}
  \item ...
\end{itemize}

...

\paragraph*{Outline} The rest of the text is structured as follows: ...
% In Section~\ref{sec:preliminaries} we provide a brief introduction to graph theory and related terms.
% In Section~\ref{sec:classification} we classify the current Big graph Data applications.
% In Section~\ref{sec:generators} we introduce the existing graph data generators in the context of the proposed categories and their main features.
% Section~\ref{sec:comparison} provides comparison of the described generators.
% In Section~\ref{sec:challenges} we discuss challenges and open problems. And in Section~\ref{sec:conclusion} we conclude.

### 2018-05-15 main.tex
First version

% v2-acmsmall-sample.tex, dated March 6 2012
% This is a sample file for ACM small trim journals
%
% Compilation using 'acmsmall.cls' - version 1.3 (March 2012), Aptara Inc.
% (c) 2010 Association for Computing Machinery (ACM)
%
% Questions/Suggestions/Feedback should be addressed to => "acmtexsupport@aptaracorp.com".
% Users can also go through the FAQs available on the journal's submission webpage.
%
% Steps to compile: latex, bibtex, latex latex
%
% For tracking purposes => this is v1.3 - March 2012

\documentclass[prodmode,acmtecs]{acmsmall} % Aptara syntax

% Package to generate and customize Algorithm as per ACM style
\usepackage[ruled]{algorithm2e}
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

\usepackage{adjustbox}
\usepackage{array}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{rotating}

\newcommand*\rot{\rotatebox{90}}
\newcommand*\OK[0]{$\surd$}
\newcommand*\NO[0]{$\times$}
\newcommand*\QQ[0]{$?$}

% Metadata Information
\acmVolume{0}
\acmNumber{0}
\acmArticle{0}
\acmYear{2016}
\acmMonth{0}

% Copyright
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\doi{0000001.0000001}

%ISSN
\issn{0360-0300}

\newcommand{\TODO}[1]{{\color{red}{\textbf{TODO: {#1}}\xspace}}}
\newcommand{\QUE}[1]{{\color{blue}{\textbf{Q: {#1}}\xspace}}}

% Document starts
\begin{document}

% Page heads
\markboth{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr}{Graph Data Generators in the World of Big Data}

% Title portion
\title{Graph Data Generators in the World of Big Data}
\author{
ANGELA BONIFATI
\affil{Lyon 1 University, France}
IRENA HOLUBOV\'{A}
\affil{Charles University, Prague, Czech Republic}
ARNAU PRAT-P\'{E}REZ
\affil{DAMA-UPC, Universitat Polit\`ecnica de Catalunya, Spain}
SHERIF SAKR
\affil{King Saud bin Abdulaziz University for Health Sciences, Saudi Arabia}
}
% NOTE! Affiliations placed here should be for the institution where the
%       BULK of the research was done. If the author has gone to a new
%       institution, before publication, the (above) affiliation should NOT be changed.
%       The authors 'current' address may be given in the "Author's addresses:" block (below).
%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
%       currently affiliated with NASA.

\begin{abstract}
In recent years the term Big Data has become a phenomenon that breaks down borders of many technologies and approaches that have so far been acknowledged as mature and robust.

...

\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}

<ccs2012>

<concept>

<concept_id>10002950.10003624.10003633</concept_id>
 <concept_desc>Mathematics of computing~Graph theory</concept_desc>

<concept_significance>500</concept_significance>
</concept>

<concept>

<concept_id>10003752.10003809.10003635</concept_id>
 <concept_desc>Theory of computation~Graph algorithms analysis</concept_desc>

<concept_significance>500</concept_significance>
</concept>

<concept>

<concept_id>10002951.10002952.10002953.10010146</concept_id>
 <concept_desc>Information systems~Graph-based database models</concept_desc>

<concept_significance>300</concept_significance>
</concept>
</ccs2012>

\end{CCSXML}

 \ccsdesc[500]{Mathematics of computing~Graph theory}
 \ccsdesc[500]{Theory of computation~Graph algorithms analysis}
 \ccsdesc[300]{Information systems~Graph-based database models}

%
% End generated code
%

% We no longer use \terms command
%\terms{Design, Algorithms, Performance}

\keywords{Big Data management, graph data, generators, benchmarks, synthetic data, ...}

\acmformat{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr, 2018. Graph Data Generators in the World of Big Data.}
% At a minimum you need to supply the author names, year and a title.
% IMPORTANT:
% Full first names whenever they are known, surname last, followed by a period.
% In the case of two authors, 'and' is placed between them.
% In the case of three or more authors, the serial comma is used, that is, all author names
% except the last one but including the penultimate author's name are followed by a comma,
% and then 'and' is placed before the final author's name.
% If only first and middle initials are known, then each initial
% is followed by a period and they are separated by a space.
% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.

\begin{bottomstuff}
This work is supported by ...

Author's addresses:
A. Bonifati, ...;
I. Holubov\'{a}, Department of Software Engineering, Faculty of Mathematics and Physics, Charles University, Malostransk\'{e} n\'{a}m. 25, 118 00 Praha~1, Czech Republic.
A. Prat-P\'erez, ...;
S. Sakr, ....
\end{bottomstuff}

\maketitle

\input{introduction}
\input{preliminaries}
\input{comparison}
\input{classification}
\input{generators}
%\input{comparison2}
\input{challenges}
\input{conclusion}

\begin{acks}
The authors would like to thank Dr. Kamesh Madduri for numerous consultations and suggestions on the covered areas.
\end{acks}

% Bibliography
\bibliographystyle{ACM-Reference-Format-Journals}
\bibliography{biblio}

% History dates
\received{August 2016}{September 2016}{December 2016}

\end{document}

### 2018-05-15 preliminaries.tex
First version

\section{Preliminaries}
\label{sec:preliminaries}

A \emph{graph} $G = (V, E)$, is a set $V$ of $n$ nodes, and a set $E$ of $m$ edges between them. The edges may be undirected or directed. \emph{Bipartite graphs} have edges between two sets of nodes.

...

While the Gaussian distribution is common in nature, there are many cases (such as the WWW, the Internet, citation graph etc.) where the probability of events far to the right of the mean is significantly higher~\cite{Chakrabarti:2006:GML:1132952.1132954}. Power-law distributions attempt to model this. Two variables $x$ and $y$ are related by a \emph{power-law} when $y(x) = A.x^{-k}$, where $A$ and $k$ are positive constants. $k$ is called the power law exponent.

Another important feature of many types of graphs (e.g., typically social networks) is the \emph{community effect}, where a \emph{community} is a set of nodes where each node is closer to the other nodes within the community than to nodes outside it. Communities reveal how a network is internally organized, and indicate the presence of special relationships between the nodes.

Most real-world graphs also have surprisingly small \emph{diameters}, i.e. the longest shortest path between any two graph vertices of a graph.

...

### 2018-05-16 introduction.tex
differences with prior surveys - cont'd

@@
 \paragraph*{Contributions} In this survey we will focus on graph data generators in the context of Big Data and related applications of graph algorithms. The key contributions are as follows:
-
 \begin{itemize}
@@
 ...
+
+\paragraph*{Differences with prior surveys}
+
+To the best of our knowledge, our work is the first surveying the wide
+landscale of graph data generators spanning different Big Data applications and 
+targeting diverse computer science subfields. In particular, we cover graph database
+generators, graph processing generators, social networks and community detection
+generators, Semantic Web data generators, graph
+analytics generators, IOT, Telecommunication and graph streaming generators, 
+and Machine Learning and Graph Mining generators .
+
+A subset of the graph database
+generators, parallel and distributed graph processing generators, along
+with a subset of the Semantic Web data generators have been discussed in
+\cite{BFHI18} while cross-comparing them with respect to input, output,
+supported workload, data model and query language; along with the
+distinguished chokepoints. However, the provided classification is
+inherently data-driven and not meant to serve the purpose of letting any
+researcher or practitioner interested in Big Data be able to choose a
+generator based on its functional features, such as the application domain,
+the supported operations and the key configuration options. 
+Moreover, our work is much broader and targets different communities, beyond database
+and graph processing communities.
+
+\TODO{Outreach other surveys in other communities.}
 

### 2018-05-24 comparison.tex
Merging of sections 3 and 4

@@
-\section{Comparative Study}
+\section{Classification and Comparative Study}
 \label{sec:comparison}
 
-In Tables~\ref{tab:comparisonCharacteristicsA},~\ref{tab:comparisonCharacteristicsB}   we overview the key characteristics of the data generators clustered according to the respective applications.
+In order to provide the reader with a quick preview of the generators and thus finding the target solutions easily, we start the survey with classification and comparative study of the existing tools.
+There are various ways how to classify them.
+We first overview approaches used in related work and then we introduce ours.
+As mentioned in the Introduction, since this survey is unique in terms of scope and new tools related to Big Data processing, our classification and comparative strategy differs too.
+
+In general, the graph data generators can be classified according to various criteria.
+Paper~\cite{DBLP:conf/sdm/ChakrabartiZF04} introduces two categories -- degree-based and procedural generators.
+Given a degree distribution (typically following a power law), \emph{degree-based generators} (e.g., Barabasi-Albert model~\cite{Barabasi99emergenceScaling}) try to find a graph that matches it, but without giving any insights about the graph or trying to match other criteria (like, e.g., small diameter, eigenvalues etc.).
+On the other hand, \emph{procedural generators} (e.g., R-MAT~\cite{DBLP:conf/sdm/ChakrabartiZF04}) try to find simple mechanisms to generate graphs that match a property of the real graphs and, typically, the power law degree distribution.
+
+Paper~\cite{Chakrabarti:2006:GML:1132952.1132954} introduces five categories of graph models that can be synthesized: (1) \emph{random graph models} (e.g., Erd\"{o}s-R\'{e}nyi~\cite{Erdos:1960}) generated by a random process, (2) \emph{preferential attachment models} (e.g., Barabasi-Albert model) which try to model the power law from the preferential attachment viewpoint, (3) \emph{optimization-based models} (e.g., HOT model~\cite{PhysRevLett.84.2529}) resulting from the idea that power laws can result from resource optimizations and tolerance to risks, (4) \emph{tensor-based models} (e.g., R-MAT) targeting a trade-off between low number of model parameters and efficiency, and (5) \emph{internet-specific models} corresponding to hybrids using ideas from the other categories in order to suit the specific features of the graphs.
+
+The type of the generator can also be influenced by the benchmark involving it, whereas we can distinguish, e.g., \emph{domain-specific} benchmarks, \emph{application-specific} benchmarks, \emph{workload-driven} benchmarks,  \emph{microbenchmarks} etc.
+
+%\paragraph{Erd\"{o}s-R\'{e}nyi} One of the first and still very popular approaches with lots of variations and modifications is the random graph model proposed in~\cite{Erdos:1960}.
+Given a positive integer $n$ and a probability value $0 \leq p \leq 1$, the graph $G(n,p)$ is an undirected graph on $n$ vertices whose edges are chosen s.t.
+for all pairs of vertices $u,v$ there is an edge $(u,v)$ with probability $p$.
+%
+%\paragraph{Barabasi-Albert} The Barabasi-Albert (BA) model~\cite{Barabasi99emergenceScaling} proposes that structure emerges in network topologies as the result of two processes -- growth and preferential attachment.
+The BA model starts with a small set of nodes and grows the network as nodes and edges are added over time.
+Preferential attachment is based on the idea that the probability of connecting to a node is proportional to the current degree of that node (i.e., ``the rich get richer'').
+%
+%\paragraph{HOT} The highly optimized tolerance (HOT)~\cite{PhysRevLett.84.2529} model is introduced  using a ``forest fire'' example as follows: Suppose we have a forest which is prone to forest fires.
+Each portion of the forest has a different chance of starting the fire.
+We wish to minimize the damage by assigning (a limited amount of) resources such as firebreaks at different positions in the forest.
+More precisely, we have $n$ possible events, each with an associated probability $p_i, 1 \le i \le n$.
+Each event can lead to some loss $l_i$, which is a function of the resources $r_i$ allocated for that event $(l_i = f (r_i))$, whose total number is limited ($\sum_i r_i \le R$ for some given $R$).
+The aim is to minimize the expected cost $\sum_i p_i l_i$.
+The authors show that resource placement is related to the probability distribution $p_i$ by a power law and the probability of events which cause a loss greater than some value $k$ is related to $k$ by a power law too.
+%
+%
+%\paragraph{R-MAT} The R-MAT (Recursive MATrix)~\cite{DBLP:conf/sdm/ChakrabartiZF04} model can be used to create graphs with community structure, power law degree distributions, and a small diameter.
+It generates weighted, directed and bipartite graphs.
+Graph generation is modeled with a matrix recursion procedure in which the adjacency matrix (empty at the beginning) is recursively subdivided into four equal-sized partitions and edges are distributed across the partitions with unequal probabilities.
+
+%In Figure~\ref{fig:classification} ...
+%
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.8\textwidth]{classification.png}
+%\caption{Classification of graph data generators}
+%\label{fig:classification}
+%\end{figure}
+
+We decided to classify the generators primarily on the basis of the respective application domains or communities.
+In Tables~\ref{tab:comparisonCharacteristicsA},~\ref{tab:comparisonCharacteristicsB}   we overview the key characteristics of the data generators clustered according to the respective application domains.
 In particular, we show:
@@
 
+As we can see...
+
 \begin{sidewaystable}
@@
 \tbl{Key characteristics of the generators (part A)} {
-\begin{tabular}{| c | p{2.2cm} | l |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
+\begin{tabular}{| c | p{2.2cm} | p{2cm} |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
  \hline
@@
                \\ \hline
-\hline   % general graphs (Angela)
-\multirow{5}{*}{\rot{\textbf{General}}}
+\hline   % ====================== general graphs
+\multirow{8}{*}{\rot{\textbf{General}}}
   & graph500  & fixed & & Y & N & Y & power-law & &  Y  \\
@@
 \hline
-\hline  % graph databases (Angela)
-\multirow{4}{*}{\rot{\textbf{DBs}}}
- & XGDBench & fixed  & social network  & fixed & Y & Y & power-law &  MAG &  Y  \\
- \cline{2-10}
-& graphGen & pattern-driven (Cypher schema) & user-defined  & -- & -- & Y & -- &  property graphs & N   \\
- \cline{2-10}
- & gMark & schema-driven (internal schema) &  user-defined  & generated &  N  & Y & uniform, normal, zipfian &  N-triples & N    \\
-\hline
-\hline % Semantic web (Irena)
-\multirow{18}{*}{\rot{\textbf{Semantic web}}}
+\hline %  ======================  Semantic web
+\multirow{22}{*}{\rot{\textbf{Semantic web}}}
  & LUBM & fixed & university  & fixed & N & Y & random (LCG) &  RDF & N   \\
@@
 \tbl{Key characteristics of the generators (part B)} {
-\begin{tabular}{| c | p{2.2cm}| l |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
+\begin{tabular}{| c | p{2.2cm}| p{2cm} |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
  \hline
@@
                \\ \hline
+\hline  % ======================  graph databases
+\multirow{7}{*}{\rot{\textbf{Graph DBs}}}
+ & XGDBench & fixed  & social network  & fixed & Y & Y & power-law &  MAG &  Y  \\
+ \cline{2-10}
+& graphGen & pattern-driven (Cypher schema) & user-defined  & -- & -- & Y & -- &  property graphs & N   \\
+ \cline{2-10}
+ & gMark & schema-driven (internal schema) &  user-defined  & generated &  N  & Y & uniform, normal, zipfian &  N-triples & N    \\
 \hline
-\hline % social networks (Arnau)
+\hline %  ======================   social networks
 \multirow{9}{*}{\rot{\textbf{Social networks}}}
@@
 \hline
-\hline   % graph analytics (Sherif)
+\hline   % ======================   graph analytics
 \multirow{5}{*}{\rot{\textbf{Analytics}}}
@@
 \hline
-\hline   % streaming (Sherif)
+\hline   %  ======================  streaming 
 \multirow{5}{*}{\rot{\textbf{Streaming}}}
@@
 \end{sidewaystable}
-
-In Table~\ref{tab:comparisonReferences} we provide an overview of works which use the respective generator for evaluation of the proposed method or comparative study of a selected set methods.
-\QUE{CSUR has strict page limit 35 pages.
-I'm afraid that this will extend the list of references extremely.}
-
-\begin{table}
-\scriptsize
-\centering
-\tbl{Exploitation of the generators}{
-\begin{tabular}{| l | p{11.5cm} | }
- \hline          \textbf{Generator}
-               & \textbf{Cited in}
-               \\ \hline
-\hline  % general graphs
-  & \\  
-\hline
-  & \\  
-\hline
-\hline % graph databases
-  & \\  
-\hline
-  & \\  
-\hline
-\hline % Linked Data
- LUBM & \\  
-\hline
- LBBM & \\  
-\hline
- UOBM & \\  
-\hline
- IIMB & \\  
-\hline
- BSBM & \\  
-\hline
- SP$^2$Bench & \\  
-\hline
- DBPSB & \\  
-\hline
- LODIB & \\  
-\hline
- SIB & \\  
-\hline
- Geographica & \\  
-\hline
- WatDiv & \\  
-\hline
- RBench & \\  
-\hline
- LDBC SPB & \\  
-\hline
-\hline  % social networks
-  & \\  
-\hline
-  & \\  
-\hline
-\end{tabular} }
-\label{tab:comparisonReferences}
-\end{table}

### 2018-05-25 introduction.tex
edits on Section 1

@@
 
-To the best of our knowledge, our work is the first surveying the wide
-landscale of graph data generators spanning different Big Data applications and 
+To the best of our knowledge, our work is the first surveying the broad landscape of graph data generators spanning different Big Data applications and 
 targeting diverse computer science subfields. In particular, we cover graph database
@@
 analytics generators, IOT, Telecommunication and graph streaming generators, 
-and Machine Learning and Graph Mining generators .
+and Machine Learning and Graph Mining generators. A comprehensive study of
+graph generators is missing for many of the specific subfields mentioned
+above.
 
@@
 
-\TODO{Outreach other surveys in other communities.}
+Graph generators matching graph patterns used in data mining have been
+studied in \cite{Chakrabarti:2006:GML:1132952.1132954},
+focusing on mostly occurring patterns, such as power laws, size of graph diameters
+and community structure. The considered graph generators are compared in
+terms of graph type, degree distributions, exponentiality, diameter and
+community effects. We refer the reader to this survey for taxonomies
+involving these properties, whereas we provide here a functionality-driven
+taxonomy across all the categories of graph generators that we consider.
+
+%\TODO{Outreach other surveys in other communities.}
 
@@
 % In Section~\ref{sec:challenges} we discuss challenges and open problems. And in Section~\ref{sec:conclusion} we conclude.
+
+}

### 2018-05-28 introduction.tex
fixed the compilation problem
completed the part on Prior Related Surveys

--- 2018-05-15 introduction.tex
@@
 ...
+
+\paragraph*{Differences with prior surveys}
+
+To the best of our knowledge, our work is the first surveying the broad landscape of graph data generators spanning different Big Data applications and 
+targeting diverse computer science subfields. In particular, we cover graph database
+generators, graph processing generators, social networks and community detection
+generators, Semantic Web data generators, graph
+analytics generators, IOT, Telecommunication and graph streaming generators, 
+and Machine Learning and graph mining generators. A comprehensive study of
+graph generators is missing for many of the specific subfields mentioned
+above.
+
+A limited subset of graph database
+generators, parallel and distributed graph processing generators, along
+with a few of the Semantic Web data generators presented in our survey have
+been discussed in a related book chapter
+\cite{BFHI18} while cross-comparing them with respect to input, output,
+supported workload, data model and query language, along with the
+distinguished chokepoints. However, the provided classification is
+inherently data-driven and not meant to serve the purpose of letting any
+researcher or practitioner interested in Big Data be able to make a guided
+choice of the desired 
+generator based on its functional and goal-driven features (such as the application domain,
+the supported operations and the key configuration options). 
+Moreover, our work is much broader and targets graph generators of several 
+diversified communities, not limiting its scope to few generators of the database
+and graph processing communities.
+
+Graph generators matching graph patterns used in data mining have been
+studied in \cite{Chakrabarti:2006:GML:1132952.1132954}, 
+focusing on mostly occurring patterns, such as power laws, size of graph diameters
+and community structure. The considered graph generators are compared in
+terms of graph type, degree distributions, exponentiality, diameter and
+community effects. We refer the reader to this survey for taxonomies
+involving these properties, whereas we provide here a functionality-driven
+taxonomy across all the categories of graph generators that we consider.    
+We also point out that this survey is outdated as it does not consider the 
+graph mining generators that fervently appeared in the last decade.
+
+\TODO{Check with Arnau}
+
+Aggarwal and Subbian \cite{AggarwalS14} have surveyed evolution analysis in
+graphs, by primarily focusing on data mining maintenance methods and on analytical 
+quantification and explanation of the changes of the underlying networks. 
+A brief discussion on evolutionary
+network data generators is carried out in
+the paper. The data generation of evolutionary networks based on 
+Densification Power Law (DPL) and shrinking diameters \cite{LeskovecKF05} and community-guided
+attachment properties \cite{LeskovecKF05} is then considered, along with tackling Kronecker
+recursion with recursive tensor multiplication \cite{AkogluMF08}.
+
+\TODO{Better highlight the differences when Sherif's part is in.}
+
+%\TODO{Outreach other surveys in other communities.}
 

### 2018-05-30 main.tex
Merging of sections 3 and 4
fixed the compilation problem
changed title; added an abstract

@@
 % Title portion
-\title{Graph Data Generators in the World of Big Data}
+%\title{Graph Data Generators in the World of Big Data}
+\title{Graph Data Generators for Data Science: A Survey}
 \author{
@@
 \begin{abstract}
-In recent years the term Big Data has become a phenomenon that breaks down borders of many technologies and approaches that have so far been acknowledged as mature and robust.
+%In recent years the term Big Data has become a phenomenon that breaks down borders of many technologies and approaches that have so far been acknowledged as mature and robust.
+%...
+The abundance of interconnected data has fueled the design and
+implementation of graph generators reproducing real-world
+properties, 
+or gauging the effectiveness of graph algorithms, graph tools and 
+applications manipulating these data.
+We consider graph generation targeting multiple subfields, such as graph databases, graph data mining ,
+graph streaming and machine learning communities, alongside community
+detection,
+social networks and IoT communities. 
+Despite the disparate requirements of graph generators throughout these
+communities, we analyze them under a common umbrella, reaching out the
+functionalities, the practical usage, and the supported operations of graph generators. 
+We argue that
+this classification is serving the need of providing data scientists,
+researchers and practitioners with the right data generator at hand.
 
-...
+This survey provides a comprehensive overview of the state-of-the-art graph generators 
+by focusing on those that are pertinent for data science tasks. Finally, we discuss
+open challenges and missing features of graph generators in view of the 
+evolving requirements in data science.
 
@@
 \input{comparison}
-\input{classification}
+%\input{classification}
 \input{generators}

### 2018-05-31 main.tex
another pass on title/abstract

@@
 %\title{Graph Data Generators in the World of Big Data}
-\title{Graph Data Generators for Data Science: A Survey}
+\title{Graph Generators for Data Science: A Survey}
 \author{
@@
 implementation of graph generators reproducing real-world
-properties, 
-or gauging the effectiveness of graph algorithms, graph tools and 
+linking properties, 
+or gauging the effectiveness of graph algorithms, techniques and 
 applications manipulating these data.
@@
 this classification is serving the need of providing data scientists,
-researchers and practitioners with the right data generator at hand.
+researchers and practitioners with the right data generator at hand for
+their work.
 
 This survey provides a comprehensive overview of the state-of-the-art graph generators 
-by focusing on those that are pertinent for data science tasks. Finally, we discuss
+by focusing on those that are pertinent and suitable for data science tasks. Finally, we discuss
 open challenges and missing features of graph generators in view of the 
-evolving requirements in data science.
+evolution of data science.
 

### 2018-06-03 main.tex
Checking the title and abstract

@@
 %...
-The abundance of interconnected data has fueled the design and
-implementation of graph generators reproducing real-world
-linking properties, 
-or gauging the effectiveness of graph algorithms, techniques and 
-applications manipulating these data.
-We consider graph generation targeting multiple subfields, such as graph databases, graph data mining ,
-graph streaming and machine learning communities, alongside community
-detection,
-social networks and IoT communities. 
-Despite the disparate requirements of graph generators throughout these
-communities, we analyze them under a common umbrella, reaching out the
-functionalities, the practical usage, and the supported operations of graph generators. 
-We argue that
-this classification is serving the need of providing data scientists,
-researchers and practitioners with the right data generator at hand for
-their work.
+The abundance of interconnected data has fueled the design and implementation of graph generators reproducing real-world linking properties, or gauging the effectiveness of graph algorithms, techniques and applications manipulating these data.
+We consider graph generation targeting multiple subfields, such as graph databases, graph data mining, graph streaming and machine learning communities, alongside community detection, social networks and IoT communities.
+Despite the disparate requirements of graph generators throughout these communities, we analyze them under a common umbrella, reaching out the functionalities, the practical usage, and the supported operations of graph generators.
+We argue that this classification is serving the need of providing data scientists, researchers and practitioners with the right data generator at hand for their work.
 
-This survey provides a comprehensive overview of the state-of-the-art graph generators 
-by focusing on those that are pertinent and suitable for data science tasks. Finally, we discuss
-open challenges and missing features of graph generators in view of the 
-evolution of data science.
-
+This survey provides a comprehensive overview of the state-of-the-art graph generators by focusing on those that are pertinent and suitable for data science tasks.
+Finally, we discuss open challenges and missing features of graph generators in view of the evolution of data science.
 \end{abstract}
@@
 \begin{acks}
-The authors would like to thank Dr. Kamesh Madduri for numerous consultations and suggestions on the covered areas.
+The authors would like to thank Dr. Kamesh Madduri for consultations and suggestions on the covered areas.
 \end{acks}

### 2018-06-05 introduction.tex
A few paragraphs in the introduction

@@
 
-In recent years the term Big Data has become a phenomenon that breaks down borders of many technologies and approaches that have so far been acknowledged as mature and robust for any conceivable application.
+%In recent years the term Big Data has become a phenomenon that breaks down borders of many technologies and approaches that have so far been acknowledged as mature and robust for any conceivable application.
 Gartner Inc.\footnote{\url{http://www.gartner.com/}} describes Big Data as ``\emph{high \textbf{v}olume, high \textbf{v}elocity, and/or high \textbf{v}ariety information assets that require new forms of processing to enable enhanced decision making, insight discovery and process optimization}''.
 
+%\TODO{The abundance of interconnected data has fueled the design and implementation of graph generators reproducing real-world linking properties, or gauging the effectiveness of graph algorithms, techniques and applications manipulating these data.}
+
+One of the most popular data structures in the world of computer science are graphs.
+They enable to represent complex information in a simple and yet powerful way supported by a strong mathematical background.
+With the dawn of the new millennium which brought numerous novel technologies and applications, the graphs have become even more popular.
+There has appeared a number of use cases\footnote{\url{https://neo4j.com/use-cases/}} (such as fraud detection, recommendation engines, social networks etc.) where graphs represent the linked information.
+
+In general, we can distinguish two types of graph data sets: (1) a single large graph (possibly with several components), such as social networks  or Linked Data graphs, and (2) a large set of small graphs, such as chemical compounds\footnote{\url{https://pubchem.ncbi.nlm.nih.gov/}} or linguistics syntax trees\footnote{\url{https://catalog.ldc.upenn.edu/ldc99t42}}.
+Naturally, the algorithms used in theses two classes differ a lot~\cite{DBLP:books/igi/Sakr2011}.
+In the former case we can search, e.g., for communities and their features or shortest paths, while in the latter case we usually query for supergraphs, subgraphs or graphs similar to a given graph pattern.
+Also, as in the other fields, quite often the respective real-world data is not publicly available (or simply does not exist when a particular method for manipulation with the data is proposed).
+As a consequence, also in the world of graphs there has appeared a number of graph data generators which enable to  reproduce the respective real-world linking properties and gauge the effectiveness of a particular algorithm.
+
+In this survey we ...
+\TODO{We consider graph generation targeting multiple subfields, such as graph databases, graph data mining, graph streaming and machine learning communities, alongside community detection, social networks and IoT communities}
+
 ...
+\TODO{Despite the disparate requirements of graph generators throughout these communities, we analyze them under a common umbrella, reaching out the functionalities, the practical usage, and the supported operations of graph generators.}
 
-\TODO{there are two types of graph big data sets - large graphs and large sets of small graphs; we focus on the former one}
+... \TODO{We argue that this classification is serving the need of providing data scientists, researchers and practitioners with the right data generator at hand for their work.}
 
-\paragraph*{Contributions} In this survey we will focus on graph data generators in the context of Big Data and related applications of graph algorithms. The key contributions are as follows:
+...
+\TODO{This survey provides a comprehensive overview of the state-of-the-art graph generators by focusing on those that are pertinent and suitable for data science tasks.
+Finally, we discuss open challenges and missing features of graph generators in view of the evolution of data science.}
+
+\paragraph*{Contributions} The key contributions of this survey are as follows:
 \begin{itemize}
@@
 generators, Semantic Web data generators, graph
-analytics generators, IOT, Telecommunication and graph streaming generators, 
+analytics generators, IoT, Telecommunication and graph streaming generators,
 and Machine Learning and graph mining generators. A comprehensive study of

### 2018-06-05 main.tex
A few paragraphs in the introduction

@@
 % Page heads
-\markboth{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr}{Graph Data Generators in the World of Big Data}
+\markboth{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr}{Graph Generators for Data Science: A Survey}
 
@@
 \begin{abstract}
-%In recent years the term Big Data has become a phenomenon that breaks down borders of many technologies and approaches that have so far been acknowledged as mature and robust.
-%...
 The abundance of interconnected data has fueled the design and implementation of graph generators reproducing real-world linking properties, or gauging the effectiveness of graph algorithms, techniques and applications manipulating these data.
@@
 
-\acmformat{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr, 2018. Graph Data Generators in the World of Big Data.}
+\acmformat{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr, 2018. Graph Generators for Data Science: A Survey.}
 % At a minimum you need to supply the author names, year and a title.

### 2018-06-06 introduction.tex
More paragraphs in the introduction

@@
 
-In this survey we ...
-\TODO{We consider graph generation targeting multiple subfields, such as graph databases, graph data mining, graph streaming and machine learning communities, alongside community detection, social networks and IoT communities}
+In this survey we provide a comprehensive overview of the state-of-the-art graph generators by focusing on those that are pertinent and suitable for data science tasks.
+Our aim is to cover a wide range of currently popular areas of graph data processing.
+In particular, we consider graph generation in the areas of graph databases, graph data mining, graph streaming and machine learning communities, alongside community detection, social networks and IoT communities.
+Despite the disparate requirements of graph generators throughout these communities, we analyze them under a common umbrella, reaching out the functionalities, the practical usage, and the supported operations of graph generators.
+The reasons for this scope and classification are as follows:
 
-...
-\TODO{Despite the disparate requirements of graph generators throughout these communities, we analyze them under a common umbrella, reaching out the functionalities, the practical usage, and the supported operations of graph generators.}
+\begin{enumerate}
+  \item Despite the differences of the covered areas, the requirements for the graph data generators can be similar in particular cases.
+Reusing or learning from tools in other fields can thus bring new opportunities for both researchers and practitioners.
+  \item The selected classification is serving the need of providing data scientists, researchers and practitioners with the right data generator at hand for their work.
+\end{enumerate}
 
-... \TODO{We argue that this classification is serving the need of providing data scientists, researchers and practitioners with the right data generator at hand for their work.}
-
-...
-\TODO{This survey provides a comprehensive overview of the state-of-the-art graph generators by focusing on those that are pertinent and suitable for data science tasks.
-Finally, we discuss open challenges and missing features of graph generators in view of the evolution of data science.}
+To conclude the comparative study, we discuss open challenges and missing features of graph generators in view of the evolution of data science.
 

### 2018-06-07 generators_general.tex
Added darwini and bter to general graph generators

@@
 
-First of all we will focus on papers dealing with generation of general graph data not aiming at particular application domain.
-Currently, there exists a number of tools which involve a kind of general graph data generator, such as gtools from projects nauty and Traces~\cite{gtools} or the Stanford GraphBase~\cite{GraphBase}.
-We will, however, focus on primarily generating/benchmarking projects targeting Big Data world.
+First of all we will focus on papers dealing with generation of general graph
+data not aiming at particular application domain. Currently, there exists a
+number of tools which involve a kind of general graph data generator, such as
+gtools from projects nauty and Traces~\cite{gtools} or the Stanford
+GraphBase~\cite{GraphBase}. We will, however, focus on primarily
+generating/benchmarking projects targeting Big Data world.
 
-\paragraph{GraphGen} For the purpose of testing the scalability of an indexing technique called FG-index~\cite{Cheng:2007:FTV:1247480.1247574} on size of the database of graphs, their average size and average density, the authors have also implemented a synthetic generator called GraphGen~\cite{GraphGen}.
-It is based on the IBM synthetic data generation code for associations and sequential patterns\footnote{From 1996, no longer available at \url{http://www.almaden.ibm.com/cs/projects/iis/hdb/Projects/data mining/mining.shtml}.}.
-GraphGen creates a collection of labeled, undirected and connected graphs aiming at performance evaluation of frequent subgraph mining algorithms and graph query processing algorithms.
-The result is represented as a list of graphs, each consisting of a list of nodes and a list of edges.
+\paragraph{GraphGen} For the purpose of testing the scalability of an indexing
+technique called FG-index~\cite{Cheng:2007:FTV:1247480.1247574} on size of the
+database of graphs, their average size and average density, the authors have
+also implemented a synthetic generator called GraphGen~\cite{GraphGen}. It is
+based on the IBM synthetic data generation code for associations and sequential
+patterns\footnote{From 1996, no longer available at
+\url{http://www.almaden.ibm.com/cs/projects/iis/hdb/Projects/data
+mining/mining.shtml}.}. GraphGen creates a collection of labeled, undirected and
+connected graphs aiming at performance evaluation of frequent subgraph mining
+algorithms and graph query processing algorithms. The result is represented as a
+list of graphs, each consisting of a list of nodes and a list of edges.
 
-\paragraph{HPC Scalable Graph Analysis Benchmark} The HPC Scalable Graph Analysis Benchmark~\cite{HPCgraph,Bader:2005:DIH:2099301.2099360} represents an application with multiple analysis techniques that access a single data structure representing a weighted, directed graph.
-The benchmark is composed of four separated operations (graph construction, classification of large vertex sets, graph extraction with BFS, and graph analysis with betweenness centrality) on a graph that follows a power-law distribution.
+\paragraph{HPC Scalable Graph Analysis Benchmark} The HPC Scalable Graph
+Analysis Benchmark~\cite{HPCgraph,Bader:2005:DIH:2099301.2099360} represents an
+application with multiple analysis techniques that access a single data
+structure representing a weighted, directed graph. The benchmark is composed of
+four separated operations (graph construction, classification of large vertex
+sets, graph extraction with BFS, and graph analysis with betweenness centrality)
+on a graph that follows a power-law distribution.
 
-The graph generator constructs a list of edge tuples containing vertex identifiers (with the edge direction from the first one to the second one) and weights that represent data assigned to the edges of the multigraph in the form of positive integers with a uniform random distribution.
-The generator has the following parameters: number of vertices, number of edges, and maximum weight of an edge.
-The algorithm of the generator is based on R-MAT.
-Since the authors aim to avoid data locality, in the final step the vertex numbers are randomly permuted, and then edge tuples randomly shuffled.
+The graph generator constructs a list of edge tuples containing vertex
+identifiers (with the edge direction from the first one to the second one) and
+weights that represent data assigned to the edges of the multigraph in the form
+of positive integers with a uniform random distribution. The generator has the
+following parameters: number of vertices, number of edges, and maximum weight of
+an edge. The algorithm of the generator is based on R-MAT. Since the authors aim
+to avoid data locality, in the final step the vertex numbers are randomly
+permuted, and then edge tuples randomly shuffled.
 
-A related project from the same authors developed for the 9th DIMACS Shortest Paths Challenge is GTgraph~\cite{GTgraph}.
-It involves three types of graphs: input graph instances used in the DARPA HPCS SSCA\#2 graph theory benchmark (version 1.0), Erd\"{o}s-R\'{e}nyi random graphs, and small-world graphs based on the R-MAT model.
+A related project from the same authors developed for the 9th DIMACS Shortest
+Paths Challenge is GTgraph~\cite{GTgraph}. It involves three types of graphs:
+input graph instances used in the DARPA HPCS SSCA\#2 graph theory benchmark
+(version 1.0), Erd\"{o}s-R\'{e}nyi random graphs, and small-world graphs based
+on the R-MAT model.
 
-\paragraph{Graph 500 Benchmark} The Graph 500 Benchmark~\cite{Graph500} includes a scalable data generator which produces weighted, undirected graph as a list of edge tuples containing the label of start vertex and end vertex together with a weight that represents data assigned to the edge.
-The space of vertex  labels is the set of integers beginning with 0.
-The input values required to describe the graph are (1) scale, i.e., the logarithm base two of the number of vertices, and (2) edge factor, i.e., the ratio of the graph's edge count to its vertex count (i.e., half the average degree of a vertex in the graph).
-The graph generator is a Kronecker generator similar to R-MAT.
-The data must not exhibit any locality, so in the final step the vertex labels and order of edges are randomly shuffled.
+\paragraph{Graph 500 Benchmark} The Graph 500 Benchmark~\cite{Graph500} includes
+a scalable data generator which produces weighted, undirected graph as a list of
+edge tuples containing the label of start vertex and end vertex together with a
+weight that represents data assigned to the edge. The space of vertex  labels is
+the set of integers beginning with 0. The input values required to describe the
+graph are (1) scale, i.e., the logarithm base two of the number of vertices, and
+(2) edge factor, i.e., the ratio of the graph's edge count to its vertex count
+(i.e., half the average degree of a vertex in the graph). The graph generator is
+a Kronecker generator similar to R-MAT. The data must not exhibit any locality,
+so in the final step the vertex labels and order of edges are randomly shuffled.
 
-The covered operations currently involve BFS; however, the authors intend to involve also two more types -- optimization (single source shortest path) and edge-oriented (maximal independent set) -- and five graph-related business areas cybersecurity, medical informatics, data enrichment, social networks, and symbolic networks.
+The covered operations currently involve BFS; however, the authors intend to
+involve also two more types -- optimization (single source shortest path) and
+edge-oriented (maximal independent set) -- and five graph-related business areas
+cybersecurity, medical informatics, data enrichment, social networks, and
+symbolic networks.
 
-%\paragraph{gtools} Projects nauty and Traces~\cite{gtools} are programs for computing automorphism groups of graphs and digraphs~\cite{McKay201494}; they can also produce a canonical label.
-In the respective package there is also suite of programs called gtools which involve generators for non-isomorphic graphs, bipartite graphs, digraphs, and multigraphs.
+\paragraph{BTER} BTER (Block Two-Level
+Erd\"{o}-R\'{e}ny)~\cite{kolda2014scalable} is a graph generator based on the
+creation of multiple Erd\"{o}s-R\'{e}ny graphs with different connection
+probabilities, connected randomly between them. As a main feature, BTER is able
+to reproduce input degree distributions and average clustering
+coefficient per degree values. The generators starts by grouping the vertices
+by degree $d$, and forming groups of size $d+1$ degree $d$ nodes. Then, these
+groups are assigned an internal edge probability in order to match the observed
+average clustering coefficient of the nodes of such degree. Based on this
+probability, for each node, the excess degree is computed (the degree that in
+expectation will not be realized internally in the group) and used to connect
+nodes from different groups at random. The authors describe a highly scalable
+MapReduce based implementation that is capable of generating large graphs (with
+billions of nodes) in reasonable amounts of time.
+
+\paragraph{Darwini} Darwini~\cite{edunov2016darwini} is an extension of BTER
+designed to run on Vertex Centric computing frameworks like
+Pregel~\cite{malewicz2010pregel} or Apache Giraph~\cite{ching2015one}, with the
+additional feature that it is more accurate when reproducing the clustering
+coefficient of the input graph. Instead of just focusing on the average
+clustering coefficient for each degree, Darwini is able to model the clustering
+coefficient distribution per degree. It achieves this by grouping the vertices
+of the graph into buckets by the expected number of closed triangles they need
+to close in order to attain the their expected clustering coefficient, which is
+sampled from the input distributions. Then, the vertices in each bucket are
+connected randomly with a probability that would produce, in expectation, the
+desired number of triangles for such bucket. Then, as in BTER, the excess degree
+is used to connect the different buckets. The authors report that Darwini is
+able to generate graphs with billions and even trillions of edges.
+
+%\paragraph{gtools} Projects nauty and Traces~\cite{gtools} are programs for
+%computing automorphism groups of graphs and digraphs~\cite{McKay201494}; they
+%can also produce a canonical label. In the respective package there is also
+%suite of programs called gtools which involve generators for non-isomorphic
+%graphs, bipartite graphs, digraphs, and multigraphs.

### 2018-06-07 introduction.tex
pass on intro

@@
 
-One of the most popular data structures in the world of computer science are graphs.
-They enable to represent complex information in a simple and yet powerful way supported by a strong mathematical background.
+%One of the most popular data structures in the world of computer science are graphs. 
+Graphs are ubiquitous data structures that span a wide array of disciplines
+and are subject of study in several subfields of computer science.
+Nowadays, due to the dawn of numerous tools and applications manipulating
+graphs, they are adopted as a rich data model in many data science use
+cases involving disparate domain knowledge, mathematical foundations and
+computer science. Interconnected data is oftentimes used to encode domain-specific 
+use cases, such as recommendation networks, social networks,
+protein-to-protein interactions, geolocation networks, and fraud detection analysis networks, to
+name a few.   
+% ANGELA: I do not think we should cite Neo4J, which is a graph database. 
+%They enable to represent complex information in a simple and yet powerful way supported by a strong mathematical background.
 With the dawn of the new millennium which brought numerous novel technologies and applications, the graphs have become even more popular.
@@
 
-In general, we can distinguish two types of graph data sets: (1) a single large graph (possibly with several components), such as social networks  or Linked Data graphs, and (2) a large set of small graphs, such as chemical compounds\footnote{\url{https://pubchem.ncbi.nlm.nih.gov/}} or linguistics syntax trees\footnote{\url{https://catalog.ldc.upenn.edu/ldc99t42}}.
+In general, we can distinguish between two broad types of graph data sets: (1) a single large graph (possibly with several components), such as social networks  or Linked Data graphs, and (2) a large set of small graphs, such as chemical compounds\footnote{\url{https://pubchem.ncbi.nlm.nih.gov/}} or linguistics syntax trees\footnote{\url{https://catalog.ldc.upenn.edu/ldc99t42}}.
 Naturally, the algorithms used in theses two classes differ a lot~\cite{DBLP:books/igi/Sakr2011}.
 In the former case we can search, e.g., for communities and their features or shortest paths, while in the latter case we usually query for supergraphs, subgraphs or graphs similar to a given graph pattern.
-Also, as in the other fields, quite often the respective real-world data is not publicly available (or simply does not exist when a particular method for manipulation with the data is proposed).
-As a consequence, also in the world of graphs there has appeared a number of graph data generators which enable to  reproduce the respective real-world linking properties and gauge the effectiveness of a particular algorithm.
+Also, as in the other fields, quite often the respective real-world data is not publicly available (or simply does not exist when a particular method for data manipulation is proposed).
+Even in the cases in which real data is abundant, many algorithms and techniques need to be tested on various order of magnitudes of the graph sizes thus leading to the inception of 
+configurable graph generators that reproduce real-world graph properties and provide unique tuning opportunities for 
+algorithms and tools handling such data. 
+%As a consequence, also in the world of graphs there has appeared a number of graph data generators which enable to  reproduce the respective real-world linking properties and gauge the effectiveness of a particular algorithm.
 
-In this survey we provide a comprehensive overview of the state-of-the-art graph generators by focusing on those that are pertinent and suitable for data science tasks.
+In this survey, we provide a comprehensive overview of the state-of-the-art graph generators by focusing on those that are pertinent and suitable for data science tasks.
 Our aim is to cover a wide range of currently popular areas of graph data processing.
@@
 
-To conclude the comparative study, we discuss open challenges and missing features of graph generators in view of the evolution of data science.
+To conclude the comparative study, we discuss open challenges and missing features of graph generators in view of identifying future challenges in data science.
 

### 2018-06-07 introduction.tex
pass on prior work

@@
 
-To the best of our knowledge, our work is the first surveying the broad landscape of graph data generators spanning different Big Data applications and
+To the best of our knowledge, our work is the first surveying the broad
+landscape of graph data generators spanning different data science applications and
 targeting diverse computer science subfields. In particular, we cover graph database
@@
 inherently data-driven and not meant to serve the purpose of letting any
-researcher or practitioner interested in Big Data be able to make a guided
+researcher or practitioner interested in data science make a guided
 choice of the desired

### 2018-06-08 introduction.tex

@@
 In the former case we can search, e.g., for communities and their features or shortest paths, while in the latter case we usually query for supergraphs, subgraphs or graphs similar to a given graph pattern.
-Also, as in the other fields, quite often the respective real-world data is not publicly available (or simply does not exist when a particular method for data manipulation is proposed).
+Also, as in the other fields, quite often the respective real-world graph data is not publicly available (or simply does not exist when a particular method for data manipulation is proposed).
 Even in the cases in which real data is abundant, many algorithms and techniques need to be tested on various order of magnitudes of the graph sizes thus leading to the inception of
@@
 
-To conclude the comparative study, we discuss open challenges and missing features of graph generators in view of identifying future challenges in data science.
+To conclude the comparative study and provide a comprehensive view of the field,  we also discuss open challenges and missing features of graph generators in view of identifying future challenges in data science.
 
-\paragraph*{Contributions} The key contributions of this survey are as follows:
-\begin{itemize}
-  \item ...
-\end{itemize}
-
-...
+\paragraph*{Contributions} Our survey reviews the representatives of graph data generators and summarizes their major features.
+The comprehensive review and analysis make this paper useful for motivating new graph data generation techniques as well as serving as a technical reference for selecting suitable solutions.
+In particular, the introductory categorization and comparative study enables the reader to quickly get his/her bearings in the field and identify a subset of generators of his/her interest.
+Since we do not limit the survey to a particular area of graph data management,  the reader can get a broader scope in the field.
+Hence, while practitioners can find a solution in another previously unexpected area, researchers can identify new target areas or exploit successful results in new fields.
+Last but not least, we identify general open problems of graph data synthesis and indicate possible solutions to show that it still forms a challenging and promising research area.
 
@@
 
-\paragraph*{Outline} The rest of the text is structured as follows: ...
-% In Section~\ref{sec:preliminaries} we provide a brief introduction to graph theory and related terms.
-% In Section~\ref{sec:classification} we classify the current Big graph Data applications.
-% In Section~\ref{sec:generators} we introduce the existing graph data generators in the context of the proposed categories and their main features.
-% Section~\ref{sec:comparison} provides comparison of the described generators.
-% In Section~\ref{sec:challenges} we discuss challenges and open problems. And in Section~\ref{sec:conclusion} we conclude.
+\paragraph*{Outline} The rest of the text is structured as follows: 
+In Section~\ref{sec:comparison} we provide the opening categorization and comparison of the generators.
+In Section~\ref{sec:generators} we overview the existing graph data generators and their main features in the frame of the proposed categories.
+In Section~\ref{sec:challenges} we discuss challenges and open problems of graph data synthesis and in Section~\ref{sec:conclusion} we conclude.

### 2018-06-08 generators_SocialNetworks.tex
Removed LFR from social networks

@@
 
-On-line social networks, like Facebook, Twitter, or LinkedIn, have become a phenomenon used by billions of people every day and thus providing extremely useful information for various domains.
-However, an analysis of such type of graph has to cope with two problems: (1) availability of the data and (2) privacy of the data.
-Hence, data generators which provide realistic synthetic social network graphs are in great demand.
+On-line social networks, like Facebook, Twitter, or LinkedIn, have become a
+phenomenon used by billions of people every day and thus providing extremely
+useful information for various domains. However, an analysis of such type of
+graph has to cope with two problems: (1) availability of the data and (2)
+privacy of the data. Hence, data generators which provide realistic synthetic
+social network graphs are in great demand.
 
-Analyses of social networks identify their various specific features~\cite{Chakrabarti:2006:GML:1132952.1132954}.
-For example, the social graph has high \emph{clustering coefficient}, i.e.
-the degree of transitivity of a graph.
-Or, its diameter, i.e.
-the minimum number of hops in which some fraction (e.g., 90\%) of all connected pairs of nodes can reach each other, is usually low due to weak ties joining faraway cliques.
-Another important aspect of social networks is the community effect.
-A detailed study of structure of communities in 70 real-world networks is provided, e.g., in paper~\cite{Leskovec:2008:SPC:1367497.1367591}.
-Authors of paper~\cite{Prat-Perez:2014:CSS:2621934.2621942} analyze the structure of communities (clustering coefficient, triangle participation ratio, bridges, diameter, conductance and size) in both real graphs and output by existing graph generators LFR~\cite{PhysRevE.78.046110} and the LDBC-SNB~\cite{Erling:2015:LSN:2723372.2742786}.
-%They discover that communities found among different graphs follow quite similar distributions and that communities in a single graph have diverse nature, and are difficult to fit with a single model.
+Analyses of social networks identify their various specific
+features~\cite{Chakrabarti:2006:GML:1132952.1132954}. For example, the social
+graph has high \emph{clustering coefficient}, i.e. the degree of transitivity of
+a graph. Or, its diameter, i.e. the minimum number of hops in which some
+fraction (e.g., 90\%) of all connected pairs of nodes can reach each other, is
+usually low due to weak ties joining faraway cliques. Another important aspect
+of social networks is the community effect. A detailed study of structure of
+communities in 70 real-world networks is provided, e.g., in
+paper~\cite{Leskovec:2008:SPC:1367497.1367591}. Authors of
+paper~\cite{Prat-Perez:2014:CSS:2621934.2621942} analyze the structure of
+communities (clustering coefficient, triangle participation ratio, bridges,
+diameter, conductance and size) in both real graphs and output by existing graph
+generators LFR~\cite{PhysRevE.78.046110} and the
+LDBC-SNB~\cite{Erling:2015:LSN:2723372.2742786}. %They discover that communities
+found among different graphs follow quite similar distributions and that
+communities in a single graph have diverse nature, and are difficult to fit with
+a single model.
 
 Network generators can be categorized into statistical and agent-based.
-\emph{Statistical approaches}~\cite{PhysRevE.78.046110,Yao2011,Armstrong:2013:LDB:2463676.2465296,Pham2013,Sukthankar-SocialInfo2014,Erling:2015:LSN:2723372.2742786,Nettleton2016} focus on reproducing aspects of the network statistics.
-In \emph{agent-based approaches}~\cite{Barrett:2009:GAL:1995456.1995598,Bernstein:2013:SAS:2499604.2499609}  the networks are constructed by directly simulating the agents' social choices.
+\emph{Statistical
+approaches}~\cite{PhysRevE.78.046110,Yao2011,Armstrong:2013:LDB:2463676.2465296,Pham2013,Sukthankar-SocialInfo2014,Erling:2015:LSN:2723372.2742786,Nettleton2016}
+focus on reproducing aspects of the network statistics. In \emph{agent-based
+approaches}~\cite{Barrett:2009:GAL:1995456.1995598,Bernstein:2013:SAS:2499604.2499609}
+the networks are constructed by directly simulating the agents' social choices.
 
-\paragraph{LFR} Lancichinetti, Fortnato and Radicchi (hence LFR)~\cite{PhysRevE.78.046110} develop a class of benchmark graphs whose nodes participate in internal community structures.
-The benchmark models directed and weighted real-world networks (e.g., social networks) containing overlapping communities of different sizes.
-The algorithm assumes that both the degree and the community size distributions are power laws.
-Each node shares a fraction $(1 - \mu)$ of its links with the other nodes of its community and a fraction $\mu$ with the other nodes of the network, where $\mu$ is called \emph{mixing parameter}.
-The sizes of the communities are taken from a power law distribution such that the sum of all sizes equals the number of nodes of the graph.
-The generation process starts with an empty graph and incrementally fills in the adjacency matrix by obeying the described constraints.
+%\paragraph{LFR} Lancichinetti, Fortnato and Radicchi (hence
+%LFR)~\cite{PhysRevE.78.046110} develop a class of benchmark graphs whose nodes
+%participate in internal community structures. The benchmark models directed and
+%weighted real-world networks (e.g., social networks) containing overlapping
+%communities of different sizes. The algorithm assumes that both the degree and
+%the community size distributions are power laws. Each node shares a fraction $(1
+%- \mu)$ of its links with the other nodes of its community and a fraction $\mu$
+%with the other nodes of the network, where $\mu$ is called \emph{mixing
+%parameter}. The sizes of the communities are taken from a power law distribution
+%such that the sum of all sizes equals the number of nodes of the graph. The
+%generation process starts with an empty graph and incrementally fills in the
+%adjacency matrix by obeying the described constraints.
 
-\paragraph{Realistic Social Network} Paper~\cite{Barrett:2009:GAL:1995456.1995598} focuses on construction of realistic social networks using a combination of public and private data sets and large-scale agent based techniques.
-The process works as follows: Step 1 creates a synthetic population by integrating databases from commercial and public sources.
-In Step 2, a set of activity templates are determined.
-Each synthetic individual is assigned a 24-hour activity sequence including geo-locations for each activity.
+\paragraph{Realistic Social Network}
+Paper~\cite{Barrett:2009:GAL:1995456.1995598} focuses on construction of
+realistic social networks using a combination of public and private data sets
+and large-scale agent based techniques. The process works as follows: Step 1
+creates a synthetic population by integrating databases from commercial and
+public sources. In Step 2, a set of activity templates are determined. Each
+synthetic individual is assigned a 24-hour activity sequence including
+geo-locations for each activity.
 
-To demonstrate the approach, the authors develop a synthetic population for the United States that models every individual in the population.
-The synthetic population is a set of geographically located people and households.
-Household structure and demographics are derived from U.S.
-Census data.
-The activity templates are  based on several thousand responses to an activity or time-use survey.
-Demographic information for each person and location, a minute-by-minute schedule of each person's activities, and the locations where these activities take place is generated by a combination of simulation and data fusion techniques.
-This information is captured by a dynamic social contact network.
+To demonstrate the approach, the authors develop a synthetic population for the
+United States that models every individual in the population. The synthetic
+population is a set of geographically located people and households. Household
+structure and demographics are derived from U.S. Census data. The activity
+templates are  based on several thousand responses to an activity or time-use
+survey. Demographic information for each person and location, a minute-by-minute
+schedule of each person's activities, and the locations where these activities
+take place is generated by a combination of simulation and data fusion
+techniques. This information is captured by a dynamic social contact network.
 
@@
 
-\paragraph{Linkage vs.
-Activity Graphs} Paper~\cite{Yao2011} distinguishes two types of social network graphs -- the \emph{linkage graph}, where nodes stand for the people in the social network and edges are their friendship links, and the \emph{activity graph}, where nodes also stand for the people but edges stand for their interactions.
-On the basis of analysis of Flickr\footnote{\url{https://www.flickr.com/}} social links and Epinions\footnote{\url{http://www.epinions.com/}} network of user interactions, the authors discover that they both exhibit power-law degree distribution, high clustering coefficient (community structure), and small diameter; also regarding the dynamic properties they both follow densification law and relatively stable clustering coefficient over time.
-However, the authors do not observe diameter shrinking in Epinions?
-activity graph and there is a difference in degree correlation (how frequently nodes with similar degrees connect to each other).
-Namely linkage graphs have positive degree correlation whereas activity graphs show neutral degree correlation.
+\paragraph{Linkage vs. Activity Graphs} Paper~\cite{Yao2011} distinguishes two
+types of social network graphs -- the \emph{linkage graph}, where nodes stand
+for the people in the social network and edges are their friendship links, and
+the \emph{activity graph}, where nodes also stand for the people but edges stand
+for their interactions. On the basis of analysis of
+Flickr\footnote{\url{https://www.flickr.com/}} social links and
+Epinions\footnote{\url{http://www.epinions.com/}} network of user interactions,
+the authors discover that they both exhibit power-law degree distribution, high
+clustering coefficient (community structure), and small diameter; also regarding
+the dynamic properties they both follow densification law and relatively stable
+clustering coefficient over time. However, the authors do not observe diameter
+shrinking in Epinions? activity graph and there is a difference in degree
+correlation (how frequently nodes with similar degrees connect to each other).
+Namely linkage graphs have positive degree correlation whereas activity graphs
+show neutral degree correlation.
 
-With regards to the findings, the proposed generator focusses on linkage graphs with positive degree correlation.
-For this purpose it extends the ``forest fire'' spreading process algorithm~\cite{Leskovec:2005:GOT:1081870.1081893} with link symmetry.
-It has two parameters -- the \emph{burning probability} $P_b$ which is in charge of the burning process, and the \emph{symmetry probability} $P_s$ which indicates backward linking from old nodes to new ones.
-$P_b$ controls a BFS-based forward burning process.
-The fire burns increasingly fiercely with $P_b$ approaching 1.
-Meanwhile, $P_s$ adds fuel to the fire as it brings more links.
-It gives chances for big nodes
-to connect back to big nodes.
+With regards to the findings, the proposed generator focusses on linkage graphs
+with positive degree correlation. For this purpose it extends the ``forest
+fire'' spreading process algorithm~\cite{Leskovec:2005:GOT:1081870.1081893} with
+link symmetry. It has two parameters -- the \emph{burning probability} $P_b$
+which is in charge of the burning process, and the \emph{symmetry probability}
+$P_s$ which indicates backward linking from old nodes to new ones. $P_b$
+controls a BFS-based forward burning process. The fire burns increasingly
+fiercely with $P_b$ approaching 1. Meanwhile, $P_s$ adds fuel to the fire as it
+brings more links. It gives chances for big nodes to connect back to big nodes.
 
-\paragraph{LinkBench} The LinkBench benchmark~\cite{Armstrong:2013:LDB:2463676.2465296} aims to predict the performance of a database when used for persistent storage of Facebook?s production data.
-The benchmark considers true Big Data and related problems with sharding, replication etc.
-The social graph at Facebook comprises objects (nodes with IDs, version, timestamp and data) and associations (directed edges, pairs of node IDs, with visibility, timestamp and data).
-The size of the target graph is the number of nodes.
-Graph edges are generated concurrently with graph nodes during bulk loading.
-The node ID space is divided into chunks based on the ID of the source node which  are processed in parallel.
-The edges of the graph are generated in accordance with the results of analysis of real-world Facebook data (such as outdegree distribution).
-A workload corresponding to 10 graph operations (such as insert object, count the number of associations etc.) and their respective characteristics over the real-world data is generated for the synthetic data.
+\paragraph{LinkBench} The LinkBench
+benchmark~\cite{Armstrong:2013:LDB:2463676.2465296} aims to predict the
+performance of a database when used for persistent storage of Facebook?s
+production data. The benchmark considers true Big Data and related problems with
+sharding, replication etc. The social graph at Facebook comprises objects (nodes
+with IDs, version, timestamp and data) and associations (directed edges, pairs
+of node IDs, with visibility, timestamp and data). The size of the target graph
+is the number of nodes. Graph edges are generated concurrently with graph nodes
+during bulk loading. The node ID space is divided into chunks based on the ID of
+the source node which  are processed in parallel. The edges of the graph are
+generated in accordance with the results of analysis of real-world Facebook data
+(such as outdegree distribution). A workload corresponding to 10 graph
+operations (such as insert object, count the number of associations etc.) and
+their respective characteristics over the real-world data is generated for the
+synthetic data.
 
-\paragraph{S3G2} The Scalable Structure-correlated Social Graph Generator (S3G2)~\cite{Pham2013} is a general framework which  generates a directed labeled graph, where the nodes are objects with property values, and their structure is determined by the class a node belongs to.
-S3G2 does not aim at generating near real-world data, but at generating synthetic graphs which a correlated structure.
-It causes that the probability to choose a certain property value (from a pre-defined dictionary), or the probability to connect two nodes with an edge are influenced by existing data values.
-For example, it is possible to have a correlated degree distribution, from which the degree of each node is generated, correlated with properties of node.
-Hence the generator can ensure that, e.g., people with many friends in a social network will typically post more pictures than people with few friends, i.e., the amount of friend nodes influences the amount of posted comment and picture nodes.
+\paragraph{S3G2} The Scalable Structure-correlated Social Graph Generator
+(S3G2)~\cite{Pham2013} is a general framework which  generates a directed
+labeled graph, where the nodes are objects with property values, and their
+structure is determined by the class a node belongs to. S3G2 does not aim at
+generating near real-world data, but at generating synthetic graphs which a
+correlated structure. It causes that the probability to choose a certain
+property value (from a pre-defined dictionary), or the probability to connect
+two nodes with an edge are influenced by existing data values. For example, it
+is possible to have a correlated degree distribution, from which the degree of
+each node is generated, correlated with properties of node. Hence the generator
+can ensure that, e.g., people with many friends in a social network will
+typically post more pictures than people with few friends, i.e., the amount of
+friend nodes influences the amount of posted comment and picture nodes.
 
-The data generation process starts with generating a number of nodes with property values generated according to specified property value correlations and then adding respective edges according to specified correlation dimensions.
-It has multiple phases, each focusing on one correlation dimension.
-Each pass along one correlation dimension is a Map phase in which data is generated, followed by a Reduce phase that sorts the data along the correlation dimension in the next pass.
-A heuristic observation that ``the probability that two nodes are connected is typically skewed with respect to some similarity between the nodes'' enables to focus only on sliding window of most probable candidates.
+The data generation process starts with generating a number of nodes with
+property values generated according to specified property value correlations and
+then adding respective edges according to specified correlation dimensions. It
+has multiple phases, each focusing on one correlation dimension. Each pass along
+one correlation dimension is a Map phase in which data is generated, followed by
+a Reduce phase that sorts the data along the correlation dimension in the next
+pass. A heuristic observation that ``the probability that two nodes are
+connected is typically skewed with respect to some similarity between the
+nodes'' enables to focus only on sliding window of most probable candidates.
 
-The core idea of the framework is demonstrated using an example of a social network (consisting of persons and social activities).
-The dictionaries for property values are inspired by DBpedia and provided with 20 property value correlations.
-The edges are generated according to 3 correlation dimensions.
+The core idea of the framework is demonstrated using an example of a social
+network (consisting of persons and social activities).  The dictionaries for
+property values are inspired by DBpedia and provided with 20 property value
+correlations. The edges are generated according to 3 correlation dimensions.
 
-\paragraph{Cloning of Social Networks} Paper~\cite{Sukthankar-SocialInfo2014} introduces a synthetic network generator designed for cloning social network statistics of an existing dataset.
-The network starts with a small number of nodes, and new nodes are added until the network reaches the required number.
-It has two basic parameters: homophily and link density.
-A high \emph{homophily} value indicates that links are more likely to be formed between nodes with the same label; these labels can be viewed as being equivalent to community membership.
+\paragraph{Cloning of Social Networks} Paper~\cite{Sukthankar-SocialInfo2014}
+introduces a synthetic network generator designed for cloning social network
+statistics of an existing dataset. The network starts with a small number of
+nodes, and new nodes are added until the network reaches the required number. It
+has two basic parameters: homophily and link density. A high \emph{homophily}
+value indicates that links are more likely to be formed between nodes with the
+same label; these labels can be viewed as being equivalent to community
+membership.
 
-Attribute Synthetic Generator (ASG) is a network generator for reproducing the node feature distribution of standard networks and rewiring the network to preferentially connect nodes that exhibit a high feature similarity.
-The network is initialized with a group of three nodes, and new nodes and links are added to the network based on link density, homophily, and feature similarity.
-As new nodes are created, their labels are assigned based on the prior label distribution.
-After the network has reached the same number of nodes as the original social media dataset, each node initially receives a random attribute assignment.
-Then a stochastic optimization
-process is used to move the initial assignments closer to the target distribution extracted from social media dataset using the Particle Swarm Optimization algorithm.
-The tuned attributes are then used to add additional links to the network based on the feature similarity parameter -- a source node is selected randomly and connected to the most similar node.
+Attribute Synthetic Generator (ASG) is a network generator for reproducing the
+node feature distribution of standard networks and rewiring the network to
+preferentially connect nodes that exhibit a high feature similarity. The network
+is initialized with a group of three nodes, and new nodes and links are added to
+the network based on link density, homophily, and feature similarity. As new
+nodes are created, their labels are assigned based on the prior label
+distribution. After the network has reached the same number of nodes as the
+original social media dataset, each node initially receives a random attribute
+assignment. Then a stochastic optimization process is used to move the initial
+assignments closer to the target distribution extracted from social media
+dataset using the Particle Swarm Optimization algorithm. The tuned attributes
+are then used to add additional links to the network based on the feature
+similarity parameter -- a source node is selected randomly and connected to the
+most similar node.
 
-Multi-Link Generator (MLG) further  uses link co-occurrence statistics from the original dataset to create a multiplex network.
-MLG uses the same network growth process as ASG..
-Based on the link density parameter, either a new node is generated with a label based on the label distribution of the target dataset or a new link is created between two existing nodes.
+Multi-Link Generator (MLG) further  uses link co-occurrence statistics from the
+original dataset to create a multiplex network. MLG uses the same network growth
+process as ASG.. Based on the link density parameter, either a new node is
+generated with a label based on the label distribution of the target dataset or
+a new link is created between two existing nodes.
 
-\paragraph{LDBC SNB} The Social Network Benchmark (SNB)~\cite{Erling:2015:LSN:2723372.2742786} provided by LDBC consists of three distinct benchmarks on a common dataset corresponding to three different workloads.
-SNB models a social network akin to Facebook.
-The dataset consists of persons and a friendship network that connects them; whereas the majority of the data is in the messages that these persons post in discussion trees on their forums.
-The three query workloads involve: (1) SNB-Interactive (i.e., complex read-only queries, that touch a significant amount of data), (2) SNB-BI (which accesses a large percentage of all entities in the dataset and groups these in various dimensions), and (3) SNB-Algorithms (i.e., graph analysis algorithms, including PageRank, Community Detection, Clustering and Breadth First Search).
-The graph generator realizes power laws, uses skewed value distributions, and introduces plausible correlations between property values and graph structures.
+\paragraph{LDBC SNB} The Social Network Benchmark
+(SNB)~\cite{Erling:2015:LSN:2723372.2742786} provided by LDBC consists of three
+distinct benchmarks on a common dataset corresponding to three different
+workloads. SNB models a social network akin to Facebook. The dataset consists of
+persons and a friendship network that connects them; whereas the majority of the
+data is in the messages that these persons post in discussion trees on their
+forums. The three query workloads involve: (1) SNB-Interactive (i.e., complex
+read-only queries, that touch a significant amount of data), (2) SNB-BI (which
+accesses a large percentage of all entities in the dataset and groups these in
+various dimensions), and (3) SNB-Algorithms (i.e., graph analysis algorithms,
+including PageRank, Community Detection, Clustering and Breadth First Search).
+The graph generator realizes power laws, uses skewed value distributions, and
+introduces plausible correlations between property values and graph structures.
 It is implemented on top of Hadoop to provide scalability.
 
-The generated data have become a part if several graph benchmarks, such as GraphBIG~\cite{Nai:2015:GUG:2807591.2807626}.
+The generated data have become a part if several graph benchmarks, such as
+GraphBIG~\cite{Nai:2015:GUG:2807591.2807626}.
 
-\paragraph{Towards More Realistic Data} The authors of paper~\cite{Nettleton2016} claim that the main body of existing work lies in topology generation which approximate the characteristics of a real social network (such as a small graph diameter, small average path length, skew degree distribution, and community structures), however without data.
-Hence, they implement a general stochastic modeling system which allows the users to populate a graph topology with data.
-The approach has three steps: (1) topology generation (using R-MAT) plus community identification using the Louvain method~\cite{1742-5468-2008-10-P10008} or usage of a real-world topology from SNAP\footnote{\url{https://snap.stanford.edu/data/}}, (2) data definition (following distribution profiles, attribute value definitions, using a parameterizable set of data propagation rules and affinities), and (3) data population.
+\paragraph{Towards More Realistic Data} The authors of
+paper~\cite{Nettleton2016} claim that the main body of existing work lies in
+topology generation which approximate the characteristics of a real social
+network (such as a small graph diameter, small average path length, skew degree
+distribution, and community structures), however without data. Hence, they
+implement a general stochastic modeling system which allows the users to
+populate a graph topology with data. The approach has three steps: (1) topology
+generation (using R-MAT) plus community identification using the Louvain
+method~\cite{1742-5468-2008-10-P10008} or usage of a real-world topology from
+SNAP\footnote{\url{https://snap.stanford.edu/data/}}, (2) data definition
+(following distribution profiles, attribute value definitions, using a
+parameterizable set of data propagation rules and affinities), and (3) data
+population.

### 2018-06-23 generators_LinkedData.tex
Sherif Changes

@@
 
-\paragraph{LUBM} The use-case driven Lehigh University Benchmark (LUBM)~\cite{Guo2005158} considers the university domain.
-The ontology defines 43 classes and 32 properties, including 25 object properties and 7 datatype properties.
+\paragraph{LUBM} The use-case driven Lehigh University Benchmark (LUBM)\footnote{\url{http://swat.cse.lehigh.edu/projects/lubm/}} considers the university domain.
+The ontology defines 43 classes and 32 properties, including 25 object properties and 7 datatype properties~\cite{Guo2005158}.
 The LUBM benchmark also provides 14 test queries.
@@
 12 test queries were designed for  the benchmark data.
-
-Another extension of LUBM, the University Ontology Benchmark (UOBM)~\cite{Ma:2006:TCO:2094613.2094629}, focuses on two aspects: (1) usage of all constructs of OWL Lite and OWL DL~\cite{owl} and (2) lack of necessary links between the generated data which thus form isolated graphs.
+Another extension of LUBM, the University Ontology Benchmark (UOBM)\footnote{\url{https://www.cs.ox.ac.uk/isg/tools/UOBMGenerator/}}, focuses on two aspects: (1) usage of all constructs of OWL Lite and OWL DL~\cite{owl} and (2) lack of necessary links between the generated data which thus form isolated graphs~\cite{Ma:2006:TCO:2094613.2094629}.
 In the former case the original ontology is replaced by the two types of extended versions from which the user can choose.
@@
 
-\paragraph{IIMB} Contrary to the previous work, paper~\cite{Ferrara08OM} proposes the ISLab Instance Matching Benchmark (IIMB) for the problem of instance matching defined as follows: Given two instances $i_1$ and $i_2$, belonging to the same ontology or to different ontologies, instance matching is defined as a function $Im(i_1, i_2) \rightarrow \{0, 1\}$,  where $1$ denotes the fact that $i_1$ and $i_2$ are referred to the same real-world object and $0$ denotes the fact that $i_1$ and $i_2$ are referred to different objects.
+\paragraph{IIMB} Contrary to the previous work, ~\cite{Ferrara08OM} proposed the ISLab Instance Matching Benchmark (IIMB)\footnote{\url{http://www.ics.forth.gr/isl/BenchmarksTutorial/}} for the problem of instance matching defined as follows: Given two instances $i_1$ and $i_2$, belonging to the same ontology or to different ontologies, instance matching is defined as a function $Im(i_1, i_2) \rightarrow \{0, 1\}$,  where $1$ denotes the fact that $i_1$ and $i_2$ are referred to the same real-world object and $0$ denotes the fact that $i_1$ and $i_2$ are referred to different objects.
 It targets the domain of movie data which contains 15 named classes, 5 object properties and 13 datatype properties.
 The data are extracted from IMDb\footnote{\url{http://www.imdb.com/}}.
-
 The data generator corresponds to a data modifier which simulates differences between the data.
@@
 
-\paragraph{BSBM} The Berlin SPARQL Benchmark (BSBM)~\cite{Bizer09theberlin}, also use-case driven, involves an e-commerce domain, where types Product, Offer and Vendor are used to model the relationships between products and the vendors offering them, while types Person and Review are used to model the relationship between users and product reviews these users write.
-The benchmark also comes with 12 queries and 2 query mixes (sequences of the 12 queries) emulating the search and navigation pattern of a consumer looking for a product.
+\paragraph{BSBM} The Berlin SPARQL Benchmark (BSBM)\footnote{\url{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}}, models an e-commerce domain where types Product, Offer and Vendor are used to model the relationships between products and the vendors offering them, while types Person and Review are used to model the relationship between users and product reviews these users write~\cite{Bizer09theberlin}.
+The benchmark comes with 12 queries and 2 query mixes (sequences of the 12 queries) emulating the search and navigation pattern of a consumer looking for a product.
 The data generator supports creation of arbitrarily large datasets using the number of products $n$ as scale factor which further influences also other characteristics of the data, such as, e.g., the depth of type hierarchy of products (defined as $d = round(log_{10}(n))/2 + 1$), branching factor ($bfr = 2 \times round(log_{10}(n))$), the number of product features (having $lowerBound = 35 \times i / (d \times (d+1)/2 ?
@@
 1)$) etc.
-
 BSBM can output two representations -- an RDF representation and a purely relational representation.
-Thus BSBM also defines an SQL~\cite{sql} representation of the queries.
+Thus, BSBM also defines an SQL~\cite{sql} representation of the queries.
 This allows comparison of SPARQL~\cite{sparql} results with the performance of traditional RDBMSs.
 
-\paragraph{SP$^2$Bench} The SP$^2$Bench is a language-specific benchmark~\cite{Schmidt2010} which uses the DBLP~\cite{dblp} as a domain for the dataset.
+\paragraph{SP$^2$Bench} The SP$^2$Bench\footnote{\url{http://dbis.informatik.uni-freiburg.de/forschung/projekte/SP2B/}} is a language-specific benchmark~\cite{Schmidt2010} which uses the DBLP~\cite{dblp} as a domain for the dataset.
 %, so the types involve Person, Inproceedings, Article etc.
@@
 The structuredness is then expressed as a weighted sum of share of set properties of each type, whereas higher weights are assigned to types with more instances.
-
 The authors show that structuredness of the chosen benchmarks is fixed, whereas real-world RDF datasets lie in currently untested parts of the spectrum.
@@
 
-\paragraph{DBPSB} DBpedia SPARQL Benchmark (DBPSB)~\cite{Morsey2011,Morsey:2012:UBR:2900929.2901031} proposed at the University of Leipzig is based on queries that were issued by humans and applications
-against existing RDF data.
+\paragraph{DBPSB} DBpedia SPARQL Benchmark (DBPSB)\footnote{\url{http://aksw.org/Projects/DBPSB.html}} proposed at the University of Leipzig is based on queries that were issued by humans and applications
+against existing RDF data~\cite{Morsey2011,Morsey:2012:UBR:2900929.2901031}.
 In addition, the authors argue that benchmarks like LUBM, BSBM, or SP$^2$Bench resemble relational database benchmarks involving relational data structures with few and homogeneously structured classes, whereas RDF knowledge bases are increasingly heterogeneous (e.g., DBpedia version 3.6, for example, contains 289,016 classes of which 275 classes belong
@@
 Hence, they propose a generic SPARQL benchmark creation methodology based on: a flexible data generation mimicking an input data source, query-log mining, clustering, and SPARQL feature analysis.
-
 The proposed dataset creation process starts with an input dataset.
@@
 
-\paragraph{LODIB} The Linked Open Data Integration Benchmark (LODIB)~\cite{DBLP:conf/www/RiveroSBR12} aims to reflect the real-world heterogeneities that exist on the Web of Data in order to enable testing of Linked Data translation systems.
+\paragraph{LODIB} The Linked Open Data Integration Benchmark (LODIB)\footnote{\url{http://lodib.wbsg.de/}} has been designed with the aim to reflect the real-world heterogeneities that exist on the Web of Data in order to enable testing of Linked Data translation systems~\cite{DBLP:conf/www/RiveroSBR12}.
 It provides a catalogue of 15 data translation patterns (e.g., rename class, remove language tag etc.), each of which is a common data translation problem in the context of Linked Data.
@@
 
-\paragraph{SIB} The authors of the Social Network Intelligence BenchMark (SIB)~\cite{sib} claim that current benchmarks are limited in representing the real RDF datasets and are mostly relational-like.
-Hence, they propose a benchmark for challenging query processing over real graphs.
+\paragraph{SIB} The authors of the Social Network Intelligence BenchMark (SIB)\footnote{\url{https://www.w3.org/wiki/Social_Network_Intelligence_BenchMark}} claim that current benchmarks are limited in representing the real RDF datasets and are mostly relational-like.
+Hence, they propose a benchmark for challenging query processing over real graphs~\cite{sib}.
 It simulates an RDF backend of a social network site, in which users and their interactions form an social graph of social activities such as writing posts, posting comments, creating/managing groups, etc.
@@
 
-\paragraph{Geographica} The authors of benchmark Geographica~\cite{DBLP:conf/semweb/GarbisKK13} target the area of geospatial data and respective SPARQL extensions GeoSPARQL and stSPARQL.
+\paragraph{Geographica} The Geographica benchmark \footnote{\url{http://geographica.di.uoa.gr/}} has been designed target the area of geospatial data~\cite{DBLP:conf/semweb/GarbisKK13} and respective SPARQL extensions GeoSPARQL~\cite{battle2012enabling} and stSPARQL~\cite{koubarakis2010modeling}.
 The benchmark involves (1) a real-world workload based on publicly available linked data sets covering a range of geometry types (e.g., points, lines, polygons) and (2) a synthetic workload.
@@
 
-\paragraph{WatDiv} The Waterloo SPARQL Diversity Test Suite (WatDiv)~\cite{Aluc:2014:DST:2717213.2717229} developed at the University of Waterloo provides stress testing tools to address the observation that existing SPARQL benchmarks are not suitable for testing systems for diverse queries and varied workloads.
-The authors introduce two classes of query features -- structural and data-driven -- and perform an in-depth analysis on existing SPARQL benchmarks (LUBM, BSBM, SP$^2$Bench, and DBPSB) using the two classes of query features.
+\paragraph{WatDiv} The Waterloo SPARQL Diversity Test Suite (WatDiv)\footnote{\url{http://dsg.uwaterloo.ca/watdiv/}} developed at the University of Waterloo provides stress testing tools to address the observation that existing SPARQL benchmarks are not suitable for testing systems for diverse queries and varied workloads~\cite{Aluc:2014:DST:2717213.2717229}.
+The benchmark introduce two classes of query features -- structural and data-driven -- and perform an in-depth analysis on existing SPARQL benchmarks (LUBM, BSBM, SP$^2$Bench, and DBPSB) using the two classes of query features.
 The structural features involve triple pattern count, join vertex count, join vertex degree, and join vertex count.
@@
 The analysis of the four benchmarks reveals that they are not sufficiently diverse to test the strengths and weaknesses of different physical design choices employed by RDF systems.
-
 The proposed solution, WatDiv, involves (1) a data generator which generates scalable datasets according to WatDiv schema, (2) a query template generator which traverses the WatDiv schema and generates a diverse set of query templates, (3) a query generator which instantiates the templates with actual RDF terms from the dataset, and (4) a feature extractor which computes the structural and data-driven features of the generated data and workload.
@@
 A query generation process is proposed to generate 5 types of queries (node queries, edge queries, star queries, path queries, and subgraph queries) for any generated data.
-
 The benchmark project FEASIBLE~\cite{Saleem2015} is also an application-specific benchmark; however, contrary to RBench, it is able to generate benchmarks from a set of queries (in particular from query logs) by selecting prototypical queries of a user-defined

### 2018-06-23 generators_analytics.tex
Sherif Changes

@@
 
-...
+\paragraph{HPC Scalable Graph Analysis Benchmark} The HPC Scalable Graph
+Analysis Benchmark~\cite{HPCgraph,Bader:2005:DIH:2099301.2099360} represents an
+application with multiple analysis techniques that access a single data
+structure representing a weighted, directed graph. The benchmark is composed of
+four separated operations (graph construction, classification of large vertex
+sets, graph extraction with BFS, and graph analysis with betweenness centrality)
+on a graph that follows a power-law distribution. The graph generator constructs a list of edge tuples containing vertex
+identifiers (with the edge direction from the first one to the second one) and
+weights that represent data assigned to the edges of the multigraph in the form
+of positive integers with a uniform random distribution. The generator has the
+following parameters: number of vertices, number of edges, and maximum weight of
+an edge. The algorithm of the generator is based on R-MAT~\cite{DBLP:conf/sdm/ChakrabartiZF04}. Since the authors aim
+to avoid data locality, in the final step the vertex numbers are randomly
+permuted, and then edge tuples randomly shuffled. A related project from the same authors developed for the 9th DIMACS Shortest
+Paths Challenge is GTgraph~\cite{GTgraph}. It involves three types of graphs:
+input graph instances used in the DARPA HPCS SSCA\#2 graph theory benchmark
+(version 1.0), Erd\"{o}s-R\'{e}nyi random graphs, and small-world graphs based
+on the R-MAT model~\cite{DBLP:conf/sdm/ChakrabartiZF04}.

### 2018-06-23 generators_general.tex
Sherif Changes

@@
 generating/benchmarking projects targeting Big Data world.
+
+\paragraph {Preferential Attachment} Barabasi and Albert introduced a graph generation model that relies on two main mechanisms~\cite{Barabasi99emergenceScaling}.
+The first mechanism is continuously expanding the graphs by adding new vertices.
+The second mechanism is to preferentially attach the new vertices   to the nodes/regions that are already well connected.
+In this approach, the generation of large graphs is governed by standard, robust self-organizing mechanism that go beyond the characteristics of individual applications.
+
+\paragraph {R-Mat} (\emph{R}ecursive \emph{Mat}rix) R-Mat is a procedural synthetic graph generator which is designed to generate power-law degree
+distributions~\cite{DBLP:conf/sdm/ChakrabartiZF04}. 
+The generator is recursive and uses only a small number of parameters.
+In principle, the strategy of this generator to find simple mechanisms to generate graphs that match
+the properties of the real graphs.
+In particular, the design goals of R-Mat is to generate graphs that match the degree distributions, imitate a community structure and have a small diameter.
+R-Mat can generate weighted, directed and bipartite graphs.
 
@@
 
-\paragraph{HPC Scalable Graph Analysis Benchmark} The HPC Scalable Graph
-Analysis Benchmark~\cite{HPCgraph,Bader:2005:DIH:2099301.2099360} represents an
-application with multiple analysis techniques that access a single data
-structure representing a weighted, directed graph. The benchmark is composed of
-four separated operations (graph construction, classification of large vertex
-sets, graph extraction with BFS, and graph analysis with betweenness centrality)
-on a graph that follows a power-law distribution.
-
-The graph generator constructs a list of edge tuples containing vertex
-identifiers (with the edge direction from the first one to the second one) and
-weights that represent data assigned to the edges of the multigraph in the form
-of positive integers with a uniform random distribution. The generator has the
-following parameters: number of vertices, number of edges, and maximum weight of
-an edge. The algorithm of the generator is based on R-MAT. Since the authors aim
-to avoid data locality, in the final step the vertex numbers are randomly
-permuted, and then edge tuples randomly shuffled.
-
-A related project from the same authors developed for the 9th DIMACS Shortest
-Paths Challenge is GTgraph~\cite{GTgraph}. It involves three types of graphs:
-input graph instances used in the DARPA HPCS SSCA\#2 graph theory benchmark
-(version 1.0), Erd\"{o}s-R\'{e}nyi random graphs, and small-world graphs based
-on the R-MAT model.
-
 \paragraph{Graph 500 Benchmark} The Graph 500 Benchmark~\cite{Graph500} includes
@@
 (i.e., half the average degree of a vertex in the graph). The graph generator is
-a Kronecker generator similar to R-MAT. The data must not exhibit any locality,
+a Kronecker generator similar to R-MAT~\cite{DBLP:conf/sdm/ChakrabartiZF04}. The data must not exhibit any locality,
 so in the final step the vertex labels and order of edges are randomly shuffled.
-
 The covered operations currently involve BFS; however, the authors intend to

### 2018-06-28 generators_LinkedData.tex
Sherif Changes

@@
 The used data sets correspond to RDF representation of relational-like data~\cite{Guo2005158,Bizer09theberlin}, social network-like data~\cite{Schmidt2010}, or specific and significantly more complex data structures such as biological data~\cite{Wu2014}.
-In the following overview we focus on benchmarking systems involving a kind of data generator or data modifier.
-Other types of systems or particular results can be found, e.g., at~\cite{RdfStoreBenchmarking}.
+In this section, we provide an overview of benchmarking systems involving a kind of graph-based RDF data generator or data modifier.
+%Other types of systems or particular results can be found, e.g., at~\cite{RdfStoreBenchmarking}.
 
+\iffalse
 Considering the Big Data world, the Linked Data in general definitely belong to this group since we assume that the Linked (Open) Data Sets form a common Linked Open Data cloud\footnote{\url{http://lod-cloud.net/}}.
 On the other hand, the particular data sets can be relatively small.
+\fi
 
@@
 The ontology defines 43 classes and 32 properties, including 25 object properties and 7 datatype properties~\cite{Guo2005158}.
-The LUBM benchmark also provides 14 test queries.
+The \texttt{LUBM} benchmark also provides 14 test queries.
 The authors focus on \emph{extensional} queries, i.e., queries about the instance data over ontologies, as an opposite to \emph{intentional} queries (i.e., queries about classes and properties).
@@
 
-An extension of LUBM, the Lehigh BibTeX Benchmark (LBBM)~\cite{Wang2005}, enables generating synthetic data for different ontologies.
+An extension of \texttt{LUBM}, the Lehigh BibTeX Benchmark (LBBM)~\cite{Wang2005}, enables generating synthetic data for different ontologies.
 The generation is divided into two phases: (1) the property-discovering phase, and (2) the data generation phase.
@@
 
-\paragraph{SIB} The authors of the Social Network Intelligence BenchMark (SIB)\footnote{\url{https://www.w3.org/wiki/Social_Network_Intelligence_BenchMark}} claim that current benchmarks are limited in representing the real RDF datasets and are mostly relational-like.
+\paragraph{SIB} The developers of the Social Network Intelligence BenchMark (SIB)\footnote{\url{https://www.w3.org/wiki/Social_Network_Intelligence_BenchMark}} based the design of their benchmark based on the claim that existing benchmarks are limited in representing the real RDF datasets and are mostly relational-like.
 Hence, they propose a benchmark for challenging query processing over real graphs~\cite{sib}.
@@
 
-\paragraph{Geographica} The Geographica benchmark \footnote{\url{http://geographica.di.uoa.gr/}} has been designed target the area of geospatial data~\cite{DBLP:conf/semweb/GarbisKK13} and respective SPARQL extensions GeoSPARQL~\cite{battle2012enabling} and stSPARQL~\cite{koubarakis2010modeling}.
+\paragraph{Geographica} The Geographica benchmark \footnote{\url{http://geographica.di.uoa.gr/}} has been designed target the area of geospatial data~\cite{DBLP:conf/semweb/GarbisKK13} and respective SPARQL extensions \texttt{GeoSPARQL}~\cite{battle2012enabling} and \texttt{stSPARQL}~\cite{koubarakis2010modeling}.
 The benchmark involves (1) a real-world workload based on publicly available linked data sets covering a range of geometry types (e.g., points, lines, polygons) and (2) a synthetic workload.
@@
 A query generation process is proposed to generate 5 types of queries (node queries, edge queries, star queries, path queries, and subgraph queries) for any generated data.
-The benchmark project FEASIBLE~\cite{Saleem2015} is also an application-specific benchmark; however, contrary to RBench, it is able to generate benchmarks from a set of queries (in particular from query logs) by selecting prototypical queries of a user-defined
+The benchmark project \texttt{FEASIBLE}~\cite{Saleem2015} is also an application-specific benchmark; however, contrary to RBench, it is able to generate benchmarks from a set of queries (in particular from query logs) by selecting prototypical queries of a user-defined
 size from the input set of queries.
 
-\paragraph{LDBC}  The Linked Data Benchmark Council\footnote{\url{http://ldbcouncil.org/industry/organization/origins}} (LDBC)~\cite{Angles:2014:LDB:2627692.2627697} is a result of a (closed) EU project that brought together a community of academic researchers and industry, whose main objective was the development of open source, yet industrial grade, benchmarks for graph and RDF databases.
-The following three benchmarks were developed and are currently maintained.
-
-The Semantic Publishing Benchmark (SPB)~\cite{spb} is inspired by the Media/Publishing industry (namely BBC\footnote{\url{http://www.bbc.com/}}).
-The application scenario considers a media or a publishing organization that deals with large volume of streaming content, namely news, articles or  ``media assets''.
+\paragraph{LDBC}  The Linked Data Benchmark Council\footnote{\url{http://ldbcouncil.org/industry/organization/origins}} (LDBC)~\cite{Angles:2014:LDB:2627692.2627697} is a result of a (closed) EU project that brought together a community of academic researchers and industry that had the main objective of developing an open source, yet industrial grade, benchmarks for graph and RDF databases.
+\iffalse The following three benchmarks were developed and are currently maintained.\fi In the Semantic Web domain, the project released the Semantic Publishing Benchmark (SPB)~\cite{spb} that has been inspired by the Media/Publishing industry (namely BBC\footnote{\url{http://www.bbc.com/}}).
+The application scenario of this benchmark considers a media or a publishing organization that deals with large volume of streaming content, namely news, articles or  ``media assets''.
 This content is enriched with metadata that describes it and links it to reference knowledge -- taxonomies and databases that include relevant concepts, entities and factual information.
@@
 Two workloads are provided: (1) basic, involving an interactive query-mix, querying the relations between entities in reference data, and (2) advanced,  consisting of interactive and analytical query-mixes.
+The LDBC designed two other benchmarks: the Social Network Benchmark (SNB)~\cite{Erling:2015:LSN:2723372.2742786} for the social network domain  (see Section~\ref{sec:generators_socialnetworks}) and Graphalytics~\cite{Iosup:2016:LGB:3007263.3007270}   for the analytics domain (see Section~\ref{sec:generators_analytics}).
 
-The Social Network Benchmark (SNB) models a social network akin to Facebook (see Section~\ref{sec:generators_socialnetworks}).
-
-Graphalytics~\cite{Iosup:2016:LGB:3007263.3007270} is an industrial-grade benchmark for graph analysis platforms.
-It involves 6 real-world datasets and 2 synthetic datasets generated by LDBC SNB (see Section~\ref{}) and Graph500 (see Section~\ref{}).
-The benchmark involves 6 algorithms: breadth-first search, PageRank, weakly connected components, community detection using label propagation, local clustering coefficient, and single-source shortest paths.
-
-LinkGen~\cite{10.1007/978-3-319-46547-0_12}
+\paragraph{LinkGen} LinkGen is a synthetic linked data generator that has been designed to generate RDF datasets for a given vocabulary~\cite{10.1007/978-3-319-46547-0_12}.
+The generator is designed to receive a vocabulary as an input  and supports two statistical distribution techniques for generating entities: Gaussian distribution and Zipf's power-law distribution.
+\texttt{LinkGen} can augment the generated data with inconsistent and noisy  data such as writing two conflicting values for a given datatype property,  adding triples with syntactic errors, adding wrong statement by assigning invalid domain and creating instances with no type information.
+The generator is also designed with  an option to inter-link the generated instances with real ones given that the user provides entities from real datasets.
+The datasets can be generated in any of of two modes: on-disk and streaming.

### 2018-06-28 generators_SocialNetworks.tex
Sherif Changes

@@
 privacy of the data. Hence, data generators which provide realistic synthetic
-social network graphs are in great demand.
-
-Analyses of social networks identify their various specific
+social network graphs are in great demand. In general, analyses of social networks identify their various specific
 features~\cite{Chakrabarti:2006:GML:1132952.1132954}. For example, the social
@@
 \paragraph{Realistic Social Network}
-Paper~\cite{Barrett:2009:GAL:1995456.1995598} focuses on construction of
+~\cite{Barrett:2009:GAL:1995456.1995598} focused on construction of
 realistic social networks using a combination of public and private data sets
@@
 synthetic individual is assigned a 24-hour activity sequence including
-geo-locations for each activity.
-
-To demonstrate the approach, the authors develop a synthetic population for the
+geo-locations for each activity. To demonstrate the approach, the authors develop a synthetic population for the
 United States that models every individual in the population. The synthetic
@@
 take place is generated by a combination of simulation and data fusion
-techniques. This information is captured by a dynamic social contact network.
+techniques. This information is captured by a dynamic social contact network. Similar methods for agent-based strategies have been reported in~\cite{Bernstein:2013:SAS:2499604.2499609}.
 
-Similar agent-based strategies can be found, e.g., in papers~\cite{Bernstein:2013:SAS:2499604.2499609}.
-
-\paragraph{Linkage vs. Activity Graphs} Paper~\cite{Yao2011} distinguishes two
+\paragraph{Linkage vs. Activity Graphs} ~\cite{Yao2011} distinguished between two
 types of social network graphs -- the \emph{linkage graph}, where nodes stand
@@
 Namely linkage graphs have positive degree correlation whereas activity graphs
-show neutral degree correlation.
-
-With regards to the findings, the proposed generator focusses on linkage graphs
+show neutral degree correlation. With regards to the findings, the proposed generator focusses on linkage graphs
 with positive degree correlation. For this purpose it extends the ``forest
@@
 \paragraph{LinkBench} The LinkBench
-benchmark~\cite{Armstrong:2013:LDB:2463676.2465296} aims to predict the
-performance of a database when used for persistent storage of Facebook?s
+benchmark~\cite{Armstrong:2013:LDB:2463676.2465296} has been designed to predict the
+performance of a database when used for persistent storage of Facebook's
 production data. The benchmark considers true Big Data and related problems with
@@
 typically post more pictures than people with few friends, i.e., the amount of
-friend nodes influences the amount of posted comment and picture nodes.
-
-The data generation process starts with generating a number of nodes with
+friend nodes influences the amount of posted comment and picture nodes. The data generation process starts with generating a number of nodes with
 property values generated according to specified property value correlations and
@@
 connected is typically skewed with respect to some similarity between the
-nodes'' enables to focus only on sliding window of most probable candidates.
-
-The core idea of the framework is demonstrated using an example of a social
+nodes'' enables to focus only on sliding window of most probable candidates. The core idea of the framework is demonstrated using an example of a social
 network (consisting of persons and social activities).  The dictionaries for
@@
 similarity parameter -- a source node is selected randomly and connected to the
-most similar node.
-
-Multi-Link Generator (MLG) further  uses link co-occurrence statistics from the
+most similar node. Multi-Link Generator (MLG) further  uses link co-occurrence statistics from the
 original dataset to create a multiplex network. MLG uses the same network growth
@@
 
-The generated data have become a part if several graph benchmarks, such as
-GraphBIG~\cite{Nai:2015:GUG:2807591.2807626}.
+%The generated data have become a part if several graph benchmarks, such as GraphBIG~\cite{Nai:2015:GUG:2807591.2807626}.
 
-\paragraph{Towards More Realistic Data} The authors of
-paper~\cite{Nettleton2016} claim that the main body of existing work lies in
+\paragraph{Towards More Realistic Data} ~\cite{Nettleton2016} argued that the main body of existing work lies in
 topology generation which approximate the characteristics of a real social
@@
 distribution, and community structures), however without data. Hence, they
-implement a general stochastic modeling system which allows the users to
+introduced a general stochastic modeling system which allows the users to
 populate a graph topology with data. The approach has three steps: (1) topology

### 2018-06-28 generators_general.tex
Sherif Changes

@@
 
-\paragraph {R-Mat} (\emph{R}ecursive \emph{Mat}rix) R-Mat is a procedural synthetic graph generator which is designed to generate power-law degree
+\paragraph {R-Mat} (\emph{R}ecursive \emph{Mat}rix) \texttt{R-Mat} is a procedural synthetic graph generator which is designed to generate power-law degree
 distributions~\cite{DBLP:conf/sdm/ChakrabartiZF04}.
@@
 the properties of the real graphs.
-In particular, the design goals of R-Mat is to generate graphs that match the degree distributions, imitate a community structure and have a small diameter.
+In particular, the design goals of \texttt{R-Mat} is to generate graphs that match the degree distributions, imitate a community structure and have a small diameter.
 R-Mat can generate weighted, directed and bipartite graphs.
@@
 database of graphs, their average size and average density, the authors have
-also implemented a synthetic generator called GraphGen~\cite{GraphGen}. It is
+also implemented a synthetic generator called \texttt{GraphGen}~\cite{GraphGen}. It is
 based on the IBM synthetic data generation code for associations and sequential
@@
 \url{http://www.almaden.ibm.com/cs/projects/iis/hdb/Projects/data
-mining/mining.shtml}.}. GraphGen creates a collection of labeled, undirected and
+mining/mining.shtml}}. \texttt{GraphGen} creates a collection of labeled, undirected and
 connected graphs aiming at performance evaluation of frequent subgraph mining
@@
 
-\paragraph{Graph 500 Benchmark} The Graph 500 Benchmark~\cite{Graph500} includes
+\paragraph{Graph 500 Benchmark} \texttt{The Graph 500 Benchmark}~\cite{Graph500} includes
 a scalable data generator which produces weighted, undirected graph as a list of
@@
 (i.e., half the average degree of a vertex in the graph). The graph generator is
-a Kronecker generator similar to R-MAT~\cite{DBLP:conf/sdm/ChakrabartiZF04}. The data must not exhibit any locality,
+a Kronecker generator similar to \texttt{R-MAT}~\cite{DBLP:conf/sdm/ChakrabartiZF04}. The data must not exhibit any locality,
 so in the final step the vertex labels and order of edges are randomly shuffled.
@@
 creation of multiple Erd\"{o}s-R\'{e}ny graphs with different connection
-probabilities, connected randomly between them. As a main feature, BTER is able
+probabilities, connected randomly between them. As a main feature, \texttt{BTER} is able
 to reproduce input degree distributions and average clustering
@@
 
-\paragraph{Darwini} Darwini~\cite{edunov2016darwini} is an extension of BTER
+\paragraph{Darwini} \texttt{Darwini}~\cite{edunov2016darwini} is an extension of \texttt{BTER}
 designed to run on Vertex Centric computing frameworks like
@@
 coefficient of the input graph. Instead of just focusing on the average
-clustering coefficient for each degree, Darwini is able to model the clustering
+clustering coefficient for each degree, \texttt{Darwini} is able to model the clustering
 coefficient distribution per degree. It achieves this by grouping the vertices
@@
 connected randomly with a probability that would produce, in expectation, the
-desired number of triangles for such bucket. Then, as in BTER, the excess degree
-is used to connect the different buckets. The authors report that Darwini is
+desired number of triangles for such bucket. Then, as in \texttt{BTER}, the excess degree
+is used to connect the different buckets. The authors report that \texttt{Darwini} is
 able to generate graphs with billions and even trillions of edges.

### 2018-07-02 generators_SocialNetworks.tex
Minor fixes

--- 2018-06-08 generators_SocialNetworks.tex
@@
 On-line social networks, like Facebook, Twitter, or LinkedIn, have become a
-phenomenon used by billions of people every day and thus providing extremely
-useful information for various domains. However, an analysis of such type of
-graph has to cope with two problems: (1) availability of the data and (2)
-privacy of the data. Hence, data generators which provide realistic synthetic
-social network graphs are in great demand.
+phenomenon used by billions of people every day. Their bussiness model is
+heavily based on understanding the behavior and interests of their users, and
+thus their analysis has been proven to be of an inestimable value.  However,
+doing research on novel and more efficient ways to analyze such requires the
+access to real datasets, which is in most cases not possible since companies
+holding the data do not want to or cannot share them. Hence, social network
+generators which provide realistic synthetic outputs are in great demand.
 
-Analyses of social networks identify their various specific
-features~\cite{Chakrabarti:2006:GML:1132952.1132954}. For example, the social
-graph has high \emph{clustering coefficient}, i.e. the degree of transitivity of
-a graph. Or, its diameter, i.e. the minimum number of hops in which some
-fraction (e.g., 90\%) of all connected pairs of nodes can reach each other, is
-usually low due to weak ties joining faraway cliques. Another important aspect
-of social networks is the community effect. A detailed study of structure of
-communities in 70 real-world networks is provided, e.g., in
-paper~\cite{Leskovec:2008:SPC:1367497.1367591}. Authors of
-paper~\cite{Prat-Perez:2014:CSS:2621934.2621942} analyze the structure of
-communities (clustering coefficient, triangle participation ratio, bridges,
-diameter, conductance and size) in both real graphs and output by existing graph
-generators LFR~\cite{PhysRevE.78.046110} and the
-LDBC-SNB~\cite{Erling:2015:LSN:2723372.2742786}. %They discover that communities
+Compared to other types of networks (e.g. computer networks or road networks),
+social networks exhibit a set of particular characteristics as explained in
+~\cite{Chakrabarti:2006:GML:1132952.1132954}. For example, people tend to
+connect to persons with similar interests, persons geo-located closely, family
+members or persons studying or working at the same place. This leads to the
+formation of what are known as communities (modules of highly interconnected
+persons that share similarities), which in turn makes these networks to exhibit
+a large clustering coefficient (e.g. percentage of transitive relations or
+triangles).  Such modular structure also leads to the formation of a network
+with a small diameter, i.e. the minimum number of hops in which some fraction
+(e.g., 90\%) of all connected pairs of nodes can reach each other. This is
+usually due to weak ties connecting far away modules. Finally, social networks
+usually have a large largest connected component, accounting for more than 90\%
+of its nodes.
+
+A detailed study of the structure of communities in 70 real-world networks is
+provided, e.g., in paper~\cite{Leskovec:2008:SPC:1367497.1367591}. Additionally,
+authors of paper~\cite{Prat-Perez:2014:CSS:2621934.2621942} analyze the
+structure of communities (clustering coefficient, triangle participation ratio,
+bridges, diameter, conductance and size) in both real graphs and output by
+existing graph generators LFR~\cite{PhysRevE.78.046110} and the
+LDBC-SNB~\cite{Erling:2015:LSN:2723372.2742786}. They discover that communities
 found among different graphs follow quite similar distributions and that
@@
 
-Network generators can be categorized into statistical and agent-based.
+Exhisting, social network generators try to reproduce different aspects of the
+generated network, from high can be categorized into statistical and agent-based.
 \emph{Statistical

### 2018-07-02 generators_GraphDatabases.tex

@@
 Hence it is questionable whether a benchmark specific for graph databases if necessary.
+~\cite{Dominguez-Sal:2010:DDG:1946050.1946053} discussed this question and related topics.
+On the basis of a review of applications of graph databases (namely social network analysis, proteomics or genetic interactions, recommendation systems, and travel planning and routing), the authors analyze and discuss the characteristics of the graphs that appear in such applications and how they could influence benchmarking, different types of operations used in these applications and the characteristics of the evaluation setup of the benchmark.
+In this section, we focus on graph data generators and benchmarks that heve been primarily targeting graph DBMSs.
 
-Paper~\cite{Dominguez-Sal:2010:DDG:1946050.1946053} discusses this question and related topics.
-On the basis of a review of applications of graph databases (namely social network analysis, proteomics or genetic interactions, recommendation systems, and travel planning and routing), the authors analyze and discuss the characteristics of the graphs that appear in such applications and how they could influence benchmarking, different types of operations used in these applications and the characteristics of the evaluation setup of the benchmark.
-
-In the following paragraphs we overview graph data generators and benchmarks primarily targeting graph DBMSs.
-
-\paragraph{XGDBench} XGDBench~\cite{Dayarathna:2014:GDB:2676904.2676939} is an extensible graph database benchmarking platform for cloud computing systems. Its intent is to automate
+\paragraph{XGDBench} \texttt{XGDBench}~\cite{Dayarathna:2014:GDB:2676904.2676939} is an extensible graph database benchmarking platform for cloud computing systems. Its intent is to automate
 the process of graph database benchmarking in the cloud focusing on a graph database application for social networking services.
-
 It extends the Yahoo!
@@
 Using them 7 workloads are created, such as update heavy, read mostly, short range scan, traverse heavy etc.
-
 The data model of XGDBench is a simplified version of the Multiplicative Attribute Graph (MAG)~\cite{Kim2010} model, a synthetic graph model for attribute graphs which models the interactions between the network structure and the node attributes.
@@
 A multi-threaded version of the graph generator that generates large graphs on multi-core systems faster was implemented.
-
-\paragraph{GraphGen}  GraphAware GraphGen~\cite{GraphGen} is a graph generation engine based on Cypher, Neo4j's\footnote{\url{https://neo4j.com/}} query language.
-It creates nodes and relationships based on a schema definition expressed in Cypher, and it can also generate property values on both
-nodes and edges.
-As such, GraphGen is a precursor of property graphs generators.
-The resulting graph can be exported to several formats (namely GraphJson and CypherQueries) or loaded directly to a DBMS.
-However, it is probably not maintained anymore.
 
@@
 whether there exists a query workload satisfying $Q$ is NP-complete.
-Hence, gMark follows a heuristic strategy in the generation -- it attempts to achieve the exact values of the parameters and it may decide to relax some of them in order to obtain linear running time.
-gMark generates graphs under the form of N-triples and query workloads in four concrete syntaxes, including Cypher, SPARQL, SQL and LogicQL.
+Hence, \texttt{gMark} follows a heuristic strategy in the generation -- it attempts to achieve the exact values of the parameters and it may decide to relax some of them in order to obtain linear running time.
+gMark generates graphs under the form of N-triples and query workloads in four concrete syntaxes, including \texttt{Cypher}, \texttt{SPARQL}, \texttt{SQL} and \texttt{LogicQL}.
+
+\paragraph{GraphGen}  GraphAware GraphGen\footnote{\url{http://graphgen.graphaware.com/}} is a graph generation engine based on \texttt{Cypher}\footnote{\url{https://neo4j.com/developer/cypher-query-language/}}, Neo4j's\footnote{\url{https://neo4j.com/}} query language~\cite{GraphGen}.
+It creates nodes and relationships based on a schema definition expressed in Cypher, and it can also generate property values on both
+nodes and edges.
+As such, GraphGen is a precursor of property graphs generators.
+The resulting graph can be exported to several formats (namely \texttt{GraphJson}\footnote{\url{https://github.com/GraphAlchemist/GraphJSON/wiki/GraphJSON}} and CypherQueries) or loaded directly to a DBMS.
+However, it is probably not maintained anymore.

### 2018-07-02 generators_analytics.tex

@@
 on the R-MAT model~\cite{DBLP:conf/sdm/ChakrabartiZF04}.
+
+Graphalytics~\cite{Iosup:2016:LGB:3007263.3007270} is an industrial-grade benchmark for graph analysis platforms.
+It involves 6 real-world datasets and 2 synthetic datasets generated that cover two commonly used type of graphs: social network graphs generated using LDBC SNB graph generator (see Section~\ref{sec:generators_socialnetworks}) and power-law graphs generated by Graph500 (see Section~\ref{sec:generators_general}).
+The benchmark workload consists of 6 deterministic algorithms: breadth-first search, PageRank, weakly connected components, community detection using label propagation, local clustering coefficient, and single-source shortest paths.
+The benchmark uses various metrics to measure the performance and throughput for systems under test such as \emph{upload time} the measures the required time to preprocess and convert the graph into a suitable format for a graph processing system and \emph{Makespan} the measures the total  execution time of a benchmarking workload algorithm.
+The benchmark also describes experiments for measuring the scalability of the systems under test.
+To facilitate the end user job of running the designed experimental workload, the benchmark provides  a performance evaluation framework, \texttt{Granula}\footnote{\url{https://github.com/atlarge-research/granula}}, that consists of three main components: the modeler, the archiver, and the visualizer.

### 2018-07-04 data_sets.tex
Moved data sets to a separate section
Partial version of data sets

@@
-\subsection{Graph Data Sets}
+\section{Graph Data Sets}
 
-Before we focus on graph data generators, we briefly overview graph data sets devoted to benchmarking of various types of graph algorithms.
-\cite{Knuth:1993:SGP:164984} denotes such a  database of graphs (or graph library or graph archive) and related computer programs as a \emph{graphbase}.
-In general, there exist several types of testing graph data sets~\cite{Bachmaier2012}:
+Besides graph data generators, many graph algorithms and systems are benchmarked
+using real graph data sets, including new graph data generation techniques. In
+this section we review the most widely used graph datasets in the literature and
+their purpose.
+
+%In general, there exist several types of testing graph data
+%sets~\cite{Bachmaier2012}:
+
+\paragraph{Large Scale Graph Analytics}
+
+Large scale graph analytics systems are usually benchmarked using a combination of
+real and synthetically generated graphs. Because of the rapid evolution of such
+systems and their increasing capability to process larger graphs, the datasets
+typically used  in the literature quickly change overtime. The most commonly
+used datasets are, which can be downloaded from several graph dataset
+repositories~\cite{snapnets,lawalgo}: 
+\begin{itemize}
+  \item Dblp~\cite{yang2015defining}: Represents a co-authorship network where
+    researchers from Dblp are represented as vertices, and there exists and edge
+    between them if they have published a paper together. 
+  \item Amazon~\cite{yang2015defining}: Represents a product co-purchasing
+    network, such that each vertex is a product and an edge between two products
+    exists if a person has bought the two products. 
+  \item Road networks~\cite{leskovec2009community}: Consist of a set of road
+    networks from the US.  
+  \item LiveJournal~\cite{yang2015defining}: A social network where vertices
+    represent the users and the edges the acquitances between them.
+  \item Orkut~\cite{yang2015defining}: Like LiveJournal, this is a social network
+    where vertices represent persons and the edges their friendships.
+  \item Twitter~\cite{kwak2010twitter}: This is a directed network representing
+    the follower-followee interaction of Twitter.
+  \item Friendster~\cite{yang2015defining}: A social network like LiveJournal and
+    Orkut, where nodes represent persons and edges their relationships.
+  \item WebUK~\cite{delis}: A web graph of the UK subdomain, where nodes represent
+    websites and edges the hyperlinks between them.
+  \item ClueWeb2012~\cite{clueweb}. This is a crawl of the web from 2012, where
+    vertices represent websites and the edges the hyperlinks connecting them.
+\end{itemize}
+
+\paragraph{Recommender Systems }
+
+Many recommender systems are based on graphs, either bipartite graphs or
+many-to-many graphs. Such systems are usually tested on several real datasets,
+many of them containing information about rating of products or other items such
+as movies, books or songs. The following are the most widely used datasets for
+testing recommender systems:
 
 \begin{itemize}
-  \item A real-world data set which represents a graph, such as the Internet Movie Database (IMDb)\footnote{\url{http://www.imdb.com/}} or various data sets available in the Stanford Large Network Dataset Collection~\cite{snapnets},
-  \item A general graphbase, such as the Open Graph Archive~\cite{Bachmaier2012}, the Stanford GraphBase~\cite{Knuth:1993:SGP:164984}, or the GraphArchive~\cite{GraphArchive},
-  \item A dataset dedicated to specific experimental goals, such as graph partitioning and graph clustering~\cite{10dimacs}, shortest paths~\cite{9dimacs}, or graph coloring~\cite{coloring}, and
-  \item A dataset devoted to matrices, such as the SuiteSparse Matrix Collection~\cite{SuiteSparse} or  the Matrix Market~\cite{MatrixMarket}.
+\item MovieLens~\cite{movielens}: Consists of a bipartite graph
+  between users and movies, where edges represent the ratings the different
+  users have made to the movies they watched. 
+\item Book-Crossings~\cite{ziegler2005improving}: Is a dataset with book ratings
+  from users. 
+\item Jester~\cite{goldberg2001eigentaste}: This dataset contains jokes (with
+  their text) and ratings from users. 
+\item Last.fm~\cite{hetrec}: This dataset contains the list of the top
+  most listened artists per user, including the number of times the songs from
+  those artists were played. Additionally, it contains connections between users
+  (the social network they form), and a set of tags attached to artists that can
+  be used to create content vectors.
+\item Netflix~\cite{zhou2008large}: This dataset was used during the famous
+  Netflix prize. It consists of a bipartite graph with movie ratings from users.
 \end{itemize}
 
-...
+\paragraph{Reputation Algorithms}
+
+Another application using social network data is that of assessing the degree of
+reputation of a user based on their past interactions and
+rankings~\cite{kamvar2003eigentrust,katz2006social,kumar2016edge}. Such
+algorithms are typically evaluated on networks with explicit user rankings or
+votings from other users, being the most widely used datasets the following
+examples:
+
+  \begin{itemize}
+    \item Bitcoin~\cite{moore2013beware}: This dataset contains information from
+      several Bitcoin exchanges, where users are able to rate other users after
+      their transactions. Here, the vertices represent the users and the edges,
+      which are labelled, the ratings between them.
+    \item Wikipedia RFA~\cite{west2014exploiting}: This is a network extracted
+      from Wikipedia, where the vertices represent users  and the
+      edges, which are labelled, the votes emitted by administrators for the
+      user to become an administrator.  Each vote is accompained with a text
+      explaining the vote's sign. 
+    \item WikiSigned~\cite{maniu2011building}: This is a network of Wikipedia
+      editors where the vertices are the editors and the edges, which are
+      labelled, represent the turst level between two editors.
+    \item Extended Epinions~\cite{massa2007trust}: This is an extended version of
+      the Epinions network which also contains the levels of distrust between the
+      users, expressed by means of edges between them.
+    \item Twitter Indian Elections~\cite{kagan2015using}: This network represents
+      a Twitter network where vertices represent users and there is an edge
+      between two users if a user mentions another one in a tweet. The edges
+      are labelled with the average sentiment of one user towards another. 
+  \end{itemize}
+
+\paragraph{Graph partitioning, Clustering and Community Detection}
+
+Many of the already discussed datasets are also typically used to test and
+compare graph partitioning, clustering and community detection algorithms. One
+can find a comprehensive lists of datasets for such algorithms
+in~\cite{10dimacs,yang2015defining}, some of them already discussed for other
+applications. Here, we summarize the most widely used in the literature:
+
+\begin{itemize}
+  \item Dblp, Amazon, LiveJournal, Orkut and Friendster~\cite{yang2015defining}
+    are widely used for evaluating community detection since they provide
+    information about the meta-communities they contain. For instance, in
+    Livejournal, users can join groups of users talking about given topics. Such
+    groups are exported as meta-communities, and similar approaches are used for
+    other graphs. Community detection algorithms are then evaluated by trying to
+    infer such meta-communities without prior knowledge of the user to group
+    assignment.
+  \item Zachary Karate Club~\cite{zachary1977information}: This graph consists
+    of a small networks of members of a karate club that was dismissed and split
+    into two new karate clubs. Vertices represent persons and edges friendship
+    relationships. Information about what people joined each of the two new
+    karate clubs is provided.
+  \item PolBlogs~\cite{adamic2005political}: This is a network consisting of
+    blogs talking about the US 2005 political elections, where a vertex
+    represents a blog and the edges the hyperlinks between the blogs. Each blog
+    has an associated label, whehter it is left or right oriented.
+  \item PolBooks~\cite{10dimacs}: Is a network of books of Amazon that talk
+    about politics, and edges between two books exist if they are co-purchased
+    together. The books have labels of whether they are left or right oriented.
+  \item Football~\cite{girvan2002network}: A network of american university
+    football teams. Each node represents a football team and the edges represent
+    the matches between them during the season. Each team is associated to a
+    division.
+\end{itemize}
+
+\paragraph{Information Diffussion}
+% - http://pure-oai.bham.ac.uk/ws/files/14790571/srep02980.pdf
+% - https://www.americanvoiceforfreedom.org/wp-content/uploads/2018/03/The-spread-of-true-and-false-news-online.pdf
+
+ \paragraph{Knowledge bases}
+% - Wikipedia https://en.wikipedia.org/wiki/Wikipedia:Database_download
+
+%\begin{itemize} 
+%  \item A real-world data set which represents a graph, such as
+%      the Internet Movie Database (IMDb)\footnote{\url{http://www.imdb.com/}} or
+%      various data sets available in the Stanford Large Network Dataset
+%      Collection~\cite{snapnets}, 
+%    \item A general graphbase, such as the Open
+%      Graph Archive~\cite{Bachmaier2012}, the Stanford
+%    GraphBase~\cite{Knuth:1993:SGP:164984}, or the
+%  GraphArchive~\cite{GraphArchive}, 
+%\item A dataset dedicated to specific
+%    experimental goals, such as graph partitioning and graph
+%    clustering~\cite{10dimacs}, shortest paths~\cite{9dimacs}, or graph
+%    coloring~\cite{coloring}, and 
+%  \item A dataset devoted to matrices, such as
+%the SuiteSparse Matrix Collection~\cite{SuiteSparse} or  the Matrix
+%Market~\cite{MatrixMarket}.  
+%\end{itemize}

### 2018-07-05 generators_analytics.tex
Sherif Changes

@@
 
-Graphalytics~\cite{Iosup:2016:LGB:3007263.3007270} is an industrial-grade benchmark for graph analysis platforms.
+\paragraph{Graphalytics} \texttt{Graphalytics}\footnote{\url{http://graphalytics.ewi.tudelft.nl/}} is an industrial-grade benchmark for graph analysis platforms~\cite{Iosup:2016:LGB:3007263.3007270}.
 It involves 6 real-world datasets and 2 synthetic datasets generated that cover two commonly used type of graphs: social network graphs generated using LDBC SNB graph generator (see Section~\ref{sec:generators_socialnetworks}) and power-law graphs generated by Graph500 (see Section~\ref{sec:generators_general}).

### 2018-07-11 data_sets.tex
Some changes to datasets section and bibliography

@@
 \paragraph{Information Diffussion}
-% - http://pure-oai.bham.ac.uk/ws/files/14790571/srep02980.pdf
-% - https://www.americanvoiceforfreedom.org/wp-content/uploads/2018/03/The-spread-of-true-and-false-news-online.pdf
 
- \paragraph{Knowledge bases}
+Information networks are studied using graph algorithms in order to understand
+how information propagates. As such, there several datasets used to understand
+such networks.
+
+\begin{itemize}
+  \item Higgs-Twitter~\cite{de2013anatomy}: This dataset contains the Twitter
+    network before, during and after the discovery of the Higgs boson.
+    Concretely, it contains the tweets, the mentions, retweets,
+    followers/followees, etc.  
+  \item Memetracker~\cite{leskovec2009memede2013}: Memetracker is a dataset that
+    contains the quotes and phrases that appear more frequently on the entire
+    news spectrum. It consists of the links of the news, the time and memes, and
+    is used to understand how information spanws, evolves and dies.
+\end{itemize}
+
+ \paragraph{Semantic Web and Knowledge bases}
+
 % - Wikipedia https://en.wikipedia.org/wiki/Wikipedia:Database_download
+% - DbPedia
 

### 2018-07-16 data_sets.tex
Added Semantic web datasets

@@
     followers/followees, etc.  
-  \item Memetracker~\cite{leskovec2009memede2013}: Memetracker is a dataset that
+  \item Memetracker~\cite{leskovec2009meme}: Memetracker is a dataset that
     contains the quotes and phrases that appear more frequently on the entire
@@
 
-% - Wikipedia https://en.wikipedia.org/wiki/Wikipedia:Database_download
-% - DbPedia
+Semantic web and RDF engines have a well accepted set of real datasets, used to
+test reasoning engines as well as to use as baselines for the creation of new
+synthetic generators for the semantic web.
+
+\begin{itemize}
+  \item DbPedia~\cite{Bizer:2009:DCP:1640541.1640848}: The DBPedia project aims at creating
+    a structured version of Wikipedia. It allows users to semantically query the
+    relationships between the different resources at wikipedia.
+  \item Freebase~\cite{bollacker2008freebase}: Is a collaborative knowledge base
+    made of metadata mainly provided by community members. It contains
+    structured data from multiple sources in an attempt to create a global
+    resource of information accessible both from persons and machines. The
+    project was discontinued in 2014 and replaced by Wikidata.
+  \item Yago~\cite{suchanek2007yago}, Yago2~\cite{hoffart2013yago2} \&
+    Yago3~\cite{mahdisoltani2013yago3}: These are
+    open source knowledge bases developed at the Max Planck Institute of
+    Computer Science in Saarbr\"ucken. It contains structured data automatically extracted
+    from Wikipedia and other sources.
+  \item Wikidata~\cite{vrandevcic2014wikidata}: This is a knowledge base
+    collaboratively edited by the community and hosted by the Wikimedia
+    Foundation. It contains structured data from its sister projects Wikipedia,
+    Wikivoyage, Wikisource and others.
+  \item Billion Triple Challenge~\cite{btc-2014}: This is a semantic dataset
+    crawled from different sources, including Freebase, DBPedia or the BBC. A
+    detailed description of the crawling process can be found in~\cite{kafer2012towards}.  
+\end{itemize}
 

### 2018-07-17 challenges.tex
Refactored graph streaming and community detection into others section
Added some braindump about open challenges

@@
 
-...
+In this section, we discuss several of the open challenges in large scale graph
+generation.
 
 \subsection{Single- vs. multi-domain}
-...
+
+Most of existing graph generators generate graphs that are either not labeled or
+are specific of a given domain (e.g.  Social Networks). Graphs from different
+domains have different schemas, structural characteristics, property
+distributions, etc. which might have an impact on the performance of the
+application under test. Thus, graph processing engine developers are asking for
+generators or tools to generate graphs flexibily, allowing to configure aspects
+such as the size, the schema, the data distributions and other structural
+characteristics such as the degree distribution, the clustering coefficient,
+etc.
 
 \subsection{Simple Usage, Simple Parameters}
-Proposal of a data generator (not necessarily for graph data) has to face an important schism.
-On the one hand, there is the aim to provide the user with as many parameters as possible in order to enable one to generate any kind of data.
-This approach seems to be reasonable, but it encounters the fact that users are usually unwilling to use complex benchmarking tools.
-This observation can be seen, for example, in the case of XML benchmarks -- even though there exist robust and complex data generators (such as ToXGene~\cite{conf/webdb/BarbosaMKL02}, which supports specification of structural aspects, value distributions, references etc.), the most popular benchmarking tool is XMark~\cite{Schmidt:2002:XBX:1287369.1287455} which models a single use case and enables to specify just the size of the data.
-Hence, the other extreme is to provide a simple data generator which does not require any complex settings and thus the benchmarking process is extremely simple and fast.
+Proposal of a data generator (not necessarily for graph data) has to face an
+important schism. On the one hand, there is the aim to provide the user with as
+many parameters as possible in order to enable one to generate any kind of data.
+This approach seems to be reasonable, but it encounters the fact that users are
+usually unwilling to use complex benchmarking tools. This observation can be
+seen, for example, in the case of XML benchmarks -- even though there exist
+robust and complex data generators (such as
+ToXGene~\cite{conf/webdb/BarbosaMKL02}, which supports specification of
+structural aspects, value distributions, references etc.), the most popular
+benchmarking tool is XMark~\cite{Schmidt:2002:XBX:1287369.1287455} which models
+a single use case and enables to specify just the size of the data. Hence, the
+other extreme is to provide a simple data generator which does not require any
+complex settings and thus the benchmarking process is extremely simple and fast.
 
-Considering the complex structure of graph data and the variety of applications having highly specific types of graphs, the latter solution is difficult to implement.
-A reasonable compromise can thus be seen in a data generator which is provided with sample graph data and is capable of automatic analysis of their structural and value specifics in order to gain the complex parameters.
+Considering the complex structure of graph data and the variety of applications
+having highly specific types of graphs, the latter solution is difficult to
+implement. A reasonable compromise can thus be seen in a data generator which is
+provided with sample graph data and is capable of automatic analysis of their
+structural and value specifics in order to gain the complex parameters.
 
 \subsection{Evolving Graph Data}
-As user requirements as well as environments change, most of the existing applications naturally evolve over time, at least to some extent.
-This evolution usually influences the structure of the data and consequently all the related parts of the application (i.e., storage strategies, operations, indices etc.).
-The respective data generator should hence be able to simulate such a growth and/or change in structure.
+As user requirements as well as environments change, most of the existing
+applications naturally evolve over time, at least to some extent. This evolution
+usually influences the structure of the data and consequently all the related
+parts of the application (i.e., storage strategies, operations, indices etc.).
+The respective data generator should hence be able to simulate such a growth
+and/or change in structure.
 
-In some graph applications, such as, e.g., social networks, the evolution of the data is a significant aspect, especially in the activity graphs, that has been studied extensively~\cite{doreian1997evolution,Kumar:2006:SEO:1150402.1150476,Hellmann2014583,wang2013,Kossinets88,Viswanath:2009:EUI:1592665.1592675}.
-A related problem is \emph{data versioning} and respective ability to query across multiple versions of data or in general its analysis.
-Considering graph data this problem is also common, for example  in the area of Linked Data~\cite{DBLP:conf/semweb/Papakonstantinou16,DBLP:conf/esws/MeimarisP16,fernandez2015towards,fernandez2015bear}.
+In some graph applications, such as, e.g., social networks, the evolution of the
+data is a significant aspect, especially in the activity graphs, that has been
+studied
+extensively~\cite{doreian1997evolution,Kumar:2006:SEO:1150402.1150476,Hellmann2014583,wang2013,Kossinets88,Viswanath:2009:EUI:1592665.1592675}.
+A related problem is \emph{data versioning} and respective ability to query
+across multiple versions of data or in general its analysis. Considering graph
+data this problem is also common, for example  in the area of Linked
+Data~\cite{DBLP:conf/semweb/Papakonstantinou16,DBLP:conf/esws/MeimarisP16,fernandez2015towards,fernandez2015bear}.
 
-As shown in papers~\cite{Leskovec:2005:RMT:2101235.2101254,Leskovec:2005:GOT:1081870.1081893}, evolving graphs have further specific features.
-For example, some graphs grow over time according to a \emph{densification power law} which means that real graphs tend to sprout many more edges than nodes, and thus are densifying as they grow.
-Also the effective diameter of graphs tends to shrink or stabilize as the graph grows with time.
+As shown in
+papers~\cite{Leskovec:2005:RMT:2101235.2101254,Leskovec:2005:GOT:1081870.1081893},
+evolving graphs have further specific features. For example, some graphs grow
+over time according to a \emph{densification power law} which means that real
+graphs tend to sprout many more edges than nodes, and thus are densifying as
+they grow. Also the effective diameter of graphs tends to shrink or stabilize as
+the graph grows with time.
 
-%\paragraph{} Following the same recursion idea, paper~\cite{Leskovec:2005:RMT:2101235.2101254} uses Kronecker multiplication to generate self-similar graphs.
-The network starts with an initial graph G1 that contains $N_1$ nodes and $E_1$ edges.
-Using matrix recursion, larger successive graphs $G_2, G_3, ...
-G_n$ are generated.
-The $k$-th graph $G_k$ contains $N_k = N^k_1$ nodes.
-Many graphs often densify over time, exhibiting a growth in the number of edges that is superlinear to the number of nodes.
-Kronecker multiplication produces graphs with a fixed diameter and a densification power law degree distribution with exponent $k = log(E_1)/log(N_1)$.
-The graph generation process introduces a staircase effect in the nodes' degrees, and each community consists of smaller nested communities that are formed through expansion and recursion.
+%\paragraph{} Following the same recursion idea,
+%paper~\cite{Leskovec:2005:RMT:2101235.2101254} uses Kronecker multiplication to
+%generate self-similar graphs. The network starts with an initial graph G1 that
+%contains $N_1$ nodes and $E_1$ edges. Using matrix recursion, larger successive
+%graphs $G_2, G_3, ... G_n$ are generated. The $k$-th graph $G_k$ contains $N_k
+%= N^k_1$ nodes. Many graphs often densify over time, exhibiting a growth in the
+%number of edges that is superlinear to the number of nodes. Kronecker
+%multiplication produces graphs with a fixed diameter and a densification power
+%law degree distribution with exponent $k = log(E_1)/log(N_1)$. The graph
+%generation process introduces a staircase effect in the nodes' degrees, and
+%each community consists of smaller nested communities that are formed through
+%expansion and recursion.
 
 \subsection{Multi-model Data}
-With the dawn of Big Data and especially its Variety aspect there have emerged also new types of database management systems.
-One of the most interesting ones are so-called \emph{multi-model databases} which enable to store and especially query across structurally different data.
-There exist various types of multi-model systems combining  distinct subsets of Big Data structures; hence, there naturally exists systems which combine graph data with other data models.
-For example, OrientDB\footnote{\url{http://orientdb.com/orientdb/}} which was implemented on the basis of an object DBMS currently supports graph, document, key/value, and object models.
+With the dawn of Big Data and especially its Variety aspect there have emerged
+also new types of database management systems. One of the most interesting ones
+are so-called \emph{multi-model databases} which enable to store and especially
+query across structurally different data. There exist various types of
+multi-model systems combining  distinct subsets of Big Data structures; hence,
+there naturally exists systems which combine graph data with other data models.
+For example, OrientDB\footnote{\url{http://orientdb.com/orientdb/}} which was
+implemented on the basis of an object DBMS currently supports graph, document,
+key/value, and object models.
 
-Such type of DBMSs also needs a specific benchmark/data generator which enables to test new features and analyze efficiency of operations.
-However, since the multi-model systems are in the context of Big Data rather new, there exist only a few benchmarks targeting multi-model DBMSs (such as Bigframe~\cite{journals/pvldb/KunjirKB14} or UniBench~\cite{conf/cidr/lu17}) with limited capabilities.
+Such type of DBMSs also needs a specific benchmark/data generator which enables
+to test new features and analyze efficiency of operations. However, since the
+multi-model systems are in the context of Big Data rather new, there exist only
+a few benchmarks targeting multi-model DBMSs (such as
+Bigframe~\cite{journals/pvldb/KunjirKB14} or UniBench~\cite{conf/cidr/lu17})
+with limited capabilities.
 
-\input{generators_community_detection}
+\subsection{Large scale graphs with realistic structure}
+
+Most of existing graph generators aiming at generating large graphs with realistic
+structural characteristics focus principally on reproducing the degree
+distribution and the clustering
+coefficient~\cite{kolda2014scalable,edunov2016darwini}. However, there are other
+structural characteristics one might be interested in reproducing for a large
+graph, such the diameter, the size of the largest connected component, or the
+hierarchical community structure. Graph practitioners are intersted in knowing
+how other high-level structural characteristics affect the performance of graph
+queries and graph algorithms. Thus, there is an open challenge to create
+graph generators that allow reproducing many other structural characteristics
+besides the degree or the clustering coefficient, that can also generat graphs
+at a scale.
+
+\subsection{Machine Learning based graph generation}
+
+With the advent of neural networks and specially generative adversarial networks
+(GANs)~\cite{goodfellow2014generative}, several researchers have started to
+explore their application to generate graphs. This is the case of
+~\cite{kipf2016variational,grover2018graphite,simonovsky2018graphvae,li2018learning,you2018graphrnn},
+which present several generative models to generate realistic graphs.  Such
+techniques still suffer from several problems. For instance, some of them are
+limited to learn from a single
+graph~\cite{kipf2016variational,grover2018graphite} or generate small
+graphs~\cite{simonovsky2018graphvae,li2018learning,you2018graphrnn}. The
+technique proposed in~\cite{you2018graphrnn} is capable of generating graphs
+with complex edge dependencies (e.g. community structure) and is not restricted
+to graphs of a fixed size. However, there is still in general several open
+challenges, including the capability of learning from and generating large graphs comparable
+in size to those typically used for benchmarking, and robust generation
+techniques with structural guarantees (e.g. degree distribution, clustering
+coefficient, etc.).

### 2018-07-18 data_sets.tex
graph stream generator

@@
 
-Besides graph data generators, many graph algorithms and systems are benchmarked
-using real graph data sets, including new graph data generation techniques. In
-this section we review the most widely used graph datasets in the literature and
-their purpose.
+Besides graph data generators, many graph algorithms and systems are benchmarked using real graph data sets, including new graph data generation techniques.
+In this section, we review the most widely used graph datasets in the literature and their purpose.
 
@@
 \begin{itemize}
-  \item Dblp~\cite{yang2015defining}: Represents a co-authorship network where
+  \item \textbf{DBLP}~\cite{yang2015defining}: Represents a co-authorship network where
     researchers from Dblp are represented as vertices, and there exists and edge
     between them if they have published a paper together.
-  \item Amazon~\cite{yang2015defining}: Represents a product co-purchasing
+  \item \textbf{Amazon}~\cite{yang2015defining}: Represents a product co-purchasing
     network, such that each vertex is a product and an edge between two products
     exists if a person has bought the two products.
-  \item Road networks~\cite{leskovec2009community}: Consist of a set of road
+  \item \textbf{Road networks}~\cite{leskovec2009community}: Consist of a set of road
     networks from the US.
-  \item LiveJournal~\cite{yang2015defining}: A social network where vertices
+  \item \textbf{LiveJournal}~\cite{yang2015defining}: A social network where vertices
     represent the users and the edges the acquitances between them.
-  \item Orkut~\cite{yang2015defining}: Like LiveJournal, this is a social network
+  \item \textbf{Orkut}~\cite{yang2015defining}: Like LiveJournal, this is a social network
     where vertices represent persons and the edges their friendships.
-  \item Twitter~\cite{kwak2010twitter}: This is a directed network representing
+  \item \textbf{Twitter}~\cite{kwak2010twitter}: This is a directed network representing
     the follower-followee interaction of Twitter.
-  \item Friendster~\cite{yang2015defining}: A social network like LiveJournal and
+  \item \textbf{Friendster}~\cite{yang2015defining}: A social network like LiveJournal and
     Orkut, where nodes represent persons and edges their relationships.
-  \item WebUK~\cite{delis}: A web graph of the UK subdomain, where nodes represent
+  \item \textbf{WebUK}~\cite{delis}: A web graph of the UK subdomain, where nodes represent
     websites and edges the hyperlinks between them.
-  \item ClueWeb2012~\cite{clueweb}. This is a crawl of the web from 2012, where
+  \item \textbf{ClueWeb2012}~\cite{clueweb}. This is a crawl of the web from 2012, where
     vertices represent websites and the edges the hyperlinks connecting them.
@@
 \begin{itemize}
-\item MovieLens~\cite{movielens}: Consists of a bipartite graph
+\item \textbf{MovieLens}~\cite{movielens}: Consists of a bipartite graph
   between users and movies, where edges represent the ratings the different
   users have made to the movies they watched.
-\item Book-Crossings~\cite{ziegler2005improving}: Is a dataset with book ratings
+\item \textbf{Book-Crossings}~\cite{ziegler2005improving}: Is a dataset with book ratings
   from users.
-\item Jester~\cite{goldberg2001eigentaste}: This dataset contains jokes (with
+\item \textbf{Jester}~\cite{goldberg2001eigentaste}: This dataset contains jokes (with
   their text) and ratings from users.
-\item Last.fm~\cite{hetrec}: This dataset contains the list of the top
+\item \textbf{Last.fm}~\cite{hetrec}: This dataset contains the list of the top
   most listened artists per user, including the number of times the songs from
@@
   be used to create content vectors.
-\item Netflix~\cite{zhou2008large}: This dataset was used during the famous
+\item \textbf{Netflix}~\cite{zhou2008large}: This dataset was used during the famous
   Netflix prize. It consists of a bipartite graph with movie ratings from users.
@@
   \begin{itemize}
-    \item Bitcoin~\cite{moore2013beware}: This dataset contains information from
+    \item \textbf{Bitcoin}~\cite{moore2013beware}: This dataset contains information from
       several Bitcoin exchanges, where users are able to rate other users after
@@
       which are labelled, the ratings between them.
-    \item Wikipedia RFA~\cite{west2014exploiting}: This is a network extracted
+    \item \textbf{Wikipedia RFA}~\cite{west2014exploiting}: This is a network extracted
       from Wikipedia, where the vertices represent users  and the
@@
       explaining the vote's sign.
-    \item WikiSigned~\cite{maniu2011building}: This is a network of Wikipedia
+    \item \textbf{WikiSigned}~\cite{maniu2011building}: This is a network of Wikipedia
       editors where the vertices are the editors and the edges, which are
       labelled, represent the turst level between two editors.
-    \item Extended Epinions~\cite{massa2007trust}: This is an extended version of
+    \item \textbf{Extended Epinions}~\cite{massa2007trust}: This is an extended version of
       the Epinions network which also contains the levels of distrust between the
       users, expressed by means of edges between them.
-    \item Twitter Indian Elections~\cite{kagan2015using}: This network represents
+    \item \textbf{Twitter Indian Elections}~\cite{kagan2015using}: This network represents
       a Twitter network where vertices represent users and there is an edge
@@
 \begin{itemize}
-  \item Dblp, Amazon, LiveJournal, Orkut and Friendster~\cite{yang2015defining}
+  \item \textbf{DBLP}, \textbf{Amazon}, \textbf{LiveJournal}, \textbf{Orkut} and \textbf{Friendster}~\cite{yang2015defining}
     are widely used for evaluating community detection since they provide
@@
     assignment.
-  \item Zachary Karate Club~\cite{zachary1977information}: This graph consists
+  \item \textbf{Zachary Karate Club}~\cite{zachary1977information}: This graph consists
     of a small networks of members of a karate club that was dismissed and split
@@
     karate clubs is provided.
-  \item PolBlogs~\cite{adamic2005political}: This is a network consisting of
+  \item \textbf{PolBlogs}~\cite{adamic2005political}: This is a network consisting of
     blogs talking about the US 2005 political elections, where a vertex
@@
     has an associated label, whehter it is left or right oriented.
-  \item PolBooks~\cite{10dimacs}: Is a network of books of Amazon that talk
+  \item \textbf{PolBooks}~\cite{10dimacs}: Is a network of books of Amazon that talk
     about politics, and edges between two books exist if they are co-purchased
     together. The books have labels of whether they are left or right oriented.
-  \item Football~\cite{girvan2002network}: A network of american university
+  \item \textbf{Football}~\cite{girvan2002network}: A network of american university
     football teams. Each node represents a football team and the edges represent
@@
 \begin{itemize}
-  \item Higgs-Twitter~\cite{de2013anatomy}: This dataset contains the Twitter
+  \item \textbf{Higgs-Twitter}~\cite{de2013anatomy}: This dataset contains the Twitter
     network before, during and after the discovery of the Higgs boson.
@@
     followers/followees, etc.
-  \item Memetracker~\cite{leskovec2009meme}: Memetracker is a dataset that
+  \item \textbf{Memetracker}~\cite{leskovec2009meme}: Memetracker is a dataset that
     contains the quotes and phrases that appear more frequently on the entire
@@
 \begin{itemize}
-  \item DbPedia~\cite{Bizer:2009:DCP:1640541.1640848}: The DBPedia project aims at creating
+  \item \textbf{DbPedia}~\cite{Bizer:2009:DCP:1640541.1640848}: The DBPedia project aims at creating
     a structured version of Wikipedia. It allows users to semantically query the
     relationships between the different resources at wikipedia.
-  \item Freebase~\cite{bollacker2008freebase}: Is a collaborative knowledge base
+  \item \textbf{Freebase}~\cite{bollacker2008freebase}: Is a collaborative knowledge base
     made of metadata mainly provided by community members. It contains
@@
     project was discontinued in 2014 and replaced by Wikidata.
-  \item Yago~\cite{suchanek2007yago}, Yago2~\cite{hoffart2013yago2} \&
+  \item \textbf{Yago}~\cite{suchanek2007yago}, \textbf{Yago2}~\cite{hoffart2013yago2} \&
     Yago3~\cite{mahdisoltani2013yago3}: These are
@@
     from Wikipedia and other sources.
-  \item Wikidata~\cite{vrandevcic2014wikidata}: This is a knowledge base
+  \item \textbf{Wikidata}~\cite{vrandevcic2014wikidata}: This is a knowledge base
     collaboratively edited by the community and hosted by the Wikimedia
@@
     Wikivoyage, Wikisource and others.
-  \item Billion Triple Challenge~\cite{btc-2014}: This is a semantic dataset
+  \item \textbf{Billion Triple Challenge}~\cite{btc-2014}: This is a semantic dataset
     crawled from different sources, including Freebase, DBPedia or the BBC. A

### 2018-07-24 generators_streaming.tex
Refactored graph streaming and community detection into others section
Removed strange character that was preventing compilation

@@
-\subsection{Graph Data Streaming}
+\subsubsection{Graph Data Streaming}
 \label{sec:generators_streaming}
+One way for dealing with big graph is to process them using the \emph{streaming} mode where the data stream could consist of the edges of the graph.
+In this mode, the graph processing algorithms can process the input stream in the order it arrives while using only a limited amount memory~\cite{mcgregor2014graph}.
+The streaming mode has attracted the attention of the RDF and Semantic Web community.
+Thus, Phuoc et al.~\cite{le2012linked} presented an evaluation framework for linked stream data processing engines.
+The framework uses a data generator for Stream Social network data Generator (\texttt{S2Gen}) that simulates what users continuously generate on their social network activities (e.g., posts) in addition to the  user metadata such as users' profile information, social network relationships, posts, photos and GPS information.
+The data generator of this framework provides the users the flexibility to control the characteristics of the generated data by tanning a range of parameters including the period in which the social activities are generated (generating period), the maximum number of posts/comments/photos for each user per week and the correlation probabilities between the different objects (e.g., users) in the social network.
 
-...
+Tommasini et al.~\cite{tommasini2017rsplab} introduced another framework for benchmarking RDF Stream Processing systems, \texttt{RSPLab}.
+The \texttt{Streamer} component of this framework is designed to publishe RDF streams from the various existing RDF benchmarks (e.g., BSBM, LUBM) (See Section~\ref{sec:generators_LinkedData}).
+In particular, the \texttt{Streamer}  component uses \texttt{TripleWave}, an open-source framework for publishing
+and sharing RDF streams on the Web~\cite{mauri2016triplewave}.
+\texttt{TripleWave}\footnote{\url{http://streamreasoning.github.io/TripleWave/}} acts as a mean for plugging in diverse Web data sources and for consuming streams in both push and pull mode.

### 2018-07-25 challenges.tex
Streaming Challenge

@@
 \subsection{Multi-model Data}
-With the dawn of Big Data and especially its Variety aspect there have emerged
+With the dawn of Big Data and especially its Variety aspect, there have emerged
 also new types of database management systems. One of the most interesting ones
@@
 implemented on the basis of an object DBMS currently supports graph, document,
-key/value, and object models.
-
-Such type of DBMSs also needs a specific benchmark/data generator which enables
+key/value, and object models. Such type of DBMSs also needs a specific benchmark/data generator which enables
 to test new features and analyze efficiency of operations. However, since the
@@
 coefficient, etc.).
+
+\subsection{Streaming Graph Generators}
+Stream computing is a new paradigm that is necessitated by various modern data generation scenarios such as the ubiquity of mobile devices, location services, 
+sensor pervasiveness and emerging Internet-of-Things (IoT) applications.
+These applications generate the data with \emph{high Velocity}, one of the main 3V characteristics of big data applications~\cite{sakr2016big}.
+In most of these high speed data generation scenarios, various objects are connected together with different relations and data exchanges  in a graph-structured manner.
+The Semantic Web community has been considering the aspect of implementing streaming RDF generator and benchmarks, however, there is still a clear lack on considering this aspect on other important and timely domains such as IoT.
+Thus, there is a crucial need to tackle this aspect.
+In addition, graph streaming generators should  consider some specific aspects for the stream processing domains such as the out-of-order handling (late arrivals)~\cite{li2008out} and the variety in the schemas and formats of the different data streaming sources.
+It is also recommended for the streaming graph generators to support the distributed environment as this is the most common scenario for such type of applications.

### 2018-08-09 introduction.tex
pass on the Intro/title/RW

@@
 %One of the most popular data structures in the world of computer science are graphs.
-Graphs are ubiquitous data structures that span a wide array of disciplines
-and are subject of study in several subfields of computer science.
+Graphs are ubiquitous data structures that span a wide array of scientific disciplines
+and are a subject of study in several subfields of computer science.
 Nowadays, due to the dawn of numerous tools and applications manipulating
-graphs, they are adopted as a rich data model in many data science use
+graphs, they are adopted as a rich data model in many data-intensive use
 cases involving disparate domain knowledge, mathematical foundations and
@@
 
-In this survey, we provide a comprehensive overview of the state-of-the-art graph generators by focusing on those that are pertinent and suitable for data science tasks.
-Our aim is to cover a wide range of currently popular areas of graph data processing.
-In particular, we consider graph generation in the areas of graph databases, graph data mining, graph streaming and machine learning communities, alongside community detection, social networks and IoT communities.
-Despite the disparate requirements of graph generators throughout these communities, we analyze them under a common umbrella, reaching out the functionalities, the practical usage, and the supported operations of graph generators.
+In this survey, we provide a comprehensive overview of the state-of-the-art
+modern
+graph generators by focusing on those that are pertinent and suitable for
+data-intensive tasks. Our aim is to cover a wide range of currently popular
+areas of graph data processing. In particular, we consider graph generation
+in the areas of graph databases, graph data mining, graph streaming and
+machine learning communities, alongside community detection, social
+networks and IoT communities.
+Despite the disparate requirements of modern graph generators throughout these communities, we analyze them under a common umbrella, reaching out the functionalities, the practical usage, and the supported operations of graph generators.
 The reasons for this scope and classification are as follows:
@@
 \begin{enumerate}
-  \item Despite the differences of the covered areas, the requirements for the graph data generators can be similar in particular cases.
-Reusing or learning from tools in other fields can thus bring new opportunities for both researchers and practitioners.
-  \item The selected classification is serving the need of providing data scientists, researchers and practitioners with the right data generator at hand for their work.
+  \item Despite the differences of the covered areas, the requirements for
+modern graph data generators can be similar in particular cases. Reusing or learning from tools in other fields can thus bring new opportunities for both researchers and practitioners.
+  \item The selected classification is serving the need of providing scientists, researchers and practitioners with the right data generator at hand for their work.
 \end{enumerate}
 
-To conclude the comparative study and provide a comprehensive view of the field,  we also discuss open challenges and missing features of graph generators in view of identifying future challenges in data science.
+To conclude the comparative study and provide a comprehensive view of the
+field,  we also discuss open challenges and missing requirements of modern
+graph generators in view of identifying their future extensions to new emerging fields.
 
-\paragraph*{Contributions} Our survey reviews the representatives of graph data generators and summarizes their major features.
+\paragraph*{Contributions} Our survey revisits the representatives of
+modern graph data generators and summarizes their major features.
 The comprehensive review and analysis make this paper useful for motivating new graph data generation techniques as well as serving as a technical reference for selecting suitable solutions.
@@
 To the best of our knowledge, our work is the first surveying the broad
-landscape of graph data generators spanning different data science applications and
-targeting diverse computer science subfields. In particular, we cover graph database
+landscape of graph data generators spanning different data-intensive applications and
+targeting many computer science subfields. In particular, we cover graph database
 generators, graph processing generators, social networks and community detection
@@
 and Machine Learning and graph mining generators. A comprehensive study of
-graph generators is missing for many of the specific subfields mentioned
+graph generators is yet missing for many of the specific subfields mentioned
 above.
@@
 distinguished chokepoints. However, the provided classification is
-inherently data-driven and not meant to serve the purpose of letting any
-researcher or practitioner interested in data science make a guided
-choice of the desired
+inherently database-oriented. 
+In our work, we provide a more comprehensive and broader classification 
+ serving the purpose of letting any
+researcher or practitioner interested in data generation make a wise
+choice of the desired graph 
 generator based on its functional and goal-driven features (such as the application domain,
 the supported operations and the key configuration options).
-Moreover, our work is much broader and targets graph generators of several
-diversified communities, not limiting its scope to few generators of the database
+Moreover, in contrast with \cite{BFHI18}, our work encompasses graph generators of several
+diverse communities, not limiting its scope to a few generators of the database
 and graph processing communities.
@@
 graph mining generators that fervently appeared in the last decade.
+We fill the gap of more recent social network and graph analytics generators
+respectively in Section 3.4 and 3.5.
 
-\TODO{Check with Arnau}
+%\TODO{Check with Arnau}
 
@@
 recursion with recursive tensor multiplication \cite{AkogluMF08}.
-
-\TODO{Better highlight the differences when Sherif's part is in.}
+We refer the reader to this survey for evolutionary network generators and
+we further discuss the open challenges of evolving graph data in Section 5. 
+%\TODO{Better highlight the differences when Sherif's part is in.}
 

### 2018-08-09 main.tex
Missing parts of intro added
Sherif Changes
pass on the Intro/title/RW

@@
 % Page heads
-\markboth{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr}{Graph Generators for Data Science: A Survey}
+\markboth{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr}{Modern Graph Generators: A Survey}
 
@@
 %\title{Graph Data Generators in the World of Big Data}
-\title{Graph Generators for Data Science: A Survey}
+\title{Modern Graph Generators: A Survey}
 \author{
@@
 SHERIF SAKR
-\affil{King Saud bin Abdulaziz University for Health Sciences, Saudi Arabia}
+\affil{University of Tartu, Estonia}
 }
@@
 \begin{abstract}
-The abundance of interconnected data has fueled the design and implementation of graph generators reproducing real-world linking properties, or gauging the effectiveness of graph algorithms, techniques and applications manipulating these data.
-We consider graph generation targeting multiple subfields, such as graph databases, graph data mining, graph streaming and machine learning communities, alongside community detection, social networks and IoT communities.
-Despite the disparate requirements of graph generators throughout these communities, we analyze them under a common umbrella, reaching out the functionalities, the practical usage, and the supported operations of graph generators.
-We argue that this classification is serving the need of providing data scientists, researchers and practitioners with the right data generator at hand for their work.
+The abundance of interconnected data has fueled the design and
+implementation of graph generators reproducing real-world linking
+properties, or gauging the effectiveness of graph algorithms, techniques
+and applications manipulating these data. We consider graph generation
+across multiple subfields, such as graph databases, graph data mining,
+graph streaming and machine learning communities, alongside community
+detection, social networks and IoT communities. Despite the disparate
+requirements of modern graph generators throughout these communities, we
+analyze them under a common umbrella, reaching out the functionalities, the
+practical usage, and their supported operations.
+We argue that this classification is serving the need of providing scientists, researchers and practitioners with the right data generator at hand for their work.
 
-This survey provides a comprehensive overview of the state-of-the-art graph generators by focusing on those that are pertinent and suitable for data science tasks.
-Finally, we discuss open challenges and missing features of graph generators in view of the evolution of data science.
+This survey provides a comprehensive overview of the state-of-the-art
+modern graph generators by focusing on those that are pertinent and
+suitable for several data-intensive tasks. Finally, we discuss open
+challenges and missing requirements of current graph generators along with their future extensions to new emerging fields.
 \end{abstract}
@@
 
-\acmformat{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr, 2018. Graph Generators for Data Science: A Survey.}
+\acmformat{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr, 2018.
+Modern Graph Generators: A Survey.}
 % At a minimum you need to supply the author names, year and a title.
@@
 \input{introduction}
-\input{preliminaries}
+%\input{preliminaries}
 \input{comparison}
@@
 %\input{comparison2}
+\input{data_sets}
 \input{challenges}

### 2018-08-09 challenges.tex
added subsection 5.7 - challenges

@@
 Most of existing graph generators generate graphs that are either not labeled or
-are specific of a given domain (e.g.  Social Networks). Graphs from different
+are specific to a given domain (e.g.  Social Networks). Graphs from different
 domains have different schemas, structural characteristics, property
@@
 application under test. Thus, graph processing engine developers are asking for
-generators or tools to generate graphs flexibily, allowing to configure aspects
-such as the size, the schema, the data distributions and other structural
-characteristics such as the degree distribution, the clustering coefficient,
-etc.
+generators or tools to flexibly and holistically generate multi-domain graphs, allowing to configure aspects
+such as size, schemata, data distributions and other structural
+characteristics such as degree distributions, clustering coefficients, and
+so on.
 
 \subsection{Simple Usage, Simple Parameters}
-Proposal of a data generator (not necessarily for graph data) has to face an
-important schism. On the one hand, there is the aim to provide the user with as
-many parameters as possible in order to enable one to generate any kind of data.
-This approach seems to be reasonable, but it encounters the fact that users are
-usually unwilling to use complex benchmarking tools. This observation can be
+The proposal of a data generator (not necessarily for graph data) has to face an
+important schism. On one hand, it must provide the user with as
+many parameters as possible in order to enable him/her to generate
+arbitrary data.
+This approach seems to be reasonable, but it entails a shortcoming due to
+the fact that ordinary users are
+unwilling to use complex benchmarking tools. This observation can be
 seen, for example, in the case of XML benchmarks -- even though there exist
@@
 structural aspects, value distributions, references etc.), the most popular
-benchmarking tool is XMark~\cite{Schmidt:2002:XBX:1287369.1287455} which models
+benchmarking tool is XMark~\cite{Schmidt:2002:XBX:1287369.1287455}, which models
 a single use case and enables to specify just the size of the data. Hence, the
 other extreme is to provide a simple data generator which does not require any
-complex settings and thus the benchmarking process is extremely simple and fast.
+complex settings and thus guarantees a simple and fast benchmarking process.
 
 Considering the complex structure of graph data and the variety of applications
-having highly specific types of graphs, the latter solution is difficult to
-implement. A reasonable compromise can thus be seen in a data generator which is
-provided with sample graph data and is capable of automatic analysis of their
-structural and value specifics in order to gain the complex parameters.
+requiring highly specific types of graphs, the latter solution is difficult to
+implement. A reasonable compromise can be found in a data generator which is
+provided with sample graph data and is capable of automatic analysis of its
+structural and value features in order to learn the complex parameters.
 
@@
 usually influences the structure of the data and consequently all the related
-parts of the application (i.e., storage strategies, operations, indices etc.).
+parts of the application (i.e., storage strategies, operations, indexes etc.).
 The respective data generator should hence be able to simulate such a growth
@@
 A related problem is \emph{data versioning} and respective ability to query
-across multiple versions of data or in general its analysis. Considering graph
-data this problem is also common, for example  in the area of Linked
-Data~\cite{DBLP:conf/semweb/Papakonstantinou16,DBLP:conf/esws/MeimarisP16,fernandez2015towards,fernandez2015bear}.
+across multiple versions of data or to carry out general analysis. 
+%Considering graph
+%data this problem is also common, for example  in the area of Linked
+This problem has been investigated for instance within the domain of Linked
+Open Data~\cite{DBLP:conf/semweb/Papakonstantinou16,DBLP:conf/esws/MeimarisP16,fernandez2015towards,fernandez2015bear}.
 
-As shown in
-papers~\cite{Leskovec:2005:RMT:2101235.2101254,Leskovec:2005:GOT:1081870.1081893},
+As shown in~\cite{Leskovec:2005:RMT:2101235.2101254,Leskovec:2005:GOT:1081870.1081893},
 evolving graphs have further specific features. For example, some graphs grow
@@
 \subsection{Multi-model Data}
-With the dawn of Big Data and especially its Variety aspect, there have emerged
-also new types of database management systems. One of the most interesting ones
-are so-called \emph{multi-model databases} which enable to store and especially
+With the dawn of Big Data and especially its variety aspect, new types of
+database management systems have emerged. One of the most interesting ones
+are the so-called \emph{multi-model databases} that enable to store and
+thus
 query across structurally different data. There exist various types of
-multi-model systems combining  distinct subsets of Big Data structures; hence,
-there naturally exists systems which combine graph data with other data models.
+multi-model systems combining  distinct subsets of Big Data structures,
+such as for instance systems that combine graph data with other data models.
 For example, OrientDB\footnote{\url{http://orientdb.com/orientdb/}} which was
 implemented on the basis of an object DBMS currently supports graph, document,
-key/value, and object models. Such type of DBMSs also needs a specific benchmark/data generator which enables
+key/value, and object models. Such type of DBMSs also needs a specific
+benchmarking data generator that would enable
 to test new features and analyze efficiency of operations. However, since the
@@
 with limited capabilities.
+Another interesting approach to multi-model data is to adopt a unifying
+expressive graph data model, known as property graph data
+model~\cite{BFVY18}. Such a model allows to specify multi-edges and list of
+properties for the nodes. Synthetic graph generators for property graphs and its
+companion standard graph query language~\cite{Angles18,AnglesABBFGLPPS18} are also needed in order to boost
+their availability and adoption for different communities.
 
@@
 graph, such the diameter, the size of the largest connected component, or the
-hierarchical community structure. Graph practitioners are intersted in knowing
+hierarchical community structure. Graph practitioners are highly interested in knowing
 how other high-level structural characteristics affect the performance of graph
-queries and graph algorithms. Thus, there is an open challenge to create
-graph generators that allow reproducing many other structural characteristics
-besides the degree or the clustering coefficient, that can also generat graphs
-at a scale.
+queries and graph algorithms. Hence, a compelling open challenge consists
+of creating
+graph generators that allow to reproduce diverse structural characteristics
+of the graphs along with large scale sizes.
 
@@
 
+\subsection{Generating noisy graphs and graphs with anomalies}
+Injecting noise and/or anomalies and errors into graphs is crucial for
+testing both machine learning algorithms working on this complex data and 
+data quality techniques aiming at detecting anomalies and repairing graph
+data.
+
+Concerning the former, analyzing and labelling structural networks is
+deemed to be more difficult for graph datasets in the presence of noise. 
+Since denoising graph data is difficult to achieve, several machine learning
+techniques have been adapted to work with noise (i.e. mislabeled
+samples) or outliers, such as 
+imbalanced graph classification \cite{PanZ13} and 
+binary graph classification with positive and negative weights \cite{CheungSML16}.  
+Synthetic graph generators that take into account noisy and missing data 
+have been studied in \cite{NamataG10}, where graph identification is presented in
+order to  model the inference of a cleaned output network from a
+noisy input graph.
+Concerning the latter, data quality techniques handling graph data are recently considering ad-hoc
+generation of graph data and graph quality rules in order to assess the
+effectiveness of error detection and data repairing algorithms \cite{FanWX16a,AriouaB18}. The
+corresponding graph quality rules are typically handcrafted by domain
+experts, whereas an automatic generation of such rules along with the graph
+data generation in tandem would be an interesting future challenge for the
+community.
+
 \subsection{Streaming Graph Generators}

### 2018-08-22 comparison.tex
Sherif Changes
Better explanation of the classiffication

@@
 It generates weighted, directed and bipartite graphs.
-Graph generation is modeled with a matrix recursion procedure in which the adjacency matrix (empty at the beginning) is recursively subdivided into four equal-sized partitions and edges are distributed across the partitions with unequal probabilities.
+Graph generation is modeled with a matrix recursion -procedure in which the adjacency matrix (empty at the beginning) is recursively subdivided into four equal-sized partitions and edges are distributed across the partitions with unequal probabilities.
 
@@
 
-We decided to classify the generators primarily on the basis of the respective application domains or communities.
+At first we classify the generators on the basis of the respective application domains or user communities.
+The selected classes are not rigorously defined (e.g., they are not disjoint as we will show later), but they correspond to the currently most active research areas.
+Thus we believe that they form a natural first acquaintance for the reader.
+
 In Tables~\ref{tab:comparisonCharacteristicsA},~\ref{tab:comparisonCharacteristicsB}   we overview the key characteristics of the data generators clustered according to the respective application domains.
@@
 \cline{2-10}
-  & Watts-Strogatz~\cite{watts1998collective} & fixed & & Y & N & Y &  & &  N  \\
-\cline{2-10}
+%  & Watts-Strogatz~\cite{watts1998collective} & fixed & & Y & N & Y &  & &  N  \\
+%\cline{2-10}
   & Preferential Attachment~\cite{barabasi1999emergence} & fixed & & Y & N & Y &  & &  N  \\
@@
 \multirow{5}{*}{\rot{\textbf{Streaming}}}
-  & & & & & & & & &    \\
+  & S2Gen & schema-driven & Social Network & Y & N & N & user-defined & RDF & N     \\
 \cline{2-10}
-  & & & & & & & & &    \\
+  & RSPLab & schema-driven & Agnostic & Y & Y & N & user-defined & RDF & N     \\
 \cline{2-10}

### 2018-09-01 challenges.tex
Temporal gaphs - update

@@
 parts of the application (i.e., storage strategies, operations, indexes etc.).
-The respective data generator should hence be able to simulate such a growth
-and/or change in structure.
+In the world of graph data such graphs that change with time are denoted as \emph{evolving}, \emph{temporal}, \emph{dynamic}, or \emph{time-varying}.
+They can be viewed as labeled graphs, where the labels capture some measure of time~\cite{Michail2015}.
 
+The evolution of graphs can be considered variously.
+We can assume a static set of nodes and a varying set of edges.
+Or, there are applications where the graphs only ``grow'', i.e., the set of nodes and/or edges is only extended with new items.
+In the most general case we can assume any changes in both set of nodes and set of edges.
+Anyway with the evolution aspect the complexity of classical graph problems increases significantly~\cite{Michail2015,Wu:2014:PPT:2732939.2732945}.
 In some graph applications, such as, e.g., social networks, the evolution of the
-data is a significant aspect, especially in the activity graphs, that has been
-studied
-extensively~\cite{doreian1997evolution,Kumar:2006:SEO:1150402.1150476,Hellmann2014583,wang2013,Kossinets88,Viswanath:2009:EUI:1592665.1592675}.
-A related problem is \emph{data versioning} and respective ability to query
-across multiple versions of data or to carry out general analysis. 
+data is a significant aspect, especially in the activity graphs~\cite{doreian1997evolution,Kumar:2006:SEO:1150402.1150476,Hellmann2014583,wang2013,Kossinets88,Viswanath:2009:EUI:1592665.1592675}.
+However, as shown in~\cite{Leskovec:2005:RMT:2101235.2101254,Leskovec:2005:GOT:1081870.1081893},
+evolving graphs have further specific features.
+For example, some graphs grow over time according to a \emph{densification power law} which means that real graphs tend to sprout many more edges than nodes, and thus are densifying as they grow.
+Also the effective diameter of graphs tends to shrink or stabilize as the graph grows with time.
+
+A related problem is \emph{data versioning} and respective ability to query across multiple versions of data or to carry out general analysis. 
 %Considering graph
@@
 
-As shown in~\cite{Leskovec:2005:RMT:2101235.2101254,Leskovec:2005:GOT:1081870.1081893},
-evolving graphs have further specific features. For example, some graphs grow
-over time according to a \emph{densification power law} which means that real
-graphs tend to sprout many more edges than nodes, and thus are densifying as
-they grow. Also the effective diameter of graphs tends to shrink or stabilize as
-the graph grows with time.
+The respective data generator should hence be able to simulate a natural growth and/or changes in the structure of the graph with regards to the various features of distinct use cases.
+However,  even though the area of dynamic graphs is intensively studied, surprisingly there seem to exist only very few proposals of a respective generator.
+
+In~\cite{GoerkeKlugeSchumm2012_1000029825} the authors focus on \emph{clustering dynamic graphs}, i.e.
+graphs where the clustering corresponds to the partition of nodes into natural groups based on the paradigm of intra-cluster density versus inter-cluster sparsity of edges.
+The generator generates a time series of random graphs $G_0, G_1, ...
+G_n$, where $G_t$ emerges from $G_{t-1}$ via atomic updates, i.e., the insertion or deletion of an edge or vertex.
+The generator keeps track of a (dynamic) ground truth clustering.
+The probability of atomic events is chosen in a way that adheres to this clustering, without losing randomness.
+
+A recent proposal of a generator~\cite{mlg2018_42} of temporal graphs results from the observation that small subgraph patterns in networks, called \emph{network motifs} or \emph{graphlets}, are crucial indicators of the structure and the evolution of the graphs~\cite{Paranjape:2017:MTN:3018661.3018731}.
+For a given graph $G$ and a predefined ordered list of structural atomic motifs $M$ the generator first computes the distribution of the motifs in the graph.
+The distribution is then used to generate a synthetic graph with the same features.
 

### 2018-09-01 data_sets.tex
Minor corrections

@@
-\section{Graph Data Sets}
+\section{Graph Datasets}
+\label{sec:data_sets}
 
-Besides graph data generators, many graph algorithms and systems are benchmarked using real graph data sets, including new graph data generation techniques.
+Besides graph data generators, many graph algorithms and systems are benchmarked using real-world graph data sets, including new graph data generation techniques.
 In this section, we review the most widely used graph datasets in the literature and their purpose.
@@
 Large scale graph analytics systems are usually benchmarked using a combination of
-real and synthetically generated graphs. Because of the rapid evolution of such
+real-world and synthetically generated graphs. Because of the rapid evolution of such
 systems and their increasing capability to process larger graphs, the datasets
 typically used  in the literature quickly change overtime. The most commonly
-used datasets are, which can be downloaded from several graph dataset
-repositories~\cite{snapnets,lawalgo}:
+used datasets (which can be downloaded from several graph dataset
+repositories~\cite{snapnets,lawalgo}) are:
 \begin{itemize}
   \item \textbf{DBLP}~\cite{yang2015defining}: Represents a co-authorship network where
-    researchers from Dblp are represented as vertices, and there exists and edge
+    researchers from DBLP are represented as vertices and there exists and edge
     between them if they have published a paper together.
@@
 
-\paragraph{Recommender Systems }
+\paragraph{Recommender Systems}
 
 Many recommender systems are based on graphs, either bipartite graphs or
-many-to-many graphs. Such systems are usually tested on several real datasets,
+many-to-many graphs. Such systems are usually tested on several real-world datasets,
 many of them containing information about rating of products or other items such
@@
 compare graph partitioning, clustering and community detection algorithms. One
-can find a comprehensive lists of datasets for such algorithms
+can find a comprehensive list of datasets for such algorithms
 in~\cite{10dimacs,yang2015defining}, some of them already discussed for other
@@
   \item \textbf{Zachary Karate Club}~\cite{zachary1977information}: This graph consists
-    of a small networks of members of a karate club that was dismissed and split
+    of a small network of members of a karate club that was dismissed and split
     into two new karate clubs. Vertices represent persons and edges friendship
@@
     represents a blog and the edges the hyperlinks between the blogs. Each blog
-    has an associated label, whehter it is left or right oriented.
+    has an associated label, whether it is left or right oriented.
   \item \textbf{PolBooks}~\cite{10dimacs}: Is a network of books of Amazon that talk
@@
 
-\paragraph{Information Diffussion}
+\paragraph{Information Diffusion}
 
@@
     news spectrum. It consists of the links of the news, the time and memes, and
-    is used to understand how information spanws, evolves and dies.
+    is used to understand how information spawns, evolves and dies.
 \end{itemize}
@@
 
-Semantic web and RDF engines have a well accepted set of real datasets, used to
+Semantic web and RDF engines have a well accepted set of real-world datasets, used to
 test reasoning engines as well as to use as baselines for the creation of new
@@
     a structured version of Wikipedia. It allows users to semantically query the
-    relationships between the different resources at wikipedia.
+    relationships between the different resources at Wikipedia.
   \item \textbf{Freebase}~\cite{bollacker2008freebase}: Is a collaborative knowledge base
@@
   \item \textbf{Yago}~\cite{suchanek2007yago}, \textbf{Yago2}~\cite{hoffart2013yago2} \&
-    Yago3~\cite{mahdisoltani2013yago3}: These are
+    \textbf{Yago3}~\cite{mahdisoltani2013yago3}: These are
     open source knowledge bases developed at the Max Planck Institute of
-    Computer Science in Saarbr\"ucken. It contains structured data automatically extracted
+    Computer Science in Saarbr\"ucken. They contain structured data automatically extracted
     from Wikipedia and other sources.

### 2018-09-01 introduction.tex
Minor corrections

@@
 In the former case we can search, e.g., for communities and their features or shortest paths, while in the latter case we usually query for supergraphs, subgraphs or graphs similar to a given graph pattern.
-Also, as in the other fields, quite often the respective real-world graph data is not publicly available (or simply does not exist when a particular method for data manipulation is proposed).
+In both the cases, as in the other fields, quite often the respective real-world graph data is not publicly available (or simply does not exist when a particular method for data manipulation is proposed).
 Even in the cases in which real data is abundant, many algorithms and techniques need to be tested on various order of magnitudes of the graph sizes thus leading to the inception of
@@
 In Section~\ref{sec:generators} we overview the existing graph data generators and their main features in the frame of the proposed categories.
+To provide a complete overview, in Section~\ref{sec:data_sets} we list most commonly used testing data sets for the particular categories.
 In Section~\ref{sec:challenges} we discuss challenges and open problems of graph data synthesis and in Section~\ref{sec:conclusion} we conclude.

### 2018-09-02 challenges.tex
Minor corrections, change of order of subsections

@@
 
-In this section, we discuss several of the open challenges in large scale graph
-generation.
+To conclude the  overview of the state-of-the-art of graph data generation, in this section we discuss several of the open challenges.
 
-\subsection{Single- vs. multi-domain}
-
-Most of existing graph generators generate graphs that are either not labeled or
-are specific to a given domain (e.g.  Social Networks). Graphs from different
-domains have different schemas, structural characteristics, property
-distributions, etc. which might have an impact on the performance of the
-application under test. Thus, graph processing engine developers are asking for
-generators or tools to flexibly and holistically generate multi-domain graphs, allowing to configure aspects
-such as size, schemata, data distributions and other structural
-characteristics such as degree distributions, clustering coefficients, and
-so on.
-
-\subsection{Simple Usage, Simple Parameters}
+\subsection{Simple Usage, simple Parameters}
 The proposal of a data generator (not necessarily for graph data) has to face an
@@
 
-\subsection{Evolving Graph Data}
-As user requirements as well as environments change, most of the existing
-applications naturally evolve over time, at least to some extent. This evolution
-usually influences the structure of the data and consequently all the related
-parts of the application (i.e., storage strategies, operations, indexes etc.).
-In the world of graph data such graphs that change with time are denoted as \emph{evolving}, \emph{temporal}, \emph{dynamic}, or \emph{time-varying}.
-They can be viewed as labeled graphs, where the labels capture some measure of time~\cite{Michail2015}.
-
-The evolution of graphs can be considered variously.
-We can assume a static set of nodes and a varying set of edges.
-Or, there are applications where the graphs only ``grow'', i.e., the set of nodes and/or edges is only extended with new items.
-In the most general case we can assume any changes in both set of nodes and set of edges.
-Anyway with the evolution aspect the complexity of classical graph problems increases significantly~\cite{Michail2015,Wu:2014:PPT:2732939.2732945}.
-In some graph applications, such as, e.g., social networks, the evolution of the
-data is a significant aspect, especially in the activity graphs~\cite{doreian1997evolution,Kumar:2006:SEO:1150402.1150476,Hellmann2014583,wang2013,Kossinets88,Viswanath:2009:EUI:1592665.1592675}.
-However, as shown in~\cite{Leskovec:2005:RMT:2101235.2101254,Leskovec:2005:GOT:1081870.1081893},
-evolving graphs have further specific features.
-For example, some graphs grow over time according to a \emph{densification power law} which means that real graphs tend to sprout many more edges than nodes, and thus are densifying as they grow.
-Also the effective diameter of graphs tends to shrink or stabilize as the graph grows with time.
-
-A related problem is \emph{data versioning} and respective ability to query across multiple versions of data or to carry out general analysis. 
-%Considering graph
-%data this problem is also common, for example  in the area of Linked
-This problem has been investigated for instance within the domain of Linked
-Open Data~\cite{DBLP:conf/semweb/Papakonstantinou16,DBLP:conf/esws/MeimarisP16,fernandez2015towards,fernandez2015bear}.
-
-The respective data generator should hence be able to simulate a natural growth and/or changes in the structure of the graph with regards to the various features of distinct use cases.
-However,  even though the area of dynamic graphs is intensively studied, surprisingly there seem to exist only very few proposals of a respective generator.
-
-In~\cite{GoerkeKlugeSchumm2012_1000029825} the authors focus on \emph{clustering dynamic graphs}, i.e.
-graphs where the clustering corresponds to the partition of nodes into natural groups based on the paradigm of intra-cluster density versus inter-cluster sparsity of edges.
-The generator generates a time series of random graphs $G_0, G_1, ...
-G_n$, where $G_t$ emerges from $G_{t-1}$ via atomic updates, i.e., the insertion or deletion of an edge or vertex.
-The generator keeps track of a (dynamic) ground truth clustering.
-The probability of atomic events is chosen in a way that adheres to this clustering, without losing randomness.
-
-A recent proposal of a generator~\cite{mlg2018_42} of temporal graphs results from the observation that small subgraph patterns in networks, called \emph{network motifs} or \emph{graphlets}, are crucial indicators of the structure and the evolution of the graphs~\cite{Paranjape:2017:MTN:3018661.3018731}.
-For a given graph $G$ and a predefined ordered list of structural atomic motifs $M$ the generator first computes the distribution of the motifs in the graph.
-The distribution is then used to generate a synthetic graph with the same features.
-
-%\paragraph{} Following the same recursion idea,
-%paper~\cite{Leskovec:2005:RMT:2101235.2101254} uses Kronecker multiplication to
-%generate self-similar graphs. The network starts with an initial graph G1 that
-%contains $N_1$ nodes and $E_1$ edges. Using matrix recursion, larger successive
-%graphs $G_2, G_3, ... G_n$ are generated. The $k$-th graph $G_k$ contains $N_k
-%= N^k_1$ nodes. Many graphs often densify over time, exhibiting a growth in the
-%number of edges that is superlinear to the number of nodes. Kronecker
-%multiplication produces graphs with a fixed diameter and a densification power
-%law degree distribution with exponent $k = log(E_1)/log(N_1)$. The graph
-%generation process introduces a staircase effect in the nodes' degrees, and
-%each community consists of smaller nested communities that are formed through
-%expansion and recursion.
-
-\subsection{Multi-model Data}
-With the dawn of Big Data and especially its variety aspect, new types of
-database management systems have emerged. One of the most interesting ones
-are the so-called \emph{multi-model databases} that enable to store and
-thus
-query across structurally different data. There exist various types of
-multi-model systems combining  distinct subsets of Big Data structures,
-such as for instance systems that combine graph data with other data models.
-For example, OrientDB\footnote{\url{http://orientdb.com/orientdb/}} which was
-implemented on the basis of an object DBMS currently supports graph, document,
-key/value, and object models. Such type of DBMSs also needs a specific
-benchmarking data generator that would enable
-to test new features and analyze efficiency of operations. However, since the
-multi-model systems are in the context of Big Data rather new, there exist only
-a few benchmarks targeting multi-model DBMSs (such as
-Bigframe~\cite{journals/pvldb/KunjirKB14} or UniBench~\cite{conf/cidr/lu17})
-with limited capabilities.
-Another interesting approach to multi-model data is to adopt a unifying
-expressive graph data model, known as property graph data
-model~\cite{BFVY18}. Such a model allows to specify multi-edges and list of
-properties for the nodes. Synthetic graph generators for property graphs and its
-companion standard graph query language~\cite{Angles18,AnglesABBFGLPPS18} are also needed in order to boost
-their availability and adoption for different communities.
-
-\subsection{Large scale graphs with realistic structure}
+\subsection{Large Scale Graphs with Realistic Structure}
 
@@
 structural characteristics one might be interested in reproducing for a large
-graph, such the diameter, the size of the largest connected component, or the
+graph, such as the diameter, the size of the largest connected component, or the
 hierarchical community structure. Graph practitioners are highly interested in knowing
@@
 
-\subsection{Machine Learning based graph generation}
+\subsection{Single- vs. Multi-domain}
 
-With the advent of neural networks and specially generative adversarial networks
-(GANs)~\cite{goodfellow2014generative}, several researchers have started to
-explore their application to generate graphs. This is the case of
-~\cite{kipf2016variational,grover2018graphite,simonovsky2018graphvae,li2018learning,you2018graphrnn},
-which present several generative models to generate realistic graphs.  Such
-techniques still suffer from several problems. For instance, some of them are
-limited to learn from a single
-graph~\cite{kipf2016variational,grover2018graphite} or generate small
-graphs~\cite{simonovsky2018graphvae,li2018learning,you2018graphrnn}. The
-technique proposed in~\cite{you2018graphrnn} is capable of generating graphs
-with complex edge dependencies (e.g. community structure) and is not restricted
-to graphs of a fixed size. However, there is still in general several open
-challenges, including the capability of learning from and generating large graphs comparable
-in size to those typically used for benchmarking, and robust generation
-techniques with structural guarantees (e.g. degree distribution, clustering
-coefficient, etc.).
+Most of existing graph generators generate graphs that are either not labeled or
+are specific to a given domain (e.g.  Social Networks). Graphs from different
+domains have different schemas, structural characteristics, property
+distributions, etc. which might have an impact on the performance of the
+application under test. Thus, graph processing engine developers are asking for
+generators or tools to flexibly and holistically generate multi-domain graphs, allowing to configure aspects
+such as size, schemata, data distributions and other structural
+characteristics such as degree distributions, clustering coefficients, and
+so on.
 
-\subsection{Generating noisy graphs and graphs with anomalies}
+\subsection{Generating Noisy Graphs and Graphs with Anomalies}
 Injecting noise and/or anomalies and errors into graphs is crucial for
@@
 Stream computing is a new paradigm that is necessitated by various modern data generation scenarios such as the ubiquity of mobile devices, location services,
-sensor pervasiveness and emerging Internet-of-Things (IoT) applications.
-These applications generate the data with \emph{high Velocity}, one of the main 3V characteristics of big data applications~\cite{sakr2016big}.
+sensor pervasiveness and emerging IoT applications.
+These applications generate the data with high Velocity, one of the main 3V characteristics of big data applications~\cite{sakr2016big}.
 In most of these high speed data generation scenarios, various objects are connected together with different relations and data exchanges  in a graph-structured manner.
-The Semantic Web community has been considering the aspect of implementing streaming RDF generator and benchmarks, however, there is still a clear lack on considering this aspect on other important and timely domains such as IoT.
-Thus, there is a crucial need to tackle this aspect.
+The Semantic Web community has been considering the aspect of implementing streaming RDF generator and benchmarks, however, there is still a clear lack on considering this aspect in other important and timely domains such as IoT.
+%Thus, there is a crucial need to tackle this aspect.
 In addition, graph streaming generators should  consider some specific aspects for the stream processing domains such as the out-of-order handling (late arrivals)~\cite{li2008out} and the variety in the schemas and formats of the different data streaming sources.
 It is also recommended for the streaming graph generators to support the distributed environment as this is the most common scenario for such type of applications.
+
+\subsection{Evolving Graph Data}
+As user requirements as well as environments change, most of the existing
+applications naturally evolve over time, at least to some extent. This evolution
+usually influences the structure of the data and consequently all the related
+parts of the application (i.e., storage strategies, operations, indexes etc.).
+In the world of graph data such graphs that change with time are denoted as \emph{evolving}, \emph{temporal}, \emph{dynamic}, or \emph{time-varying}.
+They can be modelled as labeled graphs, where the labels capture some measure of time~\cite{Michail2015}.
+
+The evolution of graphs can be considered variously.
+We can assume a static set of nodes and a varying set of edges.
+Or, there are applications where the graphs only ``grow'', i.e., the set of nodes and/or edges is only extended with new items.
+In the most general case we can assume any changes in both set of nodes and set of edges.
+Anyway with the evolution aspect the complexity of classical graph problems increases significantly~\cite{Michail2015,Wu:2014:PPT:2732939.2732945}.
+In some graph applications, such as, e.g., social networks, the evolution of the
+data is a significant aspect, especially in the activity graphs~\cite{doreian1997evolution,Kumar:2006:SEO:1150402.1150476,Hellmann2014583,wang2013,Kossinets88,Viswanath:2009:EUI:1592665.1592675}.
+However, as shown in~\cite{Leskovec:2005:RMT:2101235.2101254,Leskovec:2005:GOT:1081870.1081893},
+evolving graphs have further specific features.
+For example, some graphs grow over time according to a \emph{densification power law} which means that real graphs tend to sprout many more edges than nodes, and thus are densifying as they grow.
+Also the effective diameter of graphs tends to shrink or stabilize as the graph grows with time.
+
+A related problem is \emph{data versioning} and respective ability to query across multiple versions of data or to carry out general analysis.
+%Considering graph
+%data this problem is also common, for example  in the area of Linked
+This problem has been investigated for instance within the domain of Linked
+Open Data~\cite{DBLP:conf/semweb/Papakonstantinou16,DBLP:conf/esws/MeimarisP16,fernandez2015towards,fernandez2015bear}.
+
+The respective data generator should hence be able to simulate a natural growth and/or changes in the structure of the graph with regards to the various features of distinct use cases.
+However,  even though the area of dynamic graphs is intensively studied, surprisingly there seem to exist only very few proposals of a generator dealing with this area.
+In~\cite{GoerkeKlugeSchumm2012_1000029825} the authors focus on \emph{clustering dynamic graphs}, i.e.
+graphs where the clustering corresponds to the partition of nodes into natural groups based on the paradigm of intra-cluster density versus inter-cluster sparsity of edges.
+The generator generates a time series of random graphs $G_0, G_1, ..., G_n$, where $G_t$ emerges from $G_{t-1}$ via atomic updates, i.e., insertion or deletion of an edge or a vertex.
+The generator keeps track of a (dynamic) ground truth clustering.
+The probability of atomic events is chosen in a way that adheres to this clustering, without losing randomness.
+
+Another recent proposal of a generator~\cite{mlg2018_42} of temporal graphs results from an observation that small subgraph patterns in networks, called \emph{network motifs} or \emph{graphlets}, are crucial indicators of the structure and the evolution of the graphs~\cite{Paranjape:2017:MTN:3018661.3018731}.
+For a given graph and a predefined ordered list of structural atomic motifs the generator first computes the distribution of the motifs in the graph.
+The distribution is then used to generate a synthetic graph with the same features.
+
+%\paragraph{} Following the same recursion idea,
+%paper~\cite{Leskovec:2005:RMT:2101235.2101254} uses Kronecker multiplication to
+%generate self-similar graphs. The network starts with an initial graph G1 that
+%contains $N_1$ nodes and $E_1$ edges. Using matrix recursion, larger successive
+%graphs $G_2, G_3, ... G_n$ are generated. The $k$-th graph $G_k$ contains $N_k
+%= N^k_1$ nodes. Many graphs often densify over time, exhibiting a growth in the
+%number of edges that is superlinear to the number of nodes. Kronecker
+%multiplication produces graphs with a fixed diameter and a densification power
+%law degree distribution with exponent $k = log(E_1)/log(N_1)$. The graph
+%generation process introduces a staircase effect in the nodes' degrees, and
+%each community consists of smaller nested communities that are formed through
+%expansion and recursion.
+
+\subsection{Multi-model Data}
+With the dawn of Big Data and especially its variety aspect, new types of
+database management systems have emerged. One of the most interesting ones
+are the so-called \emph{multi-model databases} that enable to store and
+thus query across structurally different data. There exist various types of
+multi-model systems combining  distinct subsets of Big Data structures including graph data.
+For example, OrientDB\footnote{\url{http://orientdb.com/orientdb/}} which was
+implemented on the basis of an object DBMS currently supports graph, document,
+key/value, and object models. Such type of DBMSs also needs a specific
+data generator that would enable
+to test new features and analyze efficiency of operations. However, since the
+multi-model systems are in the context of Big Data rather new, there exist only
+a few benchmarks targeting multi-model DBMSs (such as
+Bigframe~\cite{journals/pvldb/KunjirKB14} or UniBench~\cite{conf/cidr/lu17})
+with limited capabilities.
+
+Another interesting approach to multi-model data is to adopt a unifying
+expressive graph data model, known as property graph data
+model~\cite{BFVY18}. Such a model allows to specify multi-edges and list of
+properties for the nodes. Synthetic graph generators for property graphs and its
+companion standard graph query language~\cite{Angles18,AnglesABBFGLPPS18} are also needed in order to boost
+their availability and adoption for different communities.
+
+\subsection{Machine Learning Based Graph Generation}
+
+With the advent of neural networks and specially generative adversarial networks
+(GANs)~\cite{goodfellow2014generative}, several researchers have started to
+explore their application to generate graphs. This is the case of
+~\cite{kipf2016variational,grover2018graphite,simonovsky2018graphvae,li2018learning,you2018graphrnn},
+which present several generative models to generate realistic graphs.  Such
+techniques still suffer from several problems. For instance, some of them are
+limited to learn from a single
+graph~\cite{kipf2016variational,grover2018graphite} or generate small
+graphs~\cite{simonovsky2018graphvae,li2018learning,you2018graphrnn}. The
+technique proposed in~\cite{you2018graphrnn} is capable of generating graphs
+with complex edge dependencies (e.g. community structure) and is not restricted
+to graphs of a fixed size. However, there are still in general several open
+challenges, including the capability of learning from and generating large graphs comparable
+in size to those typically used for benchmarking, and robust generation
+techniques with structural guarantees (e.g. degree distribution, clustering
+coefficient, etc.).

### 2018-09-09 conclusion.tex
Draft of the conclusion

@@
 
-...
+Graph data occur in a vast amount of distinct applications, such as biology, chemistry, physics, computer science, or social sciences, to name just a few.
+Graphs form one of the most complex data structures requiring specific and usually sophisticated approaches for processing and analysis.
+The history of graph theory, studying these structures and respective algorithms, can be traced back to the 18th century.
+
+With the recent dawn of Big Data there have occurred also large scale graphs where the efficiency   of  processing methods is critical.
+Approaches that work for smaller scale graphs often cannot be used, the data need to be processed in a distributed way and hence the efficiency is influenced by other aspects, such as limits of data transport.
+In addition, distribution of graphs, especially for highly connected cases, is a difficult task.
+Thus extensive testing of these methods for graphs of various sizes and structural complexity is extremely important.
+
+The aim of this survey was to provide a thorough overview and comparison of graph data generators.
+We do not limit ourselves to a single application domain, but we cover the currently most popular areas of graph data processing.
+We believe that this wide scope provides a uniquely useful insight into state-of-the-art tools as well as open issues for both researchers and practitioners.

### 2018-09-09 comparison.tex
Minor changes, extension of tables
Adding of missing entries of the tables, creating a draft of matrix
expressing overlapping

@@
 
-In order to provide the reader with a quick preview of the generators and thus finding the target solutions easily, we start the survey with classification and comparative study of the existing tools.
-There are various ways how to classify them.
-We first overview approaches used in related work and then we introduce ours.
+In order to provide the reader with a quick preview of the generators and thus to enable finding the target solutions easily, we start the survey with classification and comparative study of the existing tools.
+In general, there are various ways how to classify them.
+We first overview approaches used in related work and then we introduce our approach.
 As mentioned in the Introduction, since this survey is unique in terms of scope and new tools related to Big Data processing, our classification and comparative strategy differs too.
 
-In general, the graph data generators can be classified according to various criteria.
-Paper~\cite{DBLP:conf/sdm/ChakrabartiZF04} introduces two categories -- degree-based and procedural generators.
+The graph data generators can be classified according to various criteria.
+For example, paper~\cite{DBLP:conf/sdm/ChakrabartiZF04} introduces two categories -- degree-based and procedural generators.
 Given a degree distribution (typically following a power law), \emph{degree-based generators} (e.g., Barabasi-Albert model~\cite{Barabasi99emergenceScaling}) try to find a graph that matches it, but without giving any insights about the graph or trying to match other criteria (like, e.g., small diameter, eigenvalues etc.).
@@
 
+\subsection{Classification}
+
 At first we classify the generators on the basis of the respective application domains or user communities.
+In particular we distinguish (1) general graphs, (2) Semantic Web, (3) graph databases, (4) social networks, (5) graph analytics, and (6) graph data steaming.
 The selected classes are not rigorously defined (e.g., they are not disjoint as we will show later), but they correspond to the currently most active research areas.
@@
 
-In Tables~\ref{tab:comparisonCharacteristicsA},~\ref{tab:comparisonCharacteristicsB}   we overview the key characteristics of the data generators clustered according to the respective application domains.
-In particular, we show:
+In Tables~\ref{tab:comparisonCharacteristicsA},~\ref{tab:comparisonCharacteristicsB}   we overview the key characteristics of the data generators clustered according to the respective application domains.\footnote{``GDBs'' stands for graph databases, ``SNs'' stands for social networks, ``An.'' stands for graph analytics, ``St.'' stands for graph streaming.} In particular, we show:
 
 \begin{itemize}
-\item Characteristics of the domain - its \textit{type} (fixed, specified using a schema, or extracted from input data) and the particular \textit{target} domain, or, in case of a generic tool, the chosen sample domain,
+\item Characteristics of the domain -- its \textit{type} (fixed, specified using a schema, or extracted from input data) and the particular \textit{target} domain, or, in case of a generic tool, the chosen sample domain,
 \item Characteristics of \textit{read}/\textit{update} operations (if provided), i.e., whether the set of operations is fixed/generated, if it involves operation mixes (i.e., sets/sequences of operations), or if templates of operations are supported.
@@
     \item supported types of \textit{distributions} used for generating of the data,
-    \item \textit{output format} of the produced graph,
+    \item \textit{output format} of the produced graph, and
     \item  whether the generator is \textit{distributed} and thus enables more efficient data generation.
@@
 \end{itemize}
-
-As we can see...
 
@@
                & \textbf{Distributions}
-			   & \textbf{Output format}
+			   & \textbf{Output}
                & \textbf{\rot{Distributed\ }}
@@
 \hline   % ====================== general graphs
-\multirow{8}{*}{\rot{\textbf{General}}}
-  & graph500  & fixed & & Y & N & Y & power-law & &  Y  \\
+\multirow{7}{*}{\rot{\textbf{General}}}
+  & \cite{barabasi1999emergence} & fixed & & Y & N & Y &  & &  N  \\
 \cline{2-10}
@@
 \cline{2-10}
+  & GraphGen & & & & & & & &    \\
+\cline{2-10}
+  & Graph 500  & fixed & & Y & N & Y & power-law & &  Y  \\
+\cline{2-10}
+  & BTER & & & & & & & &    \\
+\cline{2-10}
+  & Darwini & & & & & & & &    \\
 %  & Watts-Strogatz~\cite{watts1998collective} & fixed & & Y & N & Y &  & &  N  \\
 %\cline{2-10}
-  & Preferential Attachment~\cite{barabasi1999emergence} & fixed & & Y & N & Y &  & &  N  \\
-\cline{2-10}
-  & & & & & & & &  &   \\
 \hline
 \hline %  ======================  Semantic web
-\multirow{22}{*}{\rot{\textbf{Semantic web}}}
+\multirow{20}{*}{\rot{\textbf{Semantic web}}}
  & LUBM & fixed & university  & fixed & N & Y & random (LCG) &  RDF & N   \\
@@
 \hline  % ======================  graph databases
-\multirow{7}{*}{\rot{\textbf{Graph DBs}}}
+\multirow{7}{*}{\rot{\textbf{GDBs}}}
   & XGDBench & fixed  & social network  & fixed & Y & Y & power-law &  MAG &  Y  \\
 \cline{2-10}
+  & gMark & schema-driven (internal schema) &  user-defined  & generated &  N  & Y & uniform, normal, zipfian &  N-triples & N    \\
+\cline{2-10}
   & graphGen & pattern-driven (Cypher schema) & user-defined  & -- & -- & Y & -- &  property graphs & N   \\
- \cline{2-10}
- & gMark & schema-driven (internal schema) &  user-defined  & generated &  N  & Y & uniform, normal, zipfian &  N-triples & N    \\
 \hline
 \hline %  ======================   social networks
-\multirow{9}{*}{\rot{\textbf{Social networks}}}
-& LDBC SNB  & Y & Y &   generated &  & Y & Facebook-like &  CSV, RDF & Y     \\
+\multirow{8}{*}{\rot{\textbf{SNs}}}
+ & \cite{Barrett:2009:GAL:1995456.1995598} & & & & & & & &    \\
+\cline{2-10}
+ & \cite{Yao2011} & & & & & & & &    \\
+\cline{2-10}
+ & LinkBench & & & & & & & &    \\
 \cline{2-10}
@@
 \cline{2-10}
-& SNG  & Y & Y &   N &  & Y & power-law & ? &  ?   \\
+ & \cite{Sukthankar-SocialInfo2014} & & & & & & & &    \\
 \cline{2-10}
-& Forest Fire  & N & Y   & N &  & N & power-law &  ? & N   \\
+ & LDBC SNB  & Y & Y &   generated &  & Y & Facebook-like &  CSV, RDF & Y     \\
 \cline{2-10}
-& Darwini  & N & N &   N &  & N & user-defined &  ? & Y   \\
-\cline{2-10}
-& BTER  & N & N &   N &  & N & user-defined &  ? & Y  \\
-\cline{2-10}
-  & & & & & & & & &    \\
-\cline{2-10}
-  & & & & & & & & &    \\
-\cline{2-10}
-  & & & & & & & & &    \\
+  & \cite{Nettleton2016} & & & & & & & &    \\
+%\cline{2-10}
+% & SNG  & Y & Y &   N &  & Y & power-law & ? &  ?   \\
+%\cline{2-10}
+% & Forest Fire  & N & Y   & N &  & N & power-law &  ? & N   \\
+%\cline{2-10}
+% & Darwini  & N & N &   N &  & N & user-defined &  ? & Y   \\
+%\cline{2-10}
+% & BTER  & N & N &   N &  & N & user-defined &  ? & Y  \\
 \hline
 \hline   % ======================   graph analytics
-\multirow{5}{*}{\rot{\textbf{Analytics}}}
-  & & & & & & & & &    \\
+\multirow{3}{*}{\rot{\textbf{Ana.}}}
+  & HPC Scalable Graph Analysis & & & & & & & &    \\
 \cline{2-10}
-  & & & & & & & & &    \\
-\cline{2-10}
-  & & & & & & & & &    \\
-\cline{2-10}
-  & & & & & & & & &    \\
-\cline{2-10}
-  & & & & & & & &  &   \\
+  & Graphalytics & & & & & & & &    \\
 \hline
 \hline   %  ======================  streaming
-\multirow{5}{*}{\rot{\textbf{Streaming}}}
+\multirow{2}{*}{\rot{\textbf{St.}}}
   & S2Gen & schema-driven & Social Network & Y & N & N & user-defined & RDF & N     \\
@@
   & RSPLab & schema-driven & Agnostic & Y & Y & N & user-defined & RDF & N     \\
-\cline{2-10}
-  & & & & & & & & &    \\
-\cline{2-10}
-  & & & & & & & & &    \\
-\cline{2-10}
-  & & & & & & & &  &   \\
+%\cline{2-10}
+%  & & & & & & & &  &   \\
 \hline
@@
 \end{sidewaystable}
+
+\subsection{Overlapping}
+
+As we have mentioned, the basic classification we use in this paper is  based on a relatively vague division of the generators on the basis of the current application domains or research areas.
+In addition, some of the generators are either general or have features applicable in other domains.
+So the classes can overlap, as depicted in Table~\ref{tab:overlapping}.
+
+\begin{table}[h]
+\scriptsize
+\centering
+\tbl{Overlapping of classes of generators} {
+\begin{tabular}{| c | l | l | l | l | l | l | l | }
+ \hline
+           &  \textbf{Generator}
+               & \textbf{\rot{General}}
+               & \textbf{\rot{Semantic Web}}
+               & \textbf{\rot{Graph databases\ }}
+               & \textbf{\rot{Social networks}}
+               & \textbf{\rot{Analytics}}
+               & \textbf{\rot{Steaming}}
+               \\ \hline
+\hline   % ====================== general graphs
+\multirow{6}{*}{\rot{\textbf{General}}}
+  & \cite{barabasi1999emergence} & x & & & & & \\
+\cline{2-8}
+   & R-MAt    & x & & & & & \\
+\cline{2-8}
+  & GraphGen  & x & & & & & \\
+\cline{2-8}
+  & Graph 500 & x & & & & & \\
+\cline{2-8}
+  & BTER      & x & & & & & \\
+\cline{2-8}
+  & Darwini   & x & & & & & \\
+%  & Watts-Strogatz~\cite{watts1998collective}  & x & & & & & \\
+%\cline{2-8}
+\hline
+\hline %  ======================  Semantic web
+\multirow{15}{*}{\rot{\textbf{Semantic web}}}
+ & LUBM  & & x & & & & \\
+\cline{2-8}
+ & LBBM  & & x & & & & \\
+\cline{2-8}
+ & UOBM  & & x & & & & \\
+\cline{2-8}
+ & IIMB & & x & & & & \\
+\cline{2-8}
+ & BSBM & & x & & & & \\
+\cline{2-8}
+ & SP$^2$Bench & & x & & & & \\
+\cline{2-8}
+ & \cite{Duan:2011:AOC:1989323.1989340} & & x & & & & \\
+\cline{2-8}
+ & DBPSB & & x & & & & \\
+\cline{2-8}
+ & LODIB & & x & & & & \\
+\cline{2-8}
+ & SIB & & x & & & & \\
+\cline{2-8}
+ & Geographica & & x & & & & \\
+\cline{2-8}
+ & WatDiv & & x & & & & \\
+\cline{2-8}
+ & RBench & & x & & & & \\
+\cline{2-8}
+ & LDBC SPB & & x & & & & \\
+\cline{2-8}
+ & LinkGen & & x & & & & \\
+\hline
+\hline  % ======================  graph databases
+\multirow{3}{*}{\rot{\textbf{GDBs}}}
+  & XGDBench & & & x & & & \\
+\cline{2-8}
+  & gMark & & & x & & & \\
+\cline{2-8}
+  & graphGen & & & x & & & \\
+\hline
+\hline %  ======================   social networks
+\multirow{7}{*}{\rot{\textbf{SNs}}}
+ & \cite{Barrett:2009:GAL:1995456.1995598} & & & & x & & \\
+\cline{2-8}
+ & \cite{Yao2011}  & & & & x & & \\
+\cline{2-8}
+ & LinkBench  & & & & x & & \\
+\cline{2-8}
+ & S3G2  & & & & x & & \\
+\cline{2-8}
+ & \cite{Sukthankar-SocialInfo2014}  & & & & x & & \\
+\cline{2-8}
+ & LDBC SNB   & & & & x & & \\
+\cline{2-8}
+  & \cite{Nettleton2016}  & & & & x & & \\
+%\cline{2-8}
+% & SNG  & & & & x & & \\
+%\cline{2-8}
+% & Forest Fire  & & & & x & & \\
+%\cline{2-8}
+% & Darwini & & & & x & & \\
+%\cline{2-8}
+% & BTER  & & & & x & & \\
+\hline
+\hline   % ======================   graph analytics
+\multirow{2}{*}{\rot{\textbf{An.}}}
+  & HPC Scalable Graph Analysis  & & & & & x & \\
+\cline{2-8}
+  & Graphalytics & & & & & x & \\
+\hline
+\hline   %  ======================  streaming
+\multirow{2}{*}{\rot{\textbf{St.}}}
+  & S2Gen & & & & & & x\\
+\cline{2-8}
+  & RSPLab & & & & & & x \\
+%\cline{2-8}
+%  & & & & & & \\
+\hline
+\end{tabular} }
+\label{tab:overlapping}
+\end{table}

### 2018-09-09 introduction.tex
Adding TODOs.

@@
 Hence, while practitioners can find a solution in another previously unexpected area, researchers can identify new target areas or exploit successful results in new fields.
-Last but not least, we identify general open problems of graph data synthesis and indicate possible solutions to show that it still forms a challenging and promising research area.
+\TODO{datasets} Last but not least, we identify general open problems of graph data synthesis and indicate possible solutions to show that it still forms a challenging and promising research area.
 

### 2018-09-09 generators.tex
Refactored graph streaming and community detection into others section
Minor corrections

@@
 
-...
-
-\input{data_sets}
+In this section we explore in more detail different graph data generators using the classification introduced before.
+For each category we briefly describe key features of each of the representatives.
+The aim is to provide the readers with a detailed look at each of the tools in the context of its competitors from the same domain.
 
@@
 
-\input{generators_streaming}
+\input{generators_others}
 

### 2018-09-11 generators_LinkedData.tex
Minor corrections

@@
 The ontology defines 43 classes and 32 properties, including 25 object properties and 7 datatype properties~\cite{Guo2005158}.
-The \texttt{LUBM} benchmark also provides 14 test queries.
+The LUBM benchmark also provides 14 test queries.
 The authors focus on \emph{extensional} queries, i.e., queries about the instance data over ontologies, as an opposite to \emph{intentional} queries (i.e., queries about classes and properties).
-The Univ-Bench Artificial  (UBA) data generator features random and repeatable data generation (exploting classical linear congruential generator, LCG, of numbers).
+The Univ-Bench Artificial  (UBA) data generator features random and repeatable data generation (exploiting classical linear congruential generator, LCG, of numbers).
 In particular, data generated by the tool are exactly repeatable with respect to universities (assigning them zero-based indexes, i.e., the first university is named University0 and so on).
@@
 
-An extension of \texttt{LUBM}, the Lehigh BibTeX Benchmark (LBBM)~\cite{Wang2005}, enables generating synthetic data for different ontologies.
+An extension of LUBM, the Lehigh BibTeX Benchmark (LBBM)~\cite{Wang2005}, enables generating synthetic data for different ontologies.
 The generation is divided into two phases: (1) the property-discovering phase, and (2) the data generation phase.
@@
 The benchmark comes with 12 queries and 2 query mixes (sequences of the 12 queries) emulating the search and navigation pattern of a consumer looking for a product.
-The data generator supports creation of arbitrarily large datasets using the number of products $n$ as scale factor which further influences also other characteristics of the data, such as, e.g., the depth of type hierarchy of products (defined as $d = round(log_{10}(n))/2 + 1$), branching factor ($bfr = 2 \times round(log_{10}(n))$), the number of product features (having $lowerBound = 35 \times i / (d \times (d+1)/2 ?
-1)$ and $upperBound = 75 \times i / (d \times (d+1)/2 ?
-1)$) etc.
+The data generator supports creation of arbitrarily large datasets using the number of products $n$ as scale factor which further influences also other characteristics of the data, such as, e.g., the depth of type hierarchy of products (defined as $d = round(log_{10}(n))/2 + 1$), branching factor ($bfr = 2 \times round(log_{10}(n))$), the number of product features (having $lowerBound = 35 \times i / (d \times (d+1)/2 - 1)$ and $upperBound = 75 \times i / (d \times (d+1)/2 - 1)$) etc.
 BSBM can output two representations -- an RDF representation and a purely relational representation.
@@
 
-\paragraph{Data Coherence}  A comparison of 4 RDF benchmarks (namely TPC-H~\cite{TPC-H} data expressed in RDF, LUBM, BSBM, and SP$^2$Bench) and 6 real-wold data sets (such as, e.g.,  DBpedia~\cite{Bizer:2009:DCP:1640541.1640848}, the Barton Libraries Dataset~\cite{barton-benchmark}
-WordNet~\cite{Miller:1995:WLD:219717.219748} etc.) is provided in paper~\cite{Duan:2011:AOC:1989323.1989340}.
+\paragraph{Data Coherence}  A comparison of 4 RDF benchmarks (namely TPC-H~\cite{TPC-H} data expressed in RDF, LUBM, BSBM, and SP$^2$Bench) and 6 real-wold data sets (such as, e.g.,  DBpedia~\cite{Bizer:2009:DCP:1640541.1640848}, the Barton Libraries Dataset~\cite{barton-benchmark} or
+WordNet~\cite{Miller:1995:WLD:219717.219748}) is provided in paper~\cite{Duan:2011:AOC:1989323.1989340}.
 The authors focus mainly on \emph{structuredness} (\emph{coherence}) of each benchmark dataset claiming that a primitive metric (e.g., the number of triples or the average in/outdegree) quantifies only some specific aspect of each dataset.
 The level of structuredness of a dataset $D$ with respect to a type $T$ is determined by how well the instance data in $D$ conforms to type $T$.
-The type system is extracted from the data set looking for triples whose property is \texttt{http://www.w3.org/1999/02/22-rdf-syntax-ns\#type} and extracting type $T$ from their object.
+The type system is extracted from the data set by looking for triples whose property is \texttt{http://www.w3.org/1999/02/22-rdf-syntax-ns\#type} and extracting type $T$ from their object.
 Properties of $T$ are determined as the union of all the properties that the instances of type $T$ have.
@@
 used in property values.
-Hence, they propose a generic SPARQL benchmark creation methodology based on: a flexible data generation mimicking an input data source, query-log mining, clustering, and SPARQL feature analysis.
+Hence, they propose a generic SPARQL benchmark creation methodology based on a flexible data generation mimicking an input data source, query-log mining, clustering, and SPARQL feature analysis.
 The proposed dataset creation process starts with an input dataset.
@@
 
-\paragraph{Geographica} The Geographica benchmark \footnote{\url{http://geographica.di.uoa.gr/}} has been designed target the area of geospatial data~\cite{DBLP:conf/semweb/GarbisKK13} and respective SPARQL extensions \texttt{GeoSPARQL}~\cite{battle2012enabling} and \texttt{stSPARQL}~\cite{koubarakis2010modeling}.
-The benchmark involves (1) a real-world workload based on publicly available linked data sets covering a range of geometry types (e.g., points, lines, polygons) and (2) a synthetic workload.
-In the former case they further distinguish (1) a micro benchmark that tests primitive spatial functions (involving 29 queries) and (2) macro benchmark that tests the performance of RDF stores in typical application scenarios like reverse geocoding or map search and browsing (consisting of 11 queries).
+\paragraph{Geographica} The Geographica benchmark\footnote{\url{http://geographica.di.uoa.gr/}} has been designed to target the area of geospatial data~\cite{DBLP:conf/semweb/GarbisKK13} and respective SPARQL extensions GeoSPARQL~\cite{battle2012enabling} and stSPARQL~\cite{koubarakis2010modeling}.
+The benchmark involves a real-world workload based on publicly available linked data sets covering a range of geometry types (e.g., points, lines, polygons) and  a synthetic workload.
+In the former case there is a (1) a micro benchmark that tests primitive spatial functions (involving 29 queries) and (2) macro benchmark that tests the performance of RDF stores in typical application scenarios like reverse geocoding or map search and browsing (consisting of 11 queries).
 In the latter case of a synthetic workload the generator produces synthetic datasets of various sizes that corresponds to an ontology based on OpenStreetMap (i.e., states in a country, land ownership, roads and  points of interest) and instantiates query templates.
@@
 \paragraph{WatDiv} The Waterloo SPARQL Diversity Test Suite (WatDiv)\footnote{\url{http://dsg.uwaterloo.ca/watdiv/}} developed at the University of Waterloo provides stress testing tools to address the observation that existing SPARQL benchmarks are not suitable for testing systems for diverse queries and varied workloads~\cite{Aluc:2014:DST:2717213.2717229}.
-The benchmark introduce two classes of query features -- structural and data-driven -- and perform an in-depth analysis on existing SPARQL benchmarks (LUBM, BSBM, SP$^2$Bench, and DBPSB) using the two classes of query features.
+The benchmark introduces two classes of query features -- structural and data-driven -- and performs an in-depth analysis on existing SPARQL benchmarks (LUBM, BSBM, SP$^2$Bench, and DBPSB) using the two classes of query features.
 The structural features involve triple pattern count, join vertex count, join vertex degree, and join vertex count.
@@
 
-\paragraph{RBench} RBench~\cite{Qiao:2015:RAR:2723372.2746479} is an application-specific benchmark which takes any RDF dataset as a template, and generates a set of synthetic datasets with similar characteristic, the required size scaling factor $s$ and the (node) degree scaling factor $d$.
+\paragraph{RBench} RBench~\cite{Qiao:2015:RAR:2723372.2746479} is an application-specific benchmark which takes any RDF dataset as a template and generates a set of synthetic datasets with similar characteristics, required size scaling factor $s$ and (node) degree scaling factor $d$.
 A generated benchmark dataset is considered similar to the given dataset if their values for the dataset evaluation metrics and query evaluation times for different techniques are similar.
-Three evaluation metrics -- dataset coherence (i.e., a measure how uniformly predicates are distributed among the same type/class), relationship specialty (i.e., the number of occurrences of the same predicate associated with each resource), and literal diversity -- are utilized for this purpose.
+Three evaluation metrics are utilized for this purpose: dataset coherence (i.e., a measure how uniformly predicates are distributed among the same type/class), relationship specialty (i.e., the number of occurrences of the same predicate associated with each resource), and literal diversity.
 A query generation process is proposed to generate 5 types of queries (node queries, edge queries, star queries, path queries, and subgraph queries) for any generated data.
-The benchmark project \texttt{FEASIBLE}~\cite{Saleem2015} is also an application-specific benchmark; however, contrary to RBench, it is able to generate benchmarks from a set of queries (in particular from query logs) by selecting prototypical queries of a user-defined
+The benchmark project FEASIBLE~\cite{Saleem2015} is also an application-specific benchmark; however, contrary to RBench, it is able to generate benchmarks from a set of queries (in particular from query logs) by selecting prototypical queries of a user-defined
 size from the input set of queries.
 
-\paragraph{LDBC}  The Linked Data Benchmark Council\footnote{\url{http://ldbcouncil.org/industry/organization/origins}} (LDBC)~\cite{Angles:2014:LDB:2627692.2627697} is a result of a (closed) EU project that brought together a community of academic researchers and industry that had the main objective of developing an open source, yet industrial grade, benchmarks for graph and RDF databases.
+\paragraph{LDBC}  The Linked Data Benchmark Council\footnote{\url{http://ldbcouncil.org/industry/organization/origins}} (LDBC)~\cite{Angles:2014:LDB:2627692.2627697} is a result of a (closed) EU project that brought together a community of academic researchers and industry that had the main objective of developing an open source, yet industrial grade benchmarks for graph and RDF databases.
 \iffalse The following three benchmarks were developed and are currently maintained.\fi In the Semantic Web domain, the project released the Semantic Publishing Benchmark (SPB)~\cite{spb} that has been inspired by the Media/Publishing industry (namely BBC\footnote{\url{http://www.bbc.com/}}).
@@
 Synthetic data consists of a large number of annotations of media assets that refer entities found in reference datasets.
-The data generator models three types of relations in produced synthetic data: (1) clustering of data, (2) correlations of entities, and (3) random tagging of entities.
-Two workloads are provided: (1) basic, involving an interactive query-mix, querying the relations between entities in reference data, and (2) advanced,  consisting of interactive and analytical query-mixes.
+The data generator models three types of relations in produced synthetic data: clustering of data, correlations of entities, and random tagging of entities.
+Two workloads are provided: (1) basic, involving an interactive query-mix querying the relations between entities in reference data, and (2) advanced,  consisting of interactive and analytical query-mixes.
 The LDBC designed two other benchmarks: the Social Network Benchmark (SNB)~\cite{Erling:2015:LSN:2723372.2742786} for the social network domain  (see Section~\ref{sec:generators_socialnetworks}) and Graphalytics~\cite{Iosup:2016:LGB:3007263.3007270}   for the analytics domain (see Section~\ref{sec:generators_analytics}).
@@
 The generator is designed to receive a vocabulary as an input  and supports two statistical distribution techniques for generating entities: Gaussian distribution and Zipf's power-law distribution.
-\texttt{LinkGen} can augment the generated data with inconsistent and noisy  data such as writing two conflicting values for a given datatype property,  adding triples with syntactic errors, adding wrong statement by assigning invalid domain and creating instances with no type information.
+LinkGen can augment the generated data with inconsistent and noisy  data such as writing two conflicting values for a given datatype property,  adding triples with syntactic errors, adding wrong statement by assigning invalid domain and creating instances with no type information.
 The generator is also designed with  an option to inter-link the generated instances with real ones given that the user provides entities from real datasets.

### 2018-09-11 generators_general.tex
Minor corrections

--- 2018-06-23 generators_general.tex
@@
 
-First of all we will focus on papers dealing with generation of general graph
-data not aiming at particular application domain. Currently, there exists a
+First of all we focus on papers dealing with generation of general graph
+data not aiming at a particular application domain. Currently, there exists a
 number of tools which involve a kind of general graph data generator, such as
 gtools from projects nauty and Traces~\cite{gtools} or the Stanford
-GraphBase~\cite{GraphBase}. We will, however, focus on primarily
+GraphBase~\cite{GraphBase}. We, however, focus on primarily
 generating/benchmarking projects targeting Big Data world.
 
-\paragraph {Preferential Attachment} Barabasi and Albert introduced a graph generation model that relies on two main mechanisms~\cite{Barabasi99emergenceScaling}.
+\paragraph {Preferential Attachment} Barabasi and Albert~\cite{Barabasi99emergenceScaling} introduced a graph generation model that relies on two main mechanisms.
 The first mechanism is continuously expanding the graphs by adding new vertices.
 The second mechanism is to preferentially attach the new vertices   to the nodes/regions that are already well connected.
-In this approach, the generation of large graphs is governed by standard, robust self-organizing mechanism that go beyond the characteristics of individual applications.
+So, in this approach, the generation of large graphs is governed by standard, robust self-organizing mechanisms that go beyond the characteristics of individual applications.
 
@@
 The generator is recursive and uses only a small number of parameters.
-In principle, the strategy of this generator to find simple mechanisms to generate graphs that match
+In principle, the strategy of this generator is to find simple mechanisms to generate graphs that match
 the properties of the real graphs.
@@
 \paragraph{GraphGen} For the purpose of testing the scalability of an indexing
-technique called FG-index~\cite{Cheng:2007:FTV:1247480.1247574} on size of the
+technique called FG-index~\cite{Cheng:2007:FTV:1247480.1247574} on the size of the
 database of graphs, their average size and average density, the authors have
@@
 \url{http://www.almaden.ibm.com/cs/projects/iis/hdb/Projects/data
-mining/mining.shtml}.}. GraphGen creates a collection of labeled, undirected and
+mining/mining.shtml}}. GraphGen creates a collection of labeled, undirected and
 connected graphs aiming at performance evaluation of frequent subgraph mining
@@
 (i.e., half the average degree of a vertex in the graph). The graph generator is
-a Kronecker generator similar to R-MAT~\cite{DBLP:conf/sdm/ChakrabartiZF04}. The data must not exhibit any locality,
+a Kronecker generator similar to R-MAT. The data must not exhibit any locality,
 so in the final step the vertex labels and order of edges are randomly shuffled.
@@
 involve also two more types -- optimization (single source shortest path) and
-edge-oriented (maximal independent set) -- and five graph-related business areas
+edge-oriented (maximal independent set) -- and five graph-related business areas:
 cybersecurity, medical informatics, data enrichment, social networks, and
@@
 \paragraph{BTER} BTER (Block Two-Level
-Erd\"{o}-R\'{e}ny)~\cite{kolda2014scalable} is a graph generator based on the
+Erd\"{o}s-R\'{e}ny)~\cite{kolda2014scalable} is a graph generator based on the
 creation of multiple Erd\"{o}s-R\'{e}ny graphs with different connection
-probabilities, connected randomly between them. As a main feature, BTER is able
+probabilities, connected randomly between them. As the main feature, BTER is able
 to reproduce input degree distributions and average clustering
-coefficient per degree values. The generators starts by grouping the vertices
-by degree $d$, and forming groups of size $d+1$ degree $d$ nodes. Then, these
+coefficient per degree values. The generator starts by grouping the vertices
+by degree $d$, and forming groups of size $d+1$ of nodes with degree $d$. Then, these
 groups are assigned an internal edge probability in order to match the observed
 average clustering coefficient of the nodes of such degree. Based on this
-probability, for each node, the excess degree is computed (the degree that in
-expectation will not be realized internally in the group) and used to connect
+probability, for each node, the excess degree (i.e, the degree that in
+expectation will not be realized internally in the group) is computed and used to connect
 nodes from different groups at random. The authors describe a highly scalable
@@
 of the graph into buckets by the expected number of closed triangles they need
-to close in order to attain the their expected clustering coefficient, which is
+to close in order to attain the expected clustering coefficient, which is
 sampled from the input distributions. Then, the vertices in each bucket are

### 2018-09-12 generators_GraphDatabases.tex
Minor corrections

--- 2018-05-15 generators_GraphDatabases.tex
@@
 Or the graph DBMS benchmarking tools are designed in a more general scope.
-Hence it is questionable whether a benchmark specific for graph databases if necessary.
-
-Paper~\cite{Dominguez-Sal:2010:DDG:1946050.1946053} discusses this question and related topics.
+Hence it is questionable whether a benchmark specific for graph databases is necessary.
+\cite{Dominguez-Sal:2010:DDG:1946050.1946053} discussed this question and related topics.
 On the basis of a review of applications of graph databases (namely social network analysis, proteomics or genetic interactions, recommendation systems, and travel planning and routing), the authors analyze and discuss the characteristics of the graphs that appear in such applications and how they could influence benchmarking, different types of operations used in these applications and the characteristics of the evaluation setup of the benchmark.
-
-In the following paragraphs we overview graph data generators and benchmarks primarily targeting graph DBMSs.
+In this section, we focus on graph data generators and benchmarks that have been primarily targeting graph DBMSs.
 
@@
 the process of graph database benchmarking in the cloud focusing on a graph database application for social networking services.
-
 It extends the Yahoo!
@@
 Using them 7 workloads are created, such as update heavy, read mostly, short range scan, traverse heavy etc.
-
 The data model of XGDBench is a simplified version of the Multiplicative Attribute Graph (MAG)~\cite{Kim2010} model, a synthetic graph model for attribute graphs which models the interactions between the network structure and the node attributes.
-The generated graphs are thus in MAG format, with power-law degree distribution thus closely simulating real-world social networks.
+The generated graphs are thus in MAG format, with power-law degree distribution closely simulating real-world social networks.
 The simplified MAG algorithm accepts the number of vertices of the generated graph, the number of attributes per vertex, a threshold value for random initialization of attributes, an edge affinity threshold value that determines whether there is an edge between two vertices, and an affinity matrix.
 It has been proven that MAG generates graphs with both analytically tractable and statistically interesting properties.
-A multi-threaded version of the graph generator that generates large graphs on multi-core systems faster was implemented.
+A multi-threaded version of the graph generator that generates large graphs on multi-core systems faster was implemented too.
 
-\paragraph{GraphGen}  GraphAware GraphGen~\cite{GraphGen} is a graph generation engine based on Cypher, Neo4j's\footnote{\url{https://neo4j.com/}} query language.
-It creates nodes and relationships based on a schema definition expressed in Cypher, and it can also generate property values on both
-nodes and edges.
-As such, GraphGen is a precursor of property graphs generators.
-The resulting graph can be exported to several formats (namely GraphJson and CypherQueries) or loaded directly to a DBMS.
-However, it is probably not maintained anymore.
-
-\paragraph{gMark}  gMark~\cite{gMark} is a schema-driven, domain- and query language-independent graph instance and query workload generator.  It leverages a schema definition,
+\paragraph{gMark}  gMark~\cite{gMark} is a schema-driven, domain-independent and query language-independent graph instance and query workload generator.  It leverages a schema definition,
 called a \emph{graph configuration}, which includes the enumeration of predicates (i.e., edge labels) and node types (i.e., node labels) occurring in the data, along with their properties in generated instances (occurrence constraints, degree distribution, etc.).
@@
 Hence, gMark follows a heuristic strategy in the generation -- it attempts to achieve the exact values of the parameters and it may decide to relax some of them in order to obtain linear running time.
-gMark generates graphs under the form of N-triples and query workloads in four concrete syntaxes, including Cypher, SPARQL, SQL and LogicQL.
+gMark generates graphs under the form of N-triples and query workloads in four concrete syntaxes, including Cypher\footnote{\url{https://neo4j.com/developer/cypher-query-language/}}, SPARQL, SQL and LogicQL.
+
+\paragraph{GraphGen}  GraphAware GraphGen\footnote{\url{http://graphgen.graphaware.com/}} is a graph generation engine based on Neo4j's\footnote{\url{https://neo4j.com/}} query language Cypher~\cite{GraphGen}.
+It creates nodes and relationships based on a schema definition expressed in Cypher, and it can also generate property values on both
+nodes and edges.
+As such, GraphGen is a precursor of property graphs generators.
+The resulting graph can be exported to several formats (namely GraphJson\footnote{\url{https://github.com/GraphAlchemist/GraphJSON/wiki/GraphJSON}} and CypherQueries) or loaded directly to a DBMS.
+However, it is probably not maintained anymore.

### 2018-09-12 generators_SocialNetworks.tex
Minor corrections

--- 2018-06-28 generators_SocialNetworks.tex
@@
 privacy of the data. Hence, data generators which provide realistic synthetic
-social network graphs are in great demand. In general, analyses of social networks identify their various specific
-features~\cite{Chakrabarti:2006:GML:1132952.1132954}. For example, the social
+social network graphs are in a great demand.
+
+In general, analyses of social networks identify their various specific
+features~\cite{Chakrabarti:2006:GML:1132952.1132954}. For example, a social
 graph has high \emph{clustering coefficient}, i.e. the degree of transitivity of
@@
 fraction (e.g., 90\%) of all connected pairs of nodes can reach each other, is
-usually low due to weak ties joining faraway cliques. Another important aspect
+usually low due to weak ties joining faraway cliques.
+
+Another important aspect
 of social networks is the community effect. A detailed study of structure of
@@
 communities (clustering coefficient, triangle participation ratio, bridges,
-diameter, conductance and size) in both real graphs and output by existing graph
+diameter, conductance and size) in both real-world graphs and outputs of existing graph
 generators LFR~\cite{PhysRevE.78.046110} and the
-LDBC-SNB~\cite{Erling:2015:LSN:2723372.2742786}. %They discover that communities
-found among different graphs follow quite similar distributions and that
-communities in a single graph have diverse nature, and are difficult to fit with
-a single model.
+LDBC-SNB~\cite{Erling:2015:LSN:2723372.2742786}.
+They discover that communities found in different graphs follow quite similar distributions and that communities in a single graph have diverse nature and are difficult to fit with a single model.
 
-Network generators can be categorized into statistical and agent-based.
+The existing social network generators try to reproduce different aspects of the
+generated network. They can be categorized into statistical and agent-based.
 \emph{Statistical
 approaches}~\cite{PhysRevE.78.046110,Yao2011,Armstrong:2013:LDB:2463676.2465296,Pham2013,Sukthankar-SocialInfo2014,Erling:2015:LSN:2723372.2742786,Nettleton2016}
-focus on reproducing aspects of the network statistics. In \emph{agent-based
+focus on reproducing aspects of the network. In \emph{agent-based
 approaches}~\cite{Barrett:2009:GAL:1995456.1995598,Bernstein:2013:SAS:2499604.2499609}
@@
 
-\paragraph{Towards More Realistic Data} ~\cite{Nettleton2016} argued that the main body of existing work lies in
+\paragraph{Towards More Realistic Data} \cite{Nettleton2016} argued that the main body of existing work lies in
 topology generation which approximate the characteristics of a real social

### 2018-09-12 generators_SocialNetworks.tex
Minor corrections

@@
 realistic social networks using a combination of public and private data sets
-and large-scale agent based techniques. The process works as follows: Step 1
-creates a synthetic population by integrating databases from commercial and
-public sources. In Step 2, a set of activity templates are determined. Each
+and large-scale agent based techniques. The process works as follows: In the first step
+it creates a synthetic population by integrating databases from commercial and
+public sources. In the second step, a set of activity templates are determined. Each
 synthetic individual is assigned a 24-hour activity sequence including
-geo-locations for each activity. To demonstrate the approach, the authors develop a synthetic population for the
+geolocations for each activity. To demonstrate the approach, the authors develop a synthetic population for the
 United States that models every individual in the population. The synthetic
@@
 
-\paragraph{Linkage vs. Activity Graphs} ~\cite{Yao2011} distinguished between two
+\paragraph{Linkage vs. Activity Graphs} \cite{Yao2011} distinguished between two
 types of social network graphs -- the \emph{linkage graph}, where nodes stand
@@
 clustering coefficient over time. However, the authors do not observe diameter
-shrinking in Epinions? activity graph and there is a difference in degree
+shrinking in Epinions activity graph and there is a difference in degree
 correlation (how frequently nodes with similar degrees connect to each other).
@@
 show neutral degree correlation. With regards to the findings, the proposed generator focusses on linkage graphs
-with positive degree correlation. For this purpose it extends the ``forest
-fire'' spreading process algorithm~\cite{Leskovec:2005:GOT:1081870.1081893} with
+with positive degree correlation. For this purpose it extends the forest
+fire spreading process algorithm~\cite{Leskovec:2005:GOT:1081870.1081893} with
 link symmetry. It has two parameters -- the \emph{burning probability} $P_b$
@@
 structure is determined by the class a node belongs to. S3G2 does not aim at
-generating near real-world data, but at generating synthetic graphs which a
+generating near real-world data, but at generating synthetic graphs with a
 correlated structure. It causes that the probability to choose a certain
@@
 original dataset to create a multiplex network. MLG uses the same network growth
-process as ASG.. Based on the link density parameter, either a new node is
+process as ASG. Based on the link density parameter, either a new node is
 generated with a label based on the label distribution of the target dataset or
@@
 data is in the messages that these persons post in discussion trees on their
-forums. The three query workloads involve: (1) SNB-Interactive (i.e., complex
-read-only queries, that touch a significant amount of data), (2) SNB-BI (which
+forums. The three query workloads involve: (1) SNB-Interactive, i.e., complex
+read-only queries, that touch a significant amount of data, (2) SNB-BI which
 accesses a large percentage of all entities in the dataset and groups these in
-various dimensions), and (3) SNB-Algorithms (i.e., graph analysis algorithms,
-including PageRank, Community Detection, Clustering and Breadth First Search).
+various dimensions, and (3) SNB-Algorithms, i.e., graph analysis algorithms,
+including PageRank, Community Detection, Clustering and Breadth First Search.
 The graph generator realizes power laws, uses skewed value distributions, and
@@
 \paragraph{Towards More Realistic Data} \cite{Nettleton2016} argued that the main body of existing work lies in
-topology generation which approximate the characteristics of a real social
+topology generation which approximates the characteristics of a real social
 network (such as a small graph diameter, small average path length, skew degree
@@
 SNAP\footnote{\url{https://snap.stanford.edu/data/}}, (2) data definition
-(following distribution profiles, attribute value definitions, using a
-parameterizable set of data propagation rules and affinities), and (3) data
+following distribution profiles, attribute value definitions, using a
+parameterizable set of data propagation rules and affinities, and (3) data
 population.

### 2018-09-12 generators_analytics.tex
Minor corrections

--- 2018-06-23 generators_analytics.tex
@@
 \label{sec:generators_analytics}
+
+\TODO{A short intro.}
 
@@
 following parameters: number of vertices, number of edges, and maximum weight of
-an edge. The algorithm of the generator is based on R-MAT~\cite{DBLP:conf/sdm/ChakrabartiZF04}. Since the authors aim
+an edge. The algorithm of the generator is based on R-MAT. Since the authors aim
 to avoid data locality, in the final step the vertex numbers are randomly
@@
 (version 1.0), Erd\"{o}s-R\'{e}nyi random graphs, and small-world graphs based
-on the R-MAT model~\cite{DBLP:conf/sdm/ChakrabartiZF04}.
+on the R-MAT model.
+
+\paragraph{Graphalytics} Graphalytics\footnote{\url{http://graphalytics.ewi.tudelft.nl/}} is an industrial-grade benchmark for graph analysis platforms~\cite{Iosup:2016:LGB:3007263.3007270}.
+It involves 6 real-world datasets and 2 synthetic datasets generated so that they cover two commonly used types of graphs: social network graphs generated using LDBC SNB graph generator (see Section~\ref{sec:generators_socialnetworks}) and power-law graphs generated by Graph500 (see Section~\ref{sec:generators_general}).
+The benchmark workload consists of 6 deterministic algorithms: breadth-first search, PageRank, weakly connected components, community detection using label propagation, local clustering coefficient, and single-source shortest paths.
+The benchmark uses various metrics to measure the performance and throughput for systems under test such as \emph{upload time} that measures the required time to preprocess and convert the graph into a suitable format for a graph processing system, or \emph{Makespan} that measures the total  execution time of a benchmarking workload algorithm.
+The benchmark also describes experiments for measuring the scalability of the systems under test.
+To facilitate the end user job of running the designed experimental workload, the benchmark provides  a performance evaluation framework, Granula\footnote{\url{https://github.com/atlarge-research/granula}}.%, that consists of three main components: modeler, archiver, and the visualizer.

### 2018-09-12 generators_community_detection.tex
Refactored graph streaming and community detection into others section
graph stream generator
Minor corrections

@@
-\subsection{Graphs Generators for Benchmarking Community Detection Algorithms}
+\subsubsection{Graphs Generators for Benchmarking Community Detection Algorithms}
 \label{sec:generators_community_detection}
@@
 Communities are groups of vertices that are highly connected among them, while being scarcely connected to the rest of the graph.
-Such communities emerge from the fact that real graphs are not random, but follow realworld dynamics that make similar entities to have a larger probability to be connected.
-As a consequence, detected communities are used used to reval vertices with similar characteristics, for instance to discover functionally equivalent proteins in protein-protein interaction networks, or persons with similar interests in social networks.
+Such communities emerge from the fact that real graphs are not random, but follow real-world dynamics that make similar entities to have a larger probability to be connected.
+As a consequence, detected communities are used to reveal vertices with similar characteristics, for instance to discover functionally equivalent proteins in protein-protein interaction networks, or persons with similar interests in social networks.
+Such applications have made community detection a hot topic during the last fifteen years with tens of developed algorithms and detection strategies.
+In order to compare the quality of the different proposed techniques, one needs graphs with reference communities, that is, communities known beforehand.
+Since it is very difficult to have large real graphs with reference communities (mainly because these would require a manual labeling), graphs for benchmarking community detection algorithms are typically generated synthetically.
 
-Such applications have made community detection a hot topic during the last fifteen years with tens of developed algorithms and detection strategies.
-In order to compare the quality of the different proposed techniques, one needs graphs with reference communities, that is,.
-communities which known beforehand.
-Since it is very difficult to have large real graphs with reference communities --mainly because these would require a manual labeling--, graphs for benchmarking community detection algorithms typically generated synthetically.
-
-The first attempts to compare community detection algorithms using synthetic graphs proposed the use of random graphs composed by several Erd\"{o}s-R\'{e}nyi~\cite{Erdos:1960} subgraphs, connected more internally than externally~\cite{danon2005comparing}.
+The first attempts to compare community detection algorithms using synthetic graphs proposed the use of random graphs composed by several Erd\"{o}s-R\'{e}nyi subgraphs, connected more internally than externally~\cite{danon2005comparing}.
 Each of these subgraphs has the same size and the same internal/external density of edges.
 However, such graphs miss the realism observed in real graphs, where communities are of different sizes and densities.
-
 Thus, Lancichinetti, Fortunato and Radicchi (hence LFR)~\cite{PhysRevE.78.046110} propose a class of benchmark graphs for community detection where communities are of different sizes and densities.
@@
 Additionally, the generator introduces the concept of the ``mixing factor'', which specifies the fraction of its links connecting nodes belonging to different communities.
-Such parameter allows to tune the degree of modularity of the generated graph, thus testing the robustness of hte algorithms under different conditions.
+Such parameter allows to tune the degree of modularity of the generated graph, thus testing the robustness of the algorithms under different conditions.
 The generation process starts with an empty graph and incrementally fills in the adjacency matrix by obeying the described constraints.
-
 Lancichinetti, Fortunato and Radicchi \cite{PhysRevE.80.016118} extended LFR to support the notion of directed graphs and overlapping communities.
@@
 However, a recent study from Hric, Darst and Fortunato~\cite{hric2014community} reveal a loose correspondence between  communities --the authors refer to them as structural communities-- and meta-communities.
-This result reveals that those algorithms working for structural communities do not work well for finding meta-communities and viceversa, suggesting significantly different underlying characteristics between the two types of communities, which are yet to be indentified.
+This result reveals that those algorithms working for structural communities do not work well for finding meta-communities and viceversa, suggesting significantly different underlying characteristics between the two types of communities, which are yet to be identified.
 

### 2018-09-13 generators_community_detection.tex
Minor corrections

@@
 As a consequence, detected communities are used to reveal vertices with similar characteristics, for instance to discover functionally equivalent proteins in protein-protein interaction networks, or persons with similar interests in social networks.
-Such applications have made community detection a hot topic during the last fifteen years with tens of developed algorithms and detection strategies.
-In order to compare the quality of the different proposed techniques, one needs graphs with reference communities, that is, communities known beforehand.
+Such applications have made community detection a hot topic during the last fifteen years with tens of developed algorithms and detection strategies.\TODO{references} In order to compare the quality of the different proposed techniques, one needs graphs with \emph{reference communities}, that is, communities known beforehand.
 Since it is very difficult to have large real graphs with reference communities (mainly because these would require a manual labeling), graphs for benchmarking community detection algorithms are typically generated synthetically.
@@
 The generation process starts with an empty graph and incrementally fills in the adjacency matrix by obeying the described constraints.
-Lancichinetti, Fortunato and Radicchi \cite{PhysRevE.80.016118} extended LFR to support the notion of directed graphs and overlapping communities.
+Lancichinetti, Fortunato and Radicchi~\cite{PhysRevE.80.016118} extended LFR to support the notion of directed graphs and overlapping communities.
 Overlapping communities extend the notion of communities by allowing the sharing of vertices, thus a vertex can belong to more than one community.
@@
 
-Besides synthetic graph generators, Yang and Leskovec~\cite{yang2015defining} proposed hte use of real graphs with explicit group annotations (e.g.
-forums in a social network, categories of products, etc.) to infer what they call ``meta-communities'', and use them to evaluate overlapping community detection algorithms.
-However, a recent study from Hric, Darst and Fortunato~\cite{hric2014community} reveal a loose correspondence between  communities --the authors refer to them as structural communities-- and meta-communities.
-This result reveals that those algorithms working for structural communities do not work well for finding meta-communities and viceversa, suggesting significantly different underlying characteristics between the two types of communities, which are yet to be identified.
+Besides synthetic graph generators, Yang and Leskovec~\cite{yang2015defining} proposed the use of real-world graphs with explicit group annotations (e.g., forums in a social network, categories of products, etc.) to infer what they call ``meta-communities'', and use them to evaluate overlapping community detection algorithms.
+However, a recent study from Hric, Darst and Fortunato~\cite{hric2014community} reveal a loose correspondence between  communities (the authors refer to them as structural communities) and meta-communities.
+This result reveals that  algorithms working for structural communities do not work well for finding meta-communities and viceversa, suggesting significantly different underlying characteristics between the two types of communities, which are yet to be identified.
 
@@
 
-The differences observed between structural and meta-communities reveal the need of more accurate community defeinitions thight more specifically to the domain or use case.
+The differences observed between structural and meta-communities reveal the need of more accurate community definitions tight more specifically to the domain or use case.
 Current community detection algorithms and graph generators for community detection are stuck to the traditional (and vague) definition of community, assuming that there exists a single algorithm that would fit all the use cases.
-Thus, future work requires the study of domain-specific community characteristics that can be used to generate graphs with a community structure that accurately resemble that of specific use cases, and thus revealing which are the best algorithms for each particular scenario.revealing which are the best algorithms for each particular scenario.
+Thus, future work requires the study of domain-specific community characteristics that can be used to generate graphs with a community structure that accurately resemble that of specific use cases, and thus revealing which are the best algorithms for each particular scenario.

### 2018-09-13 generators_streaming.tex
Minor corrections

--- 2018-05-15 generators_streaming.tex
@@
-\subsection{Graph Data Streaming}
+\subsubsection{Graph Data Streaming}
 \label{sec:generators_streaming}
+One way for dealing with big graphs is to process them using the \emph{streaming} mode where the data stream could consist of the edges of the graph.
+In this mode, the graph processing algorithms can process the input stream in the order it arrives while using only a limited amount memory~\cite{mcgregor2014graph}.
+The streaming mode has mainly  attracted the attention of the RDF and Semantic Web community.
+Thus, Phuoc et al.~\cite{le2012linked} presented an evaluation framework for linked stream data processing engines.
+The framework uses a data generator for Stream Social network data Generator (S2Gen) that simulates what users continuously generate on their social network activities (e.g., posts) in addition to the  user metadata such as users' profile information, social network relationships, posts, photos and GPS information.
+The data generator of this framework provides the users the flexibility to control the characteristics of the generated data by tanning a range of parameters including the period in which the social activities are generated (generating period), the maximum number of posts/comments/photos for each user per week and the correlation probabilities between the different objects (e.g., users) in the social network.
 
-...
+Tommasini et al.~\cite{tommasini2017rsplab} introduced another framework for benchmarking RDF Stream Processing systems, RSPLab.
+The Streamer component of this framework is designed to publish RDF streams from the various existing RDF benchmarks (e.g., BSBM, LUBM) (see Section~\ref{sec:generators_LinkedData}).
+In particular, the Streamer  component uses TripleWave\footnote{\url{http://streamreasoning.github.io/TripleWave/}}, an open-source framework for publishing and sharing RDF streams on the Web~\cite{mauri2016triplewave}.
+TripleWave acts as a mean for plugging in diverse Web data sources and for consuming streams in both push and pull mode.

### 2018-09-14 generators_analytics.tex
Adding of short introductions/conclusions etc.

@@
 
-\TODO{A short intro.}
+Graph analytics, especially in the context v Big Data, is a popular area of studying interesting structural specifics of graphs, usually various types of networks.
+Hence, the respective benchmarks and graph data generators developed for the purpose of testing graph analytics tools (such as, e.g.,  PowerGraph~\cite{Gonzalez:2012:PDG:2387880.2387883} or Parallel Graph analytiX~\cite{Sevenich:2016:UDL:3007263.3007265}) have to focus mainly on graphs with complex structures.
 

### 2018-09-14 generators_community_detection.tex
Adding of short introductions/conclusions etc.

@@
-\subsubsection{Graphs Generators for Benchmarking Community Detection Algorithms}
+\subsubsection{Community Detection}
 \label{sec:generators_community_detection}
@@
 As a consequence, detected communities are used to reveal vertices with similar characteristics, for instance to discover functionally equivalent proteins in protein-protein interaction networks, or persons with similar interests in social networks.
-Such applications have made community detection a hot topic during the last fifteen years with tens of developed algorithms and detection strategies.\TODO{references} In order to compare the quality of the different proposed techniques, one needs graphs with \emph{reference communities}, that is, communities known beforehand.
+Such applications have made community detection a hot topic during the last fifteen years with tens of developed algorithms and detection strategies~\cite{doi:10.1002/wics.1403,Kim:2015:CDM:2854006.2854013}.
+In order to compare the quality of the different proposed techniques, one needs graphs with \emph{reference communities}, that is, communities known beforehand.
 Since it is very difficult to have large real graphs with reference communities (mainly because these would require a manual labeling), graphs for benchmarking community detection algorithms are typically generated synthetically.

### 2018-09-14 introduction.tex
Adding of short introductions/conclusions etc.

--- 2018-09-01 introduction.tex
@@
 To conclude the comparative study and provide a comprehensive view of the
-field,  we also discuss open challenges and missing requirements of modern
+field,  we also overview the most popular real-world data sets used in the respective covered areas and discuss open challenges and missing requirements of modern
 graph generators in view of identifying their future extensions to new emerging fields.

### 2018-09-16 challenges.tex
Minor corrections
Added privacy preserving in open challenges

@@
 
-\subsection{Simple Usage, simple Parameters}
+\subsection{Simple Usage, Simple Parameters}
 The proposal of a data generator (not necessarily for graph data) has to face an
@@
 coefficient, etc.).
+
+\subsection{Privacy-preserving Graph Generation}
+
+A lot of work have been conducted on the topic of privacy-preserving graph
+randomization for publishing social graphs~\cite{wu2010survey}. However, very
+little attention has been put on generating synthetic social graphs with
+privacy-preserving guarantees.
+
+Existing work focuses on generating graphs with ``differential
+privacy''~\cite{dwork2009differential} guarantees. More specifically, in
+~\cite{wang2013preserving} the authors develop a differential privacy graph
+generation approach based on the dK-graph generation
+model~\cite{mahadevan2006systematic} that outperforms the Stochastic Kronecker
+Graph Model~\cite{LeskovecCKF05} in terms of the produced structural properties,
+eventhough the results show that there is still room for improvement.
+
+More on this line of research, recent work~\cite{qin2017generating} extends the notion of differential privacy
+and propose an `` edge local differential privacy'' based graph generation
+method. The poposed method allows generating privacy preserving synthetic social
+graphs wihtout the need of a centralized data curator, while preserving structural
+properties more accurately than than straw-hat methods such as Randomized
+Neighbor Lists (based on randomized response~\cite{dwork2014algorithmic}) and
+Degree-based Graph Generation (which perturbates the original graph degrees
+using the Laplace mechanism~\cite{dwork2009differential}). Again, eventhough the
+proposed technique outperforms the baselines, the results show that there is
+still room for improvement.

### 2018-09-16 challenges.tex
Updated privacy-preserving part

--- 2018-09-02 challenges.tex
@@
 coefficient, etc.).
+
+\subsection{Privacy-preserving Graph Generation}
+
+A lot of work has been conducted on techniques for publishing social network
+graphs with privacy guarantees~\cite{wu2010survey}. However, the topic of
+generating social graphs with a realistic structure yet private has been barely explored.
+
+Most of the existing work falls within the topic of graph generation with ``differential
+privacy''~\cite{dwork2009differential} guarantees. More specifically, in
+~\cite{wang2013preserving} the authors develop a differential privacy graph
+generation approach based on the dK-graph generation
+model~\cite{mahadevan2006systematic} that outperforms the Stochastic Kronecker
+Graph Model~\cite{LeskovecCKF05} in terms of the produced structural properties,
+eventhough the results show that there is still room for improvement.
+
+Following this line of research, recent work~\cite{qin2017generating} extends the notion of differential privacy
+and propose an `` edge local differential privacy'' based graph generation
+method. The poposed method allows generating privacy preserving synthetic social
+graphs wihtout the need of a centralized data curator, while preserving structural
+properties more accurately than straw-hat methods such as Randomized
+Neighbor Lists (based on randomized response~\cite{dwork2014algorithmic}) and
+Degree-based Graph Generation (which perturbates the original graph degrees
+using the Laplace mechanism~\cite{dwork2009differential}). Again, eventhough the
+proposed technique outperforms the baselines, the results show that there is
+still room for improvement in terms of the structural properties of the
+generated graph.

### 2018-09-24 challenges.tex
Sherif Changes

@@
 robust and complex data generators (such as
-ToXGene~\cite{conf/webdb/BarbosaMKL02}, which supports specification of
+ToXGene~\cite{conf/webdb/BarbosaMKL02}, which supports the specification of
 structural aspects, value distributions, references etc.), the most popular
 benchmarking tool is XMark~\cite{Schmidt:2002:XBX:1287369.1287455}, which models
-a single use case and enables to specify just the size of the data. Hence, the
+a single use case and enables its users to specify just the size of the data. Hence, the
 other extreme is to provide a simple data generator which does not require any
@@
 
-Most of existing graph generators aiming at generating large graphs with realistic
+Most of existing graph generators are focused on generating large graphs with realistic
 structural characteristics focus principally on reproducing the degree
@@
 coefficient~\cite{kolda2014scalable,edunov2016darwini}. However, there are other
-structural characteristics one might be interested in reproducing for a large
+structural characteristics that one might be interested in reproducing for a large
 graph, such as the diameter, the size of the largest connected component, or the
@@
 of creating
-graph generators that allow to reproduce diverse structural characteristics
+graph generators that allow one to reproduce diverse structural characteristics
 of the graphs along with large scale sizes.
@@
 
-Most of existing graph generators generate graphs that are either not labeled or
+Most of existing graph generators also generate graphs that are either not labeled or
 are specific to a given domain (e.g.  Social Networks). Graphs from different
@@
 application under test. Thus, graph processing engine developers are asking for
-generators or tools to flexibly and holistically generate multi-domain graphs, allowing to configure aspects
+generators or tools to flexibly and holistically generate multi-domain graphs  in a flexible and holistic manner, allowing to configure aspects
 such as size, schemata, data distributions and other structural
@@
 
-The evolution of graphs can be considered variously.
+The evolution of graphs can be considered from multiple perspectives.
 We can assume a static set of nodes and a varying set of edges.
@@
 
-A related problem is \emph{data versioning} and respective ability to query across multiple versions of data or to carry out general analysis.
+A related problem is \emph{data versioning} and its respective ability to query across multiple versions of data or to carry out general analysis.
 %Considering graph
@@
 The respective data generator should hence be able to simulate a natural growth and/or changes in the structure of the graph with regards to the various features of distinct use cases.
-However,  even though the area of dynamic graphs is intensively studied, surprisingly there seem to exist only very few proposals of a generator dealing with this area.
+However,  even though the area of dynamic graphs is intensively studied, surprisingly there seem to exist only very few proposals of a generator for dealing with this area.
 In~\cite{GoerkeKlugeSchumm2012_1000029825} the authors focus on \emph{clustering dynamic graphs}, i.e.
@@
 to test new features and analyze efficiency of operations. However, since the
-multi-model systems are in the context of Big Data rather new, there exist only
+multi-model systems are in the context of Big Data are rather new, there exist only
 a few benchmarks targeting multi-model DBMSs (such as

### 2018-09-24 comparison.tex
Adding TODOs.
Minor corrections
Sherif Changes

@@
 
-In order to provide the reader with a quick preview of the generators and thus to enable finding the target solutions easily, we start the survey with classification and comparative study of the existing tools.
-In general, there are various ways how to classify them.
-We first overview approaches used in related work and then we introduce our approach.
-As mentioned in the Introduction, since this survey is unique in terms of scope and new tools related to Big Data processing, our classification and comparative strategy differs too.
+In order to provide the reader with a quick preview of the generators and thus to enable finding the target solutions easily, we start the survey with a  classification and comparative study of the existing tools.
+In general, there are various ways to classify them.
+We first provide an overview of the approaches used in related work after which we then introduce our approach.
+As mentioned in the Introduction, since this survey is unique in terms of scope and new tools related to Big Data processing, our classification and comparative strategy would differ as well.
 
 The graph data generators can be classified according to various criteria.
-For example, paper~\cite{DBLP:conf/sdm/ChakrabartiZF04} introduces two categories -- degree-based and procedural generators.
+For example,~\cite{DBLP:conf/sdm/ChakrabartiZF04} introduces two categories -- degree-based and procedural generators.
 Given a degree distribution (typically following a power law), \emph{degree-based generators} (e.g., Barabasi-Albert model~\cite{Barabasi99emergenceScaling}) try to find a graph that matches it, but without giving any insights about the graph or trying to match other criteria (like, e.g., small diameter, eigenvalues etc.).
@@
 \subsection{Classification}
+
+\TODO{Add info to all three tables.}
 
@@
 \cline{2-10}
-  & BTER & & & & & & & &    \\
+  & BTER  & N & N &   N &  & N & user-defined &  ? & Y  \\
 \cline{2-10}
-  & Darwini & & & & & & & &    \\
+  & Darwini  & N & N &   N &  & N & user-defined &  ? & Y   \\
 %  & Watts-Strogatz~\cite{watts1998collective} & fixed & & Y & N & Y &  & &  N  \\
@@
 % & Forest Fire  & N & Y   & N &  & N & power-law &  ? & N   \\
-%\cline{2-10}
-% & Darwini  & N & N &   N &  & N & user-defined &  ? & Y   \\
-%\cline{2-10}
-% & BTER  & N & N &   N &  & N & user-defined &  ? & Y  \\
 \hline
@@
 
+As we can see ... \TODO{Add a summary.}
+
 \subsection{Overlapping}
 
-As we have mentioned, the basic classification we use in this paper is  based on a relatively vague division of the generators on the basis of the current application domains or research areas.
+As we have mentioned, the basic classification that we have used in this paper is  based on a relatively vague division of the generators on the basis of the current application domains or research areas.
 In addition, some of the generators are either general or have features applicable in other domains.
@@
   & Darwini   & x & & & & & \\
-%  & Watts-Strogatz~\cite{watts1998collective}  & x & & & & & \\
-%\cline{2-8}
 \hline
@@
   & \cite{Nettleton2016}  & & & & x & & \\
-%\cline{2-8}
-% & SNG  & & & & x & & \\
-%\cline{2-8}
-% & Forest Fire  & & & & x & & \\
-%\cline{2-8}
-% & Darwini & & & & x & & \\
-%\cline{2-8}
-% & BTER  & & & & x & & \\
 \hline
@@
 \end{table}
+
+As we can see ... \TODO{Add a summary.}

### 2018-09-24 conclusion.tex
Sherif Changes

@@
 Graphs form one of the most complex data structures requiring specific and usually sophisticated approaches for processing and analysis.
-The history of graph theory, studying these structures and respective algorithms, can be traced back to the 18th century.
+The history of graph theory,  that started from when these structures and their respective algorithms were studied can be traced back to the 18th century.
 
-With the recent dawn of Big Data there have occurred also large scale graphs where the efficiency   of  processing methods is critical.
+With the recent dawn of Big Data there have  been more occurrences of large scale graphs where the efficiency   of  processing methods is critical.
 Approaches that work for smaller scale graphs often cannot be used, the data need to be processed in a distributed way and hence the efficiency is influenced by other aspects, such as limits of data transport.

### 2018-09-24 data_sets.tex
Sherif Changes

@@
   \item \textbf{DBLP}~\cite{yang2015defining}: Represents a co-authorship network where
-    researchers from DBLP are represented as vertices and there exists and edge
+    researchers from DBLP are represented as vertices and there exists an edge
     between them if they have published a paper together.
@@
   \item \textbf{LiveJournal}~\cite{yang2015defining}: A social network where vertices
-    represent the users and the edges the acquitances between them.
+    represent the users and the edges represent the acquitances between them.
   \item \textbf{Orkut}~\cite{yang2015defining}: Like LiveJournal, this is a social network
-    where vertices represent persons and the edges their friendships.
+    where vertices represent persons and the edges represent their friendships.
   \item \textbf{Twitter}~\cite{kwak2010twitter}: This is a directed network representing
@@
   \item \textbf{WebUK}~\cite{delis}: A web graph of the UK subdomain, where nodes represent
-    websites and edges the hyperlinks between them.
+    websites and edges represent the hyperlinks between them.
   \item \textbf{ClueWeb2012}~\cite{clueweb}. This is a crawl of the web from 2012, where
-    vertices represent websites and the edges the hyperlinks connecting them.
+    vertices represent websites and the edges represent the hyperlinks connecting them.
 \end{itemize}
@@
 many-to-many graphs. Such systems are usually tested on several real-world datasets,
-many of them containing information about rating of products or other items such
+many of them containing information about the rating of products or other items such
 as movies, books or songs. The following are the most widely used datasets for
@@
       editors where the vertices are the editors and the edges, which are
-      labelled, represent the turst level between two editors.
+      labelled, represent the trust level between two editors.
     \item \textbf{Extended Epinions}~\cite{massa2007trust}: This is an extended version of
@@
 can find a comprehensive list of datasets for such algorithms
-in~\cite{10dimacs,yang2015defining}, some of them already discussed for other
+in~\cite{10dimacs,yang2015defining}, some of which we have already discussed for other
 applications. Here, we summarize the most widely used in the literature:
@@
     together. The books have labels of whether they are left or right oriented.
-  \item \textbf{Football}~\cite{girvan2002network}: A network of american university
+  \item \textbf{Football}~\cite{girvan2002network}: A network of American university
     football teams. Each node represents a football team and the edges represent
@@
     network before, during and after the discovery of the Higgs boson.
-    Concretely, it contains the tweets, the mentions, retweets,
+    Specifically, it contains the tweets, the mentions, retweets,
     followers/followees, etc.
@@
     relationships between the different resources at Wikipedia.
-  \item \textbf{Freebase}~\cite{bollacker2008freebase}: Is a collaborative knowledge base
-    made of metadata mainly provided by community members. It contains
+  \item \textbf{Freebase}~\cite{bollacker2008freebase}: This is a collaborative knowledge base
+    made of metadata that is mainly provided by community members. It contains
     structured data from multiple sources in an attempt to create a global
@@
     open source knowledge bases developed at the Max Planck Institute of
-    Computer Science in Saarbr\"ucken. They contain structured data automatically extracted
+    Computer Science in Saarbr\"ucken. They contain structured data  that has been automatically extracted
     from Wikipedia and other sources.

### 2018-09-24 generators.tex
Sherif Changes

@@
 
-In this section we explore in more detail different graph data generators using the classification introduced before.
-For each category we briefly describe key features of each of the representatives.
+In this section we explore in more detail the different graph data generators using the classification introduced before.
+For each category we briefly describe the key features of each of the representative examples.
 The aim is to provide the readers with a detailed look at each of the tools in the context of its competitors from the same domain.

### 2018-09-24 generators_GraphDatabases.tex
Sherif Changes

@@
 Currently there exists a number  of papers which compare the efficiency of graph databases with regards to distinct use cases, such as  the community detection problem~\cite{Beis2015}, social tagging systems~\cite{Giatsoglou2011}, graph traversal~\cite{Ciglan:2012:BTO:2374486.2375242}, graph pattern matching~\cite{Pobiedina2014}, data provenance~\cite{Vicknair:2010:CGD:1900008.1900067}, or even several distinct use cases~\cite{Grossniklaus2013Towar-24253}.
-However, the number of graph data generators and benchmarks designed particularly for graph databases is relatively small.
-Either a general graph generator is used for benchmarking graph databases, such as, e.g., the HPC Scalable Graph Analysis Benchmark~\cite{Dominguez-Sal:2010:SGD:1927585.1927590}.
-Or the graph DBMS benchmarking tools are designed in a more general scope.
-Hence it is questionable whether a benchmark specific for graph databases is necessary.
+However, the number of graph data generators and benchmarks that have been designed specifically for graph databases is relatively small.
+Either a general graph generator is used for benchmarking graph databases, such as, e.g., the HPC Scalable Graph Analysis Benchmark~\cite{Dominguez-Sal:2010:SGD:1927585.1927590} or the graph DBMS benchmarking tools are designed in a more general scope.
+Hence it is questionable whether a benchmark  that is targeted specifically for graph databases is necessary.
 \cite{Dominguez-Sal:2010:DDG:1946050.1946053} discussed this question and related topics.
-On the basis of a review of applications of graph databases (namely social network analysis, proteomics or genetic interactions, recommendation systems, and travel planning and routing), the authors analyze and discuss the characteristics of the graphs that appear in such applications and how they could influence benchmarking, different types of operations used in these applications and the characteristics of the evaluation setup of the benchmark.
+On the basis of a review of applications of graph databases (namely social network analysis, proteomics or genetic interactions, recommendation systems, and travel planning and routing), the authors analyzed and discussed the characteristics of the graphs that appear in such applications and how they could influence benchmarking, different types of operations used in these applications and the characteristics of the evaluation setup of the benchmark.
 In this section, we focus on graph data generators and benchmarks that have been primarily targeting graph DBMSs.
@@
 \paragraph{XGDBench} XGDBench~\cite{Dayarathna:2014:GDB:2676904.2676939} is an extensible graph database benchmarking platform for cloud computing systems. Its intent is to automate
-the process of graph database benchmarking in the cloud focusing on a graph database application for social networking services.
+the process of graph database benchmarking in the cloud by focusing on a graph database application for social networking services.
 It extends the Yahoo!
@@
 The workload generator of YCSB supports definition of new workload types.
-XGDBench involves basic operations read / insert / update / delete an attribute, loading of the list of neighbors and BFS traversal.
-Using them 7 workloads are created, such as update heavy, read mostly, short range scan, traverse heavy etc.
+XGDBench involves basic operations such as read / insert / update / delete an attribute, loading of the list of neighbors and BFS traversal.
+Using the generators, 7 workloads are created, such as update heavy, read mostly, short range scan, traverse heavy etc.
 The data model of XGDBench is a simplified version of the Multiplicative Attribute Graph (MAG)~\cite{Kim2010} model, a synthetic graph model for attribute graphs which models the interactions between the network structure and the node attributes.
@@
 The resulting graph can be exported to several formats (namely GraphJson\footnote{\url{https://github.com/GraphAlchemist/GraphJSON/wiki/GraphJSON}} and CypherQueries) or loaded directly to a DBMS.
-However, it is probably not maintained anymore.
+However, it is very likely that it is not maintained anymore due to the lack of updates provided.

### 2018-09-24 generators_LinkedData.tex
Sherif Changes

@@
 \label{sec:generators_LinkedData}
-With the dawn of the concept of Linked Data there have naturally emerged also respective benchmarks involving both real-world data sets and synthetic data sets with real-world characteristics.
+With the dawn of the concept of Linked Data it is a natural development that there would emerge respective benchmarks involving both real-world data sets and synthetic data sets with real-world characteristics.
 The used data sets correspond to RDF representation of relational-like data~\cite{Guo2005158,Bizer09theberlin}, social network-like data~\cite{Schmidt2010}, or specific and significantly more complex data structures such as biological data~\cite{Wu2014}.
@@
 The benchmark comes with 12 queries and 2 query mixes (sequences of the 12 queries) emulating the search and navigation pattern of a consumer looking for a product.
-The data generator supports creation of arbitrarily large datasets using the number of products $n$ as scale factor which further influences also other characteristics of the data, such as, e.g., the depth of type hierarchy of products (defined as $d = round(log_{10}(n))/2 + 1$), branching factor ($bfr = 2 \times round(log_{10}(n))$), the number of product features (having $lowerBound = 35 \times i / (d \times (d+1)/2 - 1)$ and $upperBound = 75 \times i / (d \times (d+1)/2 - 1)$) etc.
+The data generator supports the creation of arbitrarily large datasets using the number of products $n$ as scale factor which further influences also other characteristics of the data, such as, e.g., the depth of type hierarchy of products (defined as $d = round(log_{10}(n))/2 + 1$), branching factor ($bfr = 2 \times round(log_{10}(n))$), the number of product features (having $lowerBound = 35 \times i / (d \times (d+1)/2 - 1)$ and $upperBound = 75 \times i / (d \times (d+1)/2 - 1)$) etc.
 BSBM can output two representations -- an RDF representation and a purely relational representation.
 Thus, BSBM also defines an SQL~\cite{sql} representation of the queries.
-This allows comparison of SPARQL~\cite{sparql} results with the performance of traditional RDBMSs.
+This allows comparison of SPARQL~\cite{sparql} results  to be compared against the performance of traditional RDBMSs.
 
@@
 \paragraph{Data Coherence}  A comparison of 4 RDF benchmarks (namely TPC-H~\cite{TPC-H} data expressed in RDF, LUBM, BSBM, and SP$^2$Bench) and 6 real-wold data sets (such as, e.g.,  DBpedia~\cite{Bizer:2009:DCP:1640541.1640848}, the Barton Libraries Dataset~\cite{barton-benchmark} or
-WordNet~\cite{Miller:1995:WLD:219717.219748}) is provided in paper~\cite{Duan:2011:AOC:1989323.1989340}.
-The authors focus mainly on \emph{structuredness} (\emph{coherence}) of each benchmark dataset claiming that a primitive metric (e.g., the number of triples or the average in/outdegree) quantifies only some specific aspect of each dataset.
+WordNet~\cite{Miller:1995:WLD:219717.219748}) has been reported by~\cite{Duan:2011:AOC:1989323.1989340}.
+The authors focus mainly on the  \emph{structuredness} (\emph{coherence}) of each benchmark dataset claiming that a primitive metric (e.g., the number of triples or the average in/outdegree) quantifies only some specific aspect of each dataset.
 The level of structuredness of a dataset $D$ with respect to a type $T$ is determined by how well the instance data in $D$ conforms to type $T$.
@@
 The structuredness is then expressed as a weighted sum of share of set properties of each type, whereas higher weights are assigned to types with more instances.
-The authors show that structuredness of the chosen benchmarks is fixed, whereas real-world RDF datasets lie in currently untested parts of the spectrum.
+The authors show that the structuredness of the chosen benchmarks is fixed, whereas real-world RDF datasets lie in currently untested parts of the spectrum.
 As a consequence, they introduce a new benchmark that accepts as input any dataset along with a desired level of structuredness and size (smaller than the size of the original data), and uses the input dataset as a seed to produce a subset of the original data with the indicated size and structuredness.
@@
 The proposed dataset creation process starts with an input dataset.
-Datasets of multiple size of the original data are created by duplicating all triples and changing their namespaces.
+Datasets of multiple sizes of the original data are created by duplicating all triples and changing their namespaces.
 For generating smaller datasets, an appropriate fraction of all triples is selected randomly or by sampling across classes in the dataset.
@@
 
-\paragraph{LODIB} The Linked Open Data Integration Benchmark (LODIB)\footnote{\url{http://lodib.wbsg.de/}} has been designed with the aim to reflect the real-world heterogeneities that exist on the Web of Data in order to enable testing of Linked Data translation systems~\cite{DBLP:conf/www/RiveroSBR12}.
+\paragraph{LODIB} The Linked Open Data Integration Benchmark (LODIB)\footnote{\url{http://lodib.wbsg.de/}} has been designed with the aim of reflecting the real-world heterogeneities that exist on the Web of Data in order to enable testing of Linked Data translation systems~\cite{DBLP:conf/www/RiveroSBR12}.
 It provides a catalogue of 15 data translation patterns (e.g., rename class, remove language tag etc.), each of which is a common data translation problem in the context of Linked Data.
@@
 Hence, they propose a benchmark for challenging query processing over real graphs~\cite{sib}.
-It simulates an RDF backend of a social network site, in which users and their interactions form an social graph of social activities such as writing posts, posting comments, creating/managing groups, etc.
+It simulates an RDF backend of a social network site, in which users and their interactions form a social graph of social activities such as writing posts, posting comments, creating/managing groups, etc.
 The distribution of generated data on each relation conforms to the data distribution analyzed over real-world social networks.
@@
 The analysis of the four benchmarks reveals that they are not sufficiently diverse to test the strengths and weaknesses of different physical design choices employed by RDF systems.
-The proposed solution, WatDiv, involves (1) a data generator which generates scalable datasets according to WatDiv schema, (2) a query template generator which traverses the WatDiv schema and generates a diverse set of query templates, (3) a query generator which instantiates the templates with actual RDF terms from the dataset, and (4) a feature extractor which computes the structural and data-driven features of the generated data and workload.
+The proposed solution, WatDiv, involves (1) a data generator which generates scalable datasets according to the WatDiv schema, (2) a query template generator which traverses the WatDiv schema and generates a diverse set of query templates, (3) a query generator which instantiates the templates with actual RDF terms from the dataset, and (4) a feature extractor which computes the structural and data-driven features of the generated data and workload.
 For the study in the paper the authors generated 12,500 test queries from 125 query templates.
@@
 \iffalse The following three benchmarks were developed and are currently maintained.\fi In the Semantic Web domain, the project released the Semantic Publishing Benchmark (SPB)~\cite{spb} that has been inspired by the Media/Publishing industry (namely BBC\footnote{\url{http://www.bbc.com/}}).
-The application scenario of this benchmark considers a media or a publishing organization that deals with large volume of streaming content, namely news, articles or  ``media assets''.
+The application scenario of this benchmark considers a media or a publishing organization that deals with large volumes of streaming content, namely news, articles or  ``media assets''.
 This content is enriched with metadata that describes it and links it to reference knowledge -- taxonomies and databases that include relevant concepts, entities and factual information.
@@
 Two workloads are provided: (1) basic, involving an interactive query-mix querying the relations between entities in reference data, and (2) advanced,  consisting of interactive and analytical query-mixes.
-The LDBC designed two other benchmarks: the Social Network Benchmark (SNB)~\cite{Erling:2015:LSN:2723372.2742786} for the social network domain  (see Section~\ref{sec:generators_socialnetworks}) and Graphalytics~\cite{Iosup:2016:LGB:3007263.3007270}   for the analytics domain (see Section~\ref{sec:generators_analytics}).
+The LDBC has designed two other benchmarks: the Social Network Benchmark (SNB)~\cite{Erling:2015:LSN:2723372.2742786} for the social network domain  (see Section~\ref{sec:generators_socialnetworks}) and Graphalytics~\cite{Iosup:2016:LGB:3007263.3007270}   for the analytics domain (see Section~\ref{sec:generators_analytics}).
 
@@
 The generator is designed to receive a vocabulary as an input  and supports two statistical distribution techniques for generating entities: Gaussian distribution and Zipf's power-law distribution.
-LinkGen can augment the generated data with inconsistent and noisy  data such as writing two conflicting values for a given datatype property,  adding triples with syntactic errors, adding wrong statement by assigning invalid domain and creating instances with no type information.
+LinkGen can augment the generated data with inconsistent and noisy  data such as writing two conflicting values for a given datatype property,  adding triples with syntactic errors, adding wrong statements by assigning them with invalid domain and creating instances with no type information.
 The generator is also designed with  an option to inter-link the generated instances with real ones given that the user provides entities from real datasets.

### 2018-09-24 generators_SocialNetworks.tex
Sherif Changes

@@
 
-In general, analyses of social networks identify their various specific
+In general, any analysis of social networks identify their various specific
 features~\cite{Chakrabarti:2006:GML:1132952.1132954}. For example, a social
@@
 communities in 70 real-world networks is provided, e.g., in
-paper~\cite{Leskovec:2008:SPC:1367497.1367591}. Authors of
-paper~\cite{Prat-Perez:2014:CSS:2621934.2621942} analyze the structure of
+~\cite{Leskovec:2008:SPC:1367497.1367591}. 
+~\cite{Prat-Perez:2014:CSS:2621934.2621942} analyzed the structure of
 communities (clustering coefficient, triangle participation ratio, bridges,
@@
 approaches}~\cite{PhysRevE.78.046110,Yao2011,Armstrong:2013:LDB:2463676.2465296,Pham2013,Sukthankar-SocialInfo2014,Erling:2015:LSN:2723372.2742786,Nettleton2016}
-focus on reproducing aspects of the network. In \emph{agent-based
+focused on reproducing aspects of the network. In \emph{agent-based
 approaches}~\cite{Barrett:2009:GAL:1995456.1995598,Bernstein:2013:SAS:2499604.2499609}
@@
 \paragraph{Realistic Social Network}
-~\cite{Barrett:2009:GAL:1995456.1995598} focused on construction of
+~\cite{Barrett:2009:GAL:1995456.1995598} focused on the construction of
 realistic social networks using a combination of public and private data sets
@@
 the \emph{activity graph}, where nodes also stand for the people but edges stand
-for their interactions. On the basis of analysis of
+for their interactions. On the basis of the analysis of
 Flickr\footnote{\url{https://www.flickr.com/}} social links and
@@
 clustering coefficient (community structure), and small diameter; also regarding
-the dynamic properties they both follow densification law and relatively stable
+the dynamic properties they both follow the densification law and have relatively stable
 clustering coefficient over time. However, the authors do not observe diameter
-shrinking in Epinions activity graph and there is a difference in degree
+shrinking in opinions activity graph and there is a difference in degree
 correlation (how frequently nodes with similar degrees connect to each other).
@@
 the source node which  are processed in parallel. The edges of the graph are
-generated in accordance with the results of analysis of real-world Facebook data
+generated in accordance with the results of analysing  real-world Facebook data
 (such as outdegree distribution). A workload corresponding to 10 graph
@@
 is possible to have a correlated degree distribution, from which the degree of
-each node is generated, correlated with properties of node. Hence the generator
+each node is generated, correlated with the properties of node. Hence the generator
 can ensure that, e.g., people with many friends in a social network will
@@
 network (such as a small graph diameter, small average path length, skew degree
-distribution, and community structures), however without data. Hence, they
+distribution, and community structures), however,  this is usually done without any data. Hence, they
 introduced a general stochastic modeling system which allows the users to

### 2018-09-24 generators_community_detection.tex
Sherif Changes

@@
 Additionally, the generator introduces the concept of the ``mixing factor'', which specifies the fraction of its links connecting nodes belonging to different communities.
-Such parameter allows to tune the degree of modularity of the generated graph, thus testing the robustness of the algorithms under different conditions.
+Such parameter allows  the degree of modularity of the generated graph  to be tuned, thus testing the robustness of the algorithms under different conditions.
 The generation process starts with an empty graph and incrementally fills in the adjacency matrix by obeying the described constraints.
@@
 However, a recent study from Hric, Darst and Fortunato~\cite{hric2014community} reveal a loose correspondence between  communities (the authors refer to them as structural communities) and meta-communities.
-This result reveals that  algorithms working for structural communities do not work well for finding meta-communities and viceversa, suggesting significantly different underlying characteristics between the two types of communities, which are yet to be identified.
+This result reveals that  algorithms working for structural communities do not work well for finding meta-communities and vice versa, suggesting significantly different underlying characteristics between the two types of communities, which are yet to be identified.
 
 In this regard and to the best of our knowledge, there does not exist a set of generators to generate graphs with meta-communities for community detection algorithm benchmarking.
-The closest one is the LDBC-SNB data generator~\cite{Erling:2015:LSN:2723372.2742786} thanks to the generation of groups of users in the social network.
+The closest one is the LDBC-SNB data generator~\cite{Erling:2015:LSN:2723372.2742786} which has been provided by the generation of groups of users in the social network.
 Even though the generation process does not specifically enforce the generation of groups (meta-communities) for benchmarking community detection algorithms, the study from Prat-Pe\'rez and Dominguez-Sal reveals that these groups are more similar to the real meta-communities than those structural communities generated by the LFR benchmark~\cite{Prat-Perez:2014:CSS:2621934.2621942}.
@@
 Current community detection algorithms and graph generators for community detection are stuck to the traditional (and vague) definition of community, assuming that there exists a single algorithm that would fit all the use cases.
-Thus, future work requires the study of domain-specific community characteristics that can be used to generate graphs with a community structure that accurately resemble that of specific use cases, and thus revealing which are the best algorithms for each particular scenario.
+Thus, future work requires the study of domain-specific community characteristics that can be used to generate graphs with a community structure that accurately resembles that of specific use cases, and thus revealing which are the best algorithms for each particular scenario.

### 2018-09-24 generators_general.tex
Sherif Changes

@@
 
-First of all we focus on papers dealing with generation of general graph
-data not aiming at a particular application domain. Currently, there exists a
+We start by focusing on approaches that have been designed for dealing with the generation of general graph
+data that is not aimed at a particular application domain. Currently, there exists a
 number of tools which involve a kind of general graph data generator, such as
@@
 GraphBase~\cite{GraphBase}. We, however, focus on primarily
-generating/benchmarking projects targeting Big Data world.
+generating/benchmarking projects targeting the Big Data world.
 
@@
 mining/mining.shtml}}. GraphGen creates a collection of labeled, undirected and
-connected graphs aiming at performance evaluation of frequent subgraph mining
+connected graphs which focuses on the performance evaluation of frequent subgraph mining
 algorithms and graph query processing algorithms. The result is represented as a
@@
 creation of multiple Erd\"{o}s-R\'{e}ny graphs with different connection
-probabilities, connected randomly between them. As the main feature, BTER is able
+probabilities  of which they are connected randomly between them. As the main feature, BTER is able
 to reproduce input degree distributions and average clustering
@@
 MapReduce based implementation that is capable of generating large graphs (with
-billions of nodes) in reasonable amounts of time.
+billions of nodes) in a reasonable amounts of time.
 
@@
 coefficient distribution per degree. It achieves this by grouping the vertices
-of the graph into buckets by the expected number of closed triangles they need
+of the graph into buckets by the expected number of closed triangles that they need
 to close in order to attain the expected clustering coefficient, which is
 sampled from the input distributions. Then, the vertices in each bucket are
-connected randomly with a probability that would produce, in expectation, the
+connected randomly with a probability that would produce the expected 
 desired number of triangles for such bucket. Then, as in BTER, the excess degree

### 2018-09-24 generators_streaming.tex
Sherif Changes

@@
 One way for dealing with big graphs is to process them using the \emph{streaming} mode where the data stream could consist of the edges of the graph.
-In this mode, the graph processing algorithms can process the input stream in the order it arrives while using only a limited amount memory~\cite{mcgregor2014graph}.
+In this mode, the graph processing algorithms can process the input stream in the order it arrives while using only a limited amount of memory~\cite{mcgregor2014graph}.
 The streaming mode has mainly  attracted the attention of the RDF and Semantic Web community.
 Thus, Phuoc et al.~\cite{le2012linked} presented an evaluation framework for linked stream data processing engines.
-The framework uses a data generator for Stream Social network data Generator (S2Gen) that simulates what users continuously generate on their social network activities (e.g., posts) in addition to the  user metadata such as users' profile information, social network relationships, posts, photos and GPS information.
+The framework uses a data generator for the Stream Social network data Generator (S2Gen) that simulates what users continuously generate on their social network activities (e.g., posts) in addition to the  user metadata such as users' profile information, social network relationships, posts, photos and GPS information.
 The data generator of this framework provides the users the flexibility to control the characteristics of the generated data by tanning a range of parameters including the period in which the social activities are generated (generating period), the maximum number of posts/comments/photos for each user per week and the correlation probabilities between the different objects (e.g., users) in the social network.
@@
 In particular, the Streamer  component uses TripleWave\footnote{\url{http://streamreasoning.github.io/TripleWave/}}, an open-source framework for publishing and sharing RDF streams on the Web~\cite{mauri2016triplewave}.
-TripleWave acts as a mean for plugging in diverse Web data sources and for consuming streams in both push and pull mode.
+TripleWave acts as a mean for plugging-in diverse Web data sources and for consuming streams in both push and pull mode.

### 2018-09-24 introduction.tex
Sherif Changes

@@
 
-To the best of our knowledge, our work is the first surveying the broad
+To the best of our knowledge, our work is the first to survey the broad
 landscape of graph data generators spanning different data-intensive applications and
@@
 analytics generators, IoT, Telecommunication and graph streaming generators,
-and Machine Learning and graph mining generators. A comprehensive study of
-graph generators is yet missing for many of the specific subfields mentioned
-above.
+and Machine Learning and graph mining generators. However, the literature is still lacking a comprehensive study of
+graph generators  for many of the specific subfields mentioned above.
 
@@
 In our work, we provide a more comprehensive and broader classification
- serving the purpose of letting any
-researcher or practitioner interested in data generation make a wise
+ that serves the purpose of letting any
+researcher or practitioner interested in data generation  to be able to make a better 
 choice of the desired graph
@@
 
-Aggarwal and Subbian \cite{AggarwalS14} have surveyed evolution analysis in
+Aggarwal and Subbian \cite{AggarwalS14} have surveyed the evolution of analysis in
 graphs, by primarily focusing on data mining maintenance methods and on analytical
@@
 network data generators is carried out in
-the paper. The data generation of evolutionary networks based on
+the paper. The data generation of evolutionary networks is based on
 Densification Power Law (DPL) and shrinking diameters \cite{LeskovecKF05} and community-guided
@@
 
-\paragraph*{Outline} The rest of the text is structured as follows:
-In Section~\ref{sec:comparison} we provide the opening categorization and comparison of the generators.
-In Section~\ref{sec:generators} we overview the existing graph data generators and their main features in the frame of the proposed categories.
-To provide a complete overview, in Section~\ref{sec:data_sets} we list most commonly used testing data sets for the particular categories.
-In Section~\ref{sec:challenges} we discuss challenges and open problems of graph data synthesis and in Section~\ref{sec:conclusion} we conclude.
+\paragraph*{Outline} The rest of this paper is organized as follows: Section~\ref{sec:comparison}  provides the opening categorization and comparison of the generators.
+Section~\ref{sec:generators} provides an overview of the existing graph data generators and their main features in the frame of the proposed categories.
+To provide a complete overview,  we list the most commonly used testing data sets for the particular categories in Section~\ref{sec:data_sets}.
+In Section~\ref{sec:challenges}, we highlight some of the challenges and open problems of graph data synthesis before we conclude in Section~\ref{sec:conclusion}.

### 2018-09-24 comparison.tex
Sherif Changes

@@
 \cline{2-10}
-  & GraphGen & & & & & & & &    \\
+  & GraphGen & fixed & N & Y & N & Y&  & & N   \\
 \cline{2-10}
-  & Graph 500  & fixed & & Y & N & Y & power-law & &  Y  \\
+  & Graph 500  & fixed & Various Domains& Y & N & Y & power-law & &  Y  \\
 \cline{2-10}
@@
 \cline{2-10}
- & LinkGen & & & & & & & & \\
+ & LinkGen & schema-driven & user-defined & templates & Y  & N & Gaussian, Zipfian& RDF & N\\
 \hline
@@
 \multirow{3}{*}{\rot{\textbf{Ana.}}}
-  & HPC Scalable Graph Analysis & & & & & & & &    \\
+  & HPC Scalable Graph Analysis & fixed & & Y & N& N& uniform & & N   \\
 \cline{2-10}
-  & Graphalytics & & & & & & & &    \\
+  & Graphalytics & extracted & social network & Y& N& power law & & & N   \\
 \hline

### 2018-09-28 comparison.tex
Updated table with social network graphs

@@
 \multirow{8}{*}{\rot{\textbf{SNs}}}
- & \cite{Barrett:2009:GAL:1995456.1995598} & & & & & & & &    \\
+ & \cite{Barrett:2009:GAL:1995456.1995598} & fixed & social network & N & N & Y & simulation-driven & -- &  -- \\
 \cline{2-10}
- & \cite{Yao2011} & & & & & & & &    \\
+ & \cite{Yao2011} & fixed & social network & N & N & N & power-law & -- & --  \\
 \cline{2-10}
- & LinkBench & & & & & & & &    \\
+ & LinkBench & fixed & social network & Y & Y & Y & Facebook & -- & -- \\
 \cline{2-10}
- & S3G2 & Y & Y  & N &  & Y & Facebook-like  &  CSV, RDF & Y   \\
+ & S3G2 & Y & Y  & N &  & Y & Facebook  & CSV, RDF & Y   \\
 \cline{2-10}
- & \cite{Sukthankar-SocialInfo2014} & & & & & & & &    \\
+ & \cite{Sukthankar-SocialInfo2014} & schema-driven & social-network & N & N & Y & power-law & CSV & N   \\
 \cline{2-10}
- & LDBC SNB  & Y & Y &   generated &  & Y & Facebook-like &  CSV, RDF & Y     \\
+ & LDBC SNB  & Y & Y &   generated &  & Y & Facebook &  CSV, RDF & Y     \\
 \cline{2-10}
-  & \cite{Nettleton2016} & & & & & & & &    \\
+  & \cite{Nettleton2016} & schema-driven & social network & N & N & Y & power-law & -- & N  \\
 %\cline{2-10}
@@
 \cline{2-8}
- & S3G2  & & & & x & & \\
+ & S3G2  & & x & x & x & & \\
 \cline{2-8}
@@
 \cline{2-8}
- & LDBC SNB   & & & & x & & \\
+ & LDBC SNB   & & x & x & x & & \\
 \cline{2-8}
@@
 
-As we can see ... \TODO{Add a summary.}
+As we can see ... \TODO{Add a summary.} LDBC can be also seen as graph databases
+(even tough it is not specific for them, it is clear it was designed for such
+technologies).

### 2018-09-28 comparison.tex
Added two paragramhs of summary for social networks

@@
 \cline{2-10}
- & S3G2 & Y & Y  & N &  & Y & Facebook  & CSV, RDF & Y   \\
+ & S3G2 & fixed & social network  & N & N  & Y & Facebook  & CSV, RDF & Y   \\
 \cline{2-10}
@@
 \cline{2-10}
- & LDBC SNB  & Y & Y &   generated &  & Y & Facebook &  CSV, RDF & Y     \\
+ & LDBC SNB  & fixed & social network &  generated & Y  & Y & Facebook &  CSV, RDF & Y     \\
 \cline{2-10}
@@
 
-As we have mentioned, the basic classification that we have used in this paper is  based on a relatively vague division of the generators on the basis of the current application domains or research areas.
-In addition, some of the generators are either general or have features applicable in other domains.
-So the classes can overlap, as depicted in Table~\ref{tab:overlapping}.
+As we have mentioned, the basic classification that we have used in this paper
+is  based on a relatively vague division of the generators on the basis of the
+current application domains or research areas. In addition, some of the
+generators are either general or have features applicable in other domains. So
+the classes can overlap, as depicted in Table~\ref{tab:overlapping}.
 
@@
 \cline{2-8}
- & LinkBench  & & & & x & & \\
+ & LinkBench  & & & x & x & & \\
 \cline{2-8}
@@
 
-As we can see ... \TODO{Add a summary.} LDBC can be also seen as graph databases
-(even tough it is not specific for them, it is clear it was designed for such
-technologies).
+\TODO{Extend summary.}
+For example, some social network graph generators such as the LDBC-SNB, S3G2 or
+LinkBench, can be used to test graph databases. In the case of the first two,
+even though they are designed not to be specific to any type of technology,
+they graph databases are their main target.  Additionally, they also provide serializers for
+RDF, thus they can also be used to test RDF systems.
+
+In the case of LinkBench, nothing prevents the user to load the generated graph
+in a graph database (Facebook uses a MySQL in that paper) to
+test a workload similar to Facebook and extend and complement it with more
+graphy queries like those in LDBC-SNB.

### 2018-09-30 generators_general.tex
last pass on my side

@@
 database of graphs, their average size and average density, the authors have
-also implemented a synthetic generator called GraphGen~\cite{GraphGen}. It is
+also implemented a synthetic generator called
+GraphGen~\footnote{https://www.cse.ust.hk/graphgen/}. It is
 based on the IBM synthetic data generation code for associations and sequential

### 2018-09-30 comparison.tex
last pass on my side
pass on Table III
Fixed several cells in table

@@
 \multirow{7}{*}{\rot{\textbf{General}}}
-  & \cite{barabasi1999emergence} & fixed & & Y & N & Y &  & &  N  \\
+  & \cite{barabasi1999emergence} & fixed & & Y & N & Y &  & edge-list &  N  \\
 \cline{2-10}
-   & R-MAt & fixed & & Y & N & Y & power-law & &  N  \\
+   & R-MAt & fixed & & Y & N & Y & power-law & edge-list &  N  \\
 \cline{2-10}
@@
 \cline{2-10}
-  & BTER  & N & N &   N &  & N & user-defined &  ? & Y  \\
+  & BTER & fixed & N &   N &  & N & user-defined & edge-list & Y  \\
 \cline{2-10}
-  & Darwini  & N & N &   N &  & N & user-defined &  ? & Y   \\
+  & Darwini & fixed & N &   N &  & N & user-defined &  edge-list & Y   \\
 %  & Watts-Strogatz~\cite{watts1998collective} & fixed & & Y & N & Y &  & &  N  \\
@@
 \multirow{8}{*}{\rot{\textbf{SNs}}}
- & \cite{Barrett:2009:GAL:1995456.1995598} & fixed & social network & N & N & Y & simulation-driven & -- &  -- \\
+ & \cite{Barrett:2009:GAL:1995456.1995598} & fixed & social network & N & N & Y & simulation-driven & impl. not available &  -- \\
 \cline{2-10}
- & \cite{Yao2011} & fixed & social network & N & N & N & power-law & -- & --  \\
+ & \cite{Yao2011} & fixed & social network & N & N & N & power-law & impl. not available & --  \\
 \cline{2-10}
- & LinkBench & fixed & social network & Y & Y & Y & Facebook & -- & -- \\
+ & LinkBench & fixed & social network & Y & Y & Y & Facebook & impl. not available & -- \\
 \cline{2-10}
@@
 \cline{2-10}
-  & \cite{Nettleton2016} & schema-driven & social network & N & N & Y & power-law & -- & N  \\
+  & \cite{Nettleton2016} & schema-driven & social network & N & N & Y & power-law & impl. not available & --  \\
 %\cline{2-10}
@@
 \multirow{6}{*}{\rot{\textbf{General}}}
-  & \cite{barabasi1999emergence} & x & & & & & \\
+  & \cite{barabasi1999emergence} & {\bf x} & & & & & \\
 \cline{2-8}
-   & R-MAt    & x & & & & & \\
+   & R-MAt    & {\bf x} & & & & & \\
 \cline{2-8}
-  & GraphGen  & x & & & & & \\
+  & GraphGen  & {\bf x} & & x & & & \\
 \cline{2-8}
-  & Graph 500 & x & & & & & \\
+  & Graph 500 & {\bf x} & & & & & \\
 \cline{2-8}
-  & BTER      & x & & & & & \\
+  & BTER      & {\bf x} & & & & & \\
 \cline{2-8}
-  & Darwini   & x & & & & & \\
+  & Darwini   & {\bf x} & & & & & \\
 \hline
@@
 \multirow{15}{*}{\rot{\textbf{Semantic web}}}
- & LUBM  & & x & & & & \\
+ & LUBM  & & {\bf x} & & & & \\
 \cline{2-8}
- & LBBM  & & x & & & & \\
+ & LBBM  & & {\bf x} & & & & \\
 \cline{2-8}
- & UOBM  & & x & & & & \\
+ & UOBM  & & {\bf x} & & & & \\
 \cline{2-8}
- & IIMB & & x & & & & \\
+ & IIMB & & {\bf x} & & & & \\
 \cline{2-8}
- & BSBM & & x & & & & \\
+ & BSBM & & {\bf x} & & & & \\
 \cline{2-8}
- & SP$^2$Bench & & x & & & & \\
+ & SP$^2$Bench & & {\bf x} & & & & \\
 \cline{2-8}
- & \cite{Duan:2011:AOC:1989323.1989340} & & x & & & & \\
+ & \cite{Duan:2011:AOC:1989323.1989340} & & {\bf x} & & & & \\
 \cline{2-8}
- & DBPSB & & x & & & & \\
+ & DBPSB & & {\bf x} & & & & \\
 \cline{2-8}
- & LODIB & & x & & & & \\
+ & LODIB & & {\bf x} & & & & \\
 \cline{2-8}
- & SIB & & x & & & & \\
+ & SIB & & {\bf x} & & & & \\
 \cline{2-8}
- & Geographica & & x & & & & \\
+ & Geographica & & {\bf x} & & & & \\
 \cline{2-8}
- & WatDiv & & x & & & & \\
+ & WatDiv & & {\bf x} & & & & \\
 \cline{2-8}
- & RBench & & x & & & & \\
+ & RBench & & {\bf x} & & & & \\
 \cline{2-8}
- & LDBC SPB & & x & & & & \\
+ & LDBC SPB & & {\bf x} & & & & \\
 \cline{2-8}
- & LinkGen & & x & & & & \\
+ & LinkGen & & {\bf x} & & & & \\
 \hline
@@
 \multirow{3}{*}{\rot{\textbf{GDBs}}}
-  & XGDBench & & & x & & & \\
+  & XGDBench & & & {\bf x} & x & & \\
 \cline{2-8}
-  & gMark & & & x & & & \\
+  & gMark & & x & {\bf x} & x & & \\
 \cline{2-8}
-  & graphGen & & & x & & & \\
+  & graphGen & & & {\bf x} & & & \\
 \hline
@@
 \cline{2-8}
- & \cite{Yao2011}  & & & & x & & \\
+ & \cite{Yao2011}  & & & & {\bf x} & & \\
 \cline{2-8}
- & LinkBench  & & & x & x & & \\
+ & LinkBench  & & & x & {\bf x} & & \\
 \cline{2-8}
- & S3G2  & & x & x & x & & \\
+ & S3G2  & & x & x & {\bf x} & & \\
 \cline{2-8}
- & \cite{Sukthankar-SocialInfo2014}  & & & & x & & \\
+ & \cite{Sukthankar-SocialInfo2014}  & & & & {\bf x} & & \\
 \cline{2-8}
- & LDBC SNB   & & x & x & x & & \\
+ & LDBC SNB   & & x & x & {\bf x} & & \\
 \cline{2-8}
-  & \cite{Nettleton2016}  & & & & x & & \\
+  & \cite{Nettleton2016}  & & & & {\bf x} & & \\
 \hline
@@
 \multirow{2}{*}{\rot{\textbf{An.}}}
-  & HPC Scalable Graph Analysis  & & & & & x & \\
+  & HPC Scalable Graph Analysis  & & & & & {\bf x} & \\
 \cline{2-8}
-  & Graphalytics & & & & & x & \\
+  & Graphalytics & & & & & {\bf x} & \\
 \hline
@@
 \multirow{2}{*}{\rot{\textbf{St.}}}
-  & S2Gen & & & & & & x\\
+  & S2Gen & & & & & & {\bf x}\\
 \cline{2-8}
-  & RSPLab & & & & & & x \\
+  & RSPLab & & & & & & {\bf x} \\
 %\cline{2-8}

### 2018-09-30 generators_analytics.tex
Sherif Changes
Fixed typo at analytics

@@
 
-Graph analytics, especially in the context v Big Data, is a popular area of studying interesting structural specifics of graphs, usually various types of networks.
+Graph analytics, especially in the context of Big Data, is a popular area of studying interesting structural specifics of graphs, usually various types of networks.
 Hence, the respective benchmarks and graph data generators developed for the purpose of testing graph analytics tools (such as, e.g.,  PowerGraph~\cite{Gonzalez:2012:PDG:2387880.2387883} or Parallel Graph analytiX~\cite{Sevenich:2016:UDL:3007263.3007265}) have to focus mainly on graphs with complex structures.
@@
 to avoid data locality, in the final step the vertex numbers are randomly
-permuted, and then edge tuples randomly shuffled. A related project from the same authors developed for the 9th DIMACS Shortest
+permuted, and then edge tuples are randomly shuffled. A related project from the same authors developed for the 9th DIMACS Shortest
 Paths Challenge is GTgraph~\cite{GTgraph}. It involves three types of graphs:

### 2018-10-01 comparison.tex
Updated comparison table

@@
 \multirow{6}{*}{\rot{\textbf{General}}}
-  & \cite{barabasi1999emergence} & {\bf x} & & & & & \\
+  & \cite{barabasi1999emergence} & {\bf x} & & & & x & \\
 \cline{2-8}
-   & R-MAt    & {\bf x} & & & & & \\
+   & R-MAt    & {\bf x} & & & & x & \\
 \cline{2-8}
@@
 \cline{2-8}
-  & Graph 500 & {\bf x} & & & & & \\
+  & Graph 500 & {\bf x} & & & & x & \\
 \cline{2-8}
@@
 \TODO{Extend summary.}
-For example, some social network graph generators such as the LDBC-SNB, S3G2 or
+
+For example, many general or domain-agnostic graph generators such as the
+preferential attachment, RMAT or Graph500, are typically used to test graph
+analytics framweworks when large real graphs are not available. Actually,
+Graphalytics uses RMAT as one as its graph generators for benchmarking graph
+analytics.
+
+Similarly, some social network graph generators such as the LDBC-SNB, S3G2 or
 LinkBench, can be used to test graph databases. In the case of the first two,

### 2018-10-06 comparison.tex
Minor corrections of the entries in tables

@@
 
-\TODO{Add info to all three tables.}
-
 At first we classify the generators on the basis of the respective application domains or user communities.
@@
 
-In Tables~\ref{tab:comparisonCharacteristicsA},~\ref{tab:comparisonCharacteristicsB}   we overview the key characteristics of the data generators clustered according to the respective application domains.\footnote{``GDBs'' stands for graph databases, ``SNs'' stands for social networks, ``An.'' stands for graph analytics, ``St.'' stands for graph streaming.} In particular, we show:
+In Tables~\ref{tab:comparisonCharacteristicsA},~\ref{tab:comparisonCharacteristicsB}   we overview the key characteristics of the data generators clustered according to the respective application domains.\footnote{``GDBs'' stands for graph databases, ``SNs'' stands for social networks, ``An.'' stands for graph analytics, ``St.'' stands for graph streaming.
+Value $-$ means that the information is not available or relevant.} In particular, we show:
 
@@
   \begin{itemize}
-    \item whether the generator deals only with structure, or also with \textit{properties} of the graph,
+    \item whether the generator deals only with structure, or also with \textit{properties} of the graph (Y/N feature),
     \item supported types of \textit{distributions} used for generating of the data,
     \item \textit{output format} of the produced graph, and
-    \item  whether the generator is \textit{distributed} and thus enables more efficient data generation.
+    \item  whether the generator is \textit{distributed} and thus enables more efficient data generation (Y/N feature).
   \end{itemize}
@@
 \hline   % ====================== general graphs
-\multirow{7}{*}{\rot{\textbf{General}}}
+\multirow{8}{*}{\rot{\textbf{General}}}
   & \cite{barabasi1999emergence} & fixed & & Y & N & Y &  & edge-list &  N  \\
@@
 \cline{2-10}
-  & Graph 500  & fixed & Various Domains& Y & N & Y & power-law & &  Y  \\
+  & Graph 500  & fixed & various domains & Y & N & Y & power-law & &  Y  \\
 \cline{2-10}
@@
 \cline{2-10}
- & LBBM & extracted & Lehigh University BibTeX  & N & N & Y & Monte Carlo &  RDF & N   \\
+ & LBBM & extracted & Lehigh university BibTeX  & N & N & Y & Monte Carlo &  RDF & N   \\
 \cline{2-10}
@@
 \cline{2-10}
- & LinkGen & schema-driven & user-defined & templates & Y  & N & Gaussian, Zipfian& RDF & N\\
+ & LinkGen & schema-driven & user-defined & templates & Y  & N & Gaussian, Zipfian & RDF & N\\
 \hline
@@
 \cline{2-10}
-  & gMark & schema-driven (internal schema) &  user-defined  & generated &  N  & Y & uniform, normal, zipfian &  N-triples & N    \\
+  & gMark & schema-driven (internal schema) &  user-defined  & generated &  N  & Y & uniform, normal, Zipfian &  N-triples & N    \\
 \cline{2-10}
@@
 \hline %  ======================   social networks
-\multirow{8}{*}{\rot{\textbf{SNs}}}
+\multirow{11}{*}{\rot{\textbf{SNs}}}
  & \cite{Barrett:2009:GAL:1995456.1995598} & fixed & social network & N & N & Y & simulation-driven & impl. not available &  -- \\
@@
 \multirow{2}{*}{\rot{\textbf{St.}}}
-  & S2Gen & schema-driven & Social Network & Y & N & N & user-defined & RDF & N     \\
+  & S2Gen & schema-driven & social network & Y & N & N & user-defined & RDF & N     \\
 \cline{2-10}
-  & RSPLab & schema-driven & Agnostic & Y & Y & N & user-defined & RDF & N     \\
+  & RSPLab & schema-driven & agnostic & Y & Y & N & user-defined & RDF & N     \\
 %\cline{2-10}
@@
 \multirow{7}{*}{\rot{\textbf{SNs}}}
- & \cite{Barrett:2009:GAL:1995456.1995598} & & & & x & & \\
+ & \cite{Barrett:2009:GAL:1995456.1995598} & & & & {\bf x} & & \\
 \cline{2-8}
@@
 
-\TODO{Extend summary.}
-
 For example, many general or domain-agnostic graph generators such as the
 preferential attachment, RMAT or Graph500, are typically used to test graph
-analytics framweworks when large real graphs are not available. Actually,
+analytics frameworks when large real graphs are not available. Actually,
 Graphalytics uses RMAT as one as its graph generators for benchmarking graph
@@
 
-Similarly, some social network graph generators such as the LDBC-SNB, S3G2 or
+Similarly, some social network graph generators such as LDBC-SNB, S3G2 or
 LinkBench, can be used to test graph databases. In the case of the first two,
 even though they are designed not to be specific to any type of technology,
-they graph databases are their main target.  Additionally, they also provide serializers for
+the graph databases are their main target.  Additionally, they also provide serializers for
 RDF, thus they can also be used to test RDF systems.
@@
 In the case of LinkBench, nothing prevents the user to load the generated graph
-in a graph database (Facebook uses a MySQL in that paper) to
+in a graph database (Facebook uses MySQL in that paper) to
 test a workload similar to Facebook and extend and complement it with more
-graphy queries like those in LDBC-SNB.
+graph queries like those in LDBC-SNB.
+
+\TODO{Extend summary.}

### 2018-10-06 comparison.tex
Few comments of the tables

@@
 
-As we can see ... \TODO{Add a summary.}
+As we can see, the biggest set of available generators can be found in the Semantic Web application domain, probably due to its recent popularity and a number of research groups dealing with this topic.
+On the other hand, none of these generators is natively implemented in a distributed manner, so generating of output at the Big Data scale.
+The second large group of generators also corresponds to a popular application domain -- social networks.
+In this case the size of the output graph is also critical if we require realistic features of the output.
+However, most of the proposals do not provide an implementation and, thus, this aspect cannot be discussed reliably.
+
+If we consider the particular domain of the generators, in most cases it is expectably fixed.
+However, except for general graphs, in all other cases we can find a representative with schema-driven/extracted application domain.
+In the group of generators for graph databases we can see two special cases -- graphGen ...
+\TODO{Explain schema-driven (internal schema)} and graphGen ...
+\TODO{Explain pattern-driven
+(Cypher schema)}.
+
+\TODO{Extend.}
 
@@
 
-\TODO{Extend summary.}
+\TODO{Extend.}

### 2018-10-07 comparison.tex
More comments on the tables

--- 2018-10-06 comparison.tex
@@
 In Tables~\ref{tab:comparisonCharacteristicsA},~\ref{tab:comparisonCharacteristicsB}   we overview the key characteristics of the data generators clustered according to the respective application domains.\footnote{``GDBs'' stands for graph databases, ``SNs'' stands for social networks, ``An.'' stands for graph analytics, ``St.'' stands for graph streaming.
-Value $-$ means that the information is not available or relevant.} In particular, we show:
+Value ``$-$'' means that the information is not available or relevant.} In particular, we show:
 
 \begin{itemize}
-\item Characteristics of the domain -- its \textit{type} (fixed, specified using a schema, or extracted from input data) and the particular \textit{target} domain, or, in case of a generic tool, the chosen sample domain,
-\item Characteristics of \textit{read}/\textit{update} operations (if provided), i.e., whether the set of operations is fixed/generated, if it involves operation mixes (i.e., sets/sequences of operations), or if templates of operations are supported.
-\item Key configuration options:
+\item Characteristics of the \textbf{domain} -- its \textit{type} (fixed, specified using a schema, or extracted from input data) and the particular \textit{target} domain, or, in case of a generic tool, the chosen sample domain,
+\item Characteristics of \textit{read}/\textit{update} \textbf{operations} (if provided), i.e., whether the set of operations is fixed/generated, if it involves operation mixes (i.e., sets/sequences of operations), or if templates of operations are supported.
+\item Key \textbf{configuration} options:
   \begin{itemize}
@@
 \multirow{8}{*}{\rot{\textbf{General}}}
-  & \cite{barabasi1999emergence} & fixed & & Y & N & Y &  & edge-list &  N  \\
+  & \cite{barabasi1999emergence} & -- & & Y & N & Y &  & edge-list &  N  \\
 \cline{2-10}
-   & R-MAt & fixed & & Y & N & Y & power-law & edge-list &  N  \\
+   & R-MAt & -- & & Y & N & Y & power-law & edge-list &  N  \\
 \cline{2-10}
-  & GraphGen & fixed & N & Y & N & Y&  & & N   \\
+  & GraphGen & -- & N & Y & N & Y&  & & N   \\
 \cline{2-10}
-  & Graph 500  & fixed & various domains & Y & N & Y & power-law & &  Y  \\
+  & Graph 500  & -- & various domains & Y & N & Y & power-law & &  Y  \\
 \cline{2-10}
-  & BTER & fixed & N &   N &  & N & user-defined & edge-list & Y  \\
+  & BTER & -- & N &   N &  & N & user-defined & edge-list & Y  \\
 \cline{2-10}
-  & Darwini & fixed & N &   N &  & N & user-defined &  edge-list & Y   \\
+  & Darwini & -- & N &   N &  & N & user-defined &  edge-list & Y   \\
 %  & Watts-Strogatz~\cite{watts1998collective} & fixed & & Y & N & Y &  & &  N  \\
@@
 
-As we can see ... \TODO{Add a summary.}
+\paragraph{Number of Generators, Size of the Data}
+As we can see, the biggest set of available generators can be found in the Semantic Web application domain, probably due to its recent popularity and a number of research groups dealing with this topic.
+On the other hand, none of these generators is natively implemented in a distributed manner and thus generating  output at the Big Data scale.
+Linked Open Data (LOD) are expected to be large in general, however this is the case of the whole \emph{LOD Cloud}\footnote{\url{https://lod-cloud.net/}}, but not necessarily of the particular data sets forming it.
+
+The second large group of generators also corresponds to a popular application domain -- social networks.
+In this case the size of the output graph is important if we require realistic features of the output.
+However, most of the proposals do not provide an implementation and, thus, this aspect cannot be discussed reliably.
+
+In case of the other application-specific domains the amount of generators is not that significant.
+As we will show in Section~\ref{sec:overlapping}, the situation is not that critical.
+Some of the application-specific generators can be re-used also in other application domains or the general graph generators can be used as well.
+
+\paragraph{Domain}
+
+If we consider the features of the domain of the generators, in most cases it is expectably fixed which is the simplest option and which may, however, also mean that the generator focuses on other complex aspects of the output.
+Except for general graphs without any domain, in all other cases we can find a representative with schema-driven domain or a domain extracted from sample data.
+In the group of generators for graph databases we can see two special cases -- gMark ...
+\TODO{Explain schema-driven (internal schema)} and graphGen ...
+\TODO{Explain pattern-driven
+(Cypher schema)}.
+
+The particular target (in case of fixed) or sample (in case of schema-driven or extracted) domains do not provide very rich areas.
+They either correspond to the respective application domains (like in the case of social networks), or they are based on well-known and commonly used data sets (such as, e.g., DBLP or DBpedia).
+This narrow scope can can, however, be solved by using one of the representatives with schema-driven or extracted target domains.
+
+\paragraph{Operations} 
+While the read operations are quite commonly provided, in case of updates
+
+\TODO{...}
+
+\paragraph{Configuration}
+
+\TODO{...}
 
 \subsection{Overlapping}
+\label{sec:overlapping}
 
@@
 
-\TODO{Extend summary.}
+\TODO{...}

### 2018-10-07 main.tex
last pass on my side
Added affiliation

@@
 Author's addresses:
-A. Bonifati, ...;
+A. Bonifati, Universit\'{e} Claude Bernard Lyon 1, Liris CNRS Campus La
+Doua 23-25 Avenue Pierre de Coubertin, 69622 Villerubanne, France;
 I. Holubov\'{a}, Department of Software Engineering, Faculty of Mathematics and Physics, Charles University, Malostransk\'{e} n\'{a}m. 25, 118 00 Praha~1, Czech Republic.
-A. Prat-P\'erez, ...;
-S. Sakr, ....
+  A. Prat-P\'erez, DAMA-UPC, Universitat Polit\`ecnica de Catalunya, Jordi Girona 1-3, 08034 Barcelona, Spain ;
+S. Sakr, University of Tartu,J Liivi 2, Tartu 50409, Estonia.
 \end{bottomstuff}

### 2018-10-07 comparison.tex
Sherif Changes

@@
 \multirow{8}{*}{\rot{\textbf{General}}}
-  & \cite{barabasi1999emergence} & -- & & Y & N & Y &  & edge-list &  N  \\
+  & \cite{barabasi1999emergence} & -- & N & Y & N & Y &  & edge-list &  N  \\
 \cline{2-10}
-   & R-MAt & -- & & Y & N & Y & power-law & edge-list &  N  \\
+   & R-MAt & -- & N & Y & N & Y & power-law & edge-list &  N  \\
 \cline{2-10}
-  & GraphGen & -- & N & Y & N & Y&  & & N   \\
+  & GraphGen & -- & N & Y & N & Y& user-defined  & JSON & N   \\
 \cline{2-10}
@@
 \cline{2-10}
-  & gMark & schema-driven (internal schema) &  user-defined  & generated &  N  & Y & uniform, normal, Zipfian &  N-triples & N    \\
+  & gMark & schema-driven &  user-defined  & generated &  N  & Y & uniform, normal, Zipfian &  N-triples & N    \\
 \cline{2-10}
-  & graphGen & pattern-driven (Cypher schema) & user-defined  & -- & -- & Y & -- &  property graphs & N   \\
+  & graphGen & pattern-driven & user-defined  & -- & -- & Y & -- &  property graphs & N   \\
 \hline
@@
 \cline{2-10}
-  & Graphalytics & extracted & social network & Y& N& power law & & & N   \\
+  & Graphalytics & extracted & social network & Y& N& N & power law & CSV, RDF & N   \\
 \hline

### 2018-10-07 comparison.tex
Sherif Changes

@@
 \multirow{8}{*}{\rot{\textbf{General}}}
-  & \cite{barabasi1999emergence} & -- & N & Y & N & Y &  & edge-list &  N  \\
+  & \cite{barabasi1999emergence} & -- & N & Y & N & Y & power-law & edge-list &  N  \\
 \cline{2-10}
@@
 \cline{2-10}
-  & Graph 500  & -- & various domains & Y & N & Y & power-law & &  Y  \\
+  & Graph 500  & -- & various domains & Y & N & Y & power-law & edge-list &  Y  \\
 \cline{2-10}
@@
 \multirow{3}{*}{\rot{\textbf{Ana.}}}
-  & HPC Scalable Graph Analysis & fixed & & Y & N& N& uniform & & N   \\
+  & HPC Scalable Graph Analysis & fixed & & Y & N& N& uniform &edge-list & N   \\
 \cline{2-10}

### 2018-10-07 challenges.tex
More comments of tables

@@
 \subsection{Evolving Graph Data}
+\label{sec:evolving}
 As user requirements as well as environments change, most of the existing

### 2018-10-07 comparison.tex
More comments of tables

--- 2018-10-07 comparison.tex
@@
 \cline{2-10}
- & LDBC SPB & fixed & media  & mixes & N & Y & power law, skewed values, value correlation &  RDF & N  \\
+ & LDBC SPB & fixed & media  & mixes & N & Y & power-law, skewed values, value correlation &  RDF & N  \\
 \cline{2-10}
@@
 \cline{2-10}
-  & Graphalytics & extracted & social network & Y& N& N & power law & CSV, RDF & N   \\
+  & Graphalytics & extracted & social network & Y& N& N & power-law & CSV, RDF & N   \\
 \hline
@@
 
-\paragraph{Number of Generators, Size of the Data}
+\paragraph{Number of Generators, Size and Output Format of the Data}
 As we can see, the biggest set of available generators can be found in the Semantic Web application domain, probably due to its recent popularity and a number of research groups dealing with this topic.
-On the other hand, none of these generators is natively implemented in a distributed manner and thus generating  output at the Big Data scale.
-Linked Open Data (LOD) are expected to be large in general, however this is the case of the whole \emph{LOD Cloud}\footnote{\url{https://lod-cloud.net/}}, but not necessarily of the particular data sets forming it.
+None of these generators is natively implemented in a distributed manner and thus generating  output at the Big Data scale.
+On the other hand, Linked Open Data (LOD) is expected to be large in general, however this is the case of the whole \emph{LOD Cloud}\footnote{\url{https://lod-cloud.net/}}, but not necessarily of the particular data sets forming it.
 
@@
 In this case the size of the output graph is important if we require realistic features of the output.
-However, most of the proposals do not provide an implementation and, thus, this aspect cannot be discussed reliably.
+However, most of the proposals do not provide an implementation at all and, thus, this aspect cannot be discussed reliably.
 
-In case of the other application-specific domains the amount of generators is not that significant.
-As we will show in Section~\ref{sec:overlapping}, the situation is not that critical.
-Some of the application-specific generators can be re-used also in other application domains or the general graph generators can be used as well.
+In case of the other application-specific domains the amount of generators is relatively small.
+As we will show in Section~\ref{sec:overlapping}, the situation is not so critical.
+Some of the application-specific generators can be re-used also in other application domains or the general graph generators can be used.
+
+Considering the output format of the data, most commonly the generators produce data in a standard format (e.g., RDF) or in a reasonable graph-related form (e.g., edge list).
 
@@
 
-If we consider the features of the domain of the generators, in most cases it is expectably fixed which is the simplest option and which may, however, also mean that the generator focuses on other complex aspects of the output.
-Except for general graphs without any domain, in all other cases we can find a representative with schema-driven domain or a domain extracted from sample data.
-In the group of generators for graph databases we can see two special cases -- gMark ...
-\TODO{Explain schema-driven (internal schema)} and graphGen ...
-\TODO{Explain pattern-driven
-(Cypher schema)}.
-
+If we consider the features of the particular domain of the generators, in most cases it is expectably fixed.
+It is the simplest option, but it does mean that the generator is simple too -- it can still focus on other complex aspects of the output.
 The particular target (in case of fixed) or sample (in case of schema-driven or extracted) domains do not provide very rich areas.
 They either correspond to the respective application domains (like in the case of social networks), or they are based on well-known and commonly used data sets (such as, e.g., DBLP or DBpedia).
-This narrow scope can can, however, be solved by using one of the representatives with schema-driven or extracted target domains.
+Except for general graphs without any domain, in all other cases we can find a flexible representative with schema-driven domain or a domain extracted from sample data.
+In the group of generators for graph databases we can see two special cases -- gMark ...
+and graphGen ...
+\TODO{Explain schema-driven (internal schema) and pattern-driven (Cypher schema) or unify it with other generators and remove this sentence.}.
 
 \paragraph{Operations}
-While the read operations are quite commonly provided, in case of updates
+In the case of operations, most commonty the respective generators are accompanied with a set of fixed read operations or sequences of operations representing typical behavior of a user.
+In some cases this aspect is more flexible -- either query templates are used or the operations are generated, e.g., in order to access most of the data.
+\TODO{Replace "Y" in the tables with more precise information, i.e., fixed/generated/mix(es)/templates (all groups).}
 
-\TODO{...}
+On the other hand, update operations are provided only in a small amount of cases. As we will discuss in Section~\ref{sec:evolving}, the more general problem of evolving graphs is still an open issue.
 
 \paragraph{Configuration}
-
-\TODO{...}
+A natural feature of the generators is to provide as realistic result as possible.
+Hence, most of them focus not only on the structure of the output graph, but also the properties.
+For the purpose of generating graphs with near real-world characteristics various distributions are used, such as power-law, Zipfian etc.
+Especially interesting are distributions extracted from real-wold data (such as, e.g., Facebook in case of social network domain).
 

### 2018-10-07 comparison.tex
Modifications with regards to Sherif's updates

@@
 \multirow{8}{*}{\rot{\textbf{General}}}
-  & \cite{barabasi1999emergence} & -- & N & Y & N & Y & power-law & edge-list &  N  \\
+  & \cite{barabasi1999emergence} & -- & -- & Y & N & Y & power-law & edge-list &  N  \\
 \cline{2-10}
-   & R-MAt & -- & N & Y & N & Y & power-law & edge-list &  N  \\
+   & R-MAt & -- & -- & Y & N & Y & power-law & edge-list &  N  \\
 \cline{2-10}
-  & GraphGen & -- & N & Y & N & Y& user-defined  & JSON & N   \\
+  & GraphGen & -- & -- & Y & N & Y& user-defined  & JSON & N   \\
 \cline{2-10}
@@
 \cline{2-10}
-  & BTER & -- & N &   N &  & N & user-defined & edge-list & Y  \\
+  & BTER & -- & -- &   N &  & N & user-defined & edge-list & Y  \\
 \cline{2-10}
-  & Darwini & -- & N &   N &  & N & user-defined &  edge-list & Y   \\
+  & Darwini & -- & -- &   N &  & N & user-defined &  edge-list & Y   \\
 %  & Watts-Strogatz~\cite{watts1998collective} & fixed & & Y & N & Y &  & &  N  \\
@@
 
-Considering the output format of the data, most commonly the generators produce data in a standard format (e.g., RDF) or in a reasonable graph-related form (e.g., edge list).
+Considering the output format of the data, as expected, the generators produce data in a standard format (e.g., RDF) or in a reasonable graph-related form (e.g., edge list).
 
@@
 They either correspond to the respective application domains (like in the case of social networks), or they are based on well-known and commonly used data sets (such as, e.g., DBLP or DBpedia).
-Except for general graphs without any domain, in all other cases we can find a flexible representative with schema-driven domain or a domain extracted from sample data.
-In the group of generators for graph databases we can see two special cases -- gMark ...
-and graphGen ...
-\TODO{Explain schema-driven (internal schema) and pattern-driven (Cypher schema) or unify it with other generators and remove this sentence.}.
+Except for general graphs without any domain, in all other cases we can find a flexible representative with schema-driven/pattern-driven domain or a domain extracted from sample data.
 
 \paragraph{Operations}
-In the case of operations, most commonty the respective generators are accompanied with a set of fixed read operations or sequences of operations representing typical behavior of a user.
+In the case of operations, most commonly the respective generators are accompanied with a set of fixed read operations or sequences of operations representing typical behavior of a user.
 In some cases this aspect is more flexible -- either query templates are used or the operations are generated, e.g., in order to access most of the data.
-\TODO{Replace "Y" in the tables with more precise information, i.e., fixed/generated/mix(es)/templates (all groups).}
-
-On the other hand, update operations are provided only in a small amount of cases. As we will discuss in Section~\ref{sec:evolving}, the more general problem of evolving graphs is still an open issue.
+On the other hand, update operations are provided only in a small amount of cases.
+As we will discuss in Section~\ref{sec:evolving}, the more general problem of evolving graphs is still an open issue.
 
@@
 graph queries like those in LDBC-SNB.
-
-\TODO{...}

### 2018-10-08 comparison.tex
Added missing columns to BTER and Darwini
Removed "various-domains" from graph-500
Merging of Tables I and  II

@@
 
-In Tables~\ref{tab:comparisonCharacteristicsA},~\ref{tab:comparisonCharacteristicsB}   we overview the key characteristics of the data generators clustered according to the respective application domains.\footnote{``GDBs'' stands for graph databases, ``SNs'' stands for social networks, ``An.'' stands for graph analytics, ``St.'' stands for graph streaming.
+In Table~\ref{tab:comparisonCharacteristics}   we overview the key characteristics of the data generators clustered according to the respective application domains.\footnote{``GDBs'' stands for graph databases, ``SNs'' stands for social networks, ``An.'' stands for graph analytics, ``St.'' stands for graph streaming.
 Value ``$-$'' means that the information is not available or relevant.} In particular, we show:
@@
 \item Characteristics of the \textbf{domain} -- its \textit{type} (fixed, specified using a schema, or extracted from input data) and the particular \textit{target} domain, or, in case of a generic tool, the chosen sample domain,
-\item Characteristics of \textit{read}/\textit{update} \textbf{operations} (if provided), i.e., whether the set of operations is fixed/generated, if it involves operation mixes (i.e., sets/sequences of operations), or if templates of operations are supported.
+\item Characteristics of \textit{read}/\textit{update} \textbf{operations} (columns ``Read'' and ``Upd.''), i.e., whether the set of operations is fixed/generated, if it involves operation mixes (i.e., sets/sequences of operations), or if templates of operations are supported.
 \item Key \textbf{configuration} options:
   \begin{itemize}
-    \item whether the generator deals only with structure, or also with \textit{properties} of the graph (Y/N feature),
-    \item supported types of \textit{distributions} used for generating of the data,
-    \item \textit{output format} of the produced graph, and
-    \item  whether the generator is \textit{distributed} and thus enables more efficient data generation (Y/N feature).
+    \item whether the generator deals only with structure, or also with \emph{properties} (column ``Pro.'') of the graph (Y/N feature),
+    \item supported types of \emph{distributions} (column ``Distributions'') used for generating of the data,
+    \item \textit{output format} (column ``Output'') of the produced graph, and
+    \item  whether the generator is \textit{distributed} (column ``Dis.'') and thus enables more efficient data generation (Y/N feature).
   \end{itemize}
@@
 \tbl{Key characteristics of the generators (part A)} {
-\begin{tabular}{| c | p{2.2cm} | p{2cm} |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
+\begin{tabular}{| c | p{2.9cm} | p{2cm} |  p{2.2cm} | p{1.5cm} |  l | l | p{3.3cm} | p{1.4cm} | l | }
  \hline
@@
                & \textbf{Read}
-               & \textbf{Update}
-               & \textbf{\rot{Properties}}
+               & \textbf{Upd.}
+               & \textbf{Pro.}
                & \textbf{Distributions}
 			   & \textbf{Output}
-               & \textbf{\rot{Distributed\ }}
+               & \textbf{Dis.}
                \\ \hline
@@
 \cline{2-10}
-   & R-MAt & -- & -- & Y & N & Y & power-law & edge-list &  N  \\
+   & R-Mat & -- & -- & Y & N & Y & power-law & edge-list &  N  \\
 \cline{2-10}
@@
 \cline{2-10}
-  & Graph 500  & -- & various domains & Y & N & Y & power-law & edge-list &  Y  \\
+  & Graph 500  & -- & -- & Y & N & Y & power-law & edge-list &  Y  \\
 \cline{2-10}
-  & BTER & -- & -- &   N &  & N & user-defined & edge-list & Y  \\
+  & BTER & -- & -- &   N & N & N & user-defined & edge-list & Y  \\
 \cline{2-10}
-  & Darwini & -- & -- &   N &  & N & user-defined &  edge-list & Y   \\
+  & Darwini & -- & -- &   N & N & N & user-defined &  edge-list & Y   \\
 %  & Watts-Strogatz~\cite{watts1998collective} & fixed & & Y & N & Y &  & &  N  \\
@@
 \hline
-\end{tabular} }
-\label{tab:comparisonCharacteristicsA}
-\end{sidewaystable}
-
-\begin{sidewaystable}
-\scriptsize
-\centering
-\tbl{Key characteristics of the generators (part B)} {
-\begin{tabular}{| c | p{2.2cm}| p{2cm} |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
- \hline
-           &   & \multicolumn{2}{c}{\textbf{Domain}}
-               & \multicolumn{2}{|c|}{\textbf{Operations}}
-               & \multicolumn{4}{c|}{\textbf{Configuration}}
-               \\ \hline
-           &  \textbf{Generator}
-               & \textbf{Type}
-               & \textbf{Target / sample}
-               & \textbf{Read}
-               & \textbf{Update}
-               & \textbf{\rot{Properties}}
-               & \textbf{Distributions}
-			   & \textbf{Output}
-               & \textbf{\rot{Distributed\ }}
-               \\ \hline
 \hline  % ======================  graph databases
@@
 \multirow{11}{*}{\rot{\textbf{SNs}}}
- & \cite{Barrett:2009:GAL:1995456.1995598} & fixed & social network & N & N & Y & simulation-driven & impl. not available &  -- \\
+ & \cite{Barrett:2009:GAL:1995456.1995598} & fixed & social network & N & N & Y & simulation-driven & impl. NA &  -- \\
 \cline{2-10}
- & \cite{Yao2011} & fixed & social network & N & N & N & power-law & impl. not available & --  \\
+ & \cite{Yao2011} & fixed & social network & N & N & N & power-law & impl. NA & --  \\
 \cline{2-10}
- & LinkBench & fixed & social network & Y & Y & Y & Facebook & impl. not available & -- \\
+ & LinkBench & fixed & social network & Y & Y & Y & Facebook & impl. NA & -- \\
 \cline{2-10}
@@
 \cline{2-10}
-  & \cite{Nettleton2016} & schema-driven & social network & N & N & Y & power-law & impl. not available & --  \\
+  & \cite{Nettleton2016} & schema-driven & social network & N & N & Y & power-law & impl. NA & --  \\
 %\cline{2-10}
@@
 \end{tabular} }
-\label{tab:comparisonCharacteristicsB}
+\label{tab:comparisonCharacteristics}
 \end{sidewaystable}
@@
 \cline{2-8}
-   & R-MAt    & {\bf x} & & & & x & \\
+   & R-Mat    & {\bf x} & & & & x & \\
 \cline{2-8}

### 2018-10-08 challenges.tex
Correction of references

@@
 model~\cite{mahadevan2006systematic} that outperforms the Stochastic Kronecker
-Graph Model~\cite{LeskovecCKF05} in terms of the produced structural properties,
+Graph Model~\cite{Leskovec:2005:RMT:2101235.2101254} in terms of the produced structural properties,
 eventhough the results show that there is still room for improvement.

### 2018-10-08 comparison.tex
Correction of references

@@
 \centering
-\tbl{Key characteristics of the generators (part A)} {
-\begin{tabular}{| c | p{2.9cm} | p{2cm} |  p{2.2cm} | p{1.5cm} |  l | l | p{3.3cm} | p{1.4cm} | l | }
+\tbl{Key characteristics of the generators} {
+\begin{tabular}{| c | p{3.3cm} | p{2cm} |  p{2.2cm} | p{1.3cm} |  l | l | p{3.2cm} | p{1.4cm} | l | }
  \hline
@@
 \hline   % ====================== general graphs
-\multirow{8}{*}{\rot{\textbf{General}}}
-  & \cite{barabasi1999emergence} & -- & -- & Y & N & Y & power-law & edge-list &  N  \\
+\multirow{7}{*}{\rot{\textbf{General}}}
+  & \cite{Barabasi99emergenceScaling} & -- & -- & Y & N & Y & power-law & edge-list &  N  \\
 \cline{2-10}
@@
 \hline %  ======================  Semantic web
-\multirow{20}{*}{\rot{\textbf{Semantic web}}}
+\multirow{19}{*}{\rot{\textbf{Semantic web}}}
  & LUBM & fixed & university  & fixed & N & Y & random (LCG) &  RDF & N   \\
@@
 \hline  % ======================  graph databases
-\multirow{7}{*}{\rot{\textbf{GDBs}}}
+\multirow{4}{*}{\rot{\textbf{GDBs}}}
   & XGDBench & fixed  & social network  & fixed & Y & Y & power-law &  MAG &  Y  \\
@@
 \hline %  ======================   social networks
-\multirow{11}{*}{\rot{\textbf{SNs}}}
+\multirow{7}{*}{\rot{\textbf{SNs}}}
  & \cite{Barrett:2009:GAL:1995456.1995598} & fixed & social network & N & N & Y & simulation-driven & impl. NA &  -- \\
@@
 \hline   % ======================   graph analytics
-\multirow{3}{*}{\rot{\textbf{Ana.}}}
-  & HPC Scalable Graph Analysis & fixed & & Y & N& N& uniform &edge-list & N   \\
+\multirow{2}{*}{\rot{\textbf{An.}}}
+  & HPC Scal. Graph Anal. & fixed & & Y & N& N& uniform &edge-list & N   \\
 \cline{2-10}
@@
 
-\begin{table}[h]
+\begin{table}
 \scriptsize
@@
 \multirow{6}{*}{\rot{\textbf{General}}}
-  & \cite{barabasi1999emergence} & {\bf x} & & & & x & \\
+  & \cite{Barabasi99emergenceScaling} & {\bf x} & & & & x & \\
 \cline{2-8}
@@
 \multirow{2}{*}{\rot{\textbf{An.}}}
-  & HPC Scalable Graph Analysis  & & & & & {\bf x} & \\
+  & HPC Scal. Graph Anal.  & & & & & {\bf x} & \\
 \cline{2-8}

### 2018-10-08 introduction.tex
Correction of references

@@
 the paper. The data generation of evolutionary networks is based on
-Densification Power Law (DPL) and shrinking diameters \cite{LeskovecKF05} and community-guided
-attachment properties \cite{LeskovecKF05} is then considered, along with tackling Kronecker
+Densification Power Law (DPL) and shrinking diameters and community-guided
+attachment properties \cite{Leskovec:2005:GOT:1081870.1081893} is then considered, along with tackling Kronecker
 recursion with recursive tensor multiplication \cite{AkogluMF08}.

### 2018-10-08 comparison.tex
Unification fo terminology

@@
 \begin{itemize}
-\item Characteristics of the \textbf{domain} -- its \textit{type} (fixed, specified using a schema, or extracted from input data) and the particular \textit{target} domain, or, in case of a generic tool, the chosen sample domain,
+\item Characteristics of the \textbf{domain} -- its \textit{type} (column ``Type''), i.e.,  fixed, specified using a schema, or extracted from input data and the particular \textit{target} domain, or, in case of a generic tool, the chosen sample domain (column ``Target/sample''),
 \item Characteristics of \textit{read}/\textit{update} \textbf{operations} (columns ``Read'' and ``Upd.''), i.e., whether the set of operations is fixed/generated, if it involves operation mixes (i.e., sets/sequences of operations), or if templates of operations are supported.
@@
 \cline{2-10}
-   & R-Mat & -- & -- & Y & N & Y & power-law & edge-list &  N  \\
+   & R-MAT & -- & -- & Y & N & Y & power-law & edge-list &  N  \\
 \cline{2-10}
@@
 \multirow{2}{*}{\rot{\textbf{An.}}}
-  & HPC Scal. Graph Anal. & fixed & & Y & N& N& uniform &edge-list & N   \\
+  & HPC Scal. Graph Anal. & fixed & -- & Y & N& N& uniform &edge-list & N   \\
 \cline{2-10}
@@
 As we can see, the biggest set of available generators can be found in the Semantic Web application domain, probably due to its recent popularity and a number of research groups dealing with this topic.
-None of these generators is natively implemented in a distributed manner and thus generating  output at the Big Data scale.
+None of these generators is natively implemented in a distributed manner and thus primarily generating  output at the Big Data scale.
 On the other hand, Linked Open Data (LOD) is expected to be large in general, however this is the case of the whole \emph{LOD Cloud}\footnote{\url{https://lod-cloud.net/}}, but not necessarily of the particular data sets forming it.
@@
 The second large group of generators also corresponds to a popular application domain -- social networks.
-In this case the size of the output graph is important if we require realistic features of the output.
-However, most of the proposals do not provide an implementation at all and, thus, this aspect cannot be discussed reliably.
+In this case the size of the output graph is important if we require realistic features of the result.
+However, most of the proposals do not provide an implementation at all and, thus, unfortunately this aspect cannot be discussed reliably.
 
@@
 \paragraph{Operations}
-In the case of operations, most commonly the respective generators are accompanied with a set of fixed read operations or sequences of operations representing typical behavior of a user.
-In some cases this aspect is more flexible -- either query templates are used or the operations are generated, e.g., in order to access most of the data.
+In the case of operations, most commonly the respective generators are accompanied with a set of fixed read operations or sequences of operations (query mixes) representing typical behavior of a user.
+In some cases this aspect is more flexible -- either query templates are used or the operations are generated, e.g., in order to access most of the data in the generated graph.
 On the other hand, update operations are provided only in a small amount of cases.
@@
 For the purpose of generating graphs with near real-world characteristics various distributions are used, such as power-law, Zipfian etc.
-Especially interesting are distributions extracted from real-wold data (such as, e.g., Facebook in case of social network domain).
+Especially interesting are distributions extracted from real-wold data (such as, e.g., Facebook in case of the social network domain).
 
@@
 \cline{2-8}
-   & R-Mat    & {\bf x} & & & & x & \\
+   & R-MAT    & {\bf x} & & & & x & \\
 \cline{2-8}
@@
 For example, many general or domain-agnostic graph generators such as the
-preferential attachment, RMAT or Graph500, are typically used to test graph
+preferential attachment~\cite{Barabasi99emergenceScaling}, R-MAT or Graph 500, are typically used to test graph
 analytics frameworks when large real graphs are not available. Actually,
-Graphalytics uses RMAT as one as its graph generators for benchmarking graph
+Graphalytics uses R-MAT as one as its graph generators for benchmarking graph
 analytics.

### 2018-10-08 generators_general.tex
Unification fo terminology

@@
 
-\paragraph {R-Mat} (\emph{R}ecursive \emph{Mat}rix) R-Mat is a procedural synthetic graph generator which is designed to generate power-law degree
+\paragraph {R-MAT} (\emph{R}ecursive \emph{Mat}rix) R-MAT is a procedural synthetic graph generator which is designed to generate power-law degree
 distributions~\cite{DBLP:conf/sdm/ChakrabartiZF04}.
@@
 the properties of the real graphs.
-In particular, the design goals of R-Mat is to generate graphs that match the degree distributions, imitate a community structure and have a small diameter.
-R-Mat can generate weighted, directed and bipartite graphs.
+In particular, the design goals of R-MAT is to generate graphs that match the degree distributions, imitate a community structure and have a small diameter.
+R-MAT can generate weighted, directed and bipartite graphs.
 

### 2018-10-08 comparison.tex
Cirrection of formats for GraphGen and graphGen

@@
 \tbl{Key characteristics of the generators} {
-\begin{tabular}{| c | p{3.3cm} | p{2cm} |  p{2.2cm} | p{1.3cm} |  l | l | p{3.2cm} | p{1.4cm} | l | }
+\begin{tabular}{| c | p{3.3cm} | p{2cm} |  p{2cm} | p{1.3cm} |  l | l | p{3.2cm} | p{2cm} | l | }
  \hline
@@
 \cline{2-10}
-  & GraphGen & -- & -- & Y & N & Y& user-defined  & JSON & N   \\
+  & GraphGen & -- & -- & Y & N & Y& user-defined  & node/edge-list & N   \\
 \cline{2-10}
@@
 \cline{2-10}
-  & graphGen & pattern-driven & user-defined  & -- & -- & Y & -- &  property graphs & N   \\
+  & graphGen & pattern-driven & user-defined  & -- & -- & Y & -- &  GraphJson, CypherQueries & N   \\
 \hline

### 2018-10-08 generators_general.tex
Cirrection of formats for GraphGen and graphGen

@@
 also implemented a synthetic generator called
-GraphGen~\footnote{https://www.cse.ust.hk/graphgen/}. It is
+GraphGen\footnote{https://www.cse.ust.hk/graphgen/}. It is
 based on the IBM synthetic data generation code for associations and sequential

### 2018-10-08 comparison.tex
More precise information about operations

@@
 \tbl{Key characteristics of the generators} {
-\begin{tabular}{| c | p{3.3cm} | p{2cm} |  p{2cm} | p{1.3cm} |  l | l | p{3.2cm} | p{2cm} | l | }
+\begin{tabular}{| c | p{3cm} | p{2cm} |  p{2cm} | p{1.3cm} |  l | l | p{3.2cm} | p{2cm} | l | }
  \hline
@@
 \cline{2-10}
- & \cite{Duan:2011:AOC:1989323.1989340} & extracted & -- & N & Y &N & -- &  RDF & N    \\
+ & \cite{Duan:2011:AOC:1989323.1989340} & extracted & -- & N & N & Y & -- &  RDF & N    \\
 \cline{2-10}
@@
 \cline{2-10}
- & LinkGen & schema-driven & user-defined & templates & Y  & N & Gaussian, Zipfian & RDF & N\\
+ & LinkGen & schema-driven & user-defined & templates & N  & N & Gaussian, Zipfian & RDF & N\\
 \hline
@@
 \multirow{4}{*}{\rot{\textbf{GDBs}}}
-  & XGDBench & fixed  & social network  & fixed & Y & Y & power-law &  MAG &  Y  \\
+  & XGDBench & fixed  & social network  & generated & generated & Y & power-law &  MAG &  Y  \\
 \cline{2-10}
@@
 \cline{2-10}
- & LinkBench & fixed & social network & Y & Y & Y & Facebook & impl. NA & -- \\
+ & LinkBench & fixed & social network & generated & generated & Y & Facebook & impl. NA & -- \\
 \cline{2-10}
@@
 \cline{2-10}
- & LDBC SNB  & fixed & social network &  generated & Y  & Y & Facebook &  CSV, RDF & Y     \\
+ & LDBC SNB  & fixed & social network &  generated & generated  & Y & Facebook &  CSV, RDF & Y     \\
 \cline{2-10}
@@
 \multirow{2}{*}{\rot{\textbf{An.}}}
-  & HPC Scal. Graph Anal. & fixed & -- & Y & N& N& uniform &edge-list & N   \\
+  & HPC Scal. Graph Anal. & fixed & -- & fixed & N& N& uniform &edge-list & N   \\
 \cline{2-10}
-  & Graphalytics & extracted & social network & Y& N& N & power-law & CSV, RDF & N   \\
+  & Graphalytics & extracted & social network & fixed& N& N & power-law & CSV, RDF & N   \\
 \hline

### 2018-10-15 comparison.tex
MInor correction (Arnau's comment 1)

@@
 We first provide an overview of the approaches used in related work after which we then introduce our approach.
-As mentioned in the Introduction, since this survey is unique in terms of scope and new tools related to Big Data processing, our classification and comparative strategy would differ as well.
+As mentioned in the Introduction, since this survey is unique especially in terms of scope, our classification and comparative strategy would differ as well.
 

### 2018-10-19 comparison.tex
Modification of tables (community detection)

@@
 At first we classify the generators on the basis of the respective application domains or user communities.
-In particular we distinguish (1) general graphs, (2) Semantic Web, (3) graph databases, (4) social networks, (5) graph analytics, and (6) graph data steaming.
+In particular we distinguish (1) general graphs, (2) Semantic Web, (3) graph databases, (4) social networks, (5) graph analytics, (6) community detection, and (7) graph data steaming.
 The selected classes are not rigorously defined (e.g., they are not disjoint as we will show later), but they correspond to the currently most active research areas.
@@
 
-In Table~\ref{tab:comparisonCharacteristics}   we overview the key characteristics of the data generators clustered according to the respective application domains.\footnote{``GDBs'' stands for graph databases, ``SNs'' stands for social networks, ``An.'' stands for graph analytics, ``St.'' stands for graph streaming.
+In Table~\ref{tab:comparisonCharacteristics}   we overview the key characteristics of the data generators clustered according to the respective application domains.\footnote{``GDBs'' stands for graph databases, ``SNs'' stands for social networks, ``A'' stands for graph analytics, ``Co'' stands for community detection, and ``St'' stands for graph streaming.
 Value ``$-$'' means that the information is not available or relevant.} In particular, we show:
@@
 \hline   % ====================== general graphs
-\multirow{7}{*}{\rot{\textbf{General}}}
+\multirow{6}{*}{\rot{\textbf{General}}}
   & \cite{Barabasi99emergenceScaling} & -- & -- & Y & N & Y & power-law & edge-list &  N  \\
@@
 \cline{2-10}
-  & Graph 500  & -- & -- & Y & N & Y & power-law & edge-list &  Y  \\
-\cline{2-10}
+%  & Graph 500  & -- & -- & Y & N & Y & power-law & edge-list &  Y  \\
+%\cline{2-10}
   & BTER & -- & -- &   N & N & N & user-defined & edge-list & Y  \\
@@
 \hline   % ======================   graph analytics
-\multirow{2}{*}{\rot{\textbf{An.}}}
+\multirow{1}{*}{\rot{\textbf{A}}}
   & HPC Scal. Graph Anal. & fixed & -- & fixed & N& N& uniform &edge-list & N   \\
+%\cline{2-10}
+%  & Graphalytics & extracted & social network & fixed& N& N & power-law & CSV, RDF & N   \\
+\hline
+\hline   %  ======================  community detection
+\multirow{2}{*}{\rot{\textbf{Co}}}
+  &  &  &  &  &  &  &  &  &      \\
 \cline{2-10}
-  & Graphalytics & extracted & social network & fixed& N& N & power-law & CSV, RDF & N   \\
+  &  &  & &  &  &  & &  &      \\
 \hline
 \hline   %  ======================  streaming
-\multirow{2}{*}{\rot{\textbf{St.}}}
+\multirow{2}{*}{\rot{\textbf{St}}}
   & S2Gen & schema-driven & social network & Y & N & N & user-defined & RDF & N     \\
@@
 \tbl{Overlapping of classes of generators} {
-\begin{tabular}{| c | l | l | l | l | l | l | l | }
+\begin{tabular}{| c | l | l | l | l | l | l | l | l | }
  \hline
@@
                & \textbf{\rot{Analytics}}
+               & \textbf{\rot{Community detection}}
                & \textbf{\rot{Steaming}}
@@
 \hline   % ====================== general graphs
-\multirow{6}{*}{\rot{\textbf{General}}}
-  & \cite{Barabasi99emergenceScaling} & {\bf x} & & & & x & \\
-\cline{2-8}
-   & R-MAT    & {\bf x} & & & & x & \\
-\cline{2-8}
-  & GraphGen  & {\bf x} & & x & & & \\
-\cline{2-8}
-  & Graph 500 & {\bf x} & & & & x & \\
-\cline{2-8}
-  & BTER      & {\bf x} & & & & & \\
-\cline{2-8}
-  & Darwini   & {\bf x} & & & & & \\
+\multirow{5}{*}{\rot{\textbf{General}}}
+  & \cite{Barabasi99emergenceScaling} & {\bf x} & & & & x & & \\
+\cline{2-9}
+   & R-MAT    & {\bf x} & & & & x & & \\
+\cline{2-9}
+  & GraphGen  & {\bf x} & & x & & & & \\
+\cline{2-9}
+%  & Graph 500 & {\bf x} & & & & x & & \\
+%\cline{2-9}
+  & BTER      & {\bf x} & & & & & & \\
+\cline{2-9}
+  & Darwini   & {\bf x} & & & & & & \\
 \hline
@@
 \multirow{15}{*}{\rot{\textbf{Semantic web}}}
- & LUBM  & & {\bf x} & & & & \\
-\cline{2-8}
- & LBBM  & & {\bf x} & & & & \\
-\cline{2-8}
- & UOBM  & & {\bf x} & & & & \\
-\cline{2-8}
- & IIMB & & {\bf x} & & & & \\
-\cline{2-8}
- & BSBM & & {\bf x} & & & & \\
-\cline{2-8}
- & SP$^2$Bench & & {\bf x} & & & & \\
-\cline{2-8}
- & \cite{Duan:2011:AOC:1989323.1989340} & & {\bf x} & & & & \\
-\cline{2-8}
- & DBPSB & & {\bf x} & & & & \\
-\cline{2-8}
- & LODIB & & {\bf x} & & & & \\
-\cline{2-8}
- & SIB & & {\bf x} & & & & \\
-\cline{2-8}
- & Geographica & & {\bf x} & & & & \\
-\cline{2-8}
- & WatDiv & & {\bf x} & & & & \\
-\cline{2-8}
- & RBench & & {\bf x} & & & & \\
-\cline{2-8}
- & LDBC SPB & & {\bf x} & & & & \\
-\cline{2-8}
- & LinkGen & & {\bf x} & & & & \\
+ & LUBM  & & {\bf x} & & & & & \\
+\cline{2-9}
+ & LBBM  & & {\bf x} & & & & & \\
+\cline{2-9}
+ & UOBM  & & {\bf x} & & & & & \\
+\cline{2-9}
+ & IIMB & & {\bf x} & & & & & \\
+\cline{2-9}
+ & BSBM & & {\bf x} & & & & & \\
+\cline{2-9}
+ & SP$^2$Bench & & {\bf x} & & & & & \\
+\cline{2-9}
+ & \cite{Duan:2011:AOC:1989323.1989340} & & {\bf x} & & & & & \\
+\cline{2-9}
+ & DBPSB & & {\bf x} & & & & & \\
+\cline{2-9}
+ & LODIB & & {\bf x} & & & & & \\
+\cline{2-9}
+ & SIB & & {\bf x} & & & & & \\
+\cline{2-9}
+ & Geographica & & {\bf x} & & & & & \\
+\cline{2-9}
+ & WatDiv & & {\bf x} & & & & & \\
+\cline{2-9}
+ & RBench & & {\bf x} & & & & & \\
+\cline{2-9}
+ & LDBC SPB & & {\bf x} & & & & & \\
+\cline{2-9}
+ & LinkGen & & {\bf x} & & & & & \\
 \hline
@@
 \multirow{3}{*}{\rot{\textbf{GDBs}}}
-  & XGDBench & & & {\bf x} & x & & \\
-\cline{2-8}
-  & gMark & & x & {\bf x} & x & & \\
-\cline{2-8}
-  & graphGen & & & {\bf x} & & & \\
+  & XGDBench & & & {\bf x} & x & & & \\
+\cline{2-9}
+  & gMark & & x & {\bf x} & x & & & \\
+\cline{2-9}
+  & graphGen & & & {\bf x} & & & & \\
 \hline
@@
 \multirow{7}{*}{\rot{\textbf{SNs}}}
- & \cite{Barrett:2009:GAL:1995456.1995598} & & & & {\bf x} & & \\
-\cline{2-8}
- & \cite{Yao2011}  & & & & {\bf x} & & \\
-\cline{2-8}
- & LinkBench  & & & x & {\bf x} & & \\
-\cline{2-8}
- & S3G2  & & x & x & {\bf x} & & \\
-\cline{2-8}
- & \cite{Sukthankar-SocialInfo2014}  & & & & {\bf x} & & \\
-\cline{2-8}
- & LDBC SNB   & & x & x & {\bf x} & & \\
-\cline{2-8}
-  & \cite{Nettleton2016}  & & & & {\bf x} & & \\
+ & \cite{Barrett:2009:GAL:1995456.1995598} & & & & {\bf x} & & & \\
+\cline{2-9}
+ & \cite{Yao2011}  & & & & {\bf x} & & & \\
+\cline{2-9}
+ & LinkBench  & & & x & {\bf x} & & & \\
+\cline{2-9}
+ & S3G2  & & x & x & {\bf x} & & & \\
+\cline{2-9}
+ & \cite{Sukthankar-SocialInfo2014}  & & & & {\bf x} & & & \\
+\cline{2-9}
+ & LDBC SNB   & & x & x & {\bf x} & & & \\
+\cline{2-9}
+  & \cite{Nettleton2016}  & & & & {\bf x} & & & \\
 \hline
 \hline   % ======================   graph analytics
-\multirow{2}{*}{\rot{\textbf{An.}}}
-  & HPC Scal. Graph Anal.  & & & & & {\bf x} & \\
-\cline{2-8}
-  & Graphalytics & & & & & {\bf x} & \\
+\multirow{1}{*}{\rot{\textbf{A}}}
+  & HPC Scal. Graph Anal.  & & & & & {\bf x} & & \\
+%\cline{2-9}
+%  & Graphalytics & & & & & {\bf x} & & \\
+\hline
+\hline   %  ======================  community detection
+\multirow{2}{*}{\rot{\textbf{Co}}}
+  &  & & & & & & {\bf x} &\\
+\cline{2-9}
+  &  & & & & & & {\bf x} & \\
+%\cline{2-9}
+%  & & & & & & \\
 \hline
 \hline   %  ======================  streaming
-\multirow{2}{*}{\rot{\textbf{St.}}}
-  & S2Gen & & & & & & {\bf x}\\
-\cline{2-8}
-  & RSPLab & & & & & & {\bf x} \\
-%\cline{2-8}
-%  & & & & & & \\
+\multirow{2}{*}{\rot{\textbf{St}}}
+  & S2Gen & & & & & & & {\bf x}\\
+\cline{2-9}
+  & RSPLab & & & & & & & {\bf x} \\
+%\cline{2-9}
+%  & & & & & & & \\
 \hline
@@
 
-For example, many general or domain-agnostic graph generators such as the
-preferential attachment~\cite{Barabasi99emergenceScaling}, R-MAT or Graph 500, are typically used to test graph
+For example, many general or domain-agnostic graph generators, such as the
+preferential attachment~\cite{Barabasi99emergenceScaling} or R-MAT, are typically used to test graph
 analytics frameworks when large real graphs are not available. Actually,

### 2018-10-19 generators_streaming.tex
Modification of tables (community detection)
Section Streaming refactoring

@@
-\subsubsection{Graph Data Streaming}
+\subsection{Graph Data Streaming}
 \label{sec:generators_streaming}
@@
 In this mode, the graph processing algorithms can process the input stream in the order it arrives while using only a limited amount of memory~\cite{mcgregor2014graph}.
-The streaming mode has mainly  attracted the attention of the RDF and Semantic Web community.
+
+\paragraph{S2Gen}  The streaming mode has mainly  attracted the attention of the RDF and Semantic Web community.
 Thus, Phuoc et al.~\cite{le2012linked} presented an evaluation framework for linked stream data processing engines.
@@
 
-Tommasini et al.~\cite{tommasini2017rsplab} introduced another framework for benchmarking RDF Stream Processing systems, RSPLab.
+\paragraph{RSPLab} Tommasini et al.~\cite{tommasini2017rsplab} introduced another framework for benchmarking RDF Stream Processing systems, RSPLab.
 The Streamer component of this framework is designed to publish RDF streams from the various existing RDF benchmarks (e.g., BSBM, LUBM) (see Section~\ref{sec:generators_LinkedData}).

### 2018-10-19 generators_LinkedData.tex
Graphalytics and Graph 500 corrections

@@
 Two workloads are provided: (1) basic, involving an interactive query-mix querying the relations between entities in reference data, and (2) advanced,  consisting of interactive and analytical query-mixes.
-The LDBC has designed two other benchmarks: the Social Network Benchmark (SNB)~\cite{Erling:2015:LSN:2723372.2742786} for the social network domain  (see Section~\ref{sec:generators_socialnetworks}) and Graphalytics~\cite{Iosup:2016:LGB:3007263.3007270}   for the analytics domain (see Section~\ref{sec:generators_analytics}).
+The LDBC has designed two other benchmarks: the Social Network Benchmark (SNB)~\cite{Erling:2015:LSN:2723372.2742786} for the social network domain  (see Section~\ref{sec:generators_socialnetworks}) and Graphalytics~\cite{Iosup:2016:LGB:3007263.3007270}   for the analytics domain.% (see Section~\ref{sec:generators_analytics}).
 

### 2018-10-19 generators_analytics.tex
Graphalytics and Graph 500 corrections

@@
 
-\paragraph{Graphalytics} Graphalytics\footnote{\url{http://graphalytics.ewi.tudelft.nl/}} is an industrial-grade benchmark for graph analysis platforms~\cite{Iosup:2016:LGB:3007263.3007270}.
-It involves 6 real-world datasets and 2 synthetic datasets generated so that they cover two commonly used types of graphs: social network graphs generated using LDBC SNB graph generator (see Section~\ref{sec:generators_socialnetworks}) and power-law graphs generated by Graph500 (see Section~\ref{sec:generators_general}).
-The benchmark workload consists of 6 deterministic algorithms: breadth-first search, PageRank, weakly connected components, community detection using label propagation, local clustering coefficient, and single-source shortest paths.
+%\paragraph{Graphalytics} Graphalytics\footnote{\url{http://graphalytics.ewi.tudelft.nl/}} is an industrial-grade benchmark for graph analysis platforms~\cite{Iosup:2016:LGB:3007263.3007270}.
+It involves 6 real-world datasets and 2 synthetic datasets generated so that they cover two commonly used types of graphs: social network graphs generated using LDBC SNB graph generator (see Section~\ref{sec:generators_socialnetworks}) and power-law graphs generated by the Graph 500 benchmark~\cite{Graph500}.\footnote{Hence, we do not involve it in Table~\ref{tab:comparisonCharacteristics}, because it does not bring any new generator.} The benchmark workload consists of 6 deterministic algorithms: breadth-first search, PageRank, weakly connected components, community detection using label propagation, local clustering coefficient, and single-source shortest paths.
 The benchmark uses various metrics to measure the performance and throughput for systems under test such as \emph{upload time} that measures the required time to preprocess and convert the graph into a suitable format for a graph processing system, or \emph{Makespan} that measures the total  execution time of a benchmarking workload algorithm.

### 2018-10-19 generators_general.tex
Graphalytics and Graph 500 corrections

@@
 
-\paragraph {R-MAT} (\emph{R}ecursive \emph{Mat}rix) R-MAT is a procedural synthetic graph generator which is designed to generate power-law degree
+\paragraph {R-MAT} R-MAT (\emph{R}ecursive \emph{Mat}rix) is a procedural synthetic graph generator which is designed to generate power-law degree
 distributions~\cite{DBLP:conf/sdm/ChakrabartiZF04}.
@@
 
-\paragraph{Graph 500 Benchmark} The Graph 500 Benchmark~\cite{Graph500} includes
-a scalable data generator which produces weighted, undirected graph as a list of
-edge tuples containing the label of start vertex and end vertex together with a
-weight that represents data assigned to the edge. The space of vertex  labels is
-the set of integers beginning with 0. The input values required to describe the
-graph are (1) scale, i.e., the logarithm base two of the number of vertices, and
-(2) edge factor, i.e., the ratio of the graph's edge count to its vertex count
-(i.e., half the average degree of a vertex in the graph). The graph generator is
-a Kronecker generator similar to R-MAT. The data must not exhibit any locality,
-so in the final step the vertex labels and order of edges are randomly shuffled.
-The covered operations currently involve BFS; however, the authors intend to
-involve also two more types -- optimization (single source shortest path) and
-edge-oriented (maximal independent set) -- and five graph-related business areas:
-cybersecurity, medical informatics, data enrichment, social networks, and
-symbolic networks.
+%\paragraph{Graph 500 Benchmark} The Graph 500 Benchmark~\cite{Graph500} includes
+%a scalable data generator which produces weighted, undirected graph as a list of
+%edge tuples containing the label of start vertex and end vertex together with a
+%weight that represents data assigned to the edge. The space of vertex  labels is
+%the set of integers beginning with 0. The input values required to describe the
+%graph are (1) scale, i.e., the logarithm base two of the number of vertices, and
+%(2) edge factor, i.e., the ratio of the graph's edge count to its vertex count
+%(i.e., half the average degree of a vertex in the graph). The graph generator is
+%a Kronecker generator similar to R-MAT. The data must not exhibit any locality,
+%so in the final step the vertex labels and order of edges are randomly shuffled.
+%The covered operations currently involve BFS; however, the authors intend to
+%involve also two more types -- optimization (single source shortest path) and
+%edge-oriented (maximal independent set) -- and five graph-related business areas:
+%cybersecurity, medical informatics, data enrichment, social networks, and
+%symbolic networks.
 

### 2018-10-19 comparison.tex
Graphalytics and Graph 500 corrections
Minor correction

@@
 \tbl{Key characteristics of the generators} {
-\begin{tabular}{| c | p{3cm} | p{2cm} |  p{2cm} | p{1.3cm} |  l | l | p{3.2cm} | p{2cm} | l | }
+\begin{tabular}{| c | l | p{2cm} |  p{2cm} | p{1.3cm} |  l | l | p{3.2cm} | p{2cm} | l | }
  \hline
@@
 \hline   % ====================== general graphs
-\multirow{6}{*}{\rot{\textbf{General}}}
-  & \cite{Barabasi99emergenceScaling} & -- & -- & Y & N & Y & power-law & edge-list &  N  \\
+\multirow{5}{*}{\rot{\textbf{General}}}
+  & Preferential attachment & -- & -- & Y & N & Y & power-law & edge-list &  N  \\
 \cline{2-10}
@@
 \hline   %  ======================  community detection
-\multirow{2}{*}{\rot{\textbf{Co}}}
+\multirow{3}{*}{\rot{\textbf{Co}}}
+  &  &  &  &  &  &  &  &  &      \\
+\cline{2-10}
   &  &  & &  &  &  & &  &      \\
@@
 \multirow{5}{*}{\rot{\textbf{General}}}
-  & \cite{Barabasi99emergenceScaling} & {\bf x} & & & & x & & \\
+  & Preferential attachment & {\bf x} & & & & x & & \\
 \cline{2-9}
@@
 \hline   %  ======================  community detection
-\multirow{2}{*}{\rot{\textbf{Co}}}
+\multirow{3}{*}{\rot{\textbf{Co}}}
   &  & & & & & & {\bf x} &\\
+\cline{2-9}
+  &  & & & & & & {\bf x} & \\
 \cline{2-9}
@@
 For example, many general or domain-agnostic graph generators, such as the
-preferential attachment~\cite{Barabasi99emergenceScaling} or R-MAT, are typically used to test graph
-analytics frameworks when large real graphs are not available. Actually,
-Graphalytics uses R-MAT as one as its graph generators for benchmarking graph
-analytics.
+preferential attachment~\cite{Barabasi99emergenceScaling} or R-MAT, are typically used to test graph analytics frameworks when large real graphs are not available.
+%Actually, Graphalytics uses R-MAT as one as its graph generators for benchmarking graph analytics.
 

### 2018-10-20 comparison.tex
Shrinking of the table
refactored community detection

@@
                & \textbf{Type}
-               & \textbf{Target / sample}
+               & \textbf{Target/sample}
                & \textbf{Read}
@@
 \multirow{3}{*}{\rot{\textbf{Co}}}
-  &  &  &  &  &  &  &  &  &      \\
+  & Danon et al. & -- & -- & Y & N & N & uniform & edge-list &  N    \\
 \cline{2-10}
-  &  &  & &  &  &  & &  &      \\
+  & LFR & -- & -- & Y & N & N & power-law & edge-list  & N      \\
 \cline{2-10}
-  &  &  & &  &  &  & &  &      \\
+  & LFR-Overlapping & -- & -- & Y & N & N & power-law & edge-list & N     \\
 \hline
@@
 \multirow{3}{*}{\rot{\textbf{Co}}}
-  &  & & & & & & {\bf x} &\\
+  & Danon et al. & x & & & & x & {\bf x} &\\
 \cline{2-9}
-  &  & & & & & & {\bf x} & \\
+  & LFR & x & & & & x & {\bf x} & \\
 \cline{2-9}
-  &  & & & & & & {\bf x} & \\
+  & LFR-Overlapping & x & & & & x & {\bf x} & \\
 %\cline{2-9}
@@
 graph queries like those in LDBC-SNB.
+
+Generators for community detection aim, in general, at creating graphs with a
+more realistic strcture (graphs with communities of nodes where the density of
+edges is larger internally than externally). Even though these generators are,
+in general used to test community detection algorithms (they generate also the
+expected communities in the graph), some studies also use them for general graph
+purposes or to test graph analytics algorithms besides community detection.

### 2018-10-20 generators_community_detection.tex
Modification of tables (community detection)
refactored community detection

@@
-\subsubsection{Community Detection}
+\subsection{Community Detection}
 \label{sec:generators_community_detection}
 
-Community detection is one of the many graph analytics algorithms typically used on domains such as social networks or bioinformatics.
-Communities are groups of vertices that are highly connected among them, while being scarcely connected to the rest of the graph.
-Such communities emerge from the fact that real graphs are not random, but follow real-world dynamics that make similar entities to have a larger probability to be connected.
-As a consequence, detected communities are used to reveal vertices with similar characteristics, for instance to discover functionally equivalent proteins in protein-protein interaction networks, or persons with similar interests in social networks.
-Such applications have made community detection a hot topic during the last fifteen years with tens of developed algorithms and detection strategies~\cite{doi:10.1002/wics.1403,Kim:2015:CDM:2854006.2854013}.
-In order to compare the quality of the different proposed techniques, one needs graphs with \emph{reference communities}, that is, communities known beforehand.
-Since it is very difficult to have large real graphs with reference communities (mainly because these would require a manual labeling), graphs for benchmarking community detection algorithms are typically generated synthetically.
+Community detection is one of the many graph analytics algorithms typically used
+on domains such as social networks or bioinformatics. Communities are groups of
+vertices that are highly connected among them, while being scarcely connected to
+the rest of the graph. Such communities emerge from the fact that real graphs
+are not random, but follow real-world dynamics that make similar entities to
+have a larger probability to be connected. As a consequence, detected
+communities are used to reveal vertices with similar characteristics, for
+instance to discover functionally equivalent proteins in protein-protein
+interaction networks, or persons with similar interests in social networks. Such
+applications have made community detection a hot topic during the last fifteen
+years with tens of developed algorithms and detection
+strategies~\cite{doi:10.1002/wics.1403,Kim:2015:CDM:2854006.2854013}. In order
+to compare the quality of the different proposed techniques, one needs graphs
+with \emph{reference communities}, that is, communities known beforehand. Since
+it is very difficult to have large real graphs with reference communities
+(mainly because these would require a manual labeling), graphs for benchmarking
+community detection algorithms are typically generated synthetically.
 
-The first attempts to compare community detection algorithms using synthetic graphs proposed the use of random graphs composed by several Erd\"{o}s-R\'{e}nyi subgraphs, connected more internally than externally~\cite{danon2005comparing}.
-Each of these subgraphs has the same size and the same internal/external density of edges.
-However, such graphs miss the realism observed in real graphs, where communities are of different sizes and densities.
-Thus, Lancichinetti, Fortunato and Radicchi (hence LFR)~\cite{PhysRevE.78.046110} propose a class of benchmark graphs for community detection where communities are of different sizes and densities.
-The generator generates communities of different sizes following a power-law distribution whose parameters can be configured.
-The degree of the nodes is also sampled from a power-law distribution.
-Additionally, the generator introduces the concept of the ``mixing factor'', which specifies the fraction of its links connecting nodes belonging to different communities.
-Such parameter allows  the degree of modularity of the generated graph  to be tuned, thus testing the robustness of the algorithms under different conditions.
-The generation process starts with an empty graph and incrementally fills in the adjacency matrix by obeying the described constraints.
-Lancichinetti, Fortunato and Radicchi~\cite{PhysRevE.80.016118} extended LFR to support the notion of directed graphs and overlapping communities.
-Overlapping communities extend the notion of communities by allowing the sharing of vertices, thus a vertex can belong to more than one community.
-This extended generator allows controlling the same parameters of the previous version, but also the amount of overlap of the generated communities.
+\paragraph{Danon et al.} The first attempts to compare community detection algorithms using synthetic
+graphs proposed the use of random graphs composed by several Erd\"{o}s-R\'{e}nyi
+subgraphs, connected more internally than externally~\cite{danon2005comparing}.
+Each of these subgraphs has the same size and the same internal/external density
+of edges. However, such graphs miss the realism observed in real graphs, where
+communities are of different sizes and densities, thus several proposals exist
+to overcome such an issue.
 
-Besides synthetic graph generators, Yang and Leskovec~\cite{yang2015defining} proposed the use of real-world graphs with explicit group annotations (e.g., forums in a social network, categories of products, etc.) to infer what they call ``meta-communities'', and use them to evaluate overlapping community detection algorithms.
-However, a recent study from Hric, Darst and Fortunato~\cite{hric2014community} reveal a loose correspondence between  communities (the authors refer to them as structural communities) and meta-communities.
-This result reveals that  algorithms working for structural communities do not work well for finding meta-communities and vice versa, suggesting significantly different underlying characteristics between the two types of communities, which are yet to be identified.
+\paragraph{LFR} Lancichinetti, Fortunato
+and Radicchi (hence LFR)~\cite{PhysRevE.78.046110} propose a class of benchmark
+graphs for community detection where communities are of different sizes and
+densities. The generator generates communities of different sizes following a
+power-law distribution whose parameters can be configured. The degree of the
+nodes is also sampled from a power-law distribution. Additionally, the generator
+introduces the concept of the ``mixing factor'', which specifies the fraction of
+its links connecting nodes belonging to different communities. Such parameter
+allows  the degree of modularity of the generated graph  to be tuned, thus
+testing the robustness of the algorithms under different conditions. The
+generation process starts with an empty graph and incrementally fills in the
+adjacency matrix by obeying the described constraints.
 
-In this regard and to the best of our knowledge, there does not exist a set of generators to generate graphs with meta-communities for community detection algorithm benchmarking.
-The closest one is the LDBC-SNB data generator~\cite{Erling:2015:LSN:2723372.2742786} which has been provided by the generation of groups of users in the social network.
-Even though the generation process does not specifically enforce the generation of groups (meta-communities) for benchmarking community detection algorithms, the study from Prat-Pe\'rez and Dominguez-Sal reveals that these groups are more similar to the real meta-communities than those structural communities generated by the LFR benchmark~\cite{Prat-Perez:2014:CSS:2621934.2621942}.
+\paragraph{LFR-Overlapping} Lancichinetti, Fortunato and
+Radicchi~\cite{PhysRevE.80.016118} extended LFR to support the notion of
+directed graphs and overlapping communities. Overlapping communities extend the
+notion of communities by allowing the sharing of vertices, thus a vertex can
+belong to more than one community. This extended generator allows controlling
+the same parameters of LFR, as well as the amount of overlap of
+the generated communities.
 
-The differences observed between structural and meta-communities reveal the need of more accurate community definitions tight more specifically to the domain or use case.
-Current community detection algorithms and graph generators for community detection are stuck to the traditional (and vague) definition of community, assuming that there exists a single algorithm that would fit all the use cases.
-Thus, future work requires the study of domain-specific community characteristics that can be used to generate graphs with a community structure that accurately resembles that of specific use cases, and thus revealing which are the best algorithms for each particular scenario.
+Besides synthetic graph generators, Yang and Leskovec~\cite{yang2015defining}
+proposed the use of real-world graphs with explicit group annotations (e.g.,
+forums in a social network, categories of products, etc.) to infer what they
+call ``meta-communities'', and use them to evaluate overlapping community
+detection algorithms. However, a recent study from Hric, Darst and
+Fortunato~\cite{hric2014community} reveal a loose correspondence between
+communities (the authors refer to them as structural communities) and
+meta-communities.  This result reveals that  algorithms working for structural
+communities do not work well for finding meta-communities and vice versa,
+suggesting significantly different underlying characteristics
+between the two types of communities, which are yet to be
+identified.
+
+In this regard and to the best of our knowledge, there does not exist a set of
+generators to generate graphs with meta-communities for community detection
+algorithm benchmarking. The closest one is the LDBC-SNB data
+generator~\cite{Erling:2015:LSN:2723372.2742786} which has been provided by the
+generation of groups of users in the social network. Even though the generation
+process does not specifically enforce the generation of groups
+(meta-communities) for benchmarking community detection algorithms, the study
+from Prat-Pe\'rez and Dominguez-Sal reveals that these groups are more similar
+to the real meta-communities than those structural communities generated by the
+LFR benchmark~\cite{Prat-Perez:2014:CSS:2621934.2621942}.
+
+The differences observed between structural and meta-communities reveal the need
+of more accurate community definitions tight more specifically to the domain or
+use case. Current community detection algorithms and graph generators for
+community detection are stuck to the traditional (and vague) definition of
+community, assuming that there exists a single algorithm that would fit all the
+use cases. Thus, future work requires the study of domain-specific community
+characteristics that can be used to generate graphs with a community structure
+that accurately resembles that of specific use cases, and thus revealing which
+are the best algorithms for each particular scenario.

### 2018-10-20 challenges.tex
Minor corrections

--- 2018-10-07 challenges.tex
@@
 provided with sample graph data and is capable of automatic analysis of its
-structural and value features in order to learn the complex parameters.
+structural and value features in order to learn the complex parameters. We could see this type approach in some cases, such as Semantic Web generators LBBM or DBPSB.
 
@@
 Most of existing graph generators are focused on generating large graphs with realistic
-structural characteristics focus principally on reproducing the degree
+structural characteristics and focus principally on reproducing the degree
 distribution and the clustering
@@
 Most of existing graph generators also generate graphs that are either not labeled or
-are specific to a given domain (e.g.  Social Networks). Graphs from different
+are specific to a given domain (e.g.  social networks). Graphs from different
 domains have different schemas, structural characteristics, property
@@
 application under test. Thus, graph processing engine developers are asking for
-generators or tools to flexibly and holistically generate multi-domain graphs  in a flexible and holistic manner, allowing to configure aspects
+generators or tools to generate multi-domain graphs  in a flexible and holistic manner, allowing to configure aspects
 such as size, schemata, data distributions and other structural
@@
 
-Concerning the former, analyzing and labelling structural networks is
+Concerning the former, analyzing and labeling structural networks is
 deemed to be more difficult for graph datasets in the presence of noise.
-Since denoising graph data is difficult to achieve, several machine learning
+Since de-noising graph data is difficult to achieve, several machine learning
 techniques have been adapted to work with noise (i.e. mislabeled
@@
 sensor pervasiveness and emerging IoT applications.
-These applications generate the data with high Velocity, one of the main 3V characteristics of big data applications~\cite{sakr2016big}.
+These applications generate the data with high Velocity, one of the main 3V characteristics of Big Data applications~\cite{sakr2016big}.
 In most of these high speed data generation scenarios, various objects are connected together with different relations and data exchanges  in a graph-structured manner.
@@
 In the world of graph data such graphs that change with time are denoted as \emph{evolving}, \emph{temporal}, \emph{dynamic}, or \emph{time-varying}.
-They can be modelled as labeled graphs, where the labels capture some measure of time~\cite{Michail2015}.
+They can be modeled as labeled graphs, where the labels capture some measure of time~\cite{Michail2015}.
 
@@
 \subsection{Multi-model Data}
-With the dawn of Big Data and especially its variety aspect, new types of
+With the dawn of Big Data and especially its Variety, another key 3V characteristic, new types of
 database management systems have emerged. One of the most interesting ones
@@
 to test new features and analyze efficiency of operations. However, since the
-multi-model systems are in the context of Big Data are rather new, there exist only
+multi-model systems are in the context of Big Data rather new, there exist only
 a few benchmarks targeting multi-model DBMSs (such as
@@
 model~\cite{mahadevan2006systematic} that outperforms the Stochastic Kronecker
-Graph Model~\cite{LeskovecCKF05} in terms of the produced structural properties,
-eventhough the results show that there is still room for improvement.
+Graph Model~\cite{Leskovec:2005:RMT:2101235.2101254} in terms of the produced structural properties,
+even though the results show that there is still room for improvement.
 
 Following this line of research, recent work~\cite{qin2017generating} extends the notion of differential privacy
-and propose an `` edge local differential privacy'' based graph generation
-method. The poposed method allows generating privacy preserving synthetic social
-graphs wihtout the need of a centralized data curator, while preserving structural
+and propose an ``edge local differential privacy'' based graph generation
+method. The proposed method allows generating privacy preserving synthetic social
+graphs without the need of a centralized data curator, while preserving structural
 properties more accurately than straw-hat methods such as Randomized
@@
 Degree-based Graph Generation (which perturbates the original graph degrees
-using the Laplace mechanism~\cite{dwork2009differential}). Again, eventhough the
+using the Laplace mechanism~\cite{dwork2009differential}). Again, even though the
 proposed technique outperforms the baselines, the results show that there is

### 2018-10-20 conclusion.tex
Minor corrections

@@
 Graphs form one of the most complex data structures requiring specific and usually sophisticated approaches for processing and analysis.
-The history of graph theory,  that started from when these structures and their respective algorithms were studied can be traced back to the 18th century.
+The history of graph theory,  that started from when these structures and their respective algorithms were studied, can be traced back to the 18th century.
 

### 2018-10-20 introduction.tex
Minor corrections

@@
 areas of graph data processing. In particular, we consider graph generation
-in the areas of graph databases, graph data mining, graph streaming and
-machine learning communities, alongside community detection, social
-networks and IoT communities.
+in the areas of graph databases, Semantic Web, social networks, graph streaming, alongside community detection  and graph data analytics.
 Despite the disparate requirements of modern graph generators throughout these communities, we analyze them under a common umbrella, reaching out the functionalities, the practical usage, and the supported operations of graph generators.
@@
 Hence, while practitioners can find a solution in another previously unexpected area, researchers can identify new target areas or exploit successful results in new fields.
-Last but not least, we identify general open problems of graph data synthesis and indicate possible solutions to show that it still forms a challenging and promising research area.
+Last but not least, to provide a global view of the state-of-the-art, we also provide an overview of most commonly used real-world testing graph data sets.
+And, finally, we identify general open problems of graph data synthesis and indicate possible solutions to show that it still forms a challenging and promising research area.
 
@@
 landscape of graph data generators spanning different data-intensive applications and
-targeting many computer science subfields. In particular, we cover graph database
-generators, graph processing generators, social networks and community detection
-generators, Semantic Web data generators, graph
-analytics generators, IoT, Telecommunication and graph streaming generators,
-and Machine Learning and graph mining generators. However, the literature is still lacking a comprehensive study of
-graph generators  for many of the specific subfields mentioned above.
+targeting many computer science subfields.
+In particular, we cover graph databases, Semantic Web, social networks, graph streaming, community detection, and graph data analytics.
+However, the literature is still lacking a comprehensive study of graph generators  for many of the specific subfields mentioned above.
 
@@
 We also point out that this survey is outdated as it does not consider the
-graph mining generators that fervently appeared in the last decade.
+generators that appeared in the last decade.
 We fill the gap of more recent social network and graph analytics generators

### 2018-10-20 main.tex
Unification fo terminology
Graphalytics and Graph 500 corrections
Minor corrections

@@
 \acmArticle{0}
-\acmYear{2016}
+\acmYear{2018}
 \acmMonth{0}
@@
 and applications manipulating these data. We consider graph generation
-across multiple subfields, such as graph databases, graph data mining,
-graph streaming and machine learning communities, alongside community
-detection, social networks and IoT communities. Despite the disparate
+across multiple subfields, such as graph databases, Semantic Web, social networks, graph streaming, alongside community detection  and graph data analytics. Despite the disparate
 requirements of modern graph generators throughout these communities, we
@@
 
-\keywords{Big Data management, graph data, generators, benchmarks, synthetic data, ...}
+\keywords{Big Data management, graph data, generators, benchmarks, synthetic data}
 
@@
 \begin{bottomstuff}
-This work is supported by ...
-
+%This work is supported by ...
 Author's addresses:
@@
 Doua 23-25 Avenue Pierre de Coubertin, 69622 Villerubanne, France;
-I. Holubov\'{a}, Department of Software Engineering, Faculty of Mathematics and Physics, Charles University, Malostransk\'{e} n\'{a}m. 25, 118 00 Praha~1, Czech Republic.
-  A. Prat-P\'erez, DAMA-UPC, Universitat Polit\`ecnica de Catalunya, Jordi Girona 1-3, 08034 Barcelona, Spain ;
-S. Sakr, University of Tartu,J Liivi 2, Tartu 50409, Estonia.
+I. Holubov\'{a}, Department of Software Engineering, Faculty of Mathematics and Physics, Charles University, Malostransk\'{e} n\'{a}m. 25, 118 00 Praha~1, Czech Republic;
+A. Prat-P\'erez, DAMA-UPC, Universitat Polit\`ecnica de Catalunya, Jordi Girona 1-3, 08034 Barcelona, Spain;
+S. Sakr, University of Tartu, J Liivi 2, Tartu 50409, Estonia.
 \end{bottomstuff}
@@
 % History dates
-\received{August 2016}{September 2016}{December 2016}
+\received{October 2018}{October 2018}{October 2018}
 

### 2018-10-20 comparison.tex
Minor corrections

@@
 We first provide an overview of the approaches used in related work after which we then introduce our approach.
-As mentioned in the Introduction, since this survey is unique especially in terms of scope, our classification and comparative strategy would differ as well.
+As mentioned in the Introduction, since this survey is unique especially in terms of scope, our classification and comparative strategy differs as well.
 
@@
 \item Characteristics of the \textbf{domain} -- its \textit{type} (column ``Type''), i.e.,  fixed, specified using a schema, or extracted from input data and the particular \textit{target} domain, or, in case of a generic tool, the chosen sample domain (column ``Target/sample''),
-\item Characteristics of \textit{read}/\textit{update} \textbf{operations} (columns ``Read'' and ``Upd.''), i.e., whether the set of operations is fixed/generated, if it involves operation mixes (i.e., sets/sequences of operations), or if templates of operations are supported.
+\item Characteristics of \textit{read}/\textit{update} \textbf{operations} (columns ``Read'' and ``Update''), i.e., whether the set of operations is fixed/generated, if it involves operation mixes (i.e., sets/sequences of operations), or if templates of operations are supported.
 \item Key \textbf{configuration} options:
@@
                & \textbf{Read}
-               & \textbf{Upd.}
+               & \textbf{Update}
                & \textbf{Pro.}
@@
 \multirow{5}{*}{\rot{\textbf{General}}}
-  & Preferential attachment & -- & -- & Y & N & Y & power-law & edge-list &  N  \\
+  & Preferential attachment & -- & -- & N & N & Y & power-law & edge-list &  N  \\
 \cline{2-10}
-   & R-MAT & -- & -- & Y & N & Y & power-law & edge-list &  N  \\
+   & R-MAT & -- & -- & N & N & Y & power-law & edge-list &  N  \\
 \cline{2-10}
-  & GraphGen & -- & -- & Y & N & Y& user-defined  & node/edge-list & N   \\
+  & GraphGen & -- & -- & N & N & Y& user-defined  & node/edge-list & N   \\
 \cline{2-10}
@@
 None of these generators is natively implemented in a distributed manner and thus primarily generating  output at the Big Data scale.
-On the other hand, Linked Open Data (LOD) is expected to be large in general, however this is the case of the whole \emph{LOD Cloud}\footnote{\url{https://lod-cloud.net/}}, but not necessarily of the particular data sets forming it.
+On the other hand, the \emph{Linked Open Data} (LOD) is expected to be large in general, however this is the case of the whole \emph{LOD Cloud}\footnote{\url{https://lod-cloud.net/}}, but not necessarily of the particular data sets forming it.
 
@@
 The particular target (in case of fixed) or sample (in case of schema-driven or extracted) domains do not provide very rich areas.
-They either correspond to the respective application domains (like in the case of social networks), or they are based on well-known and commonly used data sets (such as, e.g., DBLP or DBpedia).
+They either correspond to the respective application domains (like in the case of social networks), or they are based on well-known and commonly used data sets (such as, e.g., DBLP~\cite{dblp} or DBpedia~\cite{Bizer:2009:DCP:1640541.1640848}).
 Except for general graphs without any domain, in all other cases we can find a flexible representative with schema-driven/pattern-driven domain or a domain extracted from sample data.
@@
 Generators for community detection aim, in general, at creating graphs with a
-more realistic strcture (graphs with communities of nodes where the density of
+more realistic structure (graphs with communities of nodes where the density of
 edges is larger internally than externally). Even though these generators are,
-in general used to test community detection algorithms (they generate also the
+in general, used to test community detection algorithms (they generate also the
 expected communities in the graph), some studies also use them for general graph

### 2018-10-20 generators_LinkedData.tex
Minor corrections

@@
 
-\paragraph{SP$^2$Bench} The SP$^2$Bench\footnote{\url{http://dbis.informatik.uni-freiburg.de/forschung/projekte/SP2B/}} is a language-specific benchmark~\cite{Schmidt2010} which uses the DBLP~\cite{dblp} as a domain for the dataset.
+\paragraph{SP$^2$Bench} The SP$^2$Bench\footnote{\url{http://dbis.informatik.uni-freiburg.de/forschung/projekte/SP2B/}} is a language-specific benchmark~\cite{Schmidt2010} which uses the DBLP as a domain for the dataset.
 %, so the types involve Person, Inproceedings, Article etc.
@@
 
-\paragraph{Data Coherence}  A comparison of 4 RDF benchmarks (namely TPC-H~\cite{TPC-H} data expressed in RDF, LUBM, BSBM, and SP$^2$Bench) and 6 real-wold data sets (such as, e.g.,  DBpedia~\cite{Bizer:2009:DCP:1640541.1640848}, the Barton Libraries Dataset~\cite{barton-benchmark} or
+\paragraph{Data Coherence}  A comparison of 4 RDF benchmarks (namely TPC-H~\cite{TPC-H} data expressed in RDF, LUBM, BSBM, and SP$^2$Bench) and 6 real-wold data sets (such as, e.g.,  DBpedia, the Barton Libraries Dataset~\cite{barton-benchmark} or
 WordNet~\cite{Miller:1995:WLD:219717.219748}) has been reported by~\cite{Duan:2011:AOC:1989323.1989340}.

### 2018-11-07 generators_GraphDatabases.tex
last pass on my side
Corrections of similarities from iThenticate - part I

@@
 
-\paragraph{gMark}  gMark~\cite{gMark} is a schema-driven, domain-independent and query language-independent graph instance and query workload generator.  It leverages a schema definition,
-called a \emph{graph configuration}, which includes the enumeration of predicates (i.e., edge labels) and node types (i.e., node labels) occurring in the data, along with their properties in generated instances (occurrence constraints, degree distribution, etc.).
+\paragraph{gMark}  gMark~\cite{gMark} is a schema-driven, domain-independent and query language-independent generator generating both graph instances and query workload.
+It is based on a  definition of \emph{graph configuration} which involves the list of predicates (i.e., edge labels) and node types (i.e., node labels) occurring in the data together with their further properties such as degree distribution, occurrence constraints, etc.
 \emph{Query workload configuration}  describes parameters of the queries to be generated (e.g., number of queries, arity, shape, selectivity etc.).
-The authors prove that given a graph configuration $G$, deciding whether there exists a graph satisfying $G$ is NP-complete.
-And, that given a query workload configuration $Q$, deciding
-whether there exists a query workload satisfying $Q$ is NP-complete.
-Hence, gMark follows a heuristic strategy in the generation -- it attempts to achieve the exact values of the parameters and it may decide to relax some of them in order to obtain linear running time.
+The authors prove that deciding whether there exists a graph satisfying a given graph configuration $G$ is NP-complete.
+And, similarly, deciding
+whether there exists a query workload satisfying a given query workload configuration $Q$ is also NP-complete.
+Hence, gMark generating is based on a heuristic strategy: it tries to achieve the exact values of the given parameters, however, in order to obtain linear running time it may decide to relax some.
 gMark generates graphs under the form of N-triples and query workloads in four concrete syntaxes, including Cypher\footnote{\url{https://neo4j.com/developer/cypher-query-language/}}, SPARQL, SQL and LogicQL.
@@
 The resulting graph can be exported to several formats (namely GraphJson\footnote{\url{https://github.com/GraphAlchemist/GraphJSON/wiki/GraphJSON}} and CypherQueries) or loaded directly to a DBMS.
-However, it is very likely that it is not maintained anymore due to the lack of updates provided.
+However, it is very likely that it is not maintained anymore due to the lack of available updates.

### 2018-11-07 generators_SocialNetworks.tex
Corrections of similarities from iThenticate - part I

@@
 
-In general, any analysis of social networks identify their various specific
+In general, any analysis of social networks identifies their various specific
 features~\cite{Chakrabarti:2006:GML:1132952.1132954}. For example, a social
-graph has high \emph{clustering coefficient}, i.e. the degree of transitivity of
-a graph. Or, its diameter, i.e. the minimum number of hops in which some
-fraction (e.g., 90\%) of all connected pairs of nodes can reach each other, is
-usually low due to weak ties joining faraway cliques.
+graph often has high \emph{clustering coefficient}, i.e. the degree of transitivity of
+a graph. Or, its diameter, i.e. the longest shortest path amongst some fraction (e.g. 90\%) of all connected nodes, is usually low due to weak ties joining faraway cliques.
 

### 2018-11-07 generators_SocialNetworks.tex
iThenticate modifications - part II

@@
 ~\cite{Barrett:2009:GAL:1995456.1995598} focused on the construction of
-realistic social networks using a combination of public and private data sets
-and large-scale agent based techniques. The process works as follows: In the first step
-it creates a synthetic population by integrating databases from commercial and
-public sources. In the second step, a set of activity templates are determined. Each
-synthetic individual is assigned a 24-hour activity sequence including
-geolocations for each activity. To demonstrate the approach, the authors develop a synthetic population for the
-United States that models every individual in the population. The synthetic
-population is a set of geographically located people and households. Household
-structure and demographics are derived from U.S. Census data. The activity
-templates are  based on several thousand responses to an activity or time-use
-survey. Demographic information for each person and location, a minute-by-minute
-schedule of each person's activities, and the locations where these activities
-take place is generated by a combination of simulation and data fusion
-techniques. This information is captured by a dynamic social contact network. Similar methods for agent-based strategies have been reported in~\cite{Bernstein:2013:SAS:2499604.2499609}.
+realistic social networks. For this purpose the authors combine both public and private data sets
+with large-scale agent based techniques. The process works as follows: In the first step
+it creates a synthetic population by integrating public and commercial databases. In the second step, it determines a set of activity templates. A 24-hour activity sequence including
+geolocations is assigned to each synthetic individual.
+To demonstrate the approach, the authors create a synthetic US population consisting of people and households together with respective geolocations.
+For this purpose the authors combine simulation and data fusion techniques utilizing various real-world data sources such as U.S.
+Census data, responses to an activity survey or a time-use survey.
+%Demographic information for each person and location, a minute-by-minute schedule of each person's activities, and the locations where these activities take place is generated by a combination of simulation and data fusion techniques.
+The result is captured by a dynamic social contact network. Similar methods for agent-based strategies have been reported in~\cite{Bernstein:2013:SAS:2499604.2499609}.
 
 \paragraph{Linkage vs. Activity Graphs} \cite{Yao2011} distinguished between two
-types of social network graphs -- the \emph{linkage graph}, where nodes stand
-for the people in the social network and edges are their friendship links, and
-the \emph{activity graph}, where nodes also stand for the people but edges stand
-for their interactions. On the basis of the analysis of
+types of social network graphs -- the \emph{linkage graph}, where nodes represent people and edges correspond to their friendships, and the \emph{activity graph}, where nodes also represent people but correspond to their interactions.
+On the basis of the analysis of
 Flickr\footnote{\url{https://www.flickr.com/}} social links and
-Epinions\footnote{\url{http://www.epinions.com/}} network of user interactions,
-the authors discover that they both exhibit power-law degree distribution, high
-clustering coefficient (community structure), and small diameter; also regarding
-the dynamic properties they both follow the densification law and have relatively stable
-clustering coefficient over time. However, the authors do not observe diameter
-shrinking in opinions activity graph and there is a difference in degree
-correlation (how frequently nodes with similar degrees connect to each other).
-Namely linkage graphs have positive degree correlation whereas activity graphs
-show neutral degree correlation. With regards to the findings, the proposed generator focusses on linkage graphs
-with positive degree correlation. For this purpose it extends the forest
-fire spreading process algorithm~\cite{Leskovec:2005:GOT:1081870.1081893} with
-link symmetry. It has two parameters -- the \emph{burning probability} $P_b$
-which is in charge of the burning process, and the \emph{symmetry probability}
-$P_s$ which indicates backward linking from old nodes to new ones. $P_b$
-controls a BFS-based forward burning process. The fire burns increasingly
-fiercely with $P_b$ approaching 1. Meanwhile, $P_s$ adds fuel to the fire as it
-brings more links. It gives chances for big nodes to connect back to big nodes.
+Epinions\footnote{\url{http://www.epinions.com/}} network of user interactions, the authors discover that they both exhibit high clustering coefficient (community structure), small diameter, and power-law degree distribution.
+Considering the dynamic properties they both have relatively stable clustering coefficient over time and follow the densification law.
+On the other hand, diameter shrinking is not observed in Epinions activity graph and there is a difference in degree
+correlation (i.e., frequency of mutual connections of similar nodes) -- linkage graphs have positive, activity graphs neutral degree correlation.
+With regards to the findings, the proposed generator focusses on linkage graphs with positive degree correlation.
+For this purpose it extends the forest fire spreading process algorithm~\cite{Leskovec:2005:GOT:1081870.1081893} with
+link symmetry.
+It has two parameters the \emph{burning probability} $P_b$ and \emph{symmetry probability} $P_s$.
+$P_b$ ensures a BFS-based forward burning process in which fire burns strongly with $P_b$ approaching 1.
+$P_s$ ensures backward linking from old nodes to new nodes and ``adds fuel to the fire as it brings more links''.
+%It gives chances for big nodes to connect back to big nodes.
 
 \paragraph{LinkBench} The LinkBench
-benchmark~\cite{Armstrong:2013:LDB:2463676.2465296} has been designed to predict the
-performance of a database when used for persistent storage of Facebook's
-production data. The benchmark considers true Big Data and related problems with
-sharding, replication etc. The social graph at Facebook comprises objects (nodes
-with IDs, version, timestamp and data) and associations (directed edges, pairs
-of node IDs, with visibility, timestamp and data). The size of the target graph
-is the number of nodes. Graph edges are generated concurrently with graph nodes
-during bulk loading. The node ID space is divided into chunks based on the ID of
-the source node which  are processed in parallel. The edges of the graph are
-generated in accordance with the results of analysing  real-world Facebook data
-(such as outdegree distribution). A workload corresponding to 10 graph
-operations (such as insert object, count the number of associations etc.) and
-their respective characteristics over the real-world data is generated for the
-synthetic data.
+benchmark~\cite{Armstrong:2013:LDB:2463676.2465296} has been designed for the purpose of analysis of efficiency of a database storing Facebook's production data.
+The benchmark considers true Big Data and related problems with sharding, replication etc.
+The social graph at Facebook comprises objects (nodes with IDs, version, timestamp and data) and associations (directed edges, pairs of node IDs, with visibility, timestamp and data).
+The size of the target graph is the number of nodes.
+Graph edges and nodes are generated concurrently during bulk loading.
+The space of node IDs is divided into chunks which enable parallel processing.
+The edges of the graph are generated in accordance with the results of analysing  real-world Facebook data (such as outdegree distribution).
+A workload corresponding to 10 graph operations (such as insert object, count the number of associations etc.) and their respective characteristics over the real-world data is generated for the synthetic data.
 

### 2018-11-07 generators_SocialNetworks.tex
iThenticate modifications - part III (the rest)

@@
 
-\paragraph{S3G2} The Scalable Structure-correlated Social Graph Generator
-(S3G2)~\cite{Pham2013} is a general framework which  generates a directed
-labeled graph, where the nodes are objects with property values, and their
-structure is determined by the class a node belongs to. S3G2 does not aim at
-generating near real-world data, but at generating synthetic graphs with a
-correlated structure. It causes that the probability to choose a certain
-property value (from a pre-defined dictionary), or the probability to connect
-two nodes with an edge are influenced by existing data values. For example, it
-is possible to have a correlated degree distribution, from which the degree of
-each node is generated, correlated with the properties of node. Hence the generator
-can ensure that, e.g., people with many friends in a social network will
-typically post more pictures than people with few friends, i.e., the amount of
-friend nodes influences the amount of posted comment and picture nodes. The data generation process starts with generating a number of nodes with
-property values generated according to specified property value correlations and
-then adding respective edges according to specified correlation dimensions. It
-has multiple phases, each focusing on one correlation dimension. Each pass along
-one correlation dimension is a Map phase in which data is generated, followed by
-a Reduce phase that sorts the data along the correlation dimension in the next
-pass. A heuristic observation that ``the probability that two nodes are
-connected is typically skewed with respect to some similarity between the
-nodes'' enables to focus only on sliding window of most probable candidates. The core idea of the framework is demonstrated using an example of a social
-network (consisting of persons and social activities).  The dictionaries for
-property values are inspired by DBpedia and provided with 20 property value
-correlations. The edges are generated according to 3 correlation dimensions.
+\paragraph{S3G2} The Scalable Structure-correlated Social Graph Generator (S3G2)~\cite{Pham2013} is a general framework which produces a directed labeled graph whose vertices represent objects having property values.
+The respective classes determine the structure of the properties.
+S3G2 does not aim at generating near real-world data, but at generating synthetic graphs with a correlated structure.
+Hence, the existing data values influence the probability of choosing a certain property value from a pre-defined dictionary, or the probability of connecting two nodes.
+For example, the degree distribution can be correlated with the properties of a node and thus, e.g., people having many friend relationships typically post more comments and pictures.
+The data generation process starts with generating a number of nodes with property values generated according to specified property value correlations and then adding respective edges according to specified correlation dimensions.
+It has multiple phases, each focusing on one correlation dimension.
+Data is generated in a Map phase corresponding to a pass along one correlation dimension.
+Then the data are sorted along the correlation dimension in the following Reduce phase.
+A heuristic observation that ``the probability that two nodes are connected is typically skewed with respect to some similarity between the nodes'' enables to focus only on sliding window of most probable candidates.
+The core idea of the framework is demonstrated using an example of a social network (consisting of persons and social activities).
+The dictionaries for property values are inspired by DBpedia and provided with 20 property value correlations.
+The edges are generated according to 3 correlation dimensions.
 
@@
 
-\paragraph{LDBC SNB} The Social Network Benchmark
-(SNB)~\cite{Erling:2015:LSN:2723372.2742786} provided by LDBC consists of three
-distinct benchmarks on a common dataset corresponding to three different
-workloads. SNB models a social network akin to Facebook. The dataset consists of
-persons and a friendship network that connects them; whereas the majority of the
-data is in the messages that these persons post in discussion trees on their
-forums. The three query workloads involve: (1) SNB-Interactive, i.e., complex
-read-only queries, that touch a significant amount of data, (2) SNB-BI which
-accesses a large percentage of all entities in the dataset and groups these in
-various dimensions, and (3) SNB-Algorithms, i.e., graph analysis algorithms,
-including PageRank, Community Detection, Clustering and Breadth First Search.
-The graph generator realizes power laws, uses skewed value distributions, and
-introduces plausible correlations between property values and graph structures.
-It is implemented on top of Hadoop to provide scalability.
+\paragraph{LDBC SNB} Despite having a common Facebook-like dataset, thanks to three distinct workloads the Social Network Benchmark (SNB)~\cite{Erling:2015:LSN:2723372.2742786} provided by LDBC corresponds to three distinct benchmarks.
+The network nodes correspond to people and the edges represent their friendship and messages they post in discussion trees on their forums.
+The three query workloads involve: (1) SNB-Interactive, i.e., complex read-only queries accessing a significant portion of data, (2) SNB-BI, i.e., queries accessing a high percentage of  entities and grouping them in various dimensions, and (3) SNB-Algorithms, involving graph analysis algorithms, such as community detection, PageRank, BFS, and clustering.
+The graph generator realizes power laws, uses skewed value distributions, and ensures reasonable correlations between graph structures and property values.
+To provide scalability it is implemented on top of Hadoop.
 
@@
 topology generation which approximates the characteristics of a real social
-network (such as a small graph diameter, small average path length, skew degree
-distribution, and community structures), however,  this is usually done without any data. Hence, they
+network (such as a small graph diameter, skew degree
+distribution, small average path length, and community structures), however,  this is usually done without any data. Hence, they
 introduced a general stochastic modeling system which allows the users to

### 2018-11-07 generators_analytics.tex
iThenticate modifications - part III (the rest)

@@
 
-\paragraph{HPC Scalable Graph Analysis Benchmark} The HPC Scalable Graph
-Analysis Benchmark~\cite{HPCgraph,Bader:2005:DIH:2099301.2099360} represents an
-application with multiple analysis techniques that access a single data
-structure representing a weighted, directed graph. The benchmark is composed of
-four separated operations (graph construction, classification of large vertex
-sets, graph extraction with BFS, and graph analysis with betweenness centrality)
-on a graph that follows a power-law distribution. The graph generator constructs a list of edge tuples containing vertex
-identifiers (with the edge direction from the first one to the second one) and
-weights that represent data assigned to the edges of the multigraph in the form
-of positive integers with a uniform random distribution. The generator has the
-following parameters: number of vertices, number of edges, and maximum weight of
-an edge. The algorithm of the generator is based on R-MAT. Since the authors aim
-to avoid data locality, in the final step the vertex numbers are randomly
-permuted, and then edge tuples are randomly shuffled. A related project from the same authors developed for the 9th DIMACS Shortest
-Paths Challenge is GTgraph~\cite{GTgraph}. It involves three types of graphs:
-input graph instances used in the DARPA HPCS SSCA\#2 graph theory benchmark
-(version 1.0), Erd\"{o}s-R\'{e}nyi random graphs, and small-world graphs based
-on the R-MAT model.
+\paragraph{HPC Scalable Graph Analysis Benchmark} The HPC Scalable Graph Analysis Benchmark~\cite{HPCgraph,Bader:2005:DIH:2099301.2099360} consists of a weighted, directed graph that follows a power-law distribution and four related analysis techniques (namely graph construction, graph extraction with BFS, classification of large vertex sets, and graph analysis with betweenness centrality).
+The generator has the following parameters: number of vertices, number of edges, and maximum weight of an edge.
+It outputs a list of tuples containing identifiers of vertices of an edge (with the direction from the first one to the second one) and weights (positive integers  with a uniform random distribution) assigned to the edges of the multigraph.
+The algorithm of the generator is based on R-MAT.
+To avoid data locality, in the final step the vertex numbers are randomly permuted and then the tuples are randomly shuffled.
+A related project from the same authors developed for the 9th DIMACS Shortest Paths Challenge is GTgraph~\cite{GTgraph}.
+It involves three types of graphs: (1) Erd\"{o}s-R\'{e}nyi random graphs, (2) input graph instances used in the DARPA HPCS SSCA\#2 graph theory benchmark (version 1.0), and (3) small-world graphs based on the R-MAT model.
 

### 2018-11-08 generators_GraphDatabases.tex
Sherif Changes

@@
 
-\paragraph{XGDBench} XGDBench~\cite{Dayarathna:2014:GDB:2676904.2676939} is an extensible graph database benchmarking platform for cloud computing systems. Its intent is to automate
+\paragraph{XGDBench} XGDBench~\cite{Dayarathna:2014:GDB:2676904.2676939} is an extensible graph database benchmarking platform for cloud-based systems. Its intent is to automate
 the process of graph database benchmarking in the cloud by focusing on a graph database application for social networking services.
 It extends the Yahoo!
-Cloud Multiplicative Attribute (MAG) Graph Serving Benchmark (YCSB)~\cite{Cooper:2010:BCS:1807128.1807152} and is composed of a workload generator client and a package of standard workloads that cover interesting parts of the performance space.
-The workload generator of YCSB supports definition of new workload types.
-XGDBench involves basic operations such as read / insert / update / delete an attribute, loading of the list of neighbors and BFS traversal.
+Cloud Multiplicative Attribute (MAG) Graph Serving Benchmark (YCSB)~\cite{Cooper:2010:BCS:1807128.1807152} and \iffalse consists of of a workload generator client and\fi provides a package of standard workloads that cover interesting parts of the performance space.
+\iffalse In particular, the workload generator of YCSB supports definition of new workload types.\fi In particular, the workload of XGDBench involves basic operations such as read / insert / update / delete an attribute, loading of the list of neighbors and BFS traversal.
 Using the generators, 7 workloads are created, such as update heavy, read mostly, short range scan, traverse heavy etc.
@@
 The simplified MAG algorithm accepts the number of vertices of the generated graph, the number of attributes per vertex, a threshold value for random initialization of attributes, an edge affinity threshold value that determines whether there is an edge between two vertices, and an affinity matrix.
-It has been proven that MAG generates graphs with both analytically tractable and statistically interesting properties.
-A multi-threaded version of the graph generator that generates large graphs on multi-core systems faster was implemented too.
+\iffalse It has been proven that MAG generates graphs with both analytically tractable and statistically interesting properties.\fi A multi-threaded version of the graph generator that generates large graphs on multi-core systems faster was implemented too.
 

### 2018-11-08 generators_LinkedData.tex
Sherif Changes

@@
 
-\paragraph{SP$^2$Bench} The SP$^2$Bench\footnote{\url{http://dbis.informatik.uni-freiburg.de/forschung/projekte/SP2B/}} is a language-specific benchmark~\cite{Schmidt2010} which uses the DBLP as a domain for the dataset.
+\paragraph{SP$^2$Bench} The SP$^2$Bench\footnote{\url{http://dbis.informatik.uni-freiburg.de/forschung/projekte/SP2B/}} is a language-specific benchmark~\cite{Schmidt2010} which is based on the DBLP  the dataset.
 %, so the types involve Person, Inproceedings, Article etc.
-The generated documents mirror key characteristics and distributions found in the original DBLP database.
-The data mimics natural correlations between entities, such as power law distributions (found in the citation system or the distribution of publications among authors) and limited growth curves (e.g., the increasing number of venues and publications over time).
-All random functions of the generator base on a fixed seed which makes data generation deterministic.
-SP$^2$Bench is accompanied by 12 queries covering different operator constellations, RDF access paths, typical RDF constructs etc.
+The generated datasets follow the key characteristics of the original DBLP dataset.
+In particular, the data mimics the correlations between entities.
+All random functions of the generator is based on a fixed seed that ensures the data generation process to be deterministic.
+SP$^2$Bench is accompanied by 12 queries covering different operator constellations such as RDF access paths and typical RDF constructs.
 
@@
 The authors focus mainly on the  \emph{structuredness} (\emph{coherence}) of each benchmark dataset claiming that a primitive metric (e.g., the number of triples or the average in/outdegree) quantifies only some specific aspect of each dataset.
-The level of structuredness of a dataset $D$ with respect to a type $T$ is determined by how well the instance data in $D$ conforms to type $T$.
-The type system is extracted from the data set by looking for triples whose property is \texttt{http://www.w3.org/1999/02/22-rdf-syntax-ns\#type} and extracting type $T$ from their object.
+The degree of structuredness of a dataset $D$ with respect to a type $T$ is based on  the regularity of instance data in $D$ on conforming to type $T$.
+The type system is extracted from the data set by finding the RDF triples that have property  \texttt{http://www.w3.org/1999/02/22-rdf-syntax-ns\#type} and extract type $T$ from their object.
 Properties of $T$ are determined as the union of all the properties that the instances of type $T$ have.
@@
 The authors show that the structuredness of the chosen benchmarks is fixed, whereas real-world RDF datasets lie in currently untested parts of the spectrum.
-As a consequence, they introduce a new benchmark that accepts as input any dataset along with a desired level of structuredness and size (smaller than the size of the original data), and uses the input dataset as a seed to produce a subset of the original data with the indicated size and structuredness.
-In addition they show that structuredness and size mutually influence each other.
+As a consequence, they introduce a new benchmark that accepts as input any dataset associated with a required level of structuredness and size (smaller than the size of the original data), and exploits the input documents as a seed to generate a subset of the original data with the target structuredness and size.
+In addition, they show that structuredness and size mutually influence each other.
 
-\paragraph{DBPSB} DBpedia SPARQL Benchmark (DBPSB)\footnote{\url{http://aksw.org/Projects/DBPSB.html}} proposed at the University of Leipzig is based on queries that were issued by humans and applications
+\paragraph{DBPSB} DBpedia SPARQL Benchmark (DBPSB)\footnote{\url{http://aksw.org/Projects/DBPSB.html}} proposed at the University of Leipzig is based on queries that have been issued by humans and applications
 against existing RDF data~\cite{Morsey2011,Morsey:2012:UBR:2900929.2901031}.
-In addition, the authors argue that benchmarks like LUBM, BSBM, or SP$^2$Bench resemble relational database benchmarks involving relational data structures with few and homogeneously structured classes, whereas RDF knowledge bases are increasingly heterogeneous (e.g., DBpedia version 3.6, for example, contains 289,016 classes of which 275 classes belong
-to the DBpedia ontology) and various datatypes and object references of different types are
+In addition, the authors argue that benchmarks like LUBM, BSBM, or SP$^2$Bench resemble relational database benchmarks involving relational data structures with few and homogeneously structured classes, whereas RDF knowledge bases are increasingly heterogeneous.
+For example, DBpedia version 3.6 consists of 289,016 classes of which 275 classes are defined based on the DBpedia ontology.
+In addition, different datatypes and object references of various types are
 used in property values.
-Hence, they propose a generic SPARQL benchmark creation methodology based on a flexible data generation mimicking an input data source, query-log mining, clustering, and SPARQL feature analysis.
+Hence, they presented a generic SPARQL benchmark creation approach which is based on a flexible data generation mechanism that mimics the input data source.
 The proposed dataset creation process starts with an input dataset.
-Datasets of multiple sizes of the original data are created by duplicating all triples and changing their namespaces.
+Multiple Datasets with different sizes  are then generated by duplicating all triples and changing their namespaces.
 For generating smaller datasets, an appropriate fraction of all triples is selected randomly or by sampling across classes in the dataset.
-The goal of the query analysis and clustering is to detect prototypical queries on the basis of their frequent usage and similarity.
-The methodology is applied on the DBpedia SPARQL endpoint and a set of 25 SPARQL query templates is derived, which cover most commonly used SPARQL features and are used to generate the actual benchmark queries by parametrization.
+\iffalse The goal of the query analysis and clustering is to detect prototypical queries on the basis of their frequent usage and similarity.\fi The methodology is applied on the DBpedia SPARQL endpoint and a set of 25 SPARQL query templates is derived, that cover the most commonly used SPARQL features.
 
@@
 
-\paragraph{SIB} The developers of the Social Network Intelligence BenchMark (SIB)\footnote{\url{https://www.w3.org/wiki/Social_Network_Intelligence_BenchMark}} based the design of their benchmark based on the claim that existing benchmarks are limited in representing the real RDF datasets and are mostly relational-like.
-Hence, they propose a benchmark for challenging query processing over real graphs~\cite{sib}.
-It simulates an RDF backend of a social network site, in which users and their interactions form a social graph of social activities such as writing posts, posting comments, creating/managing groups, etc.
-The distribution of generated data on each relation conforms to the data distribution analyzed over real-world social networks.
-Association rules are included in order to convey the real-world data correlation into synthetic data.
+\paragraph{SIB} The developers of the Social Network Intelligence BenchMark (SIB)\footnote{\url{https://www.w3.org/wiki/Social_Network_Intelligence_BenchMark}} based the design of their benchmark based on the claim that existing benchmarks are limited in reflecting the characteristics of the real RDF datasets and are mostly relational-like.
+Hence, they proposed a benchmark for  query processing over real graphs~\cite{sib}.
+The proposed benchmark simulates an RDF backend of a social network site where users and their interactions form a social graph of social activities such as creating/managing groups, writing posts and posting comments.
+The distribution of generated data on each relation follows the data distribution inferred from real-world social networks.
+In addition, association rules are included in order to convey the real-world data correlation into synthetic data.
 The  generated data is linked with the RDF datasets from DBpedia.
@@
 \paragraph{Geographica} The Geographica benchmark\footnote{\url{http://geographica.di.uoa.gr/}} has been designed to target the area of geospatial data~\cite{DBLP:conf/semweb/GarbisKK13} and respective SPARQL extensions GeoSPARQL~\cite{battle2012enabling} and stSPARQL~\cite{koubarakis2010modeling}.
-The benchmark involves a real-world workload based on publicly available linked data sets covering a range of geometry types (e.g., points, lines, polygons) and  a synthetic workload.
+The benchmark involves a real-world workload based on openly available datasets that cove a range of geometry types (e.g., points, lines, polygons) and  a synthetic workload.
 In the former case there is a (1) a micro benchmark that tests primitive spatial functions (involving 29 queries) and (2) macro benchmark that tests the performance of RDF stores in typical application scenarios like reverse geocoding or map search and browsing (consisting of 11 queries).
@@
 \paragraph{WatDiv} The Waterloo SPARQL Diversity Test Suite (WatDiv)\footnote{\url{http://dsg.uwaterloo.ca/watdiv/}} developed at the University of Waterloo provides stress testing tools to address the observation that existing SPARQL benchmarks are not suitable for testing systems for diverse queries and varied workloads~\cite{Aluc:2014:DST:2717213.2717229}.
-The benchmark introduces two classes of query features -- structural and data-driven -- and performs an in-depth analysis on existing SPARQL benchmarks (LUBM, BSBM, SP$^2$Bench, and DBPSB) using the two classes of query features.
+The benchmark introduces two classes of query features -- structural and data-driven -- and performs a detailed analysis on existing SPARQL benchmarks (LUBM, BSBM, SP$^2$Bench, and DBPSB) using the two classes of query features.
 The structural features involve triple pattern count, join vertex count, join vertex degree, and join vertex count.
 The data-driven features involve result cardinality and several types of selectivity.
-The analysis of the four benchmarks reveals that they are not sufficiently diverse to test the strengths and weaknesses of different physical design choices employed by RDF systems.
-The proposed solution, WatDiv, involves (1) a data generator which generates scalable datasets according to the WatDiv schema, (2) a query template generator which traverses the WatDiv schema and generates a diverse set of query templates, (3) a query generator which instantiates the templates with actual RDF terms from the dataset, and (4) a feature extractor which computes the structural and data-driven features of the generated data and workload.
-For the study in the paper the authors generated 12,500 test queries from 125 query templates.
+The analysis of the four benchmarks reveals that they are not sufficiently diverse to evaluate the strengths and weaknesses of the various physical design alternatives that have been implemented by the different RDF systems.
+The proposed solution, WatDiv, involves (1) a data generator which generates scalable datasets according to the WatDiv schema, (2) a query template generator which traverses the WatDiv schema and generates a diverse set of query templates, (3) a query generator which instantiates the templates with actual RDF terms from the dataset, and (4) a feature extractor which extracts the structural features of the generated data and workload.
+%For the study in the paper the authors generated 12,500 test queries from 125 query templates.
 
-\paragraph{RBench} RBench~\cite{Qiao:2015:RAR:2723372.2746479} is an application-specific benchmark which takes any RDF dataset as a template and generates a set of synthetic datasets with similar characteristics, required size scaling factor $s$ and (node) degree scaling factor $d$.
-A generated benchmark dataset is considered similar to the given dataset if their values for the dataset evaluation metrics and query evaluation times for different techniques are similar.
-Three evaluation metrics are utilized for this purpose: dataset coherence (i.e., a measure how uniformly predicates are distributed among the same type/class), relationship specialty (i.e., the number of occurrences of the same predicate associated with each resource), and literal diversity.
-A query generation process is proposed to generate 5 types of queries (node queries, edge queries, star queries, path queries, and subgraph queries) for any generated data.
-The benchmark project FEASIBLE~\cite{Saleem2015} is also an application-specific benchmark; however, contrary to RBench, it is able to generate benchmarks from a set of queries (in particular from query logs) by selecting prototypical queries of a user-defined
+\paragraph{RBench} RBench~\cite{Qiao:2015:RAR:2723372.2746479} is an application-specific benchmark which receives any RDF dataset as an input and produces as an output a set of datasets, that have similar characteristics of the input dataset, using size scaling factor $s$ and (node) degree scaling factor $d$.
+\iffalse A generated benchmark dataset is considered similar to the given dataset if their values for the dataset evaluation metrics and query evaluation times for different techniques are similar.
+Three evaluation metrics are utilized for this purpose: dataset coherence (i.e., a measure how uniformly predicates are distributed among the same type/class), relationship specialty (i.e., the number of occurrences of the same predicate associated with each resource), and literal diversity.\fi A query generation process has been implemented to produce 5 different types of queries (edge-based queries, node-based queries, path queries, star queries, subgraph queries) for any generated data.
+The benchmark project FEASIBLE~\cite{Saleem2015} is also an application-specific benchmark; however, contrary to RBench, it is designed to produce benchmarks from a set of queries (in particular from query logs) by relying on example queries of a user-defined
 size from the input set of queries.
@@
 \iffalse The following three benchmarks were developed and are currently maintained.\fi In the Semantic Web domain, the project released the Semantic Publishing Benchmark (SPB)~\cite{spb} that has been inspired by the Media/Publishing industry (namely BBC\footnote{\url{http://www.bbc.com/}}).
-The application scenario of this benchmark considers a media or a publishing organization that deals with large volumes of streaming content, namely news, articles or  ``media assets''.
-This content is enriched with metadata that describes it and links it to reference knowledge -- taxonomies and databases that include relevant concepts, entities and factual information.
+The application scenario of this benchmark simulates a media or a publishing organization that handles large amount of streaming content (e.g., news, articles).
+\iffalse This content is enriched with metadata that describes it and links it to reference knowledge -- taxonomies and databases that include relevant concepts, entities and factual information.
 The SPB data generator produces scalable in size synthetic large data.
-Synthetic data consists of a large number of annotations of media assets that refer entities found in reference datasets.
-The data generator models three types of relations in produced synthetic data: clustering of data, correlations of entities, and random tagging of entities.
-Two workloads are provided: (1) basic, involving an interactive query-mix querying the relations between entities in reference data, and (2) advanced,  consisting of interactive and analytical query-mixes.
+Synthetic data consists of a large number of annotations of media assets that refer entities found in reference datasets.\fi The data generator mimics three types of relations in the generated synthetic data: clustering of data, correlations of entities, and random tagging of entities.
+Two workloads are provided: (1) basic, involving an interactive query-mix querying the relations between entities in reference data, and (2) advanced,  focusing on interactive and analytical query-mixes.
 The LDBC has designed two other benchmarks: the Social Network Benchmark (SNB)~\cite{Erling:2015:LSN:2723372.2742786} for the social network domain  (see Section~\ref{sec:generators_socialnetworks}) and Graphalytics~\cite{Iosup:2016:LGB:3007263.3007270}   for the analytics domain.% (see Section~\ref{sec:generators_analytics}).
@@
 \paragraph{LinkGen} LinkGen is a synthetic linked data generator that has been designed to generate RDF datasets for a given vocabulary~\cite{10.1007/978-3-319-46547-0_12}.
-The generator is designed to receive a vocabulary as an input  and supports two statistical distribution techniques for generating entities: Gaussian distribution and Zipf's power-law distribution.
+The generator is designed to receive a vocabulary as an input  and supports two statistical distributions for generating entities: Gaussian distribution and Zipf's power-law distribution.
 LinkGen can augment the generated data with inconsistent and noisy  data such as writing two conflicting values for a given datatype property,  adding triples with syntactic errors, adding wrong statements by assigning them with invalid domain and creating instances with no type information.

### 2018-11-09 generators_GraphDatabases.tex
gMark - rewriting

@@
 
-\paragraph{gMark}  gMark~\cite{gMark} is a schema-driven, domain-independent and query language-independent generator generating both graph instances and query workload.
-It is based on a  definition of \emph{graph configuration} which involves the list of predicates (i.e., edge labels) and node types (i.e., node labels) occurring in the data together with their further properties such as degree distribution, occurrence constraints, etc.
-\emph{Query workload configuration}  describes parameters of the queries to be generated (e.g., number of queries, arity, shape, selectivity etc.).
-The authors prove that deciding whether there exists a graph satisfying a given graph configuration $G$ is NP-complete.
-And, similarly, deciding
-whether there exists a query workload satisfying a given query workload configuration $Q$ is also NP-complete.
+\paragraph{gMark}  gMark~\cite{gMark} is a schema-driven and domain-agnostic generator of both graph instances and graph query workloads.
+It can generate instances under the form of N-triples and queries in various concrete query languages, including OpenCypher\footnote{\url{https://neo4j.com/developer/cypher-query-language/}}, recursive SQL, SPARQL and LogicQL.
+In gMark, it is possible to specify a \emph{graph configuration} involving the admitted edge predicates and node labels occurring in the graph instance along with additional parameters such as degree distribution, occurrence constraints, etc.
+The \emph{Query workload configuration} describes parameters of the query workload to be generated, by including the number of queries, arity, shape and selectivity of the queries.
+The problem of deciding whether there exists a graph satisfying a given graph configuration $G$ is NP-complete. The same applies to the problem of deciding 
+whether it exists a query workload compliant with a a given query workload configuration $Q$. In view of this, gMark adopts a best effort approach in which the
+parameters specified in the configuration files are attained in a relaxed fashion in order to achieve linear running time whenever possible.
+
+%The authors prove that deciding whether there exists a graph satisfying a given graph configuration $G$ is NP-complete. And, similarly, deciding
+%whether there exists a query workload satisfying a given query workload configuration $Q$ is also NP-complete.
 Hence, gMark generating is based on a heuristic strategy: it tries to achieve the exact values of the given parameters, however, in order to obtain linear running time it may decide to relax some.

### 2018-11-09 classification.tex
rewriting Part I

@@
 \begin{itemize}
-  \item \emph{Degree-based generators}: Given a degree distribution (typically following a power law), these generators (e.g., Barabasi-Albert model~\cite{Barabasi99emergenceScaling}) try to find a graph that matches it, but without giving any insights about the graph or trying to match other criteria (like, e.g., small diameter, eigenvalues etc.).
+  \item \emph{Degree-based generators}: Given a (customarily power law) degree distribution, these generators (e.g., Barabasi-Albert model~\cite{Barabasi99emergenceScaling}) attempt to produce a graph matching the above distribution.
+However, they do not provide any insights about the graph or ignore the matching of other parameters such as for instance small diameter, eigenvalues and so on.
   \item \emph{Procedural generators}: These generators (e.g., R-MAT~\cite{DBLP:conf/sdm/ChakrabartiZF04}) try to find simple mechanisms to generate graphs that match a property of the real graphs and, typically, the power law degree distribution.

### 2018-11-09 introduction.tex
rewriting Part I

@@
 Densification Power Law (DPL) and shrinking diameters and community-guided
-attachment properties \cite{Leskovec:2005:GOT:1081870.1081893} is then considered, along with tackling Kronecker
-recursion with recursive tensor multiplication \cite{AkogluMF08}.
-We refer the reader to this survey for evolutionary network generators and
-we further discuss the open challenges of evolving graph data in Section 5.
+attachment properties \cite{Leskovec:2005:GOT:1081870.1081893}.
+Generation of networks tackling Kronecker
+recursion with recursive tensor multiplication \cite{AkogluMF08} is then considered in the above survey.
+We refer the reader to the aformentioned survey for evolutionary network generators and further discuss the open challenges of evolving graph data in Section 5.
 %\TODO{Better highlight the differences when Sherif's part is in.}

### 2018-11-09 generators_LinkedData.tex
rewriting pages 9-10 (iThenticate)

@@
 The Univ-Bench Artificial  (UBA) data generator features random and repeatable data generation (exploiting classical linear congruential generator, LCG, of numbers).
-In particular, data generated by the tool are exactly repeatable with respect to universities (assigning them zero-based indexes, i.e., the first university is named University0 and so on).
-The generator allows a user to specify the seed for random number generation, the number of universities, and the starting index of the universities.
+In particular, data generated by the tool are assigned zero-based indexes (i.e., the first university is named University0 and so on), thus they are reproducible at any time with the same indexes.
+The generator allows to specify a seed for random number generation, along with the desired number of universities, and the starting index of the universities.
 
@@
 The generation is divided into two phases: (1) the property-discovering phase, and (2) the data generation phase.
-The authors present a probabilistic model that, given representative data of some domain, can capture the properties of the data and generate synthetic data that has similar properties.
-A Monte Carlo algorithm is used to generate synthetic data.
-The approach is demonstrated on the Lehigh University BibTeX ontology which consists of 28 classes and 80 properties.
-12 test queries were designed for  the benchmark data.
+The authors present a probabilistic model that can emulate the properties of the data of a particular domain and generate synthetic data exhibiting similar properties.
+A Monte Carlo algorithm is employed to output synthetic data.
+The approach is demonstrated on the Lehigh University BibTeX ontology which consists of 28 classes along with 80 properties.
+The LUBM benchmark includes 12 test queries that were designed for the benchmark data.
 Another extension of LUBM, the University Ontology Benchmark (UOBM)\footnote{\url{https://www.cs.ox.ac.uk/isg/tools/UOBMGenerator/}}, focuses on two aspects: (1) usage of all constructs of OWL Lite and OWL DL~\cite{owl} and (2) lack of necessary links between the generated data which thus form isolated graphs~\cite{Ma:2006:TCO:2094613.2094629}.
@@
 \paragraph{BSBM} The Berlin SPARQL Benchmark (BSBM)\footnote{\url{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}}, models an e-commerce domain where types Product, Offer and Vendor are used to model the relationships between products and the vendors offering them, while types Person and Review are used to model the relationship between users and product reviews these users write~\cite{Bizer09theberlin}.
-The benchmark comes with 12 queries and 2 query mixes (sequences of the 12 queries) emulating the search and navigation pattern of a consumer looking for a product.
+The benchmark comes equipped with 12 queries and 2 query mixes (sequences of the 12 queries) emulating the search and navigation pattern of a consumer looking for a product.
 The data generator supports the creation of arbitrarily large datasets using the number of products $n$ as scale factor which further influences also other characteristics of the data, such as, e.g., the depth of type hierarchy of products (defined as $d = round(log_{10}(n))/2 + 1$), branching factor ($bfr = 2 \times round(log_{10}(n))$), the number of product features (having $lowerBound = 35 \times i / (d \times (d+1)/2 - 1)$ and $upperBound = 75 \times i / (d \times (d+1)/2 - 1)$) etc.

### 2018-11-09 generators_general.tex
rewriting pages 9-10 (iThenticate)

@@
 distributions~\cite{DBLP:conf/sdm/ChakrabartiZF04}.
-The generator is recursive and uses only a small number of parameters.
-In principle, the strategy of this generator is to find simple mechanisms to generate graphs that match
+The generator is recursive and employs a fairly small number of parameters.
+In principle, the strategy of this generator is to achieve simple means to generate graphs that match
 the properties of the real graphs.
@@
 also implemented a synthetic generator called
-GraphGen\footnote{https://www.cse.ust.hk/graphgen/}. It is
-based on the IBM synthetic data generation code for associations and sequential
-patterns\footnote{From 1996, no longer available at
+GraphGen\footnote{https://www.cse.ust.hk/graphgen/}. It relies on data generation code for associations and sequential
+patterns provided by IBM \footnote{From 1996, no longer available at
 \url{http://www.almaden.ibm.com/cs/projects/iis/hdb/Projects/data
-mining/mining.shtml}}. GraphGen creates a collection of labeled, undirected and
-connected graphs which focuses on the performance evaluation of frequent subgraph mining
+mining/mining.shtml}}. GraphGen yields a collection of undirected, labeled and
+connected graphs. It addresses the performance evaluation of frequent subgraph mining
 algorithms and graph query processing algorithms. The result is represented as a
-list of graphs, each consisting of a list of nodes and a list of edges.
+list of graphs, each consisting of a list of nodes along with a list of edges.
 
@@
 clustering coefficient for each degree, Darwini is able to model the clustering
-coefficient distribution per degree. It achieves this by grouping the vertices
-of the graph into buckets by the expected number of closed triangles that they need
-to close in order to attain the expected clustering coefficient, which is
+coefficient distribution per degree. It achieves this by gathering the vertices
+of the graph into buckets based on the expected number of closed triangles that they need
+to close in order to attain the expected clustering coefficient. The latter is
 sampled from the input distributions. Then, the vertices in each bucket are
 connected randomly with a probability that would produce the expected
-desired number of triangles for such bucket. Then, as in BTER, the excess degree
+desired number of triangles for each bucket. Then, as in BTER, the excess degree
 is used to connect the different buckets. The authors report that Darwini is

### 2018-11-09 generators_LinkedData.tex
last page 10 - iThenticate

@@
 
-\paragraph{IIMB} Contrary to the previous work, ~\cite{Ferrara08OM} proposed the ISLab Instance Matching Benchmark (IIMB)\footnote{\url{http://www.ics.forth.gr/isl/BenchmarksTutorial/}} for the problem of instance matching defined as follows: Given two instances $i_1$ and $i_2$, belonging to the same ontology or to different ontologies, instance matching is defined as a function $Im(i_1, i_2) \rightarrow \{0, 1\}$,  where $1$ denotes the fact that $i_1$ and $i_2$ are referred to the same real-world object and $0$ denotes the fact that $i_1$ and $i_2$ are referred to different objects.
-It targets the domain of movie data which contains 15 named classes, 5 object properties and 13 datatype properties.
+\paragraph{IIMB} Contrary to the previous work, Ferrara et al.~\cite{Ferrara08OM} proposed the ISLab Instance Matching Benchmark (IIMB)\footnote{\url{http://www.ics.forth.gr/isl/BenchmarksTutorial/}} for the problem of instance matching.
+Given two instances $i_1$ and $i_2$ adhering to the same ontology or to different ontologies, instance matching is defined as a function $Im(i_1, i_2) \rightarrow \{0, 1\}$,  where $i_1$ and $i_2$ can be mapped to the same real-world object (in which case the function maps to $1$) or $i_1$ and $i_2$ are referred to different objects (in which case the function maps to $0$).
+It targets the domain of movie data which contains 15 named classes, along with 5 object properties and 13 datatype properties.
 The data are extracted from IMDb\footnote{\url{http://www.imdb.com/}}.
 The data generator corresponds to a data modifier which simulates differences between the data.
-In particular it involves data value differences (such as typographical errors or usage of different standard formats, e.g., for names), structural heterogeneity (represented by different levels of depth for properties representation, different aggregation criteria for properties representation, or missing values specification) and logical heterogeneity (such as instantiation on different subclasses of the same superclass or instantiation on disjoint classes).
+In particular it involves data value differences (such as typographical errors or usage of different standard formats, e.g., for names), structural heterogeneity (represented by different levels of depth for properties, diverse aggregation criteria for properties, or missing values specification) and logical heterogeneity (such as instantiation on different subclasses of the same superclass or instantiation on disjoint classes).
 
-\paragraph{BSBM} The Berlin SPARQL Benchmark (BSBM)\footnote{\url{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}}, models an e-commerce domain where types Product, Offer and Vendor are used to model the relationships between products and the vendors offering them, while types Person and Review are used to model the relationship between users and product reviews these users write~\cite{Bizer09theberlin}.
-The benchmark comes equipped with 12 queries and 2 query mixes (sequences of the 12 queries) emulating the search and navigation pattern of a consumer looking for a product.
-The data generator supports the creation of arbitrarily large datasets using the number of products $n$ as scale factor which further influences also other characteristics of the data, such as, e.g., the depth of type hierarchy of products (defined as $d = round(log_{10}(n))/2 + 1$), branching factor ($bfr = 2 \times round(log_{10}(n))$), the number of product features (having $lowerBound = 35 \times i / (d \times (d+1)/2 - 1)$ and $upperBound = 75 \times i / (d \times (d+1)/2 - 1)$) etc.
-BSBM can output two representations -- an RDF representation and a purely relational representation.
+\paragraph{BSBM} The Berlin SPARQL Benchmark (BSBM)\footnote{\url{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}}, is centered around an e-commerce domain where types Product, Offer and Vendor model the relationships between products and the vendors offering them, while types Person and Review model the relationships between users and product reviews written by these users~\cite{Bizer09theberlin}.
+The benchmark comes equipped with 12 queries and 2 query mixes (sequences of the 12 queries) emulating the navigation pattern and search of a consumer seeking a product.
+The data generator is capable of producing arbitrarily large datasets using the number of products $n$ as scale factor.
+The scale factor also impacts other data characteristics, such as, e.g., the depth of type hierarchy of products (defined as $d = round(log_{10}(n))/2 + 1$), branching factor ($bfr = 2 \times round(log_{10}(n))$), the number of product features (having $lowerBound = 35 \times i / (d \times (d+1)/2 - 1)$ and $upperBound = 75 \times i / (d \times (d+1)/2 - 1)$) etc.
+BSBM can output two representations, i.e.
+an RDF representation along with a relational representation.
 Thus, BSBM also defines an SQL~\cite{sql} representation of the queries.

### 2018-11-09 generators_LinkedData.tex
typo

@@
 
-\paragraph{SP$^2$Bench} The SP$^2$Bench\footnote{\url{http://dbis.informatik.uni-freiburg.de/forschung/projekte/SP2B/}} is a language-specific benchmark~\cite{Schmidt2010} which is based on the DBLP  the dataset.
+\paragraph{SP$^2$Bench} The SP$^2$Bench\footnote{\url{http://dbis.informatik.uni-freiburg.de/forschung/projekte/SP2B/}} is a language-specific benchmark~\cite{Schmidt2010} which is based on the DBLP dataset.
 %, so the types involve Person, Inproceedings, Article etc.

### 2018-11-09 challenges.tex
Fixed text to comply with plagiarism requirements

@@
 However, as shown in~\cite{Leskovec:2005:RMT:2101235.2101254,Leskovec:2005:GOT:1081870.1081893},
-evolving graphs have further specific features.
-For example, some graphs grow over time according to a \emph{densification power law} which means that real graphs tend to sprout many more edges than nodes, and thus are densifying as they grow.
-Also the effective diameter of graphs tends to shrink or stabilize as the graph grows with time.
+evolving graphs have further specific features. For example, some graphs grow
+over time according to a \emph{densification power law} which means that in real
+graphs, edges tend to appear at a higher pace than vertices, meaning that these
+graphs densify as they grow. Also the way the new edges are distributed has the
+effect of a shrinking diameter that ends up stabilizing as the graph grows with time.
 
@@
 
-The respective data generator should hence be able to simulate a natural growth and/or changes in the structure of the graph with regards to the various features of distinct use cases.
-However,  even though the area of dynamic graphs is intensively studied, surprisingly there seem to exist only very few proposals of a generator for dealing with this area.
-In~\cite{GoerkeKlugeSchumm2012_1000029825} the authors focus on \emph{clustering dynamic graphs}, i.e.
-graphs where the clustering corresponds to the partition of nodes into natural groups based on the paradigm of intra-cluster density versus inter-cluster sparsity of edges.
-The generator generates a time series of random graphs $G_0, G_1, ..., G_n$, where $G_t$ emerges from $G_{t-1}$ via atomic updates, i.e., insertion or deletion of an edge or a vertex.
-The generator keeps track of a (dynamic) ground truth clustering.
-The probability of atomic events is chosen in a way that adheres to this clustering, without losing randomness.
+The respective data generator should hence be able to simulate a natural growth
+and/or changes in the structure of the graph with regards to the various
+features of distinct use cases. However,  even though the area of dynamic graphs
+is intensively studied, surprisingly there seem to exist only very few proposals
+of a generator for dealing with this area.
+In~\cite{GoerkeKlugeSchumm2012_1000029825} the authors focus on \emph{clustering
+dynamic graphs}, i.e. graphs where the clustering corresponds to the partition
+of nodes into natural groups based on the paradigm of intra-cluster density
+versus inter-cluster sparsity of edges. The generator generates a time series
+of random graphs $G_0, G_1, ..., G_n$, where $G_t$ emerges from $G_{t-1}$ via
+successive atomic updates like for instance, the insertion of a vertex or the removal of an
+edge. The generator monitors the (dynamic) ground truth clustering and the probability
+of the atomic events is chosen in such a way that the ground truth clustering is
+maintained while the randomness of the generated grpah is kept.
 

### 2018-11-09 data_sets.tex
Fixed text to comply with plagiarism requirements

@@
 
-Besides graph data generators, many graph algorithms and systems are benchmarked using real-world graph data sets, including new graph data generation techniques.
-In this section, we review the most widely used graph datasets in the literature and their purpose.
+Besides graph data generators, many graph algorithms and systems are benchmarked
+using real-world graph data sets, including new graph data generation
+techniques. In this section, we review those graph datasets most widely used in
+the literature and their purpose.
 
@@
   \item \textbf{Amazon}~\cite{yang2015defining}: Represents a product co-purchasing
-    network, such that each vertex is a product and an edge between two products
-    exists if a person has bought the two products.
+    network, such that each vertex represents a product while edges between two products
+    exists if a person bought both of them.
   \item \textbf{Road networks}~\cite{leskovec2009community}: Consist of a set of road
@@
   \item \textbf{LiveJournal}~\cite{yang2015defining}: A social network where vertices
-    represent the users and the edges represent the acquitances between them.
+    represent the users and the edges the acquitances between them.
   \item \textbf{Orkut}~\cite{yang2015defining}: Like LiveJournal, this is a social network
-    where vertices represent persons and the edges represent their friendships.
+    where vertices represent persons and the edges their friendships.
   \item \textbf{Twitter}~\cite{kwak2010twitter}: This is a directed network representing
@@
       which are labelled, the ratings between them.
-    \item \textbf{Wikipedia RFA}~\cite{west2014exploiting}: This is a network extracted
-      from Wikipedia, where the vertices represent users  and the
+    \item \textbf{Wikipedia RFA}~\cite{west2014exploiting}: This network is extracted
+      from Wikipedia and the vertices represent users  while the
       edges, which are labelled, the votes emitted by administrators for the
@@
     together. The books have labels of whether they are left or right oriented.
-  \item \textbf{Football}~\cite{girvan2002network}: A network of American university
-    football teams. Each node represents a football team and the edges represent
-    the matches between them during the season. Each team is associated to a
+  \item \textbf{Football}~\cite{girvan2002network}: This network represent American university
+    football teams. Each node is a football team and the edges are those 
+    games between teams during the season. Each team is associated to a
     division.
@@
   \item \textbf{Freebase}~\cite{bollacker2008freebase}: This is a collaborative knowledge base
-    made of metadata that is mainly provided by community members. It contains
+    made of metadata maintained by community members. It contains
     structured data from multiple sources in an attempt to create a global
@@
     collaboratively edited by the community and hosted by the Wikimedia
-    Foundation. It contains structured data from its sister projects Wikipedia,
-    Wikivoyage, Wikisource and others.
+    Foundation. It contains structured data from other related projects such as Wikipedia,
+    Wikivoyage or Wikisource.
   \item \textbf{Billion Triple Challenge}~\cite{btc-2014}: This is a semantic dataset

### 2018-11-09 generators_analytics.tex
Fixed text to comply with plagiarism requirements

@@
 
-\paragraph{HPC Scalable Graph Analysis Benchmark} The HPC Scalable Graph Analysis Benchmark~\cite{HPCgraph,Bader:2005:DIH:2099301.2099360} consists of a weighted, directed graph that follows a power-law distribution and four related analysis techniques (namely graph construction, graph extraction with BFS, classification of large vertex sets, and graph analysis with betweenness centrality).
-The generator has the following parameters: number of vertices, number of edges, and maximum weight of an edge.
-It outputs a list of tuples containing identifiers of vertices of an edge (with the direction from the first one to the second one) and weights (positive integers  with a uniform random distribution) assigned to the edges of the multigraph.
-The algorithm of the generator is based on R-MAT.
-To avoid data locality, in the final step the vertex numbers are randomly permuted and then the tuples are randomly shuffled.
-A related project from the same authors developed for the 9th DIMACS Shortest Paths Challenge is GTgraph~\cite{GTgraph}.
-It involves three types of graphs: (1) Erd\"{o}s-R\'{e}nyi random graphs, (2) input graph instances used in the DARPA HPCS SSCA\#2 graph theory benchmark (version 1.0), and (3) small-world graphs based on the R-MAT model.
+\paragraph{HPC Scalable Graph Analysis Benchmark} The HPC Scalable Graph
+Analysis Benchmark~\cite{HPCgraph,Bader:2005:DIH:2099301.2099360} consists of a
+weighted, directed graph that follows a power-law distribution and four related
+analysis techniques (namely graph construction, graph extraction with BFS,
+                     classification of large vertex sets, and graph analysis
+                     with betweenness centrality). The generator has the
+following parameters: the number of vertices, the number of edges, and maximum weight of
+an edge. It outputs a list of tuples containing identifiers of vertices of an
+edge (with the direction from the first one to the second one) and weights
+(positive integers  with a uniform random distribution) assigned to the edges of
+the multigraph.  The algorithm of the generator is based on R-MAT. To reduce the data
+locality, the vertex ids are randomly permuted and the output
+tuples are shuffled. A related project from the same authors
+developed for the 9th DIMACS Shortest Paths Challenge is GTgraph~\cite{GTgraph}.
+It involves three types of graphs: (1) Erd\"{o}s-R\'{e}nyi random graphs, (2)
+different graphs from the DARPA HPCS SSCA\#2 graph theory benchmark
+(version 1.0), and (3) small-world graphs generated using the R-MAT graph
+generator.
 

### 2018-11-09 generators_community_detection.tex
Fixed text to comply with plagiarism requirements

@@
 years with tens of developed algorithms and detection
-strategies~\cite{doi:10.1002/wics.1403,Kim:2015:CDM:2854006.2854013}. In order
-to compare the quality of the different proposed techniques, one needs graphs
+strategies~\cite{doi:10.1002/wics.1403,Kim:2015:CDM:2854006.2854013}. For
+comparing the quality of the different proposed techniques, one needs graphs
 with \emph{reference communities}, that is, communities known beforehand. Since
@@
 nodes is also sampled from a power-law distribution. Additionally, the generator
-introduces the concept of the ``mixing factor'', which specifies the fraction of
-its links connecting nodes belonging to different communities. Such parameter
+introduces the concept of the ``mixing factor'', which consists of the fraction of
+edges in the graph connecting nodes that belong to different communities. Such parameter
 allows  the degree of modularity of the generated graph  to be tuned, thus

### 2018-11-09 generators_streaming.tex
Fixed text to comply with plagiarism requirements

@@
 \label{sec:generators_streaming}
-One way for dealing with big graphs is to process them using the \emph{streaming} mode where the data stream could consist of the edges of the graph.
-In this mode, the graph processing algorithms can process the input stream in the order it arrives while using only a limited amount of memory~\cite{mcgregor2014graph}.
+One way for dealing with big graphs is to process them using the
+\emph{streaming} mode where the data stream could consist of the edges of the
+graph. In this mode, the graph processing algorithms can process the input
+stream in the order it arrives while using only a limited amount of
+memory~\cite{mcgregor2014graph}.
 
-\paragraph{S2Gen}  The streaming mode has mainly  attracted the attention of the RDF and Semantic Web community.
-Thus, Phuoc et al.~\cite{le2012linked} presented an evaluation framework for linked stream data processing engines.
-The framework uses a data generator for the Stream Social network data Generator (S2Gen) that simulates what users continuously generate on their social network activities (e.g., posts) in addition to the  user metadata such as users' profile information, social network relationships, posts, photos and GPS information.
-The data generator of this framework provides the users the flexibility to control the characteristics of the generated data by tanning a range of parameters including the period in which the social activities are generated (generating period), the maximum number of posts/comments/photos for each user per week and the correlation probabilities between the different objects (e.g., users) in the social network.
+\paragraph{S2Gen}  The streaming mode has mainly  attracted the attention of the
+RDF and Semantic Web community. Thus, Phuoc et al.~\cite{le2012linked} presented
+an evaluation framework for linked stream data processing engines. The framework
+uses a datasets generated with the Stream Social network data Generator
+(S2Gen), which 
+simulates streams of user interactions (or events) in social networks 
+(e.g., posts) in addition to the  user metadata such as users' profile
+information, social network relationships, posts, photos and GPS information.
+The data generator of this framework provides the users the flexibility to
+control the characteristics of the generated stream by tanning a range of
+parameters, which includes the frequency at which interactions are generated, 
+limits such as the maximum number of messages per user
+and week, and the correlation probabilities between the different objects (e.g.,
+users) in the social network.
 
-\paragraph{RSPLab} Tommasini et al.~\cite{tommasini2017rsplab} introduced another framework for benchmarking RDF Stream Processing systems, RSPLab.
-The Streamer component of this framework is designed to publish RDF streams from the various existing RDF benchmarks (e.g., BSBM, LUBM) (see Section~\ref{sec:generators_LinkedData}).
-In particular, the Streamer  component uses TripleWave\footnote{\url{http://streamreasoning.github.io/TripleWave/}}, an open-source framework for publishing and sharing RDF streams on the Web~\cite{mauri2016triplewave}.
-TripleWave acts as a mean for plugging-in diverse Web data sources and for consuming streams in both push and pull mode.
+\paragraph{RSPLab} Tommasini et al.~\cite{tommasini2017rsplab} introduced
+another framework for benchmarking RDF Stream Processing systems, RSPLab. The
+Streamer component of this framework is designed to publish RDF streams from the
+various existing RDF benchmarks (e.g., BSBM, LUBM) (see Section~\ref{sec:generators_LinkedData}).
+In particular, the Streamer  component uses TripleWave\footnote{\url{http://streamreasoning.github.io/TripleWave/}}, an
+open-source framework for publishing and sharing RDF streams on the
+Web~\cite{mauri2016triplewave}.   TripleWave acts as a means for plugging-in
+and combining streams from multiple Web data sources, in both push and pull mode.

### 2018-11-10 challenges.tex
Minor corrections befor re-submitting

@@
 of the atomic events is chosen in such a way that the ground truth clustering is
-maintained while the randomness of the generated grpah is kept.
+maintained while the randomness of the generated graph is kept.
 

### 2018-11-10 data_sets.tex
Minor corrections befor re-submitting

@@
   \item \textbf{Amazon}~\cite{yang2015defining}: Represents a product co-purchasing
-    network, such that each vertex represents a product while edges between two products
+    network, such that each vertex represents a product, while edges between two products
     exists if a person bought both of them.
@@
   \item \textbf{LiveJournal}~\cite{yang2015defining}: A social network where vertices
-    represent the users and the edges the acquitances between them.
+    represent the users and the edges the acquittances between them.
   \item \textbf{Orkut}~\cite{yang2015defining}: Like LiveJournal, this is a social network
@@
 algorithms are typically evaluated on networks with explicit user rankings or
-votings from other users, being the most widely used datasets the following
+voting from other users, being the most widely used datasets the following
 examples:
@@
     \item \textbf{Wikipedia RFA}~\cite{west2014exploiting}: This network is extracted
-      from Wikipedia and the vertices represent users  while the
+      from Wikipedia and the vertices represent users, while the
       edges, which are labelled, the votes emitted by administrators for the
-      user to become an administrator.  Each vote is accompained with a text
+      user to become an administrator.  Each vote is accompanied with a text
       explaining the vote's sign.
@@
     together. The books have labels of whether they are left or right oriented.
-  \item \textbf{Football}~\cite{girvan2002network}: This network represent American university
-    football teams. Each node is a football team and the edges are those 
-    games between teams during the season. Each team is associated to a
+  \item \textbf{Football}~\cite{girvan2002network}: This network represents American university
+    football teams. Each node is a football team and the edges are games between teams during the season. Each team is associated to a
     division.

### 2018-11-10 generators_LinkedData.tex
Minor corrections befor re-submitting

@@
 The authors focus mainly on the  \emph{structuredness} (\emph{coherence}) of each benchmark dataset claiming that a primitive metric (e.g., the number of triples or the average in/outdegree) quantifies only some specific aspect of each dataset.
-The degree of structuredness of a dataset $D$ with respect to a type $T$ is based on  the regularity of instance data in $D$ on conforming to type $T$.
+The degree of structuredness of a dataset $D$ with respect to a type $T$ is based on  the regularity of instance data in $D$ in conforming to type $T$.
 The type system is extracted from the data set by finding the RDF triples that have property  \texttt{http://www.w3.org/1999/02/22-rdf-syntax-ns\#type} and extract type $T$ from their object.
@@
 The proposed dataset creation process starts with an input dataset.
-Multiple Datasets with different sizes  are then generated by duplicating all triples and changing their namespaces.
+Multiple datasets with different sizes  are then generated by duplicating all triples and changing their namespaces.
 For generating smaller datasets, an appropriate fraction of all triples is selected randomly or by sampling across classes in the dataset.
@@
 \paragraph{Geographica} The Geographica benchmark\footnote{\url{http://geographica.di.uoa.gr/}} has been designed to target the area of geospatial data~\cite{DBLP:conf/semweb/GarbisKK13} and respective SPARQL extensions GeoSPARQL~\cite{battle2012enabling} and stSPARQL~\cite{koubarakis2010modeling}.
-The benchmark involves a real-world workload based on openly available datasets that cove a range of geometry types (e.g., points, lines, polygons) and  a synthetic workload.
+The benchmark involves a real-world workload based on openly available datasets that cover a range of geometry types (e.g., points, lines, polygons) and  a synthetic workload.
 In the former case there is a (1) a micro benchmark that tests primitive spatial functions (involving 29 queries) and (2) macro benchmark that tests the performance of RDF stores in typical application scenarios like reverse geocoding or map search and browsing (consisting of 11 queries).
@@
 Three evaluation metrics are utilized for this purpose: dataset coherence (i.e., a measure how uniformly predicates are distributed among the same type/class), relationship specialty (i.e., the number of occurrences of the same predicate associated with each resource), and literal diversity.\fi A query generation process has been implemented to produce 5 different types of queries (edge-based queries, node-based queries, path queries, star queries, subgraph queries) for any generated data.
-The benchmark project FEASIBLE~\cite{Saleem2015} is also an application-specific benchmark; however, contrary to RBench, it is designed to produce benchmarks from a set of queries (in particular from query logs) by relying on example queries of a user-defined
+The benchmark project FEASIBLE~\cite{Saleem2015} is also an application-specific benchmark; however, contrary to RBench, it is designed to produce benchmarks from a set of queries (in particular from query logs) by relying on sample queries of a user-defined
 size from the input set of queries.

### 2018-11-10 generators_SocialNetworks.tex
Minor corrections befor re-submitting

@@
 On the other hand, diameter shrinking is not observed in Epinions activity graph and there is a difference in degree
-correlation (i.e., frequency of mutual connections of similar nodes) -- linkage graphs have positive, activity graphs neutral degree correlation.
+correlation (i.e., frequency of mutual connections of similar nodes) -- linkage graphs have positive degree correlation, activity graphs have neutral degree correlation.
 With regards to the findings, the proposed generator focusses on linkage graphs with positive degree correlation.
-For this purpose it extends the forest fire spreading process algorithm~\cite{Leskovec:2005:GOT:1081870.1081893} with
-link symmetry.
-It has two parameters the \emph{burning probability} $P_b$ and \emph{symmetry probability} $P_s$.
+For this purpose it extends the forest fire spreading process algorithm~\cite{Leskovec:2005:GOT:1081870.1081893} with link symmetry.
+It has two parameters: the \emph{burning probability} $P_b$ and the \emph{symmetry probability} $P_s$.
 $P_b$ ensures a BFS-based forward burning process in which fire burns strongly with $P_b$ approaching 1.
@@
 
-\paragraph{LDBC SNB} Despite having a common Facebook-like dataset, thanks to three distinct workloads the Social Network Benchmark (SNB)~\cite{Erling:2015:LSN:2723372.2742786} provided by LDBC corresponds to three distinct benchmarks.
+\paragraph{LDBC SNB} Despite having a common Facebook-like dataset, thanks to three distinct workloads the Social Network Benchmark (SNB)~\cite{Erling:2015:LSN:2723372.2742786} provided by LDBC represents three distinct benchmarks.
 The network nodes correspond to people and the edges represent their friendship and messages they post in discussion trees on their forums.

### 2018-11-25 comparison.tex
Sherif Changes

@@
 
-In order to provide the reader with a quick preview of the generators and thus to enable finding the target solutions easily, we start the survey with a  classification and comparative study of the existing tools.
+In order to provide the reader with a quick preview of the generators and  to enable finding the target solutions easily, we start the survey with a  classification and comparative study of the existing tools.
 In general, there are various ways to classify them.
@@
 For example,~\cite{DBLP:conf/sdm/ChakrabartiZF04} introduces two categories -- degree-based and procedural generators.
-Given a degree distribution (typically following a power law), \emph{degree-based generators} (e.g., Barabasi-Albert model~\cite{Barabasi99emergenceScaling}) try to find a graph that matches it, but without giving any insights about the graph or trying to match other criteria (like, e.g., small diameter, eigenvalues etc.).
-On the other hand, \emph{procedural generators} (e.g., R-MAT~\cite{DBLP:conf/sdm/ChakrabartiZF04}) try to find simple mechanisms to generate graphs that match a property of the real graphs and, typically, the power law degree distribution.
+In general, \emph{degree-based generators} (e.g., Barabasi-Albert model~\cite{Barabasi99emergenceScaling}) are commonly attempting to find a graph that matches it, but without providing any information about the graph or attempting to match other graph features (e.g., eigenvalues, small diameter, ..., etc).
+On the other hand, \emph{procedural generators} (e.g., R-MAT~\cite{DBLP:conf/sdm/ChakrabartiZF04}) are commonly targeting simple techniques to produce graphs that the are matching the characteristics of the real graphs (e.g., the power law degree distribution).
 

### 2018-11-25 generators_LinkedData.tex
Sherif Changes

@@
 \label{sec:generators_LinkedData}
-With the dawn of the concept of Linked Data it is a natural development that there would emerge respective benchmarks involving both real-world data sets and synthetic data sets with real-world characteristics.
+With the dawn of the concept of Linked Data it is a natural development that there would emerge respective benchmarks involving both synthetic data and real-world data sets  sets with real-world characteristics.
 The used data sets correspond to RDF representation of relational-like data~\cite{Guo2005158,Bizer09theberlin}, social network-like data~\cite{Schmidt2010}, or specific and significantly more complex data structures such as biological data~\cite{Wu2014}.
@@
 \paragraph{LUBM} The use-case driven Lehigh University Benchmark (LUBM)\footnote{\url{http://swat.cse.lehigh.edu/projects/lubm/}} considers the university domain.
-The ontology defines 43 classes and 32 properties, including 25 object properties and 7 datatype properties~\cite{Guo2005158}.
-The LUBM benchmark also provides 14 test queries.
-The authors focus on \emph{extensional} queries, i.e., queries about the instance data over ontologies, as an opposite to \emph{intentional} queries (i.e., queries about classes and properties).
-The Univ-Bench Artificial  (UBA) data generator features random and repeatable data generation (exploiting classical linear congruential generator, LCG, of numbers).
-In particular, data generated by the tool are assigned zero-based indexes (i.e., the first university is named University0 and so on), thus they are reproducible at any time with the same indexes.
+The ontology defines 43 classes and 32 properties~\cite{Guo2005158}.
+In addition, the LUBM benchmark provides 14 test queries.
+In particular, the benchmark focuses on \emph{extensional} queries, i.e., queries which target the instance data over ontologies, as an opposite to \emph{intentional} queries, i.e., queries which target the properties and  classes of the ontology.
+The Univ-Bench Artificial  (UBA) data generator features repeatable and random  data generation (exploiting classical linear congruential generator, LCG, of numbers).
+In particular, the data which is generated by the tool are assigned zero-based indexes (i.e., the first university is named University0 and so on), thus they are reproducible at any time with the same indexes.
 The generator allows to specify a seed for random number generation, along with the desired number of universities, and the starting index of the universities.

### 2018-11-25 generators_general.tex
Minor corrections befor re-submitting
Sherif Changes

@@
 The generator is recursive and employs a fairly small number of parameters.
-In principle, the strategy of this generator is to achieve simple means to generate graphs that match
+In principle, the strategy of this generator is to achieve simple means to produce graphs that are matching 
 the properties of the real graphs.
-In particular, the design goals of R-MAT is to generate graphs that match the degree distributions, imitate a community structure and have a small diameter.
+In particular, the design goals of R-MAT is to produce graphs which mimics the degree distributions, imitate a community structure and have a small diameter.
 R-MAT can generate weighted, directed and bipartite graphs.
@@
 GraphGen\footnote{https://www.cse.ust.hk/graphgen/}. It relies on data generation code for associations and sequential
-patterns provided by IBM \footnote{From 1996, no longer available at
+patterns provided by IBM\footnote{From 1996, no longer available at
 \url{http://www.almaden.ibm.com/cs/projects/iis/hdb/Projects/data

### 2018-11-25 generators_LinkedData.tex
Sherif Changes

@@
 The Univ-Bench Artificial  (UBA) data generator features repeatable and random  data generation (exploiting classical linear congruential generator, LCG, of numbers).
-In particular, the data which is generated by the tool are assigned zero-based indexes (i.e., the first university is named University0 and so on), thus they are reproducible at any time with the same indexes.
+In particular, the data which is produced by the generator are assigned zero-based indexes (i.e., the first university is named \emph{University0} and so on), thus they are reproducible at any time with the same indexes.
 The generator allows to specify a seed for random number generation, along with the desired number of universities, and the starting index of the universities.
@@
 An extension of LUBM, the Lehigh BibTeX Benchmark (LBBM)~\cite{Wang2005}, enables generating synthetic data for different ontologies.
-The generation is divided into two phases: (1) the property-discovering phase, and (2) the data generation phase.
-The authors present a probabilistic model that can emulate the properties of the data of a particular domain and generate synthetic data exhibiting similar properties.
+The data generation process is managed through two main phases: (1) the property-discovery phase, and (2) the data generation phase.
+In particular, LBBM provides a probabilistic model that can emulate the properties of the data of a particular domain and generate synthetic data exhibiting similar properties.
 A Monte Carlo algorithm is employed to output synthetic data.
@@
 \paragraph{IIMB} Contrary to the previous work, Ferrara et al.~\cite{Ferrara08OM} proposed the ISLab Instance Matching Benchmark (IIMB)\footnote{\url{http://www.ics.forth.gr/isl/BenchmarksTutorial/}} for the problem of instance matching.
-Given two instances $i_1$ and $i_2$ adhering to the same ontology or to different ontologies, instance matching is defined as a function $Im(i_1, i_2) \rightarrow \{0, 1\}$,  where $i_1$ and $i_2$ can be mapped to the same real-world object (in which case the function maps to $1$) or $i_1$ and $i_2$ are referred to different objects (in which case the function maps to $0$).
+For any two objects $o_1$ and $o_2$ adhering to the same ontology or to different ontologies, instance matching is specified in the form of a function $Om(o_1, o_2) \rightarrow \{0, 1\}$,  where $o_1$ and $o_2$ are linked to the same real-world object (in which case the function maps to $1$) or $o_1$ and $o_2$ are representing different objects (in which case the function maps to $0$).
 It targets the domain of movie data which contains 15 named classes, along with 5 object properties and 13 datatype properties.
@@
 
-\paragraph{BSBM} The Berlin SPARQL Benchmark (BSBM)\footnote{\url{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}}, is centered around an e-commerce domain where types Product, Offer and Vendor model the relationships between products and the vendors offering them, while types Person and Review model the relationships between users and product reviews written by these users~\cite{Bizer09theberlin}.
-The benchmark comes equipped with 12 queries and 2 query mixes (sequences of the 12 queries) emulating the navigation pattern and search of a consumer seeking a product.
-The data generator is capable of producing arbitrarily large datasets using the number of products $n$ as scale factor.
+\paragraph{BSBM} The Berlin SPARQL Benchmark (BSBM)\footnote{\url{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}}, is centered around an e-commerce application domain with object types such as \emph{Customer}, \emph{Vendor}, \emph{Product} and \emph{Offer} in addition to the relationship among them~\cite{Bizer09theberlin}.
+The benchmark provides a workload that have 12 queries with 2 types of query workloads (i.e., 2 sequences of the 12 queries) emulating the navigation pattern and search of a consumer seeking a product.
+The data generator is capable of producing arbitrarily scalable datasets by controlling the number of products ($n$) as a scale factor.
 The scale factor also impacts other data characteristics, such as, e.g., the depth of type hierarchy of products (defined as $d = round(log_{10}(n))/2 + 1$), branching factor ($bfr = 2 \times round(log_{10}(n))$), the number of product features (having $lowerBound = 35 \times i / (d \times (d+1)/2 - 1)$ and $upperBound = 75 \times i / (d \times (d+1)/2 - 1)$) etc.
@@
 In particular, the data mimics the correlations between entities.
-All random functions of the generator is based on a fixed seed that ensures the data generation process to be deterministic.
-SP$^2$Bench is accompanied by 12 queries covering different operator constellations such as RDF access paths and typical RDF constructs.
+All random functions of the generator use a fixed seed that ensures the data generation process is deterministic.
+SP$^2$Bench is accompanied by 12 queries covering the various types of operators such as RDF access paths in addition to typical RDF constructs.
 
@@
 WordNet~\cite{Miller:1995:WLD:219717.219748}) has been reported by~\cite{Duan:2011:AOC:1989323.1989340}.
-The authors focus mainly on the  \emph{structuredness} (\emph{coherence}) of each benchmark dataset claiming that a primitive metric (e.g., the number of triples or the average in/outdegree) quantifies only some specific aspect of each dataset.
+The authors focus mainly on the  \emph{structuredness} (\emph{coherence}) of each benchmark dataset claiming that a primitive metric (e.g., the number of triples or the average in/outdegree) quantifies only some target characteristics of each dataset.
 The degree of structuredness of a dataset $D$ with respect to a type $T$ is based on  the regularity of instance data in $D$ in conforming to type $T$.
@@
 The structuredness is then expressed as a weighted sum of share of set properties of each type, whereas higher weights are assigned to types with more instances.
-The authors show that the structuredness of the chosen benchmarks is fixed, whereas real-world RDF datasets lie in currently untested parts of the spectrum.
-As a consequence, they introduce a new benchmark that accepts as input any dataset associated with a required level of structuredness and size (smaller than the size of the original data), and exploits the input documents as a seed to generate a subset of the original data with the target structuredness and size.
+The authors show that the structuredness of the chosen benchmarks is fixed, whereas real-world RDF datasets are belonging to the non-tested area of the spectrum.
+As a consequence, they introduce a new benchmark that receives as input any dataset associated with a required level of structuredness and size (smaller than the size of the original data), and exploits the input documents as a seed to produce a subset of the original data with the target structuredness and size.
 In addition, they show that structuredness and size mutually influence each other.
 
-\paragraph{DBPSB} DBpedia SPARQL Benchmark (DBPSB)\footnote{\url{http://aksw.org/Projects/DBPSB.html}} proposed at the University of Leipzig is based on queries that have been issued by humans and applications
-against existing RDF data~\cite{Morsey2011,Morsey:2012:UBR:2900929.2901031}.
-In addition, the authors argue that benchmarks like LUBM, BSBM, or SP$^2$Bench resemble relational database benchmarks involving relational data structures with few and homogeneously structured classes, whereas RDF knowledge bases are increasingly heterogeneous.
+\paragraph{DBPSB} DBpedia SPARQL Benchmark (DBPSB)\footnote{\url{http://aksw.org/Projects/DBPSB.html}} proposed at the University of Leipzig has been designed using workloads that have been issued by humans and applications over existing RDF data~\cite{Morsey2011,Morsey:2012:UBR:2900929.2901031}.
+In addition, the authors argue that benchmarks like LUBM, BSBM, or SP$^2$Bench resemble relational database benchmarks involving relational data structures with few and homogeneously structured classes, whereas, in reality, RDF datasets are increasingly heterogeneous.
 For example, DBpedia version 3.6 consists of 289,016 classes of which 275 classes are defined based on the DBpedia ontology.
@@
 used in property values.
-Hence, they presented a generic SPARQL benchmark creation approach which is based on a flexible data generation mechanism that mimics the input data source.
-The proposed dataset creation process starts with an input dataset.
-Multiple datasets with different sizes  are then generated by duplicating all triples and changing their namespaces.
+Hence, they presented a universal SPARQL benchmark generation approach which uses a flexible data production mechanism that mimics the input data source.
+This dataset generation process begins using an input dataset then multiple datasets with different sizes  are then generated by duplicating all the RDF triples with changing their namespaces.
 For generating smaller datasets, an appropriate fraction of all triples is selected randomly or by sampling across classes in the dataset.

### 2018-11-25 generators_LinkedData.tex
Sherif Changes

@@
 This dataset generation process begins using an input dataset then multiple datasets with different sizes  are then generated by duplicating all the RDF triples with changing their namespaces.
-For generating smaller datasets, an appropriate fraction of all triples is selected randomly or by sampling across classes in the dataset.
-\iffalse The goal of the query analysis and clustering is to detect prototypical queries on the basis of their frequent usage and similarity.\fi The methodology is applied on the DBpedia SPARQL endpoint and a set of 25 SPARQL query templates is derived, that cover the most commonly used SPARQL features.
+For generating smaller datasets, an adequate selection of all triples is selected randomly or using a sampling mechanism over the various classes in the dataset.
+\iffalse The goal of the query analysis and clustering is to detect prototypical queries on the basis of their frequent usage and similarity.\fi The methodology is applied on the DBpedia SPARQL endpoint and a set of 25 SPARQL query templates is derived, that cover the frequently used SPARQL features.
 
@@
 
-\paragraph{SIB} The developers of the Social Network Intelligence BenchMark (SIB)\footnote{\url{https://www.w3.org/wiki/Social_Network_Intelligence_BenchMark}} based the design of their benchmark based on the claim that existing benchmarks are limited in reflecting the characteristics of the real RDF datasets and are mostly relational-like.
-Hence, they proposed a benchmark for  query processing over real graphs~\cite{sib}.
-The proposed benchmark simulates an RDF backend of a social network site where users and their interactions form a social graph of social activities such as creating/managing groups, writing posts and posting comments.
-The distribution of generated data on each relation follows the data distribution inferred from real-world social networks.
-In addition, association rules are included in order to convey the real-world data correlation into synthetic data.
+\paragraph{SIB} The developers of the Social Network Intelligence BenchMark (SIB)\footnote{\url{https://www.w3.org/wiki/Social_Network_Intelligence_BenchMark}} based the design of their benchmark based on the claim that existing benchmarks are limited in reflecting the characteristics of the real RDF databases and are mostly focusing on the relational style aspects.
+Hence, they proposed a benchmark for  query evaluation using real graphs~\cite{sib}.
+The proposed benchmark mimics using an RDF store for a social network.
+\iffalse site where users and their interactions form a social graph of social activities such as creating/managing groups, writing posts and posting comments.\fi The distribution of the generated data for each type follows the  distribution of the associated type inferred from real-world social networks.
+Additionally, association rules are exploited for representing the real-world data correlation in the generated synthetic data.
 The  generated data is linked with the RDF datasets from DBpedia.
@@
 \paragraph{Geographica} The Geographica benchmark\footnote{\url{http://geographica.di.uoa.gr/}} has been designed to target the area of geospatial data~\cite{DBLP:conf/semweb/GarbisKK13} and respective SPARQL extensions GeoSPARQL~\cite{battle2012enabling} and stSPARQL~\cite{koubarakis2010modeling}.
-The benchmark involves a real-world workload based on openly available datasets that cover a range of geometry types (e.g., points, lines, polygons) and  a synthetic workload.
-In the former case there is a (1) a micro benchmark that tests primitive spatial functions (involving 29 queries) and (2) macro benchmark that tests the performance of RDF stores in typical application scenarios like reverse geocoding or map search and browsing (consisting of 11 queries).
-In the latter case of a synthetic workload the generator produces synthetic datasets of various sizes that corresponds to an ontology based on OpenStreetMap (i.e., states in a country, land ownership, roads and  points of interest) and instantiates query templates.
-The spatial extent of the land ownership dataset constitutes a uniform grid of $n \times n$ hexagons, whereas the size of each dataset is given relatively to $n$.
-The synthetic workload generator produces SPARQL queries corresponding to spatial selection and spatial joins by instantiating 2 query templates.
+The benchmark involves a real-world workload that uses openly available datasets that cover a range of geometry types (e.g., points, lines, polygons) and  a synthetic workload.
+In the former case there is a (1) a micro benchmark that tests primitive spatial functions (involving 29 queries) and (2) macro benchmark that tests the performance of RDF engines in various application scenarios such as  map exploring and search (consisting of 11 queries).
+In the latter case of a synthetic workload the generator produces synthetic datasets of different sizes that corresponds to an ontology based on OpenStreetMap  and instantiates query templates.
+\iffalse The spatial extent of the land ownership dataset constitutes a uniform grid of $n \times n$ hexagons, whereas the size of each dataset is given relatively to $n$.\fi The generated SPARQL query workload is corresponding to spatial selection and spatial joins by instantiating 2 query templates.
 
-\paragraph{WatDiv} The Waterloo SPARQL Diversity Test Suite (WatDiv)\footnote{\url{http://dsg.uwaterloo.ca/watdiv/}} developed at the University of Waterloo provides stress testing tools to address the observation that existing SPARQL benchmarks are not suitable for testing systems for diverse queries and varied workloads~\cite{Aluc:2014:DST:2717213.2717229}.
-The benchmark introduces two classes of query features -- structural and data-driven -- and performs a detailed analysis on existing SPARQL benchmarks (LUBM, BSBM, SP$^2$Bench, and DBPSB) using the two classes of query features.
+\paragraph{WatDiv} The Waterloo SPARQL Diversity Test Suite (WatDiv)\footnote{\url{http://dsg.uwaterloo.ca/watdiv/}} has been designed at the University of Waterloo.
+It implements stress testing tools that focus on addressing the observation that existing SPARQL benchmarks are not adequate for evaluating systems using a verity of queries and  workloads~\cite{Aluc:2014:DST:2717213.2717229}.
+The benchmark focuses on two types of query aspects -- structural and data-driven -- and performs a detailed analysis on existing SPARQL benchmarks (LUBM, BSBM, DBPSB, and SP$^2$Bench) using the two classes of query features.
 The structural features involve triple pattern count, join vertex count, join vertex degree, and join vertex count.
@@
 The analysis of the four benchmarks reveals that they are not sufficiently diverse to evaluate the strengths and weaknesses of the various physical design alternatives that have been implemented by the different RDF systems.
-The proposed solution, WatDiv, involves (1) a data generator which generates scalable datasets according to the WatDiv schema, (2) a query template generator which traverses the WatDiv schema and generates a diverse set of query templates, (3) a query generator which instantiates the templates with actual RDF terms from the dataset, and (4) a feature extractor which extracts the structural features of the generated data and workload.
+In particular, WatDiv, provides (1) a data generator which generates scalable datasets according to the WatDiv schema, (2) a query template generator which follows the WatDiv schema and produces a  set of query templates, (3) a query generator that uses the generated templates and instantiates them  with real RDF values from the dataset, and (4) a feature extractor which extracts the structural features of the generated data and workload.
 %For the study in the paper the authors generated 12,500 test queries from 125 query templates.
@@
 
-\paragraph{LDBC}  The Linked Data Benchmark Council\footnote{\url{http://ldbcouncil.org/industry/organization/origins}} (LDBC)~\cite{Angles:2014:LDB:2627692.2627697} is a result of a (closed) EU project that brought together a community of academic researchers and industry that had the main objective of developing an open source, yet industrial grade benchmarks for graph and RDF databases.
+\paragraph{LDBC}  The Linked Data Benchmark Council\footnote{\url{http://ldbcouncil.org/industry/organization/origins}} (LDBC)~\cite{Angles:2014:LDB:2627692.2627697} is a result of a (closed) EU project that brought together a community of academic researchers and industry that had the goal of developing an open source, yet industrial grade benchmarks for RDF and graph databases.
 \iffalse The following three benchmarks were developed and are currently maintained.\fi In the Semantic Web domain, the project released the Semantic Publishing Benchmark (SPB)~\cite{spb} that has been inspired by the Media/Publishing industry (namely BBC\footnote{\url{http://www.bbc.com/}}).
@@
 The generator is designed to receive a vocabulary as an input  and supports two statistical distributions for generating entities: Gaussian distribution and Zipf's power-law distribution.
-LinkGen can augment the generated data with inconsistent and noisy  data such as writing two conflicting values for a given datatype property,  adding triples with syntactic errors, adding wrong statements by assigning them with invalid domain and creating instances with no type information.
-The generator is also designed with  an option to inter-link the generated instances with real ones given that the user provides entities from real datasets.
+LinkGen can augment the generated data with inconsistent and noisy  data such as updating a given datatype property with two conflicting values or  adding triples with syntactic errors.
+\iffalse, adding wrong statements by assigning them with invalid domain and creating instances with no type information.\fi The generator also provides a feature to inter-link the generated objects with real ones given that the end-user provides entities from real datasets.
 The datasets can be generated in any of of two modes: on-disk and streaming.

### 2018-11-25 generators_GraphDatabases.tex
Minor corrections befor re-submitting
Sherif Changes

@@
 \cite{Dominguez-Sal:2010:DDG:1946050.1946053} discussed this question and related topics.
-On the basis of a review of applications of graph databases (namely social network analysis, proteomics or genetic interactions, recommendation systems, and travel planning and routing), the authors analyzed and discussed the characteristics of the graphs that appear in such applications and how they could influence benchmarking, different types of operations used in these applications and the characteristics of the evaluation setup of the benchmark.
+On the basis of a review of applications of graph databases (namely, social network analysis,  genetic interactions, recommendation systems, and travel planning and routing), the authors analyzed and discussed the characteristics of the graphs that appear in such applications and how they could influence benchmarking, different types of operations used in these applications and the characteristics of the evaluation setup of the benchmark.
 In this section, we focus on graph data generators and benchmarks that have been primarily targeting graph DBMSs.
@@
 The \emph{Query workload configuration} describes parameters of the query workload to be generated, by including the number of queries, arity, shape and selectivity of the queries.
-The problem of deciding whether there exists a graph satisfying a given graph configuration $G$ is NP-complete. The same applies to the problem of deciding 
-whether it exists a query workload compliant with a a given query workload configuration $Q$. In view of this, gMark adopts a best effort approach in which the
+The problem of deciding whether there exists a graph that satisfies a defined graph specification $G$ is NP-complete. The same applies to the problem of deciding
+whether there exists a query workload compliant with a given query workload configuration $Q$. In view of this, gMark adopts a best effort approach in which the
 parameters specified in the configuration files are attained in a relaxed fashion in order to achieve linear running time whenever possible.

### 2018-11-25 generators_SocialNetworks.tex
Sherif Changes

@@
 LDBC-SNB~\cite{Erling:2015:LSN:2723372.2742786}.
-They discover that communities found in different graphs follow quite similar distributions and that communities in a single graph have diverse nature and are difficult to fit with a single model.
+They found out that discovered communities  in different graphs have common distributions and that communities in a single graph have diverse nature and are difficult to fit with a single model.
 
@@
 
-\paragraph{Cloning of Social Networks} Paper~\cite{Sukthankar-SocialInfo2014}
-introduces a synthetic network generator designed for cloning social network
+\paragraph{Cloning of Social Networks} ~\cite{Sukthankar-SocialInfo2014}
+introduced a synthetic network generator designed for cloning social network
 statistics of an existing dataset. The network starts with a small number of

### 2018-11-25 generators_SocialNetworks.tex
Sherif Changes

@@
 
-\paragraph{Towards More Realistic Data} \cite{Nettleton2016} argued that the main body of existing work lies in
+\paragraph{Towards More Realistic Data} \cite{Nettleton2016} argued that the majority of existing work focus on 
 topology generation which approximates the characteristics of a real social
@@
 distribution, small average path length, and community structures), however,  this is usually done without any data. Hence, they
-introduced a general stochastic modeling system which allows the users to
+introduced a general stochastic modeling approach that enables the users to
 populate a graph topology with data. The approach has three steps: (1) topology
@@
 SNAP\footnote{\url{https://snap.stanford.edu/data/}}, (2) data definition
-following distribution profiles, attribute value definitions, using a
+that describes distribution profiles, attribute value definitions, using a
 parameterizable set of data propagation rules and affinities, and (3) data

### 2018-11-25 data_sets.tex
Sherif Changes

@@
   \item \textbf{Orkut}~\cite{yang2015defining}: Like LiveJournal, this is a social network
-    where vertices represent persons and the edges their friendships.
+    where vertices represent persons and the edges represent the friendship relationship between them.
   \item \textbf{Twitter}~\cite{kwak2010twitter}: This is a directed network representing

### 2018-11-25 generators_community_detection.tex
Sherif Changes

@@
 graphs for community detection where communities are of different sizes and
-densities. The generator generates communities of different sizes following a
+densities. The generator generates communities of various sizes following a
 power-law distribution whose parameters can be configured. The degree of the
@@
 generation process starts with an empty graph and incrementally fills in the
-adjacency matrix by obeying the described constraints.
+adjacency matrix by considering the described constraints.
 

### 2018-11-26 challenges.tex
Sherif Changes

@@
 deemed to be more difficult for graph datasets in the presence of noise.
-Since de-noising graph data is difficult to achieve, several machine learning
-techniques have been adapted to work with noise (i.e. mislabeled
+Since de-noising graph data is difficult to achieve, various machine learning-based 
+approaches have been adapted to work with noise (i.e. mislabeled
 samples) or outliers, such as
@@
 Concerning the latter, data quality techniques handling graph data are recently considering ad-hoc
-generation of graph data and graph quality rules in order to assess the
+generation of graph data and graph quality rules in order to evaluate the
 effectiveness of error detection and data repairing algorithms \cite{FanWX16a,AriouaB18}. The

### 2018-11-26 comparison.tex
Sherif Changes

@@
 
-In order to provide the reader with a quick preview of the generators and  to enable finding the target solutions easily, we start the survey with a  classification and comparative study of the existing tools.
+In order to provide the reader with a general preview of the generators and  to enable finding the target solutions easily, we start the survey with a  classification and comparative study of the existing tools.
 In general, there are various ways to classify them.

### 2018-11-26 generators_GraphDatabases.tex
Sherif Changes

@@
 \cite{Dominguez-Sal:2010:DDG:1946050.1946053} discussed this question and related topics.
-On the basis of a review of applications of graph databases (namely, social network analysis,  genetic interactions, recommendation systems, and travel planning and routing), the authors analyzed and discussed the characteristics of the graphs that appear in such applications and how they could influence benchmarking, different types of operations used in these applications and the characteristics of the evaluation setup of the benchmark.
+On the basis of a review of applications of graph databases (namely, social network analysis,  genetic interactions, recommendation systems, and travel planning and routing), the authors analyzed and discussed the features of the graphs for these types of applications and how they could affect the benchmarking process, different types of operations used in these applications and the characteristics of the evaluation setup of the benchmark.
 In this section, we focus on graph data generators and benchmarks that have been primarily targeting graph DBMSs.

### 2018-11-26 generators_LinkedData.tex
Sherif Changes

@@
 The data generator is capable of producing arbitrarily scalable datasets by controlling the number of products ($n$) as a scale factor.
-The scale factor also impacts other data characteristics, such as, e.g., the depth of type hierarchy of products (defined as $d = round(log_{10}(n))/2 + 1$), branching factor ($bfr = 2 \times round(log_{10}(n))$), the number of product features (having $lowerBound = 35 \times i / (d \times (d+1)/2 - 1)$ and $upperBound = 75 \times i / (d \times (d+1)/2 - 1)$) etc.
+The scale factor also impacts other data characteristics, such as, e.g., the depth of type hierarchy of products, branching factor, the number of product features,..., etc.
 BSBM can output two representations, i.e.
@@
 For example, DBpedia version 3.6 consists of 289,016 classes of which 275 classes are defined based on the DBpedia ontology.
-In addition, different datatypes and object references of various types are
+In addition, different data types and object references of the various types are
 used in property values.
@@
 For generating smaller datasets, an adequate selection of all triples is selected randomly or using a sampling mechanism over the various classes in the dataset.
-\iffalse The goal of the query analysis and clustering is to detect prototypical queries on the basis of their frequent usage and similarity.\fi The methodology is applied on the DBpedia SPARQL endpoint and a set of 25 SPARQL query templates is derived, that cover the frequently used SPARQL features.
+\iffalse The goal of the query analysis and clustering is to detect prototypical queries on the basis of their frequent usage and similarity.\fi The methodology is applied on the DBpedia SPARQL endpoint and a set of 25 SPARQL query templates is derived to cover the frequently used SPARQL features.
 
@@
 The benchmark involves a real-world workload that uses openly available datasets that cover a range of geometry types (e.g., points, lines, polygons) and  a synthetic workload.
-In the former case there is a (1) a micro benchmark that tests primitive spatial functions (involving 29 queries) and (2) macro benchmark that tests the performance of RDF engines in various application scenarios such as  map exploring and search (consisting of 11 queries).
+In the former case there is a (1) a micro benchmark that evaluates primitive spatial functions (involving 29 queries) and (2) macro benchmark that tests the performance of RDF engines in various application scenarios such as  map exploring and search (consisting of 11 queries).
 In the latter case of a synthetic workload the generator produces synthetic datasets of different sizes that corresponds to an ontology based on OpenStreetMap  and instantiates query templates.

### 2018-11-26 generators_SocialNetworks.tex
Sherif Changes

@@
 realistic social networks. For this purpose the authors combine both public and private data sets
-with large-scale agent based techniques. The process works as follows: In the first step
-it creates a synthetic population by integrating public and commercial databases. In the second step, it determines a set of activity templates. A 24-hour activity sequence including
+with large-scale agent-based techniques. The process works as follows: In the first step
+it generates a synthetic data by combining public and commercial databases. In the second step, it determines a set of activity templates. A 24-hour activity sequence including
 geolocations is assigned to each synthetic individual.
@@
 has two basic parameters: homophily and link density. A high \emph{homophily}
-value indicates that links are more likely to be formed between nodes with the
-same label; these labels can be viewed as being equivalent to community
+value reflects that links have higher chances to be established among the nodes with the
+same label; these labels can be considered as being equivalent to community
 membership.

### 2018-11-26 generators_analytics.tex
Sherif Changes

@@
 Analysis Benchmark~\cite{HPCgraph,Bader:2005:DIH:2099301.2099360} consists of a
-weighted, directed graph that follows a power-law distribution and four related
+weighted, directed graph that has a power-law distribution and four related
 analysis techniques (namely graph construction, graph extraction with BFS,
@@
                      with betweenness centrality). The generator has the
-following parameters: the number of vertices, the number of edges, and maximum weight of
+following parameters: the number of nodes, the number of edges, and maximum weight of
 an edge. It outputs a list of tuples containing identifiers of vertices of an

### 2018-11-26 generators_community_detection.tex
Sherif Changes

@@
 Community detection is one of the many graph analytics algorithms typically used
-on domains such as social networks or bioinformatics. Communities are groups of
-vertices that are highly connected among them, while being scarcely connected to
+on domains such as social networks or bioinformatics. Communities are groups of nodes that are highly connected among them, while being scarcely connected to
 the rest of the graph. Such communities emerge from the fact that real graphs
@@
 graphs for community detection where communities are of different sizes and
-densities. The generator generates communities of various sizes following a
+densities. The generator generates communities of various sizes with a
 power-law distribution whose parameters can be configured. The degree of the
 nodes is also sampled from a power-law distribution. Additionally, the generator
-introduces the concept of the ``mixing factor'', which consists of the fraction of
+introduces the concept of the ``mixing factor'', which consists of the percentage of
 edges in the graph connecting nodes that belong to different communities. Such parameter

### 2018-11-26 generators_general.tex
Sherif Changes

@@
 clustering coefficient for each degree, Darwini is able to model the clustering
-coefficient distribution per degree. It achieves this by gathering the vertices
+coefficient distribution per degree. It achieves this by gathering the nodes
 of the graph into buckets based on the expected number of closed triangles that they need

### 2018-11-26 introduction.tex
Sherif Changes

--- 2018-10-20 introduction.tex
@@
 Hence, while practitioners can find a solution in another previously unexpected area, researchers can identify new target areas or exploit successful results in new fields.
-Last but not least, to provide a global view of the state-of-the-art, we also provide an overview of most commonly used real-world testing graph data sets.
+Last but not least, to provide a global view of the state-of-the-art, we also provide an overview of most commonly used real-world testing graph datasets.
 And, finally, we identify general open problems of graph data synthesis and indicate possible solutions to show that it still forms a challenging and promising research area.
@@
 
-Aggarwal and Subbian \cite{AggarwalS14} have surveyed the evolution of analysis in
+Aggarwal and Subbian~\cite{AggarwalS14} have surveyed the evolution of analysis in
 graphs, by primarily focusing on data mining maintenance methods and on analytical
@@
 the paper. The data generation of evolutionary networks is based on
-Densification Power Law (DPL) and shrinking diameters and community-guided
-attachment properties \cite{Leskovec:2005:GOT:1081870.1081893} is then considered, along with tackling Kronecker
-recursion with recursive tensor multiplication \cite{AkogluMF08}.
-We refer the reader to this survey for evolutionary network generators and
-we further discuss the open challenges of evolving graph data in Section 5.
+Densification Power Law (DPL) and shrinking diameters, community-guided
+attachment properties~\cite{Leskovec:2005:GOT:1081870.1081893}.
+Generation of graphs tackling Kronecker
+recursion with recursive tensor multiplication~\cite{AkogluMF08} is then considered in the above survey.
+We refer the readers to the aforementioned survey for evolutionary network generators and further discuss the open challenges of evolving graph data in Section 5.
 %\TODO{Better highlight the differences when Sherif's part is in.}

### 2018-11-27 challenges.tex
fixed some plagiarism issues from page 19 and on

@@
 
-The evolution of graphs can be considered from multiple perspectives.
-We can assume a static set of nodes and a varying set of edges.
-Or, there are applications where the graphs only ``grow'', i.e., the set of nodes and/or edges is only extended with new items.
-In the most general case we can assume any changes in both set of nodes and set of edges.
-Anyway with the evolution aspect the complexity of classical graph problems increases significantly~\cite{Michail2015,Wu:2014:PPT:2732939.2732945}.
-In some graph applications, such as, e.g., social networks, the evolution of the
-data is a significant aspect, especially in the activity graphs~\cite{doreian1997evolution,Kumar:2006:SEO:1150402.1150476,Hellmann2014583,wang2013,Kossinets88,Viswanath:2009:EUI:1592665.1592675}.
-However, as shown in~\cite{Leskovec:2005:RMT:2101235.2101254,Leskovec:2005:GOT:1081870.1081893},
+The evolution of graphs can be considered from multiple perspectives. We can
+assume a static set of nodes and a varying set of edges.  Or, there are
+applications where the graphs only ``grow'', i.e., the set of nodes and/or edges
+is only extended with new items. In the most general case we can assume any
+changes in both set of nodes and set of edges. Anyway with the evolution aspect
+the complexity of classical graph problems increases
+significantly~\cite{Michail2015,Wu:2014:PPT:2732939.2732945}. In some graph
+applications, such as, e.g., social networks, the evolution of the data is a
+significant aspect, especially in the activity
+graphs~\cite{doreian1997evolution,Kumar:2006:SEO:1150402.1150476,Hellmann2014583,wang2013,Kossinets88,Viswanath:2009:EUI:1592665.1592675}.
+However, as shown
+in~\cite{Leskovec:2005:RMT:2101235.2101254,Leskovec:2005:GOT:1081870.1081893},
 evolving graphs have further specific features. For example, some graphs grow
@@
 dynamic graphs}, i.e. graphs where the clustering corresponds to the partition
-of nodes into natural groups based on the paradigm of intra-cluster density
-versus inter-cluster sparsity of edges. The generator generates a time series
+of nodes into natural groups based on the concept of intra-cluster
+versus inter-cluster density of edges. The generator generates a time series
 of random graphs $G_0, G_1, ..., G_n$, where $G_t$ emerges from $G_{t-1}$ via
 successive atomic updates like for instance, the insertion of a vertex or the removal of an
-edge. The generator monitors the (dynamic) ground truth clustering and the probability
-of the atomic events is chosen in such a way that the ground truth clustering is
+edge. The generator dynamically monitors the ground truth clustering, and the probability
+of the updates is chosen in such a way that the ground truth is
 maintained while the randomness of the generated graph is kept.
 
-Another recent proposal of a generator~\cite{mlg2018_42} of temporal graphs results from an observation that small subgraph patterns in networks, called \emph{network motifs} or \emph{graphlets}, are crucial indicators of the structure and the evolution of the graphs~\cite{Paranjape:2017:MTN:3018661.3018731}.
-For a given graph and a predefined ordered list of structural atomic motifs the generator first computes the distribution of the motifs in the graph.
-The distribution is then used to generate a synthetic graph with the same features.
+Another recent proposal of a generator~\cite{mlg2018_42} of temporal graphs
+results from an observation that small subgraph patterns in networks, called
+\emph{network motifs} or \emph{graphlets}, are crucial indicators of the
+structure and the evolution of the
+graphs~\cite{Paranjape:2017:MTN:3018661.3018731}. For a given graph and a
+predefined ordered list of structural atomic motifs the generator first computes
+the distribution of the motifs in the graph. The distribution is then used to
+generate a synthetic graph with the same features.
 
@@
 proposed technique outperforms the baselines, the results show that there is
-still room for improvement in terms of the structural properties of the
+still room for improving the structural properties of the
 generated graph.

### 2018-11-27 generators_community_detection.tex
fixed some plagiarism issues from page 19 and on

@@
 and Radicchi (hence LFR)~\cite{PhysRevE.78.046110} propose a class of benchmark
-graphs for community detection where communities are of different sizes and
-densities. The generator generates communities of various sizes with a
-power-law distribution whose parameters can be configured. The degree of the
+graphs for community detection where communities are of diverse sizes and
+densities. The generated communities follow a power-law distribution whose parameters can be configured. The degree of the
 nodes is also sampled from a power-law distribution. Additionally, the generator
@@
 testing the robustness of the algorithms under different conditions. The
-generation process starts with an empty graph and incrementally fills in the
-adjacency matrix by considering the described constraints.
+generation process is implemented as an optimization process starting with an empty graph and 
+progressively filling it with nodes and edges guided by the specified constraints.
 

### 2018-11-27 generators_GraphDatabases.tex
Correction of XGDBench

@@
 
-\paragraph{XGDBench} XGDBench~\cite{Dayarathna:2014:GDB:2676904.2676939} is an extensible graph database benchmarking platform for cloud-based systems. Its intent is to automate
-the process of graph database benchmarking in the cloud by focusing on a graph database application for social networking services.
+\paragraph{XGDBench} XGDBench~\cite{Dayarathna:2014:GDB:2676904.2676939} is an extensible  benchmarking platform for graph databases used in cloud-based systems. Its intent is to automate
+the process of graph database benchmarking in the cloud by focusing on the domain social networking services.
 It extends the Yahoo!
-Cloud Multiplicative Attribute (MAG) Graph Serving Benchmark (YCSB)~\cite{Cooper:2010:BCS:1807128.1807152} and \iffalse consists of of a workload generator client and\fi provides a package of standard workloads that cover interesting parts of the performance space.
-\iffalse In particular, the workload generator of YCSB supports definition of new workload types.\fi In particular, the workload of XGDBench involves basic operations such as read / insert / update / delete an attribute, loading of the list of neighbors and BFS traversal.
+Cloud Multiplicative Attribute (MAG) Graph Serving Benchmark (YCSB)~\cite{Cooper:2010:BCS:1807128.1807152} and provides a set of standard workloads representing various performance issues.
+In particular, the workload of XGDBench involves basic operations such as read / insert / update / delete an attribute, loading of the list of neighbors and BFS traversal.
 Using the generators, 7 workloads are created, such as update heavy, read mostly, short range scan, traverse heavy etc.
-The data model of XGDBench is a simplified version of the Multiplicative Attribute Graph (MAG)~\cite{Kim2010} model, a synthetic graph model for attribute graphs which models the interactions between the network structure and the node attributes.
+The data model of XGDBench is a simplified version of the Multiplicative Attribute Graph (MAG)~\cite{Kim2010} model, a synthetic graph model which models the interactions between  node attributes and  graph structure.
 The generated graphs are thus in MAG format, with power-law degree distribution closely simulating real-world social networks.
-The simplified MAG algorithm accepts the number of vertices of the generated graph, the number of attributes per vertex, a threshold value for random initialization of attributes, an edge affinity threshold value that determines whether there is an edge between two vertices, and an affinity matrix.
-\iffalse It has been proven that MAG generates graphs with both analytically tractable and statistically interesting properties.\fi A multi-threaded version of the graph generator that generates large graphs on multi-core systems faster was implemented too.
+The simplified MAG algorithm accepts the required number of nodes, the number of attributes per each node, a threshold value for random attribute initialization, an edge affinity threshold determining existence of an edge between two nodes, and an affinity matrix.
+\iffalse It has been proven that MAG generates graphs with both analytically tractable and statistically interesting properties.\fi
+Large graphs can be generated on multi-core systems by a multi-threaded version of the  generator.
 

### 2018-12-02 comparison.tex
A few typos before 3rd submission

@@
 In general, \emph{degree-based generators} (e.g., Barabasi-Albert model~\cite{Barabasi99emergenceScaling}) are commonly attempting to find a graph that matches it, but without providing any information about the graph or attempting to match other graph features (e.g., eigenvalues, small diameter, ..., etc).
-On the other hand, \emph{procedural generators} (e.g., R-MAT~\cite{DBLP:conf/sdm/ChakrabartiZF04}) are commonly targeting simple techniques to produce graphs that the are matching the characteristics of the real graphs (e.g., the power law degree distribution).
+On the other hand, \emph{procedural generators} (e.g., R-MAT~\cite{DBLP:conf/sdm/ChakrabartiZF04}) are commonly targeting simple techniques to produce graphs that are matching the characteristics of the real graphs (e.g., the power law degree distribution).
 

### 2018-12-02 generators_LinkedData.tex
A few typos before 3rd submission

@@
 \paragraph{BSBM} The Berlin SPARQL Benchmark (BSBM)\footnote{\url{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}}, is centered around an e-commerce application domain with object types such as \emph{Customer}, \emph{Vendor}, \emph{Product} and \emph{Offer} in addition to the relationship among them~\cite{Bizer09theberlin}.
-The benchmark provides a workload that have 12 queries with 2 types of query workloads (i.e., 2 sequences of the 12 queries) emulating the navigation pattern and search of a consumer seeking a product.
+The benchmark provides a workload that has 12 queries with 2 types of query workloads (i.e., 2 sequences of the 12 queries) emulating the navigation pattern and search of a consumer seeking a product.
 The data generator is capable of producing arbitrarily scalable datasets by controlling the number of products ($n$) as a scale factor.
-The scale factor also impacts other data characteristics, such as, e.g., the depth of type hierarchy of products, branching factor, the number of product features,..., etc.
+The scale factor also impacts other data characteristics, such as, e.g., the depth of type hierarchy of products, branching factor, the number of product features,  etc.
 BSBM can output two representations, i.e.
@@
 In particular, the data mimics the correlations between entities.
-All random functions of the generator use a fixed seed that ensures the data generation process is deterministic.
+All random functions of the generator use a fixed seed that ensures that the data generation process is deterministic.
 SP$^2$Bench is accompanied by 12 queries covering the various types of operators such as RDF access paths in addition to typical RDF constructs.
@@
 Hence, they presented a universal SPARQL benchmark generation approach which uses a flexible data production mechanism that mimics the input data source.
-This dataset generation process begins using an input dataset then multiple datasets with different sizes  are then generated by duplicating all the RDF triples with changing their namespaces.
+This dataset generation process begins using an input dataset; then multiple datasets with different sizes  are then generated by duplicating all the RDF triples with changing their namespaces.
 For generating smaller datasets, an adequate selection of all triples is selected randomly or using a sampling mechanism over the various classes in the dataset.
@@
 
-\paragraph{SIB} The developers of the Social Network Intelligence BenchMark (SIB)\footnote{\url{https://www.w3.org/wiki/Social_Network_Intelligence_BenchMark}} based the design of their benchmark based on the claim that existing benchmarks are limited in reflecting the characteristics of the real RDF databases and are mostly focusing on the relational style aspects.
+\paragraph{SIB} The developers of the Social Network Intelligence BenchMark (SIB)\footnote{\url{https://www.w3.org/wiki/Social_Network_Intelligence_BenchMark}} based the design of their benchmark on the claim that existing benchmarks are limited in reflecting the characteristics of the real RDF databases and are mostly focusing on the relational style aspects.
 Hence, they proposed a benchmark for  query evaluation using real graphs~\cite{sib}.

### 2018-12-02 generators_SocialNetworks.tex
A few typos before 3rd submission

@@
 
-\paragraph{Towards More Realistic Data} \cite{Nettleton2016} argued that the majority of existing work focus on
+\paragraph{Towards More Realistic Data} \cite{Nettleton2016} argued that the majority of existing works focuses on
 topology generation which approximates the characteristics of a real social

### 2018-12-02 generators_general.tex
A few typos before 3rd submission

@@
 the properties of the real graphs.
-In particular, the design goals of R-MAT is to produce graphs which mimics the degree distributions, imitate a community structure and have a small diameter.
+In particular, the design goal of R-MAT is to produce graphs which mimics the degree distributions, imitate a community structure and have a small diameter.
 R-MAT can generate weighted, directed and bipartite graphs.

### 2019-06-11 main.tex
title changed

@@
 % Page heads
-\markboth{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr}{Modern Graph Generators: A Survey}
+\markboth{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr}{Graph Generators: State of the Art and Open Challenges}
 
@@
 %\title{Graph Data Generators in the World of Big Data}
-\title{Modern Graph Generators: A Survey}
+%\title{Modern Graph Generators: A Survey}
+\title{Graph Generators: State of the Art and Open Challenges}
 \author{
@@
 This survey provides a comprehensive overview of the state-of-the-art
-modern graph generators by focusing on those that are pertinent and
+graph generators by focusing on those that are pertinent and
 suitable for several data-intensive tasks. Finally, we discuss open

### 2019-06-11 generators_GraphDatabases.tex
Section 3.3 - added strengths and weaknesses

@@
 Currently there exists a number of papers which compare the efficiency of graph databases with regards to distinct use cases, such as  the community detection problem~\cite{Beis2015}, social tagging systems~\cite{Giatsoglou2011}, graph traversal~\cite{Ciglan:2012:BTO:2374486.2375242}, graph pattern matching~\cite{Pobiedina2014}, data provenance~\cite{Vicknair:2010:CGD:1900008.1900067}, or even several distinct use cases~\cite{Grossniklaus2013Towar-24253}.
-However, the number of graph data generators and benchmarks that have been designed specifically for graph databases is relatively small.
-Either a general graph generator is used for benchmarking graph databases, such as, e.g., the HPC Scalable Graph Analysis Benchmark~\cite{Dominguez-Sal:2010:SGD:1927585.1927590} or the graph DBMS benchmarking tools are designed in a more general scope.
+However, the number of graph data generators and benchmarks that have been designed specifically for graph data management systems (Graph DBMS)  is relatively small.
+Either a general graph generator is used for benchmarking graph databases, such as, e.g., the HPC Scalable Graph Analysis Benchmark~\cite{Dominguez-Sal:2010:SGD:1927585.1927590} or the graph DBMS benchmarking tools are designed while having in mind a more general scope.
 Hence it is questionable whether a benchmark  that is targeted specifically for graph databases is necessary.
@@
 Cloud Multiplicative Attribute (MAG) Graph Serving Benchmark (YCSB)~\cite{Cooper:2010:BCS:1807128.1807152} and provides a set of standard workloads representing various performance issues.
-In particular, the workload of XGDBench involves basic operations such as read / insert / update / delete an attribute, loading of the list of neighbors and BFS traversal.
+In particular, the workload of XGDBench involves basic operations such as read / insert / update / delete an attribute, loading of the list of neighbours and BFS traversal.
 Using the generators, 7 workloads are created, such as update heavy, read mostly, short range scan, traverse heavy etc.
@@
 
-\paragraph{GraphGen}  GraphAware GraphGen\footnote{\url{http://graphgen.graphaware.com/}} is a graph generation engine based on Neo4j's\footnote{\url{https://neo4j.com/}} query language Cypher~\cite{GraphGen}.
+\paragraph{GraphGen}  GraphAware GraphGen\footnote{\url{http://graphgen.graphaware.com/}} is a graph generation engine based on Neo4j's\footnote{\url{https://neo4j.com/}} query language OpenCypher~\cite{GraphGen}.
 It creates nodes and relationships based on a schema definition expressed in Cypher, and it can also generate property values on both
@@
 The resulting graph can be exported to several formats (namely GraphJson\footnote{\url{https://github.com/GraphAlchemist/GraphJSON/wiki/GraphJSON}} and CypherQueries) or loaded directly to a DBMS.
-However, it is very likely that it is not maintained anymore due to the lack of available updates.
+However, it is very likely that it is not maintained anymore due to the lack of available recent commits.
+
+\paragraph{Strengths and Weaknesses of Graph Database Generators} 
+The graph DBMS generators discussed in this section have in common the fact that they can generate semantically rich labeled graphs with properties (ranging from properties values in GraphGen to MAG structures in XGDBench).
+They are also capable of generating query workloads in
+concrete syntaxes (among which OpenCypher in GraphGen and gMark) and one of them (XGDBench) can also handle update operations on both graph structure and content.
+None of these generators is enables to work on property graphs and on corresponding languages for property graphs, such as the newly emerging standard GQL~\cite{gql-2018} and G-Core~\cite{AnglesABBFGLPPS18}.
+However, a full-fledged graph DBMS generator for property graphs and property graph query workloads~\cite{BFVY18} is still missing and could be an interesting opportunity to build such a generator in the next future.
+Another weakness is represented by the fact that explicit correlations among graph elements cannot be encoded for instance in gMark or GraphGen, whereas they could be fruitful in order to reproduce the behavior of real-world graphs in which attribute values are correlated one with another.
+On the other hand, social network and Linked Data generators that support correlations (as highlighted in Section \ref{sec:generators_socialnetworks} and Section \ref{sec:generators_LinkedData}) typically exhibits a fixed schema and are not multi-domain as the graph DBMS generators discussed in this Section.

### 2019-06-11 generators_GraphDatabases.tex
still Sect. 3.3

@@
 concrete syntaxes (among which OpenCypher in GraphGen and gMark) and one of them (XGDBench) can also handle update operations on both graph structure and content.
-None of these generators is enables to work on property graphs and on corresponding languages for property graphs, such as the newly emerging standard GQL~\cite{gql-2018} and G-Core~\cite{AnglesABBFGLPPS18}.
+However, more comprehensive graph DBMS generators that also produce data manipulation operations (such as updates for graph databases) are urgently needed.
+
+Additionally, none of these generators is enabled to work on property graphs and on corresponding languages for property graphs, such as the newly emerging standard GQL~\cite{gql-2018} and G-Core~\cite{AnglesABBFGLPPS18}.
 However, a full-fledged graph DBMS generator for property graphs and property graph query workloads~\cite{BFVY18} is still missing and could be an interesting opportunity to build such a generator in the next future.

### 2019-06-11 generators_GraphDatabases.tex
Section 3.3 - tweaks

@@
 The graph DBMS generators discussed in this section have in common the fact that they can generate semantically rich labeled graphs with properties (ranging from properties values in GraphGen to MAG structures in XGDBench).
-They are also capable of generating query workloads in
+They are also capable of generating graph instances and query workloads in
 concrete syntaxes (among which OpenCypher in GraphGen and gMark) and one of them (XGDBench) can also handle update operations on both graph structure and content.
@@
 
-Additionally, none of these generators is enabled to work on property graphs and on corresponding languages for property graphs, such as the newly emerging standard GQL~\cite{gql-2018} and G-Core~\cite{AnglesABBFGLPPS18}.
-However, a full-fledged graph DBMS generator for property graphs and property graph query workloads~\cite{BFVY18} is still missing and could be an interesting opportunity to build such a generator in the next future.
-Another weakness is represented by the fact that explicit correlations among graph elements cannot be encoded for instance in gMark or GraphGen, whereas they could be fruitful in order to reproduce the behavior of real-world graphs in which attribute values are correlated one with another.
-On the other hand, social network and Linked Data generators that support correlations (as highlighted in Section \ref{sec:generators_socialnetworks} and Section \ref{sec:generators_LinkedData}) typically exhibits a fixed schema and are not multi-domain as the graph DBMS generators discussed in this Section.
+Additionally, none of these generators is enabled to work on corresponding query languages for property graphs, such as the newly emerging standard GQL~\cite{gql-2018} and G-Core~\cite{AnglesABBFGLPPS18}.
+Hence, a full-fledged graph DBMS generator for property graphs and property graph query workloads~\cite{BFVY18} is still missing and there exists an interesting opportunity to build such a generator in the next future.
+Another apparent inconvenient is represented by the fact that explicit correlations among graph elements cannot be encoded for instance in gMark or GraphGen, whereas they could be fruitful in order to reproduce the behavior of real-world graphs in which attribute values are correlated one with another.
+On the other hand, social network and Linked Data generators that support correlations (as highlighted in Section \ref{sec:generators_socialnetworks} and Section \ref{sec:generators_LinkedData}) typically exhibit a fixed schema and are not not necessarily multi-domain as some of the graph DBMS generators discussed in this Section (namely GraphGen and gMark).

### 2019-06-14 generators_SocialNetworks.tex
updated social network generators strenghts and weaknesess

@@
 features~\cite{Chakrabarti:2006:GML:1132952.1132954}. For example, a social
-graph often has high \emph{clustering coefficient}, i.e. the degree of transitivity of
-a graph. Or, its diameter, i.e. the longest shortest path amongst some fraction (e.g. 90\%) of all connected nodes, is usually low due to weak ties joining faraway cliques.
+graph often has high \emph{clustering coefficient}, i.e. the degree of
+transitivity of a graph. Or, its diameter, i.e. the longest shortest path
+amongst some fraction (e.g. 90\%) of all connected nodes, is usually low due to
+weak ties joining faraway cliques.
 
-Another important aspect
-of social networks is the community effect. A detailed study of structure of
-communities in 70 real-world networks is provided, e.g., in
-~\cite{Leskovec:2008:SPC:1367497.1367591}.
+Another important aspect of social networks is the community effect. A detailed
+study of structure of communities in 70 real-world networks is provided, e.g.,
+in ~\cite{Leskovec:2008:SPC:1367497.1367591}.
 ~\cite{Prat-Perez:2014:CSS:2621934.2621942} analyzed the structure of
 communities (clustering coefficient, triangle participation ratio, bridges,
-diameter, conductance and size) in both real-world graphs and outputs of existing graph
-generators LFR~\cite{PhysRevE.78.046110} and the
-LDBC-SNB~\cite{Erling:2015:LSN:2723372.2742786}.
-They found out that discovered communities  in different graphs have common distributions and that communities in a single graph have diverse nature and are difficult to fit with a single model.
+diameter, conductance and size) in both real-world graphs and outputs of
+existing graph generators such as LFR~\cite{PhysRevE.78.046110} and the
+LDBC-SNB~\cite{Erling:2015:LSN:2723372.2742786}. They found out that discovered
+communities  in different graphs have common distributions and that communities
+in a single graph have diverse nature and are difficult to fit with a single
+model.
 
@@
 ~\cite{Barrett:2009:GAL:1995456.1995598} focused on the construction of
-realistic social networks. For this purpose the authors combine both public and private data sets
-with large-scale agent-based techniques. The process works as follows: In the first step
-it generates a synthetic data by combining public and commercial databases. In the second step, it determines a set of activity templates. A 24-hour activity sequence including
-geolocations is assigned to each synthetic individual.
-To demonstrate the approach, the authors create a synthetic US population consisting of people and households together with respective geolocations.
-For this purpose the authors combine simulation and data fusion techniques utilizing various real-world data sources such as U.S.
+realistic social networks. For this purpose the authors combine both public and
+private data sets with large-scale agent-based techniques. The process works as
+follows: In the first step it generates a synthetic data by combining public and
+commercial databases. In the second step, it determines a set of activity
+templates. A 24-hour activity sequence including geolocations is assigned to
+each synthetic individual. To demonstrate the approach, the authors create a
+synthetic US population consisting of people and households together with
+respective geolocations. For this purpose the authors combine simulation and
+data fusion techniques utilizing various real-world data sources such as U.S.
 Census data, responses to an activity survey or a time-use survey. 
-%Demographic information for each person and location, a minute-by-minute schedule of each person's activities, and the locations where these activities take place is generated by a combination of simulation and data fusion techniques.
-The result is captured by a dynamic social contact network. Similar methods for agent-based strategies have been reported in~\cite{Bernstein:2013:SAS:2499604.2499609}.
+%Demographic information for each person and location, a minute-by-minute
+%schedule of each person's activities, and the locations where these activities
+%take place is generated by a combination of simulation and data fusion
+%techniques.
+The result is captured by a dynamic social contact network. Similar methods for
+agent-based strategies have been reported
+in~\cite{Bernstein:2013:SAS:2499604.2499609}.
 
-\paragraph{Linkage vs. Activity Graphs} \cite{Yao2011} distinguished between two
-types of social network graphs -- the \emph{linkage graph}, where nodes represent people and edges correspond to their friendships, and the \emph{activity graph}, where nodes also represent people but correspond to their interactions.
-On the basis of the analysis of
+\paragraph{Linkage vs. Activity Graphs} 
+\cite{Yao2011} distinguished between two types of social network graphs -- the
+\emph{linkage graph}, where nodes represent people and edges correspond to their
+friendships, and the \emph{activity graph}, where nodes also represent people
+but edges correspond to their interactions. On the basis of the analysis of
 Flickr\footnote{\url{https://www.flickr.com/}} social links and
-Epinions\footnote{\url{http://www.epinions.com/}} network of user interactions, the authors discover that they both exhibit high clustering coefficient (community structure), small diameter, and power-law degree distribution.
-Considering the dynamic properties they both have relatively stable clustering coefficient over time and follow the densification law.
-On the other hand, diameter shrinking is not observed in Epinions activity graph and there is a difference in degree
-correlation (i.e., frequency of mutual connections of similar nodes) -- linkage graphs have positive degree correlation, activity graphs have neutral degree correlation.
-With regards to the findings, the proposed generator focusses on linkage graphs with positive degree correlation.
-For this purpose it extends the forest fire spreading process algorithm~\cite{Leskovec:2005:GOT:1081870.1081893} with link symmetry.
-It has two parameters: the \emph{burning probability} $P_b$ and the \emph{symmetry probability} $P_s$.
-$P_b$ ensures a BFS-based forward burning process in which fire burns strongly with $P_b$ approaching 1.
-$P_s$ ensures backward linking from old nodes to new nodes and ``adds fuel to the fire as it brings more links''.
-%It gives chances for big nodes to connect back to big nodes.
+Epinions\footnote{\url{http://www.epinions.com/}} network of user interactions,
+the authors discover that they both exhibit high clustering coefficient
+(community structure), small diameter, and power-law degree distribution.
+Considering the dynamic properties they both have relatively stable clustering
+coefficient over time and follow the densification law. On the other hand,
+diameter shrinking is not observed in Epinions activity graph and there is a
+difference in degree correlation (i.e., frequency of mutual connections of
+similar nodes) -- linkage graphs have positive degree correlation, activity
+graphs have neutral degree correlation. With regards to the findings, the
+proposed generator focusses on linkage graphs with positive degree correlation.
+For this purpose it extends the forest fire spreading process
+algorithm~\cite{Leskovec:2005:GOT:1081870.1081893} with link symmetry. It has
+two parameters: the \emph{burning probability} $P_b$ and the \emph{symmetry
+probability} $P_s$. $P_b$ ensures a BFS-based forward burning process in which
+fire burns strongly with $P_b$ approaching 1.  $P_s$ ensures backward linking
+from old nodes to new nodes and ``adds fuel to the fire as it brings more
+links''. %It gives chances for big nodes to connect back to big nodes.
 
 \paragraph{LinkBench} The LinkBench
-benchmark~\cite{Armstrong:2013:LDB:2463676.2465296} has been designed for the purpose of analysis of efficiency of a database storing Facebook's production data.
-The benchmark considers true Big Data and related problems with sharding, replication etc.
-The social graph at Facebook comprises objects (nodes with IDs, version, timestamp and data) and associations (directed edges, pairs of node IDs, with visibility, timestamp and data).
-The size of the target graph is the number of nodes.
-Graph edges and nodes are generated concurrently during bulk loading.
-The space of node IDs is divided into chunks which enable parallel processing.
-The edges of the graph are generated in accordance with the results of analysing  real-world Facebook data (such as outdegree distribution).
-A workload corresponding to 10 graph operations (such as insert object, count the number of associations etc.) and their respective characteristics over the real-world data is generated for the synthetic data.
+benchmark~\cite{Armstrong:2013:LDB:2463676.2465296} has been designed for the
+purpose of analysis of efficiency of a database storing Facebook's production
+data. The benchmark considers true Big Data and related problems with sharding,
+replication etc. The social graph at Facebook comprises objects (nodes with IDs,
+version, timestamp and data) and associations (directed edges, pairs of node
+IDs, with visibility, timestamp and data). The size of the target graph is the
+number of nodes. Graph edges and nodes are generated concurrently during bulk
+loading. The space of node IDs is divided into chunks which enable parallel
+processing. The edges of the graph are generated in accordance with the results
+of analysing  real-world Facebook data (such as outdegree distribution). A
+workload corresponding to 10 graph operations (such as insert object, count the
+number of associations etc.) and their respective characteristics over the
+real-world data is generated for the synthetic data.
 
-\paragraph{S3G2} The Scalable Structure-correlated Social Graph Generator (S3G2)~\cite{Pham2013} is a general framework which produces a directed labeled graph whose vertices represent objects having property values.
-The respective classes determine the structure of the properties.
-S3G2 does not aim at generating near real-world data, but at generating synthetic graphs with a correlated structure.
-Hence, the existing data values influence the probability of choosing a certain property value from a pre-defined dictionary, or the probability of connecting two nodes.
-For example, the degree distribution can be correlated with the properties of a node and thus, e.g., people having many friend relationships typically post more comments and pictures.
-The data generation process starts with generating a number of nodes with property values generated according to specified property value correlations and then adding respective edges according to specified correlation dimensions.
-It has multiple phases, each focusing on one correlation dimension.
-Data is generated in a Map phase corresponding to a pass along one correlation dimension.
-Then the data are sorted along the correlation dimension in the following Reduce phase.
-A heuristic observation that ``the probability that two nodes are connected is typically skewed with respect to some similarity between the nodes'' enables to focus only on sliding window of most probable candidates.
-The core idea of the framework is demonstrated using an example of a social network (consisting of persons and social activities).
-The dictionaries for property values are inspired by DBpedia and provided with 20 property value correlations.
-The edges are generated according to 3 correlation dimensions.
+\paragraph{S3G2} The Scalable Structure-correlated Social Graph Generator
+(S3G2)~\cite{Pham2013} is a general framework which produces a directed labeled
+graph whose vertices represent objects having property values. The respective
+classes determine the structure of the properties. S3G2 does not aim at
+generating near real-world data, but at generating synthetic graphs with a
+correlated structure. Hence, the existing data values influence the probability
+of choosing a certain property value from a pre-defined dictionary, or the
+probability of connecting two nodes. For example, the degree distribution can be
+correlated with the properties of a node and thus, e.g., people having many
+friend relationships typically post more comments and pictures. The data
+generation process starts with generating a number of nodes with property values
+generated according to specified property value correlations and then adding
+respective edges according to specified correlation dimensions. It has multiple
+phases, each focusing on one correlation dimension. Data is generated in a Map
+phase corresponding to a pass along one correlation dimension. Then the data are
+sorted along the correlation dimension in the following Reduce phase. A
+heuristic observation that ``the probability that two nodes are connected is
+typically skewed with respect to some similarity between the nodes'' enables to
+focus only on sliding window of most probable candidates. The core idea of the
+framework is demonstrated using an example of a social network (consisting of
+persons and social activities).  The dictionaries for property values are
+inspired by DBpedia and provided with 20 property value correlations. The edges
+are generated according to 3 correlation dimensions.
 
 \paragraph{Cloning of Social Networks} ~\cite{Sukthankar-SocialInfo2014}
-introduced a synthetic network generator designed for cloning social network
-statistics of an existing dataset. The network starts with a small number of
+introduces two synthetic generators to reproduce two characteristics typically
+observed in social networks: node features and multiple link types. Both
+generators etend on the generator proposed by~\cite{wang2011leveraging}.
+which starts with a small number of
 nodes, and new nodes are added until the network reaches the required number. It
@@
 
-Attribute Synthetic Generator (ASG) is a network generator for reproducing the
-node feature distribution of standard networks and rewiring the network to
-preferentially connect nodes that exhibit a high feature similarity. The network
-is initialized with a group of three nodes, and new nodes and links are added to
-the network based on link density, homophily, and feature similarity. As new
-nodes are created, their labels are assigned based on the prior label
-distribution. After the network has reached the same number of nodes as the
-original social media dataset, each node initially receives a random attribute
-assignment. Then a stochastic optimization process is used to move the initial
-assignments closer to the target distribution extracted from social media
-dataset using the Particle Swarm Optimization algorithm. The tuned attributes
-are then used to add additional links to the network based on the feature
-similarity parameter -- a source node is selected randomly and connected to the
-most similar node. Multi-Link Generator (MLG) further  uses link co-occurrence statistics from the
-original dataset to create a multiplex network. MLG uses the same network growth
-process as ASG. Based on the link density parameter, either a new node is
-generated with a label based on the label distribution of the target dataset or
-a new link is created between two existing nodes.
+The first proposed generator is Attribute Synthetic Generator (ASG), used for
+reproducing the node feature distribution of standard networks and rewiring the
+network to preferentially connect nodes that exhibit a high feature similarity.
+The network is initialized with a group of three nodes, and new nodes and links
+are added to the network based on link density, homophily, and feature
+similarity. As new nodes are created, their labels are assigned based on the
+prior label distribution. After the network has reached the same number of nodes
+as the original social media dataset, each node initially receives a random
+attribute assignment. Then a stochastic optimization process is used to move the
+initial assignments closer to the target distribution extracted from social
+media dataset using the Particle Swarm Optimization algorithm. The tuned
+attributes are then used to add additional links to the network based on the
+feature similarity parameter -- a source node is selected randomly and connected
+to the most similar node. The second proposed generator is Multi-Link Generator
+(MLG) further  uses link co-occurrence statistics from the original dataset to
+create a multiplex network. MLG uses the same network growth process as ASG.
+Based on the link density parameter, either a new node is generated with a label
+based on the label distribution of the target dataset or a new link is created
+between two existing nodes.
 
-\paragraph{LDBC SNB} Despite having a common Facebook-like dataset, thanks to three distinct workloads the Social Network Benchmark (SNB)~\cite{Erling:2015:LSN:2723372.2742786} provided by LDBC represents three distinct benchmarks.
-The network nodes correspond to people and the edges represent their friendship and messages they post in discussion trees on their forums.
-The three query workloads involve: (1) SNB-Interactive, i.e., complex read-only queries accessing a significant portion of data, (2) SNB-BI, i.e., queries accessing a high percentage of  entities and grouping them in various dimensions, and (3) SNB-Algorithms, involving graph analysis algorithms, such as community detection, PageRank, BFS, and clustering.
-The graph generator realizes power laws, uses skewed value distributions, and ensures reasonable correlations between graph structures and property values.
-To provide scalability it is implemented on top of Hadoop.
+\paragraph{LDBC SNB} Despite having a common Facebook-like dataset, thanks to
+three distinct workloads the Social Network Benchmark
+(SNB)~\cite{Erling:2015:LSN:2723372.2742786} provided by LDBC represents three
+distinct benchmarks. The network nodes correspond to people and the edges
+represent their friendship and messages they post in discussion trees on their
+forums. The three query workloads involve: (1) SNB-Interactive, i.e., complex
+read-only queries accessing a significant portion of data, (2) SNB-BI, i.e.,
+queries accessing a high percentage of  entities and grouping them in various
+dimensions, and (3) SNB-Algorithms, involving graph analysis algorithms, such as
+community detection, PageRank, BFS, and clustering. The graph generator, called
+Datagen, is a fork of S3G2 ~\cite{Pham2013} and realizes power laws, uses skewed
+value distributions, and ensures reasonable correlations between graph
+structures and property values. Additionally, it extends S3G2 with "spiky"
+patterns in the distribution of social network activity along the timeline, also
+provides the ability of generating update streams to the social network. Datagen
+is also based on Hadoop in order to provide scalability, but comparet to S3G2 it
+contains numerous performance improvements and the ability to be deterministic
+regardless of the number of computer nodes used for the generation of the graphs
+and for a given set of configuration parameters.
 
@@
 population.
+
+\paragraph{Strengths and Weaknesses of Social Network Generators}
+Compared to more general graph generators, social network generators focus
+mainly on reproducing intra- and inter-node feature correlations. 
+Among existing genrators, LDBC-SNB and S3G2 look
+like the most advanced ones in terms of the complexity of the generated graph
+and the amount of features and correlations they can generate, while providing a
+large degree of scalability. Their generation process is based on input dictionaries and have configuration files that
+allow tweaking parameters many parameters of the generated graphs, but their schema is mainly
+static and cannot be easilly configured to meet the needs of other uses cases
+besides the benchmarks they have been designed for. In this regard, the approaches
+like those proposed in ~\cite{Nettleton2016} and ~\cite{Sukthankar-SocialInfo2014} offer a
+more flexible and understandable configuration process to tweak the types,
+values and correlations between different features.
+
+Regarding the correlation between the underlying graph structure and the node
+features, approaches such as LDBC-SNB, S3G2 or ~\cite{Nettleton2016} 
+take into account this aspect and the generated graphs have ralistic
+structural properties while similar nodes have a larger probability of being
+connected. However, their approach seems to be more based on
+intuition and common sense than to be backed up by an any study of how the
+relation between structure and attributes showcase in real social networks. In
+this reagard, this remains as a clear open challenge for social network
+generators.
+
+Finally, scalability is another aspect to be considered in social network graph
+generators. LDBC-SNB and S3G2 are engineered with this in mind, thus they
+provide a way to scale to billions of nodes and edges. This is not the case for
+the other generators, which can make them impractical if our goal is to generate
+real sized social network graphs.

### 2019-06-14 generators_community_detection.tex
Updated community detection algorithms with strengths and weaknesess

@@
 
+\paragraph{Strengths and Weaknesses of Community Detection Generators}
 Besides synthetic graph generators, Yang and Leskovec~\cite{yang2015defining}

### 2019-06-14 generators_general.tex
added strengths and weaknesses for general graph generators

@@
 
-We start by focusing on approaches that have been designed for dealing with the generation of general graph
-data that is not aimed at a particular application domain. Currently, there exists a
-number of tools which involve a kind of general graph data generator, such as
-gtools from projects nauty and Traces~\cite{gtools} or the Stanford
-GraphBase~\cite{GraphBase}. We, however, focus on primarily
-generating/benchmarking projects targeting the Big Data world.
+We start by focusing on approaches that have been designed for dealing with the
+generation of general graph data that is not aimed at a particular application
+domain. In general, such generators focus on reproducing properties observed in
+real graphs regardless of their domain such as the degree distribution, the
+diameter, the presence of a large connected component, a community structure or
+a significantly large clustering coefficient.
 
-\paragraph {Preferential Attachment} Barabasi and Albert~\cite{Barabasi99emergenceScaling} introduced a graph generation model that relies on two main mechanisms.
-The first mechanism is continuously expanding the graphs by adding new vertices.
-The second mechanism is to preferentially attach the new vertices   to the nodes/regions that are already well connected.
-So, in this approach, the generation of large graphs is governed by standard, robust self-organizing mechanisms that go beyond the characteristics of individual applications.
+%Currently, there exists a number of tools which involve a kind of
+%general graph data generator, such as gtools from projects nauty and
+%Traces~\cite{gtools} or the Stanford GraphBase~\cite{GraphBase}. We, however,
+%focus on primarily generating/benchmarking projects targeting the Big Data
+%world.
 
-\paragraph {R-MAT} R-MAT (\emph{R}ecursive \emph{Mat}rix) is a procedural synthetic graph generator which is designed to generate power-law degree
-distributions~\cite{DBLP:conf/sdm/ChakrabartiZF04}.
-The generator is recursive and employs a fairly small number of parameters.
-In principle, the strategy of this generator is to achieve simple means to produce graphs that are matching
-the properties of the real graphs.
-In particular, the design goal of R-MAT is to produce graphs which mimics the degree distributions, imitate a community structure and have a small diameter.
-R-MAT can generate weighted, directed and bipartite graphs.
+\paragraph {Preferential Attachment} Barabasi and
+Albert~\cite{Barabasi99emergenceScaling} introduced a graph generation model
+that relies on two main mechanisms. The first mechanism is continuously
+expanding the graphs by adding new vertices. The second mechanism is to
+preferentially attach the new vertices   to the nodes/regions that are already
+well connected. So, in this approach, the generation of large graphs is governed
+by standard, robust self-organizing mechanisms that go beyond the
+characteristics of individual applications.
+
+\paragraph {R-MAT} R-MAT (\emph{R}ecursive \emph{Mat}rix) is a procedural
+synthetic graph generator which is designed to generate power-law degree
+distributions~\cite{DBLP:conf/sdm/ChakrabartiZF04}.  The generator is recursive
+and employs a fairly small number of parameters.  In principle, the strategy of
+this generator is to achieve simple means to produce graphs that are matching
+the properties of the real graphs. In particular, the design goal of R-MAT is to
+produce graphs which mimics the degree distributions, imitate a community
+structure and have a small diameter. R-MAT can generate weighted, directed and
+bipartite graphs.
 
@@
 %graphs, bipartite graphs, digraphs, and multigraphs.
+
+\paragraph{Strengths and Weaknesses of General Graph Generators}
+In general, existing general graph generators produce graphs with the following
+properties: skewed degree distribution (e.g. powerlay), small diameter, large
+clustering coefficient, a large largest connected component and some degree of
+community structure. Degree distribution can be typically configured while other
+properties are just a result of the genration process and cannot be controlled
+by any means.
+
+This is not the case of BTER and Darwini which besides the degree distribution,
+they also allow tunning the clustering coefficient. However, some use cases
+demand for more control on the characteristics of the generated graphs.
+This is the case, for instance, of benchmarking, where the underlying graph
+structure has direct implications to the performance of the graph algorithms
+to run. For this reason, the design of graph generators with the capability of fine
+tunning the characteristics of the generated graphs still remains as an open
+challenge. The question that remains though is what characteristics to tune,
+and which are the algorithms whose depends on such characteristics.

### 2019-06-16 challenges.tex
Reviewer's comments - part I.

@@
 are the so-called \emph{multi-model databases} that enable to store and
-thus query across structurally different data. There exist various types of
+thus query across structurally different data, including structured, semi-structured, and unstructured. There exist various types of
 multi-model systems combining  distinct subsets of Big Data structures including graph data.

### 2019-06-16 comparison.tex
Reviewer's comments - part I.

@@
 At first we classify the generators on the basis of the respective application domains or user communities.
-In particular we distinguish (1) general graphs, (2) Semantic Web, (3) graph databases, (4) social networks, (5) graph analytics, (6) community detection, and (7) graph data steaming.
+In particular we distinguish (1) general graphs, (2) Semantic Web, (3) graph databases, (4) social networks, (5) graph analytics, (6) community detection, and (7) graph data streaming.
 The selected classes are not rigorously defined (e.g., they are not disjoint as we will show later), but they correspond to the currently most active research areas.
@@
 
-If we consider the features of the particular domain of the generators, in most cases it is expectably fixed.
+If we consider the features of the particular domain of the generators, in most cases it is expectably \emph{fixed}, i.e., it is pre-defined (describing, e.g., a social network) and cannot be modified.
 It is the simplest option, but it does mean that the generator is simple too -- it can still focus on other complex aspects of the output.
+While the \emph{schema-driven} approaches enable to influence the target domain using a user-supplied schema, there also exist approaches where the domain is \emph{extracted} from sample data.
 The particular target (in case of fixed) or sample (in case of schema-driven or extracted) domains do not provide very rich areas.
@@
 
-As we have mentioned, the basic classification that we have used in this paper
-is  based on a relatively vague division of the generators on the basis of the
-current application domains or research areas. In addition, some of the
-generators are either general or have features applicable in other domains. So
-the classes can overlap, as depicted in Table~\ref{tab:overlapping}.
+As we have mentioned, the basic classification of the generators that we have used in this paper is relatively vaguely based on the current application domains or research areas.
+In addition, some of the generators are either general, and thus can be used universally, or have features applicable in more than one domain/research area.
+So the classes we use can overlap, as depicted in Table~\ref{tab:overlapping}.
 
@@
                & \textbf{\rot{Community detection}}
-               & \textbf{\rot{Steaming}}
+               & \textbf{\rot{Streaming}}
                \\ \hline
@@
 In the case of LinkBench, nothing prevents the user to load the generated graph
-in a graph database (Facebook uses MySQL in that paper) to
+in a (graph) database (e.g., Facebook uses MySQL in~\cite{Armstrong:2013:LDB:2463676.2465296}) to
 test a workload similar to Facebook and extend and complement it with more

### 2019-06-16 generators_LinkedData.tex
Reviewer's comments - part I.

@@
 In addition, the LUBM benchmark provides 14 test queries.
-In particular, the benchmark focuses on \emph{extensional} queries, i.e., queries which target the instance data over ontologies, as an opposite to \emph{intentional} queries, i.e., queries which target the properties and  classes of the ontology.
+In particular, the benchmark focuses on \emph{extensional} queries, i.e., queries which target the particular data instances of the ontology, as an opposite to \emph{intentional} queries, i.e., queries which target properties and classes of the ontology.
 The Univ-Bench Artificial  (UBA) data generator features repeatable and random  data generation (exploiting classical linear congruential generator, LCG, of numbers).

### 2019-06-16 generators_LinkedData.tex
Reviewer's comments - part II.

@@
 In particular, the data which is produced by the generator are assigned zero-based indexes (i.e., the first university is named \emph{University0} and so on), thus they are reproducible at any time with the same indexes.
-The generator allows to specify a seed for random number generation, along with the desired number of universities, and the starting index of the universities.
+The generator naturally allows to specify a seed for random number generation, along with the desired number of universities, and the starting index of the universities.
 
@@
 The data generation process is managed through two main phases: (1) the property-discovery phase, and (2) the data generation phase.
-In particular, LBBM provides a probabilistic model that can emulate the properties of the data of a particular domain and generate synthetic data exhibiting similar properties.
+LBBM provides a probabilistic model that can emulate the discovered properties of the data of a particular domain and generate synthetic data exhibiting similar properties.
 A Monte Carlo algorithm is employed to output synthetic data.
@@
 
-\paragraph{IIMB} Contrary to the previous work, Ferrara et al.~\cite{Ferrara08OM} proposed the ISLab Instance Matching Benchmark (IIMB)\footnote{\url{http://www.ics.forth.gr/isl/BenchmarksTutorial/}} for the problem of instance matching.
+\paragraph{IIMB} Ferrara et al.~\cite{Ferrara08OM} proposed the ISLab Instance Matching Benchmark (IIMB)\footnote{\url{http://www.ics.forth.gr/isl/BenchmarksTutorial/}} for the problem of instance matching.
 For any two objects $o_1$ and $o_2$ adhering to the same ontology or to different ontologies, instance matching is specified in the form of a function $Om(o_1, o_2) \rightarrow \{0, 1\}$,  where $o_1$ and $o_2$ are linked to the same real-world object (in which case the function maps to $1$) or $o_1$ and $o_2$ are representing different objects (in which case the function maps to $0$).
@@
 
-\paragraph{Data Coherence}  A comparison of 4 RDF benchmarks (namely TPC-H~\cite{TPC-H} data expressed in RDF, LUBM, BSBM, and SP$^2$Bench) and 6 real-wold data sets (such as, e.g.,  DBpedia, the Barton Libraries Dataset~\cite{barton-benchmark} or
+\paragraph{Comparison of Data Coherence in TPC-H, LUBM, BSBM, and SP$^2$Bench}  A comparison of 4 RDF benchmarks (namely TPC-H~\cite{TPC-H} data expressed in RDF, LUBM, BSBM, and SP$^2$Bench) and 6 real-wold data sets (such as, e.g.,  DBpedia, the Barton Libraries Dataset~\cite{barton-benchmark} or
 WordNet~\cite{Miller:1995:WLD:219717.219748}) has been reported by~\cite{Duan:2011:AOC:1989323.1989340}.
@@
 \paragraph{RBench} RBench~\cite{Qiao:2015:RAR:2723372.2746479} is an application-specific benchmark which receives any RDF dataset as an input and produces as an output a set of datasets, that have similar characteristics of the input dataset, using size scaling factor $s$ and (node) degree scaling factor $d$.
+These factors ensure that the original RDF graph $G$ and the synthetic graph $G'$ are similar and the number of edges and the average node degree of $G'$ are changed by $s$ and $d$ respectively.
 \iffalse A generated benchmark dataset is considered similar to the given dataset if their values for the dataset evaluation metrics and query evaluation times for different techniques are similar.
@@
 
-\paragraph{LDBC}  The Linked Data Benchmark Council\footnote{\url{http://ldbcouncil.org/industry/organization/origins}} (LDBC)~\cite{Angles:2014:LDB:2627692.2627697} is a result of a (closed) EU project that brought together a community of academic researchers and industry that had the goal of developing an open source, yet industrial grade benchmarks for RDF and graph databases.
-\iffalse The following three benchmarks were developed and are currently maintained.\fi In the Semantic Web domain, the project released the Semantic Publishing Benchmark (SPB)~\cite{spb} that has been inspired by the Media/Publishing industry (namely BBC\footnote{\url{http://www.bbc.com/}}).
+\paragraph{LDBC}  The Linked Data Benchmark Council\footnote{\url{http://ldbcouncil.org/industry/organization/origins}} (LDBC)~\cite{Angles:2014:LDB:2627692.2627697} %is a result of a (closed) EU project that brought together a community of academic researchers and industry that
+had the goal of developing an open source, yet industrial grade benchmarks for RDF and graph databases.
+\iffalse The following three benchmarks were developed and are currently maintained.\fi In the Semantic Web domain, it released the Semantic Publishing Benchmark (SPB)~\cite{spb} that has been inspired by the Media/Publishing industry (namely BBC\footnote{\url{http://www.bbc.com/}}).
 The application scenario of this benchmark simulates a media or a publishing organization that handles large amount of streaming content (e.g., news, articles).

### 2019-06-16 generators_community_detection.tex
Reviewer's comments - part II.

@@
-\subsection{Community Detection}
+\subsection{Testing Community Detection}
 \label{sec:generators_community_detection}
@@
 Community detection is one of the many graph analytics algorithms typically used
-on domains such as social networks or bioinformatics. Communities are groups of nodes that are highly connected among them, while being scarcely connected to
+in domains such as social networks or bioinformatics. \emph{Communities} are groups of nodes that are highly connected among them, while being scarcely connected to
 the rest of the graph. Such communities emerge from the fact that real graphs

### 2019-06-29 generators_LinkedData.tex
Sherif Changes on Structure
Sherif Changes on Structure

@@
 
-\paragraph{Comparison of Data Coherence in TPC-H, LUBM, BSBM, and SP$^2$Bench}  A comparison of 4 RDF benchmarks (namely TPC-H~\cite{TPC-H} data expressed in RDF, LUBM, BSBM, and SP$^2$Bench) and 6 real-wold data sets (such as, e.g.,  DBpedia, the Barton Libraries Dataset~\cite{barton-benchmark} or
-WordNet~\cite{Miller:1995:WLD:219717.219748}) has been reported by~\cite{Duan:2011:AOC:1989323.1989340}.
-The authors focus mainly on the  \emph{structuredness} (\emph{coherence}) of each benchmark dataset claiming that a primitive metric (e.g., the number of triples or the average in/outdegree) quantifies only some target characteristics of each dataset.
-The degree of structuredness of a dataset $D$ with respect to a type $T$ is based on  the regularity of instance data in $D$ in conforming to type $T$.
-The type system is extracted from the data set by finding the RDF triples that have property  \texttt{http://www.w3.org/1999/02/22-rdf-syntax-ns\#type} and extract type $T$ from their object.
-Properties of $T$ are determined as the union of all the properties that the instances of type $T$ have.
-The structuredness is then expressed as a weighted sum of share of set properties of each type, whereas higher weights are assigned to types with more instances.
-The authors show that the structuredness of the chosen benchmarks is fixed, whereas real-world RDF datasets are belonging to the non-tested area of the spectrum.
-As a consequence, they introduce a new benchmark that receives as input any dataset associated with a required level of structuredness and size (smaller than the size of the original data), and exploits the input documents as a seed to produce a subset of the original data with the target structuredness and size.
-In addition, they show that structuredness and size mutually influence each other.
-
 \paragraph{DBPSB} DBpedia SPARQL Benchmark (DBPSB)\footnote{\url{http://aksw.org/Projects/DBPSB.html}} proposed at the University of Leipzig has been designed using workloads that have been issued by humans and applications over existing RDF data~\cite{Morsey2011,Morsey:2012:UBR:2900929.2901031}.
@@
 The data sets reflect the same e-commerce scenario used for BSBM.
-
-\paragraph{SIB} The developers of the Social Network Intelligence BenchMark (SIB)\footnote{\url{https://www.w3.org/wiki/Social_Network_Intelligence_BenchMark}} based the design of their benchmark on the claim that existing benchmarks are limited in reflecting the characteristics of the real RDF databases and are mostly focusing on the relational style aspects.
-Hence, they proposed a benchmark for  query evaluation using real graphs~\cite{sib}.
-The proposed benchmark mimics using an RDF store for a social network.
-\iffalse site where users and their interactions form a social graph of social activities such as creating/managing groups, writing posts and posting comments.\fi The distribution of the generated data for each type follows the  distribution of the associated type inferred from real-world social networks.
-Additionally, association rules are exploited for representing the real-world data correlation in the generated synthetic data.
-The  generated data is linked with the RDF datasets from DBpedia.
-The benchmark specification contains 3 query mixes -- interactive, update, and analysis -- expressed in SPARQL 1.1 Working Draft.
 
@@
 
+In practice, one way for handling big RDF graphs is to process them using the
+\emph{streaming} mode where the data stream could consist of the edges of the
+graph. In this mode, the RDF processing algorithms can process the input
+stream in the order it arrives while using only a limited amount of
+memory~\cite{mcgregor2014graph}. The streaming mode has mainly  attracted the attention of the
+RDF and Semantic Web community.
+
+\paragraph{S2Gen}   Phuoc et al.~\cite{le2012linked} presented
+an evaluation framework for linked stream data processing engines. The framework
+uses a datasets generated with the Stream Social network data Generator
+(S2Gen), which
+simulates streams of user interactions (or events) in social networks
+(e.g., posts) in addition to the  user metadata such as users' profile
+information, social network relationships, posts, photos and GPS information.
+The data generator of this framework provides the users the flexibility to
+control the characteristics of the generated stream by tanning a range of
+parameters, which includes the frequency at which interactions are generated,
+limits such as the maximum number of messages per user
+and week, and the correlation probabilities between the different objects (e.g.,
+users) in the social network.
+
+\paragraph{RSPLab} Tommasini et al.~\cite{tommasini2017rsplab} introduced
+another framework for benchmarking RDF Stream Processing systems, RSPLab. The
+Streamer component of this framework is designed to publish RDF streams from the
+various existing RDF benchmarks (e.g., BSBM, LUBM) (see Section~\ref{sec:generators_LinkedData}).
+In particular, the Streamer  component uses TripleWave\footnote{\url{http://streamreasoning.github.io/TripleWave/}}, an
+open-source framework for publishing and sharing RDF streams on the
+Web~\cite{mauri2016triplewave}.   TripleWave acts as a means for plugging-in
+and combining streams from multiple Web data sources, in both push and pull mode.
+
 \paragraph{LDBC}  The Linked Data Benchmark Council\footnote{\url{http://ldbcouncil.org/industry/organization/origins}} (LDBC)~\cite{Angles:2014:LDB:2627692.2627697} %is a result of a (closed) EU project that brought together a community of academic researchers and industry that
@@
 The datasets can be generated in any of of two modes: on-disk and streaming.
+
+\paragraph{Strengths and Weaknesses of Semantic Web Graph Generators.}  A comparison of 4 RDF benchmarks (namely TPC-H~\cite{TPC-H} data expressed in RDF, LUBM, BSBM, and SP$^2$Bench) and 6 real-wold data sets (such as, e.g.,  DBpedia, the Barton Libraries Dataset~\cite{barton-benchmark} or
+WordNet~\cite{Miller:1995:WLD:219717.219748}) has been reported by~\cite{Duan:2011:AOC:1989323.1989340}.
+The authors focus mainly on the  \emph{structuredness} (\emph{coherence}) of each benchmark dataset claiming that a primitive metric (e.g., the number of triples or the average in/outdegree) quantifies only some target characteristics of each dataset.
+The degree of structuredness of a dataset $D$ with respect to a type $T$ is based on  the regularity of instance data in $D$ in conforming to type $T$.
+The type system is extracted from the data set by finding the RDF triples that have property  \texttt{http://www.w3.org/1999/02/22-rdf-syntax-ns\#type} and extract type $T$ from their object.
+Properties of $T$ are determined as the union of all the properties that the instances of type $T$ have.
+The structuredness is then expressed as a weighted sum of share of set properties of each type, whereas higher weights are assigned to types with more instances.
+The authors show that the structuredness of the chosen benchmarks is fixed, whereas real-world RDF datasets are belonging to the non-tested area of the spectrum.
+As a consequence, they introduce a new benchmark that receives as input any dataset associated with a required level of structuredness and size (smaller than the size of the original data), and exploits the input documents as a seed to produce a subset of the original data with the target structuredness and size.
+In addition, they show that structuredness and size mutually influence each other.

### 2019-06-29 generators_SocialNetworks.tex
Sherif Changes on Structure
Sherif Changes on Structure

@@
 
+\paragraph{SIB} The developers of the Social Network Intelligence BenchMark (SIB)\footnote{\url{https://www.w3.org/wiki/Social_Network_Intelligence_BenchMark}} based the design of their benchmark on the claim that existing benchmarks are limited in reflecting the characteristics of the real RDF databases and are mostly focusing on the relational style aspects.
+Hence, they proposed a benchmark for  query evaluation using real graphs~\cite{sib}.
+The proposed benchmark mimics using an RDF store for a social network.
+\iffalse site where users and their interactions form a social graph of social activities such as creating/managing groups, writing posts and posting comments.\fi The distribution of the generated data for each type follows the  distribution of the associated type inferred from real-world social networks.
+Additionally, association rules are exploited for representing the real-world data correlation in the generated synthetic data.
+The  generated data is linked with the RDF datasets from DBpedia.
+The benchmark specification contains 3 query mixes -- interactive, update, and analysis -- expressed in SPARQL 1.1 Working Draft.
+
 \paragraph{Cloning of Social Networks} ~\cite{Sukthankar-SocialInfo2014}

### 2019-06-29 generators_streaming.tex
Sherif Changes on Structure
Sherif Changes on Structure

@@
 \label{sec:generators_streaming}
-One way for dealing with big graphs is to process them using the
-\emph{streaming} mode where the data stream could consist of the edges of the
-graph. In this mode, the graph processing algorithms can process the input
-stream in the order it arrives while using only a limited amount of
-memory~\cite{mcgregor2014graph}.
-
-\paragraph{S2Gen}  The streaming mode has mainly  attracted the attention of the
-RDF and Semantic Web community. Thus, Phuoc et al.~\cite{le2012linked} presented
-an evaluation framework for linked stream data processing engines. The framework
-uses a datasets generated with the Stream Social network data Generator
-(S2Gen), which 
-simulates streams of user interactions (or events) in social networks 
-(e.g., posts) in addition to the  user metadata such as users' profile
-information, social network relationships, posts, photos and GPS information.
-The data generator of this framework provides the users the flexibility to
-control the characteristics of the generated stream by tanning a range of
-parameters, which includes the frequency at which interactions are generated, 
-limits such as the maximum number of messages per user
-and week, and the correlation probabilities between the different objects (e.g.,
-users) in the social network.
-
-\paragraph{RSPLab} Tommasini et al.~\cite{tommasini2017rsplab} introduced
-another framework for benchmarking RDF Stream Processing systems, RSPLab. The
-Streamer component of this framework is designed to publish RDF streams from the
-various existing RDF benchmarks (e.g., BSBM, LUBM) (see Section~\ref{sec:generators_LinkedData}).
-In particular, the Streamer  component uses TripleWave\footnote{\url{http://streamreasoning.github.io/TripleWave/}}, an
-open-source framework for publishing and sharing RDF streams on the
-Web~\cite{mauri2016triplewave}.   TripleWave acts as a means for plugging-in
-and combining streams from multiple Web data sources, in both push and pull mode.

### 2019-07-01 generators_LinkedData.tex
Linked Data Changes
Linked Data Changes

@@
 
-\paragraph{Strengths and Weaknesses of Semantic Web Graph Generators.}  A comparison of 4 RDF benchmarks (namely TPC-H~\cite{TPC-H} data expressed in RDF, LUBM, BSBM, and SP$^2$Bench) and 6 real-wold data sets (such as, e.g.,  DBpedia, the Barton Libraries Dataset~\cite{barton-benchmark} or
+\paragraph{Strengths and Weaknesses of Semantic Web Graph Generators.}  Graphs are intuitive and standard representation for the RDF model that form the basis for the Semantic Web community which has been very active on building several benchmarks, associated with graph generators that had various design principles.
+A comparison of 4 RDF benchmarks (namely TPC-H~\cite{TPC-H} data expressed in RDF, LUBM, BSBM, and SP$^2$Bench) and 6 real-wold data sets (such as, e.g.,  DBpedia, the Barton Libraries Dataset~\cite{barton-benchmark} or
 WordNet~\cite{Miller:1995:WLD:219717.219748}) has been reported by~\cite{Duan:2011:AOC:1989323.1989340}.
@@
 In addition, they show that structuredness and size mutually influence each other.
+With the recent increasing momentum of streaming data, the Semantic Web community started to consider the issues and challenges of RDF streaming data.
+However, there is still a lot of open challenges that needs to tackled in this direction such as covering different real-world application scenarios.

### 2019-07-14 generators_community_detection.tex
Added stochastic block models

@@
 
+\paragraph{Stochastic Block Models} Another popular famility of generators
+widely use in the community detection field are the stochastic block
+models~\cite{holland1983stochastic}. In such models, the community structure of
+the graph is typically defined as an array of $n$ community or clusters sizes,
+and a density square matrix of size $nxn$ containing the density of
+intra-cluster edges (in the diagonal of the matrix) and the density of
+inter-cluster edges. Then, an stochastic procedure is run to sample graphs
+from such array and matrix, using the sizes to compute the possible edges
+and the densities as probabilities of such edges to exist. The popularity of
+these methods stem from its simplicity and scalability, which makes them
+suitable for generating large graphs fast and in a distributed environments,
+provided that the density matrix is sparse (as it happens in most of real
+                                            world graphs). Moreover, given
+that the generation process of such models is mathematically tractable, they
+are typically used to analyze the limitations of community detection
+algorithms such as those based on modularity
+optimization~\cite{fortunato2007resolution} or based on
+triads~\cite{prat2016put}. Extensions of such models exist, such as the
+Mixed Membership Stochastic Block Model~\cite{arioldi2008mixed}, for
+overlapping communities.
+
 \paragraph{Strengths and Weaknesses of Community Detection Generators}

### 2019-07-17 generators_general.tex
merged 3.5 with 3.1; Tables I and II updated

@@
 bipartite graphs.
+
+\paragraph{HPC Scalable Graph Analysis Benchmark} The HPC Scalable Graph
+Analysis Benchmark~\cite{HPCgraph,Bader:2005:DIH:2099301.2099360} consists of a
+weighted, directed graph that has a power-law distribution and four related
+analysis techniques (namely graph construction, graph extraction with BFS,
+                     classification of large vertex sets, and graph analysis
+                     with betweenness centrality). The generator has the
+following parameters: the number of nodes, the number of edges, and maximum weight of
+an edge. It outputs a list of tuples containing identifiers of vertices of an
+edge (with the direction from the first one to the second one) and weights
+(positive integers  with a uniform random distribution) assigned to the edges of
+the multigraph.  The algorithm of the generator is based on R-MAT. 
+%To reduce the data
+%locality, the vertex ids are randomly permuted and the output
+%tuples are shuffled. A related project from the same authors
+%developed for the 9th DIMACS Shortest Paths Challenge is GTgraph~\cite{GTgraph}.
+%t involves three types of graphs: (1) Erd\"{o}s-R\'{e}nyi random graphs, (2)
+%different graphs from the DARPA HPCS SSCA\#2 graph theory benchmark
+%(version 1.0), and (3) small-world graphs generated using the R-MAT graph
+%generator.
 

### 2019-07-23 comparison.tex
Added stochastic block models
merged 3.5 with 3.1; Tables I and II updated
Consolidation of sectioms 1-2 with the rest

@@
 For example,~\cite{DBLP:conf/sdm/ChakrabartiZF04} introduces two categories -- degree-based and procedural generators.
-In general, \emph{degree-based generators} (e.g., Barabasi-Albert model~\cite{Barabasi99emergenceScaling}) are commonly attempting to find a graph that matches it, but without providing any information about the graph or attempting to match other graph features (e.g., eigenvalues, small diameter, ..., etc).
-On the other hand, \emph{procedural generators} (e.g., R-MAT~\cite{DBLP:conf/sdm/ChakrabartiZF04}) are commonly targeting simple techniques to produce graphs that are matching the characteristics of the real graphs (e.g., the power law degree distribution).
+In general, \emph{degree-based generators} (e.g., Barabasi-Albert model~\cite{Barabasi99emergenceScaling}) are commonly attempting to find a graph that matches it, but without providing any information about the graph or attempting to match other graph features (e.g., eigenvalues, small diameter, etc).
+On the other hand, \emph{procedural generators} (e.g., R-MAT~\cite{DBLP:conf/sdm/ChakrabartiZF04}) are commonly targeting simple techniques to produce graphs that are matching the characteristics of the real-world graphs (e.g., the power law degree distribution).
 
@@
 At first we classify the generators on the basis of the respective application domains or user communities.
-In particular we distinguish (1) general graphs, (2) Semantic Web, (3) graph databases, (4) social networks, (5) graph analytics, (6) community detection, and (7) graph data streaming.
+In particular we distinguish (1) general graphs, (2) Semantic Web, (3) graph databases, (4) social networks, and (5) community detection.
 The selected classes are not rigorously defined (e.g., they are not disjoint as we will show later), but they correspond to the currently most active research areas.
@@
 
-In Table~\ref{tab:comparisonCharacteristics}   we overview the key characteristics of the data generators clustered according to the respective application domains.\footnote{``GDBs'' stands for graph databases, ``SNs'' stands for social networks, ``A'' stands for graph analytics, ``Co'' stands for community detection, and ``St'' stands for graph streaming.
+In Table~\ref{tab:comparisonCharacteristics}   we overview the key characteristics of the data generators clustered according to the respective application domains.\footnote{``GDBs'' stands for graph databases, ``SNs'' stands for social networks, and ``Co'' stands for community detection.
 Value ``$-$'' means that the information is not available or relevant.} In particular, we show:
@@
 \begin{itemize}
-\item Characteristics of the \textbf{domain} -- its \textit{type} (column ``Type''), i.e.,  fixed, specified using a schema, or extracted from input data and the particular \textit{target} domain, or, in case of a generic tool, the chosen sample domain (column ``Target/sample''),
+\item Characteristics of the \textbf{domain}:
+    \begin{itemize}
+      \item its \textit{type} (column ``Type''), i.e.,  fixed, specified using a schema, or extracted from input data, and
+      \item the particular \textit{target} domain, or, in case of a generic tool, the chosen sample domain (column ``Target/sample'').
+\end{itemize}
 \item Characteristics of \textit{read}/\textit{update} \textbf{operations} (columns ``Read'' and ``Update''), i.e., whether the set of operations is fixed/generated, if it involves operation mixes (i.e., sets/sequences of operations), or if templates of operations are supported.
@@
 \hline   % ====================== general graphs
-\multirow{5}{*}{\rot{\textbf{General}}}
+\multirow{6}{*}{\rot{\textbf{General}}}
   & Preferential attachment & -- & -- & N & N & Y & power-law & edge-list &  N  \\
@@
    & R-MAT & -- & -- & N & N & Y & power-law & edge-list &  N  \\
+\cline{2-10}
+  & HPC Scal. Graph Anal. & fixed & -- & fixed & N& N& uniform &edge-list & N   \\
 \cline{2-10}
@@
 \hline %  ======================  Semantic web
-\multirow{19}{*}{\rot{\textbf{Semantic web}}}
+\multirow{16}{*}{\rot{\textbf{Semantic Web}}}
  & LUBM & fixed & university  & fixed & N & Y & random (LCG) &  RDF & N   \\
 \cline{2-10}
- & LBBM & extracted & Lehigh university BibTeX  & N & N & Y & Monte Carlo &  RDF & N   \\
-\cline{2-10}
- & UOBM & fixed & university  & fixed & N & Y & random &  RDF & N   \\
-\cline{2-10}
+% & LBBM & extracted & Lehigh university BibTeX  & N & N & Y & Monte Carlo &  RDF & N   \\
+%\cline{2-10}
+% & UOBM & fixed & university  & fixed & N & Y & random &  RDF & N   \\
+%\cline{2-10}
  & IIMB & fixed & movies  & N & N & Y & random &  RDF & N   \\
@@
 \cline{2-10}
- & SIB & fixed & social network &  mixes & mix & Y & from real-world data &  RDF & N   \\
-\cline{2-10}
  & Geographica & fixed & OpenStreetMap  & fixed + templates  & N & Y & -- &  RDF & N   \\
@@
  & RBench & extracted & DBLP, Yago  & templates & N & Y & from real-world data &  RDF & N  \\
+\cline{2-10}
+ & S2Gen & schema-driven & social network & Y & N & N & user-defined & RDF & N     \\
+\cline{2-10}
+ & RSPLab & schema-driven & agnostic & Y & Y & N & user-defined & RDF & N     \\
 \cline{2-10}
@@
 \hline %  ======================   social networks
-\multirow{7}{*}{\rot{\textbf{SNs}}}
+\multirow{8}{*}{\rot{\textbf{SNs}}}
  & \cite{Barrett:2009:GAL:1995456.1995598} & fixed & social network & N & N & Y & simulation-driven & impl. NA &  -- \\
@@
  & S3G2 & fixed & social network  & N & N  & Y & Facebook  & CSV, RDF & Y   \\
+\cline{2-10}
+ & SIB & fixed & social network &  mixes & mix & Y & from real-world data &  RDF & N   \\
 \cline{2-10}
@@
 % & Forest Fire  & N & Y   & N &  & N & power-law &  ? & N   \\
-\hline
-\hline   % ======================   graph analytics
-\multirow{1}{*}{\rot{\textbf{A}}}
-  & HPC Scal. Graph Anal. & fixed & -- & fixed & N& N& uniform &edge-list & N   \\
+%\hline
+%\hline   % ======================   graph analytics
+%\multirow{1}{*}{\rot{\textbf{A}}}
+%  & HPC Scal. Graph Anal. & fixed & -- & fixed & N& N& uniform &edge-list & N   \\
 %\cline{2-10}
@@
 \hline   %  ======================  community detection
-\multirow{3}{*}{\rot{\textbf{Co}}}
-  & Danon et al. & -- & -- & Y & N & N & uniform & edge-list &  N    \\
+\multirow{4}{*}{\rot{\textbf{Co}}}
+  & \cite{danon2005comparing} & -- & -- & Y & N & N & uniform & edge-list &  N    \\
 \cline{2-10}
@@
   & LFR-Overlapping & -- & -- & Y & N & N & power-law & edge-list & N     \\
+\cline{2-10}
+  & Stochastic Block Models & -- & -- & Y & N & N & user-defined & edge-list & Y     \\
 \hline
-\hline   %  ======================  streaming
-\multirow{2}{*}{\rot{\textbf{St}}}
-  & S2Gen & schema-driven & social network & Y & N & N & user-defined & RDF & N     \\
-\cline{2-10}
-  & RSPLab & schema-driven & agnostic & Y & Y & N & user-defined & RDF & N     \\
+%\hline   %  ======================  streaming
+%\multirow{2}{*}{\rot{\textbf{St}}}
+%  & S2Gen & schema-driven & social network & Y & N & N & user-defined & RDF & N     \\
+%\cline{2-10}
+%  & RSPLab & schema-driven & agnostic & Y & Y & N & user-defined & RDF & N     \\
 %\cline{2-10}
 %  & & & & & & & &  &   \\
-\hline
 \end{tabular} }
@@
 None of these generators is natively implemented in a distributed manner and thus primarily generating  output at the Big Data scale.
-On the other hand, the \emph{Linked Open Data} (LOD) is expected to be large in general, however this is the case of the whole \emph{LOD Cloud}\footnote{\url{https://lod-cloud.net/}}, but not necessarily of the particular data sets forming it.
+On the other hand, the \emph{Linked Open Data} (LOD) is expected to be large in general; however, this is the case of the whole \emph{LOD Cloud}\footnote{\url{https://lod-cloud.net/}}, but not necessarily of the particular data sets forming it.
 
@@
 \tbl{Overlapping of classes of generators} {
-\begin{tabular}{| c | l | l | l | l | l | l | l | l | }
+\begin{tabular}{| c | l | l | l | l | l | l | l | }
  \hline
@@
                & \textbf{\rot{Social networks}}
-               & \textbf{\rot{Analytics}}
-               & \textbf{\rot{Community detection}}
-               & \textbf{\rot{Streaming}}
+               %& \textbf{\rot{Analytics}}
+               & \textbf{\rot{Community detection\ }}
+               %& \textbf{\rot{Streaming}}
                \\ \hline
 \hline   % ====================== general graphs
-\multirow{5}{*}{\rot{\textbf{General}}}
-  & Preferential attachment & {\bf x} & & & & x & & \\
-\cline{2-9}
-   & R-MAT    & {\bf x} & & & & x & & \\
-\cline{2-9}
-  & GraphGen  & {\bf x} & & x & & & & \\
-\cline{2-9}
-%  & Graph 500 & {\bf x} & & & & x & & \\
-%\cline{2-9}
-  & BTER      & {\bf x} & & & & & & \\
-\cline{2-9}
-  & Darwini   & {\bf x} & & & & & & \\
+\multirow{6}{*}{\rot{\textbf{General}}}
+  & Preferential attachment & {\bf x} & & &  & \\
+\cline{2-7}
+   & R-MAT    & {\bf x} & & &  &  \\
+\cline{2-7}
+   & HPC Scal. Graph Anal.  & {\bf x} & & &  &  \\
+\cline{2-7}
+  & GraphGen  & {\bf x} & & x &  & \\
+\cline{2-7}
+%  & Graph 500 & {\bf x} & & &  & \\
+%\cline{2-7}
+  & BTER      & {\bf x} & & &  & \\
+\cline{2-7}
+  & Darwini   & {\bf x} & & &  & \\
 \hline
 \hline %  ======================  Semantic web
-\multirow{15}{*}{\rot{\textbf{Semantic web}}}
- & LUBM  & & {\bf x} & & & & & \\
-\cline{2-9}
- & LBBM  & & {\bf x} & & & & & \\
-\cline{2-9}
- & UOBM  & & {\bf x} & & & & & \\
-\cline{2-9}
- & IIMB & & {\bf x} & & & & & \\
-\cline{2-9}
- & BSBM & & {\bf x} & & & & & \\
-\cline{2-9}
- & SP$^2$Bench & & {\bf x} & & & & & \\
-\cline{2-9}
- & \cite{Duan:2011:AOC:1989323.1989340} & & {\bf x} & & & & & \\
-\cline{2-9}
- & DBPSB & & {\bf x} & & & & & \\
-\cline{2-9}
- & LODIB & & {\bf x} & & & & & \\
-\cline{2-9}
- & SIB & & {\bf x} & & & & & \\
-\cline{2-9}
- & Geographica & & {\bf x} & & & & & \\
-\cline{2-9}
- & WatDiv & & {\bf x} & & & & & \\
-\cline{2-9}
- & RBench & & {\bf x} & & & & & \\
-\cline{2-9}
- & LDBC SPB & & {\bf x} & & & & & \\
-\cline{2-9}
- & LinkGen & & {\bf x} & & & & & \\
+\multirow{14}{*}{\rot{\textbf{Semantic web}}}
+ & LUBM  & & {\bf x} & &  &  \\
+\cline{2-7}
+% & LBBM  & & {\bf x} & &  &  \\
+%\cline{2-7}
+% & UOBM  & & {\bf x} & &  &  \\
+%\cline{2-7}
+ & IIMB & & {\bf x} & &  & \\
+\cline{2-7}
+ & BSBM & & {\bf x} & &  &  \\
+\cline{2-7}
+ & SP$^2$Bench & & {\bf x} & &  &  \\
+\cline{2-7}
+ & \cite{Duan:2011:AOC:1989323.1989340} & & {\bf x} & &  &  \\
+\cline{2-7}
+ & DBPSB & & {\bf x} & &  &  \\
+\cline{2-7}
+ & LODIB & & {\bf x} & &  &  \\
+\cline{2-7}
+% & SIB & & {\bf x} & &  &  \\
+%\cline{2-7}
+ & Geographica & & {\bf x} & &  &  \\
+\cline{2-7}
+ & WatDiv & & {\bf x} & &  &  \\
+\cline{2-7}
+ & RBench & & {\bf x} & &  &  \\
+\cline{2-7}
+  & S2Gen & & {\bf x} & &  &  \\
+\cline{2-7}
+  & RSPLab & & {\bf x} & &  &  \\
+\cline{2-7}
+ & LDBC SPB & & {\bf x} & &  &  \\
+\cline{2-7}
+ & LinkGen & & {\bf x} & &  &  \\
 \hline
@@
 \multirow{3}{*}{\rot{\textbf{GDBs}}}
-  & XGDBench & & & {\bf x} & x & & & \\
-\cline{2-9}
-  & gMark & & x & {\bf x} & x & & & \\
-\cline{2-9}
-  & graphGen & & & {\bf x} & & & & \\
+  & XGDBench & & & {\bf x} & x  &  \\
+\cline{2-7}
+  & gMark & & x & {\bf x} & x  &  \\
+\cline{2-7}
+  & graphGen & & & {\bf x} &  &  \\
 \hline
 \hline %  ======================   social networks
-\multirow{7}{*}{\rot{\textbf{SNs}}}
- & \cite{Barrett:2009:GAL:1995456.1995598} & & & & {\bf x} & & & \\
-\cline{2-9}
- & \cite{Yao2011}  & & & & {\bf x} & & & \\
-\cline{2-9}
- & LinkBench  & & & x & {\bf x} & & & \\
-\cline{2-9}
- & S3G2  & & x & x & {\bf x} & & & \\
-\cline{2-9}
- & \cite{Sukthankar-SocialInfo2014}  & & & & {\bf x} & & & \\
-\cline{2-9}
- & LDBC SNB   & & x & x & {\bf x} & & & \\
-\cline{2-9}
-  & \cite{Nettleton2016}  & & & & {\bf x} & & & \\
-\hline
-\hline   % ======================   graph analytics
-\multirow{1}{*}{\rot{\textbf{A}}}
-  & HPC Scal. Graph Anal.  & & & & & {\bf x} & & \\
-%\cline{2-9}
-%  & Graphalytics & & & & & {\bf x} & & \\
+\multirow{8}{*}{\rot{\textbf{SNs}}}
+ & \cite{Barrett:2009:GAL:1995456.1995598} & & & & {\bf x}  & \\
+\cline{2-7}
+ & \cite{Yao2011}  & & & & {\bf x}  & \\
+\cline{2-7}
+ & LinkBench  & & & x & {\bf x}  & \\
+\cline{2-7}
+ & S3G2  & & x & x & {\bf x}  & \\
+\cline{2-7}
+ & SIB & & x & & {\bf x}  &  \\
+\cline{2-7}
+ & \cite{Sukthankar-SocialInfo2014}  & & & & {\bf x}  & \\
+\cline{2-7}
+ & LDBC SNB   & & x & x & {\bf x}  & \\
+\cline{2-7}
+  & \cite{Nettleton2016}  & & & & {\bf x}  &  \\
+%\hline
+%\hline   % ======================   graph analytics
+%\multirow{1}{*}{\rot{\textbf{A}}}
+%  & HPC Scal. Graph Anal.  & & & & &  \\
+%\cline{2-7}
+%  & Graphalytics & & & & &  \\
 \hline
 \hline   %  ======================  community detection
-\multirow{3}{*}{\rot{\textbf{Co}}}
-  & Danon et al. & x & & & & x & {\bf x} &\\
-\cline{2-9}
-  & LFR & x & & & & x & {\bf x} & \\
-\cline{2-9}
-  & LFR-Overlapping & x & & & & x & {\bf x} & \\
-%\cline{2-9}
-%  & & & & & & \\
+\multirow{4}{*}{\rot{\textbf{Co}}}
+  & \cite{danon2005comparing} & x & & & &  {\bf x} \\
+\cline{2-7}
+  & LFR & x & & & &  {\bf x}  \\
+\cline{2-7}
+  & LFR-Overlapping & x & & & &  {\bf x} \\
+\cline{2-7}
+  & Stochastic Block Models & x & & & &  {\bf x} \\
+%\cline{2-7}
+%  & & & & &  \\
 \hline
-\hline   %  ======================  streaming
-\multirow{2}{*}{\rot{\textbf{St}}}
-  & S2Gen & & & & & & & {\bf x}\\
-\cline{2-9}
-  & RSPLab & & & & & & & {\bf x} \\
-%\cline{2-9}
-%  & & & & & & & \\
-\hline
+%\hline   %  ======================  streaming
+%\multirow{2}{*}{\rot{\textbf{St}}}
+%  & S2Gen & & & & & & & {\bf x}\\
+%\cline{2-7}
+%  & RSPLab & & & & & & & {\bf x} \\
+%%\cline{2-7}
+%%  & & & & & & \\
+%\hline
 \end{tabular} }
@@
 
-Similarly, some social network graph generators such as LDBC-SNB, S3G2 or
+Similarly, some social network graph generators such as LDBC SNB, S3G2 or
 LinkBench, can be used to test graph databases. In the case of the first two,
@@
 test a workload similar to Facebook and extend and complement it with more
-graph queries like those in LDBC-SNB.
+graph queries like those in LDBC SNB.
 

### 2019-07-23 introduction.tex
Minor changes
Removed section 4, modified bibliography
Consolidation of sectioms 1-2 with the rest

@@
 Naturally, the algorithms used in theses two classes differ a lot~\cite{DBLP:books/igi/Sakr2011}.
-In the former case we can search, e.g., for communities and their features or shortest paths, while in the latter case we usually query for supergraphs, subgraphs or graphs similar to a given graph pattern.
+In the former case we can search, e.g., for communities and their features or shortest paths, while in the latter case we usually query for supergraphs, subgraphs, or graphs similar to a given graph pattern.
 In both the cases, as in the other fields, quite often the respective real-world graph data is not publicly available (or simply does not exist when a particular method for data manipulation is proposed).
-Even in the cases in which real data is abundant, many algorithms and techniques need to be tested on various order of magnitudes of the graph sizes thus leading to the inception of
+Even in the cases in which real data is abundant, many algorithms and techniques need to be tested on various orders of magnitudes of the graph sizes thus leading to the inception of
 configurable graph generators that reproduce real-world graph properties and provide unique tuning opportunities for
@@
 areas of graph data processing. In particular, we consider graph generation
-in the areas of graph databases, Semantic Web, social networks, graph streaming, alongside community detection  and graph data analytics.
+in the areas of Semantic Web, graph databases, social networks, and community detection, along with general graphs.
 Despite the disparate requirements of modern graph generators throughout these communities, we analyze them under a common umbrella, reaching out the functionalities, the practical usage, and the supported operations of graph generators.
@@
 modern graph data generators can be similar in particular cases. Reusing or learning from tools in other fields can thus bring new opportunities for both researchers and practitioners.
-  \item The selected classification is serving the need of providing scientists, researchers and practitioners with the right data generator at hand for their work.
+  \item The selected classification is serving the need of providing scientists, researchers, and practitioners with the right data generator at hand for their work.
 \end{enumerate}
@@
 Hence, while practitioners can find a solution in another previously unexpected area, researchers can identify new target areas or exploit successful results in new fields.
-Last but not least, to provide a global view of the state-of-the-art, we also provide an overview of most commonly used real-world testing graph datasets.
-And, finally, we identify general open problems of graph data synthesis and indicate possible solutions to show that it still forms a challenging and promising research area.
+Last but not least, %to provide a global view of the state-of-the-art, we also provide an overview of most commonly used real-world testing graph datasets.
+And, finally,
+we identify general open problems of graph data synthesis and indicate possible solutions to show that it still forms a challenging and promising research area.
 
@@
 targeting many computer science subfields.
-In particular, we cover graph databases, Semantic Web, social networks, graph streaming, community detection, and graph data analytics.
+In particular, we cover Semantic Web, graph databases, social networks, and community detection, along with general graphs.
 However, the literature is still lacking a comprehensive study of graph generators  for many of the specific subfields mentioned above.
@@
 generator based on its functional and goal-driven features (such as the application domain,
-the supported operations and the key configuration options).
+the supported operations, and the key configuration options).
 Moreover, in contrast with \cite{BFHI18}, our work encompasses graph generators of several
@@
 studied in \cite{Chakrabarti:2006:GML:1132952.1132954},
-focusing on mostly occurring patterns, such as power laws, size of graph diameters
+focusing on mostly occurring patterns, such as power laws, size of graph diameters,
 and community structure. The considered graph generators are compared in
-terms of graph type, degree distributions, exponentiality, diameter and
+terms of graph type, degree distributions, exponentiality, diameter, and
 community effects. We refer the reader to this survey for taxonomies
@@
 generators that appeared in the last decade.
-We fill the gap of more recent social network and graph analytics generators
-respectively in Section 3.4 and 3.5.
+We fill the gap of more recent social network generators
+in Section~\ref{sec:generators_socialnetworks}, as well as more recent representatives of the other categories.
 
@@
 network data generators is carried out in
-the paper. The data generation of evolutionary networks is based on
+the paper. The data generation of evolutionary networks is based on the
 Densification Power Law (DPL) and shrinking diameters, community-guided
@@
 recursion with recursive tensor multiplication~\cite{AkogluMF08} is then considered in the above survey.
-We refer the readers to the aforementioned survey for evolutionary network generators and further discuss the open challenges of evolving graph data in Section 5.
+We refer the readers to the aforementioned survey for evolutionary network generators and further 
+discuss the open challenges of evolving graph data in Section~\ref{sec:challenges}.
 %\TODO{Better highlight the differences when Sherif's part is in.}
@@
 
-\paragraph*{Outline} The rest of this paper is organized as follows: Section~\ref{sec:comparison}  provides the opening categorization and comparison of the generators.
-Section~\ref{sec:generators} provides an overview of the existing graph data generators and their main features in the frame of the proposed categories.
-To provide a complete overview,  we list the most commonly used testing data sets for the particular categories in Section~\ref{sec:data_sets}.
-In Section~\ref{sec:challenges}, we highlight some of the challenges and open problems of graph data synthesis before we conclude in Section~\ref{sec:conclusion}.
+\paragraph*{Outline} The rest of this paper is organized as follows: Section~\ref{sec:comparison}  
+provides the opening categorization and comparison of the generators. Section~\ref{sec:generators} 
+provides an overview of the existing graph data generators and their main features in the frame of 
+the proposed categories. 
+%To provide a complete overview,  we list the most commonly used testing data sets for the particular categories in Section~\ref{sec:data_sets}.
+In Section~\ref{sec:challenges}, we highlight some of the challenges and open problems of graph 
+data synthesis before we conclude in Section~\ref{sec:conclusion}.

### 2019-07-23 main.tex
updated year main.tex
Minor changes
Removed section 4, modified bibliography
Consolidation of sectioms 1-2 with the rest

@@
 \acmArticle{0}
-\acmYear{2018}
+\acmYear{2019}
 \acmMonth{0}
@@
 and applications manipulating these data. We consider graph generation
-across multiple subfields, such as graph databases, Semantic Web, social networks, graph streaming, alongside community detection  and graph data analytics. Despite the disparate
+across multiple subfields, such as Semantic Web, graph databases, social networks, and community detection, along with general graphs. Despite the disparate
 requirements of modern graph generators throughout these communities, we
@@
 
-\acmformat{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr, 2018.
+\acmformat{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr, 2019.
 Modern Graph Generators: A Survey.}
@@
 %\input{comparison2}
-\input{data_sets}
+%\input{data_sets}
 \input{challenges}
@@
 % History dates
-\received{October 2018}{October 2018}{October 2018}
+\received{June 2019}{June 2019}{June 2019}
 

### 2019-07-23 challenges.tex
Consolidation of Sections 3-5

--- 2018-11-27 challenges.tex
@@
 
-\subsection{Single- vs. Multi-domain}
+\subsection{Single- vs. Multi-Domain}
 
 Most of existing graph generators also generate graphs that are either not labeled or
-are specific to a given domain (e.g.  social networks). Graphs from different
+are specific to a given domain (e.g.,  social networks). Graphs from different
 domains have different schemas, structural characteristics, property
@@
 Since de-noising graph data is difficult to achieve, various machine learning-based
-approaches have been adapted to work with noise (i.e. mislabeled
+approaches have been adapted to work with noise (i.e., mislabeled
 samples) or outliers, such as
@@
 Stream computing is a new paradigm that is necessitated by various modern data generation scenarios such as the ubiquity of mobile devices, location services,
-sensor pervasiveness and emerging IoT applications.
-These applications generate the data with high Velocity, one of the main 3V characteristics of Big Data applications~\cite{sakr2016big}.
-In most of these high speed data generation scenarios, various objects are connected together with different relations and data exchanges  in a graph-structured manner.
-The Semantic Web community has been considering the aspect of implementing streaming RDF generator and benchmarks, however, there is still a clear lack on considering this aspect in other important and timely domains such as IoT.
+sensor pervasiveness and emerging IoT applications. These applications generate the data with high Velocity, one of the 
+main 3V characteristics of Big Data applications~\cite{sakr2016big}. In most of these high speed data generation scenarios, 
+various objects are connected together with different relations and data exchanges  in a graph-structured manner. The 
+Semantic Web community has been considering the aspect of implementing streaming RDF generator and benchmarks; however, there is still a clear lack on considering this aspect in other important and timely domains such as IoT.
 %Thus, there is a crucial need to tackle this aspect.
@@
 
-\subsection{Multi-model Data}
+\subsection{Multi-Model Data}
 With the dawn of Big Data and especially its Variety, another key 3V characteristic, new types of
 database management systems have emerged. One of the most interesting ones
-are the so-called \emph{multi-model databases} that enable to store and
-thus query across structurally different data. There exist various types of
+are the so-called \emph{multi-model databases}~\cite{Lu:2019:MDN:3341324.3323214} that enable to store and
+thus query across structurally different data, including structured, semi-structured, and unstructured. There exist various types of
 multi-model systems combining  distinct subsets of Big Data structures including graph data.
@@
 
-\subsection{Privacy-preserving Graph Generation}
+\subsection{Privacy-Preserving Graph Generation}
 

### 2019-07-23 comparison.tex
Consolidation of Sections 3-5

@@
 \hline %  ======================  Semantic web
-\multirow{16}{*}{\rot{\textbf{Semantic Web}}}
+\multirow{19}{*}{\rot{\textbf{Semantic Web}}}
  & LUBM & fixed & university  & fixed & N & Y & random (LCG) &  RDF & N   \\
 \cline{2-10}
-% & LBBM & extracted & Lehigh university BibTeX  & N & N & Y & Monte Carlo &  RDF & N   \\
-%\cline{2-10}
-% & UOBM & fixed & university  & fixed & N & Y & random &  RDF & N   \\
-%\cline{2-10}
+ & LBBM & extracted & Lehigh university BibTeX  & N & N & Y & Monte Carlo &  RDF & N   \\
+\cline{2-10}
+ & UOBM & fixed & university  & fixed & N & Y & random &  RDF & N   \\
+\cline{2-10}
  & IIMB & fixed & movies  & N & N & Y & random &  RDF & N   \\
@@
 In this case the size of the output graph is important if we require realistic features of the result.
-However, most of the proposals do not provide an implementation at all and, thus, unfortunately this aspect cannot be discussed reliably.
+However, surprisingly many of the proposals do not provide an implementation at all and amongst the others there is a high percentage of those that are not highly scalable.
 
@@
 \hline %  ======================  Semantic web
-\multirow{14}{*}{\rot{\textbf{Semantic web}}}
+\multirow{16}{*}{\rot{\textbf{Semantic web}}}
  & LUBM  & & {\bf x} & &  &  \\
 \cline{2-7}
-% & LBBM  & & {\bf x} & &  &  \\
-%\cline{2-7}
-% & UOBM  & & {\bf x} & &  &  \\
-%\cline{2-7}
+ & LBBM  & & {\bf x} & &  &  \\
+\cline{2-7}
+ & UOBM  & & {\bf x} & &  &  \\
+\cline{2-7}
  & IIMB & & {\bf x} & &  & \\

### 2019-07-23 generators.tex
Sherif Changes
merged 3.5 with 3.1; Tables I and II updated
Consolidation of Sections 3-5

--- 2018-09-09 generators.tex
@@
 
-In this section we explore in more detail different graph data generators using the classification introduced before.
-For each category we briefly describe key features of each of the representatives.
+In this section, we discuss in more detail the different graph data generators using the classification introduced before.
+For each category we briefly describe the key features of each of the representative examples and summarize their strengths and weaknesses.
 The aim is to provide the readers with a detailed look at each of the tools in the context of its competitors from the same domain.
@@
 
-\input{generators_analytics}
+%\input{generators_analytics}
 

### 2019-07-23 generators_GraphDatabases.tex
Sherif Changes on Structure
Sherif Changes on Structure
Consolidation of Sections 3-5

@@
 However, more comprehensive graph DBMS generators that also produce data manipulation operations (such as updates for graph databases) are urgently needed.
+Additionally, none of these generators is enabled to work on corresponding query languages for property graphs, such as the newly emerging standard GQL~\cite{gql-2018} and G-Core~\cite{AnglesABBFGLPPS18}.
+Hence, a full-fledged graph DBMS generator for property graphs and property graph query workloads~\cite{BFVY18} is still missing and there exists an interesting opportunity to build such a generator in the near future.
 
-Additionally, none of these generators is enabled to work on corresponding query languages for property graphs, such as the newly emerging standard GQL~\cite{gql-2018} and G-Core~\cite{AnglesABBFGLPPS18}.
-Hence, a full-fledged graph DBMS generator for property graphs and property graph query workloads~\cite{BFVY18} is still missing and there exists an interesting opportunity to build such a generator in the next future.
-Another apparent inconvenient is represented by the fact that explicit correlations among graph elements cannot be encoded for instance in gMark or GraphGen, whereas they could be fruitful in order to reproduce the behavior of real-world graphs in which attribute values are correlated one with another.
-On the other hand, social network and Linked Data generators that support correlations (as highlighted in Section \ref{sec:generators_socialnetworks} and Section \ref{sec:generators_LinkedData}) typically exhibit a fixed schema and are not not necessarily multi-domain as some of the graph DBMS generators discussed in this Section (namely GraphGen and gMark).
+Another apparent inconvenience is represented by the fact that explicit correlations among graph elements cannot be encoded for instance in gMark or GraphGen, whereas they could be fruitful in order to reproduce the behavior of real-world graphs in which attribute values are correlated one with another.
+On the other hand, social network and Linked Data generators that support correlations (as highlighted in Section \ref{sec:generators_socialnetworks} and Section \ref{sec:generators_LinkedData}) typically exhibit a fixed schema and are not not necessarily multi-domain as are some of the graph DBMS generators discussed in this section (namely GraphGen and gMark).

### 2019-07-23 generators_LinkedData.tex
Consolidation of Sections 3-5

@@
 \label{sec:generators_LinkedData}
-With the dawn of the concept of Linked Data it is a natural development that there would emerge respective benchmarks involving both synthetic data and real-world data sets  sets with real-world characteristics.
+With the dawn of the concept of Linked Data it is a natural development that there would emerge respective 
+benchmarks involving both synthetic data and  data sets   with real-world characteristics. 
 The used data sets correspond to RDF representation of relational-like data~\cite{Guo2005158,Bizer09theberlin}, social network-like data~\cite{Schmidt2010}, or specific and significantly more complex data structures such as biological data~\cite{Wu2014}.
@@
 Streamer component of this framework is designed to publish RDF streams from the
-various existing RDF benchmarks (e.g., BSBM, LUBM) (see Section~\ref{sec:generators_LinkedData}).
+various existing RDF benchmarks (e.g., BSBM, LUBM).
 In particular, the Streamer  component uses TripleWave\footnote{\url{http://streamreasoning.github.io/TripleWave/}}, an
@@
 
-\paragraph{Strengths and Weaknesses of Semantic Web Graph Generators.}  Graphs are intuitive and standard representation for the RDF model that form the basis for the Semantic Web community which has been very active on building several benchmarks, associated with graph generators that had various design principles.
+\paragraph{Strengths and Weaknesses of Semantic Web Graph Generators}  Graphs are intuitive and standard representation for the RDF model that form the basis for the Semantic Web community which has been very active on building several benchmarks, associated with graph generators that had various design principles.
+
 A comparison of 4 RDF benchmarks (namely TPC-H~\cite{TPC-H} data expressed in RDF, LUBM, BSBM, and SP$^2$Bench) and 6 real-wold data sets (such as, e.g.,  DBpedia, the Barton Libraries Dataset~\cite{barton-benchmark} or
@@
 In addition, they show that structuredness and size mutually influence each other.
+
 With the recent increasing momentum of streaming data, the Semantic Web community started to consider the issues and challenges of RDF streaming data.

### 2019-07-23 generators_SocialNetworks.tex
Consolidation of Sections 3-5

@@
 useful information for various domains. However, an analysis of such type of
-graph has to cope with two problems: (1) availability of the data and (2)
+graphs has to cope with two problems: (1) availability of the data and (2)
 privacy of the data. Hence, data generators which provide realistic synthetic
@@
 features~\cite{Chakrabarti:2006:GML:1132952.1132954}. For example, a social
-graph often has high \emph{clustering coefficient}, i.e. the degree of
-transitivity of a graph. Or, its diameter, i.e. the longest shortest path
+graph often has high \emph{clustering coefficient}, i.e., the degree of
+transitivity of a graph. Or, its diameter, i.e., the longest shortest path
 amongst some fraction (e.g. 90\%) of all connected nodes, is usually low due to
@@
 study of structure of communities in 70 real-world networks is provided, e.g.,
-in ~\cite{Leskovec:2008:SPC:1367497.1367591}.
+in~\cite{Leskovec:2008:SPC:1367497.1367591}.
 ~\cite{Prat-Perez:2014:CSS:2621934.2621942} analyzed the structure of
@@
 existing graph generators such as LFR~\cite{PhysRevE.78.046110} and the
-LDBC-SNB~\cite{Erling:2015:LSN:2723372.2742786}. They found out that discovered
+LDBC SNB~\cite{Erling:2015:LSN:2723372.2742786}. They found out that discovered
 communities  in different graphs have common distributions and that communities
@@
 private data sets with large-scale agent-based techniques. The process works as
-follows: In the first step it generates a synthetic data by combining public and
+follows: In the first step it generates  synthetic data by combining public and
 commercial databases. In the second step, it determines a set of activity
@@
 observed in social networks: node features and multiple link types. Both
-generators etend on the generator proposed by~\cite{wang2011leveraging}.
+generators extend  the generator proposed by~\cite{wang2011leveraging}.
 which starts with a small number of
-nodes, and new nodes are added until the network reaches the required number. It
+nodes and new nodes are added until the network reaches the required number. It
 has two basic parameters: homophily and link density. A high \emph{homophily}
@@
 network to preferentially connect nodes that exhibit a high feature similarity.
-The network is initialized with a group of three nodes, and new nodes and links
+The network is initialized with a group of three nodes. New nodes and links
 are added to the network based on link density, homophily, and feature
@@
 feature similarity parameter -- a source node is selected randomly and connected
-to the most similar node. The second proposed generator is Multi-Link Generator
-(MLG) further  uses link co-occurrence statistics from the original dataset to
+to the most similar node. The second proposed generator, so-called Multi-Link Generator
+(MLG), further  uses link co-occurrence statistics from the original dataset to
 create a multiplex network. MLG uses the same network growth process as ASG.
@@
 \paragraph{Towards More Realistic Data} \cite{Nettleton2016} argued that the majority of existing works focuses on
-topology generation which approximates the characteristics of a real social
+topology generation which approximates the characteristics of a real-world social
 network (such as a small graph diameter, skew degree
-distribution, small average path length, and community structures), however,  this is usually done without any data. Hence, they
+distribution, small average path length, and community structures); however,  this is usually done without any data. Hence, they
 introduced a general stochastic modeling approach that enables the users to
@@
 mainly on reproducing intra- and inter-node feature correlations.
-Among existing genrators, LDBC-SNB and S3G2 look
+Among existing generators, LDBC SNB and S3G2 look
 like the most advanced ones in terms of the complexity of the generated graph
@@
 large degree of scalability. Their generation process is based on input dictionaries and have configuration files that
-allow tweaking parameters many parameters of the generated graphs, but their schema is mainly
-static and cannot be easilly configured to meet the needs of other uses cases
+allow tweaking  many parameters of the generated graphs, but their schema is mainly
+static and cannot be easily configured to meet the needs of other uses cases
 besides the benchmarks they have been designed for. In this regard, the approaches
-like those proposed in ~\cite{Nettleton2016} and ~\cite{Sukthankar-SocialInfo2014} offer a
+like those proposed in~\cite{Nettleton2016} and~\cite{Sukthankar-SocialInfo2014} offer a
 more flexible and understandable configuration process to tweak the types,
-values and correlations between different features.
+values, and correlations between different features.
 
 Regarding the correlation between the underlying graph structure and the node
-features, approaches such as LDBC-SNB, S3G2 or ~\cite{Nettleton2016}
-take into account this aspect and the generated graphs have ralistic
+features, approaches such as LDBC SNB, S3G2 or ~\cite{Nettleton2016}
+take into account this aspect and the generated graphs have realistic
 structural properties while similar nodes have a larger probability of being
 connected. However, their approach seems to be more based on
-intuition and common sense than to be backed up by an any study of how the
+intuition and common sense than to be backed up by  any study of how the
 relation between structure and attributes showcase in real social networks. In
-this reagard, this remains as a clear open challenge for social network
+this regard, this remains as a clear open challenge for social network
 generators.
@@
 Finally, scalability is another aspect to be considered in social network graph
-generators. LDBC-SNB and S3G2 are engineered with this in mind, thus they
+generators. LDBC SNB and S3G2 are engineered with this in mind, thus they
 provide a way to scale to billions of nodes and edges. This is not the case for

### 2019-07-23 generators_community_detection.tex
Consolidation of Sections 3-5

--- 2019-06-16 generators_community_detection.tex
@@
 Community detection is one of the many graph analytics algorithms typically used
-in domains such as social networks or bioinformatics. \emph{Communities} are groups of nodes that are highly connected among them, while being scarcely connected to
-the rest of the graph. Such communities emerge from the fact that real graphs
+in domains such as social networks or bioinformatics. \emph{Communities} are groups of nodes that are highly mutually connected, while being scarcely connected to
+the rest of the graph. Such communities emerge from the fact that real-world graphs
 are not random, but follow real-world dynamics that make similar entities to
@@
 communities are used to reveal vertices with similar characteristics, for
-instance to discover functionally equivalent proteins in protein-protein
+instance to discover functionally equivalent proteins in protein-to-protein
 interaction networks, or persons with similar interests in social networks. Such
-applications have made community detection a hot topic during the last fifteen
+applications have made community detection a hot topic during the last 15
 years with tens of developed algorithms and detection
@@
 with \emph{reference communities}, that is, communities known beforehand. Since
-it is very difficult to have large real graphs with reference communities
+it is very difficult to have large real-world graphs with reference communities
 (mainly because these would require a manual labeling), graphs for benchmarking
@@
 Each of these subgraphs has the same size and the same internal/external density
-of edges. However, such graphs miss the realism observed in real graphs, where
+of edges. However, such graphs miss the realism observed in real-world graphs, where
 communities are of different sizes and densities, thus several proposals exist
@@
 
+\paragraph{Stochastic Block Models} Another popular family of generators
+widely used in the community detection field are the stochastic block
+models~\cite{holland1983stochastic}. In such models, the community structure of
+the graph is typically defined as an array of $n$ community or cluster sizes
+and a density square matrix of size $n \times n$ containing the density of
+intra-cluster edges (in the diagonal of the matrix) and the density of
+inter-cluster edges. Then, a stochastic procedure is run to sample graphs
+from such array and matrix, using the sizes to compute the possible edges
+and the densities as probabilities of such edges to exist. The popularity of
+these methods stem from its simplicity and scalability, which makes them
+suitable for generating large graphs fast and in a distributed environments,
+provided that the density matrix is sparse (as it happens in most of real-world
+                                            world graphs). Moreover, given
+that the generation process of such models is mathematically tractable, they
+are typically used to analyze the limitations of community detection
+algorithms such as those based on modularity
+optimization~\cite{fortunato2007resolution} or based on
+triads~\cite{prat2016put}. Extensions of such models exist, such as the
+Mixed Membership Stochastic Block Model~\cite{airoldi2008mixed}, for
+overlapping communities.
+
 \paragraph{Strengths and Weaknesses of Community Detection Generators}
@@
 forums in a social network, categories of products, etc.) to infer what they
-call ``meta-communities'', and use them to evaluate overlapping community
+call \emph{meta-communities}, and use them to evaluate overlapping community
 detection algorithms. However, a recent study from Hric, Darst and
 Fortunato~\cite{hric2014community} reveal a loose correspondence between
-communities (the authors refer to them as structural communities) and
+communities (the authors refer to them as \emph{structural communities}) and
 meta-communities.  This result reveals that  algorithms working for structural
@@
 generators to generate graphs with meta-communities for community detection
-algorithm benchmarking. The closest one is the LDBC-SNB data
-generator~\cite{Erling:2015:LSN:2723372.2742786} which has been provided by the
+algorithm benchmarking. The closest one is the LDBC SNB data
+generator which has been provided by the
 generation of groups of users in the social network. Even though the generation
 process does not specifically enforce the generation of groups
-(meta-communities) for benchmarking community detection algorithms, the study
-from Prat-Pe\'rez and Dominguez-Sal reveals that these groups are more similar
+(meta-communities) for benchmarking community detection algorithms, the study~\cite{Prat-Perez:2014:CSS:2621934.2621942} reveals that these groups are more similar
 to the real meta-communities than those structural communities generated by the
-LFR benchmark~\cite{Prat-Perez:2014:CSS:2621934.2621942}.
+LFR benchmark.
 

### 2019-07-23 generators_general.tex
Consolidation of Sections 3-5

@@
 In general, existing general graph generators produce graphs with the following
-properties: skewed degree distribution (e.g. powerlay), small diameter, large
-clustering coefficient, a large largest connected component and some degree of
+properties: skewed degree distribution (e.g., powerlay), small diameter, large
+clustering coefficient, a large largest connected component, and some degree of
 community structure. Degree distribution can be typically configured while other
-properties are just a result of the genration process and cannot be controlled
+properties are just a result of the generation process and cannot be controlled
 by any means.
 
-This is not the case of BTER and Darwini which besides the degree distribution,
-they also allow tunning the clustering coefficient. However, some use cases
+This is not the case of BTER and Darwini, which besides the degree distribution,
+they also allow tuning of the clustering coefficient. However, some use cases
 demand for more control on the characteristics of the generated graphs.
@@
 to run. For this reason, the design of graph generators with the capability of fine
-tunning the characteristics of the generated graphs still remains as an open
-challenge. The question that remains though is what characteristics to tune,
-and which are the algorithms whose depends on such characteristics.
+tuning the characteristics of the generated graphs still remains as an open
+challenge. The questions that remain are what characteristics to tune
+and which are the algorithms that depend on such characteristics.

### 2019-07-23 generators_general.tex
Adding RTG

@@
 
+\paragraph{RTG} \emph{The Random Typing Generator} (RTG)~\cite{DBLP:journals/datamine/AkogluF09} aims at generating realistic graphs.
+In particular, it outputs (un)weighted, (un)directed, as well as uni/bipartite graphs, whereas the realism of the output is ensured by 11 laws (e.g., densification power law, weight power law, small and shrinking diameter, community structure, etc.) known to be typically exhibited by real-world graphs.
+On input it requires 4 parameters ($k$, $q$, $W$, and $\beta$) that correspond to the core Miller's observation~\cite{miller1957} that a random process (namely, random typing of $W$ words on a keyboard with $k$ characters and a space, where a space is hit with probability $q$ and other characters with probability $(1-q)/k$) leads to Zipf-like power laws (of the resulting words) plus in addition (using imbalance factor $\beta$) ensure homophily and community structure.
+RTG is based on the idea of connecting each pair of consecutive words by an edge.
+
+Paper~\cite{DBLP:conf/wbdb/AmmarO13} further extends this idea mainly in the direction of simplification of specifying of the parameters.
+Instead of Miller's parameters that are not much associated with graphs, the authors prove and exploit their relationship with size and density of the target graph.
+
 \paragraph{Strengths and Weaknesses of General Graph Generators}

### 2019-07-26 challenges.tex
Sherif Changes

@@
 multi-model systems combining  distinct subsets of Big Data structures including graph data.
-For example, OrientDB\footnote{\url{http://orientdb.com/orientdb/}} which was
-implemented on the basis of an object DBMS currently supports graph, document,
+For example, OrientDB\footnote{\url{http://orientdb.com/orientdb/}} which has been mainly designed as an object DBMS currently supports graph, document,
 key/value, and object models. Such type of DBMSs also needs a specific

### 2019-07-26 generators.tex
Sherif Changes

--- 2018-09-09 generators.tex
@@
 
-In this section we explore in more detail different graph data generators using the classification introduced before.
-For each category we briefly describe key features of each of the representatives.
-The aim is to provide the readers with a detailed look at each of the tools in the context of its competitors from the same domain.
+In this section, we discuss in more detail the various graph data generators based on the classification introduced before.
+For each category, we briefly describe the main features of each of the representative examples and summarize their strengths and weaknesses.
+The goal is to provide the readers with a detailed information about each of the tools in the context of its competitors from the same domain.
 

### 2019-07-26 generators_GraphDatabases.tex
Sherif Changes

@@
 \cite{Dominguez-Sal:2010:DDG:1946050.1946053} discussed this question and related topics.
-On the basis of a review of applications of graph databases (namely, social network analysis,  genetic interactions, recommendation systems, and travel planning and routing), the authors analyzed and discussed the features of the graphs for these types of applications and how they could affect the benchmarking process, different types of operations used in these applications and the characteristics of the evaluation setup of the benchmark.
+On the basis of a review of applications of graph databases (namely, social network analysis,  genetic interactions and recommendation systems), the authors analyzed and discussed the features of the graphs for these types of applications and how such features can affect the benchmarking process, various types of operations used in these applications and the characteristics of the evaluation setup of the benchmark.
 In this section, we focus on graph data generators and benchmarks that have been primarily targeting graph DBMSs.

### 2019-07-26 generators_LinkedData.tex
Sherif Changes

@@
 The data generator corresponds to a data modifier which simulates differences between the data.
-In particular it involves data value differences (such as typographical errors or usage of different standard formats, e.g., for names), structural heterogeneity (represented by different levels of depth for properties, diverse aggregation criteria for properties, or missing values specification) and logical heterogeneity (such as instantiation on different subclasses of the same superclass or instantiation on disjoint classes).
+In particular it involves data value differences (such as typographical errors or usage of different standard formats, e.g., for names), structural heterogeneity (represented by different levels of depth for properties, diverse aggregation criteria for properties, or missing values specification) and logical heterogeneity (such as instantiation on various subclasses of the same superclass or instantiation on disjoint classes).
 
@@
 
-\paragraph{DBPSB} DBpedia SPARQL Benchmark (DBPSB)\footnote{\url{http://aksw.org/Projects/DBPSB.html}} proposed at the University of Leipzig has been designed using workloads that have been issued by humans and applications over existing RDF data~\cite{Morsey2011,Morsey:2012:UBR:2900929.2901031}.
-In addition, the authors argue that benchmarks like LUBM, BSBM, or SP$^2$Bench resemble relational database benchmarks involving relational data structures with few and homogeneously structured classes, whereas, in reality, RDF datasets are increasingly heterogeneous.
+\paragraph{DBPSB} DBpedia SPARQL Benchmark (DBPSB)\footnote{\url{http://aksw.org/Projects/DBPSB.html}} proposed at the University of Leipzig has been designed using workloads that have been generated by applications and humans~\cite{Morsey2011,Morsey:2012:UBR:2900929.2901031}.
+In addition, the authors argue that benchmarks like LUBM, BSBM, or SP$^2$Bench resemble relational database benchmarks involving relational-like data which is structured using few and homogeneously structured classes, whereas, in reality, RDF datasets are increasingly tending to be more heterogeneous.
 For example, DBpedia version 3.6 consists of 289,016 classes of which 275 classes are defined based on the DBpedia ontology.
@@
 Three evaluation metrics are utilized for this purpose: dataset coherence (i.e., a measure how uniformly predicates are distributed among the same type/class), relationship specialty (i.e., the number of occurrences of the same predicate associated with each resource), and literal diversity.\fi A query generation process has been implemented to produce 5 different types of queries (edge-based queries, node-based queries, path queries, star queries, subgraph queries) for any generated data.
-The benchmark project FEASIBLE~\cite{Saleem2015} is also an application-specific benchmark; however, contrary to RBench, it is designed to produce benchmarks from a set of queries (in particular from query logs) by relying on sample queries of a user-defined
+The benchmark project FEASIBLE~\cite{Saleem2015} is also an application-specific benchmark; however, contrary to RBench, it is designed to produce benchmarks from a set of queries by relying on sample queries of a user-defined
 size from the input set of queries.

### 2019-07-26 generators_SocialNetworks.tex
Sherif Changes

@@
 communities  in different graphs have common distributions and that communities
-in a single graph have diverse nature and are difficult to fit with a single
+in a single graph have different characteristics and are challenging to be represented using a single
 model.
@@
 ~\cite{Barrett:2009:GAL:1995456.1995598} focused on the construction of
-realistic social networks. For this purpose the authors combine both public and
-private data sets with large-scale agent-based techniques. The process works as
+realistic social networks. For this purpose the authors combine both 
+private and public data sets with large-scale agent-based techniques. The process works as
 follows: In the first step it generates  synthetic data by combining public and
@@
 topology generation which approximates the characteristics of a real-world social
-network (such as a small graph diameter, skew degree
+network (e.g., a small graph diameter, skew degree
 distribution, small average path length, and community structures); however,  this is usually done without any data. Hence, they

### 2019-07-26 generators_community_detection.tex
Sherif Changes

@@
 
-In this regard and to the best of our knowledge, there does not exist a set of
-generators to generate graphs with meta-communities for community detection
+In this regard and to the best of our knowledge, there are no available 
+generators that can generate graphs with meta-communities for community detection
 algorithm benchmarking. The closest one is the LDBC SNB data

### 2019-07-26 generators_general.tex
Sherif Changes

@@
 demand for more control on the characteristics of the generated graphs.
-This is the case, for instance, of benchmarking, where the underlying graph
+This is the case, for example, of benchmarking, where the underlying graph
 structure has direct implications to the performance of the graph algorithms

### 2019-07-26 introduction.tex
Sherif Changes

@@
 
-In general, we can distinguish between two broad types of graph data sets: (1) a single large graph (possibly with several components), such as social networks  or Linked Data graphs, and (2) a large set of small graphs, such as chemical compounds\footnote{\url{https://pubchem.ncbi.nlm.nih.gov/}} or linguistics syntax trees\footnote{\url{https://catalog.ldc.upenn.edu/ldc99t42}}.
+In general, we can distinguish between two broad types of graph data sets: (1) a single large graph (possibly with several components), such as social networks  or Linked Data graphs, and (2) a large set of small graphs (e.g., chemical compounds\footnote{\url{https://pubchem.ncbi.nlm.nih.gov/}} or linguistics syntax trees\footnote{\url{https://catalog.ldc.upenn.edu/ldc99t42}}).
 Naturally, the algorithms used in theses two classes differ a lot~\cite{DBLP:books/igi/Sakr2011}.
@@
 \paragraph*{Contributions} Our survey revisits the representatives of
-modern graph data generators and summarizes their major features.
-The comprehensive review and analysis make this paper useful for motivating new graph data generation techniques as well as serving as a technical reference for selecting suitable solutions.
+modern graph data generators and summarizes their main characteristics.
+The comprehensive review and analysis make this paper useful for motivating new graph data generation mechanisms as well as serving as a main technical reference for selecting suitable solutions.
 In particular, the introductory categorization and comparative study enables the reader to quickly get his/her bearings in the field and identify a subset of generators of his/her interest.

### 2019-08-06 comparison.tex
Adding RTG
Irena's pass (plagiarism) pp 1-10

@@
 
-In order to provide the reader with a general preview of the generators and  to enable finding the target solutions easily, we start the survey with a  classification and comparative study of the existing tools.
+In order to provide a general preview of the generators and  to enable finding the target solutions easily, we start the survey with a  classification and comparative study of the existing tools.
 In general, there are various ways to classify them.
-We first provide an overview of the approaches used in related work after which we then introduce our approach.
+We first offer an overview of the approaches used in state-of-the-art work after which we then introduce our approach.
 As mentioned in the Introduction, since this survey is unique especially in terms of scope, our classification and comparative strategy differs as well.
 
-The graph data generators can be classified according to various criteria.
+The graph data generators can be classified using various distinct criteria.
 For example,~\cite{DBLP:conf/sdm/ChakrabartiZF04} introduces two categories -- degree-based and procedural generators.
 In general, \emph{degree-based generators} (e.g., Barabasi-Albert model~\cite{Barabasi99emergenceScaling}) are commonly attempting to find a graph that matches it, but without providing any information about the graph or attempting to match other graph features (e.g., eigenvalues, small diameter, etc).
-On the other hand, \emph{procedural generators} (e.g., R-MAT~\cite{DBLP:conf/sdm/ChakrabartiZF04}) are commonly targeting simple techniques to produce graphs that are matching the characteristics of the real-world graphs (e.g., the power law degree distribution).
+On the other hand, \emph{procedural generators} (e.g., R-MAT~\cite{DBLP:conf/sdm/ChakrabartiZF04}) are commonly targeting simple techniques to produce graphs that are matching the characteristics of the real-world graphs (such as, e.g., the power law degree distribution).
 
-Paper~\cite{Chakrabarti:2006:GML:1132952.1132954} introduces five categories of graph models that can be synthesized: (1) \emph{random graph models} (e.g., Erd\"{o}s-R\'{e}nyi~\cite{Erdos:1960}) generated by a random process, (2) \emph{preferential attachment models} (e.g., Barabasi-Albert model) which try to model the power law from the preferential attachment viewpoint, (3) \emph{optimization-based models} (e.g., HOT model~\cite{PhysRevLett.84.2529}) resulting from the idea that power laws can result from resource optimizations and tolerance to risks, (4) \emph{tensor-based models} (e.g., R-MAT) targeting a trade-off between low number of model parameters and efficiency, and (5) \emph{internet-specific models} corresponding to hybrids using ideas from the other categories in order to suit the specific features of the graphs.
+Paper~\cite{Chakrabarti:2006:GML:1132952.1132954} introduces five categories of graph models that can be synthesized: (1) \emph{random graph models} (e.g., Erd\"{o}s-R\'{e}nyi~\cite{Erdos:1960}) generated by a random process, (2) \emph{preferential attachment models} (e.g., Barabasi-Albert model) which try to model the power law from the preferential attachment viewpoint, (3) \emph{optimization-based models} (e.g., HOT model~\cite{PhysRevLett.84.2529}) resulting from the idea that power laws can result from tolerance to risks and resource optimizations, (4) \emph{tensor-based models} (e.g., R-MAT) targeting a trade-off between low number of model parameters and efficiency, and (5) \emph{internet-specific models} corresponding to hybrids using ideas from the other categories in order to suit the specific features of the graphs.
 
@@
 \hline   % ====================== general graphs
-\multirow{6}{*}{\rot{\textbf{General}}}
+\multirow{7}{*}{\rot{\textbf{General}}}
   & Preferential attachment & -- & -- & N & N & Y & power-law & edge-list &  N  \\
@@
   & Darwini & -- & -- &   N & N & N & user-defined &  edge-list & Y   \\
+\cline{2-10}
+  & RTG & -- & -- &   N & N & N & power-law &  edge-list & N  \\
 %  & Watts-Strogatz~\cite{watts1998collective} & fixed & & Y & N & Y &  & &  N  \\
@@
   & Darwini   & {\bf x} & & &  & \\
+\cline{2-7}
+  & RTG   & {\bf x} & & &  & x \\
 \hline

### 2019-08-06 generators.tex
Irena's pass (plagiarism) pp 1-10

--- 2019-07-23 generators.tex
@@
 
-In this section, we discuss in more detail the different graph data generators using the classification introduced before.
-For each category we briefly describe the key features of each of the representative examples and summarize their strengths and weaknesses.
-The aim is to provide the readers with a detailed look at each of the tools in the context of its competitors from the same domain.
+In this section, we discuss the various graph data generators based on the classification introduced before in more detail.
+For each category, we first describe the key features of each of the representative examples and summarize their strengths and weaknesses.
+The goal is to offer a detailed information about each of the tools in the context of its competitors from the same domain.
 

### 2019-08-06 generators_LinkedData.tex
Irena's pass (plagiarism) pp 1-10

@@
 The ontology defines 43 classes and 32 properties~\cite{Guo2005158}.
-In addition, the LUBM benchmark provides 14 test queries.
+In addition, 14 test queries are provided in the LUBM benchmark.
 In particular, the benchmark focuses on \emph{extensional} queries, i.e., queries which target the particular data instances of the ontology, as an opposite to \emph{intentional} queries, i.e., queries which target properties and classes of the ontology.
 The Univ-Bench Artificial  (UBA) data generator features repeatable and random  data generation (exploiting classical linear congruential generator, LCG, of numbers).
-In particular, the data which is produced by the generator are assigned zero-based indexes (i.e., the first university is named \emph{University0} and so on), thus they are reproducible at any time with the same indexes.
-The generator naturally allows to specify a seed for random number generation, along with the desired number of universities, and the starting index of the universities.
+In particular, the data which is produced by the generator are assigned zero-based indexes (i.e., \emph{University0}, \emph{University1} etc.), thus they are reproducible at any time with the same indexes.
+The generator naturally allows to specify a seed for random number generation, along with the starting index and the desired number of universities.
 
@@
 LBBM provides a probabilistic model that can emulate the discovered properties of the data of a particular domain and generate synthetic data exhibiting similar properties.
-A Monte Carlo algorithm is employed to output synthetic data.
+Synthetic data are generated using a Monte Carlo algorithm.
 The approach is demonstrated on the Lehigh University BibTeX ontology which consists of 28 classes along with 80 properties.

### 2019-08-06 generators_general.tex
Irena's pass (plagiarism) pp 1-10

@@
 and employs a fairly small number of parameters.  In principle, the strategy of
-this generator is to achieve simple means to produce graphs that are matching
-the properties of the real graphs. In particular, the design goal of R-MAT is to
+this generator is to achieve simple means to produce graphs whose properties correspond to 
+properties of the real-world graphs. In particular, the design goal of R-MAT is to
 produce graphs which mimics the degree distributions, imitate a community
@@
 nodes from different groups at random. The authors describe a highly scalable
-MapReduce based implementation that is capable of generating large graphs (with
+MapReduce-based implementation that is able to generate large graphs (consisting of
 billions of nodes) in a reasonable amounts of time.
@@
 In particular, it outputs (un)weighted, (un)directed, as well as uni/bipartite graphs, whereas the realism of the output is ensured by 11 laws (e.g., densification power law, weight power law, small and shrinking diameter, community structure, etc.) known to be typically exhibited by real-world graphs.
-On input it requires 4 parameters ($k$, $q$, $W$, and $\beta$) that correspond to the core Miller's observation~\cite{miller1957} that a random process (namely, random typing of $W$ words on a keyboard with $k$ characters and a space, where a space is hit with probability $q$ and other characters with probability $(1-q)/k$) leads to Zipf-like power laws (of the resulting words) plus in addition (using imbalance factor $\beta$) ensure homophily and community structure.
-RTG is based on the idea of connecting each pair of consecutive words by an edge.
+On input it requires 4 parameters ($k$, $q$, $W$, and $\beta$) that correspond to the core Miller's observation~\cite{miller1957} that a random process (namely, having a keyboard with $k$ characters and a space, the process of random typing of $W$ words, where the probability of hitting a space is $q$ and the probability of hitting any other characters is $(1-q)/k$) leads to Zipf-like power laws (of the resulting words) plus in addition (using imbalance factor $\beta$) ensure homophily and community structure.
+RTG is based on the idea creating an edge between pairs of consecutive words.
 
@@
 In general, existing general graph generators produce graphs with the following
-properties: skewed degree distribution (e.g., powerlay), small diameter, large
-clustering coefficient, a large largest connected component, and some degree of
+properties: skewed degree distribution (e.g., powerlay), small diameter, a large largest connected component, large
+clustering coefficient, and some degree of
 community structure. Degree distribution can be typically configured while other

### 2019-08-06 introduction.tex
Irena's pass (plagiarism) pp 1-10

@@
 
-In this survey, we provide a comprehensive overview of the state-of-the-art
+In this survey, we provide a detailed overview of the state-of-the-art
 modern
@@
 \paragraph*{Contributions} Our survey revisits the representatives of
-modern graph data generators and summarizes their main characteristics.
-The comprehensive review and analysis make this paper useful for motivating new graph data generation mechanisms as well as serving as a main technical reference for selecting suitable solutions.
-In particular, the introductory categorization and comparative study enables the reader to quickly get his/her bearings in the field and identify a subset of generators of his/her interest.
+modern graph data generators and summarizes their main characteristics. The detailed review 
+and analysis make this paper useful for stimulating new graph data generation mechanisms as well as 
+serving as a main technical reference for selecting suitable solutions. In particular, the introductory 
+categorization and comparative study enables the reader to quickly get his/her bearings in the field and 
+identify a subset of generators of his/her interest.
 Since we do not limit the survey to a particular area of graph data management,  the reader can get a broader scope in the field.
@@
 
-To the best of our knowledge, our work is the first to survey the broad
+To the best of our knowledge, this paper is the first to survey the broad
 landscape of graph data generators spanning different data-intensive applications and
@@
 the paper. The data generation of evolutionary networks is based on the
-Densification Power Law (DPL) and shrinking diameters, community-guided
+shrinking diameters and Densification Power Law (DPL), i.e., community-guided
 attachment properties~\cite{Leskovec:2005:GOT:1081870.1081893}.
@@
 
-\paragraph*{Outline} The rest of this paper is organized as follows: Section~\ref{sec:comparison}
+\paragraph*{Outline} The rest of the text is structured as follows: Section~\ref{sec:comparison}
 provides the opening categorization and comparison of the generators. Section~\ref{sec:generators}

### 2019-08-06 generators_GraphDatabases.tex
Irena's pass (plagiarism) pp 11-17

@@
 \paragraph{XGDBench} XGDBench~\cite{Dayarathna:2014:GDB:2676904.2676939} is an extensible  benchmarking platform for graph databases used in cloud-based systems. Its intent is to automate
-the process of graph database benchmarking in the cloud by focusing on the domain social networking services.
+benchmarking of graph databases in the cloud by focusing on the domain social networking services.
 It extends the Yahoo!
@@
 The generated graphs are thus in MAG format, with power-law degree distribution closely simulating real-world social networks.
-The simplified MAG algorithm accepts the required number of nodes, the number of attributes per each node, a threshold value for random attribute initialization, an edge affinity threshold determining existence of an edge between two nodes, and an affinity matrix.
+The simplified MAG algorithm accepts the required number of nodes and for each node the number of attributes, a threshold for random  initialization of attributes, a threshold for edge affinity which determines the existence of an edge between two nodes, and an affinity matrix.
 \iffalse It has been proven that MAG generates graphs with both analytically tractable and statistically interesting properties.\fi
-Large graphs can be generated on multi-core systems by a multi-threaded version of the  generator.
+Large graphs can be generated on multi-core systems by XGDBench multi-threaded version.
 

### 2019-08-06 generators_LinkedData.tex
Irena's pass (plagiarism) pp 11-17

@@
 \paragraph{IIMB} Ferrara et al.~\cite{Ferrara08OM} proposed the ISLab Instance Matching Benchmark (IIMB)\footnote{\url{http://www.ics.forth.gr/isl/BenchmarksTutorial/}} for the problem of instance matching.
-For any two objects $o_1$ and $o_2$ adhering to the same ontology or to different ontologies, instance matching is specified in the form of a function $Om(o_1, o_2) \rightarrow \{0, 1\}$,  where $o_1$ and $o_2$ are linked to the same real-world object (in which case the function maps to $1$) or $o_1$ and $o_2$ are representing different objects (in which case the function maps to $0$).
-It targets the domain of movie data which contains 15 named classes, along with 5 object properties and 13 datatype properties.
+For any two objects $o_1$ and $o_2$ adhering to different ontologies or to the same ontology, instance matching is specified in the form of a function $Om(o_1, o_2) \rightarrow \{0, 1\}$,  where $o_1$ and $o_2$ are linked to the same real-world object (in which case the function maps to $1$) or $o_1$ and $o_2$ are representing different objects (in which case the function maps to $0$).
+It targets the domain of movie data which contains 15 named classes, along with 5 objects and 13 datatypes.
 The data are extracted from IMDb\footnote{\url{http://www.imdb.com/}}.
 The data generator corresponds to a data modifier which simulates differences between the data.
-In particular it involves data value differences (such as typographical errors or usage of different standard formats, e.g., for names), structural heterogeneity (represented by different levels of depth for properties, diverse aggregation criteria for properties, or missing values specification) and logical heterogeneity (such as instantiation on various subclasses of the same superclass or instantiation on disjoint classes).
+In particular it involves data value differences (such as typographical errors or usage of different standard formats, e.g., for names), structural heterogeneity (represented by different levels of depth for properties, diverse aggregation criteria for properties, or missing values specification) and logical heterogeneity (such as, e.g., instantiation on disjoint classes or various subclasses of the same superclass).
 
@@
 
-\paragraph{SP$^2$Bench} The SP$^2$Bench\footnote{\url{http://dbis.informatik.uni-freiburg.de/forschung/projekte/SP2B/}} is a language-specific benchmark~\cite{Schmidt2010} which is based on the DBLP dataset.
-%, so the types involve Person, Inproceedings, Article etc.
+\paragraph{SP$^2$Bench} The SP$^2$Bench\footnote{\url{http://dbis.informatik.uni-freiburg.de/forschung/projekte/SP2B/}} 
+is a language-specific benchmark~\cite{Schmidt2010} which is based on the DBLP dataset. %, so the types involve Person, Inproceedings, Article etc.
 The generated datasets follow the key characteristics of the original DBLP dataset.
@@
 \paragraph{DBPSB} DBpedia SPARQL Benchmark (DBPSB)\footnote{\url{http://aksw.org/Projects/DBPSB.html}} proposed at the University of Leipzig has been designed using workloads that have been generated by applications and humans~\cite{Morsey2011,Morsey:2012:UBR:2900929.2901031}.
-In addition, the authors argue that benchmarks like LUBM, BSBM, or SP$^2$Bench resemble relational database benchmarks involving relational-like data which is structured using few and homogeneously structured classes, whereas, in reality, RDF datasets are increasingly tending to be more heterogeneous.
-For example, DBpedia version 3.6 consists of 289,016 classes of which 275 classes are defined based on the DBpedia ontology.
-In addition, different data types and object references of the various types are
-used in property values.
+In addition, the authors argue that benchmarks like LUBM, BSBM, or SP$^2$Bench resemble relational database benchmarks involving relational-like data which is structured using a small amount of homogeneous classes, whereas, in reality, RDF datasets are tending to be more heterogeneous.
+For example, DBpedia 3.6 consists of 289,016 classes, whereas 275 of them are defined based on the DBpedia ontology.
+In addition, in property values different data types as well as references to objects of the various types are
+used.
 Hence, they presented a universal SPARQL benchmark generation approach which uses a flexible data production mechanism that mimics the input data source.
@@
 For generating smaller datasets, an adequate selection of all triples is selected randomly or using a sampling mechanism over the various classes in the dataset.
-\iffalse The goal of the query analysis and clustering is to detect prototypical queries on the basis of their frequent usage and similarity.\fi The methodology is applied on the DBpedia SPARQL endpoint and a set of 25 SPARQL query templates is derived to cover the frequently used SPARQL features.
+\iffalse The goal of the query analysis and clustering is to detect prototypical queries on the basis of their frequent usage and similarity.\fi The methodology is applied on the DBpedia SPARQL endpoint and a set of 25 templates of SPARQL queries is derived to cover frequent SPARQL features.
 
@@
 \paragraph{Geographica} The Geographica benchmark\footnote{\url{http://geographica.di.uoa.gr/}} has been designed to target the area of geospatial data~\cite{DBLP:conf/semweb/GarbisKK13} and respective SPARQL extensions GeoSPARQL~\cite{battle2012enabling} and stSPARQL~\cite{koubarakis2010modeling}.
-The benchmark involves a real-world workload that uses openly available datasets that cover a range of geometry types (e.g., points, lines, polygons) and  a synthetic workload.
+The benchmark involves a real-world workload that uses openly available datasets that cover various geometry elements (such as, e.g., lines, points, polygons, etc.) and  a synthetic workload.
 In the former case there is a (1) a micro benchmark that evaluates primitive spatial functions (involving 29 queries) and (2) macro benchmark that tests the performance of RDF engines in various application scenarios such as  map exploring and search (consisting of 11 queries).
 In the latter case of a synthetic workload the generator produces synthetic datasets of different sizes that corresponds to an ontology based on OpenStreetMap  and instantiates query templates.
-\iffalse The spatial extent of the land ownership dataset constitutes a uniform grid of $n \times n$ hexagons, whereas the size of each dataset is given relatively to $n$.\fi The generated SPARQL query workload is corresponding to spatial selection and spatial joins by instantiating 2 query templates.
+\iffalse The spatial extent of the land ownership dataset constitutes a uniform grid of $n \times n$ hexagons, whereas the size of each dataset is given relatively to $n$.\fi The generated SPARQL query workload is corresponding to spatial joins and selection using 2 query templates.
 
-\paragraph{WatDiv} The Waterloo SPARQL Diversity Test Suite (WatDiv)\footnote{\url{http://dsg.uwaterloo.ca/watdiv/}} has been designed at the University of Waterloo.
-It implements stress testing tools that focus on addressing the observation that existing SPARQL benchmarks are not adequate for evaluating systems using a verity of queries and  workloads~\cite{Aluc:2014:DST:2717213.2717229}.
-The benchmark focuses on two types of query aspects -- structural and data-driven -- and performs a detailed analysis on existing SPARQL benchmarks (LUBM, BSBM, DBPSB, and SP$^2$Bench) using the two classes of query features.
-The structural features involve triple pattern count, join vertex count, join vertex degree, and join vertex count.
-The data-driven features involve result cardinality and several types of selectivity.
-The analysis of the four benchmarks reveals that they are not sufficiently diverse to evaluate the strengths and weaknesses of the various physical design alternatives that have been implemented by the different RDF systems.
-In particular, WatDiv, provides (1) a data generator which generates scalable datasets according to the WatDiv schema, (2) a query template generator which follows the WatDiv schema and produces a  set of query templates, (3) a query generator that uses the generated templates and instantiates them  with real RDF values from the dataset, and (4) a feature extractor which extracts the structural features of the generated data and workload.
+\paragraph{WatDiv} The Waterloo SPARQL Diversity Test Suite (WatDiv)\footnote{\url{http://dsg.uwaterloo.ca/watdiv/}} has 
+been designed at the University of Waterloo. It implements stress testing tools that focus on addressing the observation 
+that the state-of-the-art SPARQL benchmarks do not fully cover the variety of queries and  
+workloads~\cite{Aluc:2014:DST:2717213.2717229}. The benchmark focuses on two types of query aspects -- 
+structural and data-driven -- and performs a detailed analysis on existing SPARQL benchmarks 
+(LUBM, BSBM, DBPSB, and SP$^2$Bench) using these two properties of queries. The structural features involve triple 
+pattern count, join vertex count, join vertex degree, and join vertex count. The data-driven features involve 
+result cardinality and several types of selectivity. The analysis of the four benchmarks reveals that their diversity is
+insufficient for evaluation of the weaknesses/strengths of the distinct design alternatives implemented by the different 
+RDF systems.
+
+In particular, WatDiv, provides (1) a data generator which generates scalable datasets according to the WatDiv 
+schema, (2) a query template generator which produces a  set of query templates according to the WatDiv schema, and 
+(3) a query generator that uses the generated templates and instantiates them  with real RDF values from the dataset, and (4) a feature extractor which extracts the structural features of the generated data and workload.
 %For the study in the paper the authors generated 12,500 test queries from 125 query templates.
 
-\paragraph{RBench} RBench~\cite{Qiao:2015:RAR:2723372.2746479} is an application-specific benchmark which receives any RDF dataset as an input and produces as an output a set of datasets, that have similar characteristics of the input dataset, using size scaling factor $s$ and (node) degree scaling factor $d$.
-These factors ensure that the original RDF graph $G$ and the synthetic graph $G'$ are similar and the number of edges and the average node degree of $G'$ are changed by $s$ and $d$ respectively.
+\paragraph{RBench} RBench~\cite{Qiao:2015:RAR:2723372.2746479} is an application-specific benchmark which receives any RDF dataset as an input and produces a set of datasets, that have similar characteristics of the input dataset, using size scaling factor $s$ and (node) degree scaling factor $d$.
+These factors ensure that the original RDF graph $G$ and the synthetic graph $G'$ are similar and the average node degree and the number of edges of $G'$ are changed by $s$ and $d$ respectively.
 \iffalse A generated benchmark dataset is considered similar to the given dataset if their values for the dataset evaluation metrics and query evaluation times for different techniques are similar.
 Three evaluation metrics are utilized for this purpose: dataset coherence (i.e., a measure how uniformly predicates are distributed among the same type/class), relationship specialty (i.e., the number of occurrences of the same predicate associated with each resource), and literal diversity.\fi A query generation process has been implemented to produce 5 different types of queries (edge-based queries, node-based queries, path queries, star queries, subgraph queries) for any generated data.
-The benchmark project FEASIBLE~\cite{Saleem2015} is also an application-specific benchmark; however, contrary to RBench, it is designed to produce benchmarks from a set of queries by relying on sample queries of a user-defined
-size from the input set of queries.
+The benchmark project FEASIBLE~\cite{Saleem2015} is also an application-specific benchmark; however, contrary to RBench, it is designed to produce benchmarks from the set of sample input queries of a user-defined
+size.
 
@@
 In particular, the Streamer  component uses TripleWave\footnote{\url{http://streamreasoning.github.io/TripleWave/}}, an
-open-source framework for publishing and sharing RDF streams on the
+open-source framework which enables to share RDF streams on the
 Web~\cite{mauri2016triplewave}.   TripleWave acts as a means for plugging-in
-and combining streams from multiple Web data sources, in both push and pull mode.
+and combining streams from multiple Web data sources using either pull or push mode.
 
@@
 had the goal of developing an open source, yet industrial grade benchmarks for RDF and graph databases. 
-\iffalse The following three benchmarks were developed and are currently maintained.\fi In the Semantic Web domain, it released the Semantic Publishing Benchmark (SPB)~\cite{spb} that has been inspired by the Media/Publishing industry (namely BBC\footnote{\url{http://www.bbc.com/}}).
-The application scenario of this benchmark simulates a media or a publishing organization that handles large amount of streaming content (e.g., news, articles).
-\iffalse This content is enriched with metadata that describes it and links it to reference knowledge -- taxonomies and databases that include relevant concepts, entities and factual information.
-The SPB data generator produces scalable in size synthetic large data.
-Synthetic data consists of a large number of annotations of media assets that refer entities found in reference datasets.\fi The data generator mimics three types of relations in the generated synthetic data: clustering of data, correlations of entities, and random tagging of entities.
+\iffalse The following three benchmarks were developed and are currently maintained.\fi In the Semantic Web 
+domain, it released the Semantic Publishing Benchmark (SPB)~\cite{spb} that has been inspired by the 
+Media/Publishing industry (namely BBC\footnote{\url{http://www.bbc.com/}}). The application scenario 
+of this benchmark simulates a media or a publishing organization that handles large amount 
+of streaming content (e.g., news, articles). \iffalse This content is enriched with metadata that describes 
+it and links it to reference knowledge -- taxonomies and databases that include relevant concepts, 
+entities and factual information. The SPB data generator produces scalable in size synthetic large data. 
+Synthetic data consists of a large number of annotations of media assets that refer entities found in 
+reference datasets.\fi The data generator mimics three types of relations in the generated synthetic data: 
+correlations of entities, data clustering, and random tagging of entities.
 Two workloads are provided: (1) basic, involving an interactive query-mix querying the relations between entities in reference data, and (2) advanced,  focusing on interactive and analytical query-mixes.
@@
 \paragraph{LinkGen} LinkGen is a synthetic linked data generator that has been designed to generate RDF datasets for a given vocabulary~\cite{10.1007/978-3-319-46547-0_12}.
-The generator is designed to receive a vocabulary as an input  and supports two statistical distributions for generating entities: Gaussian distribution and Zipf's power-law distribution.
+The generator is designed to receive a vocabulary as an input  and supports two statistical distributions for generating entities:  Zipf's power-law distribution and Gaussian distribution.
 LinkGen can augment the generated data with inconsistent and noisy  data such as updating a given datatype property with two conflicting values or  adding triples with syntactic errors.
-\iffalse, adding wrong statements by assigning them with invalid domain and creating instances with no type information.\fi The generator also provides a feature to inter-link the generated objects with real ones given that the end-user provides entities from real datasets.
+\iffalse, adding wrong statements by assigning them with invalid domain and creating instances with no type information.\fi The generator also provides a feature to inter-link the generated objects with real-world ones from user-provided real-world datasets.
 The datasets can be generated in any of of two modes: on-disk and streaming.
@@
 The authors focus mainly on the  \emph{structuredness} (\emph{coherence}) of each benchmark dataset claiming that a primitive metric (e.g., the number of triples or the average in/outdegree) quantifies only some target characteristics of each dataset.
-The degree of structuredness of a dataset $D$ with respect to a type $T$ is based on  the regularity of instance data in $D$ in conforming to type $T$.
+With respect to a type $T$ the degree of structuredness of a dataset $D$  is based on  the regularity of instance data in $D$ in conforming to type $T$.
 The type system is extracted from the data set by finding the RDF triples that have property  \texttt{http://www.w3.org/1999/02/22-rdf-syntax-ns\#type} and extract type $T$ from their object.
-Properties of $T$ are determined as the union of all the properties that the instances of type $T$ have.
+Properties of $T$ are determined as the union of all properties of type $T$.
 The structuredness is then expressed as a weighted sum of share of set properties of each type, whereas higher weights are assigned to types with more instances.

### 2019-08-06 generators_SocialNetworks.tex
Irena's pass (plagiarism) pp 11-17

@@
 features~\cite{Chakrabarti:2006:GML:1132952.1132954}. For example, a social
-graph often has high \emph{clustering coefficient}, i.e., the degree of
-transitivity of a graph. Or, its diameter, i.e., the longest shortest path
+networks graph often has a high  degree of
+transitivity of the graph (so-called \emph{clustering coefficient}). Or, its diameter, i.e., the longest shortest path
 amongst some fraction (e.g. 90\%) of all connected nodes, is usually low due to
@@
 
-Another important aspect of social networks is the community effect. A detailed
+Another key aspect of social networks is the community effect. A detailed
 study of structure of communities in 70 real-world networks is provided, e.g.,
@@
 ~\cite{Prat-Perez:2014:CSS:2621934.2621942} analyzed the structure of
-communities (clustering coefficient, triangle participation ratio, bridges,
-diameter, conductance and size) in both real-world graphs and outputs of
+communities (clustering coefficient, triangle participation ratio, 
+diameter, bridges, conductance, and size) in both real-world graphs and outputs of
 existing graph generators such as LFR~\cite{PhysRevE.78.046110} and the
@@
 communities  in different graphs have common distributions and that communities
-in a single graph have different characteristics and are challenging to be represented using a single
+of a single graph have different characteristics and are challenging to be represented using a single
 model.
@@
 data fusion techniques utilizing various real-world data sources such as U.S.
-Census data, responses to an activity survey or a time-use survey.
+Census data, responses to a time-use survey or an activity survey.
 %Demographic information for each person and location, a minute-by-minute
@@
 %techniques.
-The result is captured by a dynamic social contact network. Similar methods for
+The result is captured by a dynamic network of social contacts. Similar methods for
 agent-based strategies have been reported
@@
 \cite{Yao2011} distinguished between two types of social network graphs -- the
-\emph{linkage graph}, where nodes represent people and edges correspond to their
+\emph{linkage graph}, where nodes correspond to people and edges correspond to their
 friendships, and the \emph{activity graph}, where nodes also represent people
@@
 the authors discover that they both exhibit high clustering coefficient
-(community structure), small diameter, and power-law degree distribution.
+(community structure), power-law degree distribution and small diameter.
 Considering the dynamic properties they both have relatively stable clustering
@@
 difference in degree correlation (i.e., frequency of mutual connections of
-similar nodes) -- linkage graphs have positive degree correlation, activity
-graphs have neutral degree correlation. With regards to the findings, the
+similar nodes) -- activity graphs have neutral, whereas linkage graphs have positive degree correlation. With regards to the findings, the
 proposed generator focusses on linkage graphs with positive degree correlation.
@@
 algorithm~\cite{Leskovec:2005:GOT:1081870.1081893} with link symmetry. It has
-two parameters: the \emph{burning probability} $P_b$ and the \emph{symmetry
-probability} $P_s$. $P_b$ ensures a BFS-based forward burning process in which
+two parameters: the \emph{symmetry
+probability} $P_s$ and the \emph{burning probability} $P_b$. $P_b$ ensures a forward burning process based on BFS in which
 fire burns strongly with $P_b$ approaching 1.  $P_s$ ensures backward linking

### 2019-08-06 challenges.tex
Irena's pass (plagiarism) - th rest of the text

@@
 significant aspect, especially in the activity
-graphs~\cite{doreian1997evolution,Kumar:2006:SEO:1150402.1150476,Hellmann2014583,wang2013,Kossinets88,Viswanath:2009:EUI:1592665.1592675}.
+graphs~\cite{Kumar:2006:SEO:1150402.1150476,doreian1997evolution,Hellmann2014583,wang2013,Viswanath:2009:EUI:1592665.1592675,Kossinets88}.
 However, as shown
@@
 dynamic graphs}, i.e. graphs where the clustering corresponds to the partition
-of nodes into natural groups based on the concept of intra-cluster
-versus inter-cluster density of edges. The generator generates a time series
+of nodes into natural groups based on the concept of density of edges within and between the clusters. The generator generates a time series
 of random graphs $G_0, G_1, ..., G_n$, where $G_t$ emerges from $G_{t-1}$ via
@@
 are the so-called \emph{multi-model databases}~\cite{Lu:2019:MDN:3341324.3323214} that enable to store and
-thus query across structurally different data, including structured, semi-structured, and unstructured. There exist various types of
+thus query across structurally different data, including unstructured, semi-structured, and structured. There exist various types of
 multi-model systems combining  distinct subsets of Big Data structures including graph data.
@@
 Another interesting approach to multi-model data is to adopt a unifying
-expressive graph data model, known as property graph data
-model~\cite{BFVY18}. Such a model allows to specify multi-edges and list of
+expressive graph data model, so-called \emph{property graph data
+model}~\cite{BFVY18}. Such a  model allows to specify multi-edges and list of
 properties for the nodes. Synthetic graph generators for property graphs and its
@@
 explore their application to generate graphs. This is the case of
-~\cite{kipf2016variational,grover2018graphite,simonovsky2018graphvae,li2018learning,you2018graphrnn},
+~\cite{simonovsky2018graphvae,kipf2016variational,grover2018graphite,li2018learning,you2018graphrnn},
 which present several generative models to generate realistic graphs.  Such
@@
 graph~\cite{kipf2016variational,grover2018graphite} or generate small
-graphs~\cite{simonovsky2018graphvae,li2018learning,you2018graphrnn}. The
+graphs~\cite{simonovsky2018graphvae,you2018graphrnn,li2018learning}. The
 technique proposed in~\cite{you2018graphrnn} is capable of generating graphs

### 2019-08-06 generators_SocialNetworks.tex
Irena's pass (plagiarism) - th rest of the text

@@
 correlated structure. Hence, the existing data values influence the probability
-of choosing a certain property value from a pre-defined dictionary, or the
-probability of connecting two nodes. For example, the degree distribution can be
-correlated with the properties of a node and thus, e.g., people having many
+of choosing a particular property value from a pre-defined dictionary or connecting two nodes. For example, the degree distribution can be
+correlated with the properties of a node and thus, e.g., people who have many
 friend relationships typically post more comments and pictures. The data
@@
 
-\paragraph{SIB} The developers of the Social Network Intelligence BenchMark (SIB)\footnote{\url{https://www.w3.org/wiki/Social_Network_Intelligence_BenchMark}} based the design of their benchmark on the claim that existing benchmarks are limited in reflecting the characteristics of the real RDF databases and are mostly focusing on the relational style aspects.
+\paragraph{SIB} The developers of the Social Network Intelligence BenchMark (SIB)\footnote{\url{https://www.w3.org/wiki/Social_Network_Intelligence_BenchMark}} based the design of their benchmark on the claim that the state-of-the-art benchmarks are limited in reflecting the characteristics of the real RDF databases and are mostly focusing on the relational style aspects.
 Hence, they proposed a benchmark for  query evaluation using real graphs~\cite{sib}.
@@
 has two basic parameters: homophily and link density. A high \emph{homophily}
-value reflects that links have higher chances to be established among the nodes with the
-same label; these labels can be considered as being equivalent to community
-membership.
+value reflects that links have higher chances to be established among the nodes belonging to the same community, 
+whereas the community membership is represented by the same labels.
 
@@
 forums. The three query workloads involve: (1) SNB-Interactive, i.e., complex
-read-only queries accessing a significant portion of data, (2) SNB-BI, i.e.,
+read-only queries accessing a high portion of data, (2) SNB-BI, i.e.,
 queries accessing a high percentage of  entities and grouping them in various
@@
 \paragraph{Towards More Realistic Data} \cite{Nettleton2016} argued that the majority of existing works focuses on
-topology generation which approximates the characteristics of a real-world social
-network (e.g., a small graph diameter, skew degree
-distribution, small average path length, and community structures); however,  this is usually done without any data. Hence, they
+topology generation which approximates the features of a real-world social
+network (e.g., community structures, skew degree
+distribution, a small average path length, or a small graph diameter); however,  this is usually done without any data. Hence, they
 introduced a general stochastic modeling approach that enables the users to
-populate a graph topology with data. The approach has three steps: (1) topology
+fill a graph topology with data. The approach has three steps: (1) topology
 generation (using R-MAT) plus community identification using the Louvain
@@
 SNAP\footnote{\url{https://snap.stanford.edu/data/}}, (2) data definition
-that describes distribution profiles, attribute value definitions, using a
-parameterizable set of data propagation rules and affinities, and (3) data
+that describes  definitions of attribute values (distribution profiles) using a
+parameterizable set of affinities and data propagation rules, and (3) data
 population.

### 2019-08-06 generators_community_detection.tex
Irena's pass (plagiarism) - th rest of the text

@@
 Community detection is one of the many graph analytics algorithms typically used
-in domains such as social networks or bioinformatics. \emph{Communities} are groups of nodes that are highly mutually connected, while being scarcely connected to
-the rest of the graph. Such communities emerge from the fact that real-world graphs
+in domains such as social networks or bioinformatics. \emph{Communities} are usually defined as sets of nodes that are highly mutually connected, while being scarcely connected to
+the other nodes of the graph. Such communities emerge from the fact that real-world graphs
 are not random, but follow real-world dynamics that make similar entities to
@@
 introduces the concept of the ``mixing factor'', which consists of the percentage of
-edges in the graph connecting nodes that belong to different communities. Such parameter
+edges in the graph connecting nodes that belong to distinct communities. Such parameter
 allows  the degree of modularity of the generated graph  to be tuned, thus
@@
 that the generation process of such models is mathematically tractable, they
-are typically used to analyze the limitations of community detection
-algorithms such as those based on modularity
+are typically used to analyze the limitations of algorithms for community detection
+ such as those based on modularity
 optimization~\cite{fortunato2007resolution} or based on

### 2019-12-18 generators.tex
Typos fixed by Sherif

@@
 
-\input{generators_general}
+\subsection{General Graphs}
+\label{sec:generators_general}
 
-\input{generators_LinkedData}
+We start by focusing on approaches that have been designed for dealing with the
+generation of general graph data that is not aimed at a particular application
+domain. In general, such generators focus on reproducing properties observed in
+real graphs regardless of their domain such as the degree distribution, the
+diameter, the presence of a large connected component, a community structure or
+a significantly large clustering coefficient.
 
-\input{generators_GraphDatabases}
+%Currently, there exists a number of tools which involve a kind of
+%general graph data generator, such as gtools from projects nauty and
+%Traces~\cite{gtools} or the Stanford GraphBase~\cite{GraphBase}. We, however,
+%focus on primarily generating/benchmarking projects targeting the Big Data
+%world.
 
-\input{generators_SocialNetworks}
+\paragraph {Preferential Attachment} Barabasi and
+Albert~\cite{Barabasi99emergenceScaling} introduced a graph generation model
+that relies on two main mechanisms. The first mechanism is continuously
+expanding the graphs by adding new vertices. The second mechanism is to
+preferentially attach the new vertices   to the nodes/regions that are already
+well connected. So, in this approach, the generation of large graphs is governed
+by standard, robust self-organizing mechanisms that go beyond the
+characteristics of individual applications.
+
+\paragraph {R-MAT} R-MAT (\emph{R}ecursive \emph{Mat}rix) is a procedural
+synthetic graph generator which is designed to generate power-law degree
+distributions~\cite{DBLP:conf/sdm/ChakrabartiZF04}.  The generator is recursive
+and employs a fairly small number of parameters.  In principle, the strategy of
+this generator is to achieve simple means to produce graphs whose properties correspond to
+properties of the real-world graphs. In particular, the design goal of R-MAT is to
+produce graphs which mimics the degree distributions, imitate a community
+structure and have a small diameter. R-MAT can generate weighted, directed and
+bipartite graphs.
+
+\paragraph{HPC Scalable Graph Analysis Benchmark} The HPC Scalable Graph
+Analysis Benchmark~\cite{HPCgraph,Bader:2005:DIH:2099301.2099360} consists of a
+weighted, directed graph that has a power-law distribution and four related
+analysis techniques (namely graph construction, graph extraction with BFS,
+                     classification of large vertex sets, and graph analysis
+                     with betweenness centrality). The generator has the
+following parameters: the number of nodes, the number of edges, and maximum weight of
+an edge. It outputs a list of tuples containing identifiers of vertices of an
+edge (with the direction from the first one to the second one) and weights
+(positive integers  with a uniform random distribution) assigned to the edges of
+the multigraph.  The algorithm of the generator is based on R-MAT.
+%To reduce the data
+%locality, the vertex ids are randomly permuted and the output
+%tuples are shuffled. A related project from the same authors
+%developed for the 9th DIMACS Shortest Paths Challenge is GTgraph~\cite{GTgraph}.
+%t involves three types of graphs: (1) Erd\"{o}s-R\'{e}nyi random graphs, (2)
+%different graphs from the DARPA HPCS SSCA\#2 graph theory benchmark
+%(version 1.0), and (3) small-world graphs generated using the R-MAT graph
+%generator.
+
+\paragraph{GraphGen} For the purpose of testing the scalability of an indexing
+technique called FG-index~\cite{Cheng:2007:FTV:1247480.1247574} on the size of the
+database of graphs, their average size and average density, the authors have
+also implemented a synthetic generator called
+GraphGen\footnote{https://www.cse.ust.hk/graphgen/}. It relies on data generation code for associations and sequential
+patterns provided by IBM\footnote{From 1996, no longer available at
+\url{http://www.almaden.ibm.com/cs/projects/iis/hdb/Projects/data
+mining/mining.shtml}}. GraphGen yields a collection of undirected, labeled and
+connected graphs. It addresses the performance evaluation of frequent subgraph mining
+algorithms and graph query processing algorithms. The result is represented as a
+list of graphs, each consisting of a list of nodes along with a list of edges.
+
+%\paragraph{Graph 500 Benchmark} The Graph 500 Benchmark~\cite{Graph500} includes
+%a scalable data generator which produces weighted, undirected graph as a list of
+%edge tuples containing the label of start vertex and end vertex together with a
+%weight that represents data assigned to the edge. The space of vertex  labels is
+%the set of integers beginning with 0. The input values required to describe the
+%graph are (1) scale, i.e., the logarithm base two of the number of vertices, and
+%(2) edge factor, i.e., the ratio of the graph's edge count to its vertex count
+%(i.e., half the average degree of a vertex in the graph). The graph generator is
+%a Kronecker generator similar to R-MAT. The data must not exhibit any locality,
+%so in the final step the vertex labels and order of edges are randomly shuffled.
+%The covered operations currently involve BFS; however, the authors intend to
+%involve also two more types -- optimization (single source shortest path) and
+%edge-oriented (maximal independent set) -- and five graph-related business areas:
+%cybersecurity, medical informatics, data enrichment, social networks, and
+%symbolic networks.
+
+\paragraph{BTER} BTER (Block Two-Level
+Erd\"{o}s-R\'{e}ny)~\cite{kolda2014scalable} is a graph generator based on the
+creation of multiple Erd\"{o}s-R\'{e}ny graphs with different connection
+probabilities  of which they are connected randomly between them. As the main feature, BTER is able
+to reproduce input degree distributions and average clustering
+coefficient per degree values. The generator starts by grouping the vertices
+by degree $d$, and forming groups of size $d+1$ of nodes with degree $d$. Then, these
+groups are assigned an internal edge probability in order to match the observed
+average clustering coefficient of the nodes of such degree. Based on this
+probability, for each node, the excess degree (i.e, the degree that in
+expectation will not be realized internally in the group) is computed and used to connect
+nodes from different groups at random. The authors describe a highly scalable
+MapReduce-based implementation that is able to generate large graphs (consisting of
+billions of nodes) in a reasonable amounts of time.
+
+\paragraph{Darwini} Darwini~\cite{edunov2016darwini} is an extension of BTER
+designed to run on Vertex Centric computing frameworks like
+Pregel~\cite{malewicz2010pregel} or Apache Giraph~\cite{ching2015one}, with the
+additional feature that it is more accurate when reproducing the clustering
+coefficient of the input graph. Instead of just focusing on the average
+clustering coefficient for each degree, Darwini is able to model the clustering
+coefficient distribution per degree. It achieves this by gathering the nodes
+of the graph into buckets based on the expected number of closed triangles that they need
+to close in order to attain the expected clustering coefficient. The latter is
+sampled from the input distributions. Then, the vertices in each bucket are
+connected randomly with a probability that would produce the expected
+desired number of triangles for each bucket. Then, as in BTER, the excess degree
+is used to connect the different buckets. The authors report that Darwini is
+able to generate graphs with billions and even trillions of edges.
+
+%\paragraph{gtools} Projects nauty and Traces~\cite{gtools} are programs for
+%computing automorphism groups of graphs and digraphs~\cite{McKay201494}; they
+%can also produce a canonical label. In the respective package there is also
+%suite of programs called gtools which involve generators for non-isomorphic
+%graphs, bipartite graphs, digraphs, and multigraphs.
+
+\paragraph{RTG} \emph{The Random Typing Generator} (RTG)~\cite{DBLP:journals/datamine/AkogluF09} aims at generating realistic graphs.
+In particular, it outputs (un)weighted, (un)directed, as well as uni/bipartite graphs, whereas the realism of the output is ensured by 11 laws (e.g., densification power law, weight power law, small and shrinking diameter, community structure, etc.) known to be typically exhibited by real-world graphs.
+On input it requires 4 parameters ($k$, $q$, $W$, and $\beta$) that correspond to the core Miller's observation~\cite{miller1957} that a random process (namely, having a keyboard with $k$ characters and a space, the process of random typing of $W$ words, where the probability of hitting a space is $q$ and the probability of hitting any other characters is $(1-q)/k$) leads to Zipf-like power laws (of the resulting words) plus in addition (using imbalance factor $\beta$) ensure homophily and community structure.
+RTG is based on the idea creating an edge between pairs of consecutive words.
+
+Paper~\cite{DBLP:conf/wbdb/AmmarO13} further extends this idea mainly in the direction of simplification of specifying of the parameters.
+Instead of Miller's parameters that are not much associated with graphs, the authors prove and exploit their relationship with size and density of the target graph.
+
+\paragraph{Strengths and Weaknesses of General Graph Generators}
+In general, existing general graph generators produce graphs with the following
+properties: skewed degree distribution (e.g., powerlay), small diameter, a large largest connected component, large
+clustering coefficient, and some degree of
+community structure. Degree distribution can be typically configured while other
+properties are just a result of the generation process and cannot be controlled
+by any means.
+
+This is not the case of BTER and Darwini, which besides the degree distribution,
+they also allow tuning of the clustering coefficient. However, some use cases
+demand for more control on the characteristics of the generated graphs.
+This is the case, for example, of benchmarking, where the underlying graph
+structure has direct implications to the performance of the graph algorithms
+to run. For this reason, the design of graph generators with the capability of fine
+tuning the characteristics of the generated graphs still remains as an open
+challenge. The questions that remain are what characteristics to tune
+and which are the algorithms that depend on such characteristics.
+
+\subsection{Semantic Web}
+\label{sec:generators_LinkedData}
+With the dawn of the concept of Linked Data it is a natural development that there would emerge respective
+benchmarks involving both synthetic data and  data sets   with real-world characteristics.
+The used data sets correspond to RDF representation of relational-like data~\cite{Guo2005158,Bizer09theberlin}, social network-like data~\cite{Schmidt2010}, or specific and significantly more complex data structures such as biological data~\cite{Wu2014}.
+In this section, we provide an overview of benchmarking systems involving a kind of graph-based RDF data generator or data modifier.
+%Other types of systems or particular results can be found, e.g., at~\cite{RdfStoreBenchmarking}.
+
+\iffalse
+Considering the Big Data world, the Linked Data in general definitely belong to this group since we assume that the Linked (Open) Data Sets form a common Linked Open Data cloud\footnote{\url{http://lod-cloud.net/}}.
+On the other hand, the particular data sets can be relatively small.
+\fi
+
+\paragraph{LUBM} The use-case driven Lehigh University Benchmark (LUBM)\footnote{\url{http://swat.cse.lehigh.edu/projects/lubm/}} considers the university domain.
+The ontology defines 43 classes and 32 properties~\cite{Guo2005158}.
+In addition, 14 test queries are provided in the LUBM benchmark.
+In particular, the benchmark focuses on \emph{extensional} queries, i.e., queries which target the particular data instances of the ontology, as an opposite to \emph{intentional} queries, i.e., queries which target properties and classes of the ontology.
+The Univ-Bench Artificial  (UBA) data generator features repeatable and random  data generation (exploiting classical linear congruential generator, LCG, of numbers).
+In particular, the data which is produced by the generator are assigned zero-based indexes (i.e., \emph{University0}, \emph{University1} etc.), thus they are reproducible at any time with the same indexes.
+The generator naturally allows to specify a seed for random number generation, along with the starting index and the desired number of universities.
+
+An extension of LUBM, the Lehigh BibTeX Benchmark (LBBM)~\cite{Wang2005}, enables generating synthetic data for different ontologies.
+The data generation process is managed through two main phases: (1) the property-discovery phase, and (2) the data generation phase.
+LBBM provides a probabilistic model that can emulate the discovered properties of the data of a particular domain and generate synthetic data exhibiting similar properties.
+Synthetic data are generated using a Monte Carlo algorithm.
+The approach is demonstrated on the Lehigh University BibTeX ontology which consists of 28 classes along with 80 properties.
+The LUBM benchmark includes 12 test queries that were designed for the benchmark data.
+Another extension of LUBM, the University Ontology Benchmark (UOBM)\footnote{\url{https://www.cs.ox.ac.uk/isg/tools/UOBMGenerator/}}, focuses on two aspects: (1) usage of all constructs of OWL Lite and OWL DL~\cite{owl} and (2) lack of necessary links between the generated data which thus form isolated graphs~\cite{Ma:2006:TCO:2094613.2094629}.
+In the former case the original ontology is replaced by the two types of extended versions from which the user can choose.
+In the latter case cross-university and cross-department links are added to create a more complex graph.
+
+\paragraph{IIMB} Ferrara et al.~\cite{Ferrara08OM} proposed the ISLab Instance Matching Benchmark (IIMB)\footnote{\url{http://www.ics.forth.gr/isl/BenchmarksTutorial/}} for the problem of instance matching.
+For any two objects $o_1$ and $o_2$ adhering to different ontologies or to the same ontology, instance matching is specified in the form of a function $Om(o_1, o_2) \rightarrow \{0, 1\}$,  where $o_1$ and $o_2$ are linked to the same real-world object (in which case the function maps to $1$) or $o_1$ and $o_2$ are representing different objects (in which case the function maps to $0$).
+It targets the domain of movie data which contains 15 named classes, along with 5 objects and 13 datatypes.
+The data are extracted from IMDb\footnote{\url{http://www.imdb.com/}}.
+The data generator corresponds to a data modifier which simulates differences between the data.
+In particular it involves data value differences (such as typographical errors or usage of different standard formats, e.g., for names), structural heterogeneity (represented by different levels of depth for properties, diverse aggregation criteria for properties, or missing values specification) and logical heterogeneity (such as, e.g., instantiation on disjoint classes or various subclasses of the same superclass).
+
+\paragraph{BSBM} The Berlin SPARQL Benchmark (BSBM)\footnote{\url{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}}, is centered around an e-commerce application domain with object types such as \emph{Customer}, \emph{Vendor}, \emph{Product} and \emph{Offer} in addition to the relationship among them~\cite{Bizer09theberlin}.
+The benchmark provides a workload that has 12 queries with 2 types of query workloads (i.e., 2 sequences of the 12 queries) emulating the navigation pattern and search of a consumer seeking a product.
+The data generator is capable of producing arbitrarily scalable datasets by controlling the number of products ($n$) as a scale factor.
+The scale factor also impacts other data characteristics, such as, e.g., the depth of type hierarchy of products, branching factor, the number of product features,  etc.
+BSBM can output two representations, i.e.
+an RDF representation along with a relational representation.
+Thus, BSBM also defines an SQL~\cite{sql} representation of the queries.
+This allows comparison of SPARQL~\cite{sparql} results  to be compared against the performance of traditional RDBMSs.
+
+\paragraph{SP$^2$Bench} The SP$^2$Bench\footnote{\url{http://dbis.informatik.uni-freiburg.de/forschung/projekte/SP2B/}}
+is a language-specific benchmark~\cite{Schmidt2010} which is based on the DBLP dataset. %, so the types involve Person, Inproceedings, Article etc.
+The generated datasets follow the key characteristics of the original DBLP dataset.
+In particular, the data mimics the correlations between entities.
+All random functions of the generator use a fixed seed that ensures that the data generation process is deterministic.
+SP$^2$Bench is accompanied by 12 queries covering the various types of operators such as RDF access paths in addition to typical RDF constructs.
+
+%\paragraph{JustBench} ~\cite{Bail:2010:JFO:1940281.1940285} ...
+
+\paragraph{DBPSB} DBpedia SPARQL Benchmark (DBPSB)\footnote{\url{http://aksw.org/Projects/DBPSB.html}} proposed at the University of Leipzig has been designed using workloads that have been generated by applications and humans~\cite{Morsey2011,Morsey:2012:UBR:2900929.2901031}.
+In addition, the authors argue that benchmarks like LUBM, BSBM, or SP$^2$Bench resemble relational database benchmarks involving relational-like data which is structured using a small amount of homogeneous classes, whereas, in reality, RDF datasets are tending to be more heterogeneous.
+For example, DBpedia 3.6 consists of 289,016 classes, whereas 275 of them are defined based on the DBpedia ontology.
+In addition, in property values different data types as well as references to objects of the various types are
+used.
+Hence, they presented a universal SPARQL benchmark generation approach which uses a flexible data production mechanism that mimics the input data source.
+This dataset generation process begins using an input dataset; then multiple datasets with different sizes  are then generated by duplicating all the RDF triples with changing their namespaces.
+For generating smaller datasets, an adequate selection of all triples is selected randomly or using a sampling mechanism over the various classes in the dataset.
+\iffalse The goal of the query analysis and clustering is to detect prototypical queries on the basis of their frequent usage and similarity.\fi The methodology is applied on the DBpedia SPARQL endpoint and a set of 25 templates of SPARQL queries is derived to cover frequent SPARQL features.
+
+\paragraph{LODIB} The Linked Open Data Integration Benchmark (LODIB)\footnote{\url{http://lodib.wbsg.de/}} has been designed with the aim of reflecting the real-world heterogeneities that exist on the Web of Data in order to enable testing of Linked Data translation systems~\cite{DBLP:conf/www/RiveroSBR12}.
+It provides a catalogue of 15 data translation patterns (e.g., rename class, remove language tag etc.), each of which is a common data translation problem in the context of Linked Data.
+The benchmark provides a data generator that produces three different synthetic data sets that need to be translated
+by the system under test into a single target vocabulary.
+They  reflect the pattern distribution in analyzed 84 data translation examples from the LOD Cloud.
+The data sets reflect the same e-commerce scenario used for BSBM.
+
+\paragraph{Geographica} The Geographica benchmark\footnote{\url{http://geographica.di.uoa.gr/}} has been designed to target the area of geospatial data~\cite{DBLP:conf/semweb/GarbisKK13} and respective SPARQL extensions GeoSPARQL~\cite{battle2012enabling} and stSPARQL~\cite{koubarakis2010modeling}.
+The benchmark involves a real-world workload that uses openly available datasets that cover various geometry elements (such as, e.g., lines, points, polygons, etc.) and  a synthetic workload.
+In the former case there is a (1) a micro benchmark that evaluates primitive spatial functions (involving 29 queries) and (2) macro benchmark that tests the performance of RDF engines in various application scenarios such as  map exploring and search (consisting of 11 queries).
+In the latter case of a synthetic workload the generator produces synthetic datasets of different sizes that corresponds to an ontology based on OpenStreetMap  and instantiates query templates.
+\iffalse The spatial extent of the land ownership dataset constitutes a uniform grid of $n \times n$ hexagons, whereas the size of each dataset is given relatively to $n$.\fi The generated SPARQL query workload is corresponding to spatial joins and selection using 2 query templates.
+
+\paragraph{WatDiv} The Waterloo SPARQL Diversity Test Suite (WatDiv)\footnote{\url{http://dsg.uwaterloo.ca/watdiv/}} has
+been designed at the University of Waterloo. It implements stress testing tools that focus on addressing the observation
+that the state-of-the-art SPARQL benchmarks do not fully cover the variety of queries and
+workloads~\cite{Aluc:2014:DST:2717213.2717229}. The benchmark focuses on two types of query aspects --
+structural and data-driven -- and performs a detailed analysis on existing SPARQL benchmarks
+(LUBM, BSBM, DBPSB, and SP$^2$Bench) using these two properties of queries. The structural features involve triple
+pattern count, join vertex count, join vertex degree, and join vertex count. The data-driven features involve
+result cardinality and several types of selectivity. The analysis of the four benchmarks reveals that their diversity is
+insufficient for evaluation of the weaknesses/strengths of the distinct design alternatives implemented by the different
+RDF systems.
+
+In particular, WatDiv, provides (1) a data generator which generates scalable datasets according to the WatDiv
+schema, (2) a query template generator which produces a  set of query templates according to the WatDiv schema, and
+(3) a query generator that uses the generated templates and instantiates them  with real RDF values from the dataset, and (4) a feature extractor which extracts the structural features of the generated data and workload.
+%For the study in the paper the authors generated 12,500 test queries from 125 query templates.
+
+\paragraph{RBench} RBench~\cite{Qiao:2015:RAR:2723372.2746479} is an application-specific benchmark which receives any RDF dataset as an input and produces a set of datasets, that have similar characteristics of the input dataset, using size scaling factor $s$ and (node) degree scaling factor $d$.
+These factors ensure that the original RDF graph $G$ and the synthetic graph $G'$ are similar and the average node degree and the number of edges of $G'$ are changed by $s$ and $d$ respectively.
+\iffalse A generated benchmark dataset is considered similar to the given dataset if their values for the dataset evaluation metrics and query evaluation times for different techniques are similar.
+Three evaluation metrics are utilized for this purpose: dataset coherence (i.e., a measure how uniformly predicates are distributed among the same type/class), relationship specialty (i.e., the number of occurrences of the same predicate associated with each resource), and literal diversity.\fi A query generation process has been implemented to produce 5 different types of queries (edge-based queries, node-based queries, path queries, star queries, subgraph queries) for any generated data.
+The benchmark project FEASIBLE~\cite{Saleem2015} is also an application-specific benchmark; however, contrary to RBench, it is designed to produce benchmarks from the set of sample input queries of a user-defined
+size.
+
+In practice, one way for handling big RDF graphs is to process them using the
+\emph{streaming} mode where the data stream could consist of the edges of the
+graph. In this mode, the RDF processing algorithms can process the input
+stream in the order it arrives while using only a limited amount of
+memory~\cite{mcgregor2014graph}. The streaming mode has mainly  attracted the attention of the
+RDF and Semantic Web community.
+
+\paragraph{S2Gen}   Phuoc et al.~\cite{le2012linked} presented
+an evaluation framework for linked stream data processing engines. The framework
+uses a datasets generated with the Stream Social network data Generator
+(S2Gen), which
+simulates streams of user interactions (or events) in social networks
+(e.g., posts) in addition to the  user metadata such as users' profile
+information, social network relationships, posts, photos and GPS information.
+The data generator of this framework provides the users the flexibility to
+control the characteristics of the generated stream by tanning a range of
+parameters, which includes the frequency at which interactions are generated,
+limits such as the maximum number of messages per user
+and week, and the correlation probabilities between the different objects (e.g.,
+users) in the social network.
+
+\paragraph{RSPLab} Tommasini et al.~\cite{tommasini2017rsplab} introduced
+another framework for benchmarking RDF Stream Processing systems, RSPLab. The
+Streamer component of this framework is designed to publish RDF streams from the
+various existing RDF benchmarks (e.g., BSBM, LUBM).
+In particular, the Streamer  component uses TripleWave\footnote{\url{http://streamreasoning.github.io/TripleWave/}}, an
+open-source framework which enables to share RDF streams on the
+Web~\cite{mauri2016triplewave}.   TripleWave acts as a means for plugging-in
+and combining streams from multiple Web data sources using either pull or push mode.
+
+\paragraph{LDBC}  The Linked Data Benchmark Council\footnote{\url{http://ldbcouncil.org/industry/organization/origins}} (LDBC)~\cite{Angles:2014:LDB:2627692.2627697} %is a result of a (closed) EU project that brought together a community of academic researchers and industry that
+had the goal of developing an open source, yet industrial grade benchmarks for RDF and graph databases.
+\iffalse The following three benchmarks were developed and are currently maintained.\fi In the Semantic Web
+domain, it released the Semantic Publishing Benchmark (SPB)~\cite{spb} that has been inspired by the
+Media/Publishing industry (namely BBC\footnote{\url{http://www.bbc.com/}}). The application scenario
+of this benchmark simulates a media or a publishing organization that handles large amount
+of streaming content (e.g., news, articles). \iffalse This content is enriched with metadata that describes
+it and links it to reference knowledge -- taxonomies and databases that include relevant concepts,
+entities and factual information. The SPB data generator produces scalable in size synthetic large data.
+Synthetic data consists of a large number of annotations of media assets that refer entities found in
+reference datasets.\fi The data generator mimics three types of relations in the generated synthetic data:
+correlations of entities, data clustering, and random tagging of entities.
+Two workloads are provided: (1) basic, involving an interactive query-mix querying the relations between entities in reference data, and (2) advanced,  focusing on interactive and analytical query-mixes.
+The LDBC has designed two other benchmarks: the Social Network Benchmark (SNB)~\cite{Erling:2015:LSN:2723372.2742786} for the social network domain  (see Section~\ref{sec:generators_socialnetworks}) and Graphalytics~\cite{Iosup:2016:LGB:3007263.3007270}   for the analytics domain.% (see Section~\ref{sec:generators_analytics}).
+
+\paragraph{LinkGen} LinkGen is a synthetic linked data generator that has been designed to generate RDF datasets for a given vocabulary~\cite{10.1007/978-3-319-46547-0_12}.
+The generator is designed to receive a vocabulary as an input  and supports two statistical distributions for generating entities:  Zipf's power-law distribution and Gaussian distribution.
+LinkGen can augment the generated data with inconsistent and noisy  data such as updating a given datatype property with two conflicting values or  adding triples with syntactic errors.
+\iffalse, adding wrong statements by assigning them with invalid domain and creating instances with no type information.\fi The generator also provides a feature to inter-link the generated objects with real-world ones from user-provided real-world datasets.
+The datasets can be generated in any of of two modes: on-disk and streaming.
+
+\paragraph{Strengths and Weaknesses of Semantic Web Graph Generators}  Graphs are intuitive and standard representation for the RDF model that form the basis for the Semantic Web community which has been very active on building several benchmarks, associated with graph generators that had various design principles.
+
+A comparison of 4 RDF benchmarks (namely TPC-H~\cite{TPC-H} data expressed in RDF, LUBM, BSBM, and SP$^2$Bench) and 6 real-wold data sets (such as, e.g.,  DBpedia, the Barton Libraries Dataset~\cite{barton-benchmark} or
+WordNet~\cite{Miller:1995:WLD:219717.219748}) has been reported by~\cite{Duan:2011:AOC:1989323.1989340}.
+The authors focus mainly on the  \emph{structuredness} (\emph{coherence}) of each benchmark dataset claiming that a primitive metric (e.g., the number of triples or the average in/outdegree) quantifies only some target characteristics of each dataset.
+With respect to a type $T$ the degree of structuredness of a dataset $D$  is based on  the regularity of instance data in $D$ in conforming to type $T$.
+The type system is extracted from the data set by finding the RDF triples that have property  \texttt{http://www.w3.org/1999/02/22-rdf-syntax-ns\#type} and extract type $T$ from their object.
+Properties of $T$ are determined as the union of all properties of type $T$.
+The structuredness is then expressed as a weighted sum of share of set properties of each type, whereas higher weights are assigned to types with more instances.
+The authors show that the structuredness of the chosen benchmarks is fixed, whereas real-world RDF datasets are belonging to the non-tested area of the spectrum.
+As a consequence, they introduce a new benchmark that receives as input any dataset associated with a required level of structuredness and size (smaller than the size of the original data), and exploits the input documents as a seed to produce a subset of the original data with the target structuredness and size.
+In addition, they show that structuredness and size mutually influence each other.
+
+With the recent increasing momentum of streaming data, the Semantic Web community started to consider the issues and challenges of RDF streaming data.
+However, there is still a lot of open challenges that needs to tackled in this direction such as covering different real-world application scenarios.
+
+\subsection{Graph Databases}
+\label{sec:generators_GraphDatabases}
+
+Currently there exists a number of papers which compare the efficiency of graph databases with regards to distinct use cases, such as  the community detection problem~\cite{Beis2015}, social tagging systems~\cite{Giatsoglou2011}, graph traversal~\cite{Ciglan:2012:BTO:2374486.2375242}, graph pattern matching~\cite{Pobiedina2014}, data provenance~\cite{Vicknair:2010:CGD:1900008.1900067}, or even several distinct use cases~\cite{Grossniklaus2013Towar-24253}.
+However, the number of graph data generators and benchmarks that have been designed specifically for graph data management systems (Graph DBMS)  is relatively small.
+Either a general graph generator is used for benchmarking graph databases, such as, e.g., the HPC Scalable Graph Analysis Benchmark~\cite{Dominguez-Sal:2010:SGD:1927585.1927590} or the graph DBMS benchmarking tools are designed while having in mind a more general scope.
+Hence it is questionable whether a benchmark  that is targeted specifically for graph databases is necessary.
+\cite{Dominguez-Sal:2010:DDG:1946050.1946053} discussed this question and related topics.
+On the basis of a review of applications of graph databases (namely, social network analysis,  genetic interactions and recommendation systems), the authors analyzed and discussed the features of the graphs for these types of applications and how such features can affect the benchmarking process, various types of operations used in these applications and the characteristics of the evaluation setup of the benchmark.
+In this section, we focus on graph data generators and benchmarks that have been primarily targeting graph DBMSs.
+
+\paragraph{XGDBench} XGDBench~\cite{Dayarathna:2014:GDB:2676904.2676939} is an extensible  benchmarking platform for graph databases used in cloud-based systems. Its intent is to automate
+benchmarking of graph databases in the cloud by focusing on the domain social networking services.
+It extends the Yahoo!
+Cloud Multiplicative Attribute (MAG) Graph Serving Benchmark (YCSB)~\cite{Cooper:2010:BCS:1807128.1807152} and provides a set of standard workloads representing various performance issues.
+In particular, the workload of XGDBench involves basic operations such as read / insert / update / delete an attribute, loading of the list of neighbours and BFS traversal.
+Using the generators, 7 workloads are created, such as update heavy, read mostly, short range scan, traverse heavy etc.
+The data model of XGDBench is a simplified version of the Multiplicative Attribute Graph (MAG)~\cite{Kim2010} model, a synthetic graph model which models the interactions between node attributes and  graph structure.
+The generated graphs are thus in MAG format, with power-law degree distribution closely simulating real-world social networks.
+The simplified MAG algorithm accepts the required number of nodes and for each node the number of attributes, a threshold for random  initialization of attributes, a threshold for edge affinity which determines the existence of an edge between two nodes, and an affinity matrix.
+\iffalse It has been proven that MAG generates graphs with both analytically tractable and statistically interesting properties.\fi
+Large graphs can be generated on multi-core systems by XGDBench multi-threaded version.
+
+\paragraph{gMark}  gMark~\cite{gMark} is a schema-driven and domain-agnostic generator of both graph instances and graph query workloads.
+It can generate instances under the form of N-triples and queries in various concrete query languages, including OpenCypher\footnote{\url{https://neo4j.com/developer/cypher-query-language/}}, recursive SQL, SPARQL and LogicQL.
+In gMark, it is possible to specify a \emph{graph configuration} involving the admitted edge predicates and node labels occurring in the graph instance along with additional parameters such as degree distribution, occurrence constraints, etc.
+The \emph{Query workload configuration} describes parameters of the query workload to be generated, by including the number of queries, arity, shape and selectivity of the queries.
+The problem of deciding whether there exists a graph that satisfies a defined graph specification $G$ is NP-complete. The same applies to the problem of deciding
+whether there exists a query workload compliant with a given query workload configuration $Q$. In view of this, gMark adopts a best effort approach in which the
+parameters specified in the configuration files are attained in a relaxed fashion in order to achieve linear running time whenever possible.
+
+%The authors prove that deciding whether there exists a graph satisfying a given graph configuration $G$ is NP-complete. And, similarly, deciding
+%whether there exists a query workload satisfying a given query workload configuration $Q$ is also NP-complete.
+Hence, gMark generating is based on a heuristic strategy: it tries to achieve the exact values of the given parameters, however, in order to obtain linear running time it may decide to relax some.
+gMark generates graphs under the form of N-triples and query workloads in four concrete syntaxes, including Cypher\footnote{\url{https://neo4j.com/developer/cypher-query-language/}}, SPARQL, SQL and LogicQL.
+
+\paragraph{GraphGen}  GraphAware GraphGen\footnote{\url{http://graphgen.graphaware.com/}} is a graph generation engine based on Neo4j's\footnote{\url{https://neo4j.com/}} query language OpenCypher~\cite{GraphGen}.
+It creates nodes and relationships based on a schema definition expressed in Cypher, and it can also generate property values on both
+nodes and edges.
+As such, GraphGen is a precursor of property graphs generators.
+The resulting graph can be exported to several formats (namely GraphJson\footnote{\url{https://github.com/GraphAlchemist/GraphJSON/wiki/GraphJSON}} and CypherQueries) or loaded directly to a DBMS.
+However, it is very likely that it is not maintained anymore due to the lack of available recent commits.
+
+\paragraph{Strengths and Weaknesses of Graph Database Generators}
+The graph DBMS generators discussed in this section have in common the fact that they can generate semantically rich labeled graphs with properties (ranging from properties values in GraphGen to MAG structures in XGDBench).
+They are also capable of generating graph instances and query workloads in
+concrete syntaxes (among which OpenCypher in GraphGen and gMark) and one of them (XGDBench) can also handle update operations on both graph structure and content.
+However, more comprehensive graph DBMS generators that also produce data manipulation operations (such as updates for graph databases) are urgently needed.
+Additionally, none of these generators is enabled to work on corresponding query languages for property graphs, such as the newly emerging standard GQL~\cite{gql-2018} and G-Core~\cite{AnglesABBFGLPPS18}.
+Hence, a full-fledged graph DBMS generator for property graphs and property graph query workloads~\cite{BFVY18} is still missing and there exists an interesting opportunity to build such a generator in the near future.
+
+Another apparent inconvenience is represented by the fact that explicit correlations among graph elements cannot be encoded for instance in gMark or GraphGen, whereas they could be fruitful in order to reproduce the behavior of real-world graphs in which attribute values are correlated one with another.
+On the other hand, social network and Linked Data generators that support correlations (as highlighted in Section \ref{sec:generators_socialnetworks} and Section \ref{sec:generators_LinkedData}) typically exhibit a fixed schema and are not not necessarily multi-domain as are some of the graph DBMS generators discussed in this section (namely GraphGen and gMark).
+
+\subsection{Social Networks}
+\label{sec:generators_socialnetworks}
+
+On-line social networks, like Facebook, Twitter, or LinkedIn, have become a
+phenomenon used by billions of people every day and thus providing extremely
+useful information for various domains. However, an analysis of such type of
+graphs has to cope with two problems: (1) availability of the data and (2)
+privacy of the data. Hence, data generators which provide realistic synthetic
+social network graphs are in a great demand.
+
+In general, any analysis of social networks identifies their various specific
+features~\cite{Chakrabarti:2006:GML:1132952.1132954}. For example, a social
+networks graph often has a high  degree of
+transitivity of the graph (so-called \emph{clustering coefficient}). Or, its diameter, i.e., the longest shortest path
+amongst some fraction (e.g. 90\%) of all connected nodes, is usually low due to
+weak ties joining faraway cliques.
+
+Another key aspect of social networks is the community effect. A detailed
+study of structure of communities in 70 real-world networks is provided, e.g.,
+in~\cite{Leskovec:2008:SPC:1367497.1367591}.
+~\cite{Prat-Perez:2014:CSS:2621934.2621942} analyzed the structure of
+communities (clustering coefficient, triangle participation ratio,
+diameter, bridges, conductance, and size) in both real-world graphs and outputs of
+existing graph generators such as LFR~\cite{PhysRevE.78.046110} and the
+LDBC SNB~\cite{Erling:2015:LSN:2723372.2742786}. They found out that discovered
+communities  in different graphs have common distributions and that communities
+of a single graph have different characteristics and are challenging to be represented using a single
+model.
+
+The existing social network generators try to reproduce different aspects of the
+generated network. They can be categorized into statistical and agent-based.
+\emph{Statistical
+approaches}~\cite{PhysRevE.78.046110,Yao2011,Armstrong:2013:LDB:2463676.2465296,Pham2013,Sukthankar-SocialInfo2014,Erling:2015:LSN:2723372.2742786,Nettleton2016}
+focused on reproducing aspects of the network. In \emph{agent-based
+approaches}~\cite{Barrett:2009:GAL:1995456.1995598,Bernstein:2013:SAS:2499604.2499609}
+the networks are constructed by directly simulating the agents' social choices.
+
+%\paragraph{LFR} Lancichinetti, Fortnato and Radicchi (hence
+%LFR)~\cite{PhysRevE.78.046110} develop a class of benchmark graphs whose nodes
+%participate in internal community structures. The benchmark models directed and
+%weighted real-world networks (e.g., social networks) containing overlapping
+%communities of different sizes. The algorithm assumes that both the degree and
+%the community size distributions are power laws. Each node shares a fraction $(1
+%- \mu)$ of its links with the other nodes of its community and a fraction $\mu$
+%with the other nodes of the network, where $\mu$ is called \emph{mixing
+%parameter}. The sizes of the communities are taken from a power law distribution
+%such that the sum of all sizes equals the number of nodes of the graph. The
+%generation process starts with an empty graph and incrementally fills in the
+%adjacency matrix by obeying the described constraints.
+
+\paragraph{Realistic Social Network}
+~\cite{Barrett:2009:GAL:1995456.1995598} focused on the construction of
+realistic social networks. For this purpose the authors combine both
+private and public data sets with large-scale agent-based techniques. The process works as
+follows: In the first step it generates  synthetic data by combining public and
+commercial databases. In the second step, it determines a set of activity
+templates. A 24-hour activity sequence including geolocations is assigned to
+each synthetic individual. To demonstrate the approach, the authors create a
+synthetic US population consisting of people and households together with
+respective geolocations. For this purpose the authors combine simulation and
+data fusion techniques utilizing various real-world data sources such as U.S.
+Census data, responses to a time-use survey or an activity survey.
+%Demographic information for each person and location, a minute-by-minute
+%schedule of each person's activities, and the locations where these activities
+%take place is generated by a combination of simulation and data fusion
+%techniques.
+The result is captured by a dynamic network of social contacts. Similar methods for
+agent-based strategies have been reported
+in~\cite{Bernstein:2013:SAS:2499604.2499609}.
+
+\paragraph{Linkage vs. Activity Graphs}
+\cite{Yao2011} distinguished between two types of social network graphs -- the
+\emph{linkage graph}, where nodes correspond to people and edges correspond to their
+friendships, and the \emph{activity graph}, where nodes also represent people
+but edges correspond to their interactions. On the basis of the analysis of
+Flickr\footnote{\url{https://www.flickr.com/}} social links and
+Epinions\footnote{\url{http://www.epinions.com/}} network of user interactions,
+the authors discover that they both exhibit high clustering coefficient
+(community structure), power-law degree distribution and small diameter.
+Considering the dynamic properties they both have relatively stable clustering
+coefficient over time and follow the densification law. On the other hand,
+diameter shrinking is not observed in Epinions activity graph and there is a
+difference in degree correlation (i.e., frequency of mutual connections of
+similar nodes) -- activity graphs have neutral, whereas linkage graphs have positive degree correlation. With regards to the findings, the
+proposed generator focusses on linkage graphs with positive degree correlation.
+For this purpose it extends the forest fire spreading process
+algorithm~\cite{Leskovec:2005:GOT:1081870.1081893} with link symmetry. It has
+two parameters: the \emph{symmetry
+probability} $P_s$ and the \emph{burning probability} $P_b$. $P_b$ ensures a forward burning process based on BFS in which
+fire burns strongly with $P_b$ approaching 1.  $P_s$ ensures backward linking
+from old nodes to new nodes and ``adds fuel to the fire as it brings more
+links''. %It gives chances for big nodes to connect back to big nodes.
+
+\paragraph{LinkBench} The LinkBench
+benchmark~\cite{Armstrong:2013:LDB:2463676.2465296} has been designed for the
+purpose of analysis of efficiency of a database storing Facebook's production
+data. The benchmark considers true Big Data and related problems with sharding,
+replication etc. The social graph at Facebook comprises objects (nodes with IDs,
+version, timestamp and data) and associations (directed edges, pairs of node
+IDs, with visibility, timestamp and data). The size of the target graph is the
+number of nodes. Graph edges and nodes are generated concurrently during bulk
+loading. The space of node IDs is divided into chunks which enable parallel
+processing. The edges of the graph are generated in accordance with the results
+of analysing  real-world Facebook data (such as outdegree distribution). A
+workload corresponding to 10 graph operations (such as insert object, count the
+number of associations etc.) and their respective characteristics over the
+real-world data is generated for the synthetic data.
+
+\paragraph{S3G2} The Scalable Structure-correlated Social Graph Generator
+(S3G2)~\cite{Pham2013} is a general framework which produces a directed labeled
+graph whose vertices represent objects having property values. The respective
+classes determine the structure of the properties. S3G2 does not aim at
+generating near real-world data, but at generating synthetic graphs with a
+correlated structure. Hence, the existing data values influence the probability
+of choosing a particular property value from a pre-defined dictionary or connecting two nodes. For example, the degree distribution can be
+correlated with the properties of a node and thus, e.g., people who have many
+friend relationships typically post more comments and pictures. The data
+generation process starts with generating a number of nodes with property values
+generated according to specified property value correlations and then adding
+respective edges according to specified correlation dimensions. It has multiple
+phases, each focusing on one correlation dimension. Data is generated in a Map
+phase corresponding to a pass along one correlation dimension. Then the data are
+sorted along the correlation dimension in the following Reduce phase. A
+heuristic observation that ``the probability that two nodes are connected is
+typically skewed with respect to some similarity between the nodes'' enables to
+focus only on sliding window of most probable candidates. The core idea of the
+framework is demonstrated using an example of a social network (consisting of
+persons and social activities).  The dictionaries for property values are
+inspired by DBpedia and provided with 20 property value correlations. The edges
+are generated according to 3 correlation dimensions.
+
+\paragraph{SIB} The developers of the Social Network Intelligence BenchMark (SIB)\footnote{\url{https://www.w3.org/wiki/Social_Network_Intelligence_BenchMark}} based the design of their benchmark on the claim that the state-of-the-art benchmarks are limited in reflecting the characteristics of the real RDF databases and are mostly focusing on the relational style aspects.
+Hence, they proposed a benchmark for  query evaluation using real graphs~\cite{sib}.
+The proposed benchmark mimics using an RDF store for a social network.
+\iffalse site where users and their interactions form a social graph of social activities such as creating/managing groups, writing posts and posting comments.\fi The distribution of the generated data for each type follows the  distribution of the associated type inferred from real-world social networks.
+Additionally, association rules are exploited for representing the real-world data correlation in the generated synthetic data.
+The  generated data is linked with the RDF datasets from DBpedia.
+The benchmark specification contains 3 query mixes -- interactive, update, and analysis -- expressed in SPARQL 1.1 Working Draft.
+
+\paragraph{Cloning of Social Networks} ~\cite{Sukthankar-SocialInfo2014}
+introduces two synthetic generators to reproduce two characteristics typically
+observed in social networks: node features and multiple link types. Both
+generators extend  the generator proposed by~\cite{wang2011leveraging}.
+which starts with a small number of
+nodes and new nodes are added until the network reaches the required number. It
+has two basic parameters: homophily and link density. A high \emph{homophily}
+value reflects that links have higher chances to be established among the nodes belonging to the same community,
+whereas the community membership is represented by the same labels.
+
+The first proposed generator is Attribute Synthetic Generator (ASG), used for
+reproducing the node feature distribution of standard networks and rewiring the
+network to preferentially connect nodes that exhibit a high feature similarity.
+The network is initialized with a group of three nodes. New nodes and links
+are added to the network based on link density, homophily, and feature
+similarity. As new nodes are created, their labels are assigned based on the
+prior label distribution. After the network has reached the same number of nodes
+as the original social media dataset, each node initially receives a random
+attribute assignment. Then a stochastic optimization process is used to move the
+initial assignments closer to the target distribution extracted from social
+media dataset using the Particle Swarm Optimization algorithm. The tuned
+attributes are then used to add additional links to the network based on the
+feature similarity parameter -- a source node is selected randomly and connected
+to the most similar node. The second proposed generator, so-called Multi-Link Generator
+(MLG), further  uses link co-occurrence statistics from the original dataset to
+create a multiplex network. MLG uses the same network growth process as ASG.
+Based on the link density parameter, either a new node is generated with a label
+based on the label distribution of the target dataset or a new link is created
+between two existing nodes.
+
+\paragraph{LDBC SNB} Despite having a common Facebook-like dataset, thanks to
+three distinct workloads the Social Network Benchmark
+(SNB)~\cite{Erling:2015:LSN:2723372.2742786} provided by LDBC represents three
+distinct benchmarks. The network nodes correspond to people and the edges
+represent their friendship and messages they post in discussion trees on their
+forums. The three query workloads involve: (1) SNB-Interactive, i.e., complex
+read-only queries accessing a high portion of data, (2) SNB-BI, i.e.,
+queries accessing a high percentage of  entities and grouping them in various
+dimensions, and (3) SNB-Algorithms, involving graph analysis algorithms, such as
+community detection, PageRank, BFS, and clustering. The graph generator, called
+Datagen, is a fork of S3G2 ~\cite{Pham2013} and realizes power laws, uses skewed
+value distributions, and ensures reasonable correlations between graph
+structures and property values. Additionally, it extends S3G2 with "spiky"
+patterns in the distribution of social network activity along the timeline, also
+provides the ability of generating update streams to the social network. Datagen
+is also based on Hadoop in order to provide scalability, but comparet to S3G2 it
+contains numerous performance improvements and the ability to be deterministic
+regardless of the number of computer nodes used for the generation of the graphs
+and for a given set of configuration parameters.
+
+%The generated data have become a part if several graph benchmarks, such as GraphBIG~\cite{Nai:2015:GUG:2807591.2807626}.
+
+\paragraph{Towards More Realistic Data} \cite{Nettleton2016} argued that the majority of existing works focuses on
+topology generation which approximates the features of a real-world social
+network (e.g., community structures, skew degree
+distribution, a small average path length, or a small graph diameter); however,  this is usually done without any data. Hence, they
+introduced a general stochastic modeling approach that enables the users to
+fill a graph topology with data. The approach has three steps: (1) topology
+generation (using R-MAT) plus community identification using the Louvain
+method~\cite{1742-5468-2008-10-P10008} or usage of a real-world topology from
+SNAP\footnote{\url{https://snap.stanford.edu/data/}}, (2) data definition
+that describes  definitions of attribute values (distribution profiles) using a
+parameterizable set of affinities and data propagation rules, and (3) data
+population.
+
+\paragraph{Strengths and Weaknesses of Social Network Generators}
+Compared to more general graph generators, social network generators focus
+mainly on reproducing intra- and inter-node feature correlations.
+Among existing generators, LDBC SNB and S3G2 look
+like the most advanced ones in terms of the complexity of the generated graph
+and the amount of features and correlations they can generate, while providing a
+large degree of scalability. Their generation process is based on input dictionaries and have configuration files that
+allow tweaking  many parameters of the generated graphs, but their schema is mainly
+static and cannot be easily configured to meet the needs of other uses cases
+besides the benchmarks they have been designed for. In this regard, the approaches
+like those proposed in~\cite{Nettleton2016} and~\cite{Sukthankar-SocialInfo2014} offer a
+more flexible and understandable configuration process to tweak the types,
+values, and correlations between different features.
+
+Regarding the correlation between the underlying graph structure and the node
+features, approaches such as LDBC SNB, S3G2 or ~\cite{Nettleton2016}
+take into account this aspect and the generated graphs have realistic
+structural properties while similar nodes have a larger probability of being
+connected. However, their approach seems to be more based on
+intuition and common sense than to be backed up by  any study of how the
+relation between structure and attributes showcase in real social networks. In
+this regard, this remains as a clear open challenge for social network
+generators.
+
+Finally, scalability is another aspect to be considered in social network graph
+generators. LDBC SNB and S3G2 are engineered with this in mind, thus they
+provide a way to scale to billions of nodes and edges. This is not the case for
+the other generators, which can make them impractical if our goal is to generate
+real sized social network graphs.
 
@@
 
-\input{generators_others}
+\subsection{Testing Community Detection}
+\label{sec:generators_community_detection}
+
+Community detection is one of the many graph analytics algorithms typically used
+in domains such as social networks or bioinformatics. \emph{Communities} are usually defined as sets of nodes that are highly mutually connected, while being scarcely connected to
+the other nodes of the graph. Such communities emerge from the fact that real-world graphs
+are not random, but follow real-world dynamics that make similar entities to
+have a larger probability to be connected. As a consequence, detected
+communities are used to reveal vertices with similar characteristics, for
+instance to discover functionally equivalent proteins in protein-to-protein
+interaction networks, or persons with similar interests in social networks. Such
+applications have made community detection a hot topic during the last 15
+years with tens of developed algorithms and detection
+strategies~\cite{doi:10.1002/wics.1403,Kim:2015:CDM:2854006.2854013}. For
+comparing the quality of the different proposed techniques, one needs graphs
+with \emph{reference communities}, that is, communities known beforehand. Since
+it is very difficult to have large real-world graphs with reference communities
+(mainly because these would require a manual labeling), graphs for benchmarking
+community detection algorithms are typically generated synthetically.
+
+\paragraph{Danon et al.} The first attempts to compare community detection algorithms using synthetic
+graphs proposed the use of random graphs composed by several Erd\"{o}s-R\'{e}nyi
+subgraphs, connected more internally than externally~\cite{danon2005comparing}.
+Each of these subgraphs has the same size and the same internal/external density
+of edges. However, such graphs miss the realism observed in real-world graphs, where
+communities are of different sizes and densities, thus several proposals exist
+to overcome such an issue.
+
+\paragraph{LFR} Lancichinetti, Fortunato
+and Radicchi (hence LFR)~\cite{PhysRevE.78.046110} propose a class of benchmark
+graphs for community detection where communities are of diverse sizes and
+densities. The generated communities follow a power-law distribution whose parameters can be configured. The degree of the
+nodes is also sampled from a power-law distribution. Additionally, the generator
+introduces the concept of the ``mixing factor'', which consists of the percentage of
+edges in the graph connecting nodes that belong to distinct communities. Such parameter
+allows  the degree of modularity of the generated graph  to be tuned, thus
+testing the robustness of the algorithms under different conditions. The
+generation process is implemented as an optimization process starting with an empty graph and
+progressively filling it with nodes and edges guided by the specified constraints.
+
+\paragraph{LFR-Overlapping} Lancichinetti, Fortunato and
+Radicchi~\cite{PhysRevE.80.016118} extended LFR to support the notion of
+directed graphs and overlapping communities. Overlapping communities extend the
+notion of communities by allowing the sharing of vertices, thus a vertex can
+belong to more than one community. This extended generator allows controlling
+the same parameters of LFR, as well as the amount of overlap of
+the generated communities.
+
+\paragraph{Stochastic Block Models} Another popular family of generators
+widely used in the community detection field are the stochastic block
+models~\cite{holland1983stochastic}. In such models, the community structure of
+the graph is typically defined as an array of $n$ community or cluster sizes
+and a density square matrix of size $n \times n$ containing the density of
+intra-cluster edges (in the diagonal of the matrix) and the density of
+inter-cluster edges. Then, a stochastic procedure is run to sample graphs
+from such array and matrix, using the sizes to compute the possible edges
+and the densities as probabilities of such edges to exist. The popularity of
+these methods stem from its simplicity and scalability, which makes them
+suitable for generating large graphs fast and in a distributed environments,
+provided that the density matrix is sparse (as it happens in most of real-world
+                                            world graphs). Moreover, given
+that the generation process of such models is mathematically tractable, they
+are typically used to analyze the limitations of algorithms for community detection
+ such as those based on modularity
+optimization~\cite{fortunato2007resolution} or based on
+triads~\cite{prat2016put}. Extensions of such models exist, such as the
+Mixed Membership Stochastic Block Model~\cite{airoldi2008mixed}, for
+overlapping communities.
+
+\paragraph{Strengths and Weaknesses of Community Detection Generators}
+Besides synthetic graph generators, Yang and Leskovec~\cite{yang2015defining}
+proposed the use of real-world graphs with explicit group annotations (e.g.,
+forums in a social network, categories of products, etc.) to infer what they
+call \emph{meta-communities}, and use them to evaluate overlapping community
+detection algorithms. However, a recent study from Hric, Darst and
+Fortunato~\cite{hric2014community} reveal a loose correspondence between
+communities (the authors refer to them as \emph{structural communities}) and
+meta-communities.  This result reveals that  algorithms working for structural
+communities do not work well for finding meta-communities and vice versa,
+suggesting significantly different underlying characteristics
+between the two types of communities, which are yet to be
+identified.
+
+In this regard and to the best of our knowledge, there are no available
+generators that can generate graphs with meta-communities for community detection
+algorithm benchmarking. The closest one is the LDBC SNB data
+generator which has been provided by the
+generation of groups of users in the social network. Even though the generation
+process does not specifically enforce the generation of groups
+(meta-communities) for benchmarking community detection algorithms, the study~\cite{Prat-Perez:2014:CSS:2621934.2621942} reveals that these groups are more similar
+to the real meta-communities than those structural communities generated by the
+LFR benchmark.
+
+The differences observed between structural and meta-communities reveal the need
+of more accurate community definitions tight more specifically to the domain or
+use case. Current community detection algorithms and graph generators for
+community detection are stuck to the traditional (and vague) definition of
+community, assuming that there exists a single algorithm that would fit all the
+use cases. Thus, future work requires the study of domain-specific community
+characteristics that can be used to generate graphs with a community structure
+that accurately resembles that of specific use cases, and thus revealing which
+are the best algorithms for each particular scenario.
 

### 2019-12-18 introduction.tex
Typos fixed by Sherif

@@
 In general, we can distinguish between two broad types of graph data sets: (1) a single large graph (possibly with several components), such as social networks  or Linked Data graphs, and (2) a large set of small graphs (e.g., chemical compounds\footnote{\url{https://pubchem.ncbi.nlm.nih.gov/}} or linguistics syntax trees\footnote{\url{https://catalog.ldc.upenn.edu/ldc99t42}}).
-Naturally, the algorithms used in theses two classes differ a lot~\cite{DBLP:books/igi/Sakr2011}.
+Naturally, the algorithms used in these two classes differ a lot~\cite{DBLP:books/igi/Sakr2011}.
 In the former case we can search, e.g., for communities and their features or shortest paths, while in the latter case we usually query for supergraphs, subgraphs, or graphs similar to a given graph pattern.
-In both the cases, as in the other fields, quite often the respective real-world graph data is not publicly available (or simply does not exist when a particular method for data manipulation is proposed).
+In both cases, as in the other fields, quite often the respective real-world graph data is not publicly available (or simply does not exist when a particular method for data manipulation is proposed).
 Even in the cases in which real data is abundant, many algorithms and techniques need to be tested on various orders of magnitudes of the graph sizes thus leading to the inception of

### 2019-12-18 main.tex
Irena's pass (plagiarism) pp 1-10
Typos fixed by Sherif

@@
 \acmformat{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr, 2019.
-Modern Graph Generators: A Survey.}
+Graph Generators: State of the Art and Open Challenges.}
 % At a minimum you need to supply the author names, year and a title.
@@
 
-\input{introduction}
+\section{Introduction}
+\label{sec:intro}
+
+%In recent years the term Big Data has become a phenomenon that breaks down borders of many technologies and approaches that have so far been acknowledged as mature and robust for any conceivable application.
+Gartner Inc.\footnote{\url{http://www.gartner.com/}} describes Big Data as ``\emph{high \textbf{v}olume, high \textbf{v}elocity, and/or high \textbf{v}ariety information assets that require new forms of processing to enable enhanced decision making, insight discovery and process optimization}''.
+
+%\TODO{The abundance of interconnected data has fueled the design and implementation of graph generators reproducing real-world linking properties, or gauging the effectiveness of graph algorithms, techniques and applications manipulating these data.}
+
+%One of the most popular data structures in the world of computer science are graphs.
+Graphs are ubiquitous data structures that span a wide array of scientific disciplines
+and are a subject of study in several subfields of computer science.
+Nowadays, due to the dawn of numerous tools and applications manipulating
+graphs, they are adopted as a rich data model in many data-intensive use
+cases involving disparate domain knowledge, mathematical foundations and
+computer science. Interconnected data is oftentimes used to encode domain-specific
+use cases, such as recommendation networks, social networks,
+protein-to-protein interactions, geolocation networks, and fraud detection analysis networks, to
+name a few.
+% ANGELA: I do not think we should cite Neo4J, which is a graph database.
+%They enable to represent complex information in a simple and yet powerful way supported by a strong mathematical background.
+With the dawn of the new millennium which brought numerous novel technologies and applications, the graphs have become even more popular.
+There has appeared a number of use cases\footnote{\url{https://neo4j.com/use-cases/}} (such as fraud detection, recommendation engines, social networks etc.) where graphs represent the linked information.
+
+In general, we can distinguish between two broad types of graph data sets: (1) a single large graph (possibly with several components), such as social networks  or Linked Data graphs, and (2) a large set of small graphs (e.g., chemical compounds\footnote{\url{https://pubchem.ncbi.nlm.nih.gov/}} or linguistics syntax trees\footnote{\url{https://catalog.ldc.upenn.edu/ldc99t42}}).
+Naturally, the algorithms used in these two classes differ a lot~\cite{DBLP:books/igi/Sakr2011}.
+In the former case we can search, e.g., for communities and their features or shortest paths, while in the latter case we usually query for supergraphs, subgraphs, or graphs similar to a given graph pattern.
+In both cases, as in the other fields, quite often the respective real-world graph data is not publicly available (or simply does not exist when a particular method for data manipulation is proposed).
+Even in the cases in which real data is abundant, many algorithms and techniques need to be tested on various orders of magnitudes of the graph sizes thus leading to the inception of
+configurable graph generators that reproduce real-world graph properties and provide unique tuning opportunities for
+algorithms and tools handling such data.
+%As a consequence, also in the world of graphs there has appeared a number of graph data generators which enable to  reproduce the respective real-world linking properties and gauge the effectiveness of a particular algorithm.
+
+In this survey, we provide a detailed overview of the state-of-the-art
+modern
+graph generators by focusing on those that are pertinent and suitable for
+data-intensive tasks. Our aim is to cover a wide range of currently popular
+areas of graph data processing. In particular, we consider graph generation
+in the areas of Semantic Web, graph databases, social networks, and community detection, along with general graphs.
+Despite the disparate requirements of modern graph generators throughout these communities, we analyze them under a common umbrella, reaching out the functionalities, the practical usage, and the supported operations of graph generators.
+The reasons for this scope and classification are as follows:
+
+\begin{enumerate}
+  \item Despite the differences of the covered areas, the requirements for
+modern graph data generators can be similar in particular cases. Reusing or learning from tools in other fields can thus bring new opportunities for both researchers and practitioners.
+  \item The selected classification is serving the need of providing scientists, researchers, and practitioners with the right data generator at hand for their work.
+\end{enumerate}
+
+To conclude the comparative study and provide a comprehensive view of the
+field,  we also overview the most popular real-world data sets used in the respective covered areas and discuss open challenges and missing requirements of modern
+graph generators in view of identifying their future extensions to new emerging fields.
+
+\paragraph*{Contributions} Our survey revisits the representatives of
+modern graph data generators and summarizes their main characteristics. The detailed review
+and analysis make this paper useful for stimulating new graph data generation mechanisms as well as
+serving as a main technical reference for selecting suitable solutions. In particular, the introductory
+categorization and comparative study enables the reader to quickly get his/her bearings in the field and
+identify a subset of generators of his/her interest.
+Since we do not limit the survey to a particular area of graph data management,  the reader can get a broader scope in the field.
+Hence, while practitioners can find a solution in another previously unexpected area, researchers can identify new target areas or exploit successful results in new fields.
+Last but not least, %to provide a global view of the state-of-the-art, we also provide an overview of most commonly used real-world testing graph datasets.
+And, finally,
+we identify general open problems of graph data synthesis and indicate possible solutions to show that it still forms a challenging and promising research area.
+
+\paragraph*{Differences with prior surveys}
+
+To the best of our knowledge, this paper is the first to survey the broad
+landscape of graph data generators spanning different data-intensive applications and
+targeting many computer science subfields.
+In particular, we cover Semantic Web, graph databases, social networks, and community detection, along with general graphs.
+However, the literature is still lacking a comprehensive study of graph generators  for many of the specific subfields mentioned above.
+
+A limited subset of graph database
+generators, parallel and distributed graph processing generators, along
+with a few of the Semantic Web data generators presented in our survey have
+been discussed in a related book chapter
+\cite{BFHI18} while cross-comparing them with respect to input, output,
+supported workload, data model and query language, along with the
+distinguished chokepoints. However, the provided classification is
+inherently database-oriented.
+In our work, we provide a more comprehensive and broader classification
+ that serves the purpose of letting any
+researcher or practitioner interested in data generation  to be able to make a better
+choice of the desired graph
+generator based on its functional and goal-driven features (such as the application domain,
+the supported operations, and the key configuration options).
+Moreover, in contrast with \cite{BFHI18}, our work encompasses graph generators of several
+diverse communities, not limiting its scope to a few generators of the database
+and graph processing communities.
+
+Graph generators matching graph patterns used in data mining have been
+studied in \cite{Chakrabarti:2006:GML:1132952.1132954},
+focusing on mostly occurring patterns, such as power laws, size of graph diameters,
+and community structure. The considered graph generators are compared in
+terms of graph type, degree distributions, exponentiality, diameter, and
+community effects. We refer the reader to this survey for taxonomies
+involving these properties, whereas we provide here a functionality-driven
+taxonomy across all the categories of graph generators that we consider.
+We also point out that this survey is outdated as it does not consider the
+generators that appeared in the last decade.
+We fill the gap of more recent social network generators
+in Section~\ref{sec:generators_socialnetworks}, as well as more recent representatives of the other categories.
+
+%\TODO{Check with Arnau}
+
+Aggarwal and Subbian~\cite{AggarwalS14} have surveyed the evolution of analysis in
+graphs, by primarily focusing on data mining maintenance methods and on analytical
+quantification and explanation of the changes of the underlying networks.
+A brief discussion on evolutionary
+network data generators is carried out in
+the paper. The data generation of evolutionary networks is based on the
+shrinking diameters and Densification Power Law (DPL), i.e., community-guided
+attachment properties~\cite{Leskovec:2005:GOT:1081870.1081893}.
+Generation of graphs tackling Kronecker
+recursion with recursive tensor multiplication~\cite{AkogluMF08} is then considered in the above survey.
+We refer the readers to the aforementioned survey for evolutionary network generators and further
+discuss the open challenges of evolving graph data in Section~\ref{sec:challenges}.
+%\TODO{Better highlight the differences when Sherif's part is in.}
+
+%\TODO{Outreach other surveys in other communities.}
+
+\paragraph*{Outline} The rest of the text is structured as follows: Section~\ref{sec:comparison}
+provides the opening categorization and comparison of the generators. Section~\ref{sec:generators}
+provides an overview of the existing graph data generators and their main features in the frame of
+the proposed categories.
+%To provide a complete overview,  we list the most commonly used testing data sets for the particular categories in Section~\ref{sec:data_sets}.
+In Section~\ref{sec:challenges}, we highlight some of the challenges and open problems of graph
+data synthesis before we conclude in Section~\ref{sec:conclusion}.
+
 %\input{preliminaries}
-\input{comparison}
+\section{Classification and Comparative Study}
+\label{sec:comparison}
+
+In order to provide a general preview of the generators and  to enable finding the target solutions easily, we start the survey with a  classification and comparative study of the existing tools.
+In general, there are various ways to classify them.
+We first offer an overview of the approaches used in state-of-the-art work after which we then introduce our approach.
+As mentioned in the Introduction, since this survey is unique especially in terms of scope, our classification and comparative strategy differs as well.
+
+The graph data generators can be classified using various distinct criteria.
+For example,~\cite{DBLP:conf/sdm/ChakrabartiZF04} introduces two categories -- degree-based and procedural generators.
+In general, \emph{degree-based generators} (e.g., Barabasi-Albert model~\cite{Barabasi99emergenceScaling}) are commonly attempting to find a graph that matches it, but without providing any information about the graph or attempting to match other graph features (e.g., eigenvalues, small diameter, etc).
+On the other hand, \emph{procedural generators} (e.g., R-MAT~\cite{DBLP:conf/sdm/ChakrabartiZF04}) are commonly targeting simple techniques to produce graphs that are matching the characteristics of the real-world graphs (such as, e.g., the power law degree distribution).
+
+Paper~\cite{Chakrabarti:2006:GML:1132952.1132954} introduces five categories of graph models that can be synthesized: (1) \emph{random graph models} (e.g., Erd\"{o}s-R\'{e}nyi~\cite{Erdos:1960}) generated by a random process, (2) \emph{preferential attachment models} (e.g., Barabasi-Albert model) which try to model the power law from the preferential attachment viewpoint, (3) \emph{optimization-based models} (e.g., HOT model~\cite{PhysRevLett.84.2529}) resulting from the idea that power laws can result from tolerance to risks and resource optimizations, (4) \emph{tensor-based models} (e.g., R-MAT) targeting a trade-off between low number of model parameters and efficiency, and (5) \emph{internet-specific models} corresponding to hybrids using ideas from the other categories in order to suit the specific features of the graphs.
+
+The type of the generator can also be influenced by the benchmark involving it, whereas we can distinguish, e.g., \emph{domain-specific} benchmarks, \emph{application-specific} benchmarks, \emph{workload-driven} benchmarks,  \emph{microbenchmarks} etc.
+
+%\paragraph{Erd\"{o}s-R\'{e}nyi} One of the first and still very popular approaches with lots of variations and modifications is the random graph model proposed in~\cite{Erdos:1960}.
+Given a positive integer $n$ and a probability value $0 \leq p \leq 1$, the graph $G(n,p)$ is an undirected graph on $n$ vertices whose edges are chosen s.t.
+for all pairs of vertices $u,v$ there is an edge $(u,v)$ with probability $p$.
+%
+%\paragraph{Barabasi-Albert} The Barabasi-Albert (BA) model~\cite{Barabasi99emergenceScaling} proposes that structure emerges in network topologies as the result of two processes -- growth and preferential attachment.
+The BA model starts with a small set of nodes and grows the network as nodes and edges are added over time.
+Preferential attachment is based on the idea that the probability of connecting to a node is proportional to the current degree of that node (i.e., ``the rich get richer'').
+%
+%\paragraph{HOT} The highly optimized tolerance (HOT)~\cite{PhysRevLett.84.2529} model is introduced  using a ``forest fire'' example as follows: Suppose we have a forest which is prone to forest fires.
+Each portion of the forest has a different chance of starting the fire.
+We wish to minimize the damage by assigning (a limited amount of) resources such as firebreaks at different positions in the forest.
+More precisely, we have $n$ possible events, each with an associated probability $p_i, 1 \le i \le n$.
+Each event can lead to some loss $l_i$, which is a function of the resources $r_i$ allocated for that event $(l_i = f (r_i))$, whose total number is limited ($\sum_i r_i \le R$ for some given $R$).
+The aim is to minimize the expected cost $\sum_i p_i l_i$.
+The authors show that resource placement is related to the probability distribution $p_i$ by a power law and the probability of events which cause a loss greater than some value $k$ is related to $k$ by a power law too.
+%
+%
+%\paragraph{R-MAT} The R-MAT (Recursive MATrix)~\cite{DBLP:conf/sdm/ChakrabartiZF04} model can be used to create graphs with community structure, power law degree distributions, and a small diameter.
+It generates weighted, directed and bipartite graphs.
+Graph generation is modeled with a matrix recursion -procedure in which the adjacency matrix (empty at the beginning) is recursively subdivided into four equal-sized partitions and edges are distributed across the partitions with unequal probabilities.
+
+%In Figure~\ref{fig:classification} ...
+%
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.8\textwidth]{classification.png}
+%\caption{Classification of graph data generators}
+%\label{fig:classification}
+%\end{figure}
+
+\subsection{Classification}
+
+At first we classify the generators on the basis of the respective application domains or user communities.
+In particular we distinguish (1) general graphs, (2) Semantic Web, (3) graph databases, (4) social networks, and (5) community detection.
+The selected classes are not rigorously defined (e.g., they are not disjoint as we will show later), but they correspond to the currently most active research areas.
+Thus we believe that they form a natural first acquaintance for the reader.
+
+In Table~\ref{tab:comparisonCharacteristics}   we overview the key characteristics of the data generators clustered according to the respective application domains.\footnote{``GDBs'' stands for graph databases, ``SNs'' stands for social networks, and ``Co'' stands for community detection.
+Value ``$-$'' means that the information is not available or relevant.} In particular, we show:
+
+\begin{itemize}
+\item Characteristics of the \textbf{domain}:
+    \begin{itemize}
+      \item its \textit{type} (column ``Type''), i.e.,  fixed, specified using a schema, or extracted from input data, and
+      \item the particular \textit{target} domain, or, in case of a generic tool, the chosen sample domain (column ``Target/sample'').
+\end{itemize}
+\item Characteristics of \textit{read}/\textit{update} \textbf{operations} (columns ``Read'' and ``Update''), i.e., whether the set of operations is fixed/generated, if it involves operation mixes (i.e., sets/sequences of operations), or if templates of operations are supported.
+\item Key \textbf{configuration} options:
+  \begin{itemize}
+    \item whether the generator deals only with structure, or also with \emph{properties} (column ``Pro.'') of the graph (Y/N feature),
+    \item supported types of \emph{distributions} (column ``Distributions'') used for generating of the data,
+    \item \textit{output format} (column ``Output'') of the produced graph, and
+    \item  whether the generator is \textit{distributed} (column ``Dis.'') and thus enables more efficient data generation (Y/N feature).
+  \end{itemize}
+\end{itemize}
+
+\begin{sidewaystable}
+\scriptsize
+\centering
+\tbl{Key characteristics of the generators} {
+\begin{tabular}{| c | l | p{2cm} |  p{2cm} | p{1.3cm} |  l | l | p{3.2cm} | p{2cm} | l | }
+ \hline
+           &   & \multicolumn{2}{c}{\textbf{Domain}}
+               & \multicolumn{2}{|c|}{\textbf{Operations}}
+               & \multicolumn{4}{c|}{\textbf{Configuration}}
+               \\ \hline
+           &  \textbf{Generator}
+               & \textbf{Type}
+               & \textbf{Target/sample}
+               & \textbf{Read}
+               & \textbf{Update}
+               & \textbf{Pro.}
+               & \textbf{Distributions}
+			   & \textbf{Output}
+               & \textbf{Dis.}
+               \\ \hline
+\hline   % ====================== general graphs
+\multirow{7}{*}{\rot{\textbf{General}}}
+  & Preferential attachment & -- & -- & N & N & Y & power-law & edge-list &  N  \\
+\cline{2-10}
+   & R-MAT & -- & -- & N & N & Y & power-law & edge-list &  N  \\
+\cline{2-10}
+  & HPC Scal. Graph Anal. & fixed & -- & fixed & N& N& uniform &edge-list & N   \\
+\cline{2-10}
+  & GraphGen & -- & -- & N & N & Y& user-defined  & node/edge-list & N   \\
+\cline{2-10}
+%  & Graph 500  & -- & -- & Y & N & Y & power-law & edge-list &  Y  \\
+%\cline{2-10}
+  & BTER & -- & -- &   N & N & N & user-defined & edge-list & Y  \\
+\cline{2-10}
+  & Darwini & -- & -- &   N & N & N & user-defined &  edge-list & Y   \\
+\cline{2-10}
+  & RTG & -- & -- &   N & N & N & power-law &  edge-list & N  \\
+%  & Watts-Strogatz~\cite{watts1998collective} & fixed & & Y & N & Y &  & &  N  \\
+%\cline{2-10}
+\hline
+\hline %  ======================  Semantic web
+\multirow{19}{*}{\rot{\textbf{Semantic Web}}}
+ & LUBM & fixed & university  & fixed & N & Y & random (LCG) &  RDF & N   \\
+\cline{2-10}
+ & LBBM & extracted & Lehigh university BibTeX  & N & N & Y & Monte Carlo &  RDF & N   \\
+\cline{2-10}
+ & UOBM & fixed & university  & fixed & N & Y & random &  RDF & N   \\
+\cline{2-10}
+ & IIMB & fixed & movies  & N & N & Y & random &  RDF & N   \\
+\cline{2-10}
+ & BSBM & fixed & e-commerce  & fixed & N & Y & mostly normal &  RDF, relational & N   \\
+\cline{2-10}
+ & SP$^2$Bench & fixed & DBLP  & fixed & N & Y & based on DBLP  & RDF & N   \\
+\cline{2-10}
+ & \cite{Duan:2011:AOC:1989323.1989340} & extracted & -- & N & N & Y & -- &  RDF & N    \\
+\cline{2-10}
+ & DBPSB & extracted & DBpedia &  templates & N & Y & random &  RDF & N   \\
+\cline{2-10}
+ & LODIB & fixed & e-commerce &  N & N & Y & 44 types &  RDF & N   \\
+\cline{2-10}
+ & Geographica & fixed & OpenStreetMap  & fixed + templates  & N & Y & -- &  RDF & N   \\
+\cline{2-10}
+ & WatDiv & schema-driven & user-defined  & templates & N & Y & uniform, normal, Zipfian &  RDF & N   \\
+\cline{2-10}
+ & RBench & extracted & DBLP, Yago  & templates & N & Y & from real-world data &  RDF & N  \\
+\cline{2-10}
+ & S2Gen & schema-driven & social network & Y & N & N & user-defined & RDF & N     \\
+\cline{2-10}
+ & RSPLab & schema-driven & agnostic & Y & Y & N & user-defined & RDF & N     \\
+\cline{2-10}
+ & LDBC SPB & fixed & media  & mixes & N & Y & power-law, skewed values, value correlation &  RDF & N  \\
+\cline{2-10}
+ & LinkGen & schema-driven & user-defined & templates & N  & N & Gaussian, Zipfian & RDF & N\\
+\hline
+\hline  % ======================  graph databases
+\multirow{4}{*}{\rot{\textbf{GDBs}}}
+  & XGDBench & fixed  & social network  & generated & generated & Y & power-law &  MAG &  Y  \\
+\cline{2-10}
+  & gMark & schema-driven &  user-defined  & generated &  N  & Y & uniform, normal, Zipfian &  N-triples & N    \\
+\cline{2-10}
+  & graphGen & pattern-driven & user-defined  & -- & -- & Y & -- &  GraphJson, CypherQueries & N   \\
+\hline
+\hline %  ======================   social networks
+\multirow{8}{*}{\rot{\textbf{SNs}}}
+ & \cite{Barrett:2009:GAL:1995456.1995598} & fixed & social network & N & N & Y & simulation-driven & impl. NA &  -- \\
+\cline{2-10}
+ & \cite{Yao2011} & fixed & social network & N & N & N & power-law & impl. NA & --  \\
+\cline{2-10}
+ & LinkBench & fixed & social network & generated & generated & Y & Facebook & impl. NA & -- \\
+\cline{2-10}
+ & S3G2 & fixed & social network  & N & N  & Y & Facebook  & CSV, RDF & Y   \\
+\cline{2-10}
+ & SIB & fixed & social network &  mixes & mix & Y & from real-world data &  RDF & N   \\
+\cline{2-10}
+ & \cite{Sukthankar-SocialInfo2014} & schema-driven & social-network & N & N & Y & power-law & CSV & N   \\
+\cline{2-10}
+ & LDBC SNB  & fixed & social network &  generated & generated  & Y & Facebook &  CSV, RDF & Y     \\
+\cline{2-10}
+  & \cite{Nettleton2016} & schema-driven & social network & N & N & Y & power-law & impl. NA & --  \\
+%\cline{2-10}
+% & SNG  & Y & Y &   N &  & Y & power-law & ? &  ?   \\
+%\cline{2-10}
+% & Forest Fire  & N & Y   & N &  & N & power-law &  ? & N   \\
+%\hline
+%\hline   % ======================   graph analytics
+%\multirow{1}{*}{\rot{\textbf{A}}}
+%  & HPC Scal. Graph Anal. & fixed & -- & fixed & N& N& uniform &edge-list & N   \\
+%\cline{2-10}
+%  & Graphalytics & extracted & social network & fixed& N& N & power-law & CSV, RDF & N   \\
+\hline
+\hline   %  ======================  community detection
+\multirow{4}{*}{\rot{\textbf{Co}}}
+  & \cite{danon2005comparing} & -- & -- & Y & N & N & uniform & edge-list &  N    \\
+\cline{2-10}
+  & LFR & -- & -- & Y & N & N & power-law & edge-list  & N      \\
+\cline{2-10}
+  & LFR-Overlapping & -- & -- & Y & N & N & power-law & edge-list & N     \\
+\cline{2-10}
+  & Stochastic Block Models & -- & -- & Y & N & N & user-defined & edge-list & Y     \\
+\hline
+%\hline   %  ======================  streaming
+%\multirow{2}{*}{\rot{\textbf{St}}}
+%  & S2Gen & schema-driven & social network & Y & N & N & user-defined & RDF & N     \\
+%\cline{2-10}
+%  & RSPLab & schema-driven & agnostic & Y & Y & N & user-defined & RDF & N     \\
+%\cline{2-10}
+%  & & & & & & & &  &   \\
+\end{tabular} }
+\label{tab:comparisonCharacteristics}
+\end{sidewaystable}
+
+\paragraph{Number of Generators, Size and Output Format of the Data}
+As we can see, the biggest set of available generators can be found in the Semantic Web application domain, probably due to its recent popularity and a number of research groups dealing with this topic.
+None of these generators is natively implemented in a distributed manner and thus primarily generating  output at the Big Data scale.
+On the other hand, the \emph{Linked Open Data} (LOD) is expected to be large in general; however, this is the case of the whole \emph{LOD Cloud}\footnote{\url{https://lod-cloud.net/}}, but not necessarily of the particular data sets forming it.
+
+The second large group of generators also corresponds to a popular application domain -- social networks.
+In this case the size of the output graph is important if we require realistic features of the result.
+However, surprisingly many of the proposals do not provide an implementation at all and amongst the others there is a high percentage of those that are not highly scalable.
+
+In case of the other application-specific domains the amount of generators is relatively small.
+As we will show in Section~\ref{sec:overlapping}, the situation is not so critical.
+Some of the application-specific generators can be re-used also in other application domains or the general graph generators can be used.
+
+Considering the output format of the data, as expected, the generators produce data in a standard format (e.g., RDF) or in a reasonable graph-related form (e.g., edge list).
+
+\paragraph{Domain}
+
+If we consider the features of the particular domain of the generators, in most cases it is expectably \emph{fixed}, i.e., it is pre-defined (describing, e.g., a social network) and cannot be modified.
+It is the simplest option, but it does mean that the generator is simple too -- it can still focus on other complex aspects of the output.
+While the \emph{schema-driven} approaches enable to influence the target domain using a user-supplied schema, there also exist approaches where the domain is \emph{extracted} from sample data.
+The particular target (in case of fixed) or sample (in case of schema-driven or extracted) domains do not provide very rich areas.
+They either correspond to the respective application domains (like in the case of social networks), or they are based on well-known and commonly used data sets (such as, e.g., DBLP~\cite{dblp} or DBpedia~\cite{Bizer:2009:DCP:1640541.1640848}).
+Except for general graphs without any domain, in all other cases we can find a flexible representative with schema-driven/pattern-driven domain or a domain extracted from sample data.
+
+\paragraph{Operations}
+In the case of operations, most commonly the respective generators are accompanied with a set of fixed read operations or sequences of operations (query mixes) representing typical behavior of a user.
+In some cases this aspect is more flexible -- either query templates are used or the operations are generated, e.g., in order to access most of the data in the generated graph.
+On the other hand, update operations are provided only in a small amount of cases.
+As we will discuss in Section~\ref{sec:evolving}, the more general problem of evolving graphs is still an open issue.
+
+\paragraph{Configuration}
+A natural feature of the generators is to provide as realistic graphs as possible.
+Hence, most of them focus not only on the structure of the output graph, but also the properties.
+For the purpose of generating graphs with near real-world characteristics various distributions are used, such as power-law, Zipfian etc.
+Especially interesting are distributions extracted from real-wold data (such as, e.g., Facebook in case of the social network domain).
+
+\subsection{Overlapping}
+\label{sec:overlapping}
+
+As we have mentioned, the basic classification of the generators that we have used in this paper is relatively vaguely based on the current application domains or research areas.
+In addition, some of the generators are either general, and thus can be used universally, or have features applicable in more than one domain/research area.
+So the classes we use can overlap, as depicted in Table~\ref{tab:overlapping}.
+
+\begin{table}
+\scriptsize
+\centering
+\tbl{Overlapping of classes of generators} {
+\begin{tabular}{| c | l | l | l | l | l | l | l | }
+ \hline
+           &  \textbf{Generator}
+               & \textbf{\rot{General}}
+               & \textbf{\rot{Semantic Web}}
+               & \textbf{\rot{Graph databases\ }}
+               & \textbf{\rot{Social networks}}
+               %& \textbf{\rot{Analytics}}
+               & \textbf{\rot{Community detection\ }}
+               %& \textbf{\rot{Streaming}}
+               \\ \hline
+\hline   % ====================== general graphs
+\multirow{6}{*}{\rot{\textbf{General}}}
+  & Preferential attachment & {\bf x} & & &  &  \\
+\cline{2-7}
+   & R-MAT    & {\bf x} & & &  &  \\
+\cline{2-7}
+   & HPC Scal. Graph Anal.  & {\bf x} & & &  &  \\
+\cline{2-7}
+  & GraphGen  & {\bf x} & & x &  & \\
+\cline{2-7}
+%  & Graph 500 & {\bf x} & & &  & \\
+%\cline{2-7}
+  & BTER      & {\bf x} & & &  & \\
+\cline{2-7}
+  & Darwini   & {\bf x} & & &  & \\
+\cline{2-7}
+  & RTG   & {\bf x} & & &  & x \\
+\hline
+\hline %  ======================  Semantic web
+\multirow{16}{*}{\rot{\textbf{Semantic web}}}
+ & LUBM  & & {\bf x} & &  &  \\
+\cline{2-7}
+ & LBBM  & & {\bf x} & &  &  \\
+\cline{2-7}
+ & UOBM  & & {\bf x} & &  &  \\
+\cline{2-7}
+ & IIMB & & {\bf x} & &  & \\
+\cline{2-7}
+ & BSBM & & {\bf x} & &  &  \\
+\cline{2-7}
+ & SP$^2$Bench & & {\bf x} & &  &  \\
+\cline{2-7}
+ & \cite{Duan:2011:AOC:1989323.1989340} & & {\bf x} & &  &  \\
+\cline{2-7}
+ & DBPSB & & {\bf x} & &  &  \\
+\cline{2-7}
+ & LODIB & & {\bf x} & &  &  \\
+\cline{2-7}
+% & SIB & & {\bf x} & &  &  \\
+%\cline{2-7}
+ & Geographica & & {\bf x} & &  &  \\
+\cline{2-7}
+ & WatDiv & & {\bf x} & &  &  \\
+\cline{2-7}
+ & RBench & & {\bf x} & &  &  \\
+\cline{2-7}
+  & S2Gen & & {\bf x} & &  &  \\
+\cline{2-7}
+  & RSPLab & & {\bf x} & &  &  \\
+\cline{2-7}
+ & LDBC SPB & & {\bf x} & &  &  \\
+\cline{2-7}
+ & LinkGen & & {\bf x} & &  &  \\
+\hline
+\hline  % ======================  graph databases
+\multirow{3}{*}{\rot{\textbf{GDBs}}}
+  & XGDBench & & & {\bf x} & x  &  \\
+\cline{2-7}
+  & gMark & & x & {\bf x} & x  &  \\
+\cline{2-7}
+  & graphGen & & & {\bf x} &  &  \\
+\hline
+\hline %  ======================   social networks
+\multirow{8}{*}{\rot{\textbf{SNs}}}
+ & \cite{Barrett:2009:GAL:1995456.1995598} & & & & {\bf x}  & \\
+\cline{2-7}
+ & \cite{Yao2011}  & & & & {\bf x}  & \\
+\cline{2-7}
+ & LinkBench  & & & x & {\bf x}  & \\
+\cline{2-7}
+ & S3G2  & & x & x & {\bf x}  & \\
+\cline{2-7}
+ & SIB & & x & & {\bf x}  &  \\
+\cline{2-7}
+ & \cite{Sukthankar-SocialInfo2014}  & & & & {\bf x}  & \\
+\cline{2-7}
+ & LDBC SNB   & & x & x & {\bf x}  & \\
+\cline{2-7}
+  & \cite{Nettleton2016}  & & & & {\bf x}  &  \\
+%\hline
+%\hline   % ======================   graph analytics
+%\multirow{1}{*}{\rot{\textbf{A}}}
+%  & HPC Scal. Graph Anal.  & & & & &  \\
+%\cline{2-7}
+%  & Graphalytics & & & & &  \\
+\hline
+\hline   %  ======================  community detection
+\multirow{4}{*}{\rot{\textbf{Co}}}
+  & \cite{danon2005comparing} & x & & & &  {\bf x} \\
+\cline{2-7}
+  & LFR & x & & & &  {\bf x}  \\
+\cline{2-7}
+  & LFR-Overlapping & x & & & &  {\bf x} \\
+\cline{2-7}
+  & Stochastic Block Models & x & & & &  {\bf x} \\
+%\cline{2-7}
+%  & & & & &  \\
+\hline
+%\hline   %  ======================  streaming
+%\multirow{2}{*}{\rot{\textbf{St}}}
+%  & S2Gen & & & & & & & {\bf x}\\
+%\cline{2-7}
+%  & RSPLab & & & & & & & {\bf x} \\
+%%\cline{2-7}
+%%  & & & & & & \\
+%\hline
+\end{tabular} }
+\label{tab:overlapping}
+\end{table}
+
+For example, many general or domain-agnostic graph generators, such as the
+preferential attachment~\cite{Barabasi99emergenceScaling} or R-MAT, are typically used to test graph analytics frameworks when large real graphs are not available.
+%Actually, Graphalytics uses R-MAT as one as its graph generators for benchmarking graph analytics.
+
+Similarly, some social network graph generators such as LDBC SNB, S3G2 or
+LinkBench, can be used to test graph databases. In the case of the first two,
+even though they are designed not to be specific to any type of technology,
+the graph databases are their main target.  Additionally, they also provide serializers for
+RDF, thus they can also be used to test RDF systems.
+
+In the case of LinkBench, nothing prevents the user to load the generated graph
+in a (graph) database (e.g., Facebook uses MySQL in~\cite{Armstrong:2013:LDB:2463676.2465296}) to
+test a workload similar to Facebook and extend and complement it with more
+graph queries like those in LDBC SNB.
+
+Generators for community detection aim, in general, at creating graphs with a
+more realistic structure (graphs with communities of nodes where the density of
+edges is larger internally than externally). Even though these generators are,
+in general, used to test community detection algorithms (they generate also the
+expected communities in the graph), some studies also use them for general graph
+purposes or to test graph analytics algorithms besides community detection.
+
 %\input{classification}
-\input{generators}
+\section{Graph Data Generators}
+\label{sec:generators}
+
+In this section, we discuss the various graph data generators based on the classification introduced before in more detail.
+For each category, we first describe the key features of each of the representative examples and summarize their strengths and weaknesses.
+The goal is to offer a detailed information about each of the tools in the context of its competitors from the same domain.
+
+\subsection{General Graphs}
+\label{sec:generators_general}
+
+We start by focusing on approaches that have been designed for dealing with the
+generation of general graph data that is not aimed at a particular application
+domain. In general, such generators focus on reproducing properties observed in
+real graphs regardless of their domain such as the degree distribution, the
+diameter, the presence of a large connected component, a community structure or
+a significantly large clustering coefficient.
+
+%Currently, there exists a number of tools which involve a kind of
+%general graph data generator, such as gtools from projects nauty and
+%Traces~\cite{gtools} or the Stanford GraphBase~\cite{GraphBase}. We, however,
+%focus on primarily generating/benchmarking projects targeting the Big Data
+%world.
+
+\paragraph {Preferential Attachment} Barabasi and
+Albert~\cite{Barabasi99emergenceScaling} introduced a graph generation model
+that relies on two main mechanisms. The first mechanism is continuously
+expanding the graphs by adding new vertices. The second mechanism is to
+preferentially attach the new vertices   to the nodes/regions that are already
+well connected. So, in this approach, the generation of large graphs is governed
+by standard, robust self-organizing mechanisms that go beyond the
+characteristics of individual applications.
+
+\paragraph {R-MAT} R-MAT (\emph{R}ecursive \emph{Mat}rix) is a procedural
+synthetic graph generator which is designed to generate power-law degree
+distributions~\cite{DBLP:conf/sdm/ChakrabartiZF04}.  The generator is recursive
+and employs a fairly small number of parameters.  In principle, the strategy of
+this generator is to achieve simple means to produce graphs whose properties correspond to
+properties of the real-world graphs. In particular, the design goal of R-MAT is to
+produce graphs which mimics the degree distributions, imitate a community
+structure and have a small diameter. R-MAT can generate weighted, directed and
+bipartite graphs.
+
+\paragraph{HPC Scalable Graph Analysis Benchmark} The HPC Scalable Graph
+Analysis Benchmark~\cite{HPCgraph,Bader:2005:DIH:2099301.2099360} consists of a
+weighted, directed graph that has a power-law distribution and four related
+analysis techniques (namely graph construction, graph extraction with BFS,
+                     classification of large vertex sets, and graph analysis
+                     with betweenness centrality). The generator has the
+following parameters: the number of nodes, the number of edges, and maximum weight of
+an edge. It outputs a list of tuples containing identifiers of vertices of an
+edge (with the direction from the first one to the second one) and weights
+(positive integers  with a uniform random distribution) assigned to the edges of
+the multigraph.  The algorithm of the generator is based on R-MAT.
+%To reduce the data
+%locality, the vertex ids are randomly permuted and the output
+%tuples are shuffled. A related project from the same authors
+%developed for the 9th DIMACS Shortest Paths Challenge is GTgraph~\cite{GTgraph}.
+%t involves three types of graphs: (1) Erd\"{o}s-R\'{e}nyi random graphs, (2)
+%different graphs from the DARPA HPCS SSCA\#2 graph theory benchmark
+%(version 1.0), and (3) small-world graphs generated using the R-MAT graph
+%generator.
+
+\paragraph{GraphGen} For the purpose of testing the scalability of an indexing
+technique called FG-index~\cite{Cheng:2007:FTV:1247480.1247574} on the size of the
+database of graphs, their average size and average density, the authors have
+also implemented a synthetic generator called
+GraphGen\footnote{https://www.cse.ust.hk/graphgen/}. It relies on data generation code for associations and sequential
+patterns provided by IBM\footnote{From 1996, no longer available at
+\url{http://www.almaden.ibm.com/cs/projects/iis/hdb/Projects/data
+mining/mining.shtml}}. GraphGen yields a collection of undirected, labeled and
+connected graphs. It addresses the performance evaluation of frequent subgraph mining
+algorithms and graph query processing algorithms. The result is represented as a
+list of graphs, each consisting of a list of nodes along with a list of edges.
+
+%\paragraph{Graph 500 Benchmark} The Graph 500 Benchmark~\cite{Graph500} includes
+%a scalable data generator which produces weighted, undirected graph as a list of
+%edge tuples containing the label of start vertex and end vertex together with a
+%weight that represents data assigned to the edge. The space of vertex  labels is
+%the set of integers beginning with 0. The input values required to describe the
+%graph are (1) scale, i.e., the logarithm base two of the number of vertices, and
+%(2) edge factor, i.e., the ratio of the graph's edge count to its vertex count
+%(i.e., half the average degree of a vertex in the graph). The graph generator is
+%a Kronecker generator similar to R-MAT. The data must not exhibit any locality,
+%so in the final step the vertex labels and order of edges are randomly shuffled.
+%The covered operations currently involve BFS; however, the authors intend to
+%involve also two more types -- optimization (single source shortest path) and
+%edge-oriented (maximal independent set) -- and five graph-related business areas:
+%cybersecurity, medical informatics, data enrichment, social networks, and
+%symbolic networks.
+
+\paragraph{BTER} BTER (Block Two-Level
+Erd\"{o}s-R\'{e}ny)~\cite{kolda2014scalable} is a graph generator based on the
+creation of multiple Erd\"{o}s-R\'{e}ny graphs with different connection
+probabilities  of which they are connected randomly between them. As the main feature, BTER is able
+to reproduce input degree distributions and average clustering
+coefficient per degree values. The generator starts by grouping the vertices
+by degree $d$, and forming groups of size $d+1$ of nodes with degree $d$. Then, these
+groups are assigned an internal edge probability in order to match the observed
+average clustering coefficient of the nodes of such degree. Based on this
+probability, for each node, the excess degree (i.e, the degree that in
+expectation will not be realized internally in the group) is computed and used to connect
+nodes from different groups at random. The authors describe a highly scalable
+MapReduce-based implementation that is able to generate large graphs (consisting of
+billions of nodes) in a reasonable time budget.
+
+\paragraph{Darwini} Darwini~\cite{edunov2016darwini} is an extension of BTER
+designed to run on Vertex Centric computing frameworks like
+Pregel~\cite{malewicz2010pregel} or Apache Giraph~\cite{ching2015one}, with the
+additional feature that it is more accurate when reproducing the clustering
+coefficient of the input graph. Instead of just focusing on the average
+clustering coefficient for each degree, Darwini is able to model the clustering
+coefficient distribution per degree. It achieves this by gathering the nodes
+of the graph into buckets based on the expected number of closed triangles that they need
+to close in order to attain the expected clustering coefficient. The latter is
+sampled from the input distributions. Then, the vertices in each bucket are
+connected randomly with a probability that would produce the expected
+desired number of triangles for each bucket. Then, as in BTER, the excess degree
+is used to connect the different buckets. The authors report that Darwini is
+able to generate graphs with billions and even trillions of edges.
+
+%\paragraph{gtools} Projects nauty and Traces~\cite{gtools} are programs for
+%computing automorphism groups of graphs and digraphs~\cite{McKay201494}; they
+%can also produce a canonical label. In the respective package there is also
+%suite of programs called gtools which involve generators for non-isomorphic
+%graphs, bipartite graphs, digraphs, and multigraphs.
+
+\paragraph{RTG} \emph{The Random Typing Generator} (RTG)~\cite{DBLP:journals/datamine/AkogluF09} aims at generating realistic graphs.
+In particular, it outputs (un)weighted, (un)directed, as well as uni/bipartite graphs, whereas the realism of the output is ensured by 11 laws (e.g., densification power law, weight power law, small and shrinking diameter, community structure, etc.) known to be typically exhibited by real-world graphs.
+On input it requires 4 parameters ($k$, $q$, $W$, and $\beta$) that correspond to the core Miller's observation~\cite{miller1957} that a random process (namely, having a keyboard with $k$ characters and a space, the process of random typing of $W$ words, where the probability of hitting a space is $q$ and the probability of hitting any other characters is $(1-q)/k$) leads to Zipf-like power laws (of the resulting words) plus in addition (using imbalance factor $\beta$) ensure homophily and community structure.
+RTG is based on the idea creating an edge between pairs of consecutive words.
+
+Paper~\cite{DBLP:conf/wbdb/AmmarO13} further extends this idea mainly in the direction of simplification of specifying of the parameters.
+Instead of Miller's parameters that are not much associated with graphs, the authors prove and exploit their relationship with size and density of the target graph.
+
+\paragraph{Strengths and Weaknesses of General Graph Generators}
+In general, existing general graph generators produce graphs with the following
+properties: skewed degree distribution (e.g., power law), small diameter, a large largest connected component, large
+clustering coefficient, and some degree of
+community structure. Degree distribution can be typically configured while other
+properties are just a result of the generation process and cannot be controlled
+by any means. This is not the case in the work of BTER and Darwini, which besides the degree distribution,
+they also allow tuning of the clustering coefficient. However, some use cases
+demand for more control on the characteristics of the generated graphs.
+This is the case, for example, of benchmarking, where the underlying graph
+structure has direct implications to the performance of the graph algorithms
+to run. For this reason, the design of graph generators with the capability of fine
+tuning the characteristics of the generated graphs still remains as an open
+challenge. The questions that remain are what characteristics to tune
+and which are the algorithms that depend on such characteristics.
+
+\subsection{Semantic Web}
+\label{sec:generators_LinkedData}
+With the dawn of the concept of Linked Data it is a natural development that there would emerge respective
+benchmarks involving both synthetic data and  data sets   with real-world characteristics.
+The used data sets correspond to RDF representation of relational-like data~\cite{Guo2005158,Bizer09theberlin}, social network-like data~\cite{Schmidt2010}, or specific and significantly more complex data structures such as biological data~\cite{Wu2014}.
+In this section, we provide an overview of benchmarking systems involving a kind of graph-based RDF data generator or data modifier.
+%Other types of systems or particular results can be found, e.g., at~\cite{RdfStoreBenchmarking}.
+
+\iffalse
+Considering the Big Data world, the Linked Data in general definitely belong to this group since we assume that the Linked (Open) Data Sets form a common Linked Open Data cloud\footnote{\url{http://lod-cloud.net/}}.
+On the other hand, the particular data sets can be relatively small.
+\fi
+
+\paragraph{LUBM} The use-case driven Lehigh University Benchmark (LUBM)\footnote{\url{http://swat.cse.lehigh.edu/projects/lubm/}} considers the university domain.
+The ontology defines 43 classes and 32 properties~\cite{Guo2005158}.
+In addition, 14 test queries are provided in the LUBM benchmark.
+In particular, the benchmark focuses on \emph{extensional} queries, i.e., queries which target the particular data instances of the ontology, as an opposite to \emph{intentional} queries, i.e., queries which target properties and classes of the ontology.
+The Univ-Bench Artificial  (UBA) data generator features repeatable and random  data generation (exploiting classical linear congruential generator, LCG, of numbers).
+In particular, the data which is produced by the generator are assigned zero-based indexes (i.e., \emph{University0}, \emph{University1} etc.), thus they are reproducible at any time with the same indexes.
+The generator naturally allows to specify a seed for random number generation, along with the starting index and the desired number of universities.
+
+An extension of LUBM, the Lehigh BibTeX Benchmark (LBBM)~\cite{Wang2005}, enables generating synthetic data for different ontologies.
+The data generation process is managed through two main phases: (1) the property-discovery phase, and (2) the data generation phase.
+LBBM provides a probabilistic model that can emulate the discovered properties of the data of a particular domain and generate synthetic data exhibiting similar properties.
+Synthetic data are generated using a Monte Carlo algorithm.
+The approach is demonstrated on the Lehigh University BibTeX ontology which consists of 28 classes along with 80 properties.
+The LUBM benchmark includes 12 test queries that were designed for the benchmark data.
+Another extension of LUBM, the University Ontology Benchmark (UOBM)\footnote{\url{https://www.cs.ox.ac.uk/isg/tools/UOBMGenerator/}}, focuses on two aspects: (1) usage of all constructs of OWL Lite and OWL DL~\cite{owl} and (2) lack of necessary links between the generated data which thus form isolated graphs~\cite{Ma:2006:TCO:2094613.2094629}.
+In the former case the original ontology is replaced by the two types of extended versions from which the user can choose.
+In the latter case cross-university and cross-department links are added to create a more complex graph.
+
+\paragraph{IIMB} Ferrara et al.~\cite{Ferrara08OM} proposed the ISLab Instance Matching Benchmark (IIMB)\footnote{\url{http://www.ics.forth.gr/isl/BenchmarksTutorial/}} for the problem of instance matching.
+For any two objects $o_1$ and $o_2$ adhering to different ontologies or to the same ontology, instance matching is specified in the form of a function $Om(o_1, o_2) \rightarrow \{0, 1\}$,  where $o_1$ and $o_2$ are linked to the same real-world object (in which case the function maps to $1$) or $o_1$ and $o_2$ are representing different objects (in which case the function maps to $0$).
+It targets the domain of movie data which contains 15 named classes, along with 5 objects and 13 datatypes.
+The data are extracted from IMDb\footnote{\url{http://www.imdb.com/}}.
+The data generator corresponds to a data modifier which simulates differences between the data.
+In particular it involves data value differences (such as typographical errors or usage of different standard formats, e.g., for names), structural heterogeneity (represented by different levels of depth for properties, diverse aggregation criteria for properties, or missing values specification) and logical heterogeneity (such as, e.g., instantiation on disjoint classes or various subclasses of the same superclass).
+
+\paragraph{BSBM} The Berlin SPARQL Benchmark (BSBM)\footnote{\url{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}}, is centered around an e-commerce application domain with object types such as \emph{Customer}, \emph{Vendor}, \emph{Product} and \emph{Offer} in addition to the relationship among them~\cite{Bizer09theberlin}.
+The benchmark provides a workload that has 12 queries with 2 types of query workloads (i.e., 2 sequences of the 12 queries) emulating the navigation pattern and search of a consumer seeking a product.
+The data generator is capable of producing arbitrarily scalable datasets by controlling the number of products ($n$) as a scale factor.
+The scale factor also impacts other data characteristics, such as, e.g., the depth of type hierarchy of products, branching factor, the number of product features,  etc.
+BSBM can output two representations, i.e.
+an RDF representation along with a relational representation.
+Thus, BSBM also defines an SQL~\cite{sql} representation of the queries.
+This allows comparison of SPARQL~\cite{sparql} results  to be compared against the performance of traditional RDBMSs.
+
+\paragraph{SP$^2$Bench} The SP$^2$Bench\footnote{\url{http://dbis.informatik.uni-freiburg.de/forschung/projekte/SP2B/}}
+is a language-specific benchmark~\cite{Schmidt2010} which is based on the DBLP dataset. %, so the types involve Person, Inproceedings, Article etc.
+The generated datasets follow the key characteristics of the original DBLP dataset.
+In particular, the data mimics the correlations between entities.
+All random functions of the generator use a fixed seed that ensures that the data generation process is deterministic.
+SP$^2$Bench is accompanied by 12 queries covering the various types of operators such as RDF access paths in addition to typical RDF constructs.
+
+%\paragraph{JustBench} ~\cite{Bail:2010:JFO:1940281.1940285} ...
+
+\paragraph{DBPSB} DBpedia SPARQL Benchmark (DBPSB)\footnote{\url{http://aksw.org/Projects/DBPSB.html}} proposed at the University of Leipzig has been designed using workloads that have been generated by applications and humans~\cite{Morsey2011,Morsey:2012:UBR:2900929.2901031}.
+In addition, the authors argue that benchmarks like LUBM, BSBM, or SP$^2$Bench resemble relational database benchmarks involving relational-like data which is structured using a small amount of homogeneous classes, whereas, in reality, RDF datasets are tending to be more heterogeneous.
+For example, DBpedia 3.6 consists of 289,016 classes, whereas 275 of them are defined based on the DBpedia ontology.
+In addition, in property values different data types as well as references to objects of the various types are
+used.
+Hence, they presented a universal SPARQL benchmark generation approach which uses a flexible data production mechanism that mimics the input data source.
+This dataset generation process begins using an input dataset; then multiple datasets with different sizes  are generated by duplicating all the RDF triples with changing their namespaces.
+For generating smaller datasets, an adequate selection of all triples is selected randomly or using a sampling mechanism over the various classes in the dataset.
+\iffalse The goal of the query analysis and clustering is to detect prototypical queries on the basis of their frequent usage and similarity.\fi The methodology is applied on the DBpedia SPARQL endpoint and a set of 25 templates of SPARQL queries is derived to cover frequent SPARQL features.
+
+\paragraph{LODIB} The Linked Open Data Integration Benchmark (LODIB)\footnote{\url{http://lodib.wbsg.de/}} has been designed with the aim of reflecting the real-world heterogeneities that exist on the Web of Data in order to enable testing of Linked Data translation systems~\cite{DBLP:conf/www/RiveroSBR12}.
+It provides a catalogue of 15 data translation patterns (e.g., rename class, remove language tag etc.), each of which is a common data translation problem in the context of Linked Data.
+The benchmark provides a data generator that produces three different synthetic data sets that need to be translated
+by the system under test into a single target vocabulary.
+They  reflect the pattern distribution in analyzed 84 data translation examples from the LOD Cloud.
+The data sets reflect the same e-commerce scenario used for BSBM.
+
+\paragraph{Geographica} The Geographica benchmark\footnote{\url{http://geographica.di.uoa.gr/}} has been designed to target the area of geospatial data~\cite{DBLP:conf/semweb/GarbisKK13} and respective SPARQL extensions GeoSPARQL~\cite{battle2012enabling} and stSPARQL~\cite{koubarakis2010modeling}.
+The benchmark involves a real-world workload that uses openly available datasets that cover various geometry elements (such as, e.g., lines, points, polygons, etc.) and  a synthetic workload.
+In the former case there is a (1) a micro benchmark that evaluates primitive spatial functions (involving 29 queries) and (2) macro benchmark that tests the performance of RDF engines in various application scenarios such as  map exploring and search (consisting of 11 queries).
+In the latter case of a synthetic workload the generator produces synthetic datasets of different sizes that corresponds to an ontology based on OpenStreetMap  and instantiates query templates.
+\iffalse The spatial extent of the land ownership dataset constitutes a uniform grid of $n \times n$ hexagons, whereas the size of each dataset is given relatively to $n$.\fi The generated SPARQL query workload is corresponding to spatial joins and selection using 2 query templates.
+
+\paragraph{WatDiv} The Waterloo SPARQL Diversity Test Suite (WatDiv)\footnote{\url{http://dsg.uwaterloo.ca/watdiv/}} has
+been designed at the University of Waterloo. It implements stress testing tools that focus on addressing the observation
+that the state-of-the-art SPARQL benchmarks do not fully cover the variety of queries and
+workloads~\cite{Aluc:2014:DST:2717213.2717229}. The benchmark focuses on two types of query aspects --
+structural and data-driven -- and performs a detailed analysis on existing SPARQL benchmarks
+(LUBM, BSBM, DBPSB, and SP$^2$Bench) using these two properties of queries. The structural features involve triple
+pattern count,  join vertex degree, and join vertex count. The data-driven features involve
+result cardinality and several types of selectivity. The analysis of the four benchmarks reveals that their diversity is
+insufficient for evaluation of the weaknesses/strengths of the distinct design alternatives implemented by the different
+RDF systems.
+
+In particular, WatDiv, provides (1) a data generator which generates scalable datasets according to the WatDiv
+schema, (2) a query template generator which produces a  set of query templates according to the WatDiv schema, and
+(3) a query generator that uses the generated templates and instantiates them  with real RDF values from the dataset, and (4) a feature extractor which extracts the structural features of the generated data and workload.
+%For the study in the paper the authors generated 12,500 test queries from 125 query templates.
+
+\paragraph{RBench} RBench~\cite{Qiao:2015:RAR:2723372.2746479} is an application-specific benchmark which receives any RDF dataset as an input and produces a set of datasets, that have similar characteristics of the input dataset, using size scaling factor $s$ and (node) degree scaling factor $d$.
+These factors ensure that the original RDF graph $G$ and the synthetic graph $G'$ are similar and the average node degree and the number of edges of $G'$ are changed by $s$ and $d$ respectively.
+\iffalse A generated benchmark dataset is considered similar to the given dataset if their values for the dataset evaluation metrics and query evaluation times for different techniques are similar.
+Three evaluation metrics are utilized for this purpose: dataset coherence (i.e., a measure how uniformly predicates are distributed among the same type/class), relationship specialty (i.e., the number of occurrences of the same predicate associated with each resource), and literal diversity.\fi A query generation process has been implemented to produce 5 different types of queries (edge-based queries, node-based queries, path queries, star queries, subgraph queries) for any generated data.
+The benchmark project FEASIBLE~\cite{Saleem2015} is also an application-specific benchmark; however, contrary to RBench, it is designed to produce benchmarks from the set of sample input queries of a user-defined
+size.
+
+In practice, one way for handling big RDF graphs is to process them using the
+\emph{streaming} mode where the data stream could consist of the edges of the
+graph. In this mode, the RDF processing algorithms can process the input
+stream in the order it arrives while using only a limited amount of
+memory~\cite{mcgregor2014graph}. The streaming mode has mainly  attracted the attention of the
+RDF and Semantic Web community.
+
+\paragraph{S2Gen}   Phuoc et al.~\cite{le2012linked} presented
+an evaluation framework for linked stream data processing engines. The framework
+uses a dataset generated with the Stream Social network data Generator
+(S2Gen), which
+simulates streams of user interactions (or events) in social networks
+(e.g., posts) in addition to the  user metadata such as users' profile
+information, social network relationships, posts, photos and GPS information.
+The data generator of this framework provides the users the flexibility to
+control the characteristics of the generated stream by tuning a range of
+parameters, which includes the frequency at which interactions are generated,
+limits such as the maximum number of messages per user
+and week, and the correlation probabilities between the different objects (e.g.,
+users) in the social network.
+
+\paragraph{RSPLab} Tommasini et al.~\cite{tommasini2017rsplab} introduced
+another framework for benchmarking RDF Stream Processing systems, RSPLab. The
+Streamer component of this framework is designed to publish RDF streams from the
+various existing RDF benchmarks (e.g., BSBM, LUBM).
+In particular, the Streamer  component uses TripleWave\footnote{\url{http://streamreasoning.github.io/TripleWave/}}, an
+open-source framework which enables to share RDF streams on the
+Web~\cite{mauri2016triplewave}.   TripleWave acts as a means for plugging-in
+and combining streams from multiple Web data sources using either pull or push mode.
+
+\paragraph{LDBC}  The Linked Data Benchmark Council\footnote{\url{http://ldbcouncil.org/industry/organization/origins}} (LDBC)~\cite{Angles:2014:LDB:2627692.2627697} %is a result of a (closed) EU project that brought together a community of academic researchers and industry that
+had the goal of developing open source, yet industrial grade benchmarks for RDF and graph databases.
+\iffalse The following three benchmarks were developed and are currently maintained.\fi In the Semantic Web
+domain, it released the Semantic Publishing Benchmark (SPB)~\cite{spb} that has been inspired by the
+Media/Publishing industry (namely BBC\footnote{\url{http://www.bbc.com/}}). The application scenario
+of this benchmark simulates a media or a publishing organization that handles large amount
+of streaming content (e.g., news, articles). \iffalse This content is enriched with metadata that describes
+it and links it to reference knowledge -- taxonomies and databases that include relevant concepts,
+entities and factual information. The SPB data generator produces scalable in size synthetic large data.
+Synthetic data consists of a large number of annotations of media assets that refer entities found in
+reference datasets.\fi The data generator mimics three types of relations in the generated synthetic data:
+correlations of entities, data clustering, and random tagging of entities.
+Two workloads are provided: (1) basic, involving an interactive query-mix querying the relations between entities in reference data, and (2) advanced,  focusing on interactive and analytical query-mixes.
+The LDBC has designed two other benchmarks: the Social Network Benchmark (SNB)~\cite{Erling:2015:LSN:2723372.2742786} for the social network domain  (see Section~\ref{sec:generators_socialnetworks}) and Graphalytics~\cite{Iosup:2016:LGB:3007263.3007270}   for the analytics domain.% (see Section~\ref{sec:generators_analytics}).
+
+\paragraph{LinkGen} LinkGen is a synthetic linked data generator that has been designed to generate RDF datasets for a given vocabulary~\cite{10.1007/978-3-319-46547-0_12}.
+The generator is designed to receive a vocabulary as an input  and supports two statistical distributions for generating entities:  Zipf's power-law distribution and Gaussian distribution.
+LinkGen can augment the generated data with inconsistent and noisy  data such as updating a given datatype property with two conflicting values or  adding triples with syntactic errors.
+\iffalse, adding wrong statements by assigning them with invalid domain and creating instances with no type information.\fi The generator also provides a feature to inter-link the generated objects with real-world ones from user-provided real-world datasets.
+The datasets can be generated in any of of two modes: on-disk and streaming.
+
+\paragraph{Strengths and Weaknesses of Semantic Web Graph Generators}  Graphs are intuitive and standard representation for the RDF model that form the basis for the Semantic Web community which has been very active on building several benchmarks, associated with graph generators that had various design principles.
+
+A comparison of 4 RDF benchmarks (namely TPC-H~\cite{TPC-H} data expressed in RDF, LUBM, BSBM, and SP$^2$Bench) and 6 real-wold data sets (such as, e.g.,  DBpedia, the Barton Libraries Dataset~\cite{barton-benchmark} or
+WordNet~\cite{Miller:1995:WLD:219717.219748}) has been reported by~\cite{Duan:2011:AOC:1989323.1989340}.
+The authors focus mainly on the  \emph{structuredness} (\emph{coherence}) of each benchmark dataset claiming that a primitive metric (e.g., the number of triples or the average in/outdegree) quantifies only some target characteristics of each dataset.
+With respect to a type $T$ the degree of structuredness of a dataset $D$  is based on  the regularity of instance data in $D$ in conforming to type $T$.
+The type system is extracted from the data set by finding the RDF triples that have property\footnote{\url{http://www.w3.org/1999/02/22-rdf-syntax-ns\#type}}   and extract type $T$ from their object.
+Properties of $T$ are determined as the union of all properties of type $T$.
+The structuredness is then expressed as a weighted sum of share of set properties of each type, whereas higher weights are assigned to types with more instances.
+The authors show that the structuredness of the chosen benchmarks is fixed, whereas real-world RDF datasets are belonging to the non-tested area of the spectrum.
+As a consequence, they introduce a new benchmark that receives as input any dataset associated with a required level of structuredness and size (smaller than the size of the original data), and exploits the input documents as a seed to produce a subset of the original data with the target structuredness and size.
+In addition, they show that structuredness and size mutually influence each other.
+
+With the recent increasing momentum of streaming data, the Semantic Web community started to consider the issues and challenges of RDF streaming data.
+However, there are still a lot of open challenges that need to tackled in this direction such as covering different real-world application scenarios.
+
+\subsection{Graph Databases}
+\label{sec:generators_GraphDatabases}
+
+Currently there exists a number of papers which compare the efficiency of graph databases with regards to distinct use cases, such as  the community detection problem~\cite{Beis2015}, social tagging systems~\cite{Giatsoglou2011}, graph traversal~\cite{Ciglan:2012:BTO:2374486.2375242}, graph pattern matching~\cite{Pobiedina2014}, data provenance~\cite{Vicknair:2010:CGD:1900008.1900067}, or even several distinct use cases~\cite{Grossniklaus2013Towar-24253}.
+However, the number of graph data generators and benchmarks that have been designed specifically for graph data management systems (Graph DBMS)  is relatively small.
+Either a general graph generator is used for benchmarking graph databases, such as, e.g., the HPC Scalable Graph Analysis Benchmark~\cite{Dominguez-Sal:2010:SGD:1927585.1927590} or the graph DBMS benchmarking tools are designed while having in mind a more general scope.
+Hence it is questionable whether a benchmark  that is targeted specifically for graph databases is necessary.
+\cite{Dominguez-Sal:2010:DDG:1946050.1946053} discussed this question and related topics.
+On the basis of a review of applications of graph databases (namely, social network analysis,  genetic interactions and recommendation systems), the authors analyzed and discussed the features of the graphs for these types of applications and how such features can affect the benchmarking process, various types of operations used in these applications and the characteristics of the evaluation setup of the benchmark.
+In this section, we focus on graph data generators and benchmarks that have been primarily targeting graph DBMSs.
+
+\paragraph{XGDBench} XGDBench~\cite{Dayarathna:2014:GDB:2676904.2676939} is an extensible  benchmarking platform for graph databases used in cloud-based systems. Its intent is to automate
+benchmarking of graph databases in the cloud by focusing on the domain social networking services.
+It extends the Yahoo!
+Cloud Multiplicative Attribute (MAG) Graph Serving Benchmark (YCSB)~\cite{Cooper:2010:BCS:1807128.1807152} and provides a set of standard workloads representing various performance issues.
+In particular, the workload of XGDBench involves basic operations such as read / insert / update / delete an attribute, loading of the list of neighbours and BFS traversal.
+Using the generators, 7 workloads are created, such as update heavy, read mostly, short range scan, traverse heavy etc.
+The data model of XGDBench is a simplified version of the Multiplicative Attribute Graph (MAG)~\cite{Kim2010} model, a synthetic graph model which models the interactions between node attributes and  graph structure.
+The generated graphs are thus in MAG format, with power-law degree distribution closely simulating real-world social networks.
+The simplified MAG algorithm accepts the required number of nodes and for each node the number of attributes, a threshold for random  initialization of attributes, a threshold for edge affinity which determines the existence of an edge between two nodes, and an affinity matrix.
+\iffalse It has been proven that MAG generates graphs with both analytically tractable and statistically interesting properties.\fi
+Large graphs can be generated on multi-core systems by XGDBench multi-threaded version.
+
+\paragraph{gMark}  gMark~\cite{gMark} is a schema-driven and domain-agnostic generator of both graph instances and graph query workloads.
+It can generate instances under the form of N-triples and queries in various concrete query languages, including OpenCypher\footnote{\url{https://neo4j.com/developer/cypher-query-language/}}, recursive SQL, SPARQL and LogicQL.
+In gMark, it is possible to specify a \emph{graph configuration} involving the admitted edge predicates and node labels occurring in the graph instance along with additional parameters such as degree distribution, occurrence constraints, etc.
+The \emph{Query workload configuration} describes parameters of the query workload to be generated, by including the number of queries, arity, shape and selectivity of the queries.
+The problem of deciding whether there exists a graph that satisfies a defined graph specification $G$ is NP-complete. The same applies to the problem of deciding
+whether there exists a query workload compliant with a given query workload configuration $Q$. In view of this, gMark adopts a best effort approach in which the
+parameters specified in the configuration files are attained in a relaxed fashion in order to achieve linear running time whenever possible.
+
+%The authors prove that deciding whether there exists a graph satisfying a given graph configuration $G$ is NP-complete. And, similarly, deciding
+%whether there exists a query workload satisfying a given query workload configuration $Q$ is also NP-complete.
+Hence, gMark generating is based on a heuristic strategy: it tries to achieve the exact values of the given parameters, however, in order to obtain linear running time it may decide to relax some.
+gMark generates graphs under the form of N-triples and query workloads in four concrete syntaxes, including Cypher\footnote{\url{https://neo4j.com/developer/cypher-query-language/}}, SPARQL, SQL and LogicQL.
+
+\paragraph{GraphGen}  GraphAware GraphGen\footnote{\url{http://graphgen.graphaware.com/}} is a graph generation engine based on Neo4j's\footnote{\url{https://neo4j.com/}} query language OpenCypher~\cite{GraphGen}.
+It creates nodes and relationships based on a schema definition expressed in Cypher, and it can also generate property values on both
+nodes and edges.
+As such, GraphGen is a precursor of property graphs generators.
+The resulting graph can be exported to several formats (namely GraphJson\footnote{\url{https://github.com/GraphAlchemist/GraphJSON/wiki/GraphJSON}} and CypherQueries) or loaded directly to a DBMS.
+However, it is very likely that it is not maintained anymore due to the lack of available recent commits.
+
+\paragraph{Strengths and Weaknesses of Graph Database Generators}
+The graph DBMS generators discussed in this section have in common the fact that they can generate semantically rich labeled graphs with properties (ranging from properties values in GraphGen to MAG structures in XGDBench).
+They are also capable of generating graph instances and query workloads in
+concrete syntaxes (among which OpenCypher in GraphGen and gMark) and one of them (XGDBench) can also handle update operations on both graph structure and content.
+However, more comprehensive graph DBMS generators that also produce data manipulation operations (such as updates for graph databases) are urgently needed.
+Additionally, none of these generators is enabled to work on corresponding query languages for property graphs, such as the newly emerging standard GQL~\cite{gql-2018} and G-Core~\cite{AnglesABBFGLPPS18}.
+Hence, a full-fledged graph DBMS generator for property graphs and property graph query workloads~\cite{BFVY18} is still missing and there exists an interesting opportunity to build such a generator in the near future.
+
+Another apparent inconvenience is represented by the fact that explicit correlations among graph elements cannot be encoded for instance in gMark or GraphGen, whereas they could be fruitful in order to reproduce the behavior of real-world graphs in which attribute values are correlated one with another.
+On the other hand, social network and Linked Data generators that support correlations (as highlighted in Section \ref{sec:generators_socialnetworks} and Section \ref{sec:generators_LinkedData}) typically exhibit a fixed schema and are not not necessarily multi-domain as are some of the graph DBMS generators discussed in this section (namely GraphGen and gMark).
+
+\subsection{Social Networks}
+\label{sec:generators_socialnetworks}
+
+On-line social networks, like Facebook, Twitter, or LinkedIn, have become a
+phenomenon used by billions of people every day and thus providing extremely
+useful information for various domains. However, an analysis of such type of
+graphs has to cope with two problems: (1) availability of the data and (2)
+privacy of the data. Hence, data generators which provide realistic synthetic
+social network graphs are in a great demand.
+
+In general, any analysis of social networks identifies their various specific
+features~\cite{Chakrabarti:2006:GML:1132952.1132954}. For example, a social
+networks graph often has a high  degree of
+transitivity of the graph (so-called \emph{clustering coefficient}). Or, its diameter, i.e., the longest shortest path
+amongst some fraction (e.g. 90\%) of all connected nodes, is usually low due to
+weak ties joining faraway cliques.
+
+Another key aspect of social networks is the community effect. A detailed
+study of structure of communities in 70 real-world networks is provided, e.g.,
+in~\cite{Leskovec:2008:SPC:1367497.1367591}.
+~\cite{Prat-Perez:2014:CSS:2621934.2621942} analyzed the structure of
+communities (clustering coefficient, triangle participation ratio,
+diameter, bridges, conductance, and size) in both real-world graphs and outputs of
+existing graph generators such as LFR~\cite{PhysRevE.78.046110} and the
+LDBC SNB~\cite{Erling:2015:LSN:2723372.2742786}. They found out that discovered
+communities  in different graphs have common distributions and that communities
+of a single graph have different characteristics and are challenging to be represented using a single
+model.
+
+The existing social network generators try to reproduce different aspects of the
+generated network. They can be categorized into statistical and agent-based.
+\emph{Statistical
+approaches}~\cite{PhysRevE.78.046110,Yao2011,Armstrong:2013:LDB:2463676.2465296,Pham2013,Sukthankar-SocialInfo2014,Erling:2015:LSN:2723372.2742786,Nettleton2016}
+focused on reproducing aspects of the network. In \emph{agent-based
+approaches}~\cite{Barrett:2009:GAL:1995456.1995598,Bernstein:2013:SAS:2499604.2499609}
+the networks are constructed by directly simulating the agents' social choices.
+
+%\paragraph{LFR} Lancichinetti, Fortnato and Radicchi (hence
+%LFR)~\cite{PhysRevE.78.046110} develop a class of benchmark graphs whose nodes
+%participate in internal community structures. The benchmark models directed and
+%weighted real-world networks (e.g., social networks) containing overlapping
+%communities of different sizes. The algorithm assumes that both the degree and
+%the community size distributions are power laws. Each node shares a fraction $(1
+%- \mu)$ of its links with the other nodes of its community and a fraction $\mu$
+%with the other nodes of the network, where $\mu$ is called \emph{mixing
+%parameter}. The sizes of the communities are taken from a power law distribution
+%such that the sum of all sizes equals the number of nodes of the graph. The
+%generation process starts with an empty graph and incrementally fills in the
+%adjacency matrix by obeying the described constraints.
+
+\paragraph{Realistic Social Network}
+~\cite{Barrett:2009:GAL:1995456.1995598} focused on the construction of
+realistic social networks. For this purpose the authors combine both
+private and public data sets with large-scale agent-based techniques. The process works as
+follows: In the first step it generates  synthetic data by combining public and
+commercial databases. In the second step, it determines a set of activity
+templates. A 24-hour activity sequence including geolocations is assigned to
+each synthetic individual. To demonstrate the approach, the authors create a
+synthetic US population consisting of people and households together with
+respective geolocations. For this purpose the authors combine simulation and
+data fusion techniques utilizing various real-world data sources such as U.S.
+Census data, responses to a time-use survey or an activity survey.
+%Demographic information for each person and location, a minute-by-minute
+%schedule of each person's activities, and the locations where these activities
+%take place is generated by a combination of simulation and data fusion
+%techniques.
+The result is captured by a dynamic network of social contacts. Similar methods for
+agent-based strategies have been reported
+in~\cite{Bernstein:2013:SAS:2499604.2499609}.
+
+\paragraph{Linkage vs. Activity Graphs}
+\cite{Yao2011} distinguished between two types of social network graphs -- the
+\emph{linkage graph}, where nodes correspond to people and edges correspond to their
+friendships, and the \emph{activity graph}, where nodes also represent people
+but edges correspond to their interactions. On the basis of the analysis of
+Flickr\footnote{\url{https://www.flickr.com/}} social links and
+Epinions\footnote{\url{http://www.epinions.com/}} network of user interactions,
+the authors discover that they both exhibit high clustering coefficient
+(community structure), power-law degree distribution and small diameter.
+Considering the dynamic properties they both have relatively stable clustering
+coefficient over time and follow the densification law. On the other hand,
+diameter shrinking is not observed in Epinions activity graph and there is a
+difference in degree correlation (i.e., frequency of mutual connections of
+similar nodes) -- activity graphs have neutral, whereas linkage graphs have positive degree correlation. With regards to the findings, the
+proposed generator focuses on linkage graphs with positive degree correlation.
+For this purpose it extends the forest fire spreading process
+algorithm~\cite{Leskovec:2005:GOT:1081870.1081893} with link symmetry. It has
+two parameters: the \emph{symmetry
+probability} $P_s$ and the \emph{burning probability} $P_b$. $P_b$ ensures a forward burning process based on BFS in which
+fire burns strongly with $P_b$ approaching 1.  $P_s$ ensures backward linking
+from old nodes to new nodes and ``adds fuel to the fire as it brings more
+links''. %It gives chances for big nodes to connect back to big nodes.
+
+\paragraph{LinkBench} The LinkBench
+benchmark~\cite{Armstrong:2013:LDB:2463676.2465296} has been designed for the
+purpose of analysis of efficiency of a database storing Facebook's production
+data. The benchmark considers true Big Data and related problems with sharding,
+replication etc. The social graph at Facebook comprises objects (nodes with IDs,
+version, timestamp and data) and associations (directed edges, pairs of node
+IDs, with visibility, timestamp and data). The size of the target graph is the
+number of nodes. Graph edges and nodes are generated concurrently during bulk
+loading. The space of node IDs is divided into chunks which enable parallel
+processing. The edges of the graph are generated in accordance with the results
+of analysing  real-world Facebook data (such as outdegree distribution). A
+workload corresponding to 10 graph operations (such as insert object, count the
+number of associations etc.) and their respective characteristics over the
+real-world data is generated for the synthetic data.
+
+\paragraph{S3G2} The Scalable Structure-correlated Social Graph Generator
+(S3G2)~\cite{Pham2013} is a general framework which produces a directed labeled
+graph whose vertices represent objects having property values. The respective
+classes determine the structure of the properties. S3G2 does not aim at
+generating near real-world data, but at generating synthetic graphs with a
+correlated structure. Hence, the existing data values influence the probability
+of choosing a particular property value from a pre-defined dictionary or connecting two nodes. For example, the degree distribution can be
+correlated with the properties of a node and thus, e.g., people who have many
+friend relationships typically post more comments and pictures. The data
+generation process starts with generating a number of nodes with property values
+generated according to specified property value correlations and then adding
+respective edges according to specified correlation dimensions. It has multiple
+phases, each focusing on one correlation dimension. Data is generated in a Map
+phase corresponding to a pass along one correlation dimension. Then the data are
+sorted along the correlation dimension in the following Reduce phase. A
+heuristic observation that ``the probability that two nodes are connected is
+typically skewed with respect to some similarity between the nodes'' enables to
+focus only on sliding window of most probable candidates. The core idea of the
+framework is demonstrated using an example of a social network (consisting of
+persons and social activities).  The dictionaries for property values are
+inspired by DBpedia and provided with 20 property value correlations. The edges
+are generated according to 3 correlation dimensions.
+
+\paragraph{SIB} The developers of the Social Network Intelligence BenchMark (SIB)\footnote{\url{https://www.w3.org/wiki/Social_Network_Intelligence_BenchMark}} based the design of their benchmark on the claim that the state-of-the-art benchmarks are limited in reflecting the characteristics of the real RDF databases and are mostly focusing on the relational style aspects.
+Hence, they proposed a benchmark for  query evaluation using real graphs~\cite{sib}.
+The proposed benchmark mimics using an RDF store for a social network.
+\iffalse site where users and their interactions form a social graph of social activities such as creating/managing groups, writing posts and posting comments.\fi The distribution of the generated data for each type follows the  distribution of the associated type inferred from real-world social networks.
+Additionally, association rules are exploited for representing the real-world data correlation in the generated synthetic data.
+The  generated data is linked with the RDF datasets from DBpedia.
+The benchmark specification contains 3 query mixes -- interactive, update, and analysis -- expressed in SPARQL 1.1 Working Draft.
+
+\paragraph{Cloning of Social Networks} ~\cite{Sukthankar-SocialInfo2014}
+introduces two synthetic generators to reproduce two characteristics typically
+observed in social networks: node features and multiple link types. Both
+generators extend  the generator proposed by~\cite{wang2011leveraging}.
+which starts with a small number of
+nodes and new nodes are added until the network reaches the required number. It
+has two basic parameters: homophily and link density. A high \emph{homophily}
+value reflects that links have higher chances to be established among the nodes belonging to the same community,
+whereas the community membership is represented by the same labels.
+
+The first proposed generator is Attribute Synthetic Generator (ASG), used for
+reproducing the node feature distribution of standard networks and rewiring the
+network to preferentially connect nodes that exhibit a high feature similarity.
+The network is initialized with a group of three nodes. New nodes and links
+are added to the network based on link density, homophily, and feature
+similarity. As new nodes are created, their labels are assigned based on the
+prior label distribution. After the network has reached the same number of nodes
+as the original social media dataset, each node initially receives a random
+attribute assignment. Then a stochastic optimization process is used to move the
+initial assignments closer to the target distribution extracted from social
+media dataset using the Particle Swarm Optimization algorithm. The tuned
+attributes are then used to add additional links to the network based on the
+feature similarity parameter -- a source node is selected randomly and connected
+to the most similar node. The second proposed generator, so-called Multi-Link Generator
+(MLG), further  uses link co-occurrence statistics from the original dataset to
+create a multiplex network. MLG uses the same network growth process as ASG.
+Based on the link density parameter, either a new node is generated with a label
+based on the label distribution of the target dataset or a new link is created
+between two existing nodes.
+
+\paragraph{LDBC SNB} Despite having a common Facebook-like dataset, thanks to
+three distinct workloads the Social Network Benchmark
+(SNB)~\cite{Erling:2015:LSN:2723372.2742786} provided by LDBC represents three
+distinct benchmarks. The network nodes correspond to people and the edges
+represent their friendship and messages they post in discussion trees on their
+forums. The three query workloads involve: (1) SNB-Interactive, i.e., complex
+read-only queries accessing a high portion of data, (2) SNB-BI, i.e.,
+queries accessing a high percentage of  entities and grouping them in various
+dimensions, and (3) SNB-Algorithms, involving graph analysis algorithms, such as
+community detection, PageRank, BFS, and clustering. The graph generator, called
+Datagen, is a fork of \texttt{S3G2} ~\cite{Pham2013} and realizes power laws, uses skewed
+value distributions, and ensures reasonable correlations between graph
+structures and property values. Additionally, it extends \texttt{S3G2} with "spiky"
+patterns in the distribution of social network activity along the timeline, also
+provides the ability of generating update streams to the social network. Datagen
+is also based on Hadoop in order to provide scalability, but compared to \texttt{S3G2}, it
+contains numerous performance improvements and the ability to be deterministic
+regardless of the number of computer nodes used for the generation of the graphs
+and for a given set of configuration parameters.
+
+%The generated data have become a part if several graph benchmarks, such as GraphBIG~\cite{Nai:2015:GUG:2807591.2807626}.
+
+\paragraph{Towards More Realistic Data} \cite{Nettleton2016} argued that the majority of existing works focuses on
+topology generation which approximates the features of a real-world social
+network (e.g., community structures, skew degree
+distribution, a small average path length, or a small graph diameter); however,  this is usually done without any data. Hence, they
+introduced a general stochastic modeling approach that enables the users to
+fill a graph topology with data. The approach has three steps: (1) topology
+generation (using R-MAT) plus community identification using the Louvain
+method~\cite{1742-5468-2008-10-P10008} or usage of a real-world topology from
+SNAP\footnote{\url{https://snap.stanford.edu/data/}}, (2) data definition
+that describes  definitions of attribute values (distribution profiles) using a
+parameterizable set of affinities and data propagation rules, and (3) data
+population.
+
+\paragraph{Strengths and Weaknesses of Social Network Generators}
+Compared to more general graph generators, social network generators focus
+mainly on reproducing intra- and inter-node feature correlations.
+Among existing generators, LDBC SNB and S3G2 look
+like the most advanced ones in terms of the complexity of the generated graph
+and the amount of features and correlations they can generate, while providing a
+large degree of scalability. Their generation process is based on input dictionaries and have configuration files that
+allow tweaking  many parameters of the generated graphs, but their schema is mainly
+static and cannot be easily configured to meet the needs of other use cases
+besides the benchmarks they have been designed for. In this regard, the approaches
+like those proposed in~\cite{Nettleton2016} and~\cite{Sukthankar-SocialInfo2014} offer a
+more flexible and understandable configuration process to tweak the types,
+values, and correlations between different features.
+
+Regarding the correlation between the underlying graph structure and the node
+features, approaches such as LDBC SNB, S3G2 or ~\cite{Nettleton2016}
+take into account this aspect and the generated graphs have realistic
+structural properties while similar nodes have a larger probability of being
+connected. However, their approach seems to be more based on
+intuition and common sense than to be backed up by  any study of how the
+relation between structure and attributes showcase in real social networks. In
+this regard, this remains as a clear open challenge for social network
+generators.
+
+Finally, scalability is another aspect to be considered in social network graph
+generators. LDBC SNB and S3G2 are engineered with this in mind, thus they
+provide a way to scale to billions of nodes and edges. This is not the case for
+the other generators, which can make them impractical if our goal is to generate
+real sized social network graphs.
+
+%\input{generators_analytics}
+
+\subsection{Testing Community Detection}
+\label{sec:generators_community_detection}
+
+Community detection is one of the many graph analytics algorithms typically used
+in domains such as social networks or bioinformatics. \emph{Communities} are usually defined as sets of nodes that are highly mutually connected, while being scarcely connected to
+the other nodes of the graph. Such communities emerge from the fact that real-world graphs
+are not random, but follow real-world dynamics that make similar entities to
+have a larger probability to be connected. As a consequence, detected
+communities are used to reveal vertices with similar characteristics, for
+instance to discover functionally equivalent proteins in protein-to-protein
+interaction networks, or persons with similar interests in social networks. Such
+applications have made community detection a hot topic during the last 15
+years with tens of developed algorithms and detection
+strategies~\cite{doi:10.1002/wics.1403,Kim:2015:CDM:2854006.2854013}. For
+comparing the quality of the different proposed techniques, one needs graphs
+with \emph{reference communities}, that is, communities known beforehand. Since
+it is very difficult to have large real-world graphs with reference communities
+(mainly because these would require a manual labeling), graphs for benchmarking
+community detection algorithms are typically generated synthetically.
+
+\paragraph{Danon et al.} The first attempts to compare community detection algorithms using synthetic
+graphs proposed the use of random graphs composed by several Erd\"{o}s-R\'{e}nyi
+subgraphs, connected more internally than externally~\cite{danon2005comparing}.
+Each of these subgraphs has the same size and the same internal/external density
+of edges. However, such graphs miss the realism observed in real-world graphs, where
+communities are of different sizes and densities, thus several proposals exist
+to overcome such an issue.
+
+\paragraph{LFR} Lancichinetti, Fortunato
+and Radicchi (hence LFR)~\cite{PhysRevE.78.046110} propose a class of benchmark
+graphs for community detection where communities are of diverse sizes and
+densities. The generated communities follow a power-law distribution whose parameters can be configured. The degree of the
+nodes is also sampled from a power-law distribution. Additionally, the generator
+introduces the concept of the ``mixing factor'', which consists of the percentage of
+edges in the graph connecting nodes that belong to distinct communities. Such parameter
+allows  the degree of modularity of the generated graph  to be tuned, thus
+testing the robustness of the algorithms under different conditions. The
+generation process is implemented as an optimization process starting with an empty graph and
+progressively filling it with nodes and edges guided by the specified constraints.
+
+\paragraph{LFR-Overlapping} Lancichinetti, Fortunato and
+Radicchi~\cite{PhysRevE.80.016118} extended LFR to support the notion of
+directed graphs and overlapping communities. Overlapping communities extend the
+notion of communities by allowing the sharing of vertices, thus a vertex can
+belong to more than one community. This extended generator allows controlling
+the same parameters of LFR, as well as the amount of overlap of
+the generated communities.
+
+\paragraph{Stochastic Block Models} Another popular family of generators
+widely used in the community detection field are the stochastic block
+models~\cite{holland1983stochastic}. In such models, the community structure of
+the graph is typically defined as an array of $n$ community or cluster sizes
+and a density square matrix of size $n \times n$ containing the density of
+intra-cluster edges (in the diagonal of the matrix) and the density of
+inter-cluster edges. Then, a stochastic procedure is run to sample graphs
+from such array and matrix, using the sizes to compute the possible edges
+and the densities as probabilities of such edges to exist. The popularity of
+these methods stem from its simplicity and scalability, which makes them
+suitable for generating large graphs fast and in distributed environments,
+provided that the density matrix is sparse (as it happens in most of real-world graphs). Moreover, given
+that the generation process of such models is mathematically tractable, they
+are typically used to analyze the limitations of algorithms for community detection
+ such as those based on modularity
+optimization~\cite{fortunato2007resolution} or based on
+triads~\cite{prat2016put}. Extensions of such models exist, such as the
+Mixed Membership Stochastic Block Model~\cite{airoldi2008mixed}, for
+overlapping communities.
+
+\paragraph{Strengths and Weaknesses of Community Detection Generators}
+Besides synthetic graph generators, Yang and Leskovec~\cite{yang2015defining}
+proposed the use of real-world graphs with explicit group annotations (e.g.,
+forums in a social network, categories of products, etc.) to infer what they
+call \emph{meta-communities}, and use them to evaluate overlapping community
+detection algorithms. However, a recent study from Hric, Darst and
+Fortunato~\cite{hric2014community} reveal a loose correspondence between
+communities (the authors refer to them as \emph{structural communities}) and
+meta-communities.  This result reveals that  algorithms working for structural
+communities do not work well for finding meta-communities and vice versa,
+suggesting significantly different underlying characteristics
+between the two types of communities, which are yet to be
+identified.
+
+In this regard and to the best of our knowledge, there are no available
+generators that can generate graphs with meta-communities for community detection
+algorithm benchmarking. The closest one is the LDBC SNB data
+generator which has been provided by the
+generation of groups of users in the social network. Even though the generation
+process does not specifically enforce the generation of groups
+(meta-communities) for benchmarking community detection algorithms, the study~\cite{Prat-Perez:2014:CSS:2621934.2621942} reveals that these groups are more similar
+to the real meta-communities than those structural communities generated by the
+LFR benchmark.
+
+The differences observed between structural and meta-communities reveal the need
+of more accurate community definitions that are more tight and more specific to the domain or the 
+use case. Current community detection algorithms and graph generators for
+community detection are stuck to the traditional (and vague) definition of
+community, assuming that there exists a single algorithm that would fit all the
+use cases. Thus, future work requires the study of domain-specific community
+characteristics that can be used to generate graphs with a community structure
+that accurately resembles that of specific use cases, and thus revealing which
+are the best algorithms for each particular scenario.
+
 %\input{comparison2}
 %\input{data_sets}
-\input{challenges}
-\input{conclusion}
+\section{Challenges and Open Problems}
+\label{sec:challenges}
+
+To conclude the  overview of the state-of-the-art of graph data generation, in this section we discuss several of the open challenges.
+
+\subsection{Simple Usage, Simple Parameters}
+The proposal of a data generator (not necessarily for graph data) has to face an
+important schism. On one hand, it must provide the user with as
+many parameters as possible in order to enable him/her to generate
+arbitrary data.
+This approach seems to be reasonable, but it entails a shortcoming due to
+the fact that ordinary users are
+unwilling to use complex benchmarking tools. This observation can be
+seen, for example, in the case of XML benchmarks -- even though there exist
+robust and complex data generators (such as
+ToXGene~\cite{conf/webdb/BarbosaMKL02}, which supports the specification of
+structural aspects, value distributions, references etc.), the most popular
+benchmarking tool is XMark~\cite{Schmidt:2002:XBX:1287369.1287455}, which models
+a single use case and enables its users to specify just the size of the data. Hence, the
+other extreme is to provide a simple data generator which does not require any
+complex settings and thus guarantees a simple and fast benchmarking process.
+
+Considering the complex structure of graph data and the variety of applications
+requiring highly specific types of graphs, the latter solution is difficult to
+implement. A reasonable compromise can be found in a data generator which is
+provided with sample graph data and is capable of automatic analysis of its
+structural and value features in order to learn the complex parameters. We could see this type approach in some cases, such as Semantic Web generators LBBM or DBPSB.
+
+\subsection{Large Scale Graphs with Realistic Structure}
+
+Most of existing graph generators are focused on generating large graphs with realistic
+structural characteristics and focus principally on reproducing the degree
+distribution and the clustering
+coefficient~\cite{kolda2014scalable,edunov2016darwini}. However, there are other
+structural characteristics that one might be interested in reproducing for a large
+graph, such as the diameter, the size of the largest connected component, or the
+hierarchical community structure. Graph practitioners are highly interested in knowing
+how other high-level structural characteristics affect the performance of graph
+queries and graph algorithms. Hence, a compelling open challenge consists
+of creating
+graph generators that allow one to reproduce diverse structural characteristics
+of the graphs along with large scale sizes.
+
+\subsection{Single- vs. Multi-Domain}
+
+Most of existing graph generators also generate graphs that are either not labeled or
+are specific to a given domain (e.g.,  social networks). Graphs from different
+domains have different schemas, structural characteristics, property
+distributions, etc. which might have an impact on the performance of the
+application under test. Thus, graph processing engine developers are asking for
+generators or tools to generate multi-domain graphs  in a flexible and holistic manner, allowing to configure aspects
+such as size, schemata, data distributions and other structural
+characteristics such as degree distributions, clustering coefficients, and
+so on.
+
+\subsection{Generating Noisy Graphs and Graphs with Anomalies}
+Injecting noise and/or anomalies and errors into graphs is crucial for
+testing both machine learning algorithms working on this complex data and
+data quality techniques aiming at detecting anomalies and repairing graph
+data.
+
+Concerning the former, analyzing and labeling structural networks is
+deemed to be more difficult for graph datasets in the presence of noise.
+Since de-noising graph data is difficult to achieve, various machine learning-based
+approaches have been adapted to work with noise (i.e., mislabeled
+samples) or outliers, such as
+imbalanced graph classification \cite{PanZ13} and
+binary graph classification with positive and negative weights \cite{CheungSML16}.
+Synthetic graph generators that take into account noisy and missing data
+have been studied in \cite{NamataG10}, where graph identification is presented in
+order to  model the inference of a cleaned output network from a
+noisy input graph.
+Concerning the latter, data quality techniques handling graph data are recently considering ad-hoc
+generation of graph data and graph quality rules in order to evaluate the
+effectiveness of error detection and data repairing algorithms \cite{FanWX16a,AriouaB18}. The
+corresponding graph quality rules are typically handcrafted by domain
+experts, whereas an automatic generation of such rules along with the graph
+data generation in tandem would be an interesting future challenge for the
+community.
+
+\subsection{Streaming Graph Generators}
+Stream computing is a new paradigm that is necessitated by various modern data generation scenarios such as the ubiquity of mobile devices, location services,
+sensor pervasiveness and emerging IoT applications. These applications generate the data with high Velocity, one of the
+main 3V characteristics of Big Data applications~\cite{sakr2016big}. In most of these high speed data generation scenarios,
+various objects are connected together with different relations and data exchanges  in a graph-structured manner. The
+Semantic Web community has been considering the aspect of implementing streaming RDF generator and benchmarks; however, there is still a clear lack on considering this aspect in other important and timely domains such as IoT.
+%Thus, there is a crucial need to tackle this aspect.
+In addition, graph streaming generators should  consider some specific aspects for the stream processing domains such as the out-of-order handling (late arrivals)~\cite{li2008out} and the variety in the schemas and formats of the different data streaming sources.
+It is also recommended for the streaming graph generators to support the distributed environment as this is the most common scenario for such type of applications.
+
+\subsection{Evolving Graph Data}
+\label{sec:evolving}
+As user requirements as well as environments change, most of the existing
+applications naturally evolve over time, at least to some extent. This evolution
+usually influences the structure of the data and consequently all the related
+parts of the application (i.e., storage strategies, operations, indexes etc.).
+In the world of graph data such graphs that change with time are denoted as \emph{evolving}, \emph{temporal}, \emph{dynamic}, or \emph{time-varying}.
+They can be modeled as labeled graphs, where the labels capture some measure of time~\cite{Michail2015}.
+
+The evolution of graphs can be considered from multiple perspectives. We can
+assume a static set of nodes and a varying set of edges.  Or, there are
+applications where the graphs only ``grow'', i.e., the set of nodes and/or edges
+is only extended with new items. In the most general case we can assume any
+changes in both set of nodes and set of edges. Anyway with the evolution aspect
+the complexity of classical graph problems increases
+significantly~\cite{Michail2015,Wu:2014:PPT:2732939.2732945}. In some graph
+applications, such as, e.g., social networks, the evolution of the data is a
+significant aspect, especially in the activity
+graphs~\cite{Kumar:2006:SEO:1150402.1150476,doreian1997evolution,Hellmann2014583,wang2013,Viswanath:2009:EUI:1592665.1592675,Kossinets88}.
+However, as shown
+in~\cite{Leskovec:2005:RMT:2101235.2101254,Leskovec:2005:GOT:1081870.1081893},
+evolving graphs have further specific features. For example, some graphs grow
+over time according to a \emph{densification power law} which means that in real
+graphs, edges tend to appear at a higher pace than vertices, meaning that these
+graphs densify as they grow. Also the way the new edges are distributed has the
+effect of a shrinking diameter that ends up stabilizing as the graph grows with time.
+
+A related problem is \emph{data versioning} and its respective ability to query across multiple versions of data or to carry out general analysis.
+%Considering graph
+%data this problem is also common, for example  in the area of Linked
+This problem has been investigated for instance within the domain of Linked
+Open Data~\cite{DBLP:conf/semweb/Papakonstantinou16,DBLP:conf/esws/MeimarisP16,fernandez2015towards,fernandez2015bear}.
+
+The respective data generator should hence be able to simulate a natural growth
+and/or changes in the structure of the graph with regards to the various
+features of distinct use cases. However,  even though the area of dynamic graphs
+is intensively studied, surprisingly there seem to exist only very few proposals
+of a generator for dealing with this area.
+In~\cite{GoerkeKlugeSchumm2012_1000029825} the authors focus on \emph{clustering
+dynamic graphs}, i.e. graphs where the clustering corresponds to the partition
+of nodes into natural groups based on the concept of density of edges within and between the clusters. The generator generates a time series
+of random graphs $G_0, G_1, ..., G_n$, where $G_t$ emerges from $G_{t-1}$ via
+successive atomic updates like for instance, the insertion of a vertex or the removal of an
+edge. The generator dynamically monitors the ground truth clustering, and the probability
+of the updates is chosen in such a way that the ground truth is
+maintained while the randomness of the generated graph is kept.
+
+Another recent proposal of a generator~\cite{mlg2018_42} of temporal graphs
+results from an observation that small subgraph patterns in networks, called
+\emph{network motifs} or \emph{graphlets}, are crucial indicators of the
+structure and the evolution of the
+graphs~\cite{Paranjape:2017:MTN:3018661.3018731}. For a given graph and a
+predefined ordered list of structural atomic motifs the generator first computes
+the distribution of the motifs in the graph. The distribution is then used to
+generate a synthetic graph with the same features.
+
+%\paragraph{} Following the same recursion idea,
+%paper~\cite{Leskovec:2005:RMT:2101235.2101254} uses Kronecker multiplication to
+%generate self-similar graphs. The network starts with an initial graph G1 that
+%contains $N_1$ nodes and $E_1$ edges. Using matrix recursion, larger successive
+%graphs $G_2, G_3, ... G_n$ are generated. The $k$-th graph $G_k$ contains $N_k
+%= N^k_1$ nodes. Many graphs often densify over time, exhibiting a growth in the
+%number of edges that is superlinear to the number of nodes. Kronecker
+%multiplication produces graphs with a fixed diameter and a densification power
+%law degree distribution with exponent $k = log(E_1)/log(N_1)$. The graph
+%generation process introduces a staircase effect in the nodes' degrees, and
+%each community consists of smaller nested communities that are formed through
+%expansion and recursion.
+
+\subsection{Multi-Model Data}
+With the dawn of Big Data and especially its Variety, another key 3V characteristic, new types of
+database management systems have emerged. One of the most interesting ones
+are the so-called \emph{multi-model databases}~\cite{Lu:2019:MDN:3341324.3323214} that enable to store and
+thus query across structurally different data, including unstructured, semi-structured, and structured. There exist various types of
+multi-model systems combining  distinct subsets of Big Data structures including graph data.
+For example, OrientDB\footnote{\url{http://orientdb.com/orientdb/}} which has been mainly designed as an object DBMS currently supports graph, document,
+key/value, and object models. Such type of DBMSs also needs a specific
+data generator that would enable
+to test new features and analyze efficiency of operations. However, since the
+multi-model systems are in the context of Big Data rather new, there exist only
+a few benchmarks targeting multi-model DBMSs (such as
+Bigframe~\cite{journals/pvldb/KunjirKB14} or UniBench~\cite{conf/cidr/lu17})
+with limited capabilities.
+
+Another interesting approach to multi-model data is to adopt a unifying
+expressive graph data model, so-called \emph{property graph data
+model}~\cite{BFVY18}. Such a  model allows to specify multi-edges and list of
+properties for the nodes. Synthetic graph generators for property graphs and its
+companion standard graph query language~\cite{Angles18,AnglesABBFGLPPS18} are also needed in order to boost
+their availability and adoption for different communities.
+
+\subsection{Machine Learning Based Graph Generation}
+
+With the advent of neural networks and specially generative adversarial networks
+(GANs)~\cite{goodfellow2014generative}, several researchers have started to
+explore their application to generate graphs. This is the case of
+~\cite{simonovsky2018graphvae,kipf2016variational,grover2018graphite,li2018learning,you2018graphrnn},
+which present several generative models to generate realistic graphs.  Such
+techniques still suffer from several problems. For instance, some of them are
+limited to learn from a single
+graph~\cite{kipf2016variational,grover2018graphite} or generate small
+graphs~\cite{simonovsky2018graphvae,you2018graphrnn,li2018learning}. The
+technique proposed in~\cite{you2018graphrnn} is capable of generating graphs
+with complex edge dependencies (e.g. community structure) and is not restricted
+to graphs of a fixed size. However, there are still in general several open
+challenges, including the capability of learning from and generating large graphs comparable
+in size to those typically used for benchmarking, and robust generation
+techniques with structural guarantees (e.g. degree distribution, clustering
+coefficient, etc.).
+
+\subsection{Privacy-Preserving Graph Generation}
+
+A lot of work has been conducted on techniques for publishing social network
+graphs with privacy guarantees~\cite{wu2010survey}. However, the topic of
+generating social graphs with a realistic structure yet private has been barely explored.
+
+Most of the existing work falls within the topic of graph generation with ``differential
+privacy''~\cite{dwork2009differential} guarantees. More specifically, in
+~\cite{wang2013preserving} the authors develop a differential privacy graph
+generation approach based on the dK-graph generation
+model~\cite{mahadevan2006systematic} that outperforms the Stochastic Kronecker
+Graph Model~\cite{Leskovec:2005:RMT:2101235.2101254} in terms of the produced structural properties,
+even though the results show that there is still room for improvement.
+
+Following this line of research, recent work~\cite{qin2017generating} extends the notion of differential privacy
+and propose an ``edge local differential privacy'' based graph generation
+method. The proposed method allows generating privacy preserving synthetic social
+graphs without the need of a centralized data curator, while preserving structural
+properties more accurately than straw-hat methods such as Randomized
+Neighbor Lists (based on randomized response~\cite{dwork2014algorithmic}) and
+Degree-based Graph Generation (which perturbates the original graph degrees
+using the Laplace mechanism~\cite{dwork2009differential}). Again, even though the
+proposed technique outperforms the baselines, the results show that there is
+still room for improving the structural properties of the
+generated graph.
+
+\section{Conclusion}
+\label{sec:conclusion}
+
+Graph data occur in a vast amount of distinct applications, such as biology, chemistry, physics, computer science, or social sciences, to name just a few.
+Graphs form one of the most complex data structures requiring specific and usually sophisticated approaches for processing and analysis.
+The history of graph theory,  that started from when these structures and their respective algorithms were studied, can be traced back to the 18th century.
+
+With the recent dawn of Big Data there have  been more occurrences of large scale graphs where the efficiency   of  processing methods is critical.
+Approaches that work for smaller scale graphs often cannot be used, the data need to be processed in a distributed way and hence the efficiency is influenced by other aspects, such as limits of data transport.
+In addition, distribution of graphs, especially for highly connected cases, is a difficult task.
+Thus extensive testing of these methods for graphs of various sizes and structural complexity is extremely important.
+
+The aim of this survey was to provide a thorough overview and comparison of graph data generators.
+We do not limit ourselves to a single application domain, but we cover the currently most popular areas of graph data processing.
+We believe that this wide scope provides a uniquely useful insight into state-of-the-art tools as well as open issues for both researchers and practitioners.
 
 \begin{acks}
-The authors would like to thank Dr. Kamesh Madduri for consultations and suggestions on the covered areas.
+The authors would like to thank Dr.
+Kamesh Madduri for consultations and suggestions on the covered areas.
+The work of Sherif Sakr is funded by the European Regional Development Funds via the Mobilitas Plus programme (grant MOBTT75)
 \end{acks}

### 2019-12-18 reviewresponse.tex
Response Letter

% Copyright Javier Sánchez-Monedero.
% Please report bugs and suggestions to (jsanchezm at uco.es)
%
% This document is released under a Creative Commons Licence
% CC-BY-SA (http://creativecommons.org/licenses/by-sa/3.0/)
%
% BASIC INSTRUCTIONS:
% 1. Load and set up proper language packages
% 2. Complete the paper data commands
% 3. Use commands \rcomment and \newtext as shown in the example

\documentclass[a4paper,twoside,11pt]{reviewresponse}

% 1. Load and set up proper language packages
%\usepackage[utf8x]{inputenc}
\usepackage[latin9]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{float}
\usepackage{subfig}
\usepackage{epstopdf}

% 2. Complete the paper data
\newcommand{\myAuthors}{{Angela Bonifati, Irena Holoubova, Arnau Part-Perez and Sherif Sakr} }
\newcommand{\myEmail}{holubova@ksi.mff.cuni.cz}
\newcommand{\myTitle}{Response Letter to Review Comments}
\newcommand{\myShortTitle}{CSUR-2019-0568}
\newcommand{\myJournal}{Journal: ACM Computing Surveys}
\newcommand{\manuTitle}{Manuscript Title: \textbf{Graph Generators: State of the Art and Open Challenges}}
\newcommand{\manuId}{Manuscript ID: \textbf{CSUR-2019-0568}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\usepackage[linktoc=all]{hyperref}
\usepackage[linktoc=all,bookmarks,bookmarksopen=true,bookmarksnumbered=true]{hyperref}

\hypersetup{
pdftitle = {\myTitle},
pdfsubject = {\myJournal\xspace},
colorlinks = true,
linkcolor=black!70!green,          % color of internal links
citecolor=black!70!green,        % color of links to bibliography
filecolor=magenta,      % color of file links
urlcolor=black!70!green           % color of external links
}

\begin{document}

\thispagestyle{plain}

\begin{center}
 {\LARGE\myTitle} \vspace{0.5cm} \\
  {\large\myJournal} \vspace{0.5cm} \\
  \large\manuTitle \vspace{0.5cm} \\
  \manuId \vspace{0.5cm} \\
 \myAuthors \\
 \url{\myEmail} \vspace{1cm} \\
\end{center}

%\tableofcontents

\begin{abstract}
The authors would like to thank the reviewers for their detailed, useful and constructive comments to improve the manuscript. Please find below our responses to the comments which have been included in the attached revised version for our manuscript.
\end{abstract}

\section{Reviewer 1 (Minor Revision)}

\rcomment{
I do not think it is necessary to modify the review to include lengthy discussions of graph generators that are primarily used for null models or molecule design. However, the introduction should more clearly delineate the scope of the review as being focused on graph generators that are designed for benchmarking.
}

\textbf{Response}

Thanks for the comment. We have specified benchmarking as a main context for our surveyed graph generators.

\section{Reviewer 2 (Accept)}

The reviewer has been satisfied with the manuscript and did not have comments to address.

\section{Reviewer 3 (Minor Revision)}

\rcomment{
Authors say MapReduce-based BTER algorithm can generate large graphs in a reasonable amount of time. I find such a sentence too vague to be of any substance. What is a large graph? What is a reasonable amount of time? }

\textbf{Response}

.....

\rcomment{List of Typos}
\textbf{Response}
Thanks for the listed typos. We have addressed them and made an additional proof-reading round of the manuscript.

% Uncomment in case references are needed
%\bibliographystyle{apalike}
%\bibliography{response}

\end{document}

### 2019-12-18 main.tex
Response Letter

@@
 graph generators by focusing on those that are pertinent and suitable for
-data-intensive tasks. Our aim is to cover a wide range of currently popular
+data-intensive tasks and benchmarking context. Our aim is to cover a wide range of currently popular
 areas of graph data processing. In particular, we consider graph generation

### 2019-12-21 main.tex
Sherif Commit

@@
 configurable graph generators that reproduce real-world graph properties and provide unique tuning opportunities for
-algorithms and tools handling such data.
+algorithms and tools handling such data~\cite{sakr2013processing,sakr2016large}.
 %As a consequence, also in the world of graphs there has appeared a number of graph data generators which enable to  reproduce the respective real-world linking properties and gauge the effectiveness of a particular algorithm.

### 2020-01-20 main.tex
Rev. 3 - comment fixed
Changed Arnau's affiliation

@@
 ARNAU PRAT-P\'{E}REZ
-\affil{DAMA-UPC, Universitat Polit\`ecnica de Catalunya, Spain}
+\affil{Sparsity-Technologies, Barcelona, Spain}
 SHERIF SAKR
@@
 expectation will not be realized internally in the group) is computed and used to connect
-nodes from different groups at random. The authors describe a highly scalable
-MapReduce-based implementation that is able to generate large graphs (consisting of
-billions of nodes) in a reasonable time budget.
+nodes from different groups at random. 
+The authors report that BTER is able to generate graphs with billions of edges. 
+%The authors describe a highly scalable
+%MapReduce-based implementation that is able to generate large graphs (consisting of
+%billions of nodes) in a reasonable time budget.
 

### 2020-01-21 main.tex
Irena - grant no update

@@
 \begin{acks}
-The authors would like to thank Dr.
-Kamesh Madduri for consultations and suggestions on the covered areas.
-The work of Sherif Sakr is funded by the European Regional Development Funds via the Mobilitas Plus programme (grant MOBTT75)
+The authors would like to thank Dr. Kamesh Madduri for consultations and suggestions on the covered areas.
+The work of Sherif Sakr is funded by the European Regional Development Funds via the Mobilitas Plus programme (grant MOBTT75).
+The work of Irena Holubov\'{a} was partially funded by the GA\v{C}R project no. 19-01641S.
 \end{acks}

### 2020-01-23 main.tex
Updated affiliation Arnau Prat
New CSUR style

@@
 
-\documentclass[prodmode,acmtecs]{acmsmall} % Aptara syntax
+%\documentclass[prodmode,acmtecs]{acmsmall} % Aptara syntax
+\RequirePackage{rotating}
+\documentclass[acmsmall]{acmart}
 
@@
 % Metadata Information
-\acmVolume{0}
-\acmNumber{0}
-\acmArticle{0}
-\acmYear{2019}
-\acmMonth{0}
+%\acmVolume{0}
+%\acmNumber{0}
+%\acmArticle{0}
+%\acmYear{2019}
+%\acmMonth{0}
 
@@
 % DOI
-\doi{0000001.0000001}
+%\doi{0000001.0000001}
+
+\AtBeginDocument{%
+  \providecommand\BibTeX{{%
+    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
+
+\setcopyright{acmcopyright}
+\acmJournal{CSUR}
+\acmYear{2020} \acmVolume{1} \acmNumber{1} \acmArticle{1} \acmMonth{1} \acmPrice{15.00}\acmDOI{10.1145/3379445}
 
 %ISSN
-\issn{0360-0300}
+%\issn{0360-0300}
 
@@
 % Page heads
-\markboth{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr}{Graph Generators: State of the Art and Open Challenges}
+%\markboth{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr}{Graph Generators: State of the Art and Open Challenges}
 
@@
 \title{Graph Generators: State of the Art and Open Challenges}
-\author{
-ANGELA BONIFATI
-\affil{Lyon 1 University, France}
-IRENA HOLUBOV\'{A}
-\affil{Charles University, Prague, Czech Republic}
-ARNAU PRAT-P\'{E}REZ
-\affil{Sparsity-Technologies, Barcelona, Spain}
-SHERIF SAKR
-\affil{University of Tartu, Estonia}
+
+\author{Angela Bonifati}
+\affiliation{%
+  \institution{Lyon 1 University}
+  \streetaddress{Liris CNRS Campus La Doua 23-25 Avenue Pierre de Coubertin}
+  \city{Villerubanne}
+  \postcode{69622}
+  \country{France}
    }
+\email{angela.bonifati@univ-lyon1.fr}
+
+\author{Irena Holubov\'a}
+\affiliation{%
+  \institution{Charles University}
+  \streetaddress{Faculty of Mathematics and Physics, Department of Software Engineering, Malostransk\'{e} n\'{a}m. 25}
+  \city{Prague}
+  \postcode{118 00}
+  \country{Czech Republic}
+  }
+\email{holubova@ksi.mff.cuni.cz}
+
+\author{Arnau Prat-P\'erez}
+\affiliation{%
+  \institution{Sparsity-Technologies}
+  \streetaddress{Compte Guell 13}
+  \city{Barcelona}
+  \country{Spain}}
+\email{aprat@ac.upc.edu}
+
+\author{Sherif Sakr}
+\affiliation{%
+  \institution{University of Tartu}
+  \streetaddress{J Liivi 2}
+  \city{Tartu}
+  \postcode{50409}
+  \country{Estonia}
+  }
+\email{sherif.sakr@ut.ee}
+
+\renewcommand{\shortauthors}{Bonifati, Holubov\'a, Prat-P\'erez, and Sakr}
+
+%\author{
+%ANGELA BONIFATI
+%\affil{Lyon 1 University, France}
+%IRENA HOLUBOV\'{A}
+%\affil{Charles University, Prague, Czech Republic}
+%ARNAU PRAT-P\'{E}REZ
+%\affil{Sparsity-Technologies, Barcelona, Spain}
+%SHERIF SAKR
+%\affil{University of Tartu, Estonia}
+%}
 % NOTE! Affiliations placed here should be for the institution where the
@@
 
-\acmformat{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr, 2019.
-Graph Generators: State of the Art and Open Challenges.}
+%\acmformat{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr, 2019.
+%Graph Generators: State of the Art and Open Challenges.}
 % At a minimum you need to supply the author names, year and a title.
@@
 
-\begin{bottomstuff}
-%This work is supported by ...
-Author's addresses:
-A. Bonifati, Universit\'{e} Claude Bernard Lyon 1, Liris CNRS Campus La
-Doua 23-25 Avenue Pierre de Coubertin, 69622 Villerubanne, France;
-I. Holubov\'{a}, Department of Software Engineering, Faculty of Mathematics and Physics, Charles University, Malostransk\'{e} n\'{a}m. 25, 118 00 Praha~1, Czech Republic;
-A. Prat-P\'erez, DAMA-UPC, Universitat Polit\`ecnica de Catalunya, Jordi Girona 1-3, 08034 Barcelona, Spain;
-S. Sakr, University of Tartu, J Liivi 2, Tartu 50409, Estonia.
-\end{bottomstuff}
+%\begin{bottomstuff}
+%%This work is supported by ...
+%Author's addresses:
+%A. Bonifati, Universit\'{e} Claude Bernard Lyon 1, Liris CNRS Campus La
+%Doua 23-25 Avenue Pierre de Coubertin, 69622 Villerubanne, France;
+%I. Holubov\'{a}, Department of Software Engineering, Faculty of Mathematics and Physics, Charles University, Malostransk\'{e} n\'{a}m. 25, 118 00 Praha~1, Czech Republic;
+%A. Prat-P\'erez, Sparsity-Technologies, Compte Guell 13, Barcelona, Spain;
+%S. Sakr, University of Tartu, J Liivi 2, Tartu 50409, Estonia.
+%\end{bottomstuff}
 
@@
 \centering
-\tbl{Key characteristics of the generators} {
+\caption{Key characteristics of the generators} 
 \begin{tabular}{| c | l | p{2cm} |  p{2cm} | p{1.3cm} |  l | l | p{3.2cm} | p{2cm} | l | }
@@
 %  & & & & & & & &  &   \\
-\end{tabular} }
+\end{tabular} 
 \label{tab:comparisonCharacteristics}
@@
 \centering
-\tbl{Overlapping of classes of generators} {
+\caption{Overlapping of classes of generators} 
 \begin{tabular}{| c | l | l | l | l | l | l | l | }
@@
 %\hline
-\end{tabular} }
+\end{tabular} 
 \label{tab:overlapping}
@@
 % Bibliography
-\bibliographystyle{ACM-Reference-Format-Journals}
+\bibliographystyle{ACM-Reference-Format}
 \bibliography{biblio}
@@
 \end{document}
+\endinput
